### 2019-04-23 LaTeX_code/RW_convergence_results.tex
working variable forecast

\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

\setbeamertemplate{caption}[numbered]

\title{Prediction of Power Generation}
\subtitle{ Waleed Alhaddad}

\begin{document}
\setbeamercolor{background canvas}{bg=blue!3}
\begin{frame}
\titlepage
\end{frame}
%
%\begin{frame}\frametitle{Model}
%
%\begin{equation}
%\begin{split}
%dX(t) &= a(X(t); \theta) dt + b (X(t); \theta ) dW(t) \quad t > 0 \\
%X(0) & = x_0
%\end{split}\label{main}
%\end{equation}
%where $X(t) \in [0,1]$ is the normalized stochastic analogue of the power generated $p(t)$. 
%
%\begin{enumerate}
%\item Drift is given by $a(X(t),t ; \theta) = - \theta (t) \Big(X(t)-p(t)\Big)$
%\item Non-centered diffusion is given by: $ b (X(t); \theta) = \sqrt{2\alpha(t) \theta (t) p(t) \Big(1-p(t)\Big) X(t) \Big(1-X(t)\Big)}  $
%\end{enumerate}
%
%\end{frame}

\begin{frame}[label=guide]\frametitle{ Reader's Guide }

List of changes in this iteration:
\begin{itemize}
\item Implemented Beta transitions
\item Implemented time dependent forecast
\item Numerically solve for the first two moments
\item Time dependent path variability parameter
\item Convergence results of all the above
\end{itemize}

Next steps:
\begin{itemize}
\item Use real data and forecast.
\item Try exponential decay in the mean reversion.
\end{itemize}

Note :
\begin{itemize}
\item Green slides: possible future extensions
\item Red slides: notes to be removed
\end{itemize}

\end{frame}

\begin{frame}\frametitle{ Toy model with Synthetic Data }
We generate paths from an SDE  with given parameters using Monte Carlo simulation and then fit the model to check the retrievability of the parameters. We consider the following cases:
\begin{itemize}
\item[1:]  Constant parameter Wiener process: finite and infinite horizon.
\item[2:]  Controlled Wiener process within an interval.
\item[3:]  Controlled Wiener process centered around a given function. 
\end{itemize}
\end{frame}

\begin{frame}\frametitle{ Stochastic Differential Equation }
Given the SDE
\begin{equation}
\begin{split}
dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
X_0 & = x_0
\end{split}\label{main}
\end{equation}
Consider a set of N observations, $ X=\{ X_{t_0^N} , X_{t_1^N} ,\ldots , X_{t_N^N} \}$ observed within intervals $\Delta_N$.

\begin{itemize}
\item $\Delta_N$: is any function of the number of samples, $N$. For example, $\Delta_N = \frac{1}{N}$.
\item $a(X_t; \bm{\theta})$ is the drift function \textcolor{brown}{(add technical conditions here)}
\item $b (X_t; \bm{\theta} )$ is the diffusion function \textcolor{brown}{(add technical conditions here)}
\item $\bm{\theta}$ is a vector of constant parameters
\end{itemize}
\end{frame}

\begin{frame}\frametitle{ likelihood function }
We have the Likelihood function of the transition density

\begin{equation}
\mathcal{L}(\theta;X) = \prod\limits_{i=1}^n\rho( {X_{i+1}|X_{i}}, \bm{\theta})  \rho(X_0) 
\end{equation}
Consider a Gaussian transition density,
\begin{equation*}
\mathcal{L}(\bm{\theta}; X) = \prod\limits_{i=1}^n  \frac{1}{\sqrt{2 \pi b(X_i,\bm{\theta})^2 dt}  } \exp\Big(\frac{-((X_{i+1}-X_i) - a(X_i,\bm{\theta}) dt )^2}{2b(X_i,\bm{\theta})^2 dt}\Big) \rho(X_0)
\end{equation*}

We take the improper prior $\rho(X_0)=1$.
\end{frame}

\begin{frame}\frametitle{ Case 1: Constant Parameters }
For a fixed $b(X_t; \bm{\theta})=\sigma$ and a fixed $a(X_t; \bm{\theta})=\mu$. We observe that varying the sampling and discretization parameters affects the convergence behavior.

We consider the following three situations:
\begin{enumerate}
\item[1.1] Infinite Horizon expansion caused by increasing samples N\\ ( increasing $N$ and $\Delta_N$ is fixed).
\item[1.2] Infinite Horizon expansion caused by increasing intervals $\Delta_N$ \\ ( fixed $N$ and increasing decreasing $\Delta_N$).
\item[1.3] Finite Horizon expansion with sample compression, i.e where $\Delta_N=\frac{T}{N}$ \\ (increasing $N$, fixed $T$).
\end{enumerate}
\end{frame}

\begin{frame}\frametitle{ Case 1: Implementation }

In the following, we use  L-BFGS-B algorithm to optimize the likelihood with bounds on $\sigma$ being positive. And we use $\mu=100$ and $\sigma=10$ for the path generation. We denote the estimators of $\mu$ and $\sigma$ by  $\hat{\mu}$ and $\hat{\sigma}$ where,

\begin{equation}
 \hat{\mu} = \arg \underset{\mu \in \R}{\max} \ \mathcal{L}(\bm{\theta};X) \quad \quad  \quad \quad \hat{\sigma} = \arg \underset{\sigma \in \R^+}{\max} \mathcal{L}(\bm{\theta};X)
\end{equation}

\end{frame}

\begin{frame}%\frametitle{ Case 1: Scenario illustration }
The above cases can be seen clearly in the illustration below.
\begin{figure}
  \includegraphics[scale=0.4]{Figures/data_horizons.pdf}
  %\label{fig:boat1}
\end{figure}
\end{frame}

%\begin{itemize}
%\item $ \sigma (X(t); \theta) = \sqrt{2 p(t) \Big(1-p(t)\Big) X(t) \Big(1-X(t)\Big)}  $
%\item $b(X(t),t ; \theta) = -  \Big(X(t)-p(t)\Big)$
%\end{itemize}

\begin{frame}\frametitle{ Case 1.1: Constant Parameters \\
 Infinite Horizon expansion caused by increasing samples N }
An increase of the number of samples $N$ in a growing time interval $T$. In this case, we obtain  convergence of the order $\frac{1}{\sqrt{N}}$ as expected.

\begin{figure}
  \includegraphics[scale=0.45]{Figures/case11v2.pdf}
  \caption{convergence in the case of infinite horizon expansion caused by increasing samples N}
  %\label{fig:boat1}
\end{figure}

\end{frame}

\begin{frame}\frametitle{ Case 1.2: Constant Parameters \\
 Infinite Horizon expansion caused by increasing intervals dt }
In this case, the estimator $\hat{\sigma}$ of the diffusion coefficient is inconsistent. This is because the time interval between the samples is increasing and so we do not have as much information about the variation of the process. However, the drift estimator $\hat{\mu}$ is still consistent. We have not seen any theoretical proof of this situation.

\begin{figure}
  \includegraphics[scale=0.45]{Figures/case12v3.pdf}
  \caption{convergence rate in the case of infinite horizon expansion caused by increasing intervals $\Delta_N$}
  %\label{fig:boat1}
\end{figure}

\end{frame}

\begin{frame}\frametitle{ Case 1.3: Constant Parameters \\
 Finite Horizon expansion with sample compression }
In this case, we observe increasing number of  samples in a fixed time interval (sample compression).In this case the drift estimator $\mu$ is inconsistent while the diffusion estimator $\sigma$ is consistent. This situation  matches the theoretical discussion in [1].

\begin{figure}
  \includegraphics[scale=0.45]{Figures/case13v2.pdf}
  \caption{Convergence rate in the case of finite horizon expansion with sample compression  }
  %\label{fig:boat1}
\end{figure}

We will see next that there are no consistent estimators of the drift  term $b(X(t), \theta)$ in this case.

\end{frame}

\begin{frame}\frametitle{ Remarks }
\begin{enumerate}
\item  It is easier to obtain convergence in the diffusion coefficient. Because the estimator of the diffusion has access to  information from the infinite variation of the wiener process while the drift does not. We can show this theoretically from the efficiency condition of the estimators.
\item The convergence generally follows Monte Carlo's convergence rate in terms of sampling as expected. This statement is wrong in a high frequency setting, as we have different convergence rate for estimator of the diffusion and than for the estimator of the drift as we will see next. The estimator of the drift converges slower than the Monte Carlo rate given that both are consistent.
\end{enumerate}

\end{frame}

\begin{frame}\frametitle{Motivation of high frequency SDE data}

High frequency situations are not uncommon and extreme  but may happen for data that looks reasonable. For instance, in some cases  weekly data is treated as high frequency data . A situation is considered high frequency with respect to the amount of  variation in the drift term [1] (or in regards to the speed at which it reverts to the mean).  \\

This also important for building confidence intervals as the limiting distribution of our estimator may not be Gaussian. For example, in the setting of high frequency data and fixed time $T$ (case 1.3 above) the limiting distribution of the estimator is path dependent and is given by a normal variance-mixture distribution which can be heavy tailed with no finite moments [1]. However, in this case, a  modification of the estimator can help in achieving  a Gaussian limiting distribution of the estimator.

Please note that in the setting of high frequency SDE data, we have two possibilities:
\begin{itemize}
\item Finite Horizon (fixed time $T$): this corresponds to case 1.3 above.
\item Infinite Horizon: this corresponds to other two cases.
\end{itemize}

\end{frame}

\begin{frame}\frametitle{Convergence of the drift estimator for high frequency  SDE  \\(Case 1.3 / Finite Horizon)}

In a high frequency setting with finite horizon (case 1.3), there are \textbf{no} consistent estimators of the drift term $a(X_t, \bm{\theta})$ (see [1]) as we break the following condition :\\

Given the following SDE,
\begin{equation}
\begin{split}
dX_t &= a(X_t; \alpha) dt + b(X_t; \beta ) dW_t \quad t > 0 \\
X(0) & = x_0
\end{split}\label{main}
\end{equation}

the drift estimator  $\hat{\alpha}$ of the parameter set $\alpha$ of the system is consistent if and only if
\begin{equation}
n \Delta_n \to \infty  \label{conv_cond}
\end{equation}
And this condition contradicts having a finite horizon as we trivially have $T=N \Delta_N \to \infty$. If the  condition (\ref{conv_cond}) is not satisfied, we cannot have a consistent estimator  $\hat{\alpha}$ of the drift. However, the estimator $\hat{\beta}$ of the diffusion term $b (X_t; \beta)$ is still consistent regardless. 
\end{frame}

\begin{frame}\frametitle{Convergence of the drift estimator for high frequency  SDE  \\(Case 1.3 / Finite Horizon)}
To show this result numerically, we pick any $\Delta_n$ such that $T=n \Delta_n \to \infty$. In this example, we modify the non-consistent  drift parameter estimator (case $1.3$) such that 
\begin{equation}
dt=\frac{T}{N} \quad  \rightarrow  \quad dt=\frac{T}{\sqrt{N}}
\end{equation}
Then we recover back the convergence of the other cases as this replacement turns the finite horizon to an infinite horizon. 
\end{frame}

\begin{frame}\frametitle{Numerical Convergence for high frequency  SDE}
In this numerical example, we take $\Delta_N = \frac{T}{\sqrt{N}}$ as an example.
\begin{equation}
\text{Finite Horizon:} \ dt=\frac{T}{N} \quad  \text{versus} \quad \text{Infinite Horizon:} \ dt=\frac{T}{\sqrt{N}}
\end{equation}
We confirm  condition (\ref{conv_cond}) numerically. It is clear that in the finite horizon case the estimator of the diffusion $\hat{\sigma}$ converges while the estimator of the drift $\hat{\mu}$ is not consistent. Whereas, in the infinite horizon case, we obtain the expected convergence in both parameters.
\begin{figure}
  \includegraphics[scale=0.35]{Figures/case13v2.pdf}
   \includegraphics[scale=0.35]{Figures/case13infinite.pdf}
  \caption{Right side: Finite horizon with $dt=\frac{T}{N}$, Left side: Infinite horizon with $dt=\frac{T}{\sqrt{N}}$   }
  %\label{fig:boat1}
\end{figure}

\end{frame}

\begin{frame}\frametitle{Convergence for high frequency SDE data}
We can show that the score function of the likelihood is an efficient martingale estimating function and that the obtained estimator is optimal\footnote{If we consider an approximate martingale estimator function such as the pseudo likelihood, then we require an extra condition that $n \Delta_n^{2 \kappa - 1} \to 0 $ where $\kappa$ is the order of $\Delta_N$ in RHS of the expectation (\ref{expec_martin})}. Then we have the following convergence rates [3]:

For a finite Horizon (fixed T)
\begin{equation}
\hat{\alpha} \text{ is not consistent } \quad \text{and} \quad relative \ error(\hat{\beta}) \propto \frac{1}{\sqrt{N}}
\end{equation}
For an infinite Horizon ($T \to \infty$)
\begin{equation}
relative \ error(\hat{\alpha})  \propto \frac{1}{\sqrt{N\Delta_N}} \quad \text{and} \quad  relative \ error(\hat{\beta}) \propto \frac{1}{\sqrt{N}} 
\end{equation}
Note that the estimator $\hat{\alpha}$ of the drift is affected by the time discretization while the estimator $\hat{\beta}$ of the diffusion is independent of the time discretization.

\end{frame}

\begin{frame}\frametitle{High Frequency  SDE General Convergence }
Consider a set of N observations, $X= \{ X_{t_0^N} , X_{t_1^N} ,\ldots , X_{t_N^N} \}$ and the following martingale estimator function,
\begin{equation}
G_n(\gamma) = \sum\limits_{i=1}^N g(\Delta_N , X_{t_{i}^N},X_{t_{i-1}^N} ; \gamma )
\end{equation}
where $t_{i}^n = i \Delta_n $, $\gamma = (\alpha, \beta)$ and $g=(g_1, g_2)$ .
In our martingale case\footnote{The results can also be adapted to a non martingale estimating function such as a pseudo likelihood},we must have,
\begin{equation}
E_\gamma \Big(    g(\Delta_N , X_{t_{i}^N},X_{t_{i-1}^N} ; \gamma) \Big| X_{t_{i-1}^N}  \Big) = 0
\label{expec_martin}
\end{equation} where the $\hat{\beta}$ estimator is given by solving $ G_n(\gamma) = 0 $.

\end{frame}

{
\setbeamercolor{background canvas}{bg=green!30}

\begin{frame}\frametitle{High Frequency  SDE -  Possible Extensions}

\begin{itemize}
\item Try to understand the limit of when we need to switch to the high frequency from the low frequency regime. That is how it depends on the speed of the  mean reversion in our model.
\item Get the martingale estimator function of the Gaussian transition density explicitly.
\item State the optimality and efficiency of the estimators explicitly.
\item Obtain the stated theoretical convergence rate.
\item Try to show theoretically why in case 1.2 , the diffusion estimator is not consistent.
\item Understand and state the conditions under which we have a unique parameter estimation to our SDE.
\end{itemize}

\end{frame}
}

\begin{frame}\frametitle{References}
\begin{itemize}
\item[][1] Jakobsen, N. M., \& Sørensen, M. (2017). Efficient estimation for diffusions sampled at high frequency over a fixed time interval. Bernoulli, 23(3), 1874-1910. doi:10.3150/15-bej799
\item[][2] Sørensen, M. (2007). Efficient Estimation for Ergodic Diffusions Sampled at High Frequency. SSRN Electronic Journal. doi:10.2139/ssrn.1150694
\item[][3] Kessler, M., Lindner, A., \& Sørensen, M. (2012). Statistical methods for stochastic differential equations. Boca Raton, FL: Chapman \& Hall/CRC.
\end{itemize}

\end{frame}

\begin{frame}\frametitle{ Paths as IID samples  }

We have the Likelihood function of the transition density

\begin{equation}
\mathcal{L}(\theta;X) = \prod\limits_{j=1}^M\prod\limits_{i=1}^N\rho( {X_{j,i+1}|X_{j,i}}, \bm{\theta})  \rho(X_0) 
\end{equation}
Consider a Gaussian transition density,
\begin{equation*}
\mathcal{L}(\bm{\theta}; X) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N  \frac{1}{\sqrt{2 \pi b(X_{j,i};\bm{\theta})^2 dt}  } \exp\Big(\frac{-((X_{j,i+1}-X_{j,i}) - a(X_{j,i};\bm{\theta}) dt )^2}{2b(X_{j,i};\bm{\theta})^2 dt}\Big) \rho(X_0)
\end{equation*}

We take the improper prior $\rho(X_0)=1$.

\end{frame}

\begin{frame}\frametitle{ Paths as IID samples - Implementation }

As before, we use  L-BFGS-B algorithm to optimize the likelihood with bounds on $\sigma$ being positive. We denote the estimators of $\mu$ and $\sigma$ by  $\hat{\mu}$ and $\hat{\sigma}$ where,

\begin{equation}
 \hat{\mu} = \arg \underset{\mu \in \R}{\max} \ \mathcal{L}(\bm{\theta};X) \quad \quad  \quad \quad \hat{\sigma} = \arg \underset{\sigma \in \R^+}{\max} \mathcal{L}(\bm{\theta};X)
\end{equation}

\end{frame}

\begin{frame}\frametitle{ Paths as IID samples - Convergence }
We have Monte Carlo convergence in terms of samples as expected.
\begin{figure}
  \includegraphics[scale=0.5]{Figures/conv_M_unbounded.pdf}
   \includegraphics[scale=0.5]{Figures/conv_N_unbounded.pdf}
  \caption{ Optimized using L-BFGS-B algorithm. True parameters used are $\mu = 100$ and $\sigma = 10$.M is the number of paths and N is the number of samples.    }
  %\label{fig:boat1}
\end{figure}

\end{frame}

\begin{frame}\frametitle{Case 2: Controlled Wiener process in a unit box }
We have the SDE,
\begin{equation}
\begin{split}
dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
X_0 & = 0
\end{split}\label{main}
\end{equation}
Consider a set of N observations, $X= \{ X_{t_0^N} , X_{t_1^N} ,\ldots , X_{t_N^N} \}$ on intervals of $\Delta_N$.\\ We choose,
\begin{equation}
a_{i+1}(X_i; \bm{\theta})= \mu X_i(\frac{1}{2} - X_i)  \quad \quad b_{i+1} (X_i; \bm{\theta} )=\sigma X_i (1-X_i)
\end{equation}
We choose $ 0<\sigma <<1$ and $\mu\in (0,1]$. Then, we have contained the Wiener process in the interval $[0,1]$ with high probability.

\end{frame}

\begin{frame}\frametitle{Case 2: Controlled Wiener process in a unit box }
We see that the process is contained within the unit box as we kill the diffusion coefficient if we touch the boundary. Additionally, the drift coefficient is always directed towards the center line $\frac{1}{2}$ of the unit box.
\begin{figure}
  \includegraphics[scale=0.45]{Figures/Wiener_box.pdf}
  \caption{ With  high probability the wiener process stays inside the box as $\mu \in (0,1]$ and $\sigma << 1$ }.
  %\label{fig:boat1}
\end{figure}

\end{frame}

\begin{frame}\frametitle{Case 2: Controlled Wiener process in a unit box - Parameter Inference }

We obtain the same convergence as before,

\begin{figure}
  \includegraphics[scale=0.5]{Figures/conv_M_box.pdf}
   \includegraphics[scale=0.5]{Figures/conv_N_box.pdf}
  \caption{Optimized using L-BFGS-B algorithm. True parameters used are $\mu = 0.5$ and $\sigma = 0.1$. M is the number of paths and N is the number of samples.   }
  %\label{fig:boat1}
\end{figure}

\end{frame}

\begin{frame}\frametitle{Case 3: Controlled Wiener process around a given function }
We have the SDE,
\begin{equation}
\begin{split}
dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
X_0 & = 0
\end{split}\label{main}
\end{equation}
Consider a set of N observations, $X= \{ X_{t_0^N} , X_{t_1^N} ,\ldots , X_{t_N^N} \}$ on intervals of $\Delta_N$.\\ We choose,
\begin{equation}
a_{i+1}(X_i; \bm{\theta})= \mu X_i(\frac{1}{2}(1 + p_i )- X_i)  \quad \quad b_{i+1} (X_i; \bm{\theta} )=\sigma X_i (1-X_i)
\end{equation}
We choose $ 0<\sigma <<1$ and $\mu\in (0,1]$. Then, we have contained the Wiener process in the interval $[0,1]$ with high probability. Additionally, we add mean reversion to $\frac{1}{2}(1 + p_i ) $ where  $p_i = \sin(\frac{i}{N} 2\pi)$.

\end{frame}

\begin{frame}\frametitle{Case 3: Controlled Wiener process following a given function }
We see that the process follows the sine wave  closely when the  drift parameter $\mu \approx 1$ and that we have a shift artifact when the drift parameter $\mu<<1$. Note that the process does not  escape the unit box as the diffusion is controlled and the drift is directed towards the function which is always inside the unit box.
\begin{figure}
  \includegraphics[scale=0.4]{Figures/Wiener_sine_box.pdf}
   \includegraphics[scale=0.4]{Figures/conv_sine_shift.pdf}
  \caption{Illustrative examples: On the right, we see the controlled wiener process responding to the boundary  by killing the diffusion at the peaks of the sine wave. On the right we observe an unintended  shift artifact when the drift parameter $\mu<<1$.   }
  %\label{fig:boat1}
\end{figure}

\end{frame}

\begin{frame}\frametitle{Case 3: Controlled Wiener process around a function - Paramter Inference }
We obtain the same convergence as before,

\begin{figure}
  \includegraphics[scale=0.5]{Figures/conv_M_sine.pdf}
   \includegraphics[scale=0.5]{Figures/conv_N_sine.pdf}
  \caption{ Optimized using L-BFGS-B algorithm. True parameters used are $\mu = 100$ and $\sigma = 10$.M is the number of paths and N is the number of samples.    }
  \label{fig:sine}
\end{figure}

\end{frame}

\begin{frame}\frametitle{ Case 4: Following deterministic functions }
As we construct processes that follow or revert to deterministic function it is natural to state the SDE in terms of deviations from the deterministic function. Then, we have for $V_t= X_t - p_t$

\begin{equation}
\begin{split}
dV_t &= a(V_t; \bm{\theta}_t) dt + b (V_t; \bm{\theta}_t ) dW_t \quad t > 0 \\
V_0 & = v_0
\end{split}\label{main_V}
\end{equation}

where we choose $ a(V_t; \bm{\theta}_t) = - \theta_t V_t$ to have mean reversion with exponential speed in time controlled by some strictly positive parameter $\theta_t$. To keep the process within a unit box, we choose $ b (V_t; \bm{\theta} )= \sqrt{ 2 \alpha_t \theta_t p_t (1-p_t)X_t (1-X_t)   }$

\end{frame}

\begin{frame}\frametitle{ Case 4: Implementation }
In the previous sections we relied on the Euler discretization of SDEs in order to obtain our estimators through the Maximum Likelihood approach. However, this introduces errors in the likelihood similar to the observed error in the wiener process following the sine wave in (\ref{fig:sine}). To prevent such artifacts, we solve for the moments of the process defined by the SDE in (\ref{main_V}). We have,

\begin{equation}
\begin{split}
\E [V_t^k] &=  \E \Big[ \Big( \int a(V_t; \bm{\theta}_t) dt + \int b (V_t; \bm{\theta}_t ) dW_t \Big)^k \Big] \quad t > 0 \\
V_0 & = v_0
\end{split}\label{main_V_expectations}
\end{equation}
For a Gaussian approximation, we are interested in the first two moments.

\end{frame}

\begin{frame}\frametitle{ Case 4: Implementation - first moment }
The first moment $(k=1)$ is given by,

\begin{equation}
\begin{split}
 m_1(t) =\E V_t &=  \E \Big[  \int a(V_t; \bm{\theta}_t) dt \Big] + \E \Big[ \int b (V_t; \bm{\theta}_t ) dW_t  \Big] \\
 & = \E \Big[  \int a(V_t; \bm{\theta}_t) dt \Big]
\end{split}\label{main_V_1_moment}
\end{equation}
In our case, the drift is linear and is given by $ a(V_t; \bm{\theta}_t) = - \theta_t V_t$. then, we have 
\begin{equation}
\begin{split}
 & m_1(t) =\E V_t =     \Big[  \int - \theta_t \E V_t dt \Big] 
 \iff \frac{dm_1(t)}{dt}=    - \theta_t m_1(t) \ \ ; \quad m_1(0)=\E[V_0]= v_0
\end{split}\label{main_V_1_moment}
\end{equation}
This is an ODE which has solutions of the form, 
\begin{equation}
m_1(t) = v_0 \exp ( - \int_0^t \theta_s \ ds ) 
\end{equation}

\end{frame}

\begin{frame}\frametitle{ Case 4: Implementation - second moment }
The second moment $(k=2)$ is given by,

\begin{equation}
\begin{split}
  =\E V_t^2 &=  \E \Big[ \Big( \int a(V_t; \bm{\theta}_t) dt + \int b (V_t; \bm{\theta}_t ) dW_t \Big)^2 \Big] \\
\end{split}\label{main_V_2_moment}
\end{equation}
Let $Y_t=g(V_t)=V_t^2$ then $g_t= 0 , \ g^{'} (V_t) = 2V_t$ and $g^{''} (V_t) = 2$. Using $It\hat{o}$ and Taylor, 
\begin{equation}
\begin{split}
dY_t =  \frac{\partial g}{\partial t} dt &+  \frac{\partial g}{\partial v} \Big(a (V_t; \bm{\theta}_t ) \ dt + b (V_t; \bm{\theta}_t ) dW_t  \Big)\\
& + \frac{1}{2} \frac{\partial^2 g}{\partial v^2} \Big(a (V_t; \bm{\theta}_t ) \ dt + b (V_t; \bm{\theta}_t ) dW_t  \Big)^2 + \mathcal{O}(dV_t^3)
\end{split}
\end{equation}
As $dt \to 0$, we have
\begin{equation}
\begin{split}
dY_t &=  \frac{\partial g}{\partial t} + \Big( a (V_t; \bm{\theta}_t ) \frac{\partial g}{\partial v}  + \frac{b^2 (V_t; \bm{\theta}_t )}{2} \frac{\partial^2 g}{\partial v^2} \Big) dt + b (V_t; \bm{\theta}_t ) \frac{\partial g}{\partial v} dW_t  \\
&= 2\Big( a (V_t; \bm{\theta}_t ) V_t  + \frac{b^2 (V_t; \bm{\theta}_t )}{2}  \Big) dt +  2V_t b (V_t; \bm{\theta}_t ) dW_t
\end{split}
\end{equation}

\end{frame}

\begin{frame}\frametitle{ Case 4: Implementation - second moment }
The second moment $(k=2)$ is given by,

\begin{equation}
\begin{split}
\E [V_t^2] =  \E Y_t &= 2  \E\Big[ \int \Big( a (V_t; \bm{\theta}_t ) V_t  + \frac{b^2 (V_t; \bm{\theta}_t )}{2}  \Big) dt \Big] +  2 \E \Big[ \int V_t b (V_t; \bm{\theta}_t ) dW_t \Big]\\
&= 2  \E\Big[ \int \Big( a (V_t; \bm{\theta}_t ) V_t  + \frac{b^2 (V_t; \bm{\theta}_t )}{2}  \Big) dt \Big]\\
\end{split}
\end{equation}
In our case, the drift is $ a(V_t; \bm{\theta}_t) = - \theta_t V_t$ and the diffusion is given by $ b (V_t; \bm{\theta} )= \sqrt{ 2 \alpha_t \theta_t p_t (1-p_t)X_t (1-X_t)   } =  \sqrt{ 2 \alpha_t \theta_t p_t (1-p_t)(V_t + p_t) (1-V_t-p_t)   }$. Then,
\begin{equation*}
\begin{split}
m_{2}&(t)=\E [V_t^2] = 2  \int \Big( - \theta_t \E[V_t^2]  +  \alpha_t \theta_t p_t (1-p_t)\E[(V_t + p_t) (1-V_t-p_t) ] \Big) dt \\
&=2  \int \Big( - \theta_t \E[V_t^2]  +  \alpha_t \theta_t p_t (1-p_t)( p_t(1 - p_t) +(1-2p_t)\E[V_t] - \E[V_t^2] ) \Big) dt \\
&=2  \int \Big( -\E[V_t^2] [\theta_t + \alpha_t \theta_t p_t(1-p_t) ] + \E[V_t][\alpha_t \theta_t p_t (1-p_t) (1-2p_t)] + \alpha_t \theta_t p_t^2(1-p_t)^2 \Big) dt \\
\end{split}
\end{equation*}

\end{frame}

\begin{frame}\frametitle{ Case 4: Implementation - second moment }
The second moment $m_2(t)$ is given by solving the ODE,

\begin{equation*}
\begin{split}
\frac{d m_{2}(t)}{dt}&=2 \Big( -m_{2}(t) [\theta_t + \alpha_t \theta_t p_t(1-p_t) ] + m_{1}(t)[\alpha_t \theta_t p_t (1-p_t) (1-2p_t)] + \alpha_t \theta_t p_t^2(1-p_t)^2 \Big) \\
\end{split}
\end{equation*}
where $m_2(0) = \E[V_0^2] = v_0^2$ and has a solution of the form,
\begin{equation*}
\begin{split}
&m_{2}(t) = m_{2}(0) \exp \Big( -2 \int_0^t  [\theta_\tau + \alpha_\tau \theta_\tau p_\tau(1-p_\tau) ] \ d\tau  \Big) + \\
& 2 \int\limits_{0}^{t}   \exp \Big( -2 \int_0^s  [\theta_\tau + \alpha_\tau \theta_\tau p_\tau(1-p_\tau) ] \ d\tau \Big) \Big( m_{1}(t-s)[\alpha_{t-s} \theta_{t-s} p_{t-s} (1-p_{t-s}) (1-2p_{t-s})]  \\
& + \alpha_{t-s} \theta_{t-s} p_{t-s}^2(1-p_{t-s})^2 \Big)  \  ds
\end{split}
\end{equation*}

\end{frame}

\begin{frame}\frametitle{Following deterministic functions - Cases }

We consider the following cases:
\begin{itemize}
\item[4.1] Constant parameters $\bm{\theta}_t = \bm{\theta} $
	\begin{itemize}
	\item[4.1.1] reverting to a constant function
	\item[4.1.2] reverting to a deterministic function
	\end{itemize}
\item[4.2] Time dependent parameters $\bm{\theta}_t$
\end{itemize}

\end{frame}

\begin{frame}\frametitle{ Case 4.1: Following deterministic functions - constant parameters }
In this case, the first moment  $m_1(t)$ reduces to,

\begin{equation}
m_1(t) = v_0 \exp ( -t\theta ) 
\end{equation}
And the second moment $m_2(t)$ reduces to,

\begin{equation*}
\begin{split}
&m_{2}(t) = m_{2}(0) \exp \Big( -2  [t \theta + \alpha \theta \int_0^t    p_\tau (1-p_\tau)  \ d\tau ] \Big) + \\
& 2 \int\limits_{0}^{t}    \exp \Big( -2 [s \theta + \alpha \theta \int_0^s    p_\tau (1-p_\tau)  \ d\tau ] \Big) \Big( m_{1}(t-s)[\alpha \theta p_{t-s} (1-p_{t-s}) (1-2p_{t-s})]  \\
& + \alpha \theta p_{t-s}^2(1-p_{t-s})^2  \Big) \  ds
\end{split}
\end{equation*}

\end{frame}

\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
For constant forecast $p_t = \frac{1}{2}$ the second moment reduce further,

\begin{equation*}
\begin{split}
&m_{2}(t) = m_{2}(0) \exp \Big( -2 t \theta (1 + \frac{\alpha }{4} ) \Big) +   \frac{\alpha \theta}{8} \int\limits_{0}^{t}  \exp \Big( -2 s \theta (1 + \frac{\alpha }{4} )\Big) \  ds \\
& =m_{2}(0) \exp \Big( -2 t \theta (1 + \frac{\alpha }{4} ) \Big) + \frac{\alpha }{16 (1+ \frac{\alpha}{4})} \Big(1- \exp ( -2 t \theta (1 + \frac{\alpha }{4} ) \Big) 
\end{split}
\end{equation*}
Then the variance is given by,
\begin{equation}
\V[V_t] =m_{2}(0) \exp \Big( -2 t \theta (1 + \frac{\alpha }{4} ) \Big) + \frac{\alpha }{16 (1+ \frac{\alpha}{4})} \Big(1- \exp ( -2 t \theta (1 + \frac{\alpha }{4} ) \Big)   - v_0^2 \exp ( -2t\theta ) 
\end{equation}
Note that the second moment $m_2(0)=v_0^2$ as the previous point $V_{t_{i-1}}=v_0$ deterministic.
%% CHANGE ALL zero lower bounds to t_{i-1} 
\end{frame}

\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }

To conclude, we have the following mean and variance functions,

\begin{equation}
\begin{split}
\E[V_{t_i}| V_{t_{i-1}}=v_0] &= v_0 \exp ( -(t_i - t_{i-1})\theta ) \\
 \V[V_{t_i}| V_{t_{i-1}}=v_0] &= \frac{\alpha }{16 (1+ \frac{\alpha}{4})} \Big(1- \exp ( -2 (t_i - t_{i-1}) \theta (1 + \frac{\alpha }{4} ) \Big) \\
\end{split}
\end{equation}

Next, we discretize  and obtain the likelihood.
\end{frame}

\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
To obtain the likelihood, consider a set of N observations, $X= \{ X_{t_0^N} , X_{t_1^N} ,\ldots , X_{t_N^N} \}$ on intervals of $\Delta_N$. We have $V=X-\frac{1}{2}$ .  Then,

\begin{equation}
\begin{split}
\E[V_{i}| V_{i-1}=v_0] &= v_0 \exp ( -\Delta_N \theta )  \\
 \V[V_{i}| V_{i-1}=v_0] &= \frac{\alpha }{16 (1+ \frac{\alpha}{4})} \Big(1- \exp ( -2 \Delta_N\theta (1 + \frac{\alpha }{4} ) \Big)\\
\end{split}
\end{equation}

The Likelihood  of the transition density is given by,

\begin{equation}
\mathcal{L}(\theta;X) = \prod\limits_{j=1}^M\prod\limits_{i=1}^N\rho( {V_{j,i+1}|V_{j,i}}, \bm{\theta}) 
\end{equation}
And the Gaussian transition density,
\begin{equation*}
\mathcal{L}(\bm{\theta}; V) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N  \frac{1}{\sqrt{2 \pi \V[V_{j,t_i}| V_{j,t_{i-1}}=v_0] }  } \exp\Big(\frac{-(V_{j,i+1}   - \E[V_{j,t_i}| V_{j,t_{i-1}}=v_0] )^2}{2\V[V_{t_i}| V_{j,t_{i-1}}=v_0]}\Big) 
\end{equation*}

\end{frame}

\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
We obtain the following convergence using the analytical moments obtained from the $V_t$ process and enforcing that the parameters $\theta$ and $\alpha$ are non-negative.

\begin{figure}
   \includegraphics[scale=0.22]{Figures/conv_M_moments_constant_func_sym.jpg}
    \includegraphics[scale=0.22]{Figures/conv_N_moments_constant_fun_symjpg.jpg}
  \caption{This is done for true parameters $\theta = 0.5$ and $\alpha=1$ using  L-BFGS-B optimization algorithm }
  %\label{fig:boat1}
\end{figure}
\end{frame}

\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
Further, we note that the  inference on the drift needs special care in situations of high speed reversion to the mean. Such situations seem to occur in the following cases:
\begin{itemize}
\item  $ \theta > > 1$  and big enough $\alpha$
\item  $\Delta_N > > 1$

\end{itemize}
In both cases, we see a flattening in the likelihood in the direction of the drift parameter $\theta$ which  causes the optimizer to return inconsistent estimates of the drift parameter $\theta$. These two cases are applicable if the function or the process oscillates at a high frequency with respect to the other.

\end{frame}

\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }

\begin{figure}
    \includegraphics[scale=0.22]{Figures/sample_moments_constant_func_1_01.pdf}
    \includegraphics[scale=0.22]{Figures/sample_moments_constant_func_10_01.pdf}
      \includegraphics[scale=0.22]{Figures/sample_moments_constant_func_100_01.pdf}

    \includegraphics[scale=0.22]{Figures/conv_M_moments_constant_func_1_01.pdf}
    \includegraphics[scale=0.22]{Figures/conv_M_moments_constant_func_10_01.pdf}
      \includegraphics[scale=0.22]{Figures/conv_M_moments_constant_func_100_01.pdf}

          \includegraphics[scale=0.22]{Figures/conv_N_moments_constant_fun_1_01.pdf}
    \includegraphics[scale=0.22]{Figures/conv_N_moments_constant_fun_10_01.pdf}
      \includegraphics[scale=0.22]{Figures/conv_N_moments_constant_fun_100_01.pdf}

  \caption{We can see how an increase of $\theta >>1$ with big enough $\alpha$ causes sharp oscillations that make the inference of  $\theta$ unfeasible.  }
  %\label{fig:boat1}
\end{figure}
\end{frame}

\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
In the second case of increasing $\Delta_N$, we see the following flattening of the likelihood in the direction of $\theta$.
\begin{figure}
    \includegraphics[scale=0.5]{Figures/dt_increasing_moments.pdf}

  \caption{We can see how an increase of time intervals $\Delta_N >>1$  causes a flattening of the likelihood making the valley of the optimal $\theta$ shallower  until the  inference of  $\theta$ becomes unfeasible.  }
  %\label{fig:boat1}
\end{figure}
\end{frame}

\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }

Question: How can we quantify the mean reversion of an SDE   ?  \\

The reversion to the mean is not only determined by the parameter $\theta$ but also by the diffusion term. We can see this in the following example,

\begin{equation}
dX_t = (1+X_t)dt + (1+X_t^2) dW_t
\end{equation}

which at first glance does not seem mean reverting, but in fact,  it is mean reverting. The reversion is driven  solely  by diffusion term in this case.  This is a case of volatility induced stationary, as the non-linearity in the diffusion term are responsible for the mean reversion. A similar non-linearity is present in our model and quantifying the effective mean reversion  will help determine if we are in the convergent regime  where our estimator of the drift is consistent or not.

Regarding, the specific application to wind forecasts this should not be an issue as the forecast and the recorded data are unlikely to oscillate around each other at a "high" frequency.

\end{frame}

\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }

Answer: Yes, it is true that such SDE's are stationary even though they are not "mean reverting". The  "mean reversion" or the "pull" is induced solely by the diffusion term. We can show that

\begin{equation}
dX_t = (1+X_t)dt + (1+X_t^2) dW_t
\end{equation} 
is stationary. Even though its associated process with constant diffusion $\sigma$
\begin{equation}
dX_t = (1+X_t)dt + \sigma dW_t
\end{equation}
is clearly non-stationary. We can do that using the tools we will introduce next to check and find the stationary distributions of our SDEs. Namely, using the scale and speed densities. 
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
Consider an SDE,
\begin{equation}
\begin{split}
dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
X_0 & = x_0
\end{split}\label{main}
\end{equation}
We define the scale density $s(x)$,
\begin{equation}
s(x) = exp \Big[ \int^x - \frac{2  a(y; \bm{\theta})}{b^2 (y; \bm{\theta} )}\ dy \Big]
\end{equation}
And the speed density $m(x)$,
\begin{equation}
m(x) = \frac{1}{b^2 (y; \bm{\theta}) \  s(x)}
\end{equation}

\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }

A unique stationary distribution of the process $X_t$ exists if and only if 
\begin{equation}
\int_{x_0}^r s(x) \ dx = \infty \quad \int_{l}^{x_0} s(x) \ dx = \infty \quad \int_l^r m(x) \ dx < \infty
\end{equation}
where $x_0 \in (l,r)$ and $(l,r)$ is an interval where $b^2 (y; \bm{\theta} ) > 0$

\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
Considering the  SDE of a process following a constant forecast $p$,
\begin{equation}
\begin{split}
dX_t &= -\theta(X_t - p) dt + \sqrt{2 \theta \alpha p(1-p) X_t (1-X_t)} dW_t \quad t > 0 \\
X_0 & = x_0
\end{split}\label{main}
\end{equation}
We obtain the scale density $s(x)$ with integrability condition $\frac{p}{a} \leq -1 $ and $\frac{1-p}{a} \leq -1$
\begin{equation}
s(x) = exp \Big[ \int^x - \frac{2  a(y; \bm{\theta})}{b^2 (y; \bm{\theta} )}\ dy \Big] = exp \Big[ \int^x_{x_0}  \frac{y-p}{a y (y-1)}\ dy \Big]  \propto (1-x)^{\frac{1-p}{a}} x^{p/a}
\end{equation}
where $a= - \alpha p(1-p) <0$.Then the speed density $m(x)$ becomes, 
\begin{equation}
m(x) = \frac{1}{b^2 (y; \bm{\theta}) \  s(x)} \propto (1-x)^{-\frac{1-p}{a}-1} x^{-\frac{p}{a}-1}
\end{equation}
We note that $(l,r) = (-\infty, \infty)$ is where $b^2 (y; \bm{\theta} ) >0$. Let $x_0 \in (l,r)$. Taking $x_0=1$ we see that
\begin{equation}
\int_{x_0}^r s(x) \ dx = \infty \quad \int_{l}^{x_0} s(x) \ dx = \infty \quad \int_l^r m(x) \ dx < \infty
\end{equation}
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
Under the condition,
\begin{equation}
\begin{cases}
\frac{p}{a} \leq -1\\
\frac{1-p}{a} \leq -1\\
\end{cases}\iff
\min (p, 1-p) \geq -a \iff  \min (p, 1-p) \geq \alpha p(1-p)
\end{equation}
For example, if forecast is constant $ p = \frac{1}{2}$, the condition becomes $\alpha \leq 2$.

we conclude that there exists a unique stationary distribution of  $X_t$ and its proportional to the speed density,
\begin{equation}
m(x)\propto (1-x)^{-\frac{1-p}{a}-1} x^{-\frac{p}{a}-1}
\end{equation}
 which is the kernal of a Beta distribution with shape parameters
\begin{equation}
  Beta \ \Big( \frac{p}{\alpha (1-p)}, \frac{1}{\alpha p } \Big)
\end{equation}
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
Now we consider the centered process $V_t= X_t - p$,
\begin{equation}
\begin{split}
dX_t &= -\theta V_t dt + \sqrt{2 \theta \alpha p(1-p) (V_t +p ) (1-V_t-p)} dW_t \quad t > 0 \\
X_0 & = x_0
\end{split}\label{main}
\end{equation}
We obtain the scale density $s(x)$,
\begin{equation}
s(x) = exp \Big[ \int^x - \frac{2  a(y; \bm{\theta})}{b^2 (y; \bm{\theta} )}\ dy \Big] = exp \Big[ \int^x_{x_0} \frac{y-p}{a y^2 + by +c}\ dy \Big]  
\end{equation}
where,
\begin{equation}
\begin{cases}
a&=  \alpha p(1-p)\\
b&=  \alpha p(1-p)(2p-1)\\
c&=  \alpha p^2(1-p)^2\\
\end{cases}
\end{equation}
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
To simplfy, we choose the constant forecast to be $p=\frac{1}{2}$. Then we have,

\begin{equation}
\begin{cases}
a&=  \frac{\alpha}{4} \\
b&=  0 \\
c&=  \frac{\alpha}{16} \\
\end{cases}
\end{equation}
and the scale density becomes, 
\begin{equation}
\begin{split}
s(x) &= exp \Big[ \int^x - \frac{2  a(y; \bm{\theta})}{b^2 (y; \bm{\theta} )}\ dy \Big] = exp \Big[ \int^x_{x_0} \frac{y}{a y^2 +c}\ dy \Big] =exp \Big[ \int^x_{x_0} \frac{y}{\frac{\alpha }{16}+\frac{\alpha  y^2}{4}}\ dy \Big]\\
& \propto \left(4 v^2+1\right)^{2/\alpha } \quad \quad (\alpha >0)
\end{split}
\end{equation}
Then we have the speed density $m(x)$,
\begin{equation}
m(x) = \frac{1}{b^2 (y; \bm{\theta}) \  s(x)} \propto \left(4 v^2+1\right)^{-\frac{\alpha +2}{\alpha }}
\end{equation}
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
We proceed to check if it is stationary.

We note that $(l,r) = (-\infty, \infty)$ is where $b^2 (y; \bm{\theta} ) >0$. Let $x_0 \in (l,r)$. Taking $x_0=0$, we see that
\begin{equation}
\int_{x_0}^r s(x) \ dx = \infty \quad \int_{l}^{x_0} s(x) \ dx = \infty \quad \int_l^r m(x) \ dx < \infty
\end{equation}
So we conclude that it is a stationary distribution of $V_t$ and its unique.
Hence, the kernal of the invarient distribution of the process $V_t$ with constant forecast $p=\frac{1}{2}$ is $\pi(v)= \frac{\sqrt{\pi} \  \Gamma (\frac{1}{2}+ \frac{2}{\alpha})}{\Gamma(\frac{2+\alpha}{\alpha})}\left(1+4 v^2\right)^{-\frac{\alpha +2}{\alpha }}$. Note that it almost resembles a t-student distribution.
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }

\begin{figure}
    \includegraphics[scale=0.9]{Figures/invarient_Vt.pdf}
  \caption{ The stationary distribution $\pi(v)$ of the process $V_t$ is symmetric with heavy tails.}
  %\label{fig:boat1}
\end{figure}

\end{frame}

\begin{frame}\frametitle{Following deterministic functions - Cases }

In an improved model, we incorperate  Beta density transitions. We repeat the same cases as follows:
\begin{itemize}
\item[5.1] Constant parameters $\bm{\theta}_t = \bm{\theta} $
	\begin{itemize}
	\item[5.1.1] reverting to a constant function
	\item[5.1.2] reverting to a deterministic function
	\end{itemize}
\item[5.2] Time dependent parameters $\bm{\theta}_t$
\end{itemize}

However, first lets discuss why and how do we incorperate the Beta transition densities.

\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
Recall that both $X_t$ and $V_t$ are controlled processes that are constrained within a unit box. The symmetry of the Gaussian transition density of these two processes indicate that we have some probability outside the unit box once the forecast touches the boundry. There are many ways to fix this behaviour:
\begin{enumerate}
\item Use a Beta transition density for all the transitions while matching the moments of the Gaussian transition density.
\item Use a Beta transition density only when the transition density of the process touches the boundry of the unit box.This depends on the width and position of the transition density.
\begin{enumerate}
\item match the parameters of the Beta transition with the moments of the Gaussian transition.
\item Not to match the moments of the Gaussian and introdude the beta parameters as two additional hyperparameters (increasing the degrees of freedom).
\end{enumerate}
\end{enumerate}

\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }

If we like to enforce that the Beta transition matches the moments of the Gaussian, then
we can solve for the paramters of the Beta distribution in terms of the parameters of the Gaussian transition density.

First, lets consider the non-centered process $X_t$. In that case, we choose standard Beta distribution which has support on $x \in [0,1]$. Then solving for its parameters in terms of the parameters of the Gaussian transition denisty, to obtain

\begin{equation} 
\alpha = \Big(  \frac{1-\tilde{\mu}}{\tilde{\sigma}^2} -\frac{1}{\tilde{\mu}}   \Big)\tilde{\mu}^2 \quad \quad \beta =  \alpha \Big(\frac{1}{\tilde{\mu}} -1 \Big)
\end{equation}
where $\tilde{\sigma}^2$ is the variance of the Gaussian transition density of the process and $\tilde{\mu}$ is its mean.
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
To ensure the existence of such a Beta distribution with the parameters required
\begin{equation} 
\alpha = \Big(  \frac{1-\tilde{\mu}}{\tilde{\sigma}^2} -\frac{1}{\tilde{\mu}}   \Big)\tilde{\mu}^2 \quad \quad \beta =  \alpha \Big(\frac{1}{\tilde{\mu}} -1 \Big)
\end{equation}
we have the followind conditions by the definition of the standard Beta distribution:
\begin{enumerate}
\item $x \in [0,1]$.
\item Its shape parameters $\alpha$ and $\beta$ must be positive definite.
\end{enumerate}
Solution (this only applies to Euler realizations due to time discretization):
\begin{enumerate}
\item Discard realizations $X_t$ outside the range $(0,1)$.
\item Ensure that $\alpha >0$ and $\beta >0 $ with high probability.
\end{enumerate}
The first condition is automatically satisfied with high probability. The second condition introduces the following restrictions:
\begin{equation}
\alpha >0 ,\ \beta >0 \iff  0< \tilde{\mu}_t < 1  \ \text{and} \  \tilde{\sigma}_t^2 < \tilde{\mu}_t - \tilde{\mu}_t^2
\end{equation}
while the first restriction $ 0< \tilde{\mu}_t < 1$ holds with very high probability. The second restricts the second moment of the process $X_t$ not to exceed its mean,  i.e $\E[X_t^2] \leq \tilde{\mu}_t \quad \forall t$
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
Next, we consider the centered process $V_t$. Since the process $V_t$ is  inside the range $(-1,1)$ with high probability, the standard Beta distribution cannot model its transitions. Therefore, we translate the distribution to have support on $[a,b]=[-1,1]$.  We use the linear transformation $y= g(x)= a + (b-a) x $ then we have
\begin{equation}
\  g^{-1}(y)= \frac{a-y}{b-a} \quad \text{and} \quad \Big| \frac{\partial g^{-1}(y)}{\partial y }  \Big| = \frac{1}{b-a}
\end{equation}
And the general Beta distribution becomes, 
\begin{equation}
f_Y(y)= f_X(g^{-1}(y) ) \Big| \frac{\partial g^{-1}(y)}{\partial y }  \Big| = \frac{1}{B(\alpha, \beta) (b-a)} \Big(\frac{a-y}{b-a}\Big)^{\alpha -1}\Big(1-\frac{a-y}{b-a} \Big)^{\beta -1}
\end{equation}
and we have,
\begin{equation}
\E[Y]= a + (b-a) \E[X] = a + (b-a) \frac{\alpha}{\alpha + \beta}
\end{equation}
\begin{equation}
\V[Y]= (b-a)^2 \V[X] = (b-a)^2 \frac{\alpha \beta}{(\alpha + \beta)^2 (\alpha + \beta + 1)}
\end{equation}
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
Next, we need to solve the system in terms of the mean and variance of the process $V_t$.
\begin{equation}
\begin{cases}
\tilde{\mu}_t=a + (b-a) \frac{\alpha}{\alpha + \beta}\\
\tilde{\sigma}_t^2= (b-a)^2 \frac{\alpha \beta}{(\alpha + \beta)^2 (\alpha + \beta + 1)}\\
\end{cases}
\end{equation}
to obtain, 
\begin{equation}
\alpha = \frac{(\tilde{\mu}_t-a) \left(\tilde{\mu}_t^2-\tilde{\mu}_t (a+b)+\tilde{\sigma}_t^2+a b\right)}{\tilde{\sigma}_t^2 (a-b)}
\end{equation}

\begin{equation}
\beta = \frac{(\tilde{\mu}_t-b) \left(\tilde{\mu}_t^2-\tilde{\mu}_t (a+b)+\tilde{\sigma}_t^2+a b\right)}{\tilde{\sigma}_t^2 (b-a)}
\end{equation}
then for our interval of interest $[a,b]=[-1,1]$, we have

\begin{equation}
\alpha = - \frac{(1+\tilde{\mu}_t )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \quad \quad \beta =  \frac{(\tilde{\mu}_t-1 )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \label{param_transformed_beta}
\end{equation}

\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
As before, for the general Beta distribution on the interval $[a,b]=[-1,1]$, we must have that
\begin{enumerate}
\item $x \in [-1,1]$.
\item Its shape parameters $\alpha$ and $\beta$ must be positive definite.
\end{enumerate}
Solution (this only applies to Euler realizations due to time discretization):
\begin{enumerate}
\item Discard realizations $V_t$ outside the range $(-1,1)$.
\item Ensure that $\alpha >0$ and $\beta >0 $ with high probability.
\end{enumerate}
The first condition is automatically satisfied with high probability. The second condition introduces the following restrictions:
\begin{equation}
\alpha >0 ,\ \beta >0 \iff  0< \tilde{\mu}_t < 1  \ \text{and} \  \tilde{\sigma}_t^2 < 1 - \tilde{\mu}_t^2
\end{equation}
while the first restriction $ -1< \tilde{\mu}_t < 1$ holds with very high probability. The second restricts the second moment of the process $V_t$ not to exceed one,  i.e.  $\E[V_t^2] \leq 1 \quad \forall t$
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
If we approximate all transitions by a Beta transition density, we obtain the log-likelihood, 
\begin{equation}
\ell(\bm{\theta}; V)= \sum\limits_{j=1}^M \sum\limits_{i=1}^N (\alpha -1)\log(V_{j,i+1}) + (\beta -1) \log(1-V_{j,i+1}) - \log (B(\alpha, \beta))
\end{equation}
where $B(\alpha, \beta)=\frac{\Gamma (\alpha)\Gamma (\beta)}{\Gamma (\alpha + \beta)}$ is the Beta function. And enforcing to match the transition moments of the Gaussian, we have
\begin{equation} 
\alpha = \Big(  \frac{1-E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]}{\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} -\frac{1}{E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]}   \Big)E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]^2 \label{alph}
\end{equation}

\begin{equation} 
 \beta =  \alpha \Big(\frac{1}{\E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]} -1 \Big) \label{gam}
\end{equation}
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
Another approach is to only approximate by a Beta distribution if the transition density of $X_t$ is sufficiently crossing the boarder of the unit box. For example, we approximate by a Beta the samples that satisfy either of the following conditions,
\begin{equation}
\begin{cases}
\mu_{t_i} + 3 \sigma_{t_i} >1\\
\mu_{t_i} - 3 \sigma_{t_i} <0
\end{cases} \iff
\begin{cases}
E[V_{j,t_i}| V_{j,t_{i-1}}=v_0] + p + 3 \sqrt{\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} >1\\
E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]+p - 3 \sqrt{\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} <0
\end{cases}
\end{equation}

If a sample $V_{j,t_{i-1}}$ satisfies either of these conditions, we denote it by $\bar{V}_{j,t_{i-1}}$ and the number of such samples by $\bar{N}$.

%where $B(\alpha, \beta)=\frac{\Gamma (\alpha)\Gamma (\beta)}{\Gamma (\alpha + \beta)}$ is the Beta function.
%\begin{equation} 
%\alpha = \Big(  \frac{1-E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]}{\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} -\frac{1}{E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]}   \Big)E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]^2 
%\end{equation}
%
%\begin{equation} 
% \beta =  \alpha \Big(\frac{1}{\E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]} -1 \Big)
%\end{equation}
\end{frame}

\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
We then construct the following likelihood,

\begin{equation}
\mathcal{L}(\theta;X) = \prod\limits_{j=1}^M \left[ \prod\limits_{i=1}^{N-\bar{N}}\rho( {V_{j,i+1}|V_{j,i}}, \bm{\theta}) \prod\limits_{i=1}^{\bar{N}} \bar{\rho}( {\bar{V}_{j,i+1}|\bar{V}_{j,i}}, \bm{\theta}) \right]
\end{equation}

and the log-likelihood becomes, 
\begin{equation}
\begin{split}
\ell(\bm{\theta}; V)&= \sum\limits_{j=1}^M \Big(  \sum\limits_{i=1}^{\bar{N}} (\alpha -1)\log(\bar{V}_{j,i+1}) + (\beta -1) \log(1-\bar{V}_{j,i+1}) - \log (B(\alpha, \beta))\\
&+ \sum\limits_{i=1}^{N-\bar{N}} - \frac{(V_{j,i+1}   - \E[V_{j,t_i}| V_{j,t_{i-1}}=v_0] )^2}{2\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} - \frac{1}{2} \Big(2 \pi \V[V_{j,t_i}| V_{j,t_{i-1}}=v_0] \Big) \Big)
\end{split}
\end{equation}
where $\alpha$ and $\beta$ are given as in (\ref{alph}) and (\ref{gam}).

\end{frame}

\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent  parameters }
We approximate all transitions by a Beta transition density, we obtain the log-likelihood, 
\begin{equation}
\ell(\bm{\theta}; V)= \sum\limits_{j=1}^M \sum\limits_{i=1}^N (\alpha -1)\log(\frac{V_{j,i+1}+1}{2}) + (\beta -1) \log(1-\frac{V_{j,i+1}+1}{2}) - \log ( 2 B(\alpha, \beta))
\end{equation}

where $\alpha$ and $\beta$ are given as in (\ref{param_transformed_beta}):

\begin{equation}
\alpha = - \frac{(1+\tilde{\mu}_t )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \quad \quad \beta =  \frac{(\tilde{\mu}_t-1 )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \label{param_transformed_beta}
\end{equation}
where we compute the moments numerically before each realization using Euler
\begin{equation}
\tilde{\mu} = V_{j,i-1}e^{- \Delta N \theta}
\end{equation}
\begin{equation}
\begin{split}
\tilde{\sigma}_t^2 =  V_{j,i-1}^2 +& 2\Delta N (-V_{j,i-1}^2(\theta+\alpha\theta p_i (1-p_i) )  + \\
& V_{j,i-1}(\alpha\theta p_i(1-p_i)(1-2p_i )) + \alpha\theta p_i^2(1-p_i)^2) - \tilde{\mu}^2
\end{split}
\end{equation}
where $p_i$ is the discretization of the time dependent forecast.

\end{frame}

\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent parameters }
We generate samples using the previous Euler scheme to numerically compute the moments before each realization.We obtain the following sample paths
\begin{figure}
    \includegraphics[scale=0.33]{Figures/sample_paths_beta_flex_0503.pdf}
        \includegraphics[scale=0.33]{Figures/sample_paths_beta_flex_0505.pdf}

  \caption{ Sample Paths using Beta transitions LHS: $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$. RHS:  $\theta = 0.5$, $\alpha=0.5$   }
  %\label{fig:boat1}
\end{figure}

\end{frame}

\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent parameter }
We perform a convergence test for speed of reversion parameter $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$. We obtain the following convergence result
\begin{figure}
    \includegraphics[scale=0.4]{Figures/conv_M_beta_flex_10.pdf}
    \includegraphics[scale=0.4]{Figures/conv_N_beta_flex_35.pdf}
  \caption{ Convergence results for Beta transitions with $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$   }
  %\label{fig:boat1}
\end{figure}

\end{frame}

%\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
%
%
%\end{frame}
%
%
%
%
%
%
%\begin{frame}\frametitle{ Case 4.2: Following deterministic functions - time dependent parameters }
%
%
%
%\end{frame}

\againframe{guide}

\end{document}

### 2019-04-23 LaTeX_code/abstract_Berlin_NT.tex
working variable forecast

\documentclass[12pt]{article}
\usepackage[table]{xcolor}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage[english]{babel}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{blkarray}
\usepackage{float}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{siunitx}

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{proposition}
\newtheorem{exmp}{Example}[section]\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}
\newtheorem{ex}{Exercise}
\theoremstyle{definition}
\theoremstyle{remark}
\bibliographystyle{elsarticle-num}

\DeclareMathOperator{\sinc}{sinc}
\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\matindex}[1]{\mbox{\scriptsize#1}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\prob}{\mathbb{P}}

\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}

\title{Uncertainty Quantification in Wind Power Forecasting  \\ Conference Abstract}

\author{Waleed Alhaddad \quad  Ra\'ul Fidel Tempone \\ CEMSE, KAUST}

\date{}
\begin{document}
\maketitle

%\pagebreak
%\tableofcontents
%\pagebreak
\section{Abstract 600 char}
Reliable wind power generation forecasting is crucial to meet energy demand, to trade and invest. We propose a model to simulate and quantify uncertainties in such forecasts. This model is based on Stochastic Differential Equations whose time-dependent parameters are inferred using continuous optimization of an approximate Likelihood function. The result is a skew stochastic process that simulates uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects. We apply the model to historical Uruguayan data and forecasts.

\section{Motivation}

The adoption of renewable energy is accelerating due to technological advancements. However, the power generated by renewables is difficult to predict and thus such predictions require advanced uncertainty quantification techniques to ensure the bare minimum of meeting electricity power demands. This is also of importance for energy trading and insurance, that it is to deliver power in an optimal cost-effective way to adhere to a variety of financial contracts. Uncertainty quantification is key in the design of financial contracts and taking investment decisions in the energy sector. Additionally, it assists in the placement and design of renewable power plants.

\section{Introduction}

    We propose a model to simulate and quantify uncertainties in wind power generation forecasts. This model is based on Stochastic Differential Equations (SDEs) whose time-dependent parameters are inferred using optimization techniques of an associated approximate Likelihood function. Through continuous optimization, we find the optimal parameters of an unbounded convex problem with convex constraints.

    We are able to simulate and quantify uncertainties in a variety of wind power generation forecasts while taking into account the skewness of the errors. This method is non-intrusive and is independent of forecasting technology or future developments. Through optimization, we update and tune the parameters of our SDE as we receive new sets of observations and their associated forecasts. Additionally, we are able to compare in a quantitative manner the different forecast technologies and how they behave in different real-world scenarios. This model is to be extended to the uncertainty quantification of other power generation sources such as the uncertainties in the power generation of solar power plants. This introduces new challenges in terms of optimization and modeling. Finally, we apply our model to synthetic and real wind power generation data for benchmarking. We apply the model to Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the period of March 1 to May 31, 2016.

\section{Model}
Wind power generation forecasts have certain properties that need to be satisfied. One such particularity is that the forecasts are limited to the maximum power capabilities of the wind farm. Thus a proposed model for the uncertainties of the forecast must be controlled and restricted to a certain range. Due to this requirement, we propose an SDE whose solution is a controlled stochastic process that is contained inside a given range. Another challenge is when the forecast approaches the boundaries of this power production range. In this case, the errors of the forecast are compressed into a skew or asymmetric distribution. This renders the Gaussian approximations in such situations as unrealistic. Therefore, we propose a new approximate model based on a skew stochastic process.

Another particularity of forecast uncertainties is that the validity of the forecast lessens as time evolves. Usually, such forecasts are prepared on a periodic basis and their uncertainty grows in time. This is taken into account through the mean reversion and variability of the stochastic process associated with the SDE. This behavior is learned through the time-dependent parameters of the SDE.

\section{Conclusion}
We were able to simulate and quantify the uncertainties for a diverse range of forecasts based on the Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the period of March 1 to May 31, 2016. We compare our results to similar works in the literature. And we highlight the importance of asymmetry and the avoidance of phase shift artifacts which we were able to overcome.

\end{document}

### 2019-06-06 cvpr2019AuthorKit/latex/optimization_project.tex
modified drift

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{color}
\usepackage{mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
\title{ On the Uncertainty of Wind Power Forecasts \\  \small{(AMCS Optimization course final project submission)}}

\author{Waleed  Alhaddad\\
King Abdullah University of Science (KAUST)\\
%4700 KAUST, Thuwal, Saudi Arabia\\
{\tt\small waleed.alhaddad@kaust.edu.sa}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
%Ra\'ul  Tempone\\
%KAUST/RWTH Aachen \\
% Templergraben 55, 52062 Aachen, Germany\\
%{\tt\small raul.tempone@kaust.edu.sa}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT

\begin{abstract}
Reliable wind power generation forecasting is crucial to meet energy demand, to trade and invest. We propose a model to simulate and quantify uncertainties in such forecasts. This model is based on Stochastic Differential Equations whose time-dependent parameters are inferred using continuous optimization of an approximate Likelihood function. The result is a skew stochastic process that simulates the uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects. We apply the model to historical Uruguayan data and forecasts.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

    We propose a model to simulate and quantify uncertainties in wind power generation forecasts. This model is based on Stochastic Differential Equations (SDEs) whose time-dependent parameters are inferred using optimization techniques of an associated approximate Likelihood function. Through continuous optimization, we find the optimal parameters of an unbounded convex problem with convex constraints.

    We are able to simulate and quantify uncertainties in a variety of wind power generation forecasts while taking into account the skewness of the errors. This method is non-intrusive and is independent of forecasting technology or future developments. Through optimization, we update and tune the parameters of our SDE as we receive new sets of observations and their associated forecasts. Additionally, we are able to compare in a quantitative manner the different forecast technologies and how they behave in different real-world scenarios. This model is to be extended to the uncertainty quantification of other power generation sources such as the uncertainties in the power generation of solar power plants. This introduces new challenges in terms of optimization and modeling. Finally, we apply our model to synthetic and real wind power generation data for benchmarking. We apply the model to Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the full year 2016-2017.

%-------------------------------------------------------------------------
\subsection{Model}

We propose the following parameterized stochastic differential equation (SDE), 
\begin{equation}
\begin{split}
dV_t &= a(V_t; \bm{\theta}) dt + b (V_t; \bm{\theta} ) dW_t \quad t > 0 \\
V_0 & = v_0
\end{split}\label{main}
\end{equation}

\begin{itemize}
\item $\Delta_N$: any function of the number of samples, $N$. For example, $\Delta_N = \frac{1}{N}$.
\item $a(X_t; \bm{\theta})$: Drift function 
\item $b (X_t; \bm{\theta} )$: Diffusion function 
\item $\bm{\theta}$: a vector of parameters
\item $dW_t$: Standard Wiener random process.
\end{itemize}

To respect the physical restriction of this model, we consider the following diffusion and drift functions for a parameter vector $\bm{\theta} = (\theta, \alpha)$,  
\begin{equation}
\begin{split}
a(V_t; \bm{\theta}) &= - \theta V_t \\
b(V_t; \bm{\theta}) &=\sqrt{2 \theta \alpha p_t(1-p_t) (V_t +p_t ) (1-V_t-p_t)}  \\
\end{split}
\end{equation}

Where
\begin{itemize}
\item $p_t$: Numerical wind power generation forecast.
\item $\theta >0$: Mean reversion parameter.
\item $\alpha>0$: Variablity parameter.
\end{itemize}

The SDE in (\ref{main}) define the stochastic process $V_t$ which can be characterized by its transition denisity. Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed within intervals $\Delta_N$. Then, the transitions of $V_t$ are given by the likelihood function,

\begin{equation}
\mathcal{L}(\theta;V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}}, \bm{\theta})  \rho (V_{j,0}) 
\label{likelihood}
\end{equation}

The standard approach is approximating (\ref{likelihood}) by Gaussian transitions. However, this is inadequate in our case as we expect a skew symmetric stochastic process due to physical restrictions. Thus, we approximate the transitions by a Beta distribution. This is possible by matching the moments of the Beta distributions with the moments of the SDE defined above. The momoments are given by, 
\begin{equation}
\begin{split}
\E [V_t^k] &=  \E \Big[ \Big( \int a(V_t; \bm{\theta}_t) dt + \int b (V_t; \bm{\theta}_t ) dW_t \Big)^k \Big] \quad t > 0 \\
V_0 & = v_0
\end{split}\label{main_V_expectations}
\end{equation}
The above moments define a system of Ordinary Differential Equations,

\begin{equation}
\begin{split}
 \frac{dm_1(t)}{dt} &=    - \theta_t m_1(t)  \\
\frac{d m_{2}(t)}{dt}&= -2m_{2}(t) [\theta_t + \alpha_t \theta_t p_t(1-p_t) ] \\
&+ 2m_{1}(t)[\alpha_t \theta_t p_t (1-p_t) (1-2p_t)] \\
&+ 2\alpha_t \theta_t p_t^2(1-p_t)^2  \\
%m_2(0) = \E[V_0^2] = v_0^2\\
\end{split}
\end{equation}
With initial conditions,

\begin{equation}
\begin{cases}
&m_1(0)=\E[V_0]= v_0 \\
&m_2(0)=\E[V_0^2] = v_0^2 \\
\end{cases}
\end{equation}

where $m_1(t)$ and $m_2(t)$ are the first and second moments of the stochastic process $V_t$. As we are dealing with numerical wind power generation forecasts $p_t$, we do not have a closed form solution to this system of ODEs. Thus, this system is iteratively solved by means of numerical integration.

Once the moments $m_1(t)$ and $m_2(t)$ are obtained, we match them with the shape parameters of the Beta distribution. To allow for negative and positive values of the process $V_t$, we formulate a modified Beta distribution whose support is defined on $[a,b]=[-1,1]$.  We use the linear transformation $y= g(x)= a + (b-a) x $ and we obtain the probability density function,

\begin{equation}
\begin{split}
f_Y(y; \alpha , \beta )&= f_X(g^{-1}(y) ) \Big| \frac{\partial g^{-1}(y)}{\partial y }  \Big| \\
&= \frac{1}{B(\alpha, \beta) (b-a)} \Big(\frac{a-y}{b-a}\Big)^{\alpha -1}\Big(1-\frac{a-y}{b-a} \Big)^{\beta -1} \label{modified_Beta}
\end{split}
\end{equation}
where $B(\cdot,\cdot)$ is the Beta function. Also, we find that
\begin{equation}
\E[Y]= a + (b-a) \frac{\alpha}{\alpha + \beta}
\end{equation}
\begin{equation}
\V[Y]= (b-a)^2 \frac{\alpha \beta}{(\alpha + \beta)^2 (\alpha + \beta + 1)}
\end{equation}

And by matching the moments, we find that

\begin{equation}
\alpha = \frac{(\tilde{\mu}_t-a) \left(\tilde{\mu}_t^2-\tilde{\mu}_t (a+b)+\tilde{\sigma}_t^2+a b\right)}{\tilde{\sigma}_t^2 (a-b)}
\end{equation}
\begin{equation}
\beta = \frac{(\tilde{\mu}_t-b) \left(\tilde{\mu}_t^2-\tilde{\mu}_t (a+b)+\tilde{\sigma}_t^2+a b\right)}{\tilde{\sigma}_t^2 (b-a)}
\end{equation}
where $\tilde{\mu}_t = m_1(t)$ and $\tilde{\sigma}_t^2= m_2(t)- m_1^2(t)$

\subsection{ Likelihood Optimization }

Combining the previous results and (\ref{likelihood}), we can express the log-likelihood function for $M$ paths,
\begin{equation}
\begin{split}
\ell(\alpha, \beta|V)&= \sum\limits_{j=1}^M \sum\limits_{i=1}^N (\alpha -1)\log \left(\frac{V_{j,i+1}+1}{2}\right)\\
& + (\beta -1) \log \left( 1-\frac{V_{j,i+1}+1}{2}\right) - \log \left( 2 B(\alpha, \beta)\right)\\ \label{Likelihood}
\end{split}
\end{equation}

where $\alpha$ and $\beta$ are given by,

\begin{equation}
\alpha = - \frac{(1+\tilde{\mu}_t )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \quad \quad \beta =  \frac{(\tilde{\mu}_t-1 )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \label{param_transformed_beta}
\end{equation}

We will show that the log-likelihood function in (\ref{Likelihood}) is concave. Note that it is sufficient to check the log-likelihood of the standard Beta distribution for concavity since the modified Beta distribution log-likelihood is obtained through non-negative weighted summations and a linear transformation $g(x)$ in the given data that does not affect the parameters of interest. Thus, the concavity is preserved.

We study the concavity of  log-likelihood of the standard Beta,
\begin{equation*}
\ell^*(\alpha, \beta |x)=-\log (B(\alpha ,\beta ))+(\alpha -1) \log (x)+(\beta -1) \log (1-x)\end{equation*}
It has been shown that the Beta function $B(\alpha, \beta)$ is log-concave in both its arguments on $(0, \infty)^2$ (see [1]) and the remaining terms are linear in $\alpha$ and $\beta$. Then, we conclude that the likelihood in (\ref{likelihood}) is indeed log-concave.\\

In order to infer the shape parameters $\alpha$ and $\beta$, we perform the following constrained maximuim likelihood optimization,

\begin{equation}
(\alpha^* , \beta^*) = \arg \underset{\alpha>0, \beta>0}{\min} - \ell(\alpha, \beta | V^{M,N} )
\end{equation}

We solve the above optimization problem using L-BFGS to avoid full numerical computation of the Hessian matrix.

%which has a hessian of the form,
%\[ \mathcal{H}(\ell)=
%\left(
%\begin{array}{cc}
% \psi ^{(1)}(\alpha +\beta )-\psi ^{(1)}(\alpha ) & \psi ^{(1)}(\alpha +\beta ) \\
% \psi ^{(1)}(\alpha +\beta ) & \psi ^{(1)}(\alpha +\beta )-\psi ^{(1)}(\beta ) \\
%\end{array}
%\right) 
%\]
%where $\psi ^{(1)}$ is the trigamma function. $\mathcal{H}$'s determinant is given by,
%
%\begin{equation*}
%|\mathcal{H}| = \psi ^{(1)}(\alpha ) \psi ^{(1)}(\beta )-(\psi ^{(1)}(\alpha )+\psi ^{(1)}(\beta )) \psi ^{(1)}(\alpha +\beta )
%\end{equation*}
%For $\alpha>0$ and $\beta >0$, we have that the trigamma function $\psi ^{(1)}$ is strictly monotonically decreasing and that it satisfies the following inequality,
%\begin{equation}
%0<\frac{1}{x} \leq \psi ^{(1)}(x) \quad \text{for} \ \ x >0
%\end{equation}
%
%Then we have that, 
%\begin{equation}
% \frac{1}{\alpha\beta}<\psi ^{(1)}(\alpha ) \psi ^{(1)}(\beta ) 
%\end{equation}
%
%\begin{equation}
% \frac{1}{\alpha} \frac{1}{\alpha + \beta } <\psi ^{(1)}(\alpha ) \psi ^{(1)}(\alpha + \beta ) 
%\end{equation}
%
%\begin{equation}
% \psi ^{(1)}(\alpha ) \psi ^{(1)}(\beta ) > \psi ^{(1)}(\alpha ) \psi ^{(1)}(\alpha + \beta  ) \geq  \frac{1}{\alpha} \frac{1}{\alpha + \beta } 
%\end{equation}
%
%\begin{equation}
% \psi ^{(1)}(\alpha ) \psi ^{(1)}(\beta ) > \psi ^{(1)}(\beta ) \psi ^{(1)}(\alpha + \beta  ) \geq  \frac{1}{\alpha} \frac{1}{\alpha + \beta } 
%\end{equation}
%
%\begin{equation}
%\left(
%\begin{array}{c}
% -\psi ^{(1)}(\alpha ) \text{x1}^2-\text{x2}^2 \psi ^{(1)}(\beta )+(\text{x1}+\text{x2})^2 \psi ^{(1)}(\alpha
%   +\beta ) \\
%\end{array}
%\right)
%\end{equation}

\subsection{Data}
We apply the aforementioned method to Uruguayan Windpower Generation data and their corresponding numerical wind power production forecast.

The wind power generation data set contains hourly samples of aggregated wind power production throughout the country. The samples are normalized according to the full installation power which varies across the data set. Each sample path contains 72 hourly observations and we have a total of 1217 sample paths spanning the year 2016 to 2017 (87,624 data points).

The numerical wind power generation forecast set contains  1217 forecasts of the wind power generation paths corresponding to the wind power generation data set mentioned above.

\begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.8\linewidth]{forecast_data.eps}
\end{center}
   \caption{Examples of wind power generation from the data set along with the wind power generation forecast.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

%-------------------------------------------------------------------------
\subsection{Results}
 We are able to obtain the parameters based on the complete data sets mentioned earlier. The parameters are given by $(\theta^*, \alpha^*)= (12,2)$. We show in Figure(\ref{fig:ISO}) the contours of the log-likelihood in $(\ref{Likelihood})$ using the full data set.

%We can also see in Figure() that the region surrounding the optimal parameters becomes more defined as we add more sample paths.

In Figure(\ref{fig:6hr}) and (\ref{fig:72hr}), we simulate sample forecast errors using the optimal parameters  $(\theta^*, \alpha^*)= (12,2)$ and obtain the associated confidence bands empirically using 10,000 sample paths for each forecast. Note that the confidence bands obtained are non-trivial and reflect the complexity of the uncertainties in the numerical wind power generation forecasts.

\begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.9\linewidth]{72hr_forecast_CI_343.pdf}
   \includegraphics[width=0.9\linewidth]{72hr_forecast_CI_573.pdf}
   \includegraphics[width=0.9\linewidth]{72hr_forecast_CI_396.pdf}

\end{center}
   \caption{ Examples of confidence bands obtained for the full 72 hour forecasts. }
\label{fig:72hr}
\end{figure}

\begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.9\linewidth]{6hr_forecast_CI_618.pdf}
   \includegraphics[width=0.9\linewidth]{6hr_forecast_CI_38.pdf}
   \includegraphics[width=0.9\linewidth]{6hr_forecast_CI_459.pdf}
\end{center}
   \caption{ Examples of confidence bands obtained for the first 6 hours of the forecasts. This is important as this specific forecasting company recomputes a new forecast every 6 hours.}
\label{fig:6hr}
\end{figure}

\begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.9\linewidth]{ISO_lines_detailed.pdf}
   \includegraphics[width=0.9\linewidth]{ISO_lines_zoom_2.pdf}
\end{center}
   \caption{The Beta distribution log-likelihood evaluated given the complete data set of 1217 sample paths. The optimal parameter found are indicated by the blue dot.}
\label{fig:ISO}
\end{figure}

%\subsection{Discussion}

\subsection{Conclusion}

In this project, we have proposed a model to quantify the uncertainties in wind power generation forecasts. It is important to note that this approach is agnostic of forecasting technology. We have also taken into account the physical limits of the model by respecting the full installation power of the wind farm. Additionally, we have taken into account skew-symmetric errors for which the Beta distribution is an appropriate choice. The skewness of the forecast errors is necessary to correctly model the errors when operating near full installation power production or in cases of extremely low wind power production.

%-------------------------------------------------------------------------
\subsection{References}

\begin{itemize}
\item[][1] Dragomir, S., Agarwal, R., \& Barnett, N. (2000). Inequalities for Beta and Gamma functions via some classical and new integral inequalities. Journal of Inequalities and Applications, 2000(2), 504054. doi:10.1155/s1025583400000084
\end{itemize}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2019-06-17 LaTeX_code/poster/latex/optimization_project.tex
updated code after finalizing the poster. working optmization, full data

--- 2019-06-06 cvpr2019AuthorKit/latex/optimization_project.tex
@@
 %%%%%%%%% TITLE
-\title{ On the Uncertainty of Wind Power Forecasts \\  \small{(AMCS Optimization course final project submission)}}
+\title{ On the Uncertainty of Wind Power Forecasts }  % \\  \small{Report}}
 
@@
 Finally, we apply our model to synthetic and real wind power generation data for benchmarking.
-We apply the model to Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the full year 2016-2017.
+We apply the model to Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the year 2016-2017.
 
 %-------------------------------------------------------------------------
-\subsection{Model}
+\section{Model}
 
-We propose the following parameterized stochastic differential equation (SDE), 
+\subsection{Physical Model}
+
+Let $X_t$ be the  wind power generation forecasts stochastic process defined by the  following parameterized stochastic differential equation (SDE), 
+\begin{equation}
+\begin{split}
+dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
+X_0 & = X_0
+\end{split}\label{main}
+\end{equation}
+
+\begin{itemize}
+%\item $\Delta_N$: any function of the number of samples, $N$. For example, $\Delta_N = \frac{1}{N}$.
+\item $a(X_t; \bm{\theta})$: Drift function 
+\item $b (X_t; \bm{\theta} )$: Diffusion function 
+\item $\bm{\theta}$: a vector of parameters
+\item $dW_t$: Standard Wiener random process.
+\end{itemize}
+
+%\subsection{Base Model}
+%
+%Let $V_t$ be the deviation of the wind power generation forecasts from  actual wind power generation.
+That is, $V_t$ models the errors or uncertainty of a given set of wind power generation forecasts.
+%
+%We propose a forecast-error model based on the following parameterized stochastic differential equation (SDE), 
+%\begin{equation}
+%\begin{split}
+%dV_t &= a(V_t; \bm{\theta}) dt + b (V_t; \bm{\theta} ) dW_t \quad t > 0 \\
+%V_0 & = v_0
+%\end{split}\label{main}
+%\end{equation}
+%
+%
+%\begin{itemize}
+%%\item $\Delta_N$: any function of the number of samples, $N$. For example, $\Delta_N = \frac{1}{N}$.
+%\item $a(V_t; \bm{\theta})$: Drift function 
+%\item $b (V_t; \bm{\theta} )$: Diffusion function 
+%\item $\bm{\theta}$: a vector of parameters
+%\item $dW_t$: Standard Wiener random process.
+%\end{itemize}
+
+\subsection{Physical Restrictions}
+It is necessary to keep  the power generation forecast plus its errors  inside the range $[0,1]$ after normalizing the power generated to the capacity of the power plant.
+To ensure that, we choose our model to have zero diffusion near the boundaries.
+Hence, we  formulate the following diffusion  term,
+\begin{equation*}
+\begin{split}
+b(V_t; \bm{\theta}) &=  \sqrt{2 \theta \alpha p_t(1-p_t) X_t (1-X_t)}    \\
+&= \sqrt{2 \theta \alpha p_t(1-p_t) (V_t +p_t ) (1-V_t-p_t)}  \\
+\end{split}
+\end{equation*}
+It remains to control the drift term. As a first requirement, we need the drift term to be mean reverting to the power generation forecast. Thus, we formulate the following drift, 
+\begin{equation}
+a(V_t; \bm{\theta}) =  - \theta (X_t - p_t)
+\end{equation}
+However, this does not track the rate of change of the forecast $\dot{p}$ which  results in $X_t$ being out of sync with the forecast  as can be seen in Figure (\ref{sine_wave_shift})
+
+\begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=0.8\linewidth]{conv_sine_shift.pdf}
+\end{center}
+   \caption{Example of the process $X_t$ following a sine wave without derivative tracking.}
+\label{fig:long}
+\label{fig:onecol}
+\label{sine_wave_shift}
+\end{figure}
+
+For clarity of exposition, we switch to the point of view of the forecast prediction process $X_t = V_t + p_t$ and we include the derivative tracking in the base model,
+\begin{equation}
+\begin{split}
+dX_t &= \hat{a}(X_t; \bm{\theta}) dt + \hat{b} (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
+X_0 & = x_0
+\end{split}\label{main_X}
+\end{equation}
+where 
+\begin{equation}
+\begin{split}
+\hat{a}(X_t; \bm{\theta}) &= \dot{p}_t + a(X_t; \bm{\theta}) =  \dot{p}_t - \theta \left(X_t - p_t\right)   \\
+\hat{b}(X_t; \bm{\theta}) &=  b(X_t; \bm{\theta}) =  \sqrt{2 \theta \alpha p_t(1-p_t) X_t (1-X_t)}    \\
+\end{split}
+\end{equation}
+Here the term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays inside the range $[0,1]$.
+In other words, the zero drift line defined by  setting $\hat{a}(X_t; \bm{\theta}) =0$ must  be contained inside the range $[0,1]$.
+This line is given by   $ \frac{\dot{p}_t}{\theta}  + p_t $, we call it the line of zero drift or  the line of mean stationarity.
+Thus, must have that, 
+\begin{equation}
+ 0 \leq  \frac{\dot{p}_t}{\theta}  + p_t  \leq 1
+\end{equation}
+to keep the process $X_t$ inside the interval $[0,1]$.
+The condition  can be rewritten as, 
+\begin{equation}
+\frac{- |\dot{p_t}|}{p_t} \leq \theta \leq \frac{|\dot{p}_t|}{1- p_t}
+\end{equation}
+
+To enforce the condition, we  define an adjusted drift $\theta = \theta_0 f( p_t, \dot{p}_t) $  which satisfies the condition when
+\begin{equation}
+\theta = \theta_0 f( p_t, \dot{p}_t) \leq \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)} 
+\end{equation}
+
+Hence, we choose $\theta$ such that,
+\begin{equation}
+\theta = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
+\end{equation}
+\subsection{Model prescription }
+We conclude that in order to respect the physical restrictions discussed above, we prescribe the following specifications and the final model becomes,
 \begin{equation}
@@
 
-\begin{itemize}
-\item $\Delta_N$: any function of the number of samples, $N$. For example, $\Delta_N = \frac{1}{N}$.
-\item $a(X_t; \bm{\theta})$: Drift function 
-\item $b (X_t; \bm{\theta} )$: Diffusion function 
-\item $\bm{\theta}$: a vector of parameters
-\item $dW_t$: Standard Wiener random process.
-\end{itemize}
-
-To respect the physical restriction of this model, we consider the following diffusion and drift functions for a parameter vector $\bm{\theta} = (\theta, \alpha)$,  
 \begin{equation}
@@
 
+with
+\begin{equation}
+\theta = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
+\end{equation}
+
 Where 
@@
 \item $\theta >0$: Mean reversion parameter.
-\item $\alpha>0$: Variablity parameter.
+\item $\alpha>0$: Variability parameter.
 \end{itemize}
 
-The SDE in (\ref{main}) define the stochastic process $V_t$ which can be characterized by its transition denisity.
-Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed within intervals $\Delta_N$.
+The  SDE above defines the stochastic process $V_t$ which can be characterized by its transition denisity.
+Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed in intervals of $\Delta_N$.
 Then, the transitions of $V_t$ are given by the likelihood function,
@@
  We are able to obtain the parameters based on the complete data sets mentioned earlier.
-The parameters are given by $(\theta^*, \alpha^*)= (12,2)$.
+The parameters are given by $(\theta^*, \alpha^*)\approx (8,1)$.
 We show in Figure(\ref{fig:ISO}) the contours of the log-likelihood in $(\ref{Likelihood})$ using the full data set.
@@
 
-In Figure(\ref{fig:6hr}) and (\ref{fig:72hr}), we simulate sample forecast errors using the optimal parameters  $(\theta^*, \alpha^*)= (12,2)$ and obtain the associated confidence bands empirically using 10,000 sample paths for each forecast.
+In Figure(\ref{fig:6hr}) and (\ref{fig:72hr}), we simulate sample forecast errors using the optimal parameters  $(\theta^*, \alpha^*)\approx (8,1)$ and obtain the associated confidence bands empirically using 10,000 sample paths for each forecast.
 Note that the confidence bands obtained are non-trivial and reflect the complexity of the uncertainties in the numerical wind power generation forecasts.
@@
 
+%\begin{figure}[t]
+%\begin{center}
+%%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+%   \includegraphics[width=0.9\linewidth]{ISO_lines_detailed.pdf}
+%   \includegraphics[width=0.9\linewidth]{ISO_lines_zoom_2.pdf}
+%\end{center}
+%   \caption{The Beta distribution log-likelihood evaluated given the complete data set of 1217 sample paths. The optimal parameter found are indicated by the blue dot.}
+%\label{fig:ISO}
+%\end{figure}
+
 \begin{figure}[t]
@@
 %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.9\linewidth]{ISO_lines_detailed.pdf}
-   \includegraphics[width=0.9\linewidth]{ISO_lines_zoom_2.pdf}
+   \includegraphics[width=0.5\linewidth]{ellipse100_samples_dN=14e-02.pdf}
+   \includegraphics[width=0.5\linewidth]{ellipse500_samples_dN=14e-02.pdf}
+   \includegraphics[width=0.5\linewidth]{ellipse1193_samples_dN=14e-02.pdf}
 \end{center}
-   \caption{The Beta distribution log-likelihood evaluated given the complete data set of 1217 sample paths. The optimal parameter found are indicated by the blue dot.}
-\label{fig:ISO}
+   \caption{Shrinkage of the ellipse determined by the Hessian matrix of the log-likelihood around the point of optimality $(\theta, \alpha)\approx (8,1)$}
+\label{ellipse_drawing}
+\end{figure}
+
+ \begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=0.5\linewidth]{ISO_100_samples_dN=14e-02.pdf}
+   \includegraphics[width=0.5\linewidth]{ISO_500_samples_dN=14e-02.pdf}
+   \includegraphics[width=0.5\linewidth]{ISO_1193_samples_dN=14e-02.pdf}
+\end{center}
+   \caption{Contour plot of the log-likelihood as more forecasts and data is added, point of optimality $(\theta, \alpha)\approx (8,1)$ indicated in black.}
+\label{contour}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=0.5\linewidth]{Eigen_conv_samples_dN=14e-02.pdf}
+   \includegraphics[width=0.5\linewidth]{ellipse_conv_samples_dN=14e-02.pdf}
+\end{center}
+   \caption{Convergence of the major and semi-axis of the ellipse  of the Hessian of the log-likelihood at the point optimality $(\theta, \alpha)\approx (8,1)$.
+Note that it is slightly faster than the expected rate of $1/\sqrt{M}$.
+This due to the fact that segments of some of the $M$ are uncorrelated, thus acting as an additional  uncorrelated sample to the rest of the path.
+}
+\label{Ellipse_convergance}
 \end{figure}

### 2019-06-17 LaTeX_code/poster/latex/poster.tex
updated code after finalizing the poster. working optmization, full data

\documentclass[ima, 20pt, portrait, plainboxedsections]{sciposter}

% Packages
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage{amsmath,amssymb}
\usepackage{multicol}
\usepackage{epstopdf}
\usepackage{graphicx}

\usepackage{color}
\usepackage{mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}

% Commands
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\cf}{\textit{cf.}}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\prob}{\mathrm{P}}
\newcommand{\expt}{\mathrm{E}}
\newcommand{\var}{\mathrm{Var}}
\newcommand{\rset}{\mathbb{R}}
\newcommand{\nset}{\mathbb{N}}
\newcommand{\zset}{\mathbb{Z}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\poisson}{\mathcal{P}}
\newcommand{\normal}{\mathcal{N}}
\newcommand{\binomial}{\mathcal{B}}
\newcommand{\Ordo}[1]{{\mathcal{O}}\left(#1\right)}
\newcommand{\ordo}[1]{{o}\left(#1\right)}
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
\renewcommand{\emph}{\red}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

% Theorems
\newtheorem{Def}{Definition}
\newtheorem{Lem}{Lemma}
\newtheorem{Thm}{Theorem}

% Layout parameters
\newcommand{\imsize}{0.49\columnwidth}
%\definecolor{BoxCol}{rgb}{0,0,1}
\definecolor{BoxCol}{rgb}{0.9,0.4,0.4}
\definecolor{SectionCol}{rgb}{1,1,1}
\renewcommand{\titlesize}{\Huge}
\renewcommand{\sectionsize}{\Large}
\setmargins[2cm]

\leftlogo[1.3]{KAUST_Logo.pdf}  % KAUST LOGO
\rightlogo[1.3]{rwth.pdf}

% Overrides commands in sciposter.cls
%\setlength{\columnsep}{0.02\textheight}
%\setlength{\columnseprule}{0.001\textheight}
\setlength{\parskip}{0.002\textheight}

% Author info
\title{ On the Uncertainty of Wind Power Forecasts}
\author{ Waleed Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger}}
\institute{\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor in Mathematics of Uncertainty Quantification, RWTH Aachen University,  Germany}

\begin{document}
\newcommand{\ddd}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{\ddd{#1}}
\maketitle

%%% Begin of Multicols-Enviroment
\begin{multicols}{3}

\section*{Introduction}
Reliable wind power generation forecasting is crucial to:
\begin{itemize}
\item  Meet energy demand through renewable power sources.
\item  Energy trading of future excess power.
\item Design of Investment strategies.
\end{itemize}
We propose a parametric forecast error model to:
\begin{itemize}
\item  Simulate forecast error and quantify its uncertainty.
\item  Calibrate a forecast model for  optimal dispatch of electric power.
\end{itemize}
This model is based on:
\begin{itemize}
\item Parametric Stochastic Differential Equations.
\item Approximate Maximum Likelihood based on continuous optimization.
\end{itemize} 
The result is a skewed stochastic process that simulates the uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects. We apply the model to historical Uruguayan data and forecasts (2016-2017).

\section*{Model}

\subsection*{Phenomenological  Model}

Let $X_t$ be the  wind power generation forecasts stochastic process defined by the  following parameterized stochastic differential equation (SDE), 
\begin{equation}
\begin{split}
dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
X_0 & = X_0
\end{split}
\label{main}
\end{equation}

\begin{itemize}
%\item $\Delta_N$: any function of the number of samples, $N$. For example, $\Delta_N = \frac{1}{N}$.
\item $a(\cdot; \bm{\theta}):[0,1] \to \R $  a drift function.
\item $b (\cdot; \bm{\theta} ):[0,1] \to \R$  a  diffusion function.
\item $\bm{\theta}$: a vector of parameters.
\item $W_t$: Standard Wiener random process in $\R$.
\end{itemize}
%We prescribe the following derivative tracking model:
%\begin{itemize}
%\item $a(X_t; \bm{\theta})=  \dot{p}_t- \theta (X_t - p_t)$
%\item  $ b (X_t; \bm{\theta} )= \sqrt{2 \theta \alpha p_t(1-p_t) X_t (1-X_t)} $
%\end{itemize}
%where $p_t$ is the wind power forecast.

\subsection*{Physical Constrains}
Let $p_t$ be a numerical wind power forecast, which is an input to this approach. Then the model is given by the following It\^{o} stochastic differential equation,
\begin{equation}
\begin{split}
dX_t&= \dot{p} \ dt + (\theta_t -X_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t \quad t > 0 \\
X_0&=x_0
\end{split}
\end{equation}
As the  installed power production capacity is limited, we normalize with respect to the installation power. Thus our process must be limited to the range $[0,1]$. To enforce this constraint, we must have drift and diffusion control.
\subsubsection*{Diffusion Control: } The physical constraint is respected  by choosing  diffusion coefficient $ b (x; \bm{\theta} )= \sqrt{2 \theta_t \alpha p_t(1-p_t) x (1-x)} $ that is zero on the boundaries of $[0,1]$.
\subsubsection*{Drift Control: }
$X_t$ remains in $[0,1]$ a.s. by choosing $\theta_t$ as follows, 
\begin{equation}
\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
\end{equation}

\subsubsection*{Change of Variables:}
In order to avoid differentiation of the forecast $\dot{p}_t$ and simplify, we apply a change of variables $$V_t = X_t - p_t$$  \\
Then  model becomes,
\begin{equation}
\begin{split}
dV_t &=  - \theta V_t \  dt + \sqrt{2 \theta \alpha p_t(1-p_t) (V_t +p_t ) (1-V_t-p_t)} \  dW_t \quad t > 0 \\
V_0 & = v_0
\end{split}\label{main}
\end{equation}

with
\begin{equation}
\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
\end{equation}

Where 
\begin{itemize}
\item $p_t$: Numerical wind power production forecast.
\item $\theta_0 >0$: Mean reversion parameter.
\item $\alpha>0$: Variability parameter.
\end{itemize}

\section*{Inference}

\subsection*{Likelihood}
The SDE above defines the stochastic process $V_t$ which can be characterized by its transition density. \\

Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed in intervals of $\Delta_N$. Since $V_t$ is Markovian, the likelihood function is given by  product of its  transition densities.

\begin{equation}
\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}}, \bm{\theta})  \rho (V_{j,0}) 
\label{likelihood}
\end{equation}

\subsection*{Approximate Likelihood}
Solving for transition densities of the process $V_t$ requires solving the Fokker-Planck equation at every step which is computationally prohibitive. A common choice is performing a  Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints. \\

Therefore, we propose an approximate likelihood inspired by the stationary distribution of the process $X_t$ which is a Beta distribution for a constant forecast $p_t$.Additionally,  as the process $X_t$ and $p_t$ take on values in $[0,1]$, then $V_t$ takes on values in $[-1,1]$. Therefore,  it is natural to use a  Beta distribution with compact support on $[-1,1]$.

%We obtain the modified Beta distribution, 
%
%\begin{equation}
%\begin{split}
%f_Y(y; \alpha , \beta )&= f_X(g^{-1}(y) ) \Big| \frac{\partial g^{-1}(y)}{\partial y }  \Big| \\
%&= \frac{1}{B(\alpha, \beta) (b-a)} \Big(\frac{a-y}{b-a}\Big)^{\alpha -1}\Big(1-\frac{a-y}{b-a} \Big)^{\beta -1} \label{modified_Beta}
%\end{split}
%\end{equation}
%where $B(\cdot,\cdot)$ is the Beta function. Also, we have that
%\begin{equation}
%\E[Y]= a + (b-a) \frac{\alpha}{\alpha + \beta}
%\end{equation}
%\begin{equation}
%\V[Y]= (b-a)^2 \frac{\alpha \beta}{(\alpha + \beta)^2 (\alpha + \beta + 1)}
%\end{equation}

\subsubsection*{ Moment Matching}
To approximate the transition densities of  the process $V_t$, we match its moments with the shape parameters of the Beta distribution using It\^{o}'s formula. \\

The moments of the process $V_t$ are given by,
\begin{equation}
\begin{split}
 \frac{dm_1(t_n)}{dt} &=    - \theta_t m_1(t_n)  \\
\frac{d m_{2}(t_n)}{dt}&= -2m_{2}(t_n) [\theta_t + \alpha \theta_t p_t(1-p_t) ] \\
&+ 2m_{1}(t_n)[\alpha \theta_t p_t (1-p_t) (1-2p_t)] \\
&+ 2\alpha \theta_t p_t^2(1-p_t)^2  \\
%m_2(0) = \E[V_0^2] = v_0^2\\
\end{split}
\end{equation}
with initial conditions, $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2$.

\section*{Data}

We apply the model to Uruguayan wind power generation data and their corresponding numerical wind power production forecast. \\

The wind power generation data set contains hourly samples of aggregated wind power production throughout the country. Each sample path contains 72 hourly observations and we have a total of 1217 sample paths spanning the year 2016 to 2017 (87,624 data points). \\

The numerical wind power generation forecast set contains  1217 forecasts of the wind power generation  corresponding to the actual  wind power generation data set mentioned above.

\begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.8\linewidth]{Forecast_data_68.pdf}
    \includegraphics[width=0.8\linewidth]{Forecast_data_82.pdf}
\end{center}
   \caption{Examples of wind power generation from the data set along with the wind power generation forecast.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\section*{Methodology}

\subsection*{ Optimization  }
\begin{itemize}
%\item The log-likelihood is convex in the  parameters $(\alpha, \theta_t )$ on the positive quadrant.
\item We optimize using L-BFGS algorithm constrained to the positive quadrant.
\end{itemize}
The ellipse defined by the  Hessian of the log-likelihood shrinks at a fast rate as shown in Figure (\ref{ellipse_drawing}). The contours of the  log-likelihood can be seen in Figure (\ref{contour}).

\begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.6\linewidth]{ellipse1193_samples_dN=14e-02.pdf}
    \includegraphics[width=0.6\linewidth]{ellipse_conv_samples_dN=14e-02.pdf}
\end{center}
   \caption{Left:Shrinkage of the ellipse determined by the Hessian matrix of the log-likelihood around the point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ (Axis are not in natural scale, arrows only to  eignevector direction). Right: Convergence of the major and semi-axis of the ellipse  of the Hessian of the log-likelihood at the point optimality $(\theta_0^*, \alpha^*)\approx (8,1)$. Note that it is slightly faster than the expected rate of $1/\sqrt{M}$. This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample.}
\label{ellipse_drawing}
\end{figure}

 \begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.9\linewidth]{ISO_100_samples_dN=14e-02.pdf}
   %\includegraphics[width=0.5\linewidth]{ISO_500_samples_dN=14e-02.pdf}
   %\includegraphics[width=0.5\linewidth]{ISO_1193_samples_dN=14e-02.pdf}
\end{center}
   \caption{Contour plot of the log-likelihood with only 100 sample paths, point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ indicated by the  black dot.}
\label{contour}
\end{figure}

\section*{Results}
 We are able to obtain the parameters based on the complete data sets mentioned earlier. The parameters are given by $(\theta^*, \alpha^*)\approx (8,1)$.

%We can also see in Figure() that the region surrounding the optimal parameters becomes more defined as we add more sample paths.

In Figure (\ref{fig:72hr}) and (\ref{fig:6hr}), we simulate sample forecast errors using the optimal parameters  $(\theta_0^*, \alpha^*)\approx (8,1)$ and obtain the associated confidence bands empirically using 1000 sample paths for each forecast. %Note that the confidence bands obtained are non-trivial and reflect the complexity of the uncertainties in numerical wind power generation forecasts.

\begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_31.pdf} %667
   \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_437.pdf}
   \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_82.pdf}

\end{center}
   \caption{ Examples of confidence bands obtained for the full 72 hour forecasts.We can see that the model captures the fluctuations in the actual production with non-trivial and asymmetric confidence intervals.}
\label{fig:72hr}
\end{figure}

\begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.8\linewidth]{6hr_forecast_CI_75.pdf}  %569
   \includegraphics[width=0.8\linewidth]{6hr_forecast_CI_59.pdf}
   %\includegraphics[width=0.9\linewidth]{6hr_forecast_CI_68.pdf}
\end{center}
   \caption{ Examples of confidence bands obtained for the first 6 hours of the forecasts. This is important as this specific forecasting company computes a new forecast every 6 hours for reliability.}
\label{fig:6hr}
\end{figure}

 \begin{figure}[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_623.pdf}  %569
\end{center}
   \caption{ Examples of omitted data which corresponds to production control and manual energy management decisions. In this example,  wind power production was repeatedly curtailed at around 2 AM which is a period of low power demand. Automatic detection of such scenarios is to be incorporated in future works.}
\label{fig:6hr}
\end{figure}

\section*{Conclusions}
In this project, we have proposed a model based on SDE's to quantify uncertainties in wind power generation forecasts. It has the following advantages:
\begin{itemize}
\item  Represents and quantifies  uncertainty in wind power forecasts.
\item It is forecast technology agnostic.
\item  Takes into account physical constrains and the skew-symmetric nature of forecast error.
\item Provides a basis for decision making in the optimal dispatch of electric power.
\end{itemize}

%\section*{Acknowledgement}

\section*{References}
\begin{flushleft}
[1] {Elkantassi, S., Kalligiannaki, E., \& Tempone, R. (2017). Inference And Sensitivity In Stochastic Wind Power Forecast Models. Proceedings of the 2nd International Conference on Uncertainty Quantification in Computational Sciences and Engineering (UNCECOMP 2017). doi:10.7712/120217.5377.16899}
\end{flushleft}

\end{multicols}
\end{document}

### 2019-06-19 LaTeX_code/paper/egpaper_final.tex
computation output is saved in folder structure, old code retired

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{ On the Uncertainty of Wind Power Forecasts \\  \small{(AMCS Optimization course final project submission)}}

\author{Waleed  Alhaddad\\
King Abdullah University of Science (KAUST)\\
4700 KAUST, Thuwal-Jeddah, Saudi Arabia\\
{\tt\small waleed.alhaddad@kaust.edu.sa}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Ra\'ul  Tempone\\
KAUST/RWTH Aachen \\
 Templergraben 55, 52062 Aachen, Germany\\
{\tt\small raul.tempone@kaust.edu.sa}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT

\begin{abstract}
Reliable wind power generation forecasting is crucial to meet energy demand, to trade and invest. We propose a model to simulate and quantify uncertainties in such forecasts. This model is based on Stochastic Differential Equations whose time-dependent parameters are inferred using continuous optimization of an approximate Likelihood function. The result is a skew stochastic process that simulates uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects. We apply the model to historical Uruguayan data and forecasts.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

    We propose a model to simulate and quantify uncertainties in wind power generation forecasts. This model is based on Stochastic Differential Equations (SDEs) whose time-dependent parameters are inferred using optimization techniques of an associated approximate Likelihood function. Through continuous optimization, we find the optimal parameters of an unbounded convex problem with convex constraints.

    We are able to simulate and quantify uncertainties in a variety of wind power generation forecasts while taking into account the skewness of the errors. This method is non-intrusive and is independent of forecasting technology or future developments. Through optimization, we update and tune the parameters of our SDE as we receive new sets of observations and their associated forecasts. Additionally, we are able to compare in a quantitative manner the different forecast technologies and how they behave in different real-world scenarios. This model is to be extended to the uncertainty quantification of other power generation sources such as the uncertainties in the power generation of solar power plants. This introduces new challenges in terms of optimization and modeling. Finally, we apply our model to synthetic and real wind power generation data for benchmarking. We apply the model to Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the period of March 1 to May 31, 2016.

%-------------------------------------------------------------------------
\subsection{Model}

We propose the following parameterized stochastic differential equation (SDE), 
\begin{equation}
\begin{split}
dV_t &= -\theta V_t dt + \sqrt{2 \theta \alpha p_t(1-p_t) (V_t +p_t ) (1-V_t-p_t)} dW_t\\
V_0 & = v_0
\end{split}\label{main}
\end{equation}

where $\theta >0 $ and $\alpha>0$ are parameters to be inferred.

\subsection{Dual submission}

Please refer to the author guidelines on the CVPR 2019 web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section,
must be no longer than eight pages in length. The references section
will not be included in the page count, and there is no limit on the
length of the references section. For example, a paper of eight pages
with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for CVPR 2019.}

Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper. For your results, however, you should not identify yourself and should not mention your participation in the challenge. Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the CVPR 2019 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

Please direct any questions to the production editor in charge of these
proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
Fax (714) 761-1784.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2019-07-09 LaTeX_code/poster_non_academic/optimization_project.tex
p(1-p) removed,added path simulator,path length feature, non-tech poster

--- 2019-06-17 LaTeX_code/poster/latex/poster.tex
@@
-\documentclass[ima, 20pt, portrait, plainboxedsections]{sciposter}
+\documentclass[10pt,twocolumn,letterpaper]{article}
 
-% Packages
-\usepackage[english]{babel}
-\usepackage[latin1]{inputenc}
+\usepackage{cvpr}
 \usepackage{times}
-\usepackage{amsmath,amssymb}
-\usepackage{multicol}
-\usepackage{epstopdf}
+\usepackage{epsfig}
 \usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
 
@@
 \usepackage{bm}
-
-% Commands
-\newcommand{\ie}{\textit{i.e.}}
-\newcommand{\eg}{\textit{e.g.}}
-\newcommand{\cf}{\textit{cf.}}
-\newcommand{\ud}{\mathrm{d}}
-\newcommand{\prob}{\mathrm{P}}
-\newcommand{\expt}{\mathrm{E}}
-\newcommand{\var}{\mathrm{Var}}
-\newcommand{\rset}{\mathbb{R}}
-\newcommand{\nset}{\mathbb{N}}
-\newcommand{\zset}{\mathbb{Z}}
-\newcommand{\one}{\mathbf{1}}
-\newcommand{\poisson}{\mathcal{P}}
-\newcommand{\normal}{\mathcal{N}}
-\newcommand{\binomial}{\mathcal{B}}
-\newcommand{\Ordo}[1]{{\mathcal{O}}\left(#1\right)}
-\newcommand{\ordo}[1]{{o}\left(#1\right)}
-\newcommand{\red}[1]{{\color{red}#1}}
-\newcommand{\blue}[1]{{\color{blue}#1}}
-\newcommand{\green}[1]{{\color{green}#1}}
-\renewcommand{\emph}{\red}
 
@@
 
-% Theorems
-\newtheorem{Def}{Definition}
-\newtheorem{Lem}{Lemma}
-\newtheorem{Thm}{Theorem}
+% Include other packages here, before hyperref.
 
-% Layout parameters
-\newcommand{\imsize}{0.49\columnwidth}
-%\definecolor{BoxCol}{rgb}{0,0,1}
-\definecolor{BoxCol}{rgb}{0.9,0.4,0.4}
-\definecolor{SectionCol}{rgb}{1,1,1}
-\renewcommand{\titlesize}{\Huge}
-\renewcommand{\sectionsize}{\Large}
-\setmargins[2cm]
+% If you comment hyperref and then uncomment it, you should delete
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
+% run, let it finish, and you should be clear).
+\usepackage[breaklinks=true,bookmarks=false]{hyperref}
 
-\leftlogo[1.3]{KAUST_Logo.pdf}  % KAUST LOGO
-\rightlogo[1.3]{rwth.pdf}
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
-% Overrides commands in sciposter.cls
-%\setlength{\columnsep}{0.02\textheight}
-%\setlength{\columnseprule}{0.001\textheight}
-\setlength{\parskip}{0.002\textheight}
+\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
 
-% Author info
-\title{ On the Uncertainty of Wind Power Forecasts}
-\author{ Waleed Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger}}
-\institute{\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor in Mathematics of Uncertainty Quantification, RWTH Aachen University,  Germany}
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+%\ifcvprfinal\pagestyle{empty}\fi
+\setcounter{page}{1}
+\begin{document}
 
-\begin{document}
-\newcommand{\ddd}[1]{\boldsymbol{#1}}
-\renewcommand{\vec}[1]{\ddd{#1}}
+%%%%%%%%% TITLE
+\title{ Probabilistic Wind Power Forecasting using Stochastic Differential Equations }  % \\  \small{Report}}
+
+\author{ Waleed Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
+\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor in Mathematics of Uncertainty Quantification\\ RWTH Aachen University,  Germany
+}
+
 \maketitle
+%\thispagestyle{empty}
 
-%%% Begin of Multicols-Enviroment
-\begin{multicols}{3}
+%%%%%%%%% ABSTRACT
 
-\section*{Introduction}
-Reliable wind power generation forecasting is crucial to:
-\begin{itemize}
-\item  Meet energy demand through renewable power sources.
-\item  Energy trading of future excess power.
-\item Design of Investment strategies.
-\end{itemize}
-We propose a parametric forecast error model to:
-\begin{itemize}
-\item  Simulate forecast error and quantify its uncertainty.
-\item  Calibrate a forecast model for  optimal dispatch of electric power.
-\end{itemize}
-This model is based on:
-\begin{itemize}
-\item Parametric Stochastic Differential Equations.
-\item Approximate Maximum Likelihood based on continuous optimization.
-\end{itemize} 
-The result is a skewed stochastic process that simulates the uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects.
+\begin{abstract}
+Reliable wind power generation forecasting is crucial to meeting energy demand through renewable power sources, to trade excess power and to the design of investment strategies.
+We propose a parametric forecast error model to a model to simulate forecast error and quantify its uncertainty.
+It also provide a basis to calibrate a forecast model for  optimal dispatch of electric power.
+This model is based on parametric Stochastic Differential Equations (SDE's) and an approximate Maximum Likelihood method based on continuous optimization.The result is a skewed stochastic process that simulates the uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects.
 We apply the model to historical Uruguayan data and forecasts (2016-2017).
 
-\section*{Model}
+\end{abstract}
 
-\subsection*{Phenomenological  Model}
+%%%%%%%%% BODY TEXT
+\section{Introduction}
+	Wind power forecasting is complex to model and inherits a lot of uncertainty.
+The link between physical models of  wind turbines  and power production is non-trivial, non-linear and sensitive to the configuration and state of the wind farm.
+Reliable wind power forecasting is essential and can provided by probabilistic forecasts.
+
+	There are many possible techniques to prepare probabilistic forecasts.
+In this work, we focus on the use of Stochastic Differential Equations (SDE's) to represent and quantify uncertainties in wind power forecasts.
+It is important to note that this approach is  forecast technology agnostic.
+Moreover, it can be used to calibrate and integrate wind power forecasts into optimal electrical power dispatch models.
+Also, it could serve as a basis for assessments of wind power forecasts  and uncovering their particularities.
+
+Previous attempt by M\o ller et al.
+(M\o ller, Zugno, \& Madsen, 2016)  considered probabilistic wind power forecast models based on SDE's.
+Here, we propose an improved model featuring derivative tracking and  non-Gaussian skew symmetric approximations of the stochastic process both of which are essential in wind power probabilistic forecasting.
+We apply the model to Uruguayan wind power forecasts together with Uruguayan historical data  pertaining to the year 2016-2017.
+
+%-------------------------------------------------------------------------
+\section{Phenomenological  Model}
 
@@
 \end{itemize}
-%We prescribe the following derivative tracking model:
-%\begin{itemize}
-%\item $a(X_t; \bm{\theta})=  \dot{p}_t- \theta (X_t - p_t)$
-%\item  $ b (X_t; \bm{\theta} )= \sqrt{2 \theta \alpha p_t(1-p_t) X_t (1-X_t)} $
-%\end{itemize}
-%where $p_t$ is the wind power forecast.
 
-\subsection*{Physical Constrains}
+\subsection{Physical Constrains}
+
 Let $p_t$ be a numerical wind power forecast, which is an input to this approach. Then the model is given by the following It\^{o} stochastic differential equation,
@@
 \end{equation}
+Note that the process $X_t$ mean reverts to  the wind power forecast $p_t$ and  tracks its the time derivative $\dot{p}_t$.
+An example such mean reverting model without derivative tracking exhibits consistent lags as shown in Figure (\ref{sine_wave_shift}).
+
 As the  installed power production capacity is limited, we normalize with respect to the installation power.
@@
 \subsubsection*{Diffusion Control: } The physical constraint is respected  by choosing  diffusion coefficient $ b (x; \bm{\theta} )= \sqrt{2 \theta_t \alpha p_t(1-p_t) x (1-x)} $ that is zero on the boundaries of $[0,1]$.
+Note that $\alpha$ is a path variability constant parameter to be determined.
 \subsubsection*{Drift Control: }
-$X_t$ remains in $[0,1]$ a.s. by choosing $\theta_t$ as follows, 
+
+Observe that the term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays a.s.
+inside the range $[0,1]$.
+In other words, the zero drift line defined by $a(X_t; \bm{\theta}) =0$ must  be contained inside the range $[0,1]$.
+Thus, must have that,
 \begin{equation}
-\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
+\frac{- |\dot{p_t}|}{p_t} \leq \theta \leq \frac{|\dot{p}_t|}{1- p_t}
+\end{equation}
+
+which is satisfied  by choosing $\theta_t$ as follows, 
+\begin{equation}
+\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ) \label{theta_t}
 \end{equation}
@@
 In order to avoid differentiation of the forecast $\dot{p}_t$ and simplify, we apply a change of variables $$V_t = X_t - p_t$$  \\
-Then  model becomes,
+The  model becomes,
 \begin{equation}
 \begin{split}
-dV_t &=  - \theta V_t \  dt + \sqrt{2 \theta \alpha p_t(1-p_t) (V_t +p_t ) (1-V_t-p_t)} \  dW_t \quad t > 0 \\
+dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha p_t(1-p_t) (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
 V_0 & = v_0
@@
 \end{equation}
+with $\theta_t$ given by (\ref{theta_t}).
 
-with
-\begin{equation}
-\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
-\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Where 
-\begin{itemize}
-\item $p_t$: Numerical wind power production forecast.
-\item $\theta_0 >0$: Mean reversion parameter.
-\item $\alpha>0$: Variability parameter.
-\end{itemize}
+However, this does not track the rate of change of the forecast $\dot{p}$ which  results in $X_t$ being out of sync with the forecast  as can be seen in Figure (\ref{sine_wave_shift})
 
-\section*{Inference}
+\begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=0.8\linewidth]{conv_sine_shift.pdf}
+\end{center}
+   \caption{Example of the process $X_t$ following a sine wave without derivative tracking.}
+\label{fig:long}
+\label{fig:onecol}
+\label{sine_wave_shift}
+\end{figure}
 
-\subsection*{Likelihood}
-The SDE above defines the stochastic process $V_t$ which can be characterized by its transition density. \\
+%%%%%%%%%%%%%%%%%%%%%%
+\section{Data}
 
+We apply the model to Uruguayan wind power generation data and their corresponding numerical wind power production forecast.The wind power generation data set contains hourly samples of aggregated wind power production throughout the country.
+Each sample path contains 72 hourly observations and we have a total of 1217 sample paths spanning the year 2016 to 2017 (87,624 data points).
+The numerical wind power generation forecast set contains  1217 forecasts of the wind power generation  corresponding to the actual  wind power generation data set mentioned above.
+
+\begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=0.8\linewidth]{Forecast_data_68.pdf}
+    \includegraphics[width=0.8\linewidth]{Forecast_data_82.pdf}
+\end{center}
+   \caption{Examples of wind power generation from the data set along with the wind power generation forecast.}
+\label{fig:long}
+\label{fig:onecol}
+\end{figure}
+
+\section{Inference and Optimization}
+
+\subsection{Likelihood}
+The SDE above defines the stochastic process $V_t$.
 Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed in intervals of $\Delta_N$.
@@
 
-\subsection*{Approximate Likelihood}
+\subsection{Approximate Likelihood}
 Solving for transition densities of the process $V_t$ requires solving the Fokker-Planck equation at every step which is computationally prohibitive.
@@
 \subsubsection*{ Moment Matching}
-To approximate the transition densities of  the process $V_t$, we match its moments with the shape parameters of the Beta distribution using It\^{o}'s formula. \\
-
-The moments of the process $V_t$ are given by,
+To approximate the transition densities of  the process $V_t$, we match its moments with the shape parameters $\xi_1, \xi_2$ of the Beta distribution on $[-1,1]$.
+Then, the shape parameters are given by,
+\begin{equation}
+\xi_1 = - \frac{(1+\tilde{\mu}_t )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \quad \xi_2=  \frac{(\tilde{\mu}_t-1 )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \label{param_transformed_beta}
+\end{equation}
+where $\tilde{\mu}_t = m_1(t)$ and $\tilde{\sigma}_t^2= m_2(t)- m_1^2(t)$ and $m_i$ being the i-th moment of the process $V_t$.
+Using It\^{o}'s formula, the first two moments  of the  process $V_t$ are given by,
 \begin{equation}
@@
 with initial conditions, $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2$.
-
-\section*{Data}
-
-We apply the model to Uruguayan wind power generation data and their corresponding numerical wind power production forecast. \\
-
-The wind power generation data set contains hourly samples of aggregated wind power production throughout the country.
-Each sample path contains 72 hourly observations and we have a total of 1217 sample paths spanning the year 2016 to 2017 (87,624 data points).
-\\
-
-The numerical wind power generation forecast set contains  1217 forecasts of the wind power generation  corresponding to the actual  wind power generation data set mentioned above.
-
-\begin{figure}[t]
-\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.8\linewidth]{Forecast_data_68.pdf}
-    \includegraphics[width=0.8\linewidth]{Forecast_data_82.pdf}
-\end{center}
-   \caption{Examples of wind power generation from the data set along with the wind power generation forecast.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-\section*{Methodology}
-
-\subsection*{ Optimization  }
-\begin{itemize}
-%\item The log-likelihood is convex in the  parameters $(\alpha, \theta_t )$ on the positive quadrant.
-\item We optimize using L-BFGS algorithm constrained to the positive quadrant.
-\end{itemize}
-The ellipse defined by the  Hessian of the log-likelihood shrinks at a fast rate as shown in Figure (\ref{ellipse_drawing}). The contours of the  log-likelihood can be seen in Figure (\ref{contour}).
+\subsection{Optimization}
+Let $\ell$ be the natural logarithm  of the likelihood in $(\ref{likelihood})$.
+Given the data set $V^{M,N}$, we  optimize the the log-likelihood $\ell$  using L-BFGS algorithm  for the optimal parameters $\theta_0^* , \alpha^*$ as follows,
+\begin{equation}
+(\theta_0^* , \alpha^* ) = \arg \underset{\theta_0, \alpha>0}{\min} - \ell( \theta_0,  \alpha | V^{M,N} )
+\end{equation}
+The contours of the  log-likelihood can be seen in Figure (\ref{contour}).To further inspect the log-likelihood at the point of optimality $(\theta_0^* , \alpha^* )$, we look at the ellipse defined by the  Hessian of the log-likelihood at the point of optimality.
+We observe that the ellipse shrinks at a fast rate as shown in Figure (\ref{ellipse_drawing}).
+We see that  the convergence rate of the parameters $\theta_0$ and $\alpha$ is slightly faster than the expected rate of $1/\sqrt{M}$.
+This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample.
+We note that the uncertainty in determining the parameter $\alpha$  is much higher than  in $\theta_0$.
 
@@
 
-\section*{Results}
+%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results}
  We are able to obtain the parameters based on the complete data sets mentioned earlier. The parameters are given by $(\theta^*, \alpha^*)\approx (8,1)$.
@@
 
-In Figure (\ref{fig:72hr}) and (\ref{fig:6hr}), we simulate sample forecast errors using the optimal parameters  $(\theta_0^*, \alpha^*)\approx (8,1)$ and obtain the associated confidence bands empirically using 1000 sample paths for each forecast.
+In Figure (\ref{fig:72hr}) and (\ref{fig:6hr}), we simulate sample forecast errors $V_t$ using the optimal parameters  $(\theta_0^*, \alpha^*)\approx (8,1)$ and obtain the associated confidence bands empirically using 1000 sample paths of each forecast.
 %Note that the confidence bands obtained are non-trivial and reflect the complexity of the uncertainties in numerical wind power generation forecasts.
@@
 
-\section*{Conclusions}
-In this project, we have proposed a model based on SDE's to quantify uncertainties in wind power generation forecasts. It has the following advantages:
-\begin{itemize}
-\item  Represents and quantifies  uncertainty in wind power forecasts.
-\item It is forecast technology agnostic.
-\item  Takes into account physical constrains and the skew-symmetric nature of forecast error.
-\item Provides a basis for decision making in the optimal dispatch of electric power.
-\end{itemize}
+\section{Conclusions}
+We have proposed a model based on SDE's to quantify uncertainties in wind power generation forecasts.
+A parametric SDE to represent and quantify  uncertainty in wind power forecasts.
+It is forecast technology agnostic.
+Moreover, it provides a basis for decision making in the optimal dispatch of electric power.
 
@@
 \begin{flushleft}
-[1] {Elkantassi, S., Kalligiannaki, E., \& Tempone, R.
+- M\o ller, J.
+K., Zugno, M., \& Madsen, H.
+(2016).
+Probabilistic Forecasts of Wind Power Generation by Stochastic Differential Equation Models.
+Journal of Forecasting, 35(3), 189-205.
+doi:10.1002/for.2367 \linebreak
+- Elkantassi, S., Kalligiannaki, E., \& Tempone, R.
 (2017).
@@
 Proceedings of the 2nd International Conference on Uncertainty Quantification in Computational Sciences and Engineering (UNCECOMP 2017).
-doi:10.7712/120217.5377.16899}
+doi:10.7712/120217.5377.16899
 \end{flushleft}
 
-\end{multicols}
+{\small
+\bibliographystyle{ieee}
+\bibliography{egbib}
+}
+
 \end{document}

### 2019-07-09 python_code/likelihood_explorer.py

@@ -12,7 +12,7 @@ current_plotting_dir='data/'+ script_name+'_' +current_time
 os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
 
 N=forecast_data_inter.shape[2]
-M= 10    #forecast_data_inter.shape[1]
+M= 100    #forecast_data_inter.shape[1]
 dt=1
 dN=1/N
 
@@ -23,11 +23,15 @@ V= forecast_data_inter[1,:,:] -forecast_data_inter[0,:,:]
 forecast_data_inter.shape
 this_model=model_modified_drift(disct_temp,V, forecast= p)
 
-theta_array=np.linspace(1, 30, 30)
-alpha_array=np.linspace(0.1, 3, 30)
+theta_array=np.linspace(1, 100, 30) #np.linspace(1, 30, 30)
+alpha_array=np.linspace(0.001, 0.5, 30) #np.linspace(0.1, 3, 30)
 
 np.save(current_plotting_dir+'/num_paths', M)
 np.save(current_plotting_dir+'/interpolation_points', N)
 likelihood_evaluater(theta_array=theta_array,\
     alpha_array=alpha_array,\
     this_model=this_model,path_dir=current_plotting_dir )
+print(current_plotting_dir)
+
+this_model.likelihood(np.array((60,0.001)))
+this_model.likelihood(np.array((60,0.1)))

### 2019-07-09 python_code/path_simulator.py

@@ -1,0 +1,26 @@
+import os
+os.chdir('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code')
+from Base import *
+forecast_with_data=np.load('data/forecast_with_data.npy')
+data=data_check_interpolate(forecast_with_data=forecast_with_data)
+now = dtM.datetime.now();
+current_time=now.strftime("%y-%m-%d-%H-%M-%S")
+script_name='sample_paths_'
+current_plotting_dir='plots/'+ script_name +current_time
+os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
+
+print(current_plotting_dir)
+
+current_list= list(range(0, data.shape[1])) #=list(range(0, data.shape[1])) #full_set
+M=5
+N=72
+disct_in= disct(N=N, dt=1, M=M) #M is number of paths wanted in ensamble
+real_in=real(7.26, 0.123) # SDE parameters to be generated from
+
+path_simulator(forecast_data_inter=data,hours=12,\
+    real_in=real_in, disct_in=disct_in,list_forecast_number=current_list,\
+    dir_path=current_plotting_dir)
+
+path_simulator(forecast_data_inter=data,hours=24,\
+    real_in=real_in, disct_in=disct_in,list_forecast_number=current_list,\
+    dir_path=current_plotting_dir)

### 2019-08-28 LaTeX_code/Discussion/Discussion_24_06_19.tex
updated tripizoidal

\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[activeacute, english]{babel}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{tikz}
\usepackage{float}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{subcaption}

\newcommand\dist{\stackrel{\mathclap{\footnotesize\mbox{d.}}}{=}}
\usepackage[spanish,onelanguage,ruled,lined, linesnumbered]{algorithm2e}
\usepackage[spanish,onelanguage]{algorithm2e}
\newtheorem{theorem}{Teorema}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposición}
%\newenvironment{proof}[1][Demostración]{\begin{trivlist}
%		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{definition}[1][Definición]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Ejemplo]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Nota]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\negr}[1]{\textit{\textbf{#1}}}

\title{Power Forecasting and Control\\ discussion notes}

\author{Waleed Alhaddad }

\date{}
\begin{document}
\maketitle

%\section{Notes and To-do}
\begin{itemize}
\item Check the how reasonable are the obtained parameters through the quadratic variation
\begin{equation}
\sum_{i,j} (X_{i,j} - X_{i,j})^2 \approx 2 \theta_t \alpha \sum_{i,j}  X_{i,j} (1-X_{i,j})
\end{equation}
\item Apply the model to the french data 
	\begin{itemize}
	\item We are waiting for the details of the evolution of the maximum installed capacity to be able to normalize.
	\item Exploit the pyramid structure of the forecast updates, as the french 	recompute the forecast every hour.
	\item We are also waiting to know if the forecasting technology changed during those years and when. This will enable us to  pick upon the particularities of the different forecasting technologies. Also, to check if the newest forecasting technology performs better in practice.
	\end{itemize}
\item Understand, apply and extend the "R" package DiffusionRgqd to our case of multiple paths and see how it performs in comparison.
\item Plot the likelihood as two "profile likelihood" plots as common in the statistics literature. This means fix one of the parameters, optimize in the other and plot. For instance, it  can be expressed in terms varying $\sigma$ as
\begin{equation}
R(\sigma) = \frac{\max_\mu \mathcal{L}(\mu, \sigma)}{\mathcal{L}(\hat{\mu}, \hat{\sigma})}
\end{equation}
And similarly, we plot $R(\mu)$.

\item The issue with the power curtailing or human intervention is still open. The ideas so far:
\begin{itemize}
\item set a threshold to $\theta_t$ to prevent the process from following such sudden changes. However, this involves choosing some value of $\theta_t$ and a threshold. Also, the data is not refined enough to identify such changes from natural wind speed changes (as currently its recorded at intervals of one hour)
\item Introduce a jumping process, adds complexity to the model but might enhance it overall. This will enable us to capture the sudden changes.
\item Regime switching, similar to the first point, but in this case we can assume that $\theta_t$ follows some Markov Chain instead of hard setting thresholds.
\end{itemize}
\item Double check that the Feller condition is satisfied to ensure the positivity  of the process.
\item Try to see if we can make the system ergodic, especially when we have higher frequency data. This is done when $\Delta n \to \infty$ where $\Delta$ is the interval between each sample of $n$ total samples.

 Then we can leverage existing theoretical results regarding the asymptotic behavior of our model.
\item Possibility of adding regularizers on $\theta_t$ that way we can manipulate it and differentiate it easily for further theoretical work.

\item Assign an a distribution on the initial point and optimized it separately. By that I mean, optimize it without involving the likelihood and its optimization.

\item Once we have higher frequency data, we can use Ahmad's MLE estimators to find the parameters of the model in a simpler and faster way. Regarding this point, I have his papers from 2012 and 2013 which are in the shared Dropbox folder.

\item Another motivation of the project is that power production companies are not allowed to dump more power into the grid than authorized. Otherwise, they have to pay hefty fines as they endanger the grid by using it above its capacity.

\item It may also be possible to obtain the aggregated power production of France for both controllable and non-controllable energy sources. This will benefit us in two ways, we can identify  human intervention more easily and it can be used as data and a test case for Renzo's optimal control ongoing project. Currently this data set is sparse and has some negative values we couldn't understand. (see Dropbox shared folder under "Realized\_ Production")

\end{itemize}

%\newpage
%\section{Things to do}
%\begin{itemize}
%\item 
%\end{itemize}
%
%
%
%\section{Things to do}
%\begin{itemize}
%\item 
%\end{itemize}

%\section{Motivation}

%\section{Introduction}

%\section{Model}

%\section{Conclusion}

%\subsection{Model}
%\begin{thebibliography}{99}
%	\bibitem{apo} Apostol, T. (1974). \emph{Mathematical Analysis} (2nd ed.),  Addison-Wesley. pp.218-230
%	\bibitem{E} Cabaña, E. (2012). \emph{Introducción a los
%		procesos estocásticos}, Notas
%	para el Curso de la Licenciatura en Estadística, Universidad de la República. pp.98-115
%\end{thebibliography}

\end{document}

### 2019-08-28 LaTeX_code/Discussion/Discussion_29_07_19.tex
updated tripizoidal

\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[activeacute, english]{babel}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{tikz}
\usepackage{float}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}

\newcommand\dist{\stackrel{\mathclap{\footnotesize\mbox{d.}}}{=}}
\usepackage[spanish,onelanguage,ruled,lined, linesnumbered]{algorithm2e}
\usepackage[spanish,onelanguage]{algorithm2e}
\newtheorem{theorem}{Teorema}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposición}
%\newenvironment{proof}[1][Demostración]{\begin{trivlist}
%		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{definition}[1][Definición]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Ejemplo]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Nota]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\negr}[1]{\textit{\textbf{#1}}}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\title{Power Forecasting Update \\ based on discussion notes}

\author{Waleed Alhaddad}

\date{14/08/2019}
\begin{document}
\maketitle

% Participants:
% \begin{multicols}{3}
% \begin{itemize}
% 	\item Waleed
% 	\item Ahmed
% 	\item Raul
% \end{itemize}
% \end{multicols}

\section{Notes and calculations}
\begin{itemize}
\item We prove that the stochastic process of the SDE stays within the range $[0,1]$. Our model is given as follows,
\begin{equation}
\begin{split}
dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
V_0 & = v_0
\end{split}\label{VtSDE}
\end{equation}
where $V_t = X_t - p_t$ and $\theta_t = \max \left( \theta_0 , \frac{|\dot{p}_t|}{\min \left( p_t, 1-p_t\right)} \right)$. For ease of notation, we denote the drift coefficient by $a(v,t) = -\theta_t v$  and $b(v,t)=\sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} $. It is known that the above SDE has transition densities obeying the following Fokker-Plank PDE,
\begin{equation}
	\frac{\partial f(v, t)}{\partial t} = - \frac{\partial}{\partial v} \left( a(v,t) f(v,t) \right) + \frac{\partial^2}{\partial v^2} \left( b^2(v,t) f(v,t)\right)
\end{equation}
which can be rewritten as follows,
\begin{equation}
	\frac{\partial f(v, t)}{\partial t} =- \frac{\partial}{\partial v} S(v,t)
\end{equation}
where $S$ is known as the probability current and is given by,
\begin{equation}
	S(v,t) = - a(v,t) f(v,t) - \frac{\partial}{\partial v} \left( b^2(v,t) f(v,t) \right)
\end{equation}
We can further define an associated probability potential given by,
\begin{equation}
	\Phi (v,t) = \ln \left( b^2(v,t) \right) - \int^v \frac{a(v^{'},t)}{ b^2(v^{'},t)} \ d v^{'}
\end{equation}
And the probability current $S$ can be written in terms of this potential as follows,
\begin{equation}
	S(v,t) = - b^2 (v,t) e^{-\Phi(v,t)} \frac{\partial }{\partial x} \left(  e^{\Phi (v,t) } f(v,t) \right)
\end{equation}
We will show that the probability potential  $\Phi$ tends to infinity at the boarders of the range $[0,1]$. Thus the probability current tends to zero at the boarders. In our case, the probability potential is given by,
\begin{equation}
\begin{split}
	\Phi (v,t) &=  \ln \left( 2 \theta_t \alpha \left( 1-2v-2p_t \right) \right) - \int^v \frac{- \theta_t }{2 \theta_t \alpha (1-2v^{'} - 2p_t) } \ d v^{'}\\
	&= \ln \left( 2 \theta_t \alpha \left( 1- 2v -2p_t  \right)^{1-\frac{1}{4 \alpha}} \right)
\end{split}
\end{equation}
Note that $|\left( 1- 2v -2p_t  \right)^{1-\frac{1}{4 \alpha}} | \leq 1 $ and $\alpha$ is a constant. Also, note that taking the limit as $v\to 1$ implies that $p_t\to 0 $ since $v= x- p_t$ and likewise we have that $v\to -1 $ implies that $p_t \to 1$. Taking the previous notes in consideration and that $\theta_t = \max \left( \theta_0 , \frac{|\dot{p}_t|}{\min \left( p_t, 1-p_t\right)} \right) \to \infty $ as $p_t \to 0$ (equivalently as $v \to 1$) or $p_t \to 1 $ (equivalently as $v \to -1$). Therefore, we have that
\begin{equation}
	\lim_{v \to 1} \Phi (v,t) = \infty , \quad \lim_{v \to -1} \Phi (v,t) = \infty
\end{equation}
Thus equivalently,
\begin{equation}
	\lim_{v \to 1} S(v,t)=0 , \quad \lim_{v \to -1} S(v,t) = 0
\end{equation}

Finally, we conclude that the boarders of the range $[0,1]$ are reflectors and are impenetrable. Hence, the process $V_t$ cannot exit the range $[-1,1]$.

\item Optimizer initialization
	\begin{itemize}
		\item Use least-squares as follows:
		\begin{itemize}
			\item When the first moment is explicit, we use the estimator
			$$\underset{\theta_0}{\arg\min} \sum\limits_{i}^M \sum\limits_j^N (m_1(x,t_{i,j}|\theta_t) - x_{i,j})^2$$ where $m_1(x,t_{i,j}|\theta_0)$ is the first moment of the SDE.

			\item When the first moment is not explicit, we apply least squares on the discretized SDE using Euler to get a first estimate on $\theta_0$ as follows,
			$$ \arg\min \sum\limits_{i}^M \sum\limits_j^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 $$ where $v_{i,j}=x_{i,j}-p_{i,j}$
		\end{itemize} %2*np.sum( forecast_data_inter[1,sel,:]* (1-forecast_data_inter[1,sel,:]) )
		\item Use brackets to get a first estimate on the product
		$$\theta_0 \alpha = \frac{1}{M} \sum\limits_i^M \frac{ \sum\limits_j^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_j^N x_{i,j}(1-x_{i,j}) }$$
		\item combine both estimates to obtain an estimate for the parameters $\theta_0$ and $\alpha$ individually.
	\end{itemize}

\item Compare the following models:
	\begin{itemize}
		\item Moments approach with a Beta proxy. The SDE is given by
		\begin{equation}
		\begin{split}
		dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
		V_0 & = v_0
	\end{split}\label{VtSDE}
	\end{equation}
		and the moments by,
		\begin{equation*}
		\frac{d m_1 (t)}{dt} = - m_1(t)\theta_t \implies m_1(t_2)= V_{t_1} e^{-\int_{t_1}^{t_2} \theta_t \ dt }
		\end{equation*}
		\begin{equation*}
		\begin{split}
		\frac{d m_2 (t)}{dt} &=  - m_2(t)\theta(1+\alpha) + \alpha\theta m_1(t)( (1-p_t -p_t^2)) +2 \\
		& \implies m_2(t_2) = v_{t_1}^2 e^{-(1+\alpha)\int_{t_1}^{t_2} \theta_t \ dt} \\
		& \quad \quad + \alpha \int_{t_1}^{t_2} \left(\theta_s m_1(s)( 1-p_s - p_s^2 )+2\right)   e^{-(1+\alpha)\int_{t_1}^{t_2-s} \theta_u \ du}  \ ds
		\end{split}
		\end{equation*}
		We discretize and integrate numerically step-by-step using the Tripizoidal rule,
		\begin{align*}
			m_{1,i+1}&= v_i \ e^{ - \frac{\theta_i + \theta_{i+1}}{2} \Delta t} \\
			m_{2,i+1} &= v_i^2 e^{-(1+ \alpha)\frac{\theta_i + \theta_{i+1}}{2} \Delta t } + \\
			& \alpha \Delta t  \frac{ \left( \theta_{i+1}m_{1,i+1}(1-p_{i+1} - p_{i+1}^2)+2 \right)e^{-(1+\alpha) \frac{\theta_i + \theta_{i+1}}{2} \Delta t }  + \theta_{i}v_{i}(1-p_{i} - p_{i}^2) +2    }{2}
	\end{align*}
	where $v_i$ is an observation of the process $V_t$ at the previous time step.\\
	We check the Feller condition on the boundaries $[0,1]$ of the process $V_t$. If the following condition holds
	\begin{equation*}
		\lim_{x\to x_{0}} \left( a(x,t)  - \frac{1}{2}\frac{\partial}{\partial x} b^2(x,t) \right) \geq 0
\end{equation*}
Then the process is bounded by $x_0$.
	\begin{equation*}
		\lim_{v\to -1,+1} \left( - \theta_t v - \theta_t \alpha \right( 1- 2v - 2p_t \left) \right) \geq 0
\end{equation*}
		\item Moments approach with a Gaussian proxy after a Lamperti transformation and an approximation in the first moment. The SDE is given by,
		\begin{equation}
			dZ_t= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} + \sqrt{2 \alpha \theta_t} dW_t
	\end{equation}
		where $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $. After the assumption that $\E[\sin(Z_t)]
	 \approx \E Z_t$. Note that $Z_t \in \R $ is not bounded and so this approximation is not justified. We can write approximate the moments as follows,
		\begin{equation*}
					m_1(t_2)= \arcsin \left( e^{- (1-\alpha) \int_{t_1}^{t_2} \theta_t \ dt }  \left(  \int_{t_1}^{t_2} \theta_s \left( 2p_s-1\right)e^{(1-\alpha) \int_{t_1}^{s} \theta_u \ du } \ ds \right) + \sin (Z_{t_1}) \right)
		\end{equation*}
		By linearizing the variance around the mean, we can obtain the following approximate variance
		\begin{equation}
					v(t_2)= e^{2\int_{t_1}^{t_2} \frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_1(s)} \ dt} \left(\alpha \int_{t_1}^{t_2} \theta_t e^{-2\int_{t_1}^{s} \frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_1(s)} } \ ds  \right)
		\end{equation}
		where $a(x;\theta_s)=\frac{- \theta_t (1+ \sin(x) - 2p_t) + \alpha \theta_t \sin (x)   }{\cos (x)}$ is the drift term after the Lamperti transformation.
		We first differentiate the function $a(x;\theta_s)$,
		\begin{align*}
			\frac{\partial a(x;\theta_s)}{\partial x} = \theta_t (2p_t - 1) \tan (x) \sec (x) + \theta_t (\alpha - 1)\sec^2 (x) \
		\end{align*}
		Then, we discretize and integrate numerically step-by-step using the Tripizoidal rule,
		\begin{align*}
		%\begin{split}
			m_{1,i+1} &= \arcsin \left(  \left(  \frac{ \theta_{i+1}(2p_{i_+1} - 1) + \theta_{i}(2p_{i} - 1)e^{- (1-\alpha) \frac{\theta_i + \theta_{i+1}}{2} \Delta t}   }{2} \Delta t \right)  +  \sin(v_i) \right) \\
			v_{i+1} &= \alpha \Delta t  \frac{ \theta_{i+1} e^{2 \frac{\frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_{1,i+1}}}{2} \Delta t  }+  \theta_{i}  e^{2 \frac{\frac{\partial a(x;\theta_s)}{\partial x}|_{x= v_i}}{2}   } }{2}
		%\end{split}
	\end{align*}

		\item Moments approach with a Gaussian proxy on a linearized SDE after a Lamperti transformation. The SDE becomes an Ornstein-Uhlenbeck  type,
		\begin{equation}
			dZ_t = - \theta_t (1-2p_t) \ dt + \theta_t(\alpha -1)  Z_t \ dt + \sqrt{2 \alpha \theta_t} \ dW_t
		\end{equation}
		which has an explicit solution given by,
		\begin{eqnarray*}
			Z_t = Z_0 e^{(\alpha-1)\int_0^t \theta_s \ ds } - \int_0^t \theta_s (1-2p_s) e^{(\alpha-1)\int_s^t \theta_u \ du } \ ds \\ + \int_0^t \sqrt{2 \theta_s \alpha} \ e^{(\alpha-1)\int_s^t \theta_u \ du } \ dW_s
	\end{eqnarray*}
	and its mean and variance are given by,
	\begin{align}
		m_1(t) &= Z_0e^{(\alpha-1)\int_0^t \theta_s \ ds } - \int_0^t \theta_s (1-2p_s) e^{(\alpha-1)\int_s^t \theta_u \ du } \ ds\\
		v(t)&= \int_0^t \sqrt{2 \theta_s \alpha} \ e^{(\alpha-1)\int_s^t \theta_u \ du }
\end{align}
We discretize and integrate numerically step-by-step using the Tripizoidal rule,
\begin{align*}
	m_{1,i+1} &= z_0 e^{(\alpha-1) \frac{\theta_{i+1}+ \theta_i}{2} \Delta t } - \Delta t \frac{\theta_{i+1}( 1-2p_{i+1} )e^{(\alpha-1) \frac{\theta_{i+1} + \theta_i}{2} \Delta t} + \theta_i (1-2p_i) }{2} \\
	v_{i+1} &= \sqrt{2 \alpha} \Delta t \frac{\sqrt{\theta_{i+1}} e^{(\alpha-1)\frac{\theta_{i+1} + \theta_i}{2}\Delta t} +\sqrt{\theta_{i}}  }{2}
\end{align*}

\end{itemize}

\end{itemize}

\section{To-do}
\begin{itemize}
	%\item Do a Feller test to show that the stochastic process stays almost surely inside the interval $[0,1]$.
	\item Adapt the code to run the three different SDEs mentioned above and obtain the parameters.
	\item Adapt the code to optimize using Nelder-Mead algorithm.
	\item Simulate the SDE in Lamperti space to avoid numerical errors pushing the process outside the range $[0,1]$
	\item Simulate from SDE and check and compare its Q-Q plot with that of the data. In this way, we can see if we have captured skewness and/or the heavy "tails". Do that for different power levels.
	\item Another way to showcase the skewness of the beta at different times and levels is to plot its shape parameters. When one shape parameter is larger than the other parameter, we can deduce that it is skewed either to the left or right.
	\item cleaning data from human intervention by setting a probabilistic threshold on the transitions, i.e. if the next point is extremely improbable, then it might be human intervention. The threshold is chosen depending on the number of samples in the data set.
	\item verify our optimization results with that of MCMC to be sure that there aren't any hidden far away valleys in our likelihood.
\end{itemize}
\section{Future explorations}

\begin{itemize}
	\item Introducing non-markovianity or subordinate time versus adding jumps.
	\item Define 'tails' in bounded intervals.
	\item Regularization of the mean reversion parameter $\theta_t = \max \left(  \theta_0, \frac{|\dot{p}_t|}{\min(p_t,1-p_t)} \right)$  for further analytical manipulations.
\end{itemize}

\end{document}

### 2019-08-28 LaTeX_code/Reports/old_reports/SDES_UQ.tex
updated tripizoidal

--- 2019-04-23 LaTeX_code/RW_convergence_results.tex
@@
 
-\title{Prediction of Power Generation}
+\title{Inference  Experiments on some Stochastic Differential Equations \\ (miscellaneous toy models)}
 \subtitle{ Waleed Alhaddad}
@@
 
-\begin{frame}[label=guide]\frametitle{ Reader's Guide }
+%\begin{frame}[label=guide]\frametitle{ Reader's Guide }
+%
+%List of changes in this iteration:
+%\begin{itemize}
+%\item Matched data with every forecast
+%\item Normalized according to installed power of each period
+%\item Interpolated the forecast using cubic splines.
+%
+%\end{itemize}
+%
+%Next steps:
+%\begin{itemize}
+%\item upgrade the numerical integrator and use the interpolated forecast
+%\item Check performace using the interpolated forecasts and data
+%\end{itemize}
+%
+%Note :
+%\begin{itemize}
+%\item Green slides: possible future extensions
+%\item Red slides: notes to be removed
+%\end{itemize}
+%
+%\end{frame}
 
-List of changes in this iteration:
-\begin{itemize}
-\item Implemented Beta transitions
-\item Implemented time dependent forecast
-\item Numerically solve for the first two moments
-\item Time dependent path variability parameter
-\item Convergence results of all the above
-\end{itemize}
-
-Next steps:
-\begin{itemize}
-\item Use real data and forecast.
-\item Try exponential decay in the mean reversion.
-\end{itemize}
-
-Note :
-\begin{itemize}
-\item Green slides: possible future extensions
-\item Red slides: notes to be removed
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Toy model with Synthetic Data }
-We generate paths from an SDE  with given parameters using Monte Carlo simulation and then fit the model to check the retrievability of the parameters. We consider the following cases:
+\begin{frame}\frametitle{ Toy models }
+We generate paths from an SDE  with given parameters and then fit the model to check the retrievability of the parameters. We consider the following cases:
 \begin{itemize}
@@
 {
-\setbeamercolor{background canvas}{bg=green!30}
+%\setbeamercolor{background canvas}{bg=green!30}
 
-\begin{frame}\frametitle{High Frequency  SDE -  Possible Extensions}
-
-\begin{itemize}
-\item Try to understand the limit of when we need to switch to the high frequency from the low frequency regime. That is how it depends on the speed of the  mean reversion in our model.
-\item Get the martingale estimator function of the Gaussian transition density explicitly.
-\item State the optimality and efficiency of the estimators explicitly.
-\item Obtain the stated theoretical convergence rate.
-\item Try to show theoretically why in case 1.2 , the diffusion estimator is not consistent.
-\item Understand and state the conditions under which we have a unique parameter estimation to our SDE.
-\end{itemize}
-
-\end{frame}
-}
+%\begin{frame}\frametitle{High Frequency  SDE -  Possible Extensions}
+%
+%\begin{itemize}
+%\item Try to understand the limit of when we need to switch to the high frequency from the low frequency regime. That is how it depends on the speed of the  mean reversion in our model.
+%\item Get the martingale estimator function of the Gaussian transition density explicitly.
+%\item State the optimality and efficiency of the estimators explicitly.
+%\item Obtain the stated theoretical convergence rate.
+%\item Try to show theoretically why in case 1.2 , the diffusion estimator is not consistent.
+%\item Understand and state the conditions under which we have a unique parameter estimation to our SDE.
+%\end{itemize}
+%
+%\end{frame}
+%}
 
@@
 
-\begin{frame}\frametitle{ Case 4: Following deterministic functions }
-As we construct processes that follow or revert to deterministic function it is natural to state the SDE in terms of deviations from the deterministic function. Then, we have for $V_t= X_t - p_t$
-
-\begin{equation}
-\begin{split}
-dV_t &= a(V_t; \bm{\theta}_t) dt + b (V_t; \bm{\theta}_t ) dW_t \quad t > 0 \\
-V_0 & = v_0
-\end{split}\label{main_V}
-\end{equation}
-
-where we choose $ a(V_t; \bm{\theta}_t) = - \theta_t V_t$ to have mean reversion with exponential speed in time controlled by some strictly positive parameter $\theta_t$.
-To keep the process within a unit box, we choose $ b (V_t; \bm{\theta} )= \sqrt{ 2 \alpha_t \theta_t p_t (1-p_t)X_t (1-X_t)   }$
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4: Implementation }
-In the previous sections we relied on the Euler discretization of SDEs in order to obtain our estimators through the Maximum Likelihood approach.
-However, this introduces errors in the likelihood similar to the observed error in the wiener process following the sine wave in (\ref{fig:sine}).
-To prevent such artifacts, we solve for the moments of the process defined by the SDE in (\ref{main_V}).
-We have,
-
-\begin{equation}
-\begin{split}
-\E [V_t^k] &=  \E \Big[ \Big( \int a(V_t; \bm{\theta}_t) dt + \int b (V_t; \bm{\theta}_t ) dW_t \Big)^k \Big] \quad t > 0 \\
-V_0 & = v_0
-\end{split}\label{main_V_expectations}
-\end{equation}
-For a Gaussian approximation, we are interested in the first two moments.
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4: Implementation - first moment }
-The first moment $(k=1)$ is given by,
-
-\begin{equation}
-\begin{split}
- m_1(t) =\E V_t &=  \E \Big[  \int a(V_t; \bm{\theta}_t) dt \Big] + \E \Big[ \int b (V_t; \bm{\theta}_t ) dW_t  \Big] \\
- & = \E \Big[  \int a(V_t; \bm{\theta}_t) dt \Big]
-\end{split}\label{main_V_1_moment}
-\end{equation}
-In our case, the drift is linear and is given by $ a(V_t; \bm{\theta}_t) = - \theta_t V_t$. then, we have 
-\begin{equation}
-\begin{split}
- & m_1(t) =\E V_t =     \Big[  \int - \theta_t \E V_t dt \Big] 
- \iff \frac{dm_1(t)}{dt}=    - \theta_t m_1(t) \ \ ; \quad m_1(0)=\E[V_0]= v_0
-\end{split}\label{main_V_1_moment}
-\end{equation}
-This is an ODE which has solutions of the form, 
-\begin{equation}
-m_1(t) = v_0 \exp ( - \int_0^t \theta_s \ ds ) 
-\end{equation}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4: Implementation - second moment }
-The second moment $(k=2)$ is given by,
-
-\begin{equation}
-\begin{split}
-  =\E V_t^2 &=  \E \Big[ \Big( \int a(V_t; \bm{\theta}_t) dt + \int b (V_t; \bm{\theta}_t ) dW_t \Big)^2 \Big] \\
-\end{split}\label{main_V_2_moment}
-\end{equation}
-Let $Y_t=g(V_t)=V_t^2$ then $g_t= 0 , \ g^{'} (V_t) = 2V_t$ and $g^{''} (V_t) = 2$. Using $It\hat{o}$ and Taylor, 
-\begin{equation}
-\begin{split}
-dY_t =  \frac{\partial g}{\partial t} dt &+  \frac{\partial g}{\partial v} \Big(a (V_t; \bm{\theta}_t ) \ dt + b (V_t; \bm{\theta}_t ) dW_t  \Big)\\
-& + \frac{1}{2} \frac{\partial^2 g}{\partial v^2} \Big(a (V_t; \bm{\theta}_t ) \ dt + b (V_t; \bm{\theta}_t ) dW_t  \Big)^2 + \mathcal{O}(dV_t^3)
-\end{split}
-\end{equation}
-As $dt \to 0$, we have
-\begin{equation}
-\begin{split}
-dY_t &=  \frac{\partial g}{\partial t} + \Big( a (V_t; \bm{\theta}_t ) \frac{\partial g}{\partial v}  + \frac{b^2 (V_t; \bm{\theta}_t )}{2} \frac{\partial^2 g}{\partial v^2} \Big) dt + b (V_t; \bm{\theta}_t ) \frac{\partial g}{\partial v} dW_t  \\
-&= 2\Big( a (V_t; \bm{\theta}_t ) V_t  + \frac{b^2 (V_t; \bm{\theta}_t )}{2}  \Big) dt +  2V_t b (V_t; \bm{\theta}_t ) dW_t
-\end{split}
-\end{equation}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4: Implementation - second moment }
-The second moment $(k=2)$ is given by,
-
-\begin{equation}
-\begin{split}
-\E [V_t^2] =  \E Y_t &= 2  \E\Big[ \int \Big( a (V_t; \bm{\theta}_t ) V_t  + \frac{b^2 (V_t; \bm{\theta}_t )}{2}  \Big) dt \Big] +  2 \E \Big[ \int V_t b (V_t; \bm{\theta}_t ) dW_t \Big]\\
-&= 2  \E\Big[ \int \Big( a (V_t; \bm{\theta}_t ) V_t  + \frac{b^2 (V_t; \bm{\theta}_t )}{2}  \Big) dt \Big]\\
-\end{split}
-\end{equation}
-In our case, the drift is $ a(V_t; \bm{\theta}_t) = - \theta_t V_t$ and the diffusion is given by $ b (V_t; \bm{\theta} )= \sqrt{ 2 \alpha_t \theta_t p_t (1-p_t)X_t (1-X_t)   } =  \sqrt{ 2 \alpha_t \theta_t p_t (1-p_t)(V_t + p_t) (1-V_t-p_t)   }$.
-Then,
-\begin{equation*}
-\begin{split}
-m_{2}&(t)=\E [V_t^2] = 2  \int \Big( - \theta_t \E[V_t^2]  +  \alpha_t \theta_t p_t (1-p_t)\E[(V_t + p_t) (1-V_t-p_t) ] \Big) dt \\
-&=2  \int \Big( - \theta_t \E[V_t^2]  +  \alpha_t \theta_t p_t (1-p_t)( p_t(1 - p_t) +(1-2p_t)\E[V_t] - \E[V_t^2] ) \Big) dt \\
-&=2  \int \Big( -\E[V_t^2] [\theta_t + \alpha_t \theta_t p_t(1-p_t) ] + \E[V_t][\alpha_t \theta_t p_t (1-p_t) (1-2p_t)] + \alpha_t \theta_t p_t^2(1-p_t)^2 \Big) dt \\
-\end{split}
-\end{equation*}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4: Implementation - second moment }
-The second moment $m_2(t)$ is given by solving the ODE,
-
-\begin{equation*}
-\begin{split}
-\frac{d m_{2}(t)}{dt}&=2 \Big( -m_{2}(t) [\theta_t + \alpha_t \theta_t p_t(1-p_t) ] + m_{1}(t)[\alpha_t \theta_t p_t (1-p_t) (1-2p_t)] + \alpha_t \theta_t p_t^2(1-p_t)^2 \Big) \\
-\end{split}
-\end{equation*}
-where $m_2(0) = \E[V_0^2] = v_0^2$ and has a solution of the form,
-\begin{equation*}
-\begin{split}
-&m_{2}(t) = m_{2}(0) \exp \Big( -2 \int_0^t  [\theta_\tau + \alpha_\tau \theta_\tau p_\tau(1-p_\tau) ] \ d\tau  \Big) + \\
-& 2 \int\limits_{0}^{t}   \exp \Big( -2 \int_0^s  [\theta_\tau + \alpha_\tau \theta_\tau p_\tau(1-p_\tau) ] \ d\tau \Big) \Big( m_{1}(t-s)[\alpha_{t-s} \theta_{t-s} p_{t-s} (1-p_{t-s}) (1-2p_{t-s})]  \\
-& + \alpha_{t-s} \theta_{t-s} p_{t-s}^2(1-p_{t-s})^2 \Big)  \  ds
-\end{split}
-\end{equation*}
-
-\end{frame}
-
-\begin{frame}\frametitle{Following deterministic functions - Cases }
-
-We consider the following cases:
-\begin{itemize}
-\item[4.1] Constant parameters $\bm{\theta}_t = \bm{\theta} $
-	\begin{itemize}
-	\item[4.1.1] reverting to a constant function
-	\item[4.1.2] reverting to a deterministic function
-	\end{itemize}
-\item[4.2] Time dependent parameters $\bm{\theta}_t$
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1: Following deterministic functions - constant parameters }
-In this case, the first moment  $m_1(t)$ reduces to,
-
-\begin{equation}
-m_1(t) = v_0 \exp ( -t\theta ) 
-\end{equation}
-And the second moment $m_2(t)$ reduces to,
-
-\begin{equation*}
-\begin{split}
-&m_{2}(t) = m_{2}(0) \exp \Big( -2  [t \theta + \alpha \theta \int_0^t    p_\tau (1-p_\tau)  \ d\tau ] \Big) + \\
-& 2 \int\limits_{0}^{t}    \exp \Big( -2 [s \theta + \alpha \theta \int_0^s    p_\tau (1-p_\tau)  \ d\tau ] \Big) \Big( m_{1}(t-s)[\alpha \theta p_{t-s} (1-p_{t-s}) (1-2p_{t-s})]  \\
-& + \alpha \theta p_{t-s}^2(1-p_{t-s})^2  \Big) \  ds
-\end{split}
-\end{equation*}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-For constant forecast $p_t = \frac{1}{2}$ the second moment reduce further,
-
-\begin{equation*}
-\begin{split}
-&m_{2}(t) = m_{2}(0) \exp \Big( -2 t \theta (1 + \frac{\alpha }{4} ) \Big) +   \frac{\alpha \theta}{8} \int\limits_{0}^{t}  \exp \Big( -2 s \theta (1 + \frac{\alpha }{4} )\Big) \  ds \\
-& =m_{2}(0) \exp \Big( -2 t \theta (1 + \frac{\alpha }{4} ) \Big) + \frac{\alpha }{16 (1+ \frac{\alpha}{4})} \Big(1- \exp ( -2 t \theta (1 + \frac{\alpha }{4} ) \Big) 
-\end{split}
-\end{equation*}
-Then the variance is given by,
-\begin{equation}
-\V[V_t] =m_{2}(0) \exp \Big( -2 t \theta (1 + \frac{\alpha }{4} ) \Big) + \frac{\alpha }{16 (1+ \frac{\alpha}{4})} \Big(1- \exp ( -2 t \theta (1 + \frac{\alpha }{4} ) \Big)   - v_0^2 \exp ( -2t\theta )
-\end{equation}
-Note that the second moment $m_2(0)=v_0^2$ as the previous point $V_{t_{i-1}}=v_0$ deterministic.
-%% CHANGE ALL zero lower bounds to t_{i-1} 
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-
-To conclude, we have the following mean and variance functions,
-
-\begin{equation}
-\begin{split}
-\E[V_{t_i}| V_{t_{i-1}}=v_0] &= v_0 \exp ( -(t_i - t_{i-1})\theta ) \\
- \V[V_{t_i}| V_{t_{i-1}}=v_0] &= \frac{\alpha }{16 (1+ \frac{\alpha}{4})} \Big(1- \exp ( -2 (t_i - t_{i-1}) \theta (1 + \frac{\alpha }{4} ) \Big) \\
-\end{split}
-\end{equation}
-
-Next, we discretize  and obtain the likelihood.
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-To obtain the likelihood, consider a set of N observations, $X= \{ X_{t_0^N} , X_{t_1^N} ,\ldots , X_{t_N^N} \}$ on intervals of $\Delta_N$. We have $V=X-\frac{1}{2}$ .  Then,
-
-\begin{equation}
-\begin{split}
-\E[V_{i}| V_{i-1}=v_0] &= v_0 \exp ( -\Delta_N \theta )  \\
- \V[V_{i}| V_{i-1}=v_0] &= \frac{\alpha }{16 (1+ \frac{\alpha}{4})} \Big(1- \exp ( -2 \Delta_N\theta (1 + \frac{\alpha }{4} ) \Big)\\
-\end{split}
-\end{equation}
-
-The Likelihood  of the transition density is given by,
-
-\begin{equation}
-\mathcal{L}(\theta;X) = \prod\limits_{j=1}^M\prod\limits_{i=1}^N\rho( {V_{j,i+1}|V_{j,i}}, \bm{\theta}) 
-\end{equation}
-And the Gaussian transition density,
-\begin{equation*}
-\mathcal{L}(\bm{\theta}; V) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N  \frac{1}{\sqrt{2 \pi \V[V_{j,t_i}| V_{j,t_{i-1}}=v_0] }  } \exp\Big(\frac{-(V_{j,i+1}   - \E[V_{j,t_i}| V_{j,t_{i-1}}=v_0] )^2}{2\V[V_{t_i}| V_{j,t_{i-1}}=v_0]}\Big)
-\end{equation*}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-We obtain the following convergence using the analytical moments obtained from the $V_t$ process and enforcing that the parameters $\theta$ and $\alpha$ are non-negative.
-
-\begin{figure}
-   \includegraphics[scale=0.22]{Figures/conv_M_moments_constant_func_sym.jpg}
-    \includegraphics[scale=0.22]{Figures/conv_N_moments_constant_fun_symjpg.jpg}
-  \caption{This is done for true parameters $\theta = 0.5$ and $\alpha=1$ using  L-BFGS-B optimization algorithm }
-  %\label{fig:boat1}
-\end{figure}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-Further, we note that the  inference on the drift needs special care in situations of high speed reversion to the mean. Such situations seem to occur in the following cases:
-\begin{itemize}
-\item  $ \theta > > 1$  and big enough $\alpha$
-\item  $\Delta_N > > 1$
-
-\end{itemize}
-In both cases, we see a flattening in the likelihood in the direction of the drift parameter $\theta$ which  causes the optimizer to return inconsistent estimates of the drift parameter $\theta$.
-These two cases are applicable if the function or the process oscillates at a high frequency with respect to the other.
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-
-\begin{figure}
-    \includegraphics[scale=0.22]{Figures/sample_moments_constant_func_1_01.pdf}
-    \includegraphics[scale=0.22]{Figures/sample_moments_constant_func_10_01.pdf}
-      \includegraphics[scale=0.22]{Figures/sample_moments_constant_func_100_01.pdf}
-
-    \includegraphics[scale=0.22]{Figures/conv_M_moments_constant_func_1_01.pdf}
-    \includegraphics[scale=0.22]{Figures/conv_M_moments_constant_func_10_01.pdf}
-      \includegraphics[scale=0.22]{Figures/conv_M_moments_constant_func_100_01.pdf}
-
-          \includegraphics[scale=0.22]{Figures/conv_N_moments_constant_fun_1_01.pdf}
-    \includegraphics[scale=0.22]{Figures/conv_N_moments_constant_fun_10_01.pdf}
-      \includegraphics[scale=0.22]{Figures/conv_N_moments_constant_fun_100_01.pdf}
-
-  \caption{We can see how an increase of $\theta >>1$ with big enough $\alpha$ causes sharp oscillations that make the inference of  $\theta$ unfeasible.  }
-  %\label{fig:boat1}
-\end{figure}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-In the second case of increasing $\Delta_N$, we see the following flattening of the likelihood in the direction of $\theta$.
-\begin{figure}
-    \includegraphics[scale=0.5]{Figures/dt_increasing_moments.pdf}
-
-  \caption{We can see how an increase of time intervals $\Delta_N >>1$  causes a flattening of the likelihood making the valley of the optimal $\theta$ shallower  until the  inference of  $\theta$ becomes unfeasible.
-}
-  %\label{fig:boat1}
-\end{figure}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-
-Question: How can we quantify the mean reversion of an SDE   ?  \\
-
-The reversion to the mean is not only determined by the parameter $\theta$ but also by the diffusion term. We can see this in the following example,
-
-\begin{equation}
-dX_t = (1+X_t)dt + (1+X_t^2) dW_t
-\end{equation}
-
-which at first glance does not seem mean reverting, but in fact,  it is mean reverting.
-The reversion is driven  solely  by diffusion term in this case.
-This is a case of volatility induced stationary, as the non-linearity in the diffusion term are responsible for the mean reversion.
-A similar non-linearity is present in our model and quantifying the effective mean reversion  will help determine if we are in the convergent regime  where our estimator of the drift is consistent or not.
-
-Regarding, the specific application to wind forecasts this should not be an issue as the forecast and the recorded data are unlikely to oscillate around each other at a "high" frequency.
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-
-Answer: Yes, it is true that such SDE's are stationary even though they are not "mean reverting". The  "mean reversion" or the "pull" is induced solely by the diffusion term. We can show that
-
-\begin{equation}
-dX_t = (1+X_t)dt + (1+X_t^2) dW_t
-\end{equation} 
-is stationary. Even though its associated process with constant diffusion $\sigma$
-\begin{equation}
-dX_t = (1+X_t)dt + \sigma dW_t
-\end{equation}
-is clearly non-stationary. We can do that using the tools we will introduce next to check and find the stationary distributions of our SDEs. Namely, using the scale and speed densities. 
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
-Consider an SDE,
-\begin{equation}
-\begin{split}
-dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
-X_0 & = x_0
-\end{split}\label{main}
-\end{equation}
-We define the scale density $s(x)$,
-\begin{equation}
-s(x) = exp \Big[ \int^x - \frac{2  a(y; \bm{\theta})}{b^2 (y; \bm{\theta} )}\ dy \Big]
-\end{equation}
-And the speed density $m(x)$,
-\begin{equation}
-m(x) = \frac{1}{b^2 (y; \bm{\theta}) \  s(x)}
-\end{equation}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
-
-A unique stationary distribution of the process $X_t$ exists if and only if 
-\begin{equation}
-\int_{x_0}^r s(x) \ dx = \infty \quad \int_{l}^{x_0} s(x) \ dx = \infty \quad \int_l^r m(x) \ dx < \infty
-\end{equation}
-where $x_0 \in (l,r)$ and $(l,r)$ is an interval where $b^2 (y; \bm{\theta} ) > 0$
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
-Considering the  SDE of a process following a constant forecast $p$,
-\begin{equation}
-\begin{split}
-dX_t &= -\theta(X_t - p) dt + \sqrt{2 \theta \alpha p(1-p) X_t (1-X_t)} dW_t \quad t > 0 \\
-X_0 & = x_0
-\end{split}\label{main}
-\end{equation}
-We obtain the scale density $s(x)$ with integrability condition $\frac{p}{a} \leq -1 $ and $\frac{1-p}{a} \leq -1$
-\begin{equation}
-s(x) = exp \Big[ \int^x - \frac{2  a(y; \bm{\theta})}{b^2 (y; \bm{\theta} )}\ dy \Big] = exp \Big[ \int^x_{x_0}  \frac{y-p}{a y (y-1)}\ dy \Big]  \propto (1-x)^{\frac{1-p}{a}} x^{p/a}
-\end{equation}
-where $a= - \alpha p(1-p) <0$.Then the speed density $m(x)$ becomes, 
-\begin{equation}
-m(x) = \frac{1}{b^2 (y; \bm{\theta}) \  s(x)} \propto (1-x)^{-\frac{1-p}{a}-1} x^{-\frac{p}{a}-1}
-\end{equation}
-We note that $(l,r) = (-\infty, \infty)$ is where $b^2 (y; \bm{\theta} ) >0$. Let $x_0 \in (l,r)$. Taking $x_0=1$ we see that
-\begin{equation}
-\int_{x_0}^r s(x) \ dx = \infty \quad \int_{l}^{x_0} s(x) \ dx = \infty \quad \int_l^r m(x) \ dx < \infty
-\end{equation}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
-Under the condition,
-\begin{equation}
-\begin{cases}
-\frac{p}{a} \leq -1\\
-\frac{1-p}{a} \leq -1\\
-\end{cases}\iff
-\min (p, 1-p) \geq -a \iff  \min (p, 1-p) \geq \alpha p(1-p)
-\end{equation}
-For example, if forecast is constant $ p = \frac{1}{2}$, the condition becomes $\alpha \leq 2$.
-
-we conclude that there exists a unique stationary distribution of  $X_t$ and its proportional to the speed density,
-\begin{equation}
-m(x)\propto (1-x)^{-\frac{1-p}{a}-1} x^{-\frac{p}{a}-1}
-\end{equation}
- which is the kernal of a Beta distribution with shape parameters
-\begin{equation}
-  Beta \ \Big( \frac{p}{\alpha (1-p)}, \frac{1}{\alpha p } \Big)
-\end{equation}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
-Now we consider the centered process $V_t= X_t - p$,
-\begin{equation}
-\begin{split}
-dX_t &= -\theta V_t dt + \sqrt{2 \theta \alpha p(1-p) (V_t +p ) (1-V_t-p)} dW_t \quad t > 0 \\
-X_0 & = x_0
-\end{split}\label{main}
-\end{equation}
-We obtain the scale density $s(x)$,
-\begin{equation}
-s(x) = exp \Big[ \int^x - \frac{2  a(y; \bm{\theta})}{b^2 (y; \bm{\theta} )}\ dy \Big] = exp \Big[ \int^x_{x_0} \frac{y-p}{a y^2 + by +c}\ dy \Big]  
-\end{equation}
-where,
-\begin{equation}
-\begin{cases}
-a&=  \alpha p(1-p)\\
-b&=  \alpha p(1-p)(2p-1)\\
-c&=  \alpha p^2(1-p)^2\\
-\end{cases}
-\end{equation}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
-To simplfy, we choose the constant forecast to be $p=\frac{1}{2}$. Then we have,
-
-\begin{equation}
-\begin{cases}
-a&=  \frac{\alpha}{4} \\
-b&=  0 \\
-c&=  \frac{\alpha}{16} \\
-\end{cases}
-\end{equation}
-and the scale density becomes, 
-\begin{equation}
-\begin{split}
-s(x) &= exp \Big[ \int^x - \frac{2  a(y; \bm{\theta})}{b^2 (y; \bm{\theta} )}\ dy \Big] = exp \Big[ \int^x_{x_0} \frac{y}{a y^2 +c}\ dy \Big] =exp \Big[ \int^x_{x_0} \frac{y}{\frac{\alpha }{16}+\frac{\alpha  y^2}{4}}\ dy \Big]\\
-& \propto \left(4 v^2+1\right)^{2/\alpha } \quad \quad (\alpha >0)
-\end{split}
-\end{equation}
-Then we have the speed density $m(x)$,
-\begin{equation}
-m(x) = \frac{1}{b^2 (y; \bm{\theta}) \  s(x)} \propto \left(4 v^2+1\right)^{-\frac{\alpha +2}{\alpha }}
-\end{equation}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
-We proceed to check if it is stationary.
-
-We note that $(l,r) = (-\infty, \infty)$ is where $b^2 (y; \bm{\theta} ) >0$. Let $x_0 \in (l,r)$. Taking $x_0=0$, we see that
-\begin{equation}
-\int_{x_0}^r s(x) \ dx = \infty \quad \int_{l}^{x_0} s(x) \ dx = \infty \quad \int_l^r m(x) \ dx < \infty
-\end{equation}
-So we conclude that it is a stationary distribution of $V_t$ and its unique.
-Hence, the kernal of the invarient distribution of the process $V_t$ with constant forecast $p=\frac{1}{2}$ is $\pi(v)= \frac{\sqrt{\pi} \  \Gamma (\frac{1}{2}+ \frac{2}{\alpha})}{\Gamma(\frac{2+\alpha}{\alpha})}\left(1+4 v^2\right)^{-\frac{\alpha +2}{\alpha }}$.
-Note that it almost resembles a t-student distribution.
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Theoretical Background }
-
-\begin{figure}
-    \includegraphics[scale=0.9]{Figures/invarient_Vt.pdf}
-  \caption{ The stationary distribution $\pi(v)$ of the process $V_t$ is symmetric with heavy tails.}
-  %\label{fig:boat1}
-\end{figure}
-
-\end{frame}
-
-\begin{frame}\frametitle{Following deterministic functions - Cases }
-
-In an improved model, we incorperate  Beta density transitions. We repeat the same cases as follows:
-\begin{itemize}
-\item[5.1] Constant parameters $\bm{\theta}_t = \bm{\theta} $
-	\begin{itemize}
-	\item[5.1.1] reverting to a constant function
-	\item[5.1.2] reverting to a deterministic function
-	\end{itemize}
-\item[5.2] Time dependent parameters $\bm{\theta}_t$
-\end{itemize}
-
-However, first lets discuss why and how do we incorperate the Beta transition densities.
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
-Recall that both $X_t$ and $V_t$ are controlled processes that are constrained within a unit box.
-The symmetry of the Gaussian transition density of these two processes indicate that we have some probability outside the unit box once the forecast touches the boundry.
-There are many ways to fix this behaviour:
-\begin{enumerate}
-\item Use a Beta transition density for all the transitions while matching the moments of the Gaussian transition density.
-\item Use a Beta transition density only when the transition density of the process touches the boundry of the unit box.This depends on the width and position of the transition density.
-\begin{enumerate}
-\item match the parameters of the Beta transition with the moments of the Gaussian transition.
-\item Not to match the moments of the Gaussian and introdude the beta parameters as two additional hyperparameters (increasing the degrees of freedom).
-\end{enumerate}
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
-
-If we like to enforce that the Beta transition matches the moments of the Gaussian, then
-we can solve for the paramters of the Beta distribution in terms of the parameters of the Gaussian transition density.
-
-First, lets consider the non-centered process $X_t$.
-In that case, we choose standard Beta distribution which has support on $x \in [0,1]$.
-Then solving for its parameters in terms of the parameters of the Gaussian transition denisty, to obtain
-
-\begin{equation} 
-\alpha = \Big(  \frac{1-\tilde{\mu}}{\tilde{\sigma}^2} -\frac{1}{\tilde{\mu}}   \Big)\tilde{\mu}^2 \quad \quad \beta =  \alpha \Big(\frac{1}{\tilde{\mu}} -1 \Big)
-\end{equation}
-where $\tilde{\sigma}^2$ is the variance of the Gaussian transition density of the process and $\tilde{\mu}$ is its mean.
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
-To ensure the existence of such a Beta distribution with the parameters required
-\begin{equation} 
-\alpha = \Big(  \frac{1-\tilde{\mu}}{\tilde{\sigma}^2} -\frac{1}{\tilde{\mu}}   \Big)\tilde{\mu}^2 \quad \quad \beta =  \alpha \Big(\frac{1}{\tilde{\mu}} -1 \Big)
-\end{equation}
-we have the followind conditions by the definition of the standard Beta distribution:
-\begin{enumerate}
-\item $x \in [0,1]$.
-\item Its shape parameters $\alpha$ and $\beta$ must be positive definite.
-\end{enumerate}
-Solution (this only applies to Euler realizations due to time discretization):
-\begin{enumerate}
-\item Discard realizations $X_t$ outside the range $(0,1)$.
-\item Ensure that $\alpha >0$ and $\beta >0 $ with high probability.
-\end{enumerate}
-The first condition is automatically satisfied with high probability. The second condition introduces the following restrictions:
-\begin{equation}
-\alpha >0 ,\ \beta >0 \iff  0< \tilde{\mu}_t < 1  \ \text{and} \  \tilde{\sigma}_t^2 < \tilde{\mu}_t - \tilde{\mu}_t^2
-\end{equation}
-while the first restriction $ 0< \tilde{\mu}_t < 1$ holds with very high probability.
-The second restricts the second moment of the process $X_t$ not to exceed its mean,  i.e $\E[X_t^2] \leq \tilde{\mu}_t \quad \forall t$
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
-Next, we consider the centered process $V_t$.
-Since the process $V_t$ is  inside the range $(-1,1)$ with high probability, the standard Beta distribution cannot model its transitions.
-Therefore, we translate the distribution to have support on $[a,b]=[-1,1]$.
-We use the linear transformation $y= g(x)= a + (b-a) x $ then we have
-\begin{equation}
-\  g^{-1}(y)= \frac{a-y}{b-a} \quad \text{and} \quad \Big| \frac{\partial g^{-1}(y)}{\partial y }  \Big| = \frac{1}{b-a}
-\end{equation}
-And the general Beta distribution becomes, 
-\begin{equation}
-f_Y(y)= f_X(g^{-1}(y) ) \Big| \frac{\partial g^{-1}(y)}{\partial y }  \Big| = \frac{1}{B(\alpha, \beta) (b-a)} \Big(\frac{a-y}{b-a}\Big)^{\alpha -1}\Big(1-\frac{a-y}{b-a} \Big)^{\beta -1}
-\end{equation}
-and we have,
-\begin{equation}
-\E[Y]= a + (b-a) \E[X] = a + (b-a) \frac{\alpha}{\alpha + \beta}
-\end{equation}
-\begin{equation}
-\V[Y]= (b-a)^2 \V[X] = (b-a)^2 \frac{\alpha \beta}{(\alpha + \beta)^2 (\alpha + \beta + 1)}
-\end{equation}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
-Next, we need to solve the system in terms of the mean and variance of the process $V_t$.
-\begin{equation}
-\begin{cases}
-\tilde{\mu}_t=a + (b-a) \frac{\alpha}{\alpha + \beta}\\
-\tilde{\sigma}_t^2= (b-a)^2 \frac{\alpha \beta}{(\alpha + \beta)^2 (\alpha + \beta + 1)}\\
-\end{cases}
-\end{equation}
-to obtain, 
-\begin{equation}
-\alpha = \frac{(\tilde{\mu}_t-a) \left(\tilde{\mu}_t^2-\tilde{\mu}_t (a+b)+\tilde{\sigma}_t^2+a b\right)}{\tilde{\sigma}_t^2 (a-b)}
-\end{equation}
-
-\begin{equation}
-\beta = \frac{(\tilde{\mu}_t-b) \left(\tilde{\mu}_t^2-\tilde{\mu}_t (a+b)+\tilde{\sigma}_t^2+a b\right)}{\tilde{\sigma}_t^2 (b-a)}
-\end{equation}
-then for our interval of interest $[a,b]=[-1,1]$, we have
-
-\begin{equation}
-\alpha = - \frac{(1+\tilde{\mu}_t )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \quad \quad \beta =  \frac{(\tilde{\mu}_t-1 )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \label{param_transformed_beta}
-\end{equation}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
-As before, for the general Beta distribution on the interval $[a,b]=[-1,1]$, we must have that
-\begin{enumerate}
-\item $x \in [-1,1]$.
-\item Its shape parameters $\alpha$ and $\beta$ must be positive definite.
-\end{enumerate}
-Solution (this only applies to Euler realizations due to time discretization):
-\begin{enumerate}
-\item Discard realizations $V_t$ outside the range $(-1,1)$.
-\item Ensure that $\alpha >0$ and $\beta >0 $ with high probability.
-\end{enumerate}
-The first condition is automatically satisfied with high probability. The second condition introduces the following restrictions:
-\begin{equation}
-\alpha >0 ,\ \beta >0 \iff  0< \tilde{\mu}_t < 1  \ \text{and} \  \tilde{\sigma}_t^2 < 1 - \tilde{\mu}_t^2
-\end{equation}
-while the first restriction $ -1< \tilde{\mu}_t < 1$ holds with very high probability.
-The second restricts the second moment of the process $V_t$ not to exceed one,  i.e.
-$\E[V_t^2] \leq 1 \quad \forall t$
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
-If we approximate all transitions by a Beta transition density, we obtain the log-likelihood, 
-\begin{equation}
-\ell(\bm{\theta}; V)= \sum\limits_{j=1}^M \sum\limits_{i=1}^N (\alpha -1)\log(V_{j,i+1}) + (\beta -1) \log(1-V_{j,i+1}) - \log (B(\alpha, \beta))
-\end{equation}
-where $B(\alpha, \beta)=\frac{\Gamma (\alpha)\Gamma (\beta)}{\Gamma (\alpha + \beta)}$ is the Beta function. And enforcing to match the transition moments of the Gaussian, we have
-\begin{equation} 
-\alpha = \Big(  \frac{1-E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]}{\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} -\frac{1}{E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]}   \Big)E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]^2 \label{alph}
-\end{equation}
-
-\begin{equation} 
- \beta =  \alpha \Big(\frac{1}{\E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]} -1 \Big) \label{gam}
-\end{equation}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
-Another approach is to only approximate by a Beta distribution if the transition density of $X_t$ is sufficiently crossing the boarder of the unit box.
-For example, we approximate by a Beta the samples that satisfy either of the following conditions,
-\begin{equation}
-\begin{cases}
-\mu_{t_i} + 3 \sigma_{t_i} >1\\
-\mu_{t_i} - 3 \sigma_{t_i} <0
-\end{cases} \iff
-\begin{cases}
-E[V_{j,t_i}| V_{j,t_{i-1}}=v_0] + p + 3 \sqrt{\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} >1\\
-E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]+p - 3 \sqrt{\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} <0
-\end{cases}
-\end{equation}
-
-If a sample $V_{j,t_{i-1}}$ satisfies either of these conditions, we denote it by $\bar{V}_{j,t_{i-1}}$ and the number of such samples by $\bar{N}$.
-
-%where $B(\alpha, \beta)=\frac{\Gamma (\alpha)\Gamma (\beta)}{\Gamma (\alpha + \beta)}$ is the Beta function.
-%\begin{equation} 
-%\alpha = \Big(  \frac{1-E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]}{\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} -\frac{1}{E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]}   \Big)E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]^2 
-%\end{equation}
-%
-%\begin{equation} 
-% \beta =  \alpha \Big(\frac{1}{\E[V_{j,t_i}| V_{j,t_{i-1}}=v_0]} -1 \Big)
-%\end{equation}
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.1.1: Following a constant function - constant parameters }
-We then construct the following likelihood,
-
-\begin{equation}
-\mathcal{L}(\theta;X) = \prod\limits_{j=1}^M \left[ \prod\limits_{i=1}^{N-\bar{N}}\rho( {V_{j,i+1}|V_{j,i}}, \bm{\theta}) \prod\limits_{i=1}^{\bar{N}} \bar{\rho}( {\bar{V}_{j,i+1}|\bar{V}_{j,i}}, \bm{\theta}) \right]
-\end{equation}
-
-and the log-likelihood becomes, 
-\begin{equation}
-\begin{split}
-\ell(\bm{\theta}; V)&= \sum\limits_{j=1}^M \Big(  \sum\limits_{i=1}^{\bar{N}} (\alpha -1)\log(\bar{V}_{j,i+1}) + (\beta -1) \log(1-\bar{V}_{j,i+1}) - \log (B(\alpha, \beta))\\
-&+ \sum\limits_{i=1}^{N-\bar{N}} - \frac{(V_{j,i+1}   - \E[V_{j,t_i}| V_{j,t_{i-1}}=v_0] )^2}{2\V[V_{t_i}| V_{j,t_{i-1}}=v_0]} - \frac{1}{2} \Big(2 \pi \V[V_{j,t_i}| V_{j,t_{i-1}}=v_0] \Big) \Big)
-\end{split}
-\end{equation}
-where $\alpha$ and $\beta$ are given as in (\ref{alph}) and (\ref{gam}).
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent  parameters }
-We approximate all transitions by a Beta transition density, we obtain the log-likelihood, 
-\begin{equation}
-\ell(\bm{\theta}; V)= \sum\limits_{j=1}^M \sum\limits_{i=1}^N (\alpha -1)\log(\frac{V_{j,i+1}+1}{2}) + (\beta -1) \log(1-\frac{V_{j,i+1}+1}{2}) - \log ( 2 B(\alpha, \beta))
-\end{equation}
-
-where $\alpha$ and $\beta$ are given as in (\ref{param_transformed_beta}):
-
-\begin{equation}
-\alpha = - \frac{(1+\tilde{\mu}_t )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \quad \quad \beta =  \frac{(\tilde{\mu}_t-1 )(\tilde{\mu}_t^2 + \tilde{\sigma}_t^2 -1)}{2 \tilde{\sigma}_t^2} \label{param_transformed_beta}
-\end{equation}
-where we compute the moments numerically before each realization using Euler
-\begin{equation}
-\tilde{\mu} = V_{j,i-1}e^{- \Delta N \theta}
-\end{equation}
-\begin{equation}
-\begin{split}
-\tilde{\sigma}_t^2 =  V_{j,i-1}^2 +& 2\Delta N (-V_{j,i-1}^2(\theta+\alpha\theta p_i (1-p_i) )  + \\
-& V_{j,i-1}(\alpha\theta p_i(1-p_i)(1-2p_i )) + \alpha\theta p_i^2(1-p_i)^2) - \tilde{\mu}^2
-\end{split}
-\end{equation}
-where $p_i$ is the discretization of the time dependent forecast.
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent parameters }
-We generate samples using the previous Euler scheme to numerically compute the moments before each realization.We obtain the following sample paths
-\begin{figure}
-    \includegraphics[scale=0.33]{Figures/sample_paths_beta_flex_0503.pdf}
-        \includegraphics[scale=0.33]{Figures/sample_paths_beta_flex_0505.pdf}
-
-  \caption{ Sample Paths using Beta transitions LHS: $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$. RHS:  $\theta = 0.5$, $\alpha=0.5$   }
-  %\label{fig:boat1}
-\end{figure}
-
-\end{frame}
-
-\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent parameter }
-We perform a convergence test for speed of reversion parameter $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$.
-We obtain the following convergence result
-\begin{figure}
-    \includegraphics[scale=0.4]{Figures/conv_M_beta_flex_10.pdf}
-    \includegraphics[scale=0.4]{Figures/conv_N_beta_flex_35.pdf}
-  \caption{ Convergence results for Beta transitions with $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$   }
-  %\label{fig:boat1}
-\end{figure}
-
-\end{frame}
-
-%\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }
-%
-%
-%\end{frame}
-%
-%
-%
-%
-%
-%
-%\begin{frame}\frametitle{ Case 4.2: Following deterministic functions - time dependent parameters }
-%
-%
-%
-%\end{frame}
-
-\againframe{guide}
+%\againframe{guide}
 

### 2019-08-28 LaTeX_code/paper/paper.tex
updated tripizoidal

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{color}
\usepackage{mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
\title{ Stochastic Wind Power Forecasting }  % \\  \small{Report}}

\author{ Waleed Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University,  Germany
 \\ \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539) , Villetaneuse , France }

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT

\begin{abstract}

Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price and Operation scheduling of conventional power plant. We propose a data driven model based on parametric Stochastic Differential Equations (SDEs) to captures real-world asymmetric dynamics of wind power forecast errors. The SDE proposed incorporates time derivative tracking of the forecast, time-dependent mean reversion parameter and an improved diffusion term. We are able to simulate future wind power production paths and confidence bands. The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of an information criteria. We apply the model to historical Uruguayan and French wind power production data and various forecasts on the period (2017-2018).

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Reliable wind power generation forecasting is crucial for the following applications [ref]:
\begin{itemize}
\item Allocation of energy reserves such as water levels in dams or oil and gas reserves.
\item Operation scheduling of conventional power plants.
\item Optimization of the price of electricity for different users such as electric utilities, Transmission system operator (TSOs), Electricity Service providers (ESPs), Independent power producers (IPPs), and energy traders.
\item Maintenance planning such as that of power plants components and transmission lines.

\end{itemize}

Different methods have been applied to wind power forecasting. They can be generally categorized as follows: physical models, statistical methods, artificial intelligence methods, persistence models, spatial correlation methods and hybrid approaches. The output of such methods is usually a deterministic forecast. Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles. However, little has been done in terms of producing data driven probabilistic forecasts based on real-world performance of forecasting models. It is crucial to capture actual performance of a forecast as it has been known that a given forecasting technology exhibits different behavior for different wind farms and seasons [ref]. This is due to many factors which forecast are challenged to capture such as the surrounding terrains of the wind farm and the condition of the blades such as icing or dirt. It is known that complex terrains decrease the accuracy of wind power forecasts significantly [ref]. It also has been shown that the performance of forecasts varies from month to month. Thus the performance of wind power forecasts is location and time dependent.

Many approaches have been taken to evaluate the performance of a given forecast. There are two types of errors: level errors and phase errors. The use of mean or median errors in this context may be misleading as wind power forecast errors are asymmetric. This is a natural consequence of wind power being non-negative. This is important as the associated cost to power forecast errors are also asymmetric due to different costs for up and down  power regulations which are determined by the electricity market [ref].

We propose to model wind power forecasts errors using parametric stochastic differential equations (SDEs) whose solution defines a stochastic process. This resultant stochastic process describes the time evolution dynamics of wind power forecast errors while preserving properties such as the correlation structure and asymmetry. Additionally, the model is agnostic of  wind power forecasting technology and serves as a complement to forecasting procedures by providing a data driven probabilistic forecast. Hence, we are able to evaluate wind power forecasts according to their real-world performance and we are able to compare different forecasting technologies.

Previous attempt by M\o ller et al. (M\o ller, Zugno, \& Madsen, 2016)  considered stochastic wind power forecast models based on stochastic differential equations (SDEs). Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion and non-Gaussian approximations. We apply the model to Uruguayan and french wind power forecasts together with historical wind power production data pertaining to the year 2017-2018.

%-------------------------------------------------------------------------
\section{Phenomenological  Model}
We introduce the following phenomenological model. Let $X_t$ be the  wind power generation forecasts stochastic process defined by the  following parameterized stochastic differential equation (SDE),
\begin{equation}
\begin{split}
dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
X_0 & = X_0
\end{split}
\label{main}
\end{equation}

\begin{itemize}
\item $a(\cdot; \bm{\theta}):[0,1] \to \R $  a drift function.
\item $b (\cdot; \bm{\theta} ):[0,1] \to \R$  a  diffusion function.
\item $\bm{\theta}$: a vector of parameters.
\item $W_t$: Standard Wiener random process in $\R$.
\end{itemize}

We would like to have this model closely follow wind power forecasts while ensuring that it is unbiased with respect to the forecast. That is, we would like to have $\E X_t = p_t$ where $p_t$ is a deterministic given wind power forecast.

\subsection{Physical Constrains}

Let $p_t$ be a numerical wind power forecast, which is an input to this approach. Then the model is given by the following It\^{o} stochastic differential equation,
\begin{equation}
\begin{split}
dX_t&= \dot{p} \ dt - \theta_t(X_t - p_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t \quad t > 0 \\
X_0&=x_0
\end{split}
\label{model:derivative_tracking_X}
\end{equation}
We have that the process $X_t$ mean reverts to the wind power forecast $p_t$ and tracks its the time derivative $\dot{p}_t$.  An example such mean reverting model without derivative tracking exhibits consistent lags as shown in Figure (). See section (5) for comparisons.

 We normalize the forecast and production data to installed power capacity. Thus our process must be limited to the range $[0,1]$. To enforce this constraint, we must have drift and diffusion control.
\subsubsection*{Diffusion Control: } The physical constraint to the range $[0,1]$ is respected  by choosing  diffusion coefficient $ b (x; \bm{\theta} )= \sqrt{2 \theta_t \alpha x (1-x)} $ which is zero on the boundaries of $[0,1]$. We also have that $\alpha$ is a path variability constant parameter to be determined.

\subsubsection*{Drift Control: }
Observe that the time derivative term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays a.s.  inside the range $[0,1]$. In other words, the zero drift line defined by $a(X_t; \bm{\theta}) =0$, which an attractor, must be contained inside the range $[0,1]$. Thus, we must have that
\begin{equation}
\frac{- |\dot{p_t}|}{p_t} \leq \theta \leq \frac{|\dot{p}_t|}{1- p_t}
\end{equation}
which is satisfied  by choosing a time-dependent  $\theta_t$ as follows,
\begin{equation}
\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ) \label{theta_t}
\end{equation}

\subsubsection*{Change of Variables:}
In order to avoid differentiation of the forecast $\dot{p}_t$ and simplify, we apply a change of variables $$V_t = X_t - p_t$$ \\
The  model becomes,
\begin{equation}
\begin{split}
dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
V_0 & = v_0
\end{split}\label{VtSDE}
\end{equation}
with $\theta_t$ given by (\ref{theta_t}).

\section{Data}
We apply the model to Uruguayan wind power data and their corresponding wind power forecasts. The wind power actual production data set is recorded on intervals of ten minutes for each wind farm in the country. The associated wind power forecasts are provided by two different entities. Each forecast is provided on an hourly basis and is computed for a 72 hour horizon every few hours. Sample data is shown in Figure ().

\section{Inference and Optimization}

\subsection{Likelihood}
The SDE above defines the stochastic process $V_t$. Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed in intervals of $\Delta_N$. Since $V_t$ defined by the SDE in (\ref{VtSDE}) is Markovian, the likelihood function can be written as product of transition densities.

\begin{equation}
\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}}, \bm{\theta})  \rho (V_{j,0})
\label{likelihood}
\end{equation}

The transition densities can be exactly obtained by solving the following parametric Fokker-Planck equation,

\begin{equation}
\begin{split}
\frac{ \partial f }{\partial t } & (y ,t | x , s, \theta_t, \alpha )= - \frac{\partial}{ \partial y} ( a( y;\dot{p}_t , p_t, \theta_t ) f( y ,t | x , s, \theta_t , \alpha ) ) \\
& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b(y;\theta_t, \alpha  )  f( y ,t | x , s, \theta_t , \alpha )  ) \quad  t < s\\
\end{split}
\end{equation}

The above parametric PDE is computationally prohibitive to be solved for each wind production data point and for all parameter space which is to be optimized. Therefore, we consider approximate likelihood methods.

\subsection{Approximate Likelihood}
Solving for transition densities of the process $V_t$ requires solving the Fokker-Planck equation at every step which is computationally prohibitive. A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints and the asymmetric nature of forecast errors. \\

Therefore, we propose to approximate likelihood using a Beta distribution. As the process $X_t$ and $p_t$ take on values in $[0,1]$, then $V_t$ takes on values in $[-1,1]$. Therefore, we translate and scale the Beta distribution to have compact support on the interval $[-1,1]$.

\subsubsection*{ Moment Matching}
To approximate the transition densities of  the process $V_t$ by a Beta distribution, we match its moments with the shape parameters $\xi_1, \xi_2$ of the Beta distribution on $[-1,1]$.  Then, the shape parameters are given by,
\begin{equation}
\xi_1 = - \frac{(1+\mu_t )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2} \quad \xi_2=  \frac{(\mu_t-1 )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2} \label{param_transformed_beta}
\end{equation}
where $\mu_t = \E[ V_t]$ and $\sigma_t^2= \E[ V^2_t]- \E[ V_t]^2$ and $m_i$ being the i-th moment of the process $V_t$. Using It\^{o}'s formula, the moments  of the  process $V_t$ are iteratively given by,

\begin{equation}
\begin{split}
\frac{d \E[ V^k_t]}{dt} = - k \theta_t \E [ V^k_t] + \frac{k(k-1)}{2} \E [ V^{k-2}_t  b(y;\theta_t, \alpha)]
\end{split}
\end{equation}

with initial conditions, $\E[ V^k_t]= v_{s}^k$ where $t<s$.
\subsection{Optimization}
Let $\ell$ be the natural logarithm  of the likelihood in $(\ref{likelihood})$. Given the data set $V^{M,N}$, we  optimize the the log-likelihood $\ell$  using L-BFGS algorithm  for the optimal parameters $\theta_0^* , \alpha^*$ as follows,
\begin{equation}
(\theta_0^* , \alpha^* ) = \arg \underset{\theta_0, \alpha>0}{\min} - \ell( \theta_0,  \alpha | V^{M,N} )
\end{equation}
The contours of the  log-likelihood can be seen in Figure (\ref{contour}). To further inspect the log-likelihood at the point of optimality $(\theta_0^* , \alpha^* )$, we check the ellipse defined by the  Hessian of the log-likelihood at the point of optimality.  We observe that the ellipse shrinks at a fast rate as shown in Figure (\ref{ellipse_drawing}). We see that  the convergence rate of the parameters $\theta_0$ and $\alpha$ is slightly faster than the expected rate of $1/\sqrt{M}$. This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample. We note that the uncertainty in determining the parameter $\alpha$  is much higher than  in $\theta_0$.

\section{Model Comparison}
We compare the following candidate models to find the best-fit that maximizes the retained information,
\begin{itemize}
  \item Model 0: This model is the most basic model without derivative tracking.
  \begin{equation}
  \begin{split}
  dX_t &=  - \theta_0 (p_t-X_t) \  dt + \sqrt{2 \theta \alpha X_t (1-X_t)} \  dW_t  \\ %\quad t > 0
  X_0 & = x_0
\end{split}\label{M0}
  \end{equation}
  with $\theta_t= \theta_0 $.

  \item Model 1: This model features derivative tracking, i.e. it's equivalent to $\ref{model:derivative_tracking_X}$ with a diffusion term that is forecast dependent by including the term $p_t(1-p_t)$.
  \begin{equation}
  \begin{split}
  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha p_t(1-p_t)(V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
  V_0 & = v_0
  \end{split}\label{M2}
  \end{equation}
  with $\theta_t$ given by (\ref{theta_t}).

  \item Model 2: This model features derivative tracking, i.e. it's equivalent to $\ref{model:derivative_tracking_X}$
\begin{equation}
  \begin{split}
  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
  V_0 & = v_0
  \end{split}\label{M2}
  \end{equation}
  with $\theta_t$ given by (\ref{theta_t}).
\end{itemize}

\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Model   &  parameters $(\theta_0, \alpha)$   & AIC & BIC \\ \hline
Model 0 &  (,)   &     &     \\ \hline
Model 1 &   (,)  &     &      \\ \hline
Model 2 &   (,)  &     &       \\ \hline
\end{tabular}
\caption{We compare the different models based on information criterion. <discuss results> }
\label{tab:model_comparison}
\end{table}

\section{Forecast Provider Comparison}
We compare forecasts from two different companies for the same period.
\begin{table}[]
\centering
\begin{tabular}{|c|l|c|c|}
\hline
Forecast Provider & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
Provider A        &                                 &     &     \\ \hline
Provider B        &                                 &     &     \\ \hline
\end{tabular}
\caption{<discuss results>}
\label{tab:forcast_comparison}
\end{table}
In Figure ()-(), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.

 \begin{table}[]
 \centering
 \begin{tabular}{|c|l|c|c|}
 \hline
 Model                                                                              & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
 \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}              &                                 &     &     \\ \hline
 \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &                                 &     &     \\ \hline
 \end{tabular}
 \caption{<discuss results>}
 \label{tab:freq_comparison}
 \end{table}

\section{Model on Disaggregated Data}
We apply Model 2 to disaggregated wind power production data and forecasts. The data is available in this case on an hourly basis. Results are shown in Table (\ref{tab:disagregated_data}).

\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Forecast Provider A & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
Wind Farm 1         &                                 &     &     \\ \hline
Wind Farm 2         &                                 &     &     \\ \hline
Wind Farm 3         &                                 &     &     \\ \hline
Wind Farm 4         &                                 &     &     \\ \hline
Wind Farm 5         &                                 &     &     \\ \hline
Wind Farm 6         &                                 &     &     \\ \hline
\end{tabular}
\caption{<discuss results>}
\label{tab:disagregated_data}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Forecast Provider B & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
Wind Farm 1         &                                 &     &     \\ \hline
Wind Farm 2         &                                 &     &     \\ \hline
Wind Farm 3         &                                 &     &     \\ \hline
Wind Farm 4         &                                 &     &     \\ \hline
Wind Farm 5         &                                 &     &     \\ \hline
Wind Farm 6         &                                 &     &     \\ \hline
\end{tabular}
\caption{\textless{}discuss results\textgreater{}}
\label{tab:disagregated_data_B}
\end{table}

\section{Results}
 We are able to obtain the parameters based on the complete data sets. Using the different models variations, we are able to simulate wind power production given a forecast. We see in figures ()-()
five possible wind power production paths for each model.\\

In Figures ()-(), we show point-wise empirical confidence bands for the different models.

\section{Conclusions}

We have proposed a method to produce stochastic wind power forecasts based on parametric SDEs. This method is agnostic of the wind power forecasting technology. Using this method, we were able to simulate future wind power production paths and obtain confidence bands. We conclude that Model 2 is a best-fit model. It features time-derivative tracking of the forecast, time-dependent mean reversion parameter, and a more natural diffusion term. Moreover, the model preserves the asymmetry of wind power forecast errors and their correlation structure.

We were also able to compare two different forecast providers with respect to their real-world performance on the aggregated data set and on specific wind farm sites. Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.

%\section*{Acknowledgement}

\section*{References}
\begin{flushleft}
- M\o ller, J. K., Zugno, M., \& Madsen, H. (2016). Probabilistic Forecasts of Wind Power Generation by Stochastic Differential Equation Models. Journal of Forecasting, 35(3), 189-205. doi:10.1002/for.2367 \linebreak
- G. Giebel, R. Brownsword, G. Kariniotakis, M. Denhard, and C. Draxl, The State-Of-The-Art in Short-Term Prediction of Wind Power: A Literature Overview, 2nd edition. ANEMOS.plus, 2011, project funded by the European Commission under the 6th Framework Program, Priority 6.1: Sustainable Energy Systems.\linebreak
- Ravn, H. F. (2006). Short term wind power prognosis with different success criteria. 2006 International Conference on Probabilistic Methods Applied to Power Systems. doi:10.1109/pmaps.2006.360291 \linebreak
- Chang, W. (2014). A Literature Review of Wind Forecasting Methods. Journal of Power and Energy Engineering, 02(04), 161-168. doi:10.4236/jpee.2014.24023\linebreak
- Elkantassi, S., Kalligiannaki, E., \& Tempone, R. (2017). Inference And Sensitivity In Stochastic Wind Power Forecast Models. Proceedings of the 2nd International Conference on Uncertainty Quantification in Computational Sciences and Engineering (UNCECOMP 2017). doi:10.7712/120217.5377.16899
\end{flushleft}

% {\small
% \bibliographystyle{ieee}
% \bibliography{egbib}
% }

\end{document}

% \begin{figure}[t]
% \begin{center}
% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%    \includegraphics[width=0.8\linewidth]{Forecast_data_68.pdf}
%     \includegraphics[width=0.8\linewidth]{Forecast_data_82.pdf}
% \end{center}
%    \caption{Examples of wind power generation from the data set along with the wind power generation forecast.}
% \label{fig:long}
% \label{fig:onecol}
% \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{figure}[t]
% \begin{center}
% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%    \includegraphics[width=0.6\linewidth]{ellipse1193_samples_dN=14e-02.pdf}
%     \includegraphics[width=0.6\linewidth]{ellipse_conv_samples_dN=14e-02.pdf}
% \end{center}
%    \caption{Left:Shrinkage of the ellipse determined by the Hessian matrix of the log-likelihood around the point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ (Axis are not in natural scale, arrows only to  eignevector direction). Right: Convergence of the major and semi-axis of the ellipse  of the Hessian of the log-likelihood at the point optimality $(\theta_0^*, \alpha^*)\approx (8,1)$. Note that it is slightly faster than the expected rate of $1/\sqrt{M}$. This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample.}
% \label{ellipse_drawing}
% \end{figure}

%  \begin{figure}[t]
% \begin{center}
% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%    \includegraphics[width=0.9\linewidth]{ISO_100_samples_dN=14e-02.pdf}
%    %\includegraphics[width=0.5\linewidth]{ISO_500_samples_dN=14e-02.pdf}
%    %\includegraphics[width=0.5\linewidth]{ISO_1193_samples_dN=14e-02.pdf}
% \end{center}
%    \caption{Contour plot of the log-likelihood with only 100 sample paths, point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ indicated by the  black dot.}
% \label{contour}
% \end{figure}

%%%%%%%%%%%%%%%%%%%%%%

% \begin{figure}[t]
% \begin{center}
% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%    \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_31.pdf} %667
%    \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_437.pdf}
%    \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_82.pdf}
%
% \end{center}
%    \caption{ Examples of confidence bands obtained for the full 72 hour forecasts.We can see that the model captures the fluctuations in the actual production with non-trivial and asymmetric confidence intervals.}
% \label{fig:72hr}
% \end{figure}
%
% \begin{figure}[t]
% \begin{center}
% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%    \includegraphics[width=0.8\linewidth]{6hr_forecast_CI_75.pdf}  %569
%    \includegraphics[width=0.8\linewidth]{6hr_forecast_CI_59.pdf}
%    %\includegraphics[width=0.9\linewidth]{6hr_forecast_CI_68.pdf}
% \end{center}
%    \caption{ Examples of confidence bands obtained for the first 6 hours of the forecasts. This is important as this specific forecasting company computes a new forecast every 6 hours for reliability.}
% \label{fig:6hr}
% \end{figure}

%  \begin{figure}[t]
% \begin{center}
% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%    \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_623.pdf}  %569
% \end{center}
%    \caption{ Examples of omitted data which corresponds to production control and manual energy management decisions. In this example,  wind power production was repeatedly curtailed at around 2 AM which is a period of low power demand. Automatic detection of such scenarios is to be incorporated in future works.}
% \label{fig:6hr}
% \end{figure}

%We obtain the modified Beta distribution,
%
%\begin{equation}
%\begin{split}
%f_Y(y; \alpha , \beta )&= f_X(g^{-1}(y) ) \Big| \frac{\partial g^{-1}(y)}{\partial y }  \Big| \\
%&= \frac{1}{B(\alpha, \beta) (b-a)} \Big(\frac{a-y}{b-a}\Big)^{\alpha -1}\Big(1-\frac{a-y}{b-a} \Big)^{\beta -1} \label{modified_Beta}
%\end{split}
%\end{equation}
%where $B(\cdot,\cdot)$ is the Beta function. Also, we have that
%\begin{equation}
%\E[Y]= a + (b-a) \frac{\alpha}{\alpha + \beta}
%\end{equation}
%\begin{equation}
%\V[Y]= (b-a)^2 \frac{\alpha \beta}{(\alpha + \beta)^2 (\alpha + \beta + 1)}
%\end{equation}

### 2019-08-28 LaTeX_code/paper/paper_v3.tex
updated tripizoidal

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{color}
\usepackage{mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
\title{Paper Plan  \\ "Stochastic Wind Power Forecasting"  }  % \\  \small{Report}}

\author{ Waleed Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University,  Germany
 \\ \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539) , Villetaneuse , France }

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT

\begin{abstract}

\begin{itemize}
    \item Briefly say the motivation and applications
    \item What is novel here and why its better.
    \item summarize the technique
    \item mention the data used.
    \item mention concluding results.
\end{itemize}

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

\begin{itemize}
    \item Importance and interested parties
    \item Literature review on current forecasting practices
    \item shortcomings of current deterministic and probabilistic forecasts.
    \item Mention our ability of simulating production and why it's important.
    \item Consequence of not taking into account the real world performance of the forecasts. And present proofs where such forecasts fail such as in complex terrains.
    \item Consequences of not taking into account skewness of the errors this includes asymmetric cost for up and down-regulation of power.
    \item Emphasize that it works independent of the forecasting technology. Thus we are able to compare different forecasts based on their real world performance.
    \item Mention past contributions to the topic and show what is novel in this approach.
    \item Mention the data used in this study.
\end{itemize}

%-------------------------------------------------------------------------
\section{Phenomenological  Model}

\begin{itemize}
    \item Introduce the intuitive main model in $X$ in a general setting and what class it belongs to.
    \item motivate such choice by requiring mean reversion and boundedness of the process.
    \item Introduce derivative tracking and explain why it's needed.
    \item State the associated Fokker-Plank
    \item State the iterated expression for all the moments.
\end{itemize}

\subsection{Physical Constrains}

\begin{itemize}
    \item Introduce why we have the physical constrains.
    \item Discuss the normalization between $[0,1]$ and why its needed
\end{itemize}

\begin{itemize}
    \item Motivate the choice of diffusion and its behavior at the boundaries.
    \item Note that this diffusion is state-dependent and why this is a challenge.
\end{itemize}

\begin{itemize}
    \item Motivate the time-dependent  $\theta_t$
\end{itemize}

\begin{itemize}
    \item combine both drift and diffusion control
    \item Do a Feller test to show that the process stays almost surely in $[0,1]$
    \item Show that if we start with zero error it will stay that way indefinitely.

\end{itemize}

\begin{itemize}
    \item Motivate the change of variables to avoid numerical differentiation.
\end{itemize}

\subsubsection{State Independent-Models}

\begin{itemize}
    \item say that we have two main approaches based on moment matching:
    \begin{itemize}
        \item state dependent diffusion and use either a  Beta distribution as a proxy or a maximum entropy distribution.
        \item state-independent diffusion and use the gaussian as a proxy either by linearizing the SDE or its moments equations.
    \end{itemize}
    \item introduce Lamperti transformation on $V$, write the new SDE and its moments.
    \item give explicit expression to compute the moments as a proposition.
    \item Say that We may infer in either spaces, the original space or Lamperti space.
    \item Discuss why we approximate the SDE directly by linearization or why to approximate its moments instead.

\end{itemize}

\section{Data}

\begin{itemize}
    \item introduce the data sets: observations, forecast, frequency.
    \item Show histograms exhibiting the skewness.
    \item Show the correction to the skewness after Lamperti.
    \item conclude that the diffusion model $\sqrt{x(1-x)}$ is correct as the Lamperti shows.
    \item Discuss cleaning the data set from instances of curtailing.
    \item Example plot of forecast and real production from the data set.
\end{itemize}

\section{Parameter Estimation}
\begin{itemize}
    \item Write the likelihood for one path first using markovianity.
    \item Justify the product of paths by introducing observation error to the recoded production observations. Write that it's independent and small Gaussian noise.
    \item Mention that the Fokker-Plank written in the model section is computationally formidable for parameter estimation.
    \item Mention the two approaches: State dependent diffusion and state-independent diffusion SDE.
    \item discuss that state dependent diffusion SDE approach assumes a proxy distribution either a Beta or a maximum entropy distribution. That this is the underlaying assumption and reason it based on the skewness and boundedness of the data explained in the above section.
    \item discuss that the state-independent approach requires either linearizing the SDE or its moments equations. Justify it by saying that the time intervals are small and such approximations are reasonable.
\end{itemize}

\subsection{Initial Parameter Estimation}

\begin{itemize}
    \item Introduce why this is important to cross check and it may be possible to use it as an estimating procedure for high-frequency data.
    \item mention that it is important to help initialize the optimization procedure and save on computations.
    \item estimate the product of the parameters using the brackets.
    \item estimate the mean reversion parameter using least squares.
\end{itemize}

Then,

\begin{itemize}
    \item State the objective function and the optimization technique
\end{itemize}

\section{Results}
For each model and technique we will state the following as a results:
\begin{itemize}
    \item Results from optimization
    \begin{itemize}
        \item Convergence of the ellipse around the optimal point.
        \item confidence intervals on obtained the parameters
        \item AIC and BIC information criteria.
    \end{itemize}
    \item Plots of forecast simulations.
    \item Plots of forecast confidence intervals.
\end{itemize}

\subsection{ Comparison Parameter Estimation Technique}
State the results above for the following models:
\begin{itemize}
    \item  Moment matching with a Beta proxy.
    \item Approximate Moment matching  with a Gaussian proxy in Lamperti space.
    \item Moments matching of a Linearized version of the SDE in the Lamperti space.
\end{itemize}

\section{Model Comparison}
Choose the best candidate from the different Parameter Estimation Techniques to compare the following models:
\begin{itemize}
  \item Model 0: This model is the most basic model without derivative tracking.

  \item Model 1: This model features derivative tracking with a diffusion term that is forecast dependent by including the term $p_t(1-p_t)$.

  \item Model 2:  Model features derivative tracking and excluding the term $p_t(1-p_t)$
\end{itemize}

\section{Forecast Provider Comparison}
Choose the best technique form the "Comparison Parameter Estimation Technique" section. Then choose the best candidate from the "Model Comparison" section and apply it on forecasts from two different forecasting companies. State results as mentioned before.

\section{Model on Disaggregated Data}
Choose the best forecasting company, model, technique and  apply it on the disaggregated data. State results as before for each wind farm.

\section{Extra: Optimal forecasting update interval}
\begin{itemize}
    \item We have hourly updated forecast from France. Therefore we can choose the best series of predictions (the first point of each update which is at an hourly frequency).
    \item  Allows us to evaluate the uncertainty for the "next hour" wind power production forecasts.
    \item redo the same evaluation on series made up of updates every 4 hours and another every 6 hours and so on.
    \item this allows us to find the optimal update frequency for different operational uses and clients.
    \item we are able to classify forecasts according to which forecast horizon they are better at. Say forecaster A technology is better at forecasting the next 12 hours and must be recomputed at that frequency. However, forecaster B is better at forecasting the next hour and must be recomputed hourly.
\end{itemize}

\section{Conclusions}

\begin{itemize}
    \item state our achievements
    \item summarize results briefly.
    \item recap of the abstract.
    \item close with a remark for the future
\end{itemize}

\section*{Acknowledgement}

\section*{References}

\end{document}

### 2019-08-28 LaTeX_code/paper/paper_v4.tex
updated tripizoidal

--- 2019-08-28 LaTeX_code/paper/paper_v3.tex
@@
 %%%%%%%%% TITLE
-\title{Paper Plan  \\ "Stochastic Wind Power Forecasting"  }  % \\  \small{Report}}
+\title{Paper Outline  \\ "Stochastic Wind Power Forecasting"  }  % \\  \small{Report}}
 
@@
     \item What is novel here and why its better.
+    \begin{itemize}
+        \item Fast
+        \item accurate
+        \item computationally efficient
+    \end{itemize}
     \item summarize the technique
+    \begin{itemize}
+        \item Indirect inference
+        \item Moment based approximation of the transition densities
+    \end{itemize}
     \item mention the data used.
+    \begin{itemize}
+        \item Uruguay
+        \item frequency
+        \item Period
+    \end{itemize}
     \item mention concluding results.
@@
     \item Mention the data used in this study.
+    \item Summary of the structure of the paper, describe the flow and what each section contains.
 \end{itemize}
@@
     \item Introduce why we have the physical constrains.
+    \item We want to fulfill the physical constraints with the least number of parameters and assumptions (parsimony).
     \item Discuss the normalization between $[0,1]$ and why its needed
@@
 \begin{itemize}
-    \item combine both drift and diffusion control
+    \item write the model including the drift and diffusion.
     \item Do a Feller test to show that the process stays almost surely in $[0,1]$
-    \item Show that if we start with zero error it will stay that way indefinitely.
+    \item Show that if we start with zero error in the mean it will stay that way indefinitely. Show this using Ito.
 
@@
 \begin{itemize}
-    \item say that we have two main approaches based on moment matching:
-    \begin{itemize}
-        \item state dependent diffusion and use either a  Beta distribution as a proxy or a maximum entropy distribution.
-        \item state-independent diffusion and use the gaussian as a proxy either by linearizing the SDE or its moments equations.
-    \end{itemize}
+    \item note that the state-independent diffusion model is favorable to utilize probability theory.
     \item introduce Lamperti transformation on $V$, write the new SDE and its moments.
     \item give explicit expression to compute the moments as a proposition.
+    \item Remark that in the lamperti space:
+    \begin{itemize}
+        \item no longer able to obtain the exact moment equations as we had in the original space.
+        \item inexactness of the moment equations introduces a bias which we didn't have in the original space.
+    \end{itemize}
+    \item We can work in either the original space (state dependent diffusion) or the Lamperti space (state-independent diffusion).
+    \begin{itemize}
+        \item In the original space we use either a  Beta distribution as a proxy or a maximum entropy distribution.
+        \item In the Lamperti space we use the gaussian as a proxy either by linearizing the SDE or its moments equations.
+    \end{itemize}
     \item Say that We may infer in either spaces, the original space or Lamperti space.
     \item Discuss why we approximate the SDE directly by linearization or why to approximate its moments instead.
+    \item Ability to estimate parameters using the brackets and least squares when high-frequency data is available.
 
@@
     \item Mention that the Fokker-Plank written in the model section is computationally formidable for parameter estimation.
-    \item Mention the two approaches: State dependent diffusion and state-independent diffusion SDE.
-    \item discuss that state dependent diffusion SDE approach assumes a proxy distribution either a Beta or a maximum entropy distribution.
+
+    \item Mention the two spaces: the original space and Lamperti space.
+
+    \item We assumes a proxy distribution either a Beta or a maximum entropy distribution.
 That this is the underlaying assumption and reason it based on the skewness and boundedness of the data explained in the above section.
-    \item discuss that the state-independent approach requires either linearizing the SDE or its moments equations.
-Justify it by saying that the time intervals are small and such approximations are reasonable.
+    \item In Lamperti space discuss that we either linearize the SDE or its moments equations. Justify it by saying that the time intervals are small and such approximations are reasonable.
 \end{itemize}
@@
         \item confidence intervals on obtained the parameters
-        \item AIC and BIC information criteria.
+        \item AIC and BIC information criteria for model comparison.
     \end{itemize}
+    \item Results from MCMC to verify and demonstrate that we have exhaustively searched the space. This is important as we are not able to guarantee the convexity of our objective function.
     \item Plots of forecast simulations.
@@
 
+\begin{itemize}
+    \item Assigning weights for making forecast ensembles.
+\end{itemize}
+
 \section{Model on Disaggregated Data}
 Choose the best forecasting company, model, technique and  apply it on the disaggregated data. State results as before for each wind farm.
-
+\begin{itemize}
+    \item We study it as a network and how it behaves for power transport and load management.
+This means that we cannot assume that the nodes are independent, but we need to capture the interplay between them with a minimal number of parameters to tune.
+    \item Must incorporate correlation between wind farms in the noise $dW_t$.
+\end{itemize}
 \section{Extra: Optimal forecasting update interval}

### 2019-08-28 LaTeX_code/poster/poster.tex
p(1-p) removed,added path simulator,path length feature, non-tech poster
updated tripizoidal

--- 2019-06-17 LaTeX_code/poster/latex/poster.tex
@@
 
+\section*{Data}
+
+To capture real-world performance of  wind power forecasts, our model incorporates historical wind power production data along with their corresponding forecasts.\\
+
+We apply the model to Uruguayan wind power generation data and their corresponding numerical wind power production forecasts. \\
+
+The wind power generation data set contains hourly samples of aggregated wind power production throughout the country.
+Each sample path contains 72 hourly observations and we have a total of 1217 sample paths spanning the year 2016 to 2017 (87,624 data points).
+\\
+
+The numerical wind power generation forecast set contains  1217 forecasts of the wind power generation  corresponding to the actual  wind power generation data set mentioned above.
+
+\begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   %\includegraphics[width=0.8\linewidth]{Forecast_data_68.pdf}
+    \includegraphics[width=0.8\linewidth]{Forecast_data_82.pdf}
+\end{center}
+   \caption{Examples of wind power generation from the data set along with the wind power generation forecast.}
+\label{fig:long}
+\label{fig:onecol}
+\end{figure}
+
 \section*{Model}
@@
 \begin{split}
-dX_t&= \dot{p} \ dt + (\theta_t -X_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t \quad t > 0 \\
+dX_t&= \dot{p} \ dt - \theta_t( X_t- p_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t \quad t > 0 \\
 X_0&=x_0
@@
 To enforce this constraint, we must have drift and diffusion control.
-\subsubsection*{Diffusion Control: } The physical constraint is respected  by choosing  diffusion coefficient $ b (x; \bm{\theta} )= \sqrt{2 \theta_t \alpha p_t(1-p_t) x (1-x)} $ that is zero on the boundaries of $[0,1]$.
-\subsubsection*{Drift Control: }
+\subsubsection*{Diffusion: } The physical constraint is respected  by choosing  diffusion coefficient $ b (x; \bm{\theta} )= \sqrt{2 \theta_t \alpha x (1-x)} $ that is zero on the boundaries of $[0,1]$.
+\subsubsection*{Drift: }
 $X_t$ remains in $[0,1]$ a.s. by choosing $\theta_t$ as follows,
@@
 \subsubsection*{Change of Variables:}
-In order to avoid differentiation of the forecast $\dot{p}_t$ and simplify, we apply a change of variables $$V_t = X_t - p_t$$  \\
-Then  model becomes,
+In order to avoid differentiation of the forecast $\dot{p}_t$ and simplify, we apply a change of variables $V_t = X_t - p_t$. Then  model becomes,
 \begin{equation}
 \begin{split}
-dV_t &=  - \theta V_t \  dt + \sqrt{2 \theta \alpha p_t(1-p_t) (V_t +p_t ) (1-V_t-p_t)} \  dW_t \quad t > 0 \\
+dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t \quad t > 0 \\
 V_0 & = v_0
@@
 
-\section*{Data}
-
-We apply the model to Uruguayan wind power generation data and their corresponding numerical wind power production forecast. \\
-
-The wind power generation data set contains hourly samples of aggregated wind power production throughout the country.
-Each sample path contains 72 hourly observations and we have a total of 1217 sample paths spanning the year 2016 to 2017 (87,624 data points).
-\\
-
-The numerical wind power generation forecast set contains  1217 forecasts of the wind power generation  corresponding to the actual  wind power generation data set mentioned above.
-
-\begin{figure}[t]
-\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.8\linewidth]{Forecast_data_68.pdf}
-    \includegraphics[width=0.8\linewidth]{Forecast_data_82.pdf}
-\end{center}
-   \caption{Examples of wind power generation from the data set along with the wind power generation forecast.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
 \section*{Methodology}
@@
 \subsection*{ Optimization  }
-\begin{itemize}
-%\item The log-likelihood is convex in the  parameters $(\alpha, \theta_t )$ on the positive quadrant.
-\item We optimize using L-BFGS algorithm constrained to the positive quadrant.
-\end{itemize}
-The ellipse defined by the  Hessian of the log-likelihood shrinks at a fast rate as shown in Figure (\ref{ellipse_drawing}). The contours of the  log-likelihood can be seen in Figure (\ref{contour}).
-
-\begin{figure}[t]
-\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.6\linewidth]{ellipse1193_samples_dN=14e-02.pdf}
-    \includegraphics[width=0.6\linewidth]{ellipse_conv_samples_dN=14e-02.pdf}
-\end{center}
-   \caption{Left:Shrinkage of the ellipse determined by the Hessian matrix of the log-likelihood around the point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ (Axis are not in natural scale, arrows only to  eignevector direction).
-Right: Convergence of the major and semi-axis of the ellipse  of the Hessian of the log-likelihood at the point optimality $(\theta_0^*, \alpha^*)\approx (8,1)$.
-Note that it is slightly faster than the expected rate of $1/\sqrt{M}$.
-This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample.}
-\label{ellipse_drawing}
-\end{figure}
-
  \begin{figure}[t]
@@
 \end{figure}
-
-\section*{Results}
- We are able to obtain the parameters based on the complete data sets mentioned earlier. The parameters are given by $(\theta^*, \alpha^*)\approx (8,1)$.
-
-%We can also see in Figure() that the region surrounding the optimal parameters becomes more defined as we add more sample paths.
-
-In Figure (\ref{fig:72hr}) and (\ref{fig:6hr}), we simulate sample forecast errors using the optimal parameters  $(\theta_0^*, \alpha^*)\approx (8,1)$ and obtain the associated confidence bands empirically using 1000 sample paths for each forecast.
-%Note that the confidence bands obtained are non-trivial and reflect the complexity of the uncertainties in numerical wind power generation forecasts.
+\begin{itemize}
+%\item The log-likelihood is convex in the  parameters $(\alpha, \theta_t )$ on the positive quadrant.
+\item We optimize using L-BFGS algorithm constrained to the positive quadrant.
+\end{itemize}
+The ellipse defined by the  Hessian of the log-likelihood shrinks at a fast rate as shown in Figure (\ref{ellipse_drawing}). The contours of the  log-likelihood can be seen in Figure (\ref{contour}).
 
@@
 %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_31.pdf} %667
-   \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_437.pdf}
-   \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_82.pdf}
+    \includegraphics[width=0.6\linewidth]{ellipse_conv_samples_dN=14e-02.pdf}
+   \includegraphics[width=0.6\linewidth]{ellipse1193_samples_dN=14e-02.pdf}
+\end{center}
+   \caption{Left:Shrinkage of the ellipse determined by the Hessian matrix of the log-likelihood around the point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ (Axis are not in natural scale, arrows only to  eignevector direction).
+Right: Convergence of the major and semi-axis of the ellipse  of the Hessian of the log-likelihood at the point optimality $(\theta_0^*, \alpha^*)\approx (8,1)$.
+Note that it is slightly faster than the expected rate of $1/\sqrt{M}$.
+This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample.}
+\label{ellipse_drawing}
+\end{figure}
+
+\section*{Results}
+In the following figures , we simulate sample wind power production forecasts using the optimal parameters  $(\theta_0^*, \alpha^*)\approx (8,1)$ and obtain the associated confidence bands empirically using 1000 sample paths for each forecast.
+
+\begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=0.8\linewidth]{simulated/12hr/1124.pdf}
+   \includegraphics[width=0.8\linewidth]{simulated/24hr/19.pdf}  %569
+   %\includegraphics[width=1\linewidth]{simulated/24hr/1099.pdf}
+   %\includegraphics[width=0.9\linewidth]{6hr_forecast_CI_68.pdf}
+\end{center}
+   \caption{ Examples of simulated paths of wind power production for the next 12 and 24 hours.}
+\label{simulated_24hr}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+  \includegraphics[width=0.8\linewidth]{confidence_intervals/24hr/31.pdf}
+  \includegraphics[width=0.8\linewidth]{confidence_intervals/24hr/820.pdf}
+  %\includegraphics[width=1\linewidth]{confidence_intervals/24hr/82.pdf}
 
 \end{center}
-   \caption{ Examples of confidence bands obtained for the full 72 hour forecasts.We can see that the model captures the fluctuations in the actual production with non-trivial and asymmetric confidence intervals.}
+  \caption{ Examples of confidence bands obtained for 24 hour forecasts.
+We can see that the model captures the fluctuations in the actual production with non-trivial and asymmetric confidence intervals.}
 \label{fig:72hr}
@@
 %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.8\linewidth]{6hr_forecast_CI_75.pdf}  %569
-   \includegraphics[width=0.8\linewidth]{6hr_forecast_CI_59.pdf}
+  \includegraphics[width=0.8\linewidth]{confidence_intervals/12hr/75.pdf}
+  \includegraphics[width=0.8\linewidth]{confidence_intervals/12hr/148.pdf}
   %\includegraphics[width=0.9\linewidth]{6hr_forecast_CI_68.pdf}
 \end{center}
-   \caption{ Examples of confidence bands obtained for the first 6 hours of the forecasts.
-This is important as this specific forecasting company computes a new forecast every 6 hours for reliability.}
+  \caption{ Examples of confidence bands obtained for the first 12 hours of the forecasts. Note that this forecasting company computes a new forecast every 6-9 hours for reliability.}
 \label{fig:6hr}
@@
 \section*{Conclusions}
-In this project, we have proposed a model based on SDE's to quantify uncertainties in wind power generation forecasts. It has the following advantages:
+In this project, we have proposed a model based on parametric Stochastic Differential Equations and advanced inference to quantify uncertainties in wind power generation forecasts.
+It has the following advantages:
 \begin{itemize}
-\item  Represents and quantifies  uncertainty in wind power forecasts.
+\item  Represents and quantifies uncertainty in wind power forecasts accordingly to their real-world performance.
+\item Ability to simulate paths of wind power production.
 \item It is forecast technology agnostic.
@@
 
-\section*{References}
-\begin{flushleft}
-[1] {Elkantassi, S., Kalligiannaki, E., \& Tempone, R.
+% \section*{References}
+% \begin{flushleft}
+% [1] {Elkantassi, S., Kalligiannaki, E., \& Tempone, R.
 (2017).
@@
 doi:10.7712/120217.5377.16899}
-\end{flushleft}
+% \end{flushleft}
 

### 2019-08-28 python_code/data_cleansing.py

@@ -1,0 +1,95 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+from scipy import interpolate
+import datetime as dt
+import pandas as pd
+import os
+##############
+#constants
+##############
+
+# %%
+# new functions to be added
+
+#function to convert np.datetime64 to unix time, regardless of the units
+def get_unixtime(dt64):
+    return dt64.astype('datetime64[s]').astype('int')
+
+#function: returns datetime64 object from a unix timestamp in seconds
+def get_datetime64(time_stamp):
+    return np.datetime64(int(time_stamp),'s')
+get_datetime64=np.vectorize(get_datetime64)
+
+#this function splits forecast paths into equal chunks as requested
+def split_data(array_in,path_length,axis=1):
+    number_paths=array_in.shape[1]//path_length
+    if isinstance(number_paths, int):
+        temp=np.split(array_in,number_paths, axis=axis)
+        out=np.stack(temp, axis=0)
+    else:
+        raise ValueError('non-integer divisions of forecasts')
+    return(out)
+
+#this function get the shape of each array in a list
+def get_list_array_sizes(list):
+    out=[];
+    for i in range(0,len(list)):
+        out.append(list[i].shape)
+    return(out)
+
+# depreciated, functionality included in func: remove_partial_observations
+#this function filters paths with observations less than minimuim
+#WARNING: Index order may change !!! modifty it to fill with np.nan
+def remove_partial_observations(list, min_threshold_observations ):
+    temp = get_list_array_sizes(list)
+    temp1,temp2=zip(*temp) #temp1 is selector (datetime, data), temp2 is
+    #number  of observations
+    complete_observations=[list[i] for i,v in enumerate(temp2) \
+     if v >= min_threshold_observations]
+    return(complete_observations)
+
+#match data to forecast: input forecast(paths,2 ,72), production is time stamp and production
+def match_data_to_forecast(forecast, production, min_threshold_observations):
+    observ_path=[] #=np.zeros((forecast.shape[0]))
+    for j in range(0,forecast.shape[0]): #forecast.shape[0]
+        path_start=forecast[j,0,0];
+        path_end=forecast[j,0,71]
+        observation_index=np.where(np.logical_and(path_start<=production[0,:], production[0,:]<=path_end  ))
[…]

### 2019-08-28 python_code/likelihood_explorer.py

@@ -1,7 +1,7 @@
 
 import os
 os.chdir('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code')
-from Base import *
+from Base_plus import *
 #from multi_path_base import model_modified_drift
 forecast_with_data=np.load('data/forecast_with_data.npy')
 forecast_data_inter=data_check_interpolate(forecast_with_data=forecast_with_data)
@@ -11,27 +11,31 @@ script_name='likelihood_explorer'
 current_plotting_dir='data/'+ script_name+'_' +current_time
 os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
 
-N=forecast_data_inter.shape[2]
-M= 100    #forecast_data_inter.shape[1]
+N=forecast_data_inter.shape[2]-1
+M= 100 #forecast_data_inter.shape[1]
 dt=1
 dN=1/N
-
+dN
 disct_temp = disct(N,dt,M)
 p=forecast_data_inter[0,:,:]
-V= forecast_data_inter[1,:,:] -forecast_data_inter[0,:,:]
+V= forecast_data_inter[1,:,:]-forecast_data_inter[0,:,:]
 
-forecast_data_inter.shape
+N
+dN
+
 this_model=model_modified_drift(disct_temp,V, forecast= p)
 
-theta_array=np.linspace(1, 100, 30) #np.linspace(1, 30, 30)
-alpha_array=np.linspace(0.001, 0.5, 30) #np.linspace(0.1, 3, 30)
+theta_array=np.linspace(1, 100, 50)
+alpha_array=np.linspace(0.001, 0.15, 50)
 
 np.save(current_plotting_dir+'/num_paths', M)
 np.save(current_plotting_dir+'/interpolation_points', N)
+
+
 likelihood_evaluater(theta_array=theta_array,\
     alpha_array=alpha_array,\
-    this_model=this_model,path_dir=current_plotting_dir )
+    this_model=this_model,inference="beta_likelihood" , path_dir=current_plotting_dir )
 print(current_plotting_dir)
 
-this_model.likelihood(np.array((60,0.001)))
-this_model.likelihood(np.array((60,0.1)))
+#this_model.likelihood(np.array((10,0.11)))
+#this_model.likelihood(np.array((60,0.1)))

### 2019-08-28 python_code/skew_test.py

@@ -1,0 +1,275 @@
+import os
+os.chdir('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code')
+from Base import *
+from scipy.stats import moment,skew,probplot, norm
+forecast_with_data=np.load('data/forecast_with_data.npy')
+forecast_data_inter=data_check_interpolate(forecast_with_data=forecast_with_data)
+
+
+# %%
+def plot_QQ(list_data,labels, colors=['r','k','y', 'm', 'g']):
+    plt.clf()
+    fig = plt.figure()
+    for i in range(0,len(list_data)):
+        x,y=probplot(list_data[i])[0]
+        plt.plot(x,y, 'o'+ colors[i], label=labels[i] )
+        plt.plot(np.unique(x), np.poly1d(np.polyfit(x, y, 1))(np.unique(x)), colors[i])
+        plt.xlabel('Theoretical quantiles', fontsize=18)
+        plt.ylabel('Ordered Values', fontsize=16)
+        plt.legend()
+    return()
+# %%
+
+X=forecast_data_inter[1,:,:]
+P=forecast_data_inter[0,:,:]
+V=forecast_data_inter[1,:,:] -forecast_data_inter[0,:,:]
+
+
+Xm3=moment(V, axis=1, moment=3)
+Vm3=moment(X, axis=1, moment=3)
+Z=np.arcsin(2*X-1)
+Zm3=moment(Z, axis=1, moment=3)
+
+
+plt.hist(np.diff(V.flatten()), 30, density=True)
+
+plt.hist(np.diff(Z).flatten() ,30, density=True, color='r')
+
+
+
+
+
+
+mean,std=norm.fit(np.diff(X).flatten())
+range_1=np.linspace(-1,1,100)
+y=norm.pdf(range_1,mean,std)
+plt.plot(range_1,y, 'k')
+plt.hist(np.diff(X).flatten() ,30, density=True , color='k')
+
+mean,std=norm.fit(np.diff(Z).flatten())
+range_1=np.linspace(-1,1,100)
+y=norm.pdf(range_1,mean,std)
+plt.plot(range_1,y, 'r')
+plt.hist(np.diff(Z).flatten() ,30, density=True, color='r')
+
[…]

### 2019-09-11 LaTeX_code/Discussion/Discussion_29_07_19.tex
fixed parallel, progress bar, RK45

@@
 
-Finally, we conclude that the boarders of the range $[0,1]$ are reflectors and are impenetrable. Hence, the process $V_t$ cannot exit the range $[-1,1]$.
+Finally, we conclude that the boarders of the range $[-1,1]$ are reflectors and are impenetrable. Hence, the process $V_t$ cannot exit the range $[-1,1]$.
 
@@
 		and the moments by,
-		\begin{equation*}
-		\frac{d m_1 (t)}{dt} = - m_1(t)\theta_t \implies m_1(t_2)= V_{t_1} e^{-\int_{t_1}^{t_2} \theta_t \ dt }
-		\end{equation*}
+		\begin{equation}
+		\begin{split}
+		\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t \\
+		\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta(1+\alpha) + 2\alpha\theta m_1(t)(1-2p_t) + 2 \alpha\theta p_t (1-p_t)\\
+		\end{split}
+		\end{equation}
+		with initial conditions $m_1(t_1)=x,\ m_2(t_1)=x^2$ where $x$ is an observation of the process $V_t$ at the previous time step.\\
+		The solution of the ODEs above is given by,
+		\begin{equation}
+		\begin{split}
+			m_1(t_2) & = m_1(t_1) e^{-\int_{t_1}^{t_2} \theta_t \ dt }\\
+		m_2(t_2) & = m_2 (t_1) e^{-2(1+\alpha)\int_{t_1}^{t_2} \theta_t \ dt} \\
+		& + \alpha \int_{t_1}^{t_2} \left(2\theta_s m_1(s)( 1-2p_s)+ 2\theta_s p_s(1-p_s)\right)   e^{-2(1+\alpha)\int_{t_1}^{t_2-s} \theta_u \ du}  \ ds
+		\end{split}
+		\end{equation}
+
+		We linearly interpolate the forecast, observations and parameters between the observation.
+Then we integrate numerically using the tripizoidal rule.
+We define a uniform grid $i=\{0,1,2,3 \ \cdots K \}$ such that $\Delta t = \frac{t_2 - t_1}{K} =  \frac{\Delta N }{K} $.
+Where $\Delta N $ is the time between the observations of the process $V_t$.
+		\begin{align*}
+			\int_{t_1}^{t_2} \theta_t \ dt & \approx I_{1,K} = \sum_{i=0}^K \frac{ \theta_i + \theta_{i+1} } {2} \Delta t  \\
+	\end{align*}
+Similarly,
 	\begin{equation*}
 	\begin{split}
-		\frac{d m_2 (t)}{dt} &=  - m_2(t)\theta(1+\alpha) + \alpha\theta m_1(t)( (1-p_t -p_t^2)) +2 \\
-		& \implies m_2(t_2) = v_{t_1}^2 e^{-(1+\alpha)\int_{t_1}^{t_2} \theta_t \ dt} \\
-		& \quad \quad + \alpha \int_{t_1}^{t_2} \left(\theta_s m_1(s)( 1-p_s - p_s^2 )+2\right)   e^{-(1+\alpha)\int_{t_1}^{t_2-s} \theta_u \ du}  \ ds
+		\int_{t_1}^{t_2} & \left(2\theta_s m_1(s)( 1-2p_s)+ 2\theta_s p_s(1-p_s)\right)   e^{-2(1+\alpha)\int_{t_1}^{t_2-s} \theta_u \ du}  \ ds \\
+		 & \approx I_{2,K} = \sum_{i=0}^K \Delta t  \frac{ \left( 2 \theta_{i+1}m_{1,i+1}(1-2p_{i+1}) +2 \theta_{i+1} p_{i+1} (1-p_{i+1})  \right) e^{-2(1+\alpha) I_{1,i+1} } }{2} \ +\\
+		&  \Delta t \frac{\left( 2 \theta_{i}m_{1,i}(1-2p_{i}) +2 \theta_{i} p_{i} (1-p_{i})  \right) e^{-2(1+\alpha) I_{i} } }{2}  \\
 \end{split}
 \end{equation*}
-		We discretize and integrate numerically step-by-step using the Tripizoidal rule,
-		\begin{align*}
-			m_{1,i+1}&= v_i \ e^{ - \frac{\theta_i + \theta_{i+1}}{2} \Delta t} \\
-			m_{2,i+1} &= v_i^2 e^{-(1+ \alpha)\frac{\theta_i + \theta_{i+1}}{2} \Delta t } + \\
-			& \alpha \Delta t  \frac{ \left( \theta_{i+1}m_{1,i+1}(1-p_{i+1} - p_{i+1}^2)+2 \right)e^{-(1+\alpha) \frac{\theta_i + \theta_{i+1}}{2} \Delta t }  + \theta_{i}v_{i}(1-p_{i} - p_{i}^2) +2    }{2}
-	\end{align*}
-	where $v_i$ is an observation of the process $V_t$ at the previous time step.\\
-	We check the Feller condition on the boundaries $[0,1]$ of the process $V_t$. If the following condition holds
-	\begin{equation*}
-		\lim_{x\to x_{0}} \left( a(x,t)  - \frac{1}{2}\frac{\partial}{\partial x} b^2(x,t) \right) \geq 0
-\end{equation*}
-Then the process is bounded by $x_0$.
-	\begin{equation*}
-		\lim_{v\to -1,+1} \left( - \theta_t v - \theta_t \alpha \right( 1- 2v - 2p_t \left) \right) \geq 0
-\end{equation*}
+Finally, we have
+\begin{equation}
+\begin{split}
+	m_1(t_2) & \approx m_1(t_1) e^{-I_1 }\\
+m_2(t_2) & = m_2 (t_1) e^{-2(1+\alpha)I_1}  + \alpha I_2 \\
+\end{split}
+\end{equation}
+with initial conditions $m_1(t_1)= m_{1,0}=x,\ m_2(t_1)=m_{2,0}=x^2$ where $x$ is an observation of the process $V_t$ at the previous time step.\\
 		\item Moments approach with a Gaussian proxy after a Lamperti transformation and an approximation in the first moment. The SDE is given by,
@@
 		where $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $. After the assumption that $\E[\sin(Z_t)]
-	 \approx \E Z_t$. Note that $Z_t \in \R $ is not bounded and so this approximation is not justified. We can write approximate the moments as follows,
+	 \approx \E Z_t$. Note that $Z_t \in \R $ is not bounded and so this approximation cannot be justified by a small angle approximation. We can write approximate moments as follows,
 		\begin{equation*}
@@
 		\begin{equation}
-					v(t_2)= e^{2\int_{t_1}^{t_2} \frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_1(s)} \ dt} \left(\alpha \int_{t_1}^{t_2} \theta_t e^{-2\int_{t_1}^{s} \frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_1(s)} } \ ds  \right)
+					v(t_2)= e^{2\int_{t_1}^{t_2} \frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_1(s)} \ ds} \left(\alpha \int_{t_1}^{t_2} \theta_s e^{-2\int_{t_1}^{s} \frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_1(u)} du } \ ds  \right)
 		\end{equation}
-		where $a(x;\theta_s)=\frac{- \theta_t (1+ \sin(x) - 2p_t) + \alpha \theta_t \sin (x)   }{\cos (x)}$ is the drift term after the Lamperti transformation.
-		We first differentiate the function $a(x;\theta_s)$,
+		where $a(x;\theta_s)=\frac{- \theta_t (1+ \sin(x) - 2p_t) + \alpha \theta_t \sin (x)   }{\cos (x)}$ is the drift term after the Lamperti transformation. Thus,
 		\begin{align*}
@@
 		\end{align*}
-		Then, we discretize and integrate numerically step-by-step using the Tripizoidal rule,
-		\begin{align*}
-		%\begin{split}
-			m_{1,i+1} &= \arcsin \left(  \left(  \frac{ \theta_{i+1}(2p_{i_+1} - 1) + \theta_{i}(2p_{i} - 1)e^{- (1-\alpha) \frac{\theta_i + \theta_{i+1}}{2} \Delta t}   }{2} \Delta t \right)  +  \sin(v_i) \right) \\
-			v_{i+1} &= \alpha \Delta t  \frac{ \theta_{i+1} e^{2 \frac{\frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_{1,i+1}}}{2} \Delta t  }+  \theta_{i}  e^{2 \frac{\frac{\partial a(x;\theta_s)}{\partial x}|_{x= v_i}}{2}   } }{2}
-		%\end{split}
-	\end{align*}
+		We linearly interpolate the forecast, observations and parameters between the observation. Then, we integrate numerically using the tripizoidal rule,
+		\begin{equation*}
+			\begin{split}
+			& \int_{t_1}^{t_2}  \frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_1(s)} \ ds \\
+			& \approx I_{3,K}= \sum_{i=0}^K \frac{ \theta_{i+1} (2p_{i+1} - 1) \tan (m_{1,i+1}) \sec (m_{1,i+1}) + \theta_{i+1}(\alpha - 1)\sec^2 (m_{1,i+1}) }{2} \Delta t \ + \\
+			& \frac{ \theta_i (2p_i - 1) \tan (m_{1,i}) \sec (m_{1,i}) + \theta_{i} (\alpha - 1)\sec^2 (m_{1,i}) }{2} \Delta t
+			\end{split}
+		\end{equation*}
+
+		\begin{equation*}
+			\begin{split}
+			& \int_{t_1}^{t_2} \theta_s \left( 2p_s-1\right)e^{(1-\alpha) \int_{t_1}^{s} \theta_u \ du } \ ds \\
+			& \approx I_{4,K}= \sum_{i=0}^K \frac{ \theta_{i+1} \left( 2p_{i+1}-1\right)e^{(1-\alpha)I_{1,i+1} } +  \theta_i \left( 2p_i-1\right)e^{(1-\alpha) I_{1,i} }}{2} \Delta t \\
+			\end{split}
+		\end{equation*}
+
+		\begin{equation*}
+			\begin{split}
+			& \int_{t_1}^{t_2} \theta_s e^{-2\int_{t_1}^{s} \frac{\partial a(x;\theta_s)}{\partial x}|_{x=m_1(u)} du } \ ds \approx I_{5,K}= \sum_{i=0}^K \frac{ \theta_{i+1}e^{-2 I_{3,i+1} } + \theta_{i}e^{-2 I_{3,i} } }{2} \Delta t \\
+			\end{split}
+		\end{equation*}
+
+Finally, we have
+		\begin{equation}
+			m_{1}(t_2)  \approx \arcsin \left(   e^{-(1-\alpha)I_{1,K}} I_{4,K} +  \sin(m_{1}(t_1) \right)
+	\end{equation}
+	\begin{equation}
+		v(t_2)  \approx e^{2I_{3,K}} \alpha I_{5,K}
+\end{equation}
 
@@
 	\begin{align}
-		m_1(t) &= Z_0e^{(\alpha-1)\int_0^t \theta_s \ ds } - \int_0^t \theta_s (1-2p_s) e^{(\alpha-1)\int_s^t \theta_u \ du } \ ds\\
-		v(t)&= \int_0^t \sqrt{2 \theta_s \alpha} \ e^{(\alpha-1)\int_s^t \theta_u \ du }
+		m_1(t_2) &= m_1(t_1) e^{(\alpha-1)\int_{t_1}^{t_2} \theta_s \ ds } - \int_{t_1}^{t_2} \theta_s (1-2p_s) e^{(\alpha-1)\int_s^t_2 \theta_u \ du } \ ds\\
+		v(t_2) &= \int_{t_1}^{t_2} \sqrt{2 \theta_s \alpha} \ e^{(\alpha-1)\int_s^{t_2} \theta_u \ du }
 \end{align}
-We discretize and integrate numerically step-by-step using the Tripizoidal rule,
-\begin{align*}
-	m_{1,i+1} &= z_0 e^{(\alpha-1) \frac{\theta_{i+1}+ \theta_i}{2} \Delta t } - \Delta t \frac{\theta_{i+1}( 1-2p_{i+1} )e^{(\alpha-1) \frac{\theta_{i+1} + \theta_i}{2} \Delta t} + \theta_i (1-2p_i) }{2} \\
-	v_{i+1} &= \sqrt{2 \alpha} \Delta t \frac{\sqrt{\theta_{i+1}} e^{(\alpha-1)\frac{\theta_{i+1} + \theta_i}{2}\Delta t} +\sqrt{\theta_{i}}  }{2}
-\end{align*}
+
+\begin{equation*}
+	\begin{split}
+	& \int_s^{t_2} \theta_u \ du \approx I_{6,n}= \sum_{i=n}^K \frac{ \theta_i + \theta_{i+1} }{2}\Delta t \\
+	\end{split}
+\end{equation*}
+for $n$ such that $s=n \Delta t$.
+
+\begin{equation*}
+	\begin{split}
+	& \int_{t_1}^{t_2} \theta_s (1-2p_s) e^{(\alpha-1)\int_s^t_2 \theta_u \ du } \ ds \\
+	& \approx I_{7,K}= \sum_{i=0}^K \frac{    \theta_{i+1} (1-2p_{i+1}) e^{(\alpha-1)I_{6,i+1} }    +    \theta_{i} (1-2p_{i}) e^{(\alpha-1)I_{6,i} }      }{2}\Delta t \\
+	\end{split}
+\end{equation*}
+
+\begin{equation*}
+	\begin{split}
+	& \int_{t_1}^{t_2} \sqrt{2 \theta_s \alpha} \ e^{(\alpha-1)\int_s^{t_2} \theta_u \ du } \\
+	& \approx I_{8,K}= \sum_{i=0}^K \frac{     \sqrt{2 \theta_{i+1} \alpha} \ e^{(\alpha-1)I_{6,i+1} }    +     \sqrt{2 \theta_{i} \alpha} \ e^{(\alpha-1)I_{6,i} }      }{2}\Delta t \\
+	\end{split}
+\end{equation*}
+
+Finally, we have
+		\begin{equation}
+			m_{1}(t_2)  \approx m_1(t_1) e^{(\alpha-1)I_{1,K}} - I_{7,K}
+	\end{equation}
+	\begin{equation}
+		v(t_2)  \approx I_{8,K}
+\end{equation}
 

### 2019-09-11 LaTeX_code/poster_non_academic/poster.tex
fixed parallel, progress bar, RK45

--- 2019-08-28 LaTeX_code/poster/poster.tex
@@
-\documentclass[ima, 20pt, portrait, plainboxedsections]{sciposter}
+\documentclass[ima, 25pt, portrait, plainboxedsections]{sciposter}
 
@@
 \usepackage{bm}
+\usepackage{anyfontsize}
+\usepackage{times}
 
@@
 % Author info
-\title{ On the Uncertainty of Wind Power Forecasts}
+\title{  Probabilistic Wind Power Forecasting}
 \author{ Waleed Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger}}
@@
 \begin{multicols}{3}
-
+%\normalsize
+\fontsize{32}{32}\selectfont
 \section*{Introduction}
@@
 \item  Energy trading of future excess power.
-\item Design of Investment strategies.
+\item Design of investment strategies.
 \end{itemize}
-We propose a parametric forecast error model to:
+\quad \\
+We propose a stochastic forecast error model to:
 \begin{itemize}
-\item  Simulate forecast error and quantify its uncertainty.
-\item  Calibrate a forecast model for  optimal dispatch of electric power.
+\item  Simulate forecast error and quantify its uncertainty with respect to real-world performance.
+\item  Calibrate a short-term stochastic forecast model for  optimal dispatch of electric power.
 \end{itemize}
+\quad \\
 This model is based on:
@@
 
-\section*{Data}
+\section*{Model}
 
+\subsection*{Phenomenological  Model}
+
+We propose to model and predict errors in wind power production forecasts according to their real-world performance and conditions.
+
+\subsection*{Physical Constrains} The proposed model respects the full installed capacity of the wind farms. Additionally, it is  unbiased with respect to the wind power forecast.
+
+\section*{Sample Data Set}
 To capture real-world performance of  wind power forecasts, our model incorporates historical wind power production data along with their corresponding forecasts.\\
@@
 %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{Forecast_data_68.pdf}
-    \includegraphics[width=0.8\linewidth]{Forecast_data_82.pdf}
+   \includegraphics[width=1\linewidth]{Forecast_data_68.pdf}
+    \includegraphics[width=1\linewidth]{Forecast_data_82.pdf}
 \end{center}
-   \caption{Examples of wind power generation from the data set along with the wind power generation forecast.}
+   \caption{Examples of wind power generation set along with the wind power generation forecast from the data set.}
 \label{fig:long}
@@
 
-\section*{Model}
+\section*{Inference}
+Using inference techniques, we were able to obtain the optimal parameters to our model of stochastic differential equations.\\
 
-\subsection*{Phenomenological  Model}
+Moreover, the results are confirmed by the increasing accuracy of our optimal parameters estimation as we increase the number of samples in the data set.\\
 
-Let $X_t$ be the  wind power generation forecasts stochastic process defined by the  following parameterized stochastic differential equation (SDE),
-\begin{equation}
-\begin{split}
-dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
-X_0 & = X_0
-\end{split}
-\label{main}
-\end{equation}
+The proposed model is computationally efficient, providing an accurate and reliable solution.
 
-\begin{itemize}
-%\item $\Delta_N$: any function of the number of samples, $N$. For example, $\Delta_N = \frac{1}{N}$.
-\item $a(\cdot; \bm{\theta}):[0,1] \to \R $  a drift function.
-\item $b (\cdot; \bm{\theta} ):[0,1] \to \R$  a  diffusion function.
-\item $\bm{\theta}$: a vector of parameters.
-\item $W_t$: Standard Wiener random process in $\R$.
-\end{itemize}
-%We prescribe the following derivative tracking model:
+%\section*{Methodology}
+%
+%
+%
 %\begin{itemize}
-%\item $a(X_t; \bm{\theta})=  \dot{p}_t- \theta (X_t - p_t)$
-%\item  $ b (X_t; \bm{\theta} )= \sqrt{2 \theta \alpha p_t(1-p_t) X_t (1-X_t)} $
+%%\item The log-likelihood is convex in the  parameters $(\alpha, \theta_t )$ on the positive quadrant.
+%\item We optimize using L-BFGS algorithm constrained to the positive quadrant.
 %\end{itemize}
-%where $p_t$ is the wind power forecast.
+%The ellipse defined by the  Hessian of the log-likelihood shrinks at a fast rate as shown in Figure (\ref{ellipse_drawing}). The contours of the  log-likelihood can be seen in Figure (\ref{contour}).
+%
+%\begin{figure}[t]
+%\begin{center}
+%%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+%    \includegraphics[width=0.6\linewidth]{ellipse_conv_samples_dN=14e-02.pdf}
+%\end{center}
+%   \caption{Left:Shrinkage of the ellipse determined by the Hessian matrix of the log-likelihood around the point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ (Axis are not in natural scale, arrows only to  eignevector direction).
+Right: Convergence of the major and semi-axis of the ellipse  of the Hessian of the log-likelihood at the point optimality $(\theta_0^*, \alpha^*)\approx (8,1)$.
+Note that it is slightly faster than the expected rate of $1/\sqrt{M}$.
+This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample.}
+%\label{ellipse_drawing}
+%\end{figure}
 
-\subsection*{Physical Constrains}
-Let $p_t$ be a numerical wind power forecast, which is an input to this approach. Then the model is given by the following It\^{o} stochastic differential equation,
-\begin{equation}
-\begin{split}
-dX_t&= \dot{p} \ dt - \theta_t( X_t- p_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t \quad t > 0 \\
-X_0&=x_0
-\end{split}
-\end{equation}
-As the  installed power production capacity is limited, we normalize with respect to the installation power.
-Thus our process must be limited to the range $[0,1]$.
-To enforce this constraint, we must have drift and diffusion control.
-\subsubsection*{Diffusion: } The physical constraint is respected  by choosing  diffusion coefficient $ b (x; \bm{\theta} )= \sqrt{2 \theta_t \alpha x (1-x)} $ that is zero on the boundaries of $[0,1]$.
-\subsubsection*{Drift: }
-$X_t$ remains in $[0,1]$ a.s. by choosing $\theta_t$ as follows,
-\begin{equation}
-\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
-\end{equation}
+% \quad\\
+% \quad\\
 
-\subsubsection*{Change of Variables:}
-In order to avoid differentiation of the forecast $\dot{p}_t$ and simplify, we apply a change of variables $V_t = X_t - p_t$. Then  model becomes,
-\begin{equation}
-\begin{split}
-dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t \quad t > 0 \\
-V_0 & = v_0
-\end{split}\label{main}
-\end{equation}
+\section*{Results}
+ We were able to obtain the optimal  parameters of the model based on the complete data sets mentioned earlier.\\
 
-with
-\begin{equation}
-\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
-\end{equation}
+ In Figure (\ref{simulated_24hr}) and (\ref{simulated_12hr}), we simulate possible  paths wind power production for a given wind power forecast.
 
-Where
-\begin{itemize}
-\item $p_t$: Numerical wind power production forecast.
-\item $\theta_0 >0$: Mean reversion parameter.
-\item $\alpha>0$: Variability parameter.
-\end{itemize}
-
-\section*{Inference}
-
-\subsection*{Likelihood}
-The SDE above defines the stochastic process $V_t$ which can be characterized by its transition density. \\
-
-Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed in intervals of $\Delta_N$.
-Since $V_t$ is Markovian, the likelihood function is given by  product of its  transition densities.
-
-\begin{equation}
-\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}}, \bm{\theta})  \rho (V_{j,0})
-\label{likelihood}
-\end{equation}
-
-\subsection*{Approximate Likelihood}
-Solving for transition densities of the process $V_t$ requires solving the Fokker-Planck equation at every step which is computationally prohibitive.
-A common choice is performing a  Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints.
-\\
-
-Therefore, we propose an approximate likelihood inspired by the stationary distribution of the process $X_t$ which is a Beta distribution for a constant forecast $p_t$.Additionally,  as the process $X_t$ and $p_t$ take on values in $[0,1]$, then $V_t$ takes on values in $[-1,1]$.
-Therefore,  it is natural to use a  Beta distribution with compact support on $[-1,1]$.
-
-%We obtain the modified Beta distribution,
-%
-%\begin{equation}
-%\begin{split}
-%f_Y(y; \alpha , \beta )&= f_X(g^{-1}(y) ) \Big| \frac{\partial g^{-1}(y)}{\partial y }  \Big| \\
-%&= \frac{1}{B(\alpha, \beta) (b-a)} \Big(\frac{a-y}{b-a}\Big)^{\alpha -1}\Big(1-\frac{a-y}{b-a} \Big)^{\beta -1} \label{modified_Beta}
-%\end{split}
-%\end{equation}
-%where $B(\cdot,\cdot)$ is the Beta function. Also, we have that
-%\begin{equation}
-%\E[Y]= a + (b-a) \frac{\alpha}{\alpha + \beta}
-%\end{equation}
-%\begin{equation}
-%\V[Y]= (b-a)^2 \frac{\alpha \beta}{(\alpha + \beta)^2 (\alpha + \beta + 1)}
-%\end{equation}
-
-\subsubsection*{ Moment Matching}
-To approximate the transition densities of  the process $V_t$, we match its moments with the shape parameters of the Beta distribution using It\^{o}'s formula. \\
-
-The moments of the process $V_t$ are given by,
-\begin{equation}
-\begin{split}
- \frac{dm_1(t_n)}{dt} &=    - \theta_t m_1(t_n)  \\
-\frac{d m_{2}(t_n)}{dt}&= -2m_{2}(t_n) [\theta_t + \alpha \theta_t p_t(1-p_t) ] \\
-&+ 2m_{1}(t_n)[\alpha \theta_t p_t (1-p_t) (1-2p_t)] \\
-&+ 2\alpha \theta_t p_t^2(1-p_t)^2  \\
-%m_2(0) = \E[V_0^2] = v_0^2\\
-\end{split}
-\end{equation}
-with initial conditions, $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2$.
-
-\section*{Methodology}
-
-\subsection*{ Optimization  }
- \begin{figure}[t]
-\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.9\linewidth]{ISO_100_samples_dN=14e-02.pdf}
-   %\includegraphics[width=0.5\linewidth]{ISO_500_samples_dN=14e-02.pdf}
-   %\includegraphics[width=0.5\linewidth]{ISO_1193_samples_dN=14e-02.pdf}
-\end{center}
-   \caption{Contour plot of the log-likelihood with only 100 sample paths, point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ indicated by the  black dot.}
-\label{contour}
-\end{figure}
-\begin{itemize}
-%\item The log-likelihood is convex in the  parameters $(\alpha, \theta_t )$ on the positive quadrant.
-\item We optimize using L-BFGS algorithm constrained to the positive quadrant.
-\end{itemize}
-The ellipse defined by the  Hessian of the log-likelihood shrinks at a fast rate as shown in Figure (\ref{ellipse_drawing}). The contours of the  log-likelihood can be seen in Figure (\ref{contour}).
+ %Note that the confidence bands obtained are non-trivial and reflect the complexity of the uncertainties in numerical wind power generation forecasts.
 
@@
  %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-    \includegraphics[width=0.6\linewidth]{ellipse_conv_samples_dN=14e-02.pdf}
-   \includegraphics[width=0.6\linewidth]{ellipse1193_samples_dN=14e-02.pdf}
-\end{center}
-   \caption{Left:Shrinkage of the ellipse determined by the Hessian matrix of the log-likelihood around the point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ (Axis are not in natural scale, arrows only to  eignevector direction).
-Right: Convergence of the major and semi-axis of the ellipse  of the Hessian of the log-likelihood at the point optimality $(\theta_0^*, \alpha^*)\approx (8,1)$.
-Note that it is slightly faster than the expected rate of $1/\sqrt{M}$.
-This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample.}
-\label{ellipse_drawing}
-\end{figure}
-
-\section*{Results}
-In the following figures , we simulate sample wind power production forecasts using the optimal parameters  $(\theta_0^*, \alpha^*)\approx (8,1)$ and obtain the associated confidence bands empirically using 1000 sample paths for each forecast.
-
-\begin{figure}[t]
-\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.8\linewidth]{simulated/12hr/1124.pdf}
-   \includegraphics[width=0.8\linewidth]{simulated/24hr/19.pdf}  %569
-   %\includegraphics[width=1\linewidth]{simulated/24hr/1099.pdf}
+    \includegraphics[width=1\linewidth]{simulated/24hr/19.pdf}  %569
+    \includegraphics[width=1\linewidth]{simulated/24hr/1099.pdf}
     %\includegraphics[width=0.9\linewidth]{6hr_forecast_CI_68.pdf}
  \end{center}
-   \caption{ Examples of simulated paths of wind power production for the next 12 and 24 hours.}
+    \caption{ Examples of simulated paths of wind power production for the next 24 hours.}
  \label{simulated_24hr}
@@
  %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{confidence_intervals/24hr/31.pdf}
-  \includegraphics[width=0.8\linewidth]{confidence_intervals/24hr/820.pdf}
-  %\includegraphics[width=1\linewidth]{confidence_intervals/24hr/82.pdf}
+    \includegraphics[width=1\linewidth]{simulated/12hr/622.pdf}  %569
+    \includegraphics[width=1\linewidth]{simulated/12hr/1124.pdf}
+    %\includegraphics[width=0.9\linewidth]{6hr_forecast_CI_68.pdf}
+ \end{center}
+    \caption{ Examples of simulated paths of wind power production for the next 12 hours.}
+ \label{simulated_12hr}
+ \end{figure}
+
+ In Figure (\ref{fig:72hr}) and (\ref{fig:6hr}), we obtain empirical confidence bands using the optimal parameters.
+
+\begin{figure}[t]
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=1\linewidth]{confidence_intervals/24hr/31.pdf}
+   \includegraphics[width=1\linewidth]{confidence_intervals/24hr/820.pdf}
+   \includegraphics[width=1\linewidth]{confidence_intervals/24hr/82.pdf}
 
@@
 %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-  \includegraphics[width=0.8\linewidth]{confidence_intervals/12hr/75.pdf}
-  \includegraphics[width=0.8\linewidth]{confidence_intervals/12hr/148.pdf}
+   \includegraphics[width=1\linewidth]{confidence_intervals/12hr/75.pdf}
+   \includegraphics[width=1\linewidth]{confidence_intervals/12hr/148.pdf}
    %\includegraphics[width=0.9\linewidth]{6hr_forecast_CI_68.pdf}
@@
 
- \begin{figure}[t]
-\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_623.pdf}  %569
-\end{center}
-   \caption{ Examples of omitted data which corresponds to production control and manual energy management decisions.
+% \begin{figure}[t]
+%\begin{center}
+%%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+%   \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_623.pdf}  %569
+%\end{center}
+%   \caption{ Examples of omitted data which corresponds to production control and manual energy management decisions.
 In this example,  wind power production was repeatedly curtailed at around 2 AM which is a period of low power demand.
 Automatic detection of such scenarios is to be incorporated in future works.}
-\label{fig:6hr}
-\end{figure}
+%\label{fig:6hr}
+%\end{figure}
 

### 2019-09-11 parallel_test_loop.py

@@ -1,0 +1,103 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+import scipy.stats
+from scipy.optimize import minimize
+from scipy.stats import multivariate_normal, norm
+from mpl_toolkits.mplot3d import Axes3D
+import operator
+from scipy.optimize import minimize
+from scipy.optimize import basinhopping
+import math
+import random
+from scipy import interpolate
+from math import pi
+from numpy import linalg as LA
+import datetime as dtM
+import os
+from multiprocessing import Process
+import time
+
+def f(name, sec):
+    info('function f')
+    time.sleep(sec)
+    print ('hello', name)
+    L=sec
+
+def info(title):
+    print (title)
+    print ('module name:', __name__)
+    if hasattr(os, 'getppid'):  # only available on Unix
+        print('parent process:', os.getppid())
+    print('process id:', os.getpid())
+
+if __name__ == '__main__':
+    p1 = Process(target=f, args=('bob',0))
+    p2 = Process(target=f, args=('tom',5))
+    p3 = Process(target=f, args=('goerge',10))
+    p1.start()
+    p2.start()
+    p3.start()
+    p1.join()
+
+
+def moment_compute(dN, X_prev, X_next, p_prev, theta_current, alpha_current ):
+    m_1=X_prev*np.exp(- dN*theta_current)
+    m_2=  (X_prev**2 + 2*dN*( X_prev*(alpha_current*theta_current*p_prev*(1-p_prev)*(1-2*p_prev )) + \
+                 alpha_current*theta_current*p_prev**2*(1-p_prev)**2) ) /(  1+ dN*2*(theta_current+alpha_current*theta_current*p_prev*(1-p_prev) ))
+    a=m_1;
+    b=m_2- m_1**2;
+
+    if b==0: b=1e-16
+    if b<0:
+        b=1e-16
+
+    beta_param_alpha= - ( (1+a)*(a**2 +b -1)    )/(2*b)
+    beta_param_beta= ( (a-1)*(a**2 + b -1)  )  /(2*b)
+
+    L_n_current=(beta_param_alpha-1 )*np.log(  (X_next+1)/2 ) +\
+     (beta_param_beta-1)*np.log(1-( X_next +1)/2 )-\
+     scipy.special.betaln(beta_param_alpha, beta_param_beta)
+
+    return(L_n_current)
+
+
+
[…]

### 2019-09-11 python_code/Base_plus.py

@@ -15,6 +15,13 @@ from math import pi
 from numpy import linalg as LA
 import datetime as dtM
 import os
+import multiprocessing as mp
+import time
+from scipy.integrate import solve_ivp
+import sys
+import warnings
+from tqdm import tqdm
+
 ##############
 #constants
 Nfeval=0
@@ -43,7 +50,7 @@ class model_modified_drift:
         self.optimal=optimal()
         self.Nfeval=0
 
-    def lamperti_likelihood_SDE_approx(self,param):
+    def lamperti_likelihood_SDE_approx(self,param,send_end_to_evaluater=None):
         #data
         X=self.data
         p=self.forecast
@@ -53,46 +60,62 @@ class model_modified_drift:
         M=self.disct.M
         #input parameters
         theta,alpha = param;
-        #print( theta, alpha)
         L_n=0;
         L_m=0;
-        a=0;b=0;
         eps=np.finfo(float).eps;
-        m_1=0
-        m_2=0
         dN=1/N
+        dA=0
         counter=0
         for j in range(0,M):
-            h=0
-            g=0
             mean=0
             var=0
             L_m = L_m + L_n
             theta_adjusted, _ = theta_adjust( theta , p[j,:] )
-            for i in range(0,N-1): #start from 1 or zero #Implement Tripizoidal scheme
-                #theta_adjusted[i]
-                g= g + theta_adjusted[i]*(1-2*p[j,i])*h*dN #this h is approx.
-                h= h + theta_adjusted[i]*(alpha-1)*dN
+            L_n=0
+            for i in range(0,N-2): #start from 1 or zero #Implement Tripizoidal scheme
 
-                mean= X[j,i]* np.exp(h) - g
-                var= var + 2*alpha*theta*np.exp(2*h) *dN
+                mean, var =moment_compute_approx_lamperti(dN, X_prev=X[j,i], X_next=X[j,i+1], p_prev=p[j,i],p_next=p[j,i+1], theta_prev=theta_adjusted[i], theta_next=theta_adjusted[i+1],alpha=alpha )
 
-                if np.isnan(mean): print('mean is nan')
-                if np.isnan(var): print('var is nan')
[…]

### 2019-09-11 python_code/fit_SDE_gauss_linearize_NDLM.py

@@ -1,0 +1,67 @@
+import os
+os.chdir('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code')
+from Base_plus import *
+forecast_data_in=np.load('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code/data/cleansed/URG_forecast_data_A_2018.npy')
+#forecast_data_inter=data_check_interpolate(forecast_with_data=forecast_with_data)
+now = dtM.datetime.now();
+current_time=now.strftime("%y-%m-%d-%H-%M-%S")
+script_name='fit_SDE'
+current_data_dir='data/'+ script_name +current_time
+os.mkdir(current_data_dir)
+
+forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
+print(current_data_dir)
+
+
+
+#check no nans
+np.sum( np.isnan(forecast_data_inter.flatten()))
+np.max(forecast_data_inter[1:,:,:])<=1
+np.min(forecast_data_inter[1:,:,:])>=0
+
+N=forecast_data_inter.shape[2]
+M=forecast_data_inter.shape[1]-240 #to be changed in generalization
+dt=1
+#forecast_data_inter[0,:,:] #forecast
+
+N
+M
+dt
+
+disct_temp = disct(N,dt,M)
+p=forecast_data_inter[2,:-240,:]
+V= forecast_data_inter[2,:-240,:]-forecast_data_inter[1,:-240,:]
+X=forecast_data_inter[1,:-240,:]
+#Z = np.arcsin(2*X - 1)
+
+#answer 9.06 , 0.473
+this_model=model_modified_drift(disct_temp,V, forecast= p)
+intial_point= np.array((1,0.8))
+optim=this_model.optimize(inference="lamperti_likelihood_linearized" ,method="Nelder-Mead",param_initial=intial_point)
+
+
+optim
+
+
+file_object  = open(current_data_dir+'/results.out', 'w')
+note='Fit for ' + str(M) +' paths' + ' of ' + str(N) +' hours. Initialized at '\
+    + str(intial_point)
+file_object.write( note +'\n'+str(optim.x) +'\n' +optim.message[0])
+file_object.close()
+
+optim
+
+
+# co=np.zeros((forecast_data_inter.shape[1]))
+# for sel in range(0,forecast_data_inter.shape[1]):
[…]

### 2019-09-11 python_code/fit_SDE_new_Beta_NDLM_many_runs.py

@@ -1,0 +1,67 @@
+import os
+os.chdir('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code')
+from Base_plus import *
+forecast_data_in=np.load('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code/data/cleansed/URG_forecast_data_A_2018.npy')
+#forecast_data_inter=data_check_interpolate(forecast_with_data=forecast_with_data)
+now = dtM.datetime.now();
+current_time=now.strftime("%y-%m-%d-%H-%M-%S")
+script_name='fit_SDE'
+current_data_dir='data/'+ script_name +current_time
+os.mkdir(current_data_dir)
+
+forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
+print(current_data_dir)
+
+
+
+#check no nans
+np.sum( np.isnan(forecast_data_inter.flatten()))
+np.max(forecast_data_inter[1:,:,:])<=1
+np.min(forecast_data_inter[1:,:,:])>=0
+
+N=forecast_data_inter.shape[2]
+M=forecast_data_inter.shape[1]-240 #to be changed in generalization
+dt=1
+#forecast_data_inter[0,:,:] #forecast
+
+N
+M
+dt
+
+disct_temp = disct(N,dt,M)
+p=forecast_data_inter[2,:-240,:]
+V= forecast_data_inter[2,:-240,:]-forecast_data_inter[1,:-240,:]
+X=forecast_data_inter[1,:-240,:]
+#Z = np.arcsin(2*X - 1)
+
+#answer 9.06 , 0.473
+this_model=model_modified_drift(disct_temp,V, forecast= p)
+intial_point= np.array((1,0.8))
+optim=this_model.optimize(inference="beta_likelihood" ,method="Nelder-Mead",param_initial=intial_point, niter=10)
+
+
+optim
+
+
+file_object  = open(current_data_dir+'/results.out', 'w')
+note='Fit for ' + str(M) +' paths' + ' of ' + str(N) +' hours. Initialized at '\
+    + str(intial_point)
+file_object.write( note +'\n'+str(optim.x) +'\n' +optim.message[0])
+file_object.close()
+
+optim
+
+
+# co=np.zeros((forecast_data_inter.shape[1]))
+# for sel in range(0,forecast_data_inter.shape[1]):
[…]

### 2019-09-11 python_code/likelihood_explorer.py

@@ -1,6 +1,6 @@
 
 import os
-os.chdir('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code')
+os.chdir('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code')
 from Base_plus import *
 #from multi_path_base import model_modified_drift
 forecast_with_data=np.load('data/forecast_with_data.npy')
@@ -12,7 +12,7 @@ current_plotting_dir='data/'+ script_name+'_' +current_time
 os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
 
 N=forecast_data_inter.shape[2]-1
-M= 100 #forecast_data_inter.shape[1]
+M=forecast_data_inter.shape[1]
 dt=1
 dN=1/N
 dN
@@ -25,17 +25,26 @@ dN
 
 this_model=model_modified_drift(disct_temp,V, forecast= p)
 
-theta_array=np.linspace(1, 100, 50)
-alpha_array=np.linspace(0.001, 0.15, 50)
+theta_array=np.linspace(0.01, 30, 50)
+alpha_array=np.linspace(0.01, 2, 50)
 
 np.save(current_plotting_dir+'/num_paths', M)
 np.save(current_plotting_dir+'/interpolation_points', N)
+
+# start = time.time()
+# this_model.beta_likelihood_parallel(np.array((10,0.5)))
+# end = time.time()
+# print(end - start)
+
+# start = time.time()
+# this_model.beta_likelihood(np.array((10,0.5)))
+# end = time.time()
+# print(end - start)
 
 
 likelihood_evaluater(theta_array=theta_array,\
     alpha_array=alpha_array,\
     this_model=this_model,inference="beta_likelihood" , path_dir=current_plotting_dir )
-print(current_plotting_dir)
 
-#this_model.likelihood(np.array((10,0.11)))
-#this_model.likelihood(np.array((60,0.1)))
+
+print(current_plotting_dir)

### 2019-09-11 python_code/likelihood_explorer_new_importer.py

@@ -1,8 +1,22 @@
 import os
-os.chdir('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code')
+os.chdir('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code')
 from Base_plus import *
+
+orig_stdout = sys.stdout
+f = open('approx_lamperti_out.txt', 'w')
+sys.stdout = f
+
+def customwarn(message, category, filename, lineno, file=None, line=None):
+    sys.stdout.write(warnings.formatwarning(message, category, filename, lineno))
+
+warnings.showwarning = customwarn
+
+warnings.simplefilter("once")
+
+warnings.warn("test warning")
+
 #from multi_path_base import model_modified_drift
-forecast_data_in=np.load('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code/data/cleansed/URG_forecast_data_A_2018.npy')
+forecast_data_in=np.load('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code/data/cleansed/URG_forecast_data_A_2018.npy')
 now = dtM.datetime.now();
 current_time=now.strftime("%y-%m-%d-%H-%M-%S")
 script_name='likelihood_explorer'
@@ -12,30 +26,38 @@ os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
 forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
 
 N=forecast_data_inter.shape[2];N
-M=forecast_data_inter.shape[1]-500;M
+M=forecast_data_inter.shape[1]-1070;M
 dt=1
 dN=1/N;dN
-
+M
+N
 disct_temp = disct(N,dt,M)
-p=forecast_data_inter[2,:-500,:]  #240
-V= forecast_data_inter[2,:-500,:] -forecast_data_inter[1,:-500,:]
+p=forecast_data_inter[2,:-973,:]  #240
+V=forecast_data_inter[2,:-973,:] -forecast_data_inter[1,:-973,:]
 
 #plt.plot(p[105])
 #plt.plot(forecast_data_inter[1,105,:])
 #plt.plot(V[105,:])
 #X=forecast_data_inter[1,:-500,:]
 
-#Z = np.arcsin(2*X - 1)
+Z = np.arcsin(2*(forecast_data_inter[1,:-973,:]) - 1)
+
 
 #now for V
[…]

### 2019-09-11 python_code/likelihood_explorer_new_importer_3.py

@@ -1,0 +1,53 @@
+import os
+os.chdir('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code')
+from Base_plus import *
+
+orig_stdout = sys.stdout
+f = open('beta_out.txt', 'w')
+sys.stdout = f
+
+def customwarn(message, category, filename, lineno, file=None, line=None):
+    sys.stdout.write(warnings.formatwarning(message, category, filename, lineno))
+
+warnings.showwarning = customwarn
+
+warnings.simplefilter("once")
+
+#from multi_path_base import model_modified_drift
+forecast_data_in=np.load('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code/data/cleansed/URG_forecast_data_A_2018.npy')
+now = dtM.datetime.now();
+current_time=now.strftime("%y-%m-%d-%H-%M-%S")
+script_name='likelihood_explorer'
+current_plotting_dir='data/'+ script_name+'_' +current_time
+os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
+
+forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
+
+N=forecast_data_inter.shape[2];N
+M=forecast_data_inter.shape[1]-973;M
+dt=1
+dN=1/N;dN
+M
+N
+disct_temp = disct(N,dt,M)
+p=forecast_data_inter[2,:-973,:]  #240
+V=forecast_data_inter[2,:-973,:] -forecast_data_inter[1,:-973,:]
+
+
+this_model=model_modified_drift(disct_temp,V, forecast= p)
+
+
+
+theta_array=np.linspace(0.01, 25, 10)
+alpha_array=np.linspace(0.01, 2, 10)
+
+np.save(current_plotting_dir+'/num_paths', M)
+np.save(current_plotting_dir+'/interpolation_points', N)
+likelihood_evaluater(theta_array=theta_array,\
+    alpha_array=alpha_array,\
+    this_model=this_model,inference="beta_likelihood", path_dir=current_plotting_dir )
+print(current_plotting_dir)
+
+
+sys.stdout = orig_stdout
+f.close()

### 2019-09-22 LaTeX_code/presentation/DELFT_pres.tex
presntation,corrected paths

\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{lmodern}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

\setbeamertemplate{caption}[numbered]

\title{On the Uncertainty of Wind Power Generation}
\subtitle{ Waleed Alhaddad \ Raul Tempone \ Ahmad kebaier }

\begin{document}
\setbeamercolor{background canvas}{bg=blue!35}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}[label=guide]\frametitle{ Introduction }
Integration of renewable resources into the urban power grid is a challenge due to uncertainties in power production. We focus on wind power. Reliable wind power production forecasting is crucial to:
\begin{itemize}
\item \textbf{Optimization of the price of electricity} for different users such as electric utilities, Transmission system operator (TSOs), Electricity Service providers (ESPs), Independent power producers (IPPs), and energy traders.
\item \textbf{Allocation of energy reserves} such as water levels in dams or oil and gas reserves.
\item \textbf{Operation scheduling} of conventional power plants.
\item \textbf{Maintenance planning} such as that of power plants components and transmission lines.
\end{itemize}

\end{frame}

\begin{frame}\frametitle{Status quo }
  Wind power forecasts can be generally categorized as follows:
  \begin{itemize}
    \item physical models
    \item statistical methods
    \item artificial intelligence methods
    \item spatial correlation methods
    \item persistence models
    \item other hybrid approaches
  \end{itemize}
 The output of such methods is usually a \textbf{deterministic forecast}. Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles. However, little has been done in terms of producing \textbf{data driven probabilistic forecasts} based on real-world performance of forecasting models.
\end{frame}

\begin{frame}\frametitle{Data}
This is data from Uruguay based on \textbf{10 minute observation interval and 1000 paths}.
\begin{figure}
  \includegraphics[width=70mm,scale=1]{plots/data_1516064400.pdf}
  \includegraphics[width=70mm,scale=1]{plots/data_1516323600.pdf}\\
  \includegraphics[width=70mm,scale=1]{plots/data_1517619600.pdf}
  \includegraphics[width=70mm,scale=1]{plots/data_1529456400.pdf}
  % \caption{title}
\end{figure}
Have a better data set ? send it our way.
\end{frame}

\begin{frame}\frametitle{Data Skewness}
\begin{figure}
  \includegraphics[width=47.5mm,scale=1]{plots/hist_low.pdf}
  \includegraphics[width=50mm,scale=1]{plots/hist_mid.pdf}
  \includegraphics[width=50mm,scale=1]{plots/hist_high.pdf}
  % \caption{title}
\end{figure}
\end{frame}

\begin{frame}\frametitle{Model}
We wish to:
\begin{itemize}
  \item Generate a probabilistic forecast from a deterministic forecast.
  \item Capture the dynamics and correlation structure.
  \item Capture the skew nature of the process.
  \item Be forecasting technology agnostic. Thus, compatible with future forecasting technology.
  \item Learn from historical power production data.
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Model}
We propose to model wind power\textbf{ forecasts errors using parametric stochastic differential equations (SDEs)} whose solution defines a stochastic process. This resultant stochastic process describes the time evolution dynamics of wind power forecast errors.
\begin{equation}
\begin{split}
dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
X_0 & = X_0
\end{split}
\label{main}
\end{equation}

\begin{itemize}
\item $a(\cdot; \bm{\theta}):[0,1] \to \R $  a drift function.
\item $b (\cdot; \bm{\theta} ):[0,1] \to \R$  a  diffusion function.
\item $\bm{\theta}$: a vector of parameters.
\item $W_t$: Standard Wiener random process in $\R$.
\end{itemize}

Question: How do we choose an appropriate drift and diffusion functions ?

\end{frame}

\begin{frame}\frametitle{Model}
Answer:
\begin{enumerate}
  \item We want the process to follow the wind forecast, thus we choose a drift term that is mean reverting and tracks the derivative of the deterministic forecast $p$ which is an input to our model.
  \begin{equation}
    a(X_t; \bm{\theta})=  \dot{p} \ dt - \theta_t(X_t - p_t)
  \end{equation}
where $\theta_t$ is a time-dependent paramter that controls the speed of reversion.
  \item We want a diffusion term that vanishes at the boundries to prevent the process from escaping the region $[0,1]$.
  \begin{equation}
    b (\cdot; \bm{\theta} )= \sqrt{2 \theta_t \alpha x (1-x)}
  \end{equation}
  where $\alpha$ is a constant prameter that controls the path variability.

To further ensure that the process does not escape the region $[0,1]$, the mean reversion parameter has to be selected according to the following rule,
\begin{equation}
\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ) \label{theta_t}
\end{equation}

\end{enumerate}
\end{frame}

\begin{frame}\frametitle{Model}
Thus, our SDE becomes
\begin{equation}
\begin{split}
dX_t&= \dot{p}_t \ dt - \theta_t(X_t - p_t) \ dt + \sqrt{2 \theta_t \alpha x (1-x)}  \ dW_t \quad t > 0 \\
X_0&=x_0\\
\theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
\end{split}
\label{model:derivative_tracking_X}
\end{equation}
To avoid differentiation of the forecast $p_t$ and simplify, we apply a change of variables $$V_t = X_t - p_t$$ \\
The  model becomes,
\begin{equation}
\begin{split}
dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
V_0 & = v_0\\
\theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
\end{split}\label{VtSDE}
\end{equation}
Note that this model is Markovian.
\end{frame}

\begin{frame}\frametitle{Model}
Since $V_t$ defined by the SDE in (\ref{VtSDE}) is Markovian, the likelihood function can be written as product of transition densities.

\begin{equation}
\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}}, \bm{\theta})  \rho (V_{j,0})
\label{likelihood}
\end{equation}

The transition densities can be exactly obtained by solving the following parametric Fokker-Planck equation,

\begin{equation}
\begin{split}
\frac{ \partial f }{\partial t } & (y ,t | x , s, \theta_t, \alpha )= - \frac{\partial}{ \partial y} ( a( y;\dot{p}_t , p_t, \theta_t ) f( y ,t | x , s, \theta_t , \alpha ) ) \\
& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b(y;\theta_t, \alpha  )  f( y ,t | x , s, \theta_t , \alpha )  ) \quad  t < s\\
\end{split}
\end{equation}
This is a parametric PDE which computationally prohibitive to solve for every transition.
\end{frame}

\begin{frame}\frametitle{Moment Matching}
Instead of solving for exact transition densities by the Fokker-Planck, we propose a \textbf{proxy transition denisty}. A suitable candidate is a Beta transition density as it can morph into symmetric and asymetric shapes.

\begin{equation}
\begin{split}
\frac{d \E[ V^k_t]}{dt} = - k \theta_t \E [ V^k_t] + \frac{k(k-1)}{2} \E [ V^{k-2}_t  b(y;\theta_t, \alpha)]
\end{split}
\end{equation}

\end{frame}

\end{document}

### 2019-09-22 python_code/Urugauy_data_importer.py

@@ -1,16 +1,17 @@
 #%%
 import os
-os.chdir('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code')
+import sys
+os.chdir(sys.path[0])
 from data_cleansing import *
 #%%
 
-
 # %%
 #file paths
-forecast_A='/Users/alhaddwt/Google Drive/GitLab/wind-power/raw_data/Uruguay/wind/Wind_Data_2018_provider_A.csv'
-forecast_B='/Users/alhaddwt/Google Drive/GitLab/wind-power/raw_data/Uruguay/wind/Wind_Data_provider_B.csv'
-production_path='/Users/alhaddwt/Google Drive/GitLab/wind-power/raw_data/Uruguay/wind/anuales_gen_int_2018_10m_aggregated.csv'
+forecast_A='./raw_data/Uruguay/wind/Wind_Data_2018_provider_A.csv'
+forecast_B='./raw_data/Uruguay/wind/Wind_Data_provider_B.csv'
+production_path='./raw_data/Uruguay/wind/anuales_gen_int_2018_10m_aggregated.csv'
 #normalization_path='/Users/alhaddwt/Google Drive/GitLab/wind-power/raw_data/France/normalization_2019.txt'
+
 
 #import files
 d = pd.read_csv(production_path, delimiter= ',', header=2,  dtype=str)
@@ -69,7 +70,21 @@ forecast_data_A[:,1:,:]=np.abs(forecast_data_A[:,1:,:]/1500)
 np.max(forecast_data_A[:,1:,:])
 np.min(forecast_data_A[:,1:,:])
 
-plt.plot(forecast_data_A[640,2,:])
+
+path=56;
+
+fig=plt.figure(2,figsize=(10, 4))
+plt.plot(get_datetime64( forecast_data_A[path,0,:]   ), forecast_data_A[path,1,:] , label='data'  )
+plt.plot(get_datetime64( forecast_data_A[path,0,:]   ), forecast_data_A[path,2,:], label='forecast'   )
+plt.ylim(-0.1, 1.1)
+plt.xticks( fontsize = 15);
+plt.yticks( fontsize = 20);
+plt.xlabel('Time [hr]',fontsize = 24)
+plt.ylabel('Normalized Power',fontsize = 24)
+plt.legend( prop={'size': 20})
+plt.savefig('data_' + str(int(forecast_data_A[path,0,0]))+'.pdf',bbox_inches="tight")
+
+
[…]

### 2019-09-24 LaTeX_code/presentation/DELFT_pres.tex
added lampert, fixed optimization holes

@@
 \usepackage{lmodern}
+\usepackage{algorithm2e}
 
@@
 \title{On the Uncertainty of Wind Power Generation}
-\subtitle{ Waleed Alhaddad \ Raul Tempone \ Ahmad kebaier }
+% \subtitle{ Waleed Alhaddad \ Raul Tempone \ Ahmad kebaier }
+
+\author{ Waleed Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\  \vskip 0.2in
+\textsuperscript{\textasteriskcentered}CEMSE Division, KAUST , Saudi Arabia
+ \\ \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539) , France  \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University,  Germany}
 
 \begin{document}
-\setbeamercolor{background canvas}{bg=blue!35}
+\setbeamercolor{background canvas}{bg=blue!10}
 
@@
 Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles.
-However, little has been done in terms of producing \textbf{data driven probabilistic forecasts} based on real-world performance of forecasting models.
+However, little has been done in terms of producing \textbf{data driven probabilistic forecasts} based on the real-world performance of forecasting models.
 \end{frame}
@@
 \begin{frame}\frametitle{Data}
-This is data from Uruguay based on \textbf{10 minute observation interval and 1000 paths}.
+This is a year long data set from Uruguay based on \textbf{10 minute observation interval of one thousand 72-hour paths} (2018).
 \begin{figure}
@@
 \end{figure}
-Have a better data set ? send it our way.
+% Do you have more data? send it our way.
 \end{frame}
@@
   \includegraphics[width=50mm,scale=1]{plots/hist_high.pdf}
-  % \caption{title}
+  \caption{We see that forecast errors exhibit skewness near the boundries (i.e. low and high power production regimes.)}
 \end{figure}
@@
 \begin{frame}\frametitle{Model}
-We wish to:
+Our goals are to
 \begin{itemize}
-  \item Generate a probabilistic forecast from a deterministic forecast.
+  \item Generate a probabilistic forecast centered around a given deterministic forecast, i.e. unbiased with respect to the deterministic forecast.
   \item Capture the dynamics and correlation structure.
-  \item Capture the skew nature of the process.
+  \item Capture the skew nature of forecast errors.
   \item Be forecasting technology agnostic. Thus, compatible with future forecasting technology.
@@
 
-Question: How do we choose an appropriate drift and diffusion functions ?
+Question: How do we choose an appropriate drift and diffusion functions?
 
@@
 \begin{enumerate}
-  \item We want the process to follow the wind forecast, thus we choose a drift term that is mean reverting and tracks the derivative of the deterministic forecast $p$ which is an input to our model.
+  \item We want the process to follow the wind forecast, thus we choose a drift term that is mean reverting and tracks the derivative of the deterministic forecast $p$, which is an input to our model.
   \begin{equation}
@@
 where $\theta_t$ is a time-dependent paramter that controls the speed of reversion.
-  \item We want a diffusion term that vanishes at the boundries to prevent the process from escaping the region $[0,1]$.
+  \item We want a diffusion term that vanishes at the boundaries to prevent the process from escaping the region $[0,1]$.
   \begin{equation}
@@
 \end{equation}
-
 \end{enumerate}
@@
 X_0&=x_0\\
-\theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
+% \theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
 \end{split}
@@
 V_0 & = v_0\\
-\theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
+% \theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
 \end{split}\label{VtSDE}
@@
 \begin{frame}\frametitle{Model}
-Since $V_t$ defined by the SDE in (\ref{VtSDE}) is Markovian, the likelihood function can be written as product of transition densities.
+Since $V_t$ defined by our SDE is Markovian, the likelihood function can be written as a product of transition densities.
 
@@
 \end{equation}
-This is a parametric PDE which computationally prohibitive to solve for every transition.
+This is a parametric PDE which is computationally prohibitive to solve and optimize for every transition.
 \end{frame}
@@
 Instead of solving for exact transition densities by the Fokker-Planck, we propose a \textbf{proxy transition denisty}.
-A suitable candidate is a Beta transition density as it can morph into symmetric and asymetric shapes.
+We match the moments of our SDE model with that of the proxy density.
+Using Ito, we arrive at the following iterative ODEs.
 
@@
 \end{equation}
+For the first two moments, we obtain
+\begin{equation}
+\begin{split}
+\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t \\
+\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta(1+\alpha) + 2\alpha\theta m_1(t)(1-2p_t) + 2 \alpha\theta p_t (1-p_t)\\
+\end{split}
+\end{equation}
+
+ A suitable candidate is a Beta transition density as it is compactly supported and can morph into symmetric and asymmetric shapes.
 
@@
 
+\begin{frame}\frametitle{Algorithm}
+
+Execute the following until an accuracy threshold is met:
+\begin{enumerate}
+\item initialize.
+\item optimize the log-likelihood function.
+\begin{enumerate}
+\item For every evaluation of the log-liklihood function:
+\begin{enumerate}
+  \item Sample a batch of transitions and their associated forecast and parameters.
+  \item Solve the ODE system for every transition.
+  \item Match the resulting moments with the parameters of the chosen proxy distribution for every transition.
+\end{enumerate}
+\end{enumerate}
+\item go to step 1 (i.e. re-initialize the optimization with the most recent result ).
+\end{enumerate}
+
+Notes:
+\begin{itemize}
+\item Choose your favorite deterministic optimization algorithm.
+\item Choose your favorite integrator to solve the ODE system.
+\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Inference Results}
+Here we show the convergence path of the optimization in 2D, the likelihood in 3D and rate of the shrinking ellipses in one slide.
+\end{frame}
+
+\begin{frame}\frametitle{Simulation and Confidence Bands}
+Here we show simulated future wind power production and another plot with confidence bands.
+\end{frame}
+
+\begin{frame}\frametitle{State-Independent model}
+The model we have demostrated previously is state-dependent, that is the diffusion of the SDE depends on the state.
+\begin{equation}
+\begin{split}
+dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
+V_0 & = v_0\\
+\end{split}\label{VtSDE}
+\end{equation}
+
+Why are we interested in a state-independent model? Because it's more tractable.\\
+We apply a \textbf{Lamperti transform} to obtain the following state-independent system,
+
+\begin{equation}
+  \begin{split}
+    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} + \sqrt{2 \alpha \theta_t} dW_t \\
+    Z_0&=z_0
+  \end{split}
+\end{equation}
+where $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
+\end{frame}
+
+\begin{frame}\frametitle{Data Skewness after Lamperti transformation}
+As stated before, the state-independent SDE follows a Lamperti transformed process $Z_t$ give by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
+\begin{figure}
+  \includegraphics[width=50mm,scale=1]{plots/hist_low_lamperti.pdf}
+  \includegraphics[width=50mm,scale=1]{plots/hist_mid_lamperti.pdf}
+  \includegraphics[width=50mm,scale=1]{plots/hist_high_lamperti.pdf}
+  \caption{We observe that most of the skewness has been removed after the lamperti transformation. This motivates us to use a Gaussian transition density as a proxy denisty.}
+\end{figure}
+\end{frame}
+
+\begin{frame}\frametitle{State-Independent model}
+Similarly, we try to obtain a system of ODEs to determine the centered moments of the Lamperti transformed process $V_t$.
+Due to the non-linearity in the drift, we can only approximate the centered moments by the following ODEs,
+\begin{equation}
+\begin{split}
+\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\alpha) - \theta (1-2 p_t) \\
+\frac{d v(t)}{dt} &=  2 v(t) \theta_t (2p_t - 1 ) \tan(x) \sec(x) + \theta_t (\alpha - 1) \sec^2(x)  + 2 \theta_t \alpha\\
+\end{split}
+\end{equation}
+These are not exact moment ODEs, however they are good enough for small time intervals.
+\end{frame}
+
+\begin{frame}\frametitle{Inference Results}
+Here we show the convergence path of the optimization in 2D, the likelihood in 3D and rate of the shrinking ellipses in one slide.
+\end{frame}
+
+\begin{frame}\frametitle{Simulation and Confidence Bands}
+Here we show simulated future wind power production and another plot with confidence bands.
+\end{frame}
+
+\begin{frame}\frametitle{Model comparison}
+\begin{table}[]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+Model   &  parameters $(\theta_0, \alpha)$   & AIC & BIC \\ \hline
+state-dependent &   (,)  &     &      \\ \hline
+state-independent &   (,)  &     &       \\ \hline
+\end{tabular}
+\caption{We compare the two models based on information criterion here.... }
+\label{tab:model_comparison}
+\end{table}
+\end{frame}
+
+\begin{frame}\frametitle{Concluding remarks}
+We were able to:
+\begin{itemize}
+  \item simulate future wind power production based on real data.
+  \item have an analytical description of the uncertainty of wind power forecasts in the form of an SDE.
+  \item develop a forecasting technology agnostic method.
+  \item capture skewness of the error process and its correlation structure.
+\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{References}
+\begin{itemize}
+  \item source
+  \item source
+  \item source
+\end{itemize}
+\end{frame}
+
 \end{document}

### 2019-09-24 python_code/skew_test_quantiles_10m.py

@@ -91,14 +91,14 @@ probplot(R[P.flatten()<0.3], plot=plt)
 
 
 R[P.flatten()>0.6].shape
-plt.hist(R[P.flatten()>0.6],20,density=True)
+plt.hist(R[P.flatten()>0.7],20,density=True)
 plt.xticks( fontsize = 15);
 plt.yticks( fontsize = 20);
 plt.xlabel('Forecast Error',fontsize = 20)
 # plt.ylabel('Number of Incident',fontsize = 20)
 # plt.legend( prop={'size': 20})
 plt.title('High Power Range' ,fontsize=24)
-plt.savefig('hist_low.pdf',bbox_inches="tight")
+plt.savefig('hist_high.pdf',bbox_inches="tight")
 
 
 
@@ -106,7 +106,14 @@ plt.savefig('hist_low.pdf',bbox_inches="tight")
 probplot(R[P.flatten()>0.6], plot=plt)
 
 R[(P.flatten()>=0.4)   & (P.flatten()<=0.6)].shape
-plt.hist(R[ (P.flatten()>=0.4)   & (P.flatten()<=0.6)],20,density=True)
+plt.hist(R[ (P.flatten()>=0.3)   & (P.flatten()<=0.7)],20,density=True)
+plt.xticks( fontsize = 15);
+plt.yticks( fontsize = 20);
+plt.xlabel('Forecast Error',fontsize = 20)
+# plt.ylabel('Number of Incident',fontsize = 20)
+# plt.legend( prop={'size': 20})
+plt.title('Mid Power Range' ,fontsize=24)
+plt.savefig('hist_mid.pdf',bbox_inches="tight")
 
 probplot(R[(P.flatten()>=0.4)   & (P.flatten()<=0.6)], plot=plt)
 
@@ -122,17 +129,41 @@ plt.hist(Q,20,density=True)
 probplot(Q, plot=plt)
 
 
-Q[P.flatten()<0.35].shape
-plt.hist(Q[P.flatten()<0.35],20,density=True)
+Q[P.flatten()<0.30].shape
+plt.hist(Q[P.flatten()<0.30],20,density=True)
+plt.xticks( fontsize = 15);
+plt.yticks( fontsize = 20);
+plt.xlabel('Forecast Error',fontsize = 20)
+# plt.ylabel('Number of Incident',fontsize = 20)
+# plt.legend( prop={'size': 20})
[…]

### 2019-10-01 LaTeX_code/presentation/DELFT_pres.tex
lamperti optimization adjustment

@@
 \title{On the Uncertainty of Wind Power Generation}
-% \subtitle{ Waleed Alhaddad \ Raul Tempone \ Ahmad kebaier }
 
 \author{ Waleed Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\  \vskip 0.2in
-\textsuperscript{\textasteriskcentered}CEMSE Division, KAUST , Saudi Arabia
- \\ \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539) , France  \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University,  Germany}
+\textsuperscript{\textasteriskcentered}CEMSE Division, KAUST, Saudi Arabia \vskip 0.05in  \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539) , France\vskip 0.05in  
+ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen  University,  Germany}
 
@@
 \setbeamercolor{background canvas}{bg=blue!10}
+\date{}
 
@@
 \titlepage
+\center
+  \includegraphics[width=40mm,scale=1]{KAUST_Logo.pdf}\quad 
+  \includegraphics[width=60mm,scale=1]{rwth_UQ.png}\quad 
+  \includegraphics[width=40mm,scale=1]{UParis_13.png} \quad
 \end{frame}
@@
     \item spatial correlation methods
-    \item persistence models
     \item other hybrid approaches
   \end{itemize}
- The output of such methods is usually a \textbf{deterministic forecast}.
+ The output of such methods is usually a \textcolor{red}{deterministic forecast}.
 Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles.
-However, little has been done in terms of producing \textbf{data driven probabilistic forecasts} based on the real-world performance of forecasting models.
+However, little has been done in terms of producing \textcolor{red}{data driven probabilistic forecasts} based on the real-world performance of forecasting models.
 \end{frame}
@@
 \begin{frame}\frametitle{Data}
-This is a year long data set from Uruguay based on \textbf{10 minute observation interval of one thousand 72-hour paths} (2018).
+This is a year long data set from Uruguay based on \textbf{1000 72-hour long paths of observations every 10 min \textcolor{red}{ ($\sim$ half a million data points)}} recorded in 2018.
 \begin{figure}
@@
   \includegraphics[width=50mm,scale=1]{plots/hist_high.pdf}
-  \caption{We see that forecast errors exhibit skewness near the boundries (i.e. low and high power production regimes.)}
+  \caption{We see that forecast errors exhibit \textcolor{red}{skewness} near the boundries (i.e. low and high power production regimes.)}
 \end{figure}
@@
 \begin{frame}\frametitle{Model}
-We propose to model wind power\textbf{ forecasts errors using parametric stochastic differential equations (SDEs)} whose solution defines a stochastic process.
+We propose to model wind power forecasts errors using \textcolor{red}{parametric stochastic differential equations (SDEs)} whose solution defines a stochastic process.
 This resultant stochastic process describes the time evolution dynamics of wind power forecast errors.
@@
 \begin{split}
-dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
-X_0 & = X_0
+dX_t &= a(X_t; p_t,\bm{\theta}) dt + b (X_t;p_t, \bm{\theta} ) dW_t \quad t > 0 \\
+X_0 & = x_0
 \end{split}
@@
 \item $\bm{\theta}$: a vector of parameters.
+\item $p_t$ time-dependent scalar value.
 \item $W_t$: Standard Wiener random process in $\R$.
@@
 
-Question: How do we choose an appropriate drift and diffusion functions?
+\textcolor{blue}{Question: How do we choose an appropriate drift and diffusion functions?}
 
@@
 \begin{frame}\frametitle{Model}
-Answer:
+\textcolor{blue}{Answer:}
+Let $\bm{\theta} = (\textcolor{red}{\theta_0}, \textcolor{red}{\alpha})$
 \begin{enumerate}
-  \item We want the process to follow the wind forecast, thus we choose a drift term that is mean reverting and tracks the derivative of the deterministic forecast $p$, which is an input to our model.
+  \item We want the process to follow the wind forecast, thus we choose a drift term that is mean reverting and tracks the derivative of the deterministic forecast $p_t$, which is an input to our model.
   \begin{equation}
-    a(X_t; \bm{\theta})=  \dot{p} \ dt - \theta_t(X_t - p_t)
+    a(x; \bm{\theta})=  \dot{p_t} - \theta_t(x - p_t)
   \end{equation}
-where $\theta_t$ is a time-dependent paramter that controls the speed of reversion.
+where $\theta_t$ is a time-dependent parameter that controls the speed of reversion.
   \item We want a diffusion term that vanishes at the boundaries to prevent the process from escaping the region $[0,1]$.
   \begin{equation}
-    b (\cdot; \bm{\theta} )= \sqrt{2 \theta_t \alpha x (1-x)}
+    b (x; \bm{\theta} )= \sqrt{2 \theta_t \textcolor{red}{\textcolor{red}{\alpha}} x (1-x)}
   \end{equation}
-  where $\alpha$ is a constant prameter that controls the path variability.
+  where $\textcolor{red}{\alpha}$ is a constant parameter that controls the path variability.
 
@@
 \begin{equation}
-\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ) \label{theta_t}
+\theta_t = \max \left( \textcolor{red}{\theta_0} \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ) \label{theta_t}
 \end{equation}
@@
 \begin{split}
-dX_t&= \dot{p}_t \ dt - \theta_t(X_t - p_t) \ dt + \sqrt{2 \theta_t \alpha x (1-x)}  \ dW_t \quad t > 0 \\
+dX_t&= \dot{p}_t \ dt - \theta_t(X_t - p_t) \ dt + \sqrt{2 \theta_t \textcolor{red}{\alpha} X_t (1-X_t)}  \ dW_t \quad t > 0 \\
 X_0&=x_0\\
-% \theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
+% \theta_t &= \max \left( \textcolor{red}{\theta_0} \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
 \end{split}
@@
 \begin{split}
-dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
+dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \textcolor{red}{\alpha} (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
 V_0 & = v_0\\
-% \theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
+% \theta_t &= \max \left( \textcolor{red}{\theta_0} \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
 \end{split}\label{VtSDE}
 \end{equation}
-Note that this model is Markovian.
+Note that this model is \textcolor{red}{Markovian.}
 \end{frame}
@@
 \begin{frame}\frametitle{Model}
-Since $V_t$ defined by our SDE is Markovian, the likelihood function can be written as a product of transition densities.
+Since $V_t$ defined by our SDE is Markovian, the \textcolor{red}{ likelihood function can be written as a product of transition densities}.
+Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed in intervals of $\Delta_N$.
 
@@
 \begin{split}
-\frac{ \partial f }{\partial t } & (y ,t | x , s, \theta_t, \alpha )= - \frac{\partial}{ \partial y} ( a( y;\dot{p}_t , p_t, \theta_t ) f( y ,t | x , s, \theta_t , \alpha ) ) \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b(y;\theta_t, \alpha  )  f( y ,t | x , s, \theta_t , \alpha )  ) \quad  t < s\\
+\frac{ \partial f }{\partial t } & (y ,t | x , s, \theta_t, \textcolor{red}{\alpha} )= - \frac{\partial}{ \partial y} ( a( y;\dot{p}_t , p_t, \theta_t ) f( y ,t | x , s, \theta_t , \textcolor{red}{\alpha} ) ) \\
+& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b(y;\theta_t, \textcolor{red}{\alpha}  )  f( y ,t | x , s, \theta_t , \textcolor{red}{\alpha} )  ) \quad  t < s\\
 \end{split}
 \end{equation}
-This is a parametric PDE which is computationally prohibitive to solve and optimize for every transition.
+This is a parametric PDE which is \textcolor{red}{computationally expensive to solve} and optimize for every transition.
 \end{frame}
@@
 \begin{frame}\frametitle{Moment Matching}
-Instead of solving for exact transition densities by the Fokker-Planck, we propose a \textbf{proxy transition denisty}.
+Instead of solving for exact transition densities by the Fokker-Planck, we propose a \textcolor{red}{proxy transition density}.
 We match the moments of our SDE model with that of the proxy density.
@@
 \begin{split}
-\frac{d \E[ V^k_t]}{dt} = - k \theta_t \E [ V^k_t] + \frac{k(k-1)}{2} \E [ V^{k-2}_t  b(y;\theta_t, \alpha)]
+\frac{d \E[ V^k_t]}{dt} = - k \theta_t \E [ V^k_t] + \frac{k(k-1)}{2} \E [ V^{k-2}_t  b(V^k_t;\theta_t, \textcolor{red}{\alpha})]
 \end{split}
 \end{equation}
-For the first two moments, we obtain
+For $t\in [t_{n-1}, t]$, the first two moments are given by
 \begin{equation}
@@
 \frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t \\
-\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta(1+\alpha) + 2\alpha\theta m_1(t)(1-2p_t) + 2 \alpha\theta p_t (1-p_t)\\
+\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta(1+\textcolor{red}{\alpha}) + 2\textcolor{red}{\alpha}\theta_t m_1(t)(1-2p_t) + 2 \textcolor{red}{\alpha}\theta_t p_t (1-p_t)\\
 \end{split}
 \end{equation}
+with initial conditions, $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2$ where $t_{n-1}$ is the time of the previous obseravtion and $v_{n-1}$ is its value.
 
- A suitable candidate is a Beta transition density as it is compactly supported and can morph into symmetric and asymmetric shapes.
+ A suitable candidate is a \textcolor{red}{Beta transition } density as it is compactly supported and can morph into symmetric and asymmetric shapes.
 
@@
 \begin{enumerate}
-\item initialize.
-\item optimize the log-likelihood function.
+\item \textcolor{red}{initialize}.
+\item \textcolor{red}{optimize} the log-likelihood function.
 \begin{enumerate}
@@
 \begin{enumerate}
-  \item Sample a batch of transitions and their associated forecast and parameters.
-  \item Solve the ODE system for every transition.
-  \item Match the resulting moments with the parameters of the chosen proxy distribution for every transition.
+  \item \textcolor{red}{Sample} a random mini-batch of transitions and their associated forecast and parameters.
+  \item \textcolor{red}{Solve} the ODE system for every transition to obtain the moments.
+  \item \textcolor{red}{Match} the resulting moments with the parameters of the chosen proxy distribution for every transition.
 \end{enumerate}
 \end{enumerate}
-\item go to step 1 (i.e. re-initialize the optimization with the most recent result ).
+\item go to step 1 (i.e. \textcolor{red}{re-initialize} the optimization with the most recent result ).
 \end{enumerate}
 
-Notes:
+In the above:
 \begin{itemize}
@@
 \begin{frame}\frametitle{Inference Results}
-Here we show the convergence path of the optimization in 2D, the likelihood in 3D and rate of the shrinking ellipses in one slide.
+% Here we show the convergence path of the optimization in 2D, the likelihood in 3D and rate of the shrinking ellipses in one slide.
+
+\begin{figure}
+  \includegraphics[width=110mm,scale=1]{plots/beta_likeli_3d.pdf}
+  \caption{3-D view of the \textcolor{red}{inverted beta log-likelihood}  function of 100 sample paths. That is a total of  \textcolor{red}{ $\sim 42,700$ data points }}
+\end{figure}
 \end{frame}
 
-\begin{frame}\frametitle{Simulation and Confidence Bands}
-Here we show simulated future wind power production and another plot with confidence bands.
+\begin{frame}\frametitle{Inference Results}
+\begin{figure}
+  \includegraphics[width=70mm,scale=1]{plots/alpha_conv_beta.pdf}
+  \includegraphics[width=70mm,scale=1]{plots/theta_conv_beta.pdf}
+  \caption{We have \textcolor{red}{self-convergence} of our algorithm at a rate that matches the convergence rate of Monte Carlo.}
+\end{figure}
+\end{frame}
+
+\begin{frame}\frametitle{Future Wind Power Simulation}
+    \begin{figure}
+      \includegraphics[width=75mm,scale=1]{simulated/24hr/1099.pdf}
+      \includegraphics[width=75mm,scale=1]{simulated/24hr/1178.pdf}
+      \caption{We simulate five possible future wind power production paths using the obtain optimal parameters $(\textcolor{red}{\theta_0}, \textcolor{red}{\alpha} )=(12,0.3)$ }
+    \end{figure}
+\end{frame}
+
+\begin{frame}\frametitle{Confidence Bands}
+    \begin{figure}
+      \includegraphics[width=75mm,scale=1]{confidence_intervals/24hr/31.pdf}
+      \includegraphics[width=75mm,scale=1]{confidence_intervals/24hr/820.pdf}
+       \caption{We obtain confidence intervals for future wind power production using the obtain optimal parameters $(\textcolor{red}{\theta_0}, \textcolor{red}{\alpha} )=(12,0.3)$.
+Actual production plotted in retrospect.
+}
+    \end{figure}
 \end{frame}
@@
 \begin{frame}\frametitle{State-Independent model}
-The model we have demostrated previously is state-dependent, that is the diffusion of the SDE depends on the state.
+The model we have demonstrated previously is state-dependent, that is the diffusion of the SDE depends on the state.
 \begin{equation}
 \begin{split}
-dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
+dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \textcolor{red}{\alpha} (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
 V_0 & = v_0\\
@@
   \begin{split}
-    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} + \sqrt{2 \alpha \theta_t} dW_t \\
+    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \textcolor{red}{\alpha} \theta_t \sin (Z_t)   }{\cos (Z_t)} + \sqrt{2 \textcolor{red}{\alpha} \theta_t} dW_t \\
     Z_0&=z_0
@@
   \includegraphics[width=50mm,scale=1]{plots/hist_high_lamperti.pdf}
-  \caption{We observe that most of the skewness has been removed after the lamperti transformation. This motivates us to use a Gaussian transition density as a proxy denisty.}
+  \caption{We observe that skewness has been greatly reduced after the Lamperti transformation. This motivates us to use a \textcolor{red}{Gaussian transition} density as a proxy density.}
 \end{figure}
@@
 \begin{split}
-\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\alpha) - \theta (1-2 p_t) \\
-\frac{d v(t)}{dt} &=  2 v(t) \theta_t (2p_t - 1 ) \tan(x) \sec(x) + \theta_t (\alpha - 1) \sec^2(x)  + 2 \theta_t \alpha\\
+\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\textcolor{red}{\alpha}) - \theta (1-2 p_t) \\
+\frac{d v(t)}{dt} &=  2 v(t) \theta_t (2p_t - 1 ) \tan(x) \sec(x) + \theta_t (\textcolor{red}{\alpha} - 1) \sec^2(x)  + 2 \theta_t \textcolor{red}{\alpha}\\
 \end{split}
 \end{equation}
-These are not exact moment ODEs, however they are good enough for small time intervals.
+These are not exact moment ODEs, however they are accurate enough for small time intervals.
 \end{frame}
@@
 \begin{frame}\frametitle{Inference Results}
-Here we show the convergence path of the optimization in 2D, the likelihood in 3D and rate of the shrinking ellipses in one slide.
-\end{frame}
-
-\begin{frame}\frametitle{Simulation and Confidence Bands}
-Here we show simulated future wind power production and another plot with confidence bands.
+\begin{figure}
+  \includegraphics[width=70mm,scale=1]{plots/alpha_conv_beta.pdf}
+  \includegraphics[width=70mm,scale=1]{plots/theta_conv_beta.pdf}
+    \caption{We have self-convergence of our algorithm in the Lamperti space at a rate that matches the convergence rate of Monte Carlo.}
+\end{figure}
 \end{frame}
@@
 \centering
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|}
 \hline
-Model   &  parameters $(\theta_0, \alpha)$   & AIC & BIC \\ \hline
-state-dependent &   (,)  &     &      \\ \hline
-state-independent &   (,)  &     &       \\ \hline
+Model   &  parameters $(\textcolor{red}{\theta_0}, \textcolor{red}{\alpha})$    \\ \hline
+state-dependent &   (12,0.3)    \\ \hline
+state-independent &   (14,0.29)     \\ \hline
 \end{tabular}
-\caption{We compare the two models based on information criterion here.... }
+\caption{We compare the parameters obtain in both the original and Lamperti space. }
 \label{tab:model_comparison}
@@
   \item simulate future wind power production based on real data.
-  \item have an analytical description of the uncertainty of wind power forecasts in the form of an SDE.
+  \item obtain an analytical description of the uncertainty of wind power forecasts in the form of an SDE.
   \item develop a forecasting technology agnostic method.
@@
 \begin{frame}\frametitle{References}
+
+\section*{References}
+\begin{flushleft}
 \begin{itemize}
-  \item source
-  \item source
-  \item source
+\item Alhaddad, W. ,  Kebaier, A. , \& Tempone, R. (2019). Stochastic Wind Power Forecasting. Coming soon to  arXiv.
+\item  M\o ller, J.
+K., Zugno, M., \& Madsen, H.
+(2016).
+Probabilistic Forecasts of Wind Power Generation by Stochastic Differential Equation Models.
+Journal of Forecasting, 35(3), 189-205.
+doi:10.1002/for.2367
+\item  Elkantassi, S., Kalligiannaki, E., \& Tempone, R.
+(2017).
+Inference And Sensitivity In Stochastic Wind Power Forecast Models.
+Proceedings of the 2nd International Conference on Uncertainty Quantification in Computational Sciences and Engineering (UNCECOMP 2017).
+doi:10.7712/120217.5377.16899
+\item Giebel, G., Brownsword, R., Kariniotakis, G., Denhard, M., \& Draxl, C.
+(2011).
+The State-Of-The-Art in Short- Term Prediction of Wind Power: A Literature Overview, 2nd edition.
+ANEMOS.plus.
+https://doi.org/10.11581/DTU:00000017
+\item Chang, W.-Y. (2014) A Literature Review of Wind Forecasting Methods. Journal of Power and Energy Engineering, 2, 161-168. http://dx.doi.org/10.4236/jpee.2014.24023
 \end{itemize}
+\end{flushleft}
+
 \end{frame}

### 2019-10-07 python_code/Base_plus.py
finalized presentation delft

@@ -1856,6 +1856,7 @@ def empirical_Confidence_Interval_plots(forecast_data_inter,hours,\
     if isinstance(hours, int)==False:
         raise ValueError('hours is not an integer. Please use integer values only.')
     os.makedirs(dir_path + '/'+str(hours)+'hr',exist_ok=True)
+    os.makedirs(dir_path + '/'+'data_plots',exist_ok=True)
     N=disct_in.N
     freq=(N+1)*1 # evert 10 minutes
     #interpolation_points=disct_in.N
@@ -1875,29 +1876,29 @@ def empirical_Confidence_Interval_plots(forecast_data_inter,hours,\
     alpha= real_in.sigma #1.072
     j=0
     for k in list_forecast_number: #   #range(0,n_paths): #n_paths
-        p=forecast_data_inter[0,k,:N] #obtain cleansed forecast
+        p=forecast_data_inter[2,k,:N] #obtain cleansed forecast
         inter_1=interpolate.interp1d(x, p, fill_value='extrapolate')
         p=inter_1(xnew)
         d=forecast_data_inter[1,k,:N]
-        dt_object = dtM.datetime.fromtimestamp(forecast_data_inter[2,k,0])
+        dt_object = dtM.datetime.fromtimestamp(forecast_data_inter[0,k,0])
         dt=1
         M_test=disct_in.M
 
-        # fig=plt.figure(2,figsize=(10, 4))
-        # fig.clf()
-        # plt.plot(xnew,p, label='forecast')
-        # plt.plot(xnew,d, label='actual production')
-        #
-        # plt.xlim(1, 73)
-        # plt.ylim(-0.1, 1.1)
-        # plt.title('{:%d, %b %Y (%H:%M)}'.format(dt_object),fontsize=24)#,fontsize=24
-        #
-        # plt.xticks( fontsize = 20);
-        # plt.yticks( fontsize = 20);
-        # plt.xlabel('Time [hr]',fontsize = 24)
-        # plt.ylabel('Power',fontsize = 24)
-        # plt.legend( prop={'size': 15})
-        # plt.savefig('Forecast_data_'+ str(k)+'.pdf', bbox_inches="tight")
+        fig=plt.figure(2,figsize=(10, 4))
+        fig.clf()
+        plt.plot(xnew,p, label='forecast')
[…]

### 2019-10-07 python_code/fit_model_testing.py

@@ -1,6 +1,6 @@
 import os
 import sys
-os.chdir(sys.path[0])
+os.chdir(sys.path[0]) #+'/python_code'
 from Base_plus import *
 import config.loadconfig
 import argparse
@@ -16,7 +16,6 @@ from shutil import copyfile
 #Warning control
 warnings.filterwarnings('error', '.*invalid value encountered.*',)
 
-
 parser = argparse.ArgumentParser(description='Likelihood Evaluator v1.0')
 parser.add_argument('-filename', help=' Config file name or path')
 parser.add_argument('--version', action='version', version='Likelihood Evaluator v1.0')
@@ -24,7 +23,7 @@ args = parser.parse_args()
 
 print( ' loading configuration ')
 #args.filename
-config_file= open('config/approx_lamperti_config_test.JSON')  #config/beta_config.JSON
+config_file= open('config/beta_config_test.JSON')  #config/beta_config.JSON
 
 
 setup=config.loadconfig.Test(config_file)
@@ -84,7 +83,7 @@ now = dtM.datetime.now();
 current_time=now.strftime("%y-%m-%d-%H-%M-%S")
 script_name='fit_SDE'
 current_data_dir= script_name +current_time
-os.mkdir(current_data_dir)
+os.makedirs(current_data_dir,exist_ok=True)
 
 forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
 print('Data output will be save in ',current_data_dir)
@@ -120,6 +119,7 @@ file_object  = open(current_data_dir+'/results.out', 'w')
 
 copyfile('config/beta_config_test.JSON', current_data_dir + '/beta_config_test.JSON' )
 
+# width,height,angle, eig_vect_opt,Hess, FAIL = this_model.compute_ellipse(inference=setup.likelihood, param=(12, 0.4 ), batch_size=10 , plot=False);
 
 
 #initialize parameters

### 2019-10-07 python_code/likelihood_ISO_plotter.py

@@ -29,7 +29,7 @@ data_path=base_path+chosen_folder
 
 #plotting chosen_folder
 
-os.mkdir('plots/'+chosen_folder)
+os.makedirs('plots/'+chosen_folder, exist_ok=True)
 
 Z=np.load(data_path+'/value.npy')
 X=np.load(data_path+'/theta.npy')

### 2019-10-08 LaTeX_code/paper/paper.tex
paper update

@@
 \item Allocation of energy reserves such as water levels in dams or oil and gas reserves.
-\item Operation scheduling of conventional power plants.
-\item Optimization of the price of electricity for different users such as electric utilities, Transmission system operator (TSOs), Electricity Service providers (ESPs), Independent power producers (IPPs), and energy traders.
+\item Operation scheduling of non-controlable power plants.
+\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity Service providers (ESPs), Independent power producers (IPPs), and energy traders.
 \item Maintenance planning such as that of power plants components and transmission lines.
@@
 Different methods have been applied to wind power forecasting.
-They can be generally categorized as follows: physical models, statistical methods, artificial intelligence methods, persistence models, spatial correlation methods and hybrid approaches.
+They can be generally categorized as follows: physical models, statistical methods, artificial intelligence methods and hybrid approaches.
 The output of such methods is usually a deterministic forecast.
 Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles.
-However, little has been done in terms of producing data driven probabilistic forecasts based on real-world performance of forecasting models.
-It is crucial to capture actual performance of a forecast as it has been known that a given forecasting technology exhibits different behavior for different wind farms and seasons [ref].
-This is due to many factors which forecast are challenged to capture such as the surrounding terrains of the wind farm and the condition of the blades such as icing or dirt.
-It is known that complex terrains decrease the accuracy of wind power forecasts significantly [ref].
+However, there is a lacking in simulating and producing data driven stochastic forecasts based on real-world performance of forecasting models.
+It is crucial to capture actual performance of a forecast as it has been known that different forecasting technologies exhibits different behavior for different wind farms and seasons [ref].
+This is due to many factors which forecast are challenged to capture such as the surrounding terrains of the wind farm and the condition of the blades such as icing,wear and tear or dirt.
+It is known that complex terrains in both off shore and on shore locations decrease the accuracy of wind power forecasts significantly [ref].
 It also has been shown that the performance of forecasts varies from month to month.
@@
 
-Many approaches have been taken to evaluate the performance of a given forecast.
+Many approaches have been taken to evaluate the uncertainty of a given forecast.
 There are two types of errors: level errors and phase errors.
 The use of mean or median errors in this context may be misleading as wind power forecast errors are asymmetric.
-This is a natural consequence of wind power being non-negative.
+This is a natural consequence of wind power being non-negative and bounded by the maximuim capacity of production.
 This is important as the associated cost to power forecast errors are also asymmetric due to different costs for up and down  power regulations which are determined by the electricity market [ref].
@@
 We propose to model wind power forecasts errors using parametric stochastic differential equations (SDEs) whose solution defines a stochastic process.
-This resultant stochastic process describes the time evolution dynamics of wind power forecast errors while preserving properties such as the correlation structure and asymmetry.
-Additionally, the model is agnostic of  wind power forecasting technology and serves as a complement to forecasting procedures by providing a data driven probabilistic forecast.
+This resultant stochastic process describes the time evolution dynamics of wind power forecast errors while capturing properties such as a correlation structure and the inherent asymmetry.
+Additionally, the model we propose is agnostic of the forecasting technology and serves to complement forecasting procedures by providing a data driven stochastic forecast.
 Hence, we are able to evaluate wind power forecasts according to their real-world performance and we are able to compare different forecasting technologies.
+Most notably, we are able to simulate future wind power production given a deterministic wind power forecast.
+Future wind power production as well as the analytical form of the proposed SDE can be used in optimal control problems involving wind power production.
 
@@
 
+We use a year long data set from Uruguay based on 1000 observation paths, each of which is 72-hours long with observations recorded every 10 min.
+In total, it is a data set of approximatly half a million data points recorded in 2018.
+See figure (\ref{fig:sample_data}).
+The data is normalized with respect to the maximuim power capacity of wind power production in Uruguay.
+The asymmetry or skew nature of the data is clear when inspected for different power production levels.
+We split the aggregated data into a low, meduim and high power range.
+See figure (\ref{fig:skew_data}).
+
+In this paper we present the phenomenological underlaying model in section (2) and describe the physical constraints in section (3) and how these constrains can be met.
+Then, in section (4), we will introduce an alternative formulation of the model in Lamperti space.
+In section (5), we show our parameter estimation procedure and its results in section (6).
+We compare alternative models in section (7) and different forecast providers in section (8).
+\begin{figure}
+  \includegraphics[width=40mm,scale=1]{plots/data_1516064400.pdf}
+  \includegraphics[width=40mm,scale=1]{plots/data_1516323600.pdf}\\
+  \caption{Two samples from the Uruguayan of 2018.
+Each sample compromises of two 72-hour paths.
+In yellow is an hourly wind power production forecast.
+In blue is the actual wind power production recorded in 10 minute intervals.}
+  \label{fig:sample_data}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=26mm,scale=1]{plots/hist_low.pdf}
+  \includegraphics[width=26mm,scale=1]{plots/hist_mid.pdf}
+  \includegraphics[width=26mm,scale=1]{plots/hist_high.pdf}
+  \caption{We see that forecast errors exhibit skewness near the boundries (i.e.
+low and high power production regimes.).
+Low power is when produced power is less than $0.3$, mid power is when it is between $0.3$ and $0.6$ and high power when is larger than $0.6$.
+}
+  \label{fig:skew_data}
+\end{figure}
+
 %-------------------------------------------------------------------------
@@
 \begin{split}
-dX_t &= a(X_t; \bm{\theta}) dt + b (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
-X_0 & = X_0
+dX_t &= a(X_t; p_t, \dot{p}_t,\bm{\theta}) \ dt + b (X_t;p_t, \bm{\theta} ) \ dW_t \quad t > 0 \\
+X_0 & = x_0
 \end{split}
@@
 \begin{itemize}
-\item $a(\cdot; \bm{\theta}):[0,1] \to \R $  a drift function.
-\item $b (\cdot; \bm{\theta} ):[0,1] \to \R$  a  diffusion function.
+\item $a(\cdot; p_t, \dot{p}_t,\bm{\theta}):[0,1] \to \R \ $  a drift function.
+\item $b (\cdot;p_t, \bm{\theta} ):[0,1] \to \R \ $  a  diffusion function.
 \item $\bm{\theta}$: a vector of parameters.
+\item $p_t$ time-dependent scalar value and $ \dot{p}_t$ is its time derivative at time $t$. (in our case  $p_t$ is a deterministic forecast).
 \item $W_t$: Standard Wiener random process in $\R$.
@@
 We would like to have this model closely follow wind power forecasts while ensuring that it is unbiased with respect to the forecast.
-That is, we would like to have $\E X_t = p_t$ where $p_t$ is a deterministic given wind power forecast.
+It straightforward to show that $\E X_t = p_t$ where $p_t$ is a deterministic given wind power forecast in the model above.
 
@@
 \frac{ \partial f }{\partial t } & (y ,t | x , s, \theta_t, \alpha )= - \frac{\partial}{ \partial y} ( a( y;\dot{p}_t , p_t, \theta_t ) f( y ,t | x , s, \theta_t , \alpha ) ) \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b(y;\theta_t, \alpha  )  f( y ,t | x , s, \theta_t , \alpha )  ) \quad  t < s\\
+& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b^2(y;\theta_t, \alpha  )  f( y ,t | x , s, \theta_t , \alpha )  ) \quad  t < s\\
 \end{split}

### 2019-11-06 LaTeX_code/paper/paper.tex
update

@@
 \newcommand{\I}{\mathbb{I}}
+
+\newcommand{\add}{\textcolor{red}{[insert]}}
 
@@
 
+\begin{figure}
+  \includegraphics[width=26mm,scale=1]{plots/hist_low_lamperti.pdf}
+  \includegraphics[width=26mm,scale=1]{plots/hist_mid_lamperti.pdf}
+  \includegraphics[width=26mm,scale=1]{plots/hist_high_lamperti.pdf}
+  \caption{We observe that skewness has been greatly reduced after the Lamperti transformation. This motivates us to use a Gaussian transition density as a proxy density.}
+  \label{fig:skew_after_lamperti}
+\end{figure}
+
 %-------------------------------------------------------------------------
@@
 \end{equation}
+
 We have that the process $X_t$ mean reverts to the wind power forecast $p_t$ and tracks its the time derivative $\dot{p}_t$.
-An example such mean reverting model without derivative tracking exhibits consistent lags as shown in Figure ().
-See section (5) for comparisons.
+An example such mean reverting model without derivative tracking exhibits consistent lags as shown in Figure (\ref{fig:derivative_tracking}).
+See section (7) for comparisons.
 
- We normalize the forecast and production data to installed power capacity. Thus our process must be limited to the range $[0,1]$. To enforce this constraint, we must have drift and diffusion control.
-\subsubsection*{Diffusion Control: } The physical constraint to the range $[0,1]$ is respected  by choosing  diffusion coefficient $ b (x; \bm{\theta} )= \sqrt{2 \theta_t \alpha x (1-x)} $ which is zero on the boundaries of $[0,1]$.
-We also have that $\alpha$ is a path variability constant parameter to be determined.
+\begin{figure}
+  %\includegraphics[width=26mm,scale=1]{}
+  \caption{insert figure showing the difference with and without derivative tracking}
+  \label{fig:derivative_tracking}
+\end{figure}
 
-\subsubsection*{Drift Control: }
+ We normalize the forecast and production data to Uruguay  installed power capacity.
+at the time of observation.
+Thus our process must be limited to the range $[0,1]$.
+To enforce this constraint, we our  drift and diffusion terms  must satisfy certain rules.
+
+Let $\bm{\theta} = (\theta_0,\alpha)$.
+We would like that the process to follow the wind forecast, thus we choose a drift term that is mean reverting and tracks the derivative of the deterministic forecast $p_t$, which is an input to our model.
+  \begin{equation}
+    a(x; p_t,\bm{\theta})=  \dot{p_t} - \theta_t(x - p_t)
+  \end{equation}
+where $\theta_t>0$ is a time-dependent parameter that controls the speed of reversion.
+
+We would like  a diffusion term that vanishes at the boundaries to prevent the process from escaping the region $[0,1]$.
+  \begin{equation}
+    b (x; p_t,\bm{\theta} )= \sqrt{2 \theta_t \alpha x (1-x)}
+  \end{equation}
+  where $\alpha >0$ is a constant parameter that controls the path variability. This diffusion term belongs to the Pearson diffusion family and , in particular, it is a Jacobi type diffusion.
+
+To further ensure that the process does not escape the region $[0,1]$, the mean reversion parameter has to be selected according to the following rule.
 Observe that the time derivative term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays a.s.
 inside the range $[0,1]$.
-In other words, the zero drift line defined by $a(X_t; \bm{\theta}) =0$, which an attractor, must be contained inside the range $[0,1]$.
+In other words, the zero drift line defined by $a(x; p_t,\bm{\theta}) =0$, which an attractor, must be contained inside the range $[0,1]$.
 Thus, we must have that
@@
 \begin{equation}
-\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ) \label{theta_t}
+\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \theta_0 >0 \label{theta_t}
 \end{equation}
@@
 \subsubsection*{Change of Variables:}
-In order to avoid differentiation of the forecast $\dot{p}_t$ and simplify, we apply a change of variables $$V_t = X_t - p_t$$ \\
+To avoid differentiation of the forecast $p_t$ and simplify, we apply a change of variables $$V_t = X_t - p_t$$ \\
 The  model becomes,
@@
 dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
-V_0 & = v_0
+V_0 & = v_0\\
+% \theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
 \end{split}\label{VtSDE}
 \end{equation}
-with $\theta_t$ given by (\ref{theta_t}).
 
-\section{Data}
-We apply the model to Uruguayan wind power data and their corresponding wind power forecasts.
-The wind power actual production data set is recorded on intervals of ten minutes for each wind farm in the country.
-The associated wind power forecasts are provided by two different entities.
-Each forecast is provided on an hourly basis and is computed for a 72 hour horizon every few hours.
-Sample data is shown in Figure ().
+\section{State independent diffusion formulation:}
+The model we have demonstrated previously (\ref{VtSDE}) is  a state-dependent diffusion formulation, that is the diffusion of the SDE clearly depends on the state.
+We are interested in state independent diffusion as it is more tractable and numerically stable.To achieve that, we apply a Lamperti transform to obtain the following state-independent diffusion SDE,
+\begin{equation}
+  \begin{split}
+    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} \ dt + \sqrt{2 \alpha \theta_t} dW_t \\
+    Z_0&=z_0
+  \end{split}
+\end{equation}
+where the Lamperti trasform is given by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
+We can see in figure (\ref{fig:skew_after_lamperti} ) the effects of the Lamperti transform on the forecast error data.
+The Lamperti transform has greatly reduced  the forecast error skewness and ensures that the process stays in the range $[0,1]$.
+Thus, in this case,  we can consider using a Gaussian density as a proxy transition density.
 
@@
 \subsection{Likelihood}
-The SDE above defines the stochastic process $V_t$.
+
+Since $V_t$ defined by our SDE is Markovian, the likelihood function can be written as a product of transition densities.
 Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed in intervals of $\Delta_N$.
-Since $V_t$ defined by the SDE in (\ref{VtSDE}) is Markovian, the likelihood function can be written as product of transition densities.
 
 \begin{equation}
-\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}}, \bm{\theta})  \rho (V_{j,0})
+\mathcal{L}(\theta;V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}},\bm{\theta} )  \rho (V_{j,0})
 \label{likelihood}
@@
 \begin{split}
-\frac{ \partial f }{\partial t } & (y ,t | x , s, \theta_t, \alpha )= - \frac{\partial}{ \partial y} ( a( y;\dot{p}_t , p_t, \theta_t ) f( y ,t | x , s, \theta_t , \alpha ) ) \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b^2(y;\theta_t, \alpha  )  f( y ,t | x , s, \theta_t , \alpha )  ) \quad  t < s\\
+\frac{ \partial f }{\partial t } & (y ,t | x , s, \theta_0 , \alpha )= - \frac{\partial}{ \partial y} ( a( y;  p_t, \dot{p}_t, \theta_0 ) f( y ,t | x , s, \theta_0  , \alpha ) ) \\
+& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b^2(y; p_t, \theta_0, \alpha  )  f(y ,t | x , s,\theta_0 , \alpha ) ) \quad  t < s\\
+\end{split}
+\end{equation}
+This is a parametric PDE which is computationally expensive to solve and optimize for every transition. Therefore, we consider approximate likelihood methods.
+
+\subsection{Approximate Likelihood}
+Solving for transition densities of the process $V_t$ requires solving the Fokker-Planck equation at every step which is computationally prohibitive.
+A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints which give rise to asymmetric forecasting errors as seen in figure (\ref{fig:skew_data}).\\
+
+We propose a proxy transition density.
+We match the moments of our SDE model with that of the proxy density.
+Using It$\hat{o}$ formula, we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
+\begin{equation}
+\begin{split}
+\frac{d \E[ V^k_t]}{dt} = - k \theta_t \E [ V^k_t] + \frac{k(k-1)}{2} \E [ V^{k-2}_t  b(V^k_t;\theta_t, \alpha)]
+\end{split}
+\end{equation}
+For $t\in [t_{n-1}, t]$, the first two moments are given by
+\begin{equation}
+\begin{split}
+\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t \\
+\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta_t(1+\alpha) + 2\alpha\theta_t m_1(t)(1-2p_t) \\
+&\quad + 2 \alpha\theta_t p_t (1-p_t)\\
+\end{split}
+\end{equation}
+with initial conditions, $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2$.
+
+And for the state independent diffusion formulation, similarly, we  obtain a system of ODEs to determine the centered moments of the Lamperti transformed process $V_t$.
+Due to the non-linearity in the drift, we can only approximate the centered moments by the following ODEs,
+\begin{equation}
+\begin{split}
+\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\alpha) - \theta (1-2 p_t) \\
+\frac{d var(t)}{dt} &=  2 var(t) \theta_t (2p_t - 1 ) \tan(m_1 (t)) \sec(m_1 (t))\\
+& \quad + \theta_t (\alpha - 1) \sec^2(m_1 (t))  + 2 \theta_t \alpha\\
 \end{split}
@@
 
-The above parametric PDE is computationally prohibitive to be solved for each wind production data point and for all parameter space which is to be optimized.
-Therefore, we consider approximate likelihood methods.
-
-\subsection{Approximate Likelihood}
-Solving for transition densities of the process $V_t$ requires solving the Fokker-Planck equation at every step which is computationally prohibitive.
-A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints and the asymmetric nature of forecast errors.
-\\
-
-Therefore, we propose to approximate likelihood using a Beta distribution.
-As the process $X_t$ and $p_t$ take on values in $[0,1]$, then $V_t$ takes on values in $[-1,1]$.
-Therefore, we translate and scale the Beta distribution to have compact support on the interval $[-1,1]$.
+ A suitable candidate for a proxy transition density is a Beta probability distribution as it is compactly supported and can morph into symmetric and asymmetric shapes.
 
 \subsubsection*{ Moment Matching}
-To approximate the transition densities of  the process $V_t$ by a Beta distribution, we match its moments with the shape parameters $\xi_1, \xi_2$ of the Beta distribution on $[-1,1]$.
-Then, the shape parameters are given by,
+To approximate the transition densities of  the process $V_t$ by a Beta distribution, we match its moments with the shape parameters $\xi_1, \xi_2$ of a Beta proxy density on $[-1,1]$.
+The any moment of the process $V_t$ is  given by solving the corresponding ODE system  for the $k^{th}$  moment,
+
+The shape parameters are given by,
 \begin{equation}
@@
 \end{equation}
-where $\mu_t = \E[ V_t]$ and $\sigma_t^2= \E[ V^2_t]- \E[ V_t]^2$ and $m_i$ being the i-th moment of the process $V_t$.
-Using It\^{o}'s formula, the moments  of the  process $V_t$ are iteratively given by,
+where $\mu_t = m_1 (t)$ and $\sigma_t^2= m_2 (t)- m_1 (t)^2$.
+
+\subsection{Optimization}
+
+To initialize the the optimization process, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$.
 
 \begin{equation}
-\begin{split}
-\frac{d \E[ V^k_t]}{dt} = - k \theta_t \E [ V^k_t] + \frac{k(k-1)}{2} \E [ V^{k-2}_t  b(y;\theta_t, \alpha)]
-\end{split}
+ \arg\min \sum\limits_{i}^M \sum\limits_j^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 
  \end{equation}
 
-with initial conditions, $\E[ V^k_t]= v_{s}^k$ where $t<s$.
-\subsection{Optimization}
-Let $\ell$ be the natural logarithm  of the likelihood in $(\ref{likelihood})$.
-Given the data set $V^{M,N}$, we  optimize the the log-likelihood $\ell$  using L-BFGS algorithm  for the optimal parameters $\theta_0^* , \alpha^*$ as follows,
+ where $v_{i,j}=x_{i,j}-p_{i,j}$,  $x_{i,j}$ is historical wind power production and $p_{i,j}$ is the wind power forecast.
+
+ By assuming ergodicity, we can obtain a first estimate on the product of the parameters as follows,
+
 \begin{equation}
-(\theta_0^* , \alpha^* ) = \arg \underset{\theta_0, \alpha>0}{\min} - \ell( \theta_0,  \alpha | V^{M,N} )
+\theta_0 \alpha = \frac{1}{M} \sum\limits_i^M \frac{ \sum\limits_j^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_j^N x_{i,j}(1-x_{i,j}) }
 \end{equation}
-The contours of the  log-likelihood can be seen in Figure (\ref{contour}).
-To further inspect the log-likelihood at the point of optimality $(\theta_0^* , \alpha^* )$, we check the ellipse defined by the  Hessian of the log-likelihood at the point of optimality.
-We observe that the ellipse shrinks at a fast rate as shown in Figure (\ref{ellipse_drawing}).
-We see that  the convergence rate of the parameters $\theta_0$ and $\alpha$ is slightly faster than the expected rate of $1/\sqrt{M}$.
-This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample.
-We note that the uncertainty in determining the parameter $\alpha$  is much higher than  in $\theta_0$.
+
+Solving for $\alpha$, we have both first estimates to kick start the inference processes given as follows:
+\begin{enumerate}
+\item[Step 1.]  initialize
+\item[Step 2.]  optimize the log-likelihood function using  Nelder-Mead optimization algorithm on a mini-batch sampled with replacement.
+\item[Step 3. ] check if  accuracy threshold is reached. Else, re-initialize the optimization with the most recent result on a larger mini-batch.
+\end{enumerate}
 
@@
   \item Model 1: This model features derivative tracking, i.e.
-it's equivalent to $\ref{model:derivative_tracking_X}$ with a diffusion term that is forecast dependent by including the term $p_t(1-p_t)$.
+it is equivalent to (\ref{model:derivative_tracking_X}) with a diffusion term that is forecast dependent by including the term $p_t(1-p_t)$.
   \begin{equation}
@@
   with $\theta_t$ given by (\ref{theta_t}).
+This model has been used by [ insert ref ] and [ insert ref ].
+Initial interest in this model stems from interest in long-term stationary solution, which may exists  if the forecast is constant.
+However, this is almost never occurs and thus including the term $p_t(1-p_t)$ is irrelevant.
+Additionally, the term $p_t(1-p_t)$ leads the model to become deterministic when the forecast is at the boundaries (i.e.$p=1$ or $p=0$)  which is not realistic.
+We have run computations on this model and the results were not satisfactory.
+Therefore, we exclude this model from further discussions.
 
-  \item Model 2: This model features derivative tracking, i.e. it's equivalent to $\ref{model:derivative_tracking_X}$
+  \item Model 2: This model features derivative tracking, i.e. it's equivalent to (\ref{model:derivative_tracking_X}).
 \begin{equation}
@@
 Model   &  parameters $(\theta_0, \alpha)$   & AIC & BIC \\ \hline
-Model 0 &  (,)   &     &     \\ \hline
-Model 1 &   (,)  &     &      \\ \hline
-Model 2 &   (,)  &     &       \\ \hline
+Model 0 &  $(\add,\add) $    &  \add   &  \add   \\ \hline
+Model 2 &   $(\add,\add)$   &  \add   &   \add    \\ \hline
 \end{tabular}
-\caption{We compare the different models based on information criterion. <discuss results> }
+\caption{We compare the different models based on information criterion. \add }
 \label{tab:model_comparison}
@@
 Forecast Provider & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
-Provider A        &                                 &     &     \\ \hline
-Provider B        &                                 &     &     \\ \hline
+Provider A  &  $(\add,\add)$      &  \add   & \add    \\ \hline
+Provider B  & $(\add,\add) $  &  \add   &   \add  \\ \hline
 \end{tabular}
-\caption{<discuss results>}
+\caption{\add}
 \label{tab:forcast_comparison}
 \end{table}
-In Figure ()-(), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.
+In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.
 
@@
  \hline
- Model                                                                              & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
- \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}              &                                 &     &     \\ \hline
- \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &                                 &     &     \\ \hline
+ Model & parameters $(\theta_0, \alpha)$  \\ \hline
+ \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ \hline
+ \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \hline
  \end{tabular}
- \caption{<discuss results>}
+ \caption{ \add confidence interval obtained using bootstrap}
  \label{tab:freq_comparison}
@@
 
-\section{Model on Disaggregated Data}
-We apply Model 2 to disaggregated wind power production data and forecasts. The data is available in this case on an hourly basis. Results are shown in Table (\ref{tab:disagregated_data}).
+%\section{Model on Disaggregated Data}
+%We apply Model 2 to disaggregated wind power production data and forecasts. The data is available in this case on an hourly basis. Results are shown in Table (\ref{tab:disagregated_data}).
+%
+%\begin{table}[]
+%\centering
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%Forecast Provider A & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
+%Wind Farm 1         &                                 &     &     \\ \hline
+%Wind Farm 2         &                                 &     &     \\ \hline
+%Wind Farm 3         &                                 &     &     \\ \hline
+%Wind Farm 4         &                                 &     &     \\ \hline
+%Wind Farm 5         &                                 &     &     \\ \hline
+%Wind Farm 6         &                                 &     &     \\ \hline
+%\end{tabular}
+%\caption{<discuss results>}
+%\label{tab:disagregated_data}
+%\end{table}
+%
+%\begin{table}[]
+%\centering
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%Forecast Provider B & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
+%Wind Farm 1         &                                 &     &     \\ \hline
+%Wind Farm 2         &                                 &     &     \\ \hline
+%Wind Farm 3         &                                 &     &     \\ \hline
+%Wind Farm 4         &                                 &     &     \\ \hline
+%Wind Farm 5         &                                 &     &     \\ \hline
+%Wind Farm 6         &                                 &     &     \\ \hline
+%\end{tabular}
+%\caption{\textless{}discuss results\textgreater{}}
+%\label{tab:disagregated_data_B}
+%\end{table}
 
+\section{Results}
+
+We were able to obtain the following for 
 \begin{table}[]
 \centering
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|}
 \hline
-Forecast Provider A & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
-Wind Farm 1         &                                 &     &     \\ \hline
-Wind Farm 2         &                                 &     &     \\ \hline
-Wind Farm 3         &                                 &     &     \\ \hline
-Wind Farm 4         &                                 &     &     \\ \hline
-Wind Farm 5         &                                 &     &     \\ \hline
-Wind Farm 6         &                                 &     &     \\ \hline
+Formulation   &  parameters $(\theta_0, \alpha)$    \\ \hline
+Without Lamperti transform &   $(12,0.3) \pm (\add , \add) $   \\ \hline
+With Lamperti transform &   $(12,0.29) \pm (\add , \add)  $   \\ \hline
 \end{tabular}
-\caption{<discuss results>}
-\label{tab:disagregated_data}
+\caption{We compare the parameters obtained in both the original and Lamperti space. Parameters have been obtained based on \add data points from the Uruguayan pertaining to the year 2018  \add }.
+\label{tab:model_comparison}
 \end{table}
 
-\begin{table}[]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-Forecast Provider B & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
-Wind Farm 1         &                                 &     &     \\ \hline
-Wind Farm 2         &                                 &     &     \\ \hline
-Wind Farm 3         &                                 &     &     \\ \hline
-Wind Farm 4         &                                 &     &     \\ \hline
-Wind Farm 5         &                                 &     &     \\ \hline
-Wind Farm 6         &                                 &     &     \\ \hline
-\end{tabular}
-\caption{\textless{}discuss results\textgreater{}}
-\label{tab:disagregated_data_B}
-\end{table}
-
-\section{Results}
  We are able to obtain the parameters based on the complete data sets. Using the different models variations, we are able to simulate wind power production given a forecast. We see in figures ()-()
@@
 In Figures ()-(), we show point-wise empirical confidence bands for the different models.
+
+\begin{figure}
+  \includegraphics[width=39mm,scale=1]{plots/alpha_conv_beta.png}
+  \includegraphics[width=39mm,scale=1]{plots/theta_conv_beta.png}
+  \caption{We show self-convergence of our algorithm applied to model $2$. We conlcude that the rate  matches that of of Monte Carlo. Data is from Uruguay pertaining to  year 2018. }
+\end{figure}
+
+    \begin{figure}
+      \includegraphics[width=75mm,scale=1]{simulated/24hr/1099.pdf}
+      \includegraphics[width=75mm,scale=1]{simulated/24hr/1178.pdf}
+      \caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha )=(12,0.3)$.
+Forecast is from Uruguay pertaining to  year 2018.
+}
+    \end{figure}
+
+    \begin{figure}
+      \includegraphics[width=75mm,scale=1]{confidence_intervals/24hr/31.pdf}
+      \includegraphics[width=75mm,scale=1]{confidence_intervals/24hr/820.pdf}
+       \caption{We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha )=(12,0.3)$.
+Actual production plotted in retrospect.
+Forecast and data is from Uruguay pertaining to  year 2018.
+}
+    \end{figure}
 

### 2020-01-09 LaTeX_code/paper/paper.tex
I added the latest versions of the paper, the poster and the presentation.

@@
 %\thispagestyle{empty}
-
+{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, model selection, sensitivity.}
 %%%%%%%%% ABSTRACT
@@
 The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of an information criteria.
-We apply the model to historical Uruguayan and French wind power production data and various forecasts on the period (2017-2018).
+We apply the model to historical French and Uruguayan wind power production data and forecasts on the period (2017-2018).
 
@@
 \begin{itemize}
-\item Allocation of energy reserves such as water levels in dams or oil and gas reserves.
+\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
 \item Operation scheduling of non-controlable power plants.
@@
 Most notably, we are able to simulate future wind power production given a deterministic wind power forecast.
-Future wind power production as well as the analytical form of the proposed SDE can be used in optimal control problems involving wind power production.
+Future wind power production using Monte Carlo methods, as well as the analytic form of the proposed SDE, can be used in optimal control problems involving wind power production.
 
@@
 Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion and non-Gaussian approximations.
-We apply the model to Uruguayan and french wind power forecasts together with historical wind power production data pertaining to the year 2017-2018.
+We apply the model to French and Uruguayan wind power forecasts together with historical wind power production data pertaining to the year 2017-2018.
 
@@
 
-In this paper we present the phenomenological underlaying model in section (2) and describe the physical constraints in section (3) and how these constrains can be met.
-Then, in section (4), we will introduce an alternative formulation of the model in Lamperti space.
-In section (5), we show our parameter estimation procedure and its results in section (6).
-We compare alternative models in section (7) and different forecast providers in section (8).
+In this paper we present the phenomenological underlying model in Section \ref{Section_2} and describe the physical constraints in Section \ref{Section_3} and how these constrains can be met.
+Then, in Section \ref{Section_4}, we will introduce an alternative formulation of the model in Lamperti space.
+In Section \ref{Section_5}, we show our parameter estimation procedure and its results in Section \ref{Section_6}.
+We compare alternative models in Section \ref{Section_7} and different forecast providers in Section \ref{Section_8}.
 \begin{figure}
@@
 %-------------------------------------------------------------------------
-\section{Phenomenological  Model}
+\section{Phenomenological  Model} \label{Section_2}
+
 We introduce the following phenomenological model. Let $X_t$ be the  wind power generation forecasts stochastic process defined by the  following parameterized stochastic differential equation (SDE),
@@
 We would like to have this model closely follow wind power forecasts while ensuring that it is unbiased with respect to the forecast.
-It straightforward to show that $\E X_t = p_t$ where $p_t$ is a deterministic given wind power forecast in the model above.
+It straightforward to show that $\E\left[X_t\right] = p_t$, where $p_t$ is a deterministic given wind power forecast in the model above.
 
@@
 An example such mean reverting model without derivative tracking exhibits consistent lags as shown in Figure (\ref{fig:derivative_tracking}).
-See section (7) for comparisons.
+See Section \ref{Section_7} for comparisons.
 
@@
 
- We normalize the forecast and production data to Uruguay  installed power capacity.
-at the time of observation.
+ We normalize the forecast and production data to Uruguay  installed power capacity at the time of observation.
 Thus our process must be limited to the range $[0,1]$.
-To enforce this constraint, we our  drift and diffusion terms  must satisfy certain rules.
+To enforce this constraint, our  drift and diffusion terms  must satisfy certain rules.
 
 Let $\bm{\theta} = (\theta_0,\alpha)$.
-We would like that the process to follow the wind forecast, thus we choose a drift term that is mean reverting and tracks the derivative of the deterministic forecast $p_t$, which is an input to our model.
+We want a process that follow the wind forecast, thus we choose mean reverting drift term which also tracks the derivative of $p_t$, which is an input to our model.
   \begin{equation}
@@
 
-\section{State independent diffusion formulation:}
-The model we have demonstrated previously (\ref{VtSDE}) is  a state-dependent diffusion formulation, that is the diffusion of the SDE clearly depends on the state.
-We are interested in state independent diffusion as it is more tractable and numerically stable.To achieve that, we apply a Lamperti transform to obtain the following state-independent diffusion SDE,
+\section{State independent diffusion: Lamparti transform} \label{Section_3}
+
+Our model in (\ref{VtSDE}) is  a state-dependent diffusion formulation, that is the diffusion of the SDE clearly depends on the state.
+We are interested in state independent diffusion as it is more tractable and numerically stable.
+To achieve that, we apply a Lamperti transform to obtain the following state-independent diffusion SDE,
 \begin{equation}
@@
 where the Lamperti trasform is given by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
-We can see in figure (\ref{fig:skew_after_lamperti} ) the effects of the Lamperti transform on the forecast error data.
+We can see in figure (\ref{fig:skew_after_lamperti}) the effects of the Lamperti transform on the forecast error data.
 The Lamperti transform has greatly reduced  the forecast error skewness and ensures that the process stays in the range $[0,1]$.
@@
 
-\section{Inference and Optimization}
+\section{Likelihood in $V$ space} \label{Section_4}
 
@@
 Since $V_t$ defined by our SDE is Markovian, the likelihood function can be written as a product of transition densities.
-Consider a set of M paths with N observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ observed in intervals of $\Delta_N$.
+Consider the set of $M$ paths with $N$ observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$, observed in $\Delta_N$ intervals.
 
@@
 \begin{split}
-\frac{ \partial f }{\partial t } & (y ,t | x , s, \theta_0 , \alpha )= - \frac{\partial}{ \partial y} ( a( y;  p_t, \dot{p}_t, \theta_0 ) f( y ,t | x , s, \theta_0  , \alpha ) ) \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b^2(y; p_t, \theta_0, \alpha  )  f(y ,t | x , s,\theta_0 , \alpha ) ) \quad  t < s\\
+\frac{ \partial f }{\partial t } & (v ,t | x , s, \theta_0 , \alpha )= - \frac{\partial}{ \partial v} ( a( v;  p_t, \dot{p}_t, \theta_0 ) f( v ,t | x , s, \theta_0  , \alpha ) ) \\
+& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( b^2(v; p_t, \theta_0, \alpha  )  f(v ,t | x , s,\theta_0 , \alpha ) ) \quad  t < s\\
 \end{split}
@@
 We match the moments of our SDE model with that of the proxy density.
-Using It$\hat{o}$ formula, we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
+Using It\^o formula, we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
 \begin{equation}
@@
 
-To initialize the the optimization process, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$.
+To initialize the optimization process, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$.
 
@@
 
-Solving for $\alpha$, we have both first estimates to kick start the inference processes given as follows:
+Solving for $\alpha$, we have both first estimates to quick start the inference processes given as follows:
 \begin{enumerate}
@@
 
-\section{Model Comparison}
+\section{Model Comparison} \label{Section_5}
 We compare the following candidate models to find the best-fit that maximizes the retained information,
@@
 
-\section{Forecast Provider Comparison}
+\section{Forecast Provider Comparison} \label{Section_6}
 We compare forecasts from two different companies for the same period.
@@
 
-\section{Results}
+\section{Results} \label{Section_7}
 
@@
 
-\section{Conclusions}
+\section{Conclusions} \label{Section_8}
+
+{\color{red} Application: Using this tool, it is possible to iterate over hyper parameters for the wind power forecasting, reaching an optimal forecasting.}
 

### 2020-01-09 graph/ToDo/ToDo.tex
I added the graph.

\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[activeacute, english]{babel}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{tikz}
\usepackage{float}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}

\newcommand\dist{\stackrel{\mathclap{\footnotesize\mbox{d.}}}{=}}
\usepackage[spanish,onelanguage,ruled,lined, linesnumbered]{algorithm2e}
\usepackage[spanish,onelanguage]{algorithm2e}
\newtheorem{theorem}{Teorema}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposición}
%\newenvironment{proof}[1][Demostración]{\begin{trivlist}
%		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{definition}[1][Definición]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Ejemplo]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Nota]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\negr}[1]{\textit{\textbf{#1}}}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\title{Paper To-Do List}

\author{Waleed Alhaddad}

\date{19/11/2019}
\begin{document}
\maketitle

% Participants:
% \begin{multicols}{3}
% \begin{itemize}
% 	\item Waleed
% 	\item Ahmed
% 	\item Raul
% \end{itemize}
% \end{multicols}

\section{To do}
\begin{enumerate}
\item Read, understand and reference Japan literature ( 3 Days )
\item Add references through out the paper and learn how to use bibilex (1 hr )
\item Copy subject calssification and keywords from Somaya's paper. Then discuss the choice and improve it with Raul and Ahmad. (30 m)
\item Add labels to the paper sections. We do this because it is easier to refer to sections after they have an associated label.
\item Add two simulation function with zero diffusion, where one is with derivative tracking and the other without it. Select an oscilattory forecast or synthesize one to test on it and plot bth plots to show the phase error when we don't have derivative tracking. (30 m)
\item Rename section 3 to: state Independent Diffusion; Lamperti transform
\item Number and emphasize the Lamperti transform excplicitly.
\item Change title of section 4 to: Likelihood in V space.
\item Fockker-Plank equation 
\begin{itemize}
\item Change variable in Fockker-Plank from y to $V_{t_{i,j}}$
\item define the functions $a$ and $b$ in the statement
\item  clearly state the time interval that it is between $t_{i,j}$ and $t_{j,i+1}$
\item State initial condition to be a Dirac function at $V_{j,i}$
\item make a connection between the fokker plank and the likelihood transitions, i.e. $\rho(V_{j,i+1}| V_{j,i})  = f(V_{j,i+1}, t_{j,i+1}|V_{j,i}, t_{j,i} )$
\end{itemize}

\item check dimensions of $\theta$ and if it looks reasonable with the average number of crossings $(\sim 5)$ (0.5 Day)
\item relate the $\theta$ to the time correlation structure and see how big of a gap should be left between two consecutive best samples. Then cut accordingly if possible. Check the ratio of time correlation to the length of the path if its much less than one as we would like. (2 Days)
\item Import data (1 Weeks)
\begin{itemize}
\item import the data again
\item Detect when the forecast has started or read it as indicated in the data set.
\item arrange the forecast in chronological order and  know which are consecutive forecasts
\item check if the forecast has no missing or corrupt data points
\item check the difference of time between the start times of the forecasts and record that information.
\item adapt the number of samples to be variable in every path. Then adjust all the code and solvers for this added flexibility.
\item Check which segments are the most recent for the time in question , i.e. choosing the path of best available forecast.
\end{itemize}
\item Add discussion about Lamperti and linearization of the non-linear drif that arises. Mention that the best proxy is Gaussian and approximation is good enough as the time between samples is small. 
\item obtain an estimate of the product $\theta_0 \alpha$ using quadratic variations and implement a function that computes that. Justify assuming that $\theta_t$ is independent of time here is somehow acceptable otherwise it is not possible to estimate $\theta_t \alpha$ using the quadratic variations.write a funciton that checks the number of crossing in the processed data set in order to seperate the product of $\alpha \theta_0$. (0.25 Day)
\item Implement Model 0 and adjust the rest of the code and plotting to this. (3 Days)
\item Remove Model 1 and write a paragraph about it because when $p=1$ or $p=0$ it is not physical to have zero diffusion. (0.2 Days)
\item Import, clean, filter and process the french data as done in step (12). Then run the best model in standard and in Lamperti space ( 1 week )
\item Fix the mini-batching in the optimization as it resets the samples in each evaluation. Should store the sample for next evaluations within one optimization run. (3 Days)
\item Produce documentation for all functions, scripts and objects. (1.5 weeks)
\end{enumerate}
Total continous time needed: 8-9 weeks to do the above list.

\end{document}

### 2020-01-20 graph/ToDo/ToDo.tex
Update of the main algorithm (adding comments), and some latex files

@@
-\documentclass[a4paper, 12pt]{article}
+\documentclass[12pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{float}
-\usepackage{algpseudocode}
 \usepackage{caption}
@@
 \usepackage{multicol}
+\usepackage{listings}
+\usepackage[margin=0.8in]{geometry}
+\usepackage{algpseudocode}
 
-\newcommand\dist{\stackrel{\mathclap{\footnotesize\mbox{d.}}}{=}}
-\usepackage[spanish,onelanguage,ruled,lined, linesnumbered]{algorithm2e}
-\usepackage[spanish,onelanguage]{algorithm2e}
+% \usepackage[spanish,onelanguage,ruled,lined, linesnumbered]{algorithm2e}
+\usepackage[onelanguage,ruled,lined, linesnumbered]{algorithm2e}
 \newtheorem{theorem}{Teorema}[section]
@@
 \newtheorem{proposition}[theorem]{Proposición}
-%\newenvironment{proof}[1][Demostración]{\begin{trivlist}
-%		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
 \newenvironment{definition}[1][Definición]{\begin{trivlist}
@@
 \newcommand{\T}{\mathbb{T}}
+
+\begin{document}
 \title{Paper To-Do List}
-
 \author{Waleed Alhaddad}
-
 \date{19/11/2019}
-\begin{document}
 \maketitle
@@
 \begin{enumerate}
-\item Read, understand and reference Japan literature ( 3 Days )
-\item Add references through out the paper and learn how to use bibilex (1 hr )
+\item Read, understand and reference Japan literature (3 Days)
+\item Add references through out the paper and learn how to use bibilex (1 hr)
 \item Copy subject calssification and keywords from Somaya's paper. Then discuss the choice and improve it with Raul and Ahmad. (30 m)
@@
 \end{itemize}
-\item Add discussion about Lamperti and linearization of the non-linear drif that arises.
-Mention that the best proxy is Gaussian and approximation is good enough as the time between samples is small.
+\item Add discussion about Lamperti and linearization of the non-linear drif that arises. Mention that the best proxy is Gaussian and approximation is good enough as the time between samples is small.
 \item obtain an estimate of the product $\theta_0 \alpha$ using quadratic variations and implement a function that computes that.
@@
 \end{enumerate}
-Total continous time needed: 8-9 weeks to do the above list.
 
+\section{Code correction report:}
+
+\begin{enumerate}
+
+\item The data is wrong. There are many repeated paths. After correcting most of the code, it is needed to download all again and do the processing again.
+\item We have to be careful about that is $(\theta,\alpha)$ in the Likelihood. When we optimize, we need to optimize over $(\theta_0,\alpha)$ so we would have
+\begin{equation*}
+\mathcal{L}=\mathcal{L}\left(\theta_0,\alpha,\{V\},\{p\}\right).
+\end{equation*}
+Notice that $\theta=\theta(\theta_0,\dot{p})$.
+
+\end{enumerate}
+
+\section{Pseudocode:}
+
+\begin{algorithm}[H]
+
+	* load paths information into this\_model *;\\
+
+    \While{\textup{current\_batch\_size $<=$ max\_batch\_size}}{
+		this\_model.{\color{blue}\textbf{optimize}}(intial\_point, current\_batch\_size, $\dots$)\;
+		current\_batch\_size = current\_batch\_size * batch\_multiplier;\
+    }
+
+    \textbf{** Methods from this\_model object **}\\
+    \SetKwFunction{FMain}{this\_model.{\color{blue}\textbf{optimize}}}
+	\SetKwProg{Pn}{Method}{:}{\KwRet}
+    \Pn{\FMain{\textup{intial\_point, current\_batch\_size, $\dots$}}}{
+		likelihood = self.{\color{violet}\textbf{rand\_beta\_objective}}\;
+		batch = self.{\color{red}\textbf{gen\_mini\_batch}}(batch\_size)\;
+		min\_param = scipy.optimize.minimize(fun = likelihood, x0 = param\_initial, args = (batch\_size, batch), method = "Nelder-Mead")\;
+		\textbf{Returns} = min\_param
+	}
+
+	\SetKwFunction{FMain}{this\_model.{\color{red}\textbf{gen\_mini\_batch}}}
+	\SetKwProg{Pn}{Method}{:}{\KwRet}
+    \Pn{\FMain{\textup{current\_batch\_size, $\dots$}}}{
+		self.\{X,p,N,M\};\\
+		* create $\dot{p}$ *;\\
+		* create linked-lists with V,p, and $\dot{p}$ *;\\
+		* create 2D array with the linked-lists (call it combined\_iter) *;\\
+		batch = random\_combination(combined\_iter, batch\_size);\\
+		\textbf{Returns} = batch
+	}
+
+	\SetKwFunction{FMain}{this\_model.{\color{violet}\textbf{rand\_beta\_objective}}}
+	\SetKwProg{Pn}{Method}{:}{\KwRet}
+    \Pn{\FMain{\textup{current\_batch\_size, $\dots$}}}{
+    	\For{\textup{j in range(batch\_size)}}{
+    		* find moments using {\color{orange}\textbf{beta\_moment}} *;\\
+    		L\_n = L\_n + ($\dots$);
+    	}
+		\textbf{Returns} = -L\_n
+	}
+
+\caption{Main Algorithm}
+\end{algorithm}
+eee
 \end{document}

### 2020-01-24 LaTeX_code/paper/paper.tex
added paper in one line plus .bib

@@
 
-\author{ Waleed Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
+\author{ Waled Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
 \textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University,  Germany

### 2020-01-24 LaTeX_code/paper/paper_1line.tex
added paper in one line plus .bib

--- 2020-01-24 LaTeX_code/paper/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\documentclass{article}
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
 \usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\usepackage{amssymb, amsmath}
+\usepackage{bm} % more powerful version to get bold
 
-\usepackage{color}
-\usepackage{mathtools}
-\usepackage{mathptmx}
-\usepackage[11pt]{moresize}
-\usepackage{wrapfig}
-\usepackage{bbm}
 \usepackage{xcolor}
-\usepackage{tabularx}
-\usepackage{bm}
 
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\E}{\mathbb{E}}
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\V}{\mathbb{V}}
-\newcommand{\Q}{\mathbb{Q}}
-\newcommand{\K}{\mathbb{K}}
-\newcommand{\C}{\mathbb{C}}
-\newcommand{\T}{\mathbb{T}}
-\newcommand{\I}{\mathbb{I}}
+\usepackage[backend=biber, style=apa,autocite=inline]{biblatex} % package for bibliography
+\DeclareLanguageMapping{english}{english-apa}
+
+\addbibresource{sdewind.bib}
+
+%\usepackage[backend=biber, style=authoryear,autocite=inline]{biblatex}
 
@@
 
-% Include other packages here, before hyperref.
+\setcounter{page}{1}
 
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
-
-\cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{1}
 \begin{document}
 
-%%%%%%%%% TITLE
 \title{ Stochastic Wind Power Forecasting }  % \\  \small{Report}}
@@
 %\thispagestyle{empty}
-{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, model selection, sensitivity.}
+{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, model selection, sensitivity.}
 %%%%%%%%% ABSTRACT
@@
 
-Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price and Operation scheduling of conventional power plant.
+Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price and operation scheduling of conventional power plant.
 We propose a data driven model based on parametric Stochastic Differential Equations (SDEs) to captures real-world asymmetric dynamics of wind power forecast errors.
-The SDE proposed incorporates time derivative tracking of the forecast, time-dependent mean reversion parameter and an improved diffusion term.
-We are able to simulate future wind power production paths and confidence bands.
-The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of an information criteria.
+Our SDE framework incorporates time derivative tracking of the forecast, time-dependent mean reversion parameter and an improved diffusion term.
+We are able to simulate future wind power production paths and to get sharp confidence bands.
+The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of information criteria.
 We apply the model to historical French and Uruguayan wind power production data and forecasts on the period (2017-2018).
@@
 %%%%%%%%% BODY TEXT
-\section{Introduction}
+
+%---BEGIN SECTION 1---
+\section{Introduction}  \label{Section_1}
 
@@
 \item Operation scheduling of non-controlable power plants.
-\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity Service providers (ESPs), Independent power producers (IPPs), and energy traders.
+\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
 \item Maintenance planning such as that of power plants components and transmission lines.
@@
 It is crucial to capture actual performance of a forecast as it has been known that different forecasting technologies exhibits different behavior for different wind farms and seasons [ref].
-This is due to many factors which forecast are challenged to capture such as the surrounding terrains of the wind farm and the condition of the blades such as icing,wear and tear or dirt.
+This is due to many factors which forecast are challenged to capture such as the surrounding terrains of the wind farm and the condition of the blades such as icing, wear and tear or dirt.
 It is known that complex terrains in both off shore and on shore locations decrease the accuracy of wind power forecasts significantly [ref].
@@
 
-Previous attempt by M\o ller et al.
-(M\o ller, Zugno, \& Madsen, 2016)  considered stochastic wind power forecast models based on stochastic differential equations (SDEs).
+Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations (SDEs).
 Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion and non-Gaussian approximations.
@@
 In total, it is a data set of approximatly half a million data points recorded in 2018.
-See figure (\ref{fig:sample_data}).
+See Figure (\ref{fig:sample_data}).
 The data is normalized with respect to the maximuim power capacity of wind power production in Uruguay.
@@
 We split the aggregated data into a low, meduim and high power range.
-See figure (\ref{fig:skew_data}).
+See Figure (\ref{fig:skew_data}).
 
@@
 We compare alternative models in Section \ref{Section_7} and different forecast providers in Section \ref{Section_8}.
+
 \begin{figure}
-  \includegraphics[width=40mm,scale=1]{plots/data_1516064400.pdf}
-  \includegraphics[width=40mm,scale=1]{plots/data_1516323600.pdf}\\
+  \includegraphics[width=60mm,scale=1]{plots/data_1516064400.pdf}
+  \includegraphics[width=60mm,scale=1]{plots/data_1516323600.pdf}\\
   \caption{Two samples from the Uruguayan of 2018.
@@
 \begin{figure}
-  \includegraphics[width=26mm,scale=1]{plots/hist_low.pdf}
-  \includegraphics[width=26mm,scale=1]{plots/hist_mid.pdf}
-  \includegraphics[width=26mm,scale=1]{plots/hist_high.pdf}
+  \includegraphics[width=38mm,scale=1]{plots/hist_low.pdf}
+  \includegraphics[width=38mm,scale=1]{plots/hist_mid.pdf}
+  \includegraphics[width=38mm,scale=1]{plots/hist_high.pdf}
   \caption{We see that forecast errors exhibit skewness near the boundries (i.e.
@@
 \begin{figure}
-  \includegraphics[width=26mm,scale=1]{plots/hist_low_lamperti.pdf}
-  \includegraphics[width=26mm,scale=1]{plots/hist_mid_lamperti.pdf}
-  \includegraphics[width=26mm,scale=1]{plots/hist_high_lamperti.pdf}
+  \includegraphics[width=38mm,scale=1]{plots/hist_low_lamperti.pdf}
+  \includegraphics[width=38mm,scale=1]{plots/hist_mid_lamperti.pdf}
+  \includegraphics[width=38mm,scale=1]{plots/hist_high_lamperti.pdf}
   \caption{We observe that skewness has been greatly reduced after the Lamperti transformation. This motivates us to use a Gaussian transition density as a proxy density.}
@@
 \end{figure}
+%---END SECTION 1---
 
-%-------------------------------------------------------------------------
+%---BEGIN SECTION 2---
 \section{Phenomenological  Model} \label{Section_2}
 
-We introduce the following phenomenological model. Let $X_t$ be the  wind power generation forecasts stochastic process defined by the  following parameterized stochastic differential equation (SDE),
-\begin{equation}
-\begin{split}
-dX_t &= a(X_t; p_t, \dot{p}_t,\bm{\theta}) \ dt + b (X_t;p_t, \bm{\theta} ) \ dW_t \quad t > 0 \\
-X_0 & = x_0
-\end{split}
-\label{main}
-\end{equation}
+We introduce the following phenomenological model.
+Let $\{X_t, \, t>0\}$  be the  wind power generation forecasts stochastic process defined by the following parameterized stochastic differential equation (SDE)
+
+\begin{align}
+dX_t & =  a(X_t; p_t, \dot{p}_t,\bm{\theta}) \ dt + b (X_t; p_t, \bm{\theta} ) \ dW_t \nonumber \\ 
+X_0 & =  x_0\,,   \label{eq:main}
+\end{align}
+where
 
 \begin{itemize}
-\item $a(\cdot; p_t, \dot{p}_t,\bm{\theta}):[0,1] \to \R \ $  a drift function.
-\item $b (\cdot;p_t, \bm{\theta} ):[0,1] \to \R \ $  a  diffusion function.
-\item $\bm{\theta}$: a vector of parameters.
-\item $p_t$ time-dependent scalar value and $ \dot{p}_t$ is its time derivative at time $t$. (in our case  $p_t$ is a deterministic forecast).
-\item $W_t$: Standard Wiener random process in $\R$.
+\item $a(\cdot; p_t, \dot{p}_t,\bm{\theta}):[0,1] \to \mathbb{R} \ $  denotes a drift function,
+\item $b (\cdot;p_t, \bm{\theta} ):[0,1] \to \mathbb{R} \ $  a  diffusion function,
+\item $\bm{\theta}$ is a vector of parameters,
+\item $p_t$ is a time-dependent scalar value and $ \dot{p}_t$ is its time derivative at time $t$,
+\item $\{W_t, \, t >0\}$ is a standard Wiener process in $\mathbb{R}$.
 \end{itemize}
 
-We would like to have this model closely follow wind power forecasts while ensuring that it is unbiased with respect to the forecast.
-It straightforward to show that $\E\left[X_t\right] = p_t$, where $p_t$ is a deterministic given wind power forecast in the model above.
+ In this work, $p_t$ is to be considered as a deterministic forecast of the wind power generation at time $t$ which is available from an official source.
+
+Our goal is to provide a specification of the model (\ref{eq:main}) to follow closely the available wind power forecasts while ensuring its unbiasedness with respect to the forecast.
+It is straightforward to show that $\mathbb{E} \left[X_t\right] = p_t$, where $p_t$ is the available deterministic wind power forecast for the time $t$.
 
@@
 
-Let $p_t$ be a numerical wind power forecast, which is an input to this approach. Then the model is given by the following It\^{o} stochastic differential equation,
-\begin{equation}
-\begin{split}
-dX_t&= \dot{p} \ dt - \theta_t(X_t - p_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t \quad t > 0 \\
-X_0&=x_0
-\end{split}
-\label{model:derivative_tracking_X}
-\end{equation}
+Let $p_t$ be a numerical wind power forecast, which is an input to this approach.
+Assume that the wind power generation forecasts are modeled as solutions to the following It\^{o} stochastic differential equation
+\begin{align}
+dX_t&= \dot{p}_t \ dt - \theta_t (X_t - p_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t\,, \quad t > 0 \nonumber \\
+X_0 &= x_0\,. \label{model:derivative_tracking_X}
+\end{align}
 
-We have that the process $X_t$ mean reverts to the wind power forecast $p_t$ and tracks its the time derivative $\dot{p}_t$.
-An example such mean reverting model without derivative tracking exhibits consistent lags as shown in Figure (\ref{fig:derivative_tracking}).
-See Section \ref{Section_7} for comparisons.
+According to the SDE specification in (\ref{model:derivative_tracking_X}), the process $X_t$ satisfies the two following properties: \begin{itemize}
+\item it is mean reverting to the wind power forecast $p_t$, and 
+\item it tracks the time derivative wind power forecast $\dot{p}_t$.  
+\end{itemize} 
+Observe that a mean reverting model without derivative tracking exhibits consistent lags, as it is shown in Figure (\ref{fig:derivative_tracking}). See Section \ref{Section_7} for comparisons.
 
@@
 \subsubsection*{Change of Variables:}
-To avoid differentiation of the forecast $p_t$ and simplify, we apply a change of variables $$V_t = X_t - p_t$$ \\
+To avoid differentiation of the forecast $p_t$ and simplify, we apply the change of variables $$V_t = X_t - p_t \,.$$
+
 The  model becomes,
-\begin{equation}
-\begin{split}
-dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
-V_0 & = v_0\\
+\begin{align}
+dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \nonumber \\ %\quad t > 0
+V_0 & = v_0 \,. \label{VtSDE}
 % \theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
-\end{split}\label{VtSDE}
-\end{equation}
+\end{align}
+%---END SECTION 2---
 
-\section{State independent diffusion: Lamparti transform} \label{Section_3}
+%---BEGIN SECTION 3---
+\section{State independent diffusion: Lamperti transform} \label{Section_3}
 
@@
 We are interested in state independent diffusion as it is more tractable and numerically stable.
-To achieve that, we apply a Lamperti transform to obtain the following state-independent diffusion SDE,
-\begin{equation}
-  \begin{split}
+To achieve that, we apply the Lamperti transform \autocite[98--100]{saso} to obtain the following state-independent diffusion SDE,
+\begin{align}
     dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} \ dt + \sqrt{2 \alpha \theta_t} dW_t \\
-    Z_0&=z_0
-  \end{split}
-\end{equation}
+    Z_0&=z_0 \,,
+\end{align}
 where the Lamperti trasform is given by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
-We can see in figure (\ref{fig:skew_after_lamperti}) the effects of the Lamperti transform on the forecast error data.
+We can see in Figure (\ref{fig:skew_after_lamperti}) the effects of the Lamperti transform on the forecast error data.
 The Lamperti transform has greatly reduced  the forecast error skewness and ensures that the process stays in the range $[0,1]$.
 Thus, in this case,  we can consider using a Gaussian density as a proxy transition density.
+%---END SECTION 3---
 
+%---BEGIN SECTION 4---
 \section{Likelihood in $V$ space} \label{Section_4}
@@
 
-\begin{equation}
-\begin{split}
-\frac{ \partial f }{\partial t } & (v ,t | x , s, \theta_0 , \alpha )= - \frac{\partial}{ \partial v} ( a( v;  p_t, \dot{p}_t, \theta_0 ) f( v ,t | x , s, \theta_0  , \alpha ) ) \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( b^2(v; p_t, \theta_0, \alpha  )  f(v ,t | x , s,\theta_0 , \alpha ) ) \quad  t < s\\
-\end{split}
-\end{equation}
+\begin{align}
+\frac{ \partial f }{\partial t } & (v ,t | x , s, \theta_0 , \alpha )= - \frac{\partial}{ \partial v} ( a( v;  p_t, \dot{p}_t, \theta_0 ) f( v ,t | x , s, \theta_0  , \alpha ) ) \nonumber \\
+& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( b^2(v; p_t, \theta_0, \alpha  )  f(v ,t | x , s,\theta_0 , \alpha ) ) \quad  t < s \,.\\
+\end{align}
+
 This is a parametric PDE which is computationally expensive to solve and optimize for every transition. Therefore, we consider approximate likelihood methods.
@@
 \begin{equation}
-\begin{split}
-\frac{d \E[ V^k_t]}{dt} = - k \theta_t \E [ V^k_t] + \frac{k(k-1)}{2} \E [ V^{k-2}_t  b(V^k_t;\theta_t, \alpha)]
-\end{split}
+\frac{d \mathbb{E}[ V^k_t]}{dt} = - k \theta_t \mathbb{E}[ V^k_t] + \frac{k(k-1)}{2} \mathbb{E}[ V^{k-2}_t  b(V^k_t;\theta_t, \alpha)]
 \end{equation}
+
 For $t\in [t_{n-1}, t]$, the first two moments are given by
-\begin{equation}
-\begin{split}
-\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t \\
-\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta_t(1+\alpha) + 2\alpha\theta_t m_1(t)(1-2p_t) \\
-&\quad + 2 \alpha\theta_t p_t (1-p_t)\\
-\end{split}
-\end{equation}
-with initial conditions, $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2$.
+\begin{align}
+\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t   \nonumber \\
+\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta_t(1+\alpha) + 2\alpha\theta_t m_1(t)(1-2p_t)  \nonumber \\
+&\quad + 2 \alpha\theta_t p_t (1-p_t) \,,
+\end{align}
+with initial conditions $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2 \,.$
 
@@
 Due to the non-linearity in the drift, we can only approximate the centered moments by the following ODEs,
-\begin{equation}
-\begin{split}
-\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\alpha) - \theta (1-2 p_t) \\
-\frac{d var(t)}{dt} &=  2 var(t) \theta_t (2p_t - 1 ) \tan(m_1 (t)) \sec(m_1 (t))\\
-& \quad + \theta_t (\alpha - 1) \sec^2(m_1 (t))  + 2 \theta_t \alpha\\
-\end{split}
-\end{equation}
+\begin{align}
+\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\alpha) - \theta (1-2 p_t) \nonumber \\
+\frac{d var(t)}{dt} &=  2 var(t) \theta_t (2p_t - 1 ) \tan(m_1 (t)) \sec(m_1 (t))   \nonumber \\
+& \quad + \theta_t (\alpha - 1) \sec^2(m_1 (t))  + 2 \theta_t \alpha \,.
+\end{align}
 
@@
 
-The shape parameters are given by,
+The shape parameters are given by
 \begin{equation}
-\xi_1 = - \frac{(1+\mu_t )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2} \quad \xi_2=  \frac{(\mu_t-1 )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2} \label{param_transformed_beta}
+\xi_1 = - \frac{(1+\mu_t )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2}\,, \quad \xi_2=  \frac{(\mu_t-1 )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2} \,, \label{param_transformed_beta}
 \end{equation}
-where $\mu_t = m_1 (t)$ and $\sigma_t^2= m_2 (t)- m_1 (t)^2$.
+where $\mu_t = m_1 (t)$ and $\sigma_t^2= m_2 (t)- m_1 (t)^2\,.$
 
@@
 
-To initialize the optimization process, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$.
+To initialize the optimization process, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$:
 
 \begin{equation}
- \arg\min \sum\limits_{i}^M \sum\limits_j^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 
+ \arg\min \sum\limits_{i}^M \sum\limits_j^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 ,
  \end{equation}
@@
 \begin{equation}
-\theta_0 \alpha = \frac{1}{M} \sum\limits_i^M \frac{ \sum\limits_j^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_j^N x_{i,j}(1-x_{i,j}) }
+\theta_0 \alpha = \frac{1}{M} \sum\limits_i^M \frac{ \sum\limits_j^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_j^N x_{i,j}(1-x_{i,j}) } \,.
 \end{equation}
@@
 \begin{enumerate}
-\item[Step 1.]  initialize
-\item[Step 2.]  optimize the log-likelihood function using  Nelder-Mead optimization algorithm on a mini-batch sampled with replacement.
-\item[Step 3. ] check if  accuracy threshold is reached. Else, re-initialize the optimization with the most recent result on a larger mini-batch.
+\item[Step 1.]  initialize;
+\item[Step 2.]  optimize the log-likelihood function using  Nelder-Mead optimization algorithm on a mini-batch sampled with replacement;
+\item[Step 3.] check if  accuracy threshold is reached. Else, re-initialize the optimization with the most recent result on a larger mini-batch.
 \end{enumerate}
+%---END SECTION 4---
 
+%---BEGIN SECTION 5---
 \section{Model Comparison} \label{Section_5}
-We compare the following candidate models to find the best-fit that maximizes the retained information,
+
+We compare two candidate models to find the best-fit that maximizes the retained information,
 \begin{itemize}
-  \item Model 0: This model is the most basic model without derivative tracking.
-  \begin{equation}
-  \begin{split}
-  dX_t &=  - \theta_0 (p_t-X_t) \  dt + \sqrt{2 \theta \alpha X_t (1-X_t)} \  dW_t  \\ %\quad t > 0
-  X_0 & = x_0
-\end{split}\label{M0}
-  \end{equation}
+  \item Model 0: This model does not feature derivative tracking.
+  \begin{align}
+  dX_t &=  - \theta_0 (p_t-X_t) \  dt + \sqrt{2 \theta \alpha X_t (1-X_t)} \  dW_t   \nonumber \\ %\quad t > 0
+  X_0 & = x_0 \,, \label{M0}
+ \end{align}
   with $\theta_t= \theta_0 $.
 
-  \item Model 1: This model features derivative tracking, i.e.
+%  \item Model 1: This model features derivative tracking, i.e.
 it is equivalent to (\ref{model:derivative_tracking_X}) with a diffusion term that is forecast dependent by including the term $p_t(1-p_t)$.
-  \begin{equation}
-  \begin{split}
-  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha p_t(1-p_t)(V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
-  V_0 & = v_0
-  \end{split}\label{M2}
-  \end{equation}
-  with $\theta_t$ given by (\ref{theta_t}).
+%  \begin{equation}
+%  \begin{split}
+%  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha p_t(1-p_t)(V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
+%  V_0 & = v_0
+%  \end{split}\label{M2}
+%  \end{equation}
+%  with $\theta_t$ given by (\ref{theta_t}).
 This model has been used by [ insert ref ] and [ insert ref ].
@@
 Therefore, we exclude this model from further discussions.
+%
 
-  \item Model 2: This model features derivative tracking, i.e. it's equivalent to (\ref{model:derivative_tracking_X}).
-\begin{equation}
-  \begin{split}
-  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
-  V_0 & = v_0
-  \end{split}\label{M2}
-  \end{equation}
+  \item Model 1: This model features derivative tracking, i.e. it is equivalent to (\ref{model:derivative_tracking_X}).
+  \begin{align}
+  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t   \nonumber \\ %\quad t > 0
+  V_0 & = v_0 \,, \label{M2}
+  \end{align}
   with $\theta_t$ given by (\ref{theta_t}).
@@
 
-\begin{table}[]
+\begin{table}
 \centering
@@
 \end{table}
+%---END SECTION 5---
 
+%---BEGIN SECTION 6---
 \section{Forecast Provider Comparison} \label{Section_6}
 We compare forecasts from two different companies for the same period.
-\begin{table}[]
+\begin{table}
 \centering
@@
 
- \begin{table}[]
+ \begin{table}[h]
  \centering
@@
  \end{table}
+%---END SECTION 6---
 
-%\section{Model on Disaggregated Data}
-%We apply Model 2 to disaggregated wind power production data and forecasts. The data is available in this case on an hourly basis. Results are shown in Table (\ref{tab:disagregated_data}).
-%
-%\begin{table}[]
-%\centering
-%\begin{tabular}{|c|c|c|c|}
-%\hline
-%Forecast Provider A & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
-%Wind Farm 1         &                                 &     &     \\ \hline
-%Wind Farm 2         &                                 &     &     \\ \hline
-%Wind Farm 3         &                                 &     &     \\ \hline
-%Wind Farm 4         &                                 &     &     \\ \hline
-%Wind Farm 5         &                                 &     &     \\ \hline
-%Wind Farm 6         &                                 &     &     \\ \hline
-%\end{tabular}
-%\caption{<discuss results>}
-%\label{tab:disagregated_data}
-%\end{table}
-%
-%\begin{table}[]
-%\centering
-%\begin{tabular}{|c|c|c|c|}
-%\hline
-%Forecast Provider B & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
-%Wind Farm 1         &                                 &     &     \\ \hline
-%Wind Farm 2         &                                 &     &     \\ \hline
-%Wind Farm 3         &                                 &     &     \\ \hline
-%Wind Farm 4         &                                 &     &     \\ \hline
-%Wind Farm 5         &                                 &     &     \\ \hline
-%Wind Farm 6         &                                 &     &     \\ \hline
-%\end{tabular}
-%\caption{\textless{}discuss results\textgreater{}}
-%\label{tab:disagregated_data_B}
-%\end{table}
-
+%---BEGIN SECTION 7---
 \section{Results} \label{Section_7}
@@
 \begin{figure}
-  \includegraphics[width=39mm,scale=1]{plots/alpha_conv_beta.png}
-  \includegraphics[width=39mm,scale=1]{plots/theta_conv_beta.png}
+  \includegraphics[width=56mm,scale=1]{plots/alpha_conv_beta.png}
+  \includegraphics[width=56mm,scale=1]{plots/theta_conv_beta.png}
   \caption{We show self-convergence of our algorithm applied to model $2$. We conlcude that the rate  matches that of of Monte Carlo. Data is from Uruguay pertaining to  year 2018. }
@@
 
-    \begin{figure}
-      \includegraphics[width=75mm,scale=1]{simulated/24hr/1099.pdf}
-      \includegraphics[width=75mm,scale=1]{simulated/24hr/1178.pdf}
+    \begin{figure}[h]
+      \includegraphics[width=70mm,scale=1]{simulated/24hr/1099.pdf}
+      \includegraphics[width=70mm,scale=1]{simulated/24hr/1178.pdf}
       \caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha )=(12,0.3)$.
@@
 
-    \begin{figure}
-      \includegraphics[width=75mm,scale=1]{confidence_intervals/24hr/31.pdf}
-      \includegraphics[width=75mm,scale=1]{confidence_intervals/24hr/820.pdf}
+    \begin{figure}[h]
+      \includegraphics[width=70mm,scale=1]{confidence_intervals/24hr/31.pdf}
+      \includegraphics[width=70mm,scale=1]{confidence_intervals/24hr/820.pdf}
        \caption{We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha )=(12,0.3)$.
@@
     \end{figure}
+%---END SECTION 7---
 
+%---BEGIN SECTION 8---
 \section{Conclusions} \label{Section_8}
@@
 Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.
+%---END SECTION 7---
 
-%\section*{Acknowledgement}
+%---REFERENCES---
 
-\section*{References}
-\begin{flushleft}
-- M\o ller, J.
-K., Zugno, M., \& Madsen, H.
-(2016).
-Probabilistic Forecasts of Wind Power Generation by Stochastic Differential Equation Models.
-Journal of Forecasting, 35(3), 189-205.
-doi:10.1002/for.2367 \linebreak
-- G.
-Giebel, R.
-Brownsword, G.
-Kariniotakis, M.
-Denhard, and C.
-Draxl, The State-Of-The-Art in Short-Term Prediction of Wind Power: A Literature Overview, 2nd edition.
-ANEMOS.plus, 2011, project funded by the European Commission under the 6th Framework Program, Priority 6.1: Sustainable Energy Systems.\linebreak
-- Ravn, H.
-F.
-(2006).
-Short term wind power prognosis with different success criteria.
-2006 International Conference on Probabilistic Methods Applied to Power Systems.
-doi:10.1109/pmaps.2006.360291 \linebreak
-- Chang, W. (2014). A Literature Review of Wind Forecasting Methods. Journal of Power and Energy Engineering, 02(04), 161-168. doi:10.4236/jpee.2014.24023\linebreak
-- Elkantassi, S., Kalligiannaki, E., \& Tempone, R.
-(2017).
-Inference And Sensitivity In Stochastic Wind Power Forecast Models.
-Proceedings of the 2nd International Conference on Uncertainty Quantification in Computational Sciences and Engineering (UNCECOMP 2017).
-doi:10.7712/120217.5377.16899
-\end{flushleft}
+\nocite{*}
 
-% {\small
-% \bibliographystyle{ieee}
-% \bibliography{egbib}
-% }
+%\printbibliography
+\printbibliography[keyword={Wind-SDE},title={References}]
 
 \end{document}
-
-% \begin{figure}[t]
-% \begin{center}
-% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%    \includegraphics[width=0.8\linewidth]{Forecast_data_68.pdf}
-%     \includegraphics[width=0.8\linewidth]{Forecast_data_82.pdf}
-% \end{center}
-%    \caption{Examples of wind power generation from the data set along with the wind power generation forecast.}
-% \label{fig:long}
-% \label{fig:onecol}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \begin{figure}[t]
-% \begin{center}
-% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%    \includegraphics[width=0.6\linewidth]{ellipse1193_samples_dN=14e-02.pdf}
-%     \includegraphics[width=0.6\linewidth]{ellipse_conv_samples_dN=14e-02.pdf}
-% \end{center}
-%    \caption{Left:Shrinkage of the ellipse determined by the Hessian matrix of the log-likelihood around the point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ (Axis are not in natural scale, arrows only to  eignevector direction).
-Right: Convergence of the major and semi-axis of the ellipse  of the Hessian of the log-likelihood at the point optimality $(\theta_0^*, \alpha^*)\approx (8,1)$.
-Note that it is slightly faster than the expected rate of $1/\sqrt{M}$.
-This is due to the correlation structure of the process $V_t$, thus a path may act  as more than one  uncorrelated sample.}
-% \label{ellipse_drawing}
-% \end{figure}
-
-%  \begin{figure}[t]
-% \begin{center}
-% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%    \includegraphics[width=0.9\linewidth]{ISO_100_samples_dN=14e-02.pdf}
-%    %\includegraphics[width=0.5\linewidth]{ISO_500_samples_dN=14e-02.pdf}
-%    %\includegraphics[width=0.5\linewidth]{ISO_1193_samples_dN=14e-02.pdf}
-% \end{center}
-%    \caption{Contour plot of the log-likelihood with only 100 sample paths, point of optimality $(\theta_0^*, \alpha^*)\approx (8,1)$ indicated by the  black dot.}
-% \label{contour}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%
-
-% \begin{figure}[t]
-% \begin{center}
-% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%    \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_31.pdf} %667
-%    \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_437.pdf}
-%    \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_82.pdf}
-%
-% \end{center}
-%    \caption{ Examples of confidence bands obtained for the full 72 hour forecasts.We can see that the model captures the fluctuations in the actual production with non-trivial and asymmetric confidence intervals.}
-% \label{fig:72hr}
-% \end{figure}
-%
-% \begin{figure}[t]
-% \begin{center}
-% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%    \includegraphics[width=0.8\linewidth]{6hr_forecast_CI_75.pdf}  %569
-%    \includegraphics[width=0.8\linewidth]{6hr_forecast_CI_59.pdf}
-%    %\includegraphics[width=0.9\linewidth]{6hr_forecast_CI_68.pdf}
-% \end{center}
-%    \caption{ Examples of confidence bands obtained for the first 6 hours of the forecasts.
-This is important as this specific forecasting company computes a new forecast every 6 hours for reliability.}
-% \label{fig:6hr}
-% \end{figure}
-
-%  \begin{figure}[t]
-% \begin{center}
-% %\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%    \includegraphics[width=0.8\linewidth]{72hr_forecast_CI_623.pdf}  %569
-% \end{center}
-%    \caption{ Examples of omitted data which corresponds to production control and manual energy management decisions.
-In this example,  wind power production was repeatedly curtailed at around 2 AM which is a period of low power demand.
-Automatic detection of such scenarios is to be incorporated in future works.}
-% \label{fig:6hr}
-% \end{figure}
-
-%We obtain the modified Beta distribution,
-%
-%\begin{equation}
-%\begin{split}
-%f_Y(y; \alpha , \beta )&= f_X(g^{-1}(y) ) \Big| \frac{\partial g^{-1}(y)}{\partial y }  \Big| \\
-%&= \frac{1}{B(\alpha, \beta) (b-a)} \Big(\frac{a-y}{b-a}\Big)^{\alpha -1}\Big(1-\frac{a-y}{b-a} \Big)^{\beta -1} \label{modified_Beta}
-%\end{split}
-%\end{equation}
-%where $B(\cdot,\cdot)$ is the Beta function. Also, we have that
-%\begin{equation}
-%\E[Y]= a + (b-a) \frac{\alpha}{\alpha + \beta}
-%\end{equation}
-%\begin{equation}
-%\V[Y]= (b-a)^2 \frac{\alpha \beta}{(\alpha + \beta)^2 (\alpha + \beta + 1)}
-%\end{equation}

### 2020-01-28 LaTeX_code/paper/paper_1line.tex
more on Lamperti

@@
 
-Our model in (\ref{VtSDE}) is  a state-dependent diffusion formulation, that is the diffusion of the SDE clearly depends on the state.
-We are interested in state independent diffusion as it is more tractable and numerically stable.
-To achieve that, we apply the Lamperti transform \autocite[98--100]{saso} to obtain the following state-independent diffusion SDE,
-\begin{align}
-    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} \ dt + \sqrt{2 \alpha \theta_t} dW_t \\
-    Z_0&=z_0 \,,
-\end{align}
-where the Lamperti trasform is given by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
+Our model (\ref{VtSDE}) for the forecast error has a diffusion term that depends on the state variable $V_t$.
+To estimate the unknown model parameters, a recommended technique is to modify the SDE (\ref{VtSDE}) by applying the so-called Lamperti transform (see \cite[40--41]{iacus1}, \cite{moma}, \cite[98--100]{saso}) to the process $V$ to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
+\\
+
+We consider the following transformation 
+\begin{equation}
+Z_t = h(V_t) = \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
+\end{equation}
+where $\xi$ is an arbitrary point of the state space of the process $V$. The choice of $\xi = \frac{1}{2} - p_t$, where $p_t$ is a known input, leads to the process 
+\begin{equation}
+Z_t = h(V_t) = \arcsin (2(V_t + p_t) -1)\,,
+\end{equation}
+that, after applying It\^{o}'s formula on $h(V_t)$, gives the state-independent diffusion SDE
+\begin{equation}
+dZ_t = \left[  \frac{- \theta_t V_t}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{2} \frac{\left( \frac{1}{2} - (V_t + p_t)\right)}{(V_t + p_t)(1 - V_t - p_t)}  \right] \,dt + \sqrt{2 \theta_t \alpha}\, dW_t \,.
+\label{eq:stindepSDE}
+\end{equation}
+After replacing $V_t = \frac{\sin(Z_t) + 1}{2} - p_t$ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
+\begin{equation}
+dZ_t = \frac{- \theta_t (\sin(Z_t) + 1 - 2 p_t) + \frac{\sin{Z_t}}{2}}{\cos{Z_t}} \,dt + \sqrt{2 \theta_t \alpha}\, dW_t \,. \label{eq:stindepSDE}
+\end{equation}
+
+%\begin{align}
+%    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} \ dt + \sqrt{2 \alpha \theta_t} dW_t \\
+%    Z_0&=z_0 \,,
+%\end{align}
+%where the Lamperti trasform is given by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
+
 We can see in Figure (\ref{fig:skew_after_lamperti}) the effects of the Lamperti transform on the forecast error data.

### 2020-01-29 LaTeX_code/paper/paper_1line.tex
ok Lamperti

@@
 \begin{equation}
-dZ_t = \left[  \frac{- \theta_t V_t}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{2} \frac{\left( \frac{1}{2} - (V_t + p_t)\right)}{(V_t + p_t)(1 - V_t - p_t)}  \right] \,dt + \sqrt{2 \theta_t \alpha}\, dW_t \,.
+dZ_t = \left[  \frac{- \theta_t V_t}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{2} \frac{\theta_t \alpha \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \right] \,dt + \sqrt{2 \theta_t \alpha}\, dW_t \,.
 \label{eq:stindepSDE}
@@
 \begin{equation}
-dZ_t = \frac{- \theta_t (\sin(Z_t) + 1 - 2 p_t) + \frac{\sin{Z_t}}{2}}{\cos{Z_t}} \,dt + \sqrt{2 \theta_t \alpha}\, dW_t \,. \label{eq:stindepSDE}
+dZ_t = \frac{- \theta_t (\sin(Z_t) + 1 - 2 p_t) + \theta_t \alpha \sin{(Z_t)}}{\cos{(Z_t)}} \,dt + \sqrt{2 \theta_t \alpha}\, dW_t \,. 
 \end{equation}
@@
 We can see in Figure (\ref{fig:skew_after_lamperti}) the effects of the Lamperti transform on the forecast error data. 
-The Lamperti transform has greatly reduced  the forecast error skewness and ensures that the process stays in the range $[0,1]$.
-Thus, in this case,  we can consider using a Gaussian density as a proxy transition density.
+The Lamperti transform has greatly reduced the forecast error skewness, ensuring that the process stays in the range $[0,1]$.
+Therefore, in this case, the transition densities of the process Z can be approximated through Gaussian densities.
 %---END SECTION 3---
@@
 
-Since $V_t$ defined by our SDE is Markovian, the likelihood function can be written as a product of transition densities.
+The It\^{o} process $V_t$ defined by the SDE (\ref{VtSDE}) is Markovian, then the likelihood function can be written as a product of transition densities.
 Consider the set of $M$ paths with $N$ observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$, observed in $\Delta_N$ intervals.
@@
 \begin{equation}
-\mathcal{L}(\theta;V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}},\bm{\theta} )  \rho (V_{j,0})
+\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}},\bm{\theta} )  \rho (V_{j,0})
 \label{likelihood}

### 2020-02-01 LaTeX_code/paper/paper_1line.tex
a version for FPK equation

@@
-\documentclass{article}
+\documentclass[11pt,english]{article}
 
@@
 \usepackage{xcolor}
+
+\usepackage{authblk}
 
@@
 
-\author{ Waled Alhaddad\textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
-\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University,  Germany
- \\ \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539) , Villetaneuse , France }
+\author[1]{Waled Alhaddad}
+\author[2]{Ahmed Kebaier}
+\author[3]{ Ra\'ul  Tempone}
+%\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
+\affil[1,3]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
+\affil[3]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}
+\affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
+
+%\author{ Waled Alhaddad \textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
+%\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University, Germany
+% \\ \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
 
@@
 %\thispagestyle{empty}
-{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, model selection, sensitivity.}
+
 %%%%%%%%% ABSTRACT
@@
 
+{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, model selection, sensitivity.}
+
 %%%%%%%%% BODY TEXT
@@
 
-Reliable wind power generation forecasting is crucial for the following applications [ref]:
+Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
 \begin{itemize}
@@
 We introduce the following phenomenological model.
-Let $\{X_t, \, t>0\}$  be the  wind power generation forecasts stochastic process defined by the following parameterized stochastic differential equation (SDE)
+Let $X = \{X_t, \, t>0\}$  be the  wind power generation forecasts stochastic process defined by the following parameterized stochastic differential equation (SDE)
 
-\begin{align}
-dX_t & =  a(X_t; p_t, \dot{p}_t,\bm{\theta}) \ dt + b (X_t; p_t, \bm{\theta} ) \ dW_t \nonumber \\ 
-X_0 & =  x_0\,,   \label{eq:main}
-\end{align}
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    dX_t \!\!\!&=  a(X_t; p_t, \dot{p}_t,\bm{\theta}) \,dt + b (X_t; p_t, \bm{\theta} ) \,dW_t  \\
+     X_0  \!\!\!&=  x_0,
+  \end{array}\right. \label{eq:main}
+\end{equation}
+
 where
@@
 
-We consider the following transformation 
+We consider the following Lamperti transformation 
 \begin{equation}
@@
 
-We can see in Figure (\ref{fig:skew_after_lamperti}) the effects of the Lamperti transform on the forecast error data. 
-The Lamperti transform has greatly reduced the forecast error skewness, ensuring that the process stays in the range $[0,1]$.
-Therefore, in this case, the transition densities of the process Z can be approximated through Gaussian densities.
+We can see in Figure (\ref{fig:skew_after_lamperti}) the effect of the Lamperti transformation upon the forecast error data. 
+The Lamperti transformation has greatly reduced the forecast error skewness, ensuring that the process stays in the range $[0,1]$.
+Therefore, in this case, the transition densities of the process Z can be adequately approximated through Gaussian densities.
 %---END SECTION 3---
@@
 
-The It\^{o} process $V_t$ defined by the SDE (\ref{VtSDE}) is Markovian, then the likelihood function can be written as a product of transition densities.
-Consider the set of $M$ paths with $N$ observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$, observed in $\Delta_N$ intervals.
+Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t >0 \}$ is sampled at $N$ equispaced discrete points with length interval $\Delta_N$, and let $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ denote this random sample.
 
+Let $\rho_i(v \vert v_{j, t_{i-1}} ; \bm{\theta})$ denote the conditional probability density of $V_{j, t_i}$ given $V_{j, t_{i-1}} = v_{j, t_{i-1}}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha)$ are the unknown model parameters.
+
+The It\^{o} process $V$ defined by the SDE (\ref{VtSDE}) is Markovian, then the likelihood function of the data can be written as the following product of transition densities:  
+%Consider the set of $M$ paths with $N$ observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$, observed in $\Delta_N$ intervals.
 \begin{equation}
-\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}},\bm{\theta} )  \rho (V_{j,0})
+\mathcal{L}(\bm{\theta}; V^{M,N}) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho_i ( {V_{j, t_i}| V_{j, t_{i-1}}} ; \bm{\theta} )  \, \rho_0 (V_{j, t_0}) \,.
 \label{likelihood}
@@
 
-The transition densities can be exactly obtained by solving the following parametric Fokker-Planck equation,
+The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized, for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}, \cite[61-68]{saso}):
 
 \begin{align}
-\frac{ \partial f }{\partial t } & (v ,t | x , s, \theta_0 , \alpha )= - \frac{\partial}{ \partial v} ( a( v;  p_t, \dot{p}_t, \theta_0 ) f( v ,t | x , s, \theta_0  , \alpha ) ) \nonumber \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( b^2(v; p_t, \theta_0, \alpha  )  f(v ,t | x , s,\theta_0 , \alpha ) ) \quad  t < s \,.\\
+\frac{ \partial f }{\partial t } & \rho_i(v_{j,i} ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} )= - \frac{\partial}{ \partial v} (- \theta_t v \, \rho_i(v ,t_{j,i} \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) ) \nonumber \\
+& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( 2 \theta_t \alpha (v+ p_t) (1 - v- p_t) \, \rho_i(v ,t_{j,i} \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) )\,,  \label{eq:fpk}
 \end{align}
+subject to the initial conditions $\rho_{i-1}(v , t_{j, i-1} , \bm{\theta} ) = \delta(v - V_{j, t_{i-1}}) \,,$ where $ \delta(v - V_{j, t_{i-1}})$ is the Dirac-delta generalized function centered at $ V_{j, t_{i-1}}\,,$ and suitable boundary conditions.
 
-This is a parametric PDE which is computationally expensive to solve and optimize for every transition. Therefore, we consider approximate likelihood methods.
+Nevertheless, closed-form solutions to this initial-boundary value problem can be obtained only in a few cases.
+Besides, solving numerically (\ref{eq:fpk}) at every transition step is computationally expensive.
+Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.
 

### 2020-02-03 LaTeX_code/paper/paper_1line.tex
last version added

@@
 
-Nevertheless, closed-form solutions to this initial-boundary value problem can be obtained only in a few cases.
-Besides, solving numerically (\ref{eq:fpk}) at every transition step is computationally expensive.
+Closed-form solutions to initial-boundary value problem for SDEs can be obtained only in a few cases.
+Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
 Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.
+Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.
 
 \subsection{Approximate Likelihood}
-Solving for transition densities of the process $V_t$ requires solving the Fokker-Planck equation at every step which is computationally prohibitive.
+
 A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints which give rise to asymmetric forecasting errors as seen in figure (\ref{fig:skew_data}).\\

### 2020-02-05 LaTeX_code/paper/paper_1line.tex
paper version with annotations meeting feb 4

@@
 
+{\color{red} Add AMS Classification.}
+
 %%%%%%%%% BODY TEXT
@@
 \item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
-\item Operation scheduling of non-controlable power plants.
+\item Operation scheduling of controlable power plants.
 \item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
@@
 Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles.
-However, there is a lacking in simulating and producing data driven stochastic forecasts based on real-world performance of forecasting models.
+{\color{red} Expand discussion about works on probabilistic forecasting.} However, there is a lacking in simulating and producing data driven stochastic forecasts based on real-world performance of forecasting models.
 It is crucial to capture actual performance of a forecast as it has been known that different forecasting technologies exhibits different behavior for different wind farms and seasons [ref].
@@
 
+{\color{red} Change this paragraph. Discuss with the global dataset, the dataset after removing days when curtailing has been detected, the data set without curtailing and with Lamperti transform.}
 We use a year long data set from Uruguay based on 1000 observation paths, each of which is 72-hours long with observations recorded every 10 min.
@@
 See Figure (\ref{fig:skew_data}).
+{\color{red} Analysis of the autocorrelation, removing days to achieve independence.}
 
@@
 In yellow is an hourly wind power production forecast.
-In blue is the actual wind power production recorded in 10 minute intervals.}
+In blue is the actual wind power production recorded in 10 minute intervals.
+{\color{red} New figures with 2019 Uruguayan dataset.}}
   \label{fig:sample_data}
@@
 Low power is when produced power is less than $0.3$, mid power is when it is between $0.3$ and $0.6$ and high power when is larger than $0.6$.
-}
+{\color{red} New figures with 2019 Uruguayan dataset.}}
   \label{fig:skew_data}
@@
   \includegraphics[width=38mm,scale=1]{plots/hist_high_lamperti.pdf}
-  \caption{We observe that skewness has been greatly reduced after the Lamperti transformation. This motivates us to use a Gaussian transition density as a proxy density.}
+  \caption{We observe that skewness has been greatly reduced after the Lamperti transformation.
+This motivates us to use a Gaussian transition density as a proxy density.
+{\color{red} New figures with 2019 Uruguayan dataset.}}
   \label{fig:skew_after_lamperti}
@@
 Assume that the wind power generation forecasts are modeled as solutions to the following It\^{o} stochastic differential equation
-\begin{align}
-dX_t&= \dot{p}_t \ dt - \theta_t (X_t - p_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t\,, \quad t > 0 \nonumber \\
-X_0 &= x_0\,. \label{model:derivative_tracking_X}
-\end{align}
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    dX_t \!\!\!&= \dot{p}_t \ dt - \theta_t (X_t - p_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t\,, \quad t > 0  \\
+   X_0  \!\!\!&=  x_0 \,.
+ \end{array}\right.  \label{model:derivative_tracking_X}
+\end{equation}
 
@@
   \end{equation}
-where $\theta_t>0$ is a time-dependent parameter that controls the speed of reversion.
+where $\theta_t>0$ is a time-dependent parameter that controls the speed of reversion. {\color{red} Derivative tracking does not assure that the paths of the process $X$ take values in $[0,1]$.}
 
@@
   \end{equation}
-  where $\alpha >0$ is a constant parameter that controls the path variability. This diffusion term belongs to the Pearson diffusion family and , in particular, it is a Jacobi type diffusion.
+  where $\alpha >0$ is a constant parameter that controls the path variability.
+This diffusion term belongs to the Pearson diffusion family and , in particular, it is a Jacobi type diffusion.
+{\color{red} Add expressions and references for these class of diffusions, for example \cite{iacus1}.}
 
@@
 \begin{equation}
-\frac{- |\dot{p_t}|}{p_t} \leq \theta \leq \frac{|\dot{p}_t|}{1- p_t}
+\frac{- |\dot{p_t}|}{p_t} \leq \theta_t \leq \frac{|\dot{p}_t|}{1- p_t}
 \end{equation}
@@
 \begin{equation}
-\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \theta_0 >0 \label{theta_t}
+\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \theta_0 >0\,. \label{theta_t}
 \end{equation}
+
+{\color{red} The expression for $\theta_t$ is important: $\theta_t$ depens on $t$ through $\dot{p_t}$ and $p_t$.
+Besides it is parsimonious because only one unkonwn parameter appear in \ref{theta_t}.
+}
 
@@
 The  model becomes,
-\begin{align}
-dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \nonumber \\ %\quad t > 0
-V_0 & = v_0 \,. \label{VtSDE}
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    dV_t \!\!\!&=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t   \\ %\quad t > 0
+V_0 \!\!\!&=  v_0 \,. \label{VtSDE}
 % \theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
-\end{align}
+\end{array}\right. 
+\end{equation}
 %---END SECTION 2---
@@
 
-We consider the following Lamperti transformation 
+We consider the following Lamperti transformation  {\color{red} (Modify the transformation to obtain an unitary diffusion coefficient in the SDE for $Z$.
+Remind that in continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
+Besides, it can be unstable to work with low frequency.
+If the frequency of the data is too low, the Lamperti transform helps to detect this problem (in principle, it is not clear how to determine the right frequency for estimation.
+)}
 \begin{equation}
@@
 \begin{equation}
-\mathcal{L}(\bm{\theta}; V^{M,N}) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho_i ( {V_{j, t_i}| V_{j, t_{i-1}}} ; \bm{\theta} )  \, \rho_0 (V_{j, t_0}) \,.
+\mathcal{L}(\bm{\theta}; V^{M,N}) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j, t_i}| V_{j, t_{i-1}}} ; p_{[t_{i-1}, t_{i}]},  \bm{\theta} )  \, \rho_0 (V_{j, t_0}) \,.
 \label{likelihood}
 \end{equation}
+
+ {\color{red} In \ref{likelihood} modify the expression for $\rho_0$ contemplating the lag, say $\delta$, between the time when the forecast is done and the first time of forecasting.
+$\rho_0$ can be written as a conditional density between these two times.
+Once $\theta_0$ and $\alpha$ have been estimated, one could estimate $\delta$.}
 
@@
 \end{align}
-subject to the initial conditions $\rho_{i-1}(v , t_{j, i-1} , \bm{\theta} ) = \delta(v - V_{j, t_{i-1}}) \,,$ where $ \delta(v - V_{j, t_{i-1}})$ is the Dirac-delta generalized function centered at $ V_{j, t_{i-1}}\,,$ and suitable boundary conditions.
+subject to the initial conditions $\rho_{i-1}(v , t_{j, i-1} , \bm{\theta} ) = \delta(v - V_{j, t_{i-1}}) \,,$ where $ \delta(v - V_{j, t_{i-1}})$ is the Dirac-delta generalized function centered at $ V_{j, t_{i-1}}\,.$
 
@@
 A suitable candidate for a proxy transition density is a Beta probability distribution as it is compactly supported and can morph into symmetric and asymmetric shapes.
+{\color{red} Move this sentence to next section.}
 
@@
 \subsection{Optimization}
+{\color{red} Rewrite the discussion to obtain fast initial estimate for the two unknow parameters.}
 
-To initialize the optimization process, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$:
+To initialize the optimization process for the likelihood function of the process $V$, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$: {\color{red} Add explanation regarding the motivation for this objective function.}
 
@@
 
- By assuming ergodicity, we can obtain a first estimate on the product of the parameters as follows,
+ By assuming ergodicity {\color{red} not ergodicity, instead simply for the quadratic variation formula.}, we can obtain a first estimate on the product of the parameters as follows,
 
@@
 \begin{itemize}
-  \item Model 0: This model does not feature derivative tracking.
+  \item Model 1: This model does not feature derivative tracking.
   \begin{align}
@@
 
-  \item Model 1: This model features derivative tracking, i.e. it is equivalent to (\ref{model:derivative_tracking_X}).
+  \item Model 2: This model features derivative tracking, i.e. it is equivalent to (\ref{model:derivative_tracking_X}).
   \begin{align}
@@
 Model   &  parameters $(\theta_0, \alpha)$   & AIC & BIC \\ \hline
-Model 0 &  $(\add,\add) $    &  \add   &  \add   \\ \hline
+Model 1 &  $(\add,\add) $    &  \add   &  \add   \\ \hline
 Model 2 &   $(\add,\add)$   &  \add   &   \add    \\ \hline
@@
 
+{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models (if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.)}
+
+{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
+How many data we need to achive enough accuracy for the estimates of the two parameters?
+Generally, such accuracy is application dependent}
+
  We are able to obtain the parameters based on the complete data sets. Using the different models variations, we are able to simulate wind power production given a forecast. We see in figures ()-()
@@
   \includegraphics[width=56mm,scale=1]{plots/theta_conv_beta.png}
-  \caption{We show self-convergence of our algorithm applied to model $2$. We conlcude that the rate  matches that of of Monte Carlo. Data is from Uruguay pertaining to  year 2018. }
+  \caption{We show self-convergence of our algorithm applied to model $2$.
+We conlcude that the rate  matches that of of Monte Carlo.
+Data is from Uruguay pertaining to  year 2018.{\color{red} Figure with data 2019} }
 \end{figure}
@@
 Forecast is from Uruguay pertaining to  year 2018.
-}
+{\color{red} Figure with data 2019}}
     \end{figure}
@@
 Forecast and data is from Uruguay pertaining to  year 2018.
-}
+{\color{red} Figure with data 2019}}
     \end{figure}
@@
 \section{Conclusions} \label{Section_8}
-
-{\color{red} Application: Using this tool, it is possible to iterate over hyper parameters for the wind power forecasting, reaching an optimal forecasting.}
 

### 2020-02-06 LaTeX_code/paper/paper_1line.tex
change figures in paper

@@
 \begin{figure}
-  \includegraphics[width=60mm,scale=1]{plots/data_1516064400.pdf}
-  \includegraphics[width=60mm,scale=1]{plots/data_1516323600.pdf}\\
+  \includegraphics[width=60mm,scale=1]{plots/5.eps}
+  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
+   \includegraphics[width=60mm,scale=1]{plots/661.eps}
+  \includegraphics[width=60mm,scale=1]{plots/805.eps}
   \caption{Two samples from the Uruguayan of 2018.
@@
 \begin{figure}
-  \includegraphics[width=38mm,scale=1]{plots/hist_low.pdf}
-  \includegraphics[width=38mm,scale=1]{plots/hist_mid.pdf}
-  \includegraphics[width=38mm,scale=1]{plots/hist_high.pdf}
+  \includegraphics[width=60mm,scale=1]{plots/LP_6.eps}
+  \includegraphics[width=60mm,scale=1]{plots/MP_6.eps}\\
+   \includegraphics[width=60mm,scale=1]{plots/HP_6.eps}
+  \includegraphics[width=60mm,scale=1]{plots/AP_6.eps}
   \caption{We see that forecast errors exhibit skewness near the boundries (i.e.
@@
 \begin{figure}
-  \includegraphics[width=38mm,scale=1]{plots/hist_low_lamperti.pdf}
-  \includegraphics[width=38mm,scale=1]{plots/hist_mid_lamperti.pdf}
-  \includegraphics[width=38mm,scale=1]{plots/hist_high_lamperti.pdf}
+  \includegraphics[width=60mm,scale=1]{plots/LP.eps}
+  \includegraphics[width=60mm,scale=1]{plots/MP.eps}\\
+   \includegraphics[width=60mm,scale=1]{plots/HP.eps}
+  \includegraphics[width=60mm,scale=1]{plots/AP.eps}
   \caption{We observe that skewness has been greatly reduced after the Lamperti transformation.
@@
 {\color{red} New figures with 2019 Uruguayan dataset.}}
+  \label{fig:skew_after_lamperti}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=60mm,scale=1]{plots/LP_t.eps}
+  \includegraphics[width=60mm,scale=1]{plots/MP_t.eps}\\
+   \includegraphics[width=60mm,scale=1]{plots/HP_t.eps}
+  \includegraphics[width=60mm,scale=1]{plots/AP_t.eps}
+  \caption{Transitions.}
+  \label{fig:skew_after_lamperti}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=60mm,scale=1]{plots/LP_t_LP.eps}
+  \includegraphics[width=60mm,scale=1]{plots/MP_t_LP.eps}\\
+   \includegraphics[width=60mm,scale=1]{plots/HP_t_LP.eps}
+  \includegraphics[width=60mm,scale=1]{plots/AP_t_LP.eps}
+  \caption{Transitions after the Lamperti transform.}
   \label{fig:skew_after_lamperti}
@@
 \begin{equation}
- \arg\min \sum\limits_{i}^M \sum\limits_j^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 ,
+ \arg\min \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 ,
  \end{equation}
@@
 \begin{equation}
-\theta_0 \alpha = \frac{1}{M} \sum\limits_i^M \frac{ \sum\limits_j^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_j^N x_{i,j}(1-x_{i,j}) } \,.
+\theta_0 \alpha = \frac{1}{M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
 \end{equation}

### 2020-02-06 python_code/path_simulator_copy.py

@@ -1,0 +1,55 @@
+import os
+import sys
+os.chdir(sys.path[0])
+from Base_plus import *
+
+import config.loadconfig
+
+warnings.filterwarnings('error', '.*invalid value encountered.*',)
+
+parser = argparse.ArgumentParser(description='Likelihood Evaluator v1.0')
+parser.add_argument('-filename', help=' Config file name or path')
+parser.add_argument('--version', action='version', version='Likelihood Evaluator v1.0')
+args = parser.parse_args()
+
+print( ' loading configuration ')
+# args.filename
+config_file= open(args.filename)  #config/beta_config.JSON
+
+setup=config.loadconfig.Test(config_file)
+
+
+forecast_data_in=np.load(setup.data_path)
+
+forecast_data_in.shape
+
+data=np.swapaxes(forecast_data_in, 0,1)
+
+data_unique=np.unique(data[:,:,:], axis=1  )
+
+
+now = dtM.datetime.now();
+current_time=now.strftime("%y-%m-%d-%H-%M-%S")
+script_name='sample_paths_'
+current_plotting_dir='plots/'+ script_name +current_time
+# os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
+os.makedirs(current_plotting_dir,exist_ok=True)
+
+print(current_plotting_dir)
+
+current_list= list(range(0, setup.num_paths)) #=list(range(0, data.shape[1])) #full_set
+M=1 #number of simulated paths in each plot
+N=427
+disct_in= disct(N=N, dt=1, M=M) #M is number of paths wanted in ensamble
+real_in=real(1.36, 0.020) # SDE parameters to be generated from
+
+
+path_simulator(forecast_data_inter=data_unique,hours=59,\
+    real_in=real_in, disct_in=disct_in,list_forecast_number=current_list,\
+    dir_path=current_plotting_dir)
+    # Notice: We plot from 0 transitions to "hours" transitions. E,g,. is "hours" = 100, we plot from 0 to 100
+    # where this 100 has units transitions.
+
+# path_simulator(forecast_data_inter=data,hours=427,\
+#     real_in=real_in, disct_in=disct_in,list_forecast_number=current_list,\
+#     dir_path=current_plotting_dir)

### 2020-02-07 LaTeX_code/paper/paper_1line.tex
Added captions

@@
 
+{\color{red} Show with plots as the use of wind and solar power is increasing.}\\
 Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
@@
   \includegraphics[width=60mm,scale=1]{plots/805.eps}
-  \caption{Two samples from the Uruguayan of 2018.
-Each sample compromises of two 72-hour paths.
-In yellow is an hourly wind power production forecast.
-In blue is the actual wind power production recorded in 10 minute intervals.
-{\color{red} New figures with 2019 Uruguayan dataset.}}
+  \caption{Four samples from the Uruguayan data of 2019.
+Each sample compromises of two 24-hour paths.
+In blue is an hourly wind power production forecast.
+In orange is the actual wind power production recorded in 10 minute intervals from the company ADME.}
   \label{fig:sample_data}
@@
   \includegraphics[width=60mm,scale=1]{plots/AP_6.eps}
-  \caption{We see that forecast errors exhibit skewness near the boundries (i.e.
-low and high power production regimes.).
-Low power is when produced power is less than $0.3$, mid power is when it is between $0.3$ and $0.6$ and high power when is larger than $0.6$.
-{\color{red} New figures with 2019 Uruguayan dataset.}}
+  \caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production.
+Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$.
+We have a total of 363 days to use.}
   \label{fig:skew_data}
@@
   \includegraphics[width=60mm,scale=1]{plots/AP.eps}
-  \caption{We observe that skewness has been greatly reduced after the Lamperti transformation.
-This motivates us to use a Gaussian transition density as a proxy density.
-{\color{red} New figures with 2019 Uruguayan dataset.}}
+  \caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
   \label{fig:skew_after_lamperti}
@@
   \includegraphics[width=60mm,scale=1]{plots/AP_t.eps}
-  \caption{Transitions.}
+  \caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
   \label{fig:skew_after_lamperti}
@@
   \includegraphics[width=60mm,scale=1]{plots/AP_t_LP.eps}
-  \caption{Transitions after the Lamperti transform.}
+  \caption{Transitions after the Lamperti transform.
+The transitions now present a normal Gaussian shape.
+This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
   \label{fig:skew_after_lamperti}

### 2020-02-07 LaTeX_code/paper/paper_1line.tex
Corrected some red text in the paper, corrected all dates and information related with data. Removed many unuseful old plots

@@
-\documentclass[11pt,english]{article}
+\documentclass[11pt]{article}
 
@@
 \usepackage{bm} % more powerful version to get bold
+\usepackage{siunitx}
 
@@
 The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of information criteria.
-We apply the model to historical French and Uruguayan wind power production data and forecasts on the period (2017-2018).
+We apply the model to historical Uruguayan wind power production data and forecasts on the year 2019.
 
@@
 
-{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, model selection, sensitivity.}
+{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, model selection.}
 
@@
 
-{\color{red} Show with plots as the use of wind and solar power is increasing.}\\
-Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
+\begin{figure}
+  \includegraphics[width=120mm,scale=1]{plots/1.png}
+  \caption{Installed wind and solar power over the years.
+We recall the importance of accurate forecasts to use green energies optimally.
+{\color{red} We still have to ensure that the source is trusthable (Renzo will do it)}.}
+\end{figure}Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
 \begin{itemize}
@@
 
-Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations (SDEs).
+Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations.
 Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion and non-Gaussian approximations.
-We apply the model to French and Uruguayan wind power forecasts together with historical wind power production data pertaining to the year 2017-2018.
+We apply the model to Uruguayan wind power forecasts together with historical wind power production data pertaining to the year 2019.
 
 {\color{red} Change this paragraph. Discuss with the global dataset, the dataset after removing days when curtailing has been detected, the data set without curtailing and with Lamperti transform.}
-We use a year long data set from Uruguay based on 1000 observation paths, each of which is 72-hours long with observations recorded every 10 min.
-In total, it is a data set of approximatly half a million data points recorded in 2018.
+We have available a year long data set from Uruguay based on 363 observation paths, each of which is 24-hours long with observations recorded every 10 min.
+In total, it is a data set of approximately fifty thousand data points recorded in 2019.
 See Figure (\ref{fig:sample_data}).
-The data is normalized with respect to the maximuim power capacity of wind power production in Uruguay.
-The asymmetry or skew nature of the data is clear when inspected for different power production levels.
-We split the aggregated data into a low, meduim and high power range.
-See Figure (\ref{fig:skew_data}).
-{\color{red} Analysis of the autocorrelation, removing days to achieve independence.}
+The data is normalized with respect to the maximuim power capacity of wind power production in Uruguay, which is $\SI{1474}{\mega\watt}$.
+However, sometimes the real production is artificially modifies due to curtailing.
+This effect becomes clear when we inspect for different power production levels.
+We split the available data into a low, meduim and high power range.
+See Figure (\ref{fig:data_curtailing}).\\
+We identify and remove the days with curtailing, removing a total of 108 days.
+From the resulting 255 days, we use 127 days to train the system and 128 to test it.
+Also, to avoid correlation between days, we intercalate the days we use for training and testing ({\color{red} Show that 24h is enough to ensure independence}).
 
@@
 We have a total of 363 days to use.}
-  \label{fig:skew_data}
+  \label{fig:data_curtailing}
 \end{figure}
@@
   \caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
-  \label{fig:skew_after_lamperti}
+  \label{fig:data_after_clean}
 \end{figure}
@@
   \caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
-  \label{fig:skew_after_lamperti}
+  \label{fig:error_transitions}
 \end{figure}
@@
 This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
-  \label{fig:skew_after_lamperti}
+  \label{fig:LP_transitions}
 \end{figure}
@@
 Besides it is parsimonious because only one unkonwn parameter appear in \ref{theta_t}.
+Recall it is an upped bound for the real inequality.
 }
@@
 \begin{equation}
-\mathcal{L}(\bm{\theta}; V^{M,N}) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j, t_i}| V_{j, t_{i-1}}} ; p_{[t_{i-1}, t_{i}]},  \bm{\theta} )  \, \rho_0 (V_{j, t_0}) \,.
+\mathcal{L}(\bm{\theta},\delta; V^{M,N}) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j, t_i}| V_{j, t_{i-1}}} ; p_{[t_{i-1}, t_{i}]},  \bm{\theta} )  \, \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
 \label{likelihood}
@@
 \end{tabular}
-\caption{We compare the parameters obtained in both the original and Lamperti space. Parameters have been obtained based on \add data points from the Uruguayan pertaining to the year 2018  \add }.
-\label{tab:model_comparison}
+\caption{We compare the parameters obtained in both the original and Lamperti space. Parameters have been obtained based on \add data points from the Uruguayan pertaining to the year 2019\add .}
+\label{tab:model_comparison_2}
 \end{table}
@@
   \includegraphics[width=56mm,scale=1]{plots/theta_conv_beta.png}
-  \caption{We show self-convergence of our algorithm applied to model $2$.
-We conlcude that the rate  matches that of of Monte Carlo.
-Data is from Uruguay pertaining to  year 2018.{\color{red} Figure with data 2019} }
+  \caption{We show self-convergence of our algorithm applied to model $2$. We conlcude that the rate  matches that of of Monte Carlo. Data is from Uruguay pertaining to year 2019.}
 \end{figure}
@@
       \caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha )=(12,0.3)$.
-Forecast is from Uruguay pertaining to  year 2018.
-{\color{red} Figure with data 2019}}
+Forecast is from Uruguay pertaining to  year 2019.}
     \end{figure}
@@
 Actual production plotted in retrospect.
-Forecast and data is from Uruguay pertaining to  year 2018.
-{\color{red} Figure with data 2019}}
+Forecast and data is from Uruguay pertaining to  year 2019.}
     \end{figure}

### 2020-02-07 LaTeX_code/paper/paper_1line.tex
Minor edits

@@
 
-\author[1]{Waled Alhaddad}
+%\author[1]{Waled Alhaddad}
+\author[1]{Renzo Caballero}
 \author[2]{Ahmed Kebaier}
-\author[3]{ Ra\'ul  Tempone}
+\author[3]{Marco Scavino}
+\author[4]{ Ra\'ul  Tempone}
 %\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
-\affil[1,3]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
-\affil[3]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}
+\affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
 \affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
+\affil[3]{Universidad de la Rep\'ublica, Montevideo Uruguay}
+\affil[4]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}
 
@@
 We recall the importance of accurate forecasts to use green energies optimally.
-{\color{red} We still have to ensure that the source is trusthable (Renzo will do it)}.}
+{\color{red} We still have to ensure that the source is trustworthy (Renzo will do it)}.
+Redo the figure as well}
 \end{figure}Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
@@
 In blue is an hourly wind power production forecast.
-In orange is the actual wind power production recorded in 10 minute intervals from the company ADME.}
+In orange is the actual wind power production recorded in 10 minute intervals from  ADME.}
   \label{fig:sample_data}

### 2020-02-09 LaTeX_code/MATLAB_readMe/MATLAB_readMe.tex
Added MATLAB ReadMe in LaTeX_code

\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{commath}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{siunitx}
\usepackage{multirow}

\usepackage{listings}
\definecolor{mygreen}{RGB}{28,172,0}
\definecolor{mylilas}{RGB}{170,55,241}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

\title{MATLAB: Read Me}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\lstset{language=Matlab,
    breaklines=true,
    morekeywords={matlab2tikz},
    keywordstyle=\color{blue},
    morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
    identifierstyle=\color{black},
    stringstyle=\color{mylilas},
    commentstyle=\color{mygreen},
    showstringspaces=false,
    numbers=left,%
    numberstyle={\tiny \color{black}},
    numbersep=9pt,
    emph=[1]{for,end,break},emphstyle=[1]\color{red},  
}

\begin{frame}
\titlepage
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Questions:}

\begin{itemize}

\item Why $\dif X=a(X;\alert{\theta})\dif t+b(X;\alert{\theta},\alert{\alpha})\dif W$ and no $\dif X=a(X;\alert{\theta})\dif t+b(X;\alert{\gamma})\dif W$? Where all $\alert{\theta},\alert{\alpha},\alert{\gamma}\in\R^+$. {\color{green}Because in the way it is defined, $\theta$ controls the mean reversion and $\alpha$ the wide of the confidence band.} {\color{red} However, maybe it is better to optimize over $\theta$ and $\gamma$? Because of the relative dimension. After, trivially we can compute $\alpha=\gamma/\theta$}.

\item Which is Beta, the measurements or the transitions?

\item Which data in the histograms? Measurements or transitions?

\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Some keywords:}

\begin{itemize}

\item Our process is: \textbf{High-frequency in a fixed time-interval}.

\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Normalization:}

Given the SDE
\begin{equation*}
\dif V_t=-\theta_tV_t\dif t+\sqrt{2\theta_t\alpha(V_t+p_t)(1-V_t-p_t)}\dif W_t,
\end{equation*}
we consider the normalized differentials $\dif\hat{t}=\frac{\dif t}{T}$, and $\dif\hat{W}_t=\frac{\dif W_t}{\sqrt{T}}$. Then, we can write the SDE as
\begin{equation*}
\dif V_t=-\alert{\theta_tT}V_t\dif\hat{t}+\sqrt{2\alert{\theta_tT}\alpha(V_t+p_t)(1-V_t-p_t)}\dif\hat{W}_t.
\end{equation*}
We conclude that, whatever the normalization constant T is, it gets absorbed by the parameter $\theta_t$ (let $\hat{\theta}_t=\theta_t T$).
\quad\\
The E-M representation is
\begin{equation*}
V_{t_{n+1}}=V_{t_{n}}-\left[\hat{\theta}_{t_n}V_{t_n}\right]\Delta s+\left[\sqrt{2\hat{\theta}_{t_n}\alpha(V_{t_n}+p_{t_n})(1-V_{t_n}-p_{t_n})}\right]\sqrt{\Delta s}\Delta\hat{W}_{t_n},\ V_{t_0}=v_0,
\end{equation*}
for $n\in\{0\dots,m-1\}$, $t_j=t_0+j\Delta s$, $t_0=0$, $t_m=1$, and $\Delta\hat{W}_{t_n}$ normal (0,1) for each $t_n$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE first moment (1/2):} \label{m1}

Given some measurement $v_{t_{n-1}}$, we want to compute the first moment at time $t_n$. The exact first moment $m_1(s)$ for $s\in[t_{n-1},t_n]$ is the solution of the ODE

\begin{equation*}
\begin{cases}
\dif m_1(s)=\left[-m_1(s)\theta(s)\right]\dif s,\\
m_1(t_{n-1})=v_{t_{n-1}}.
\end{cases}
\end{equation*}
If $\theta(t_{n-1})=\theta(t_{n})=\theta$, the solution is $m_1(t_n)=m_1(t_{n-1})e^{-\theta(t_n-t_{n-1})}$.\\
\quad\\
Otherwise, we compute a linear interpolation for $\theta(s)$ and solve the ODE using Forward-Euler:
\begin{equation*}
m_1(s_{n})=m_1(s_{n-1})(1-\theta(s_{n-1})\Delta s).
\end{equation*}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE first moment (2/2): CODE} \label{m1_code}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\footnotesize
\lstinputlisting{../moment_1.m}
}\\
\bottomrule
\end{tabular}
\end{center}

The code is automatically imported from the MATLAB script.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE second moment (1/2):} \label{m2}

Given some measurement $v_{t_{n-1}}$, we want to compute the second moment at time $t_n$. The exact second moment $m_2(s)$ for $s\in[t_{n-1},t_n]$ is the solution of the ODE

\begin{equation*}
\begin{cases}
\dif m_2(s)&=\alert{\left[-2(1+\alpha)m_2(s)\theta(s)+2\alpha\theta(s)m_1(s)(1-2p(s))+2\alpha\theta(s)p(s)(1-p(s))\right]\dif s,}\\
&=2\theta(s)\left[-(1+\alpha)m_2(s)+\alpha m_1(s)(1-2p(s))+\alpha p(s)(1-p(s))\right]\dif s,\\
m_2(t_{n-1})&=v^2_{t_{n-1}}.
\end{cases}
\end{equation*}
We compute a linear interpolation for the functions $\theta(s)$ and $p(s)$. After, we solve the ODE using Forward-Euler:
{\scriptsize
\begin{equation*}
m_2(s_n)=m_2(s_{n-1})+2\theta(s_{n-1})\left[-(1+\alpha)m_2(s_{n-1})+\alpha m_1(s_{n-1})(1-2p(s_{n-1}))+\alpha p(s_{n-1})(1-p(s_{n-1}))\right]\Delta s.
\end{equation*}}
We use the same discretization points for both $m_1(s)$ and $m_2(s)$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE second moment (2/2): CODE} \label{m2_code}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\footnotesize
\lstinputlisting{../moment_2.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Density next measurement (1/2):} \label{Tr}

We want the next measurement $V_{t_n}|V_{t_{n-1}}$ to have a Beta distribution, but with support in $[a,b]=[-1,1]$. Given $X\sim\beta(\xi_1,\xi_2)$ a \alert{Beta distributed random variable}, we define the new random variable $V=a+(b-a)X$ with support in $[-1,1]$, and PDF $f_V(v)$.\\
\quad\\
We can compute:
\begin{itemize}
\item $\E[V]=a+(b-a)\E[X]=a+(b-a)\frac{\xi_1}{\xi_1+\xi_2}=\mu_V$.
\item $\V[V]=(b-a)^2\V[X]=\frac{(b-a)^2\xi_1\xi_2}{(\xi_1+\xi_2)^2(\xi_1+\xi_2+1)}=\sigma^2_V$.
\end{itemize}
\quad\\
\quad\\
Then, we want the SDE and our new PDF $f_V(v)$ to have the same moments at each $t\in\{\text{some appropriate domain}\}$, i.e., $\mu(t)=m_1(t)$ and $\sigma^2(t)=m_2(t)-m_1^2(t)$.\\
$\mu(t)$ and $\sigma^2(t)$ refers to the mean and variance of $V_{t_n}|V_{t_{n-1}}$, following the structure described for $f_V(v)$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Density next measurement (2/2):}

For each measurement $V_{t_{n-1}}$, we can find the analytical moments for the SDE at time $t_n$ solving the ODEs from slides {\color{blue}\ref{m1}} and {\color{blue}\ref{m2}}. Then, we can find the parameters $\xi_1$ and $\xi_2$ such that both the SDE and the PDF of $V_{t_n}|V_{t_{n-1}}$ have the same first and second moments at time $t_n$.
\begin{itemize}
\item $\xi_1=-\frac{(1+\mu)(\mu^2+\sigma^2-1)}{2\sigma^2}$ all evaluated at time $t_n$ (verified in \textbf{Mathematica 11.0}\footnote{File: {\color{blue}matchingVerification.nb}.}).
\item $\xi_2=\frac{(\mu-1)(\mu^2+\sigma^2-1)}{2\sigma^2}$ all evaluated at time $t_n$ (verified in \textbf{Mathematica 11.0}).
\end{itemize}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\footnotesize
\lstinputlisting{../moments_matching.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Log-density (1/2):}

Recall the PDF $f_V(v)$ from slide {\color{blue}\ref{Tr}}. We will use this density to model the random variables $V_{t_n}|V_{t_{n-1}}$. For $[a,b]=[-1,1]$, we have that
\begin{equation*}
f_V(v)=f_X(g^{-1}(v))\left|\frac{\dif}{\dif v}g^{-1}(v)\right|\quad \text{where}\quad f_X(x)=\text{Beta}(\xi_1,\xi_2)\quad\text{and}\quad g(x)=a+(b-a)x.
\end{equation*}
Then, $f_V(v)=\frac{1}{|(b-a)|}\frac{1}{B(\xi_1,\xi_2)}\left(\frac{v-a}{b-a}\right)^{\xi_1-1}\left(1-\frac{v-a}{b-a}\right)^{\xi_2-1}$ because $g^{-1}(v)=\frac{v-a}{b-a}$.\\
\quad\\
Also, we have that (up to some constant values)
\begin{equation*}
\log\left(f_V(v)\right)=\log\left(\frac{1}{B(\xi_1,\xi_2)}\right)+(\xi_1-1)\log\left(\frac{v-a}{b-a}\right)+(\xi_2-1)\log\left(\frac{b-v}{b-a}\right),
\end{equation*}
where $\xi_1$ and $\xi_2$ depends on the SDE moments.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Log-density (2/2): CODE}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\footnotesize
\lstinputlisting{../log_dist.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Log-likelihood (1/2):}

We introduce the number of paths $M$, and the number of measurements per path $N+1$ ($N$ transitions). Then, we have a total of $M\times N$ samples to use. Notice that each pair $(\xi_1,\xi_2)$ depends on $i\in\{1,\dots,M\}$ and $j\in\{2,\dots,N+1\}$. Then, the log-likelihood is
\begin{equation*}
\mathfrak{L}\left(\{V\}_{M,N}\right)=\sum_{i=1}^M\sum_{j=2}^{N+1}\log\left[\rho_{i,j}\left(V_{i,j}|V_{i,j-1}\right)\right],
\end{equation*}
where $\rho_{i,j}\left(V_{i,j}|V_{i,j-1}\right)=\rho_{i,j}\left(V_{i,j}|V_{i,j-1};\xi_{1_{i,j}},\xi_{2_{i,j}}\right)$, and where we assumed a non-informative prior.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Data: CODE}

We load our three tables: \textbf{Table\_Training\_Complete}, \textbf{Table\_Testing\_Complete}, and \textbf{Table\_Complete}.

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../load_data.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Create a new batch (1/2):} \label{cre_batch}

To guarantee the data homogeneity, we sample per day and not per transition. This means that each batch is composed of data corresponding to some amount of days. If we sample a total of $Z\in\N$ days, the batch corresponding to this days is
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\multicolumn{7}{|l|}{PATH 1}                                                                                       & ...                  & PATH Z               \\ \hline
\multicolumn{2}{|l|}{$t_n=01:10$}   & \multicolumn{2}{l|}{$t_n=01:20$}    & ... & \multicolumn{2}{l|}{$t_n=00:50$} & \multirow{4}{*}{...} & \multirow{4}{*}{...} \\ \cline{1-7}
$p(t_{n-1})$      & $p(t_{n})$      & $p(t_{n-1})$      & $p(t_{n})$      & ... & $p(t_{n-1})$     & $p(t_{n})$    &                      &                      \\ \cline{1-7}
$\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & $\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & ... & $\dot{p}(t_{n-1})$     & $\dot{p}(t_{n})$    &                      &                      \\ \cline{1-7}

$V(t_{n-1})$      & $V(t_{n})$      & $V(t_{n-1})$      & $V(t_{n})$      & ... & $V(t_{n-1})$     & $V(t_{n})$    &                      &                      \\ \hline
\end{tabular}
\end{table}
with dimensions $3\times(2Z(N-1))$. As an example: If we have 145 measurements (N+1), then $N=144$ and $N-1=143$. We use 143 samples because we need to ignore the initial measurement (because we do not have data at time $t_{-1}$) and the final one (because it does not have $\dot{p}$). Then, each day has 143 samples. In this implementation, we are duplicating the data. In case of a lack of RAM, we can reduce the dimensions to $3\times(Z(N-1))$.
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Create a new batch (2/2): CODE}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../new_batch.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{From $\theta_0$ to $\theta_t$:}

To ensure that the analytical solutions is always in $[0,1]$, we choose the drift parameter to be
\begin{equation*}
\theta(t) = \max\left(\theta_0,\frac{|\dot{p}(t)|}{\min(p(t),1-p(t))}\right),\quad\theta_0>0.
\end{equation*}
\quad\\
\quad\\
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../theta_t.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Complete batch:}

After we created a batch with the elements $(p(t),\dot{p}(t),V(t))$, we want to add the parameter $\theta(t)$ to use in the likelihood. Following the same idea than in slide {\color{blue}\ref{cre_batch}}, the complete batch is
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\multicolumn{7}{|l|}{PATH 1}                                                                                       & ...                  & PATH Z               \\ \hline
\multicolumn{2}{|l|}{$t_n=01:10$}   & \multicolumn{2}{l|}{$t_n=01:20$}    & ... & \multicolumn{2}{l|}{$t_n=00:50$} & \multirow{4}{*}{...} & \multirow{4}{*}{...} \\ \cline{1-7}
$p(t_{n-1})$      & $p(t_{n})$      & $p(t_{n-1})$      & $p(t_{n})$      & ... & $p(t_{n-1})$     & $p(t_{n})$    &                      &                      \\ \cline{1-7}
$\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & $\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & ... & $\dot{p}(t_{n-1})$     & $\dot{p}(t_{n})$    &                      &                      \\ \cline{1-7}

$V(t_{n-1})$      & $V(t_{n})$      & $V(t_{n-1})$      & $V(t_{n})$      & ... & $V(t_{n-1})$     & $V(t_{n})$    &                      &                      \\ \hline
$\theta(t_{n-1})$      & $\theta(t_{n})$      & $\theta(t_{n-1})$      & $\theta(t_{n})$      & ... & $\theta(t_{n-1})$     & $\theta(t_{n})$    &                      &                      \\ \hline

\end{tabular}
\end{table}
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../batch_with_theta.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Initial guess for $\theta_0\cdot\alpha$:}
Recall we have $M$ paths with $N+1$ measurements each.
\begin{equation*}
\theta_0 \alpha\approx \frac{1}{2M\Delta t} \sum\limits_{j=1}^M \frac{ \sum\limits_{i=1}^{N} (x_{i+1,j}  - x_{i,j})^2}{\sum\limits_{i=1}^{N} x_{i,j}(1-x_{i,j}) }\alert{\approx 0.021}.
\end{equation*}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../initial_guess.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Initial guess for $\theta_0$:}
Recall we have $M$ paths with $N+1$ measurements each.
\begin{equation*}
\theta_0\approx\arg\min_{\theta_0}\left[\sum_{j=1}^M\sum_{i=1}^N\left(v_{i+1,j}-v_{i,j}+\theta_{t_i}v_{i,j}\Delta t\right)^2\right].
\end{equation*}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../initial_theta.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Initial guess for $\theta_0$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{theta_0.eps}
\end{figure}

\alert{$\theta_0\approx 1.1450
$ and $\theta_0\alpha\approx 0.021\implies\alpha\approx0.018$.}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Log-likelihood evaluation: CODE}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../log_LH_evaluation.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Log-likelihood: Plot}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../log_likelihood.eps}\quad\includegraphics[width=0.45\textwidth]{../log_likelihood_2.eps}
\end{figure}

\end{frame}

\end{document}

### 2020-02-09 LaTeX_code/paper/paper_1line.tex
Minor edits
Added MATLAB ReadMe in LaTeX_code

@@
 \affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
-\affil[3]{Universidad de la Rep\'ublica, Montevideo Uruguay}
+\affil[3]{Universidad de la Rep\'ublica, Instituto de Estad\'{\i}stica (IESTA), Montevideo, Uruguay}
 \affil[4]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}
@@
 In blue is an hourly wind power production forecast.
-In orange is the actual wind power production recorded in 10 minute intervals from  ADME.}
+In orange is the actual wind power production recorded in 10 minute intervals.}
   \label{fig:sample_data}

### 2020-02-09 LaTeX_code/paper/paper_1line.tex
Corrected plots in paper and added initial guess for delta

@@
 
-Solving for $\alpha$, we have both first estimates to quick start the inference processes given as follows:
+Solving for $\alpha$, we have both first estimates and we can also estimate $\delta$ solving the problem
+
+\begin{equation}
+\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
+\label{likelihood_delta}
+\end{equation}
+
+With our estimations of $\bm{\theta}$, we can start the inference processes as follows:
 \begin{enumerate}
@@
 \hline
-Model   &  parameters $(\theta_0, \alpha)$   & AIC & BIC \\ \hline
+Model   &  parameters $(\theta_0, \alpha,\delta)$   & AIC & BIC \\ \hline
 Model 1 &  $(\add,\add) $    &  \add   &  \add   \\ \hline
-Model 2 &   $(\add,\add)$   &  \add   &   \add    \\ \hline
+Model 2 &   $(1.2,0.1,0.6)$   &  \add   &   \add    \\ \hline
 \end{tabular}
@@
 \hline
-Forecast Provider & parameters $(\theta_0, \alpha)$ & AIC & BIC \\ \hline
+Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \hline
 Provider A  &  $(\add,\add)$      &  \add   & \add    \\ \hline
@@
 \hline
-Formulation   &  parameters $(\theta_0, \alpha)$    \\ \hline
-Without Lamperti transform &   $(12,0.3) \pm (\add , \add) $   \\ \hline
+Formulation   &  parameters $(\theta_0, \alpha,\delta)$    \\ \hline
+Without Lamperti transform &   $(1.2,0.1,0.6) \pm (\add , \add) $   \\ \hline
 With Lamperti transform &   $(12,0.29) \pm (\add , \add)  $   \\ \hline
@@
     \begin{figure}[h]
-      \includegraphics[width=70mm,scale=1]{simulated/24hr/1099.pdf}
-      \includegraphics[width=70mm,scale=1]{simulated/24hr/1178.pdf}
-      \caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha )=(12,0.3)$.
+        \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/1.eps}
+  \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/2.eps}\\
+   \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/3.eps}
+  \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/4.eps}
+      \caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
 Forecast is from Uruguay pertaining to  year 2019.}
@@
     \begin{figure}[h]
-      \includegraphics[width=70mm,scale=1]{confidence_intervals/24hr/31.pdf}
-      \includegraphics[width=70mm,scale=1]{confidence_intervals/24hr/820.pdf}
-       \caption{We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha )=(12,0.3)$.
+      \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/1.eps}
+  \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/2.eps}\\
+   \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/3.eps}
+  \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/4.eps}
+       \caption{{\color{red}Pending add legend and choose better colors.}We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
 Actual production plotted in retrospect.

### 2020-02-10 LaTeX_code/paper/paper_1line.tex
Added initial guess plot in paper, corrected other plots.

@@
 \usepackage{siunitx}
-
+\usepackage{booktabs}
 \usepackage{xcolor}
-
 \usepackage{authblk}
@@
 \begin{figure}
-  \includegraphics[width=120mm,scale=1]{plots/1.png}
-  \caption{Installed wind and solar power over the years.
-We recall the importance of accurate forecasts to use green energies optimally.
-{\color{red} We still have to ensure that the source is trustworthy (Renzo will do it)}.
-Redo the figure as well}
-\end{figure}Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
+\centering
+\includegraphics[width=0.9\textwidth]{plots/wind_and_solar/plot_over_years.eps}
+\caption{Installed wind and solar power over the years \cite{sultana2017review}. We recall the importance of accurate forecasts to use green energies optimally.}
+\end{figure}
+
+Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
 \begin{itemize}
@@
 \begin{figure}
-  \includegraphics[width=60mm,scale=1]{plots/5.eps}
-  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
-   \includegraphics[width=60mm,scale=1]{plots/661.eps}
-  \includegraphics[width=60mm,scale=1]{plots/805.eps}
+\centering
+\includegraphics[width=0.45\textwidth]{plots/5.eps}
+\includegraphics[width=0.45\textwidth]{plots/245.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/661.eps}
+\includegraphics[width=0.45\textwidth]{plots/805.eps}
 \caption{Four samples from the Uruguayan data of 2019.
@@
 \begin{figure}
-  \includegraphics[width=60mm,scale=1]{plots/LP_6.eps}
-  \includegraphics[width=60mm,scale=1]{plots/MP_6.eps}\\
-   \includegraphics[width=60mm,scale=1]{plots/HP_6.eps}
-  \includegraphics[width=60mm,scale=1]{plots/AP_6.eps}
+\centering
+\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
+\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
+\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
 \caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production.
@@
 \begin{figure}
-  \includegraphics[width=60mm,scale=1]{plots/LP.eps}
-  \includegraphics[width=60mm,scale=1]{plots/MP.eps}\\
-   \includegraphics[width=60mm,scale=1]{plots/HP.eps}
-  \includegraphics[width=60mm,scale=1]{plots/AP.eps}
+\centering
+\includegraphics[width=0.45\textwidth]{plots/LP.eps}
+\includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/HP.eps}
+\includegraphics[width=0.45\textwidth]{plots/AP.eps}
 \caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
@@
 \begin{figure}
-  \includegraphics[width=60mm,scale=1]{plots/LP_t.eps}
-  \includegraphics[width=60mm,scale=1]{plots/MP_t.eps}\\
-   \includegraphics[width=60mm,scale=1]{plots/HP_t.eps}
-  \includegraphics[width=60mm,scale=1]{plots/AP_t.eps}
+\centering
+\includegraphics[width=0.45\textwidth]{plots/LP_t.eps}
+\includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
+\includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
 \caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
@@
 \begin{figure}
-  \includegraphics[width=60mm,scale=1]{plots/LP_t_LP.eps}
-  \includegraphics[width=60mm,scale=1]{plots/MP_t_LP.eps}\\
-   \includegraphics[width=60mm,scale=1]{plots/HP_t_LP.eps}
-  \includegraphics[width=60mm,scale=1]{plots/AP_t_LP.eps}
+\centering
+\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
+\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
+\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
 \caption{Transitions after the Lamperti transform.
@@
 
-\subsection{Optimization}
+\subsection{Optimization} \label{opt_sec}
 {\color{red} Rewrite the discussion to obtain fast initial estimate for the two unknow parameters.}
@@
 \begin{equation}
- \arg\min \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 ,
+\theta_0\approx\arg\min_{\theta} \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2,
+\label{inital_theta}
 \end{equation}
@@
 \begin{equation}
-\theta_0 \alpha = \frac{1}{M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
+\theta_0 \alpha \approx \frac{1}{2M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{ \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
 \end{equation}
@@
 \centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-Model   &  parameters $(\theta_0, \alpha,\delta)$   & AIC & BIC \\ \hline
-Model 1 &  $(\add,\add) $    &  \add   &  \add   \\ \hline
-Model 2 &   $(1.2,0.1,0.6)$   &  \add   &   \add    \\ \hline
+\begin{tabular}{cccc}
+\toprule
+Model   &  parameters $(\theta_0, \alpha,\delta)$   & AIC & BIC \\ \midrule
+Model 1 &  $(\add,\add) $    &  \add   &  \add   \\
+Model 2 &   $(1.2,0.1,0.6)$   &  \add   &   \add    \\ 
+\bottomrule
 \end{tabular}
@@
 \centering
-\begin{tabular}{|c|l|c|c|}
-\hline
-Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \hline
-Provider A  &  $(\add,\add)$      &  \add   & \add    \\ \hline
-Provider B  & $(\add,\add) $  &  \add   &   \add  \\ \hline
+\begin{tabular}{cccc}
+\toprule
+Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \midrule
+Provider A  &  $(\add,\add)$      &  \add   & \add    \\
+Provider B  & $(\add,\add) $  &  \add   &   \add  \\ 
+\bottomrule
 \end{tabular}
@@
  \centering
- \begin{tabular}{|c|l|c|c|}
- \hline
- Model & parameters $(\theta_0, \alpha)$  \\ \hline
- \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ \hline
- \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \hline
+ \begin{tabular}{cccc}
+ \toprule
+ Model & parameters $(\theta_0, \alpha)$  \\
+ \midrule
+ \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ 
+ \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \bottomrule
  \end{tabular}
@@
 \section{Results} \label{Section_7}
+
+\subsection{Initial guesses}
+
+Following the instruction for the initial guesses from section $\ref{opt_sec}$, we get the initial guesses $(\theta_0,\alpha,\delta)\approx(1.2,0.1,0.6)$.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.6\textwidth]{plots/initial_guess/initial_theta_1.eps}
+\caption{Value function from ($\ref{inital_theta}$) as a function of different $\theta_0$ values. We can observe that the function if flat for a wide range.}
+\end{figure}
+
+\subsection{Main guesses}
 
@@
 
-    \begin{figure}[h]
-        \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/1.eps}
-  \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/2.eps}\\
-   \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/3.eps}
-  \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/4.eps}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/1.eps}
+\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/2.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/3.eps}
+\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/4.eps}
 \caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
@@
 
-    \begin{figure}[h]
-      \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/1.eps}
-  \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/2.eps}\\
-   \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/3.eps}
-  \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/4.eps}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/1.eps}
+\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/2.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/3.eps}
+\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/4.eps}
 \caption{{\color{red}Pending add legend and choose better colors.}We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.

### 2020-02-11 LaTeX_code/paper/paper_1line.tex
Added plots in slides and paper, corrected beta function in code

@@
 \centering
-\includegraphics[width=0.6\textwidth]{plots/initial_guess/initial_theta_1.eps}
+\includegraphics[width=0.45\textwidth]{plots/initial_guess/initial_theta_1.eps}\quad\includegraphics[width=0.42\textwidth]{plots/initial_guess/initial_theta_2.eps}
 \caption{Value function from ($\ref{inital_theta}$) as a function of different $\theta_0$ values. We can observe that the function if flat for a wide range.}
+\end{figure}
+
+\subsection{Negative Log-Lihelihood}
+
+We plot the Negative Log-Likelihood as a function of the parameters.
+The plots can be seen in Figure (\ref{fig:neg-LL}).
+We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood.eps}\quad\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_refined.eps}
+\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_more_refined.eps}
+\caption{Negative Log-Likelihood for different domains.}
+\label{fig:neg-LL}
 \end{figure}

### 2020-02-14 LaTeX_code/paper/paper_1line.tex
Lamperti with unitary coefficient diffusion

@@
 
-We consider the following Lamperti transformation  {\color{red} (Modify the transformation to obtain an unitary diffusion coefficient in the SDE for $Z$.
-Remind that in continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
+We consider the following Lamperti transformation  {\color{red} (Remind that in continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
 Besides, it can be unstable to work with low frequency.
@@
 \begin{equation}
-Z_t = h(V_t) = \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
+Z_t = h(V_t) = \frac{1}{\sqrt{2 \theta_t \alpha}} \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
 \end{equation}
@@
 \begin{equation}
-Z_t = h(V_t) = \arcsin (2(V_t + p_t) -1)\,,
+Z_t = h(V_t) = \frac{1}{\sqrt{2 \theta_t \alpha}} \arcsin (2(V_t + p_t) -1)\,,
 \end{equation}
@@
 \begin{equation}
-dZ_t = \left[  \frac{- \theta_t V_t}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{2} \frac{\theta_t \alpha \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \right] \,dt + \sqrt{2 \theta_t \alpha}\, dW_t \,.
+dZ_t = \left[  \frac{- \theta_t V_t}{ \sqrt{2 \theta_t \alpha (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \theta_t \alpha} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \right] \,dt + dW_t \,.
 \label{eq:stindepSDE}
@@
 \begin{equation}
-dZ_t = \frac{- \theta_t (\sin(Z_t) + 1 - 2 p_t) + \theta_t \alpha \sin{(Z_t)}}{\cos{(Z_t)}} \,dt + \sqrt{2 \theta_t \alpha}\, dW_t \,. 
+dZ_t = \left[ \frac{- \theta_t (\sin(Z_t) + 1 - 2 p_t)}{\sqrt{2 \theta_t \alpha} \cos{(Z_t)}} + \frac{\sqrt{2 \theta_t \alpha} \sin{(Z_t)}}{2 \cos{(Z_t)}} \right] \,dt + dW_t \,. 
 \end{equation}

### 2020-02-14 LaTeX_code/paper/paper_1line.tex
correction formula (11)

@@
 \end{equation}
-After replacing $V_t = \frac{\sin(Z_t) + 1}{2} - p_t$ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
-\begin{equation}
-dZ_t = \left[ \frac{- \theta_t (\sin(Z_t) + 1 - 2 p_t)}{\sqrt{2 \theta_t \alpha} \cos{(Z_t)}} + \frac{\sqrt{2 \theta_t \alpha} \sin{(Z_t)}}{2 \cos{(Z_t)}} \right] \,dt + dW_t \,. 
-\end{equation}
+After replacing $V_t = \frac{\sin(\sqrt{2 \theta_t \alpha} Z_t) + 1}{2} - p_t$ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
+\begin{align}
+dZ_t & = \left[ \frac{- \theta_t (\sin(\sqrt{2 \theta_t \alpha} Z_t) + 1 - 2 p_t)}{\sqrt{2 \theta_t \alpha} \cos{(\sqrt{2 \theta_t \alpha} Z_t)}} + \frac{\sqrt{2 \theta_t \alpha} \sin{(\sqrt{2 \theta_t \alpha} Z_t)}}{2 \cos{(\sqrt{2 \theta_t \alpha} Z_t)}} \right] \,dt + dW_t \nonumber \\
+&  = \left[  \frac{\sqrt{2 \theta_t} \left( \sin(\sqrt{2 \theta_t \alpha} Z_t) (\alpha - 1) + (2 p_t -1 ) \right)}{2 \sqrt{\alpha} \cos{(\sqrt{2 \theta_t \alpha} Z_t)}}  \right] \,dt + dW_t \,. 
+\end{align}
 

### 2020-02-19 LaTeX_code/paper/paper_1line.tex
Added apendix in the paper with the proofs of Professor Kebaier

@@
 \usepackage{amssymb, amsmath}
-\usepackage{bm} % more powerful version to get bold
+\usepackage{bm}
 \usepackage{siunitx}
@@
 \usepackage{authblk}
+\usepackage{amsmath}
+\usepackage{todonotes}
+\usepackage{ulem}
+\usepackage{amssymb}
+\usepackage{float}
+\usepackage{amsthm}
+\usepackage{fancybox}
+
+\theoremstyle{definition}
+\newtheorem{Def}{Definition}[section]
+\newtheorem{Eg}{Example}[section]
+\newtheorem{Rm}{Remark}[section]
+\newtheorem{Ex}{Exercise}[section]
+\newtheorem{Prop}[Def]{Proposition}
+\newtheorem{Lem}[Def]{Lemma}
+\newtheorem{Thm}[Def]{Theorem}
+\newtheorem{Cor}[Def]{Corollary}
+\newtheorem{Rem}[Def]{Remark}
+\newtheorem{Ass}[Def]{Assumption}
+\newtheorem{Met}[Def]{Method}
+\newtheorem{Res}[Def]{Result}
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
 
-\begin{table}
+\begin{table}[H]
 \centering
@@
 We compare forecasts from two different companies for the same period.
-\begin{table}
+\begin{table}[H]
 \centering
@@
 
- \begin{table}[h]
+ \begin{table}[H]
  \centering
@@
 
-\begin{figure}[h!]
+\begin{figure}[H]
 \centering
@@
 We were able to obtain the following for 
-\begin{table}[]
+\begin{table}[H]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[H]
   \includegraphics[width=56mm,scale=1]{plots/alpha_conv_beta.png}
@@
 
+\section{Appendix} \label{Appendix}
+
+\section{The model}
+For a time horizon $T>0$ and  a parameter $\alpha > 0$ and $(\theta_t)_{t\in[0,T]}$ a positive deterministic  function,  let us consider the model  given by
+\begin{align}\label{eq:model}
+dX_t&= \big(\dot p_t - \theta_t(X_t-p_t)  \big)dt  +\sqrt{2\alpha \theta_tX_t(1-X_t)} dW_t\quad t\in[0,T]\\
+X_0&=x_0\in[0,1],\notag
+\end{align}
+where $(p_t)_{t\in[0,T]}$ denotes the prediction function that satisfies $0\le p_t\le 1$ for all $t\in[0,T]$. This prediction function is assumed to be a smooth function of the time so that 
+$$\sup_{t\in[0,T]}\bigl( |p_s| + |\dot p_s|\big) <+\infty .$$
+The following proofs are based on standard arguments for stochastic processes that can be found e.g.
+in  Alfonsi \cite{Alf} and Karatzas and Shreve \cite{KarShr} that we adapted to the setting of our model \eqref{eq:model}.
+\begin{Thm}\label{thm:exun}
+Assume that    
+\begin{equation}\label{Assumption:1}
+\forall  t\in[0,T],\;\; 0\le \dot p_t +\theta_tp_t\le \theta_t, \;\;\mbox{ and }\;\;
+\sup_{t\in[0,T]}|\theta_t|<+\infty\tag{A}. 
+\end{equation}
+Then, there is a unique strong solution to \eqref{eq:model} s.t.  for all $t\in[0,T]$, $X_t\in[0,1]$ a.s.
+\end{Thm}
+\begin{proof}
+Let us first consider the following SDE for $t\in[0,T]$
+\begin{equation}\label{eq:eds1}
+X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)ds  + \int_0^t\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s, \quad x_0>0.
+\end{equation}
+According to Proposition 2.13, p.
+291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X$ to \eqref{eq:eds1}.
+Moreover, as the diffusion coefficient is of linear growth, we have  for all $p>0$
+\begin{equation}\label{prop:fm}
+\mathbb E[ \sup_{t\in[0,T]}|X_t|^p]<\infty.
+\end{equation}
+Then, it remains to show that for all $t\in[0,T]$, $X_t\in[0,1]$ a.s.
+For this aim, we need to use the so-called Yamada function $\psi_n$ that is a $\mathcal C^2$ function that satisfies a bench of useful properties:
+\begin{align*}
+&|\psi_n(x)|\underset{n\rightarrow+\infty}{\rightarrow}|x|, \;\; x{\psi'}_n(x)\underset{n\rightarrow+\infty}{\rightarrow}|x|, \;\; |\psi_n(x)|\wedge |x{\psi'}_n(x)| \le |x|\\
+&{\psi'}_n(x)\le 1, \;\; \mbox{ and } {\psi''}_n(x)=g_n(|x|)\ge 0\;\; \mbox{ with } \;\; g_n(x)x\le \frac 2n\;\;  \mbox{ for all } x\in \mathbb R .
+\end{align*}
+See the proof of Proposition 2.13, p. 291 of \cite{KarShr} for the construction of such fucntion.
+Applying Itô's formula we get
+\begin{align*}
+\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)ds + \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s\\
+&+ \alpha \int_0^t \theta_sg_n(|X_s|)|X_s(1-X_s)|ds.
+\end{align*}
+Now, thanks to  \eqref{Assumption:1}, \eqref{prop:fm} and to the above properties of $\psi_n$ and $g_n$, we get
+$$
+\mathbb E[\psi_n(X_t)]\le \psi_n(x_0) +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \big)ds + \frac{2\alpha}{n}\int_0^t \theta_s\mathbb E |1-X_s|ds.
+$$
+Therefore, letting $n$ tends to infinity we use Lebesgue's theorem to get
+$$
+\mathbb E[|X_t|]\le x_0 +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E|X_s| \big)ds.
+$$
+Besides, taking the expectation of \eqref{eq:eds1}, we get
+$$
+\mathbb E X_t=x_0+  \int_0^t\big(\dot p_s +\theta_sp_s - \theta_s \mathbb EX_s  \big)ds
+$$
+and thus we have 
+$$
+\mathbb E[|X_t| -X_t ]\le \int_0^t \theta_s \mathbb E[|X_s| - X_s ]ds.
+$$
+Then, Gronwall's lemma gives us $\mathbb E[|X_t|]=\mathbb E X_t$ and thus for any $t\in[0,T]$ $X_t\ge0$ a.s.
+The same arguments work to prove that  for any $t\in[0,T]$ $Y_t:=1-X_t\ge0$  a.s.
+since the process $(Y_t)_{t\in[0,T]}$ is solution to
+$$
+dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \theta_tY_t(1-Y_t)} dW_t,
+$$
+Then similarly, we need to assume that $\dot p_t +\theta_tp_t\ge 0$. This completes the proof.
+\end{proof}
+
+\begin{Thm}
+Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
+Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$. Assume in addition that
+\begin{equation}\label{Assumption:2}
+0<\alpha < \frac 12\quad \mbox{ and }\quad \forall  t\in[0,T],\;\; \alpha\theta_t\le \dot p_t +\theta_tp_t \le (1-\alpha)\theta_t \tag{B}. 
+\end{equation}
+ Then, $\tau_0=\tau_1=+\infty$ a.s.
+\end{Thm}
+\begin{proof}
+For $t\in[0,\tau_0[$, we have 
+$$
+\frac{dX_t}{X_t}= \frac{\dot p_t +\theta_t p_t}{X_t} - \theta_tdt  +\sqrt{\frac{2\alpha \theta_t(1-X_t)}{X_t}} dW_t 
+$$  
+so that
+$$
+X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_s(p_s-\alpha)}{X_s}ds-(1-\alpha)\int_0^t\theta_sds + M_t\Big),
+$$
+where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_s(1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_t(p_t-\alpha)\ge0$, we deduce that
+$$
+X_t\ge x_0\exp\Big(-(1-\alpha)\int_0^t\theta_sds + M_t\Big).
+$$
+By way of contradiction let us assume that  $\{\tau_0<\infty\}$, then letting $t\to \tau_0$ we deduce that $\lim_{t\to \infty} \mathbf 1_{\{\tau_0<\infty\}}M_{t\wedge \tau_0}=\mathbf -1_{\{\tau_0<\infty\}}\infty$ a.s.
+This leads to a contradiction since we know that continuous martingales likewise the Brownian motion cannot converge  almost surely to $+\infty$ or $-\infty$.
+It follows that $\tau_0=\infty$ almost surely.
+Next, recalling that  the process $(Y_t)_{t\geq 0}$  given by $Y_t=1-X_t$ is solution to
+$$
+dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \theta_tY_t(1-Y_t)} dW_t 
+$$
+we deduce using similar arguments as above 
+$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \theta_t\ge 0$.
+ \end{proof}
+\textcolor{red}{When using Lamperti, the form }
+
 %---REFERENCES---

### 2020-02-21 LaTeX_code/paper/paper_1line.tex
Minor changes in the paper

@@
 \usepackage{amsthm}
+\usepackage{commath}
 \usepackage{fancybox}
@@
 $$
-\frac{dX_t}{X_t}= \frac{\dot p_t +\theta_t p_t}{X_t} - \theta_tdt  +\sqrt{\frac{2\alpha \theta_t(1-X_t)}{X_t}} dW_t 
+\frac{dX_t}{X_t}=\left( \frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)\dif t  +\sqrt{\frac{2\alpha \theta_t(1-X_t)}{X_t}} \dif W_t 
 $$  

### 2020-02-23 LaTeX_code/paper/paper_1line.tex
preliminary changes

@@
 \usepackage{graphicx}
-\usepackage{amssymb, amsmath}
 \usepackage{bm}
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{todonotes}
-\usepackage{ulem}
-\usepackage{amssymb}
+%\usepackage[normalem]{ulem}
 \usepackage{float}
-\usepackage{amsthm}
 \usepackage{commath}
 \usepackage{fancybox}
+\usepackage{url}
 
@@
 
-\usepackage[backend=biber, style=apa,autocite=inline]{biblatex} % package for bibliography
-\DeclareLanguageMapping{english}{english-apa}
+\usepackage[backend=biber, style=authoryear, citestyle=authoryear, autocite=inline]{biblatex} % package for bibliography 
+%\DeclareLanguageMapping{english}{english-apa}
 
@@
 
-%\usepackage[backend=biber, style=authoryear,autocite=inline]{biblatex}
+%\renewbibmacro*{title}{%
+%  \ifboolexpr{
+%    test {\iffieldundef{title}}
+%    and
+%    test {\iffieldundef{subtitle}}
+%  }
+%    {}
+%    {\printtext{%
+%     \printtext[titlecase]{\usefield{\uline}{title}}%
+%     \setunit{\subtitlepunct}%
+%     \printfield[titlecase]{subtitle}}%
+%     \newunit}%
+%  \printfield{titleaddon}}
 
@@
 See Figure (\ref{fig:sample_data}).
-The data is normalized with respect to the maximuim power capacity of wind power production in Uruguay, which is $\SI{1474}{\mega\watt}$.
+Data are normalized with respect to the maximum power capacity of wind power production in Uruguay, which is $\SI{1474}{\mega\watt}$.
 However, sometimes the real production is artificially modifies due to curtailing.
@@
 $$\sup_{t\in[0,T]}\bigl( |p_s| + |\dot p_s|\big) <+\infty .$$
-The following proofs are based on standard arguments for stochastic processes that can be found e.g.
-in  Alfonsi \cite{Alf} and Karatzas and Shreve \cite{KarShr} that we adapted to the setting of our model \eqref{eq:model}.
+The following proofs are based on standard arguments for stochastic processes that can be found e.g. in \cite{Alf} and \cite{KarShr} that we adapted to the setting of our model \eqref{eq:model}.
 \begin{Thm}\label{thm:exun}
@@
 \end{equation}
-According to Proposition 2.13, p.
-291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X$ to \eqref{eq:eds1}.
+According to Proposition 2.13, p.291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X$ to \eqref{eq:eds1}.
 Moreover, as the diffusion coefficient is of linear growth, we have  for all $p>0$
@@
 \begin{align*}
-\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)ds + \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s\\
-&+ \alpha \int_0^t \theta_sg_n(|X_s|)|X_s(1-X_s)|ds.
+\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)ds \\
+&+ \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s + \alpha \int_0^t \theta_sg_n(|X_s|)|X_s(1-X_s)|ds.
 \end{align*}

### 2020-02-24 LaTeX_code/paper/paper_1line.tex
Pearson diffusion

@@
   where $\alpha >0$ is a constant parameter that controls the path variability.
-This diffusion term belongs to the Pearson diffusion family and , in particular, it is a Jacobi type diffusion.
-{\color{red} Add expressions and references for these class of diffusions, for example \cite{iacus1}.}
+This diffusion term belongs to the Pearson diffusion family and, in particular, it is a Jacobi type diffusion.
+It is useful to recall that (\cite[440]{foso}) a Pearson diffusion is a stationary solution to a stochastic differential equation of the form
+ \begin{equation}
+    dX_t = - \theta (X_t - \mu) dt + \sqrt{2 \theta (a X_t^2 + b X_t + c)} dW_t
+  \end{equation}
+where $\theta>0$, and $a$, $b$ and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space and, together with $\mu$, the mean of the invariant distribution, determine the state space of the diffusion as well as the shape of the invariant distribution.
+\\ An exhaustive classification of the Pearson diffusions is presented in (\cite[440-443]{foso}) where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 \theta a x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the so-called Jacobi diffusions because the related eigenfunctions are Jacobi polynomials.
 
@@
 inside the range $[0,1]$.
-In other words, the zero drift line defined by $a(x; p_t,\bm{\theta}) =0$, which an attractor, must be contained inside the range $[0,1]$.
+In other words, the zero drift line defined by $a(x; p_t,\bm{\theta}) =0$, which is an attractor, must be contained inside the range $[0,1]$.
 Thus, we must have that

### 2020-03-10 LaTeX_code/paper/paper_1line.tex
to sincronize version

@@
 
-We introduce the following phenomenological model.
-Let $X = \{X_t, \, t>0\}$  be the  wind power generation forecasts stochastic process defined by the following parameterized stochastic differential equation (SDE)
+We consider a general phenomenological model for the normalized wind power generation forecasts is the stochastic process $X = \{X_t, \, t>0\}$  be the   c process is defined by the following stochastic differential equation (SDE)
 
@@
 \end{align*}
-See the proof of Proposition 2.13, p. 291 of \cite{KarShr} for the construction of such fucntion.
+See the proof of Proposition 2.13, p. 291 of \cite{KarShr} for the construction of such function.
 Applying Itô's formula we get

### 2020-03-10 LaTeX_code/paper/paper_1line.tex
Added Prof Kebaier theorem in apendex

--- 2020-02-24 LaTeX_code/paper/paper_1line.tex
@@
 \newtheorem{Res}[Def]{Result}
+\newcommand{\red}{\textcolor{red}}
 
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dV_t \!\!\!&=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t   \\ %\quad t > 0
-V_0 \!\!\!&=  v_0 \,. \label{VtSDE}
-% \theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )\\
-\end{array}\right. 
+\begin{cases}
+    \dif V_t &=  - \theta_t V_t \ \dif t + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  \dif W_t \\
+V_0 \!\!\!&=  v_0 \,.\\ 
+%\theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
+\end{cases}
+\label{VtSDE}
 \end{equation}
@@
 
- By assuming ergodicity {\color{red} not ergodicity, instead simply for the quadratic variation formula.}, we can obtain a first estimate on the product of the parameters as follows,
+ By assuming ergodicity {\color{red} not ergodicity, instead simply for the \textbf{quadratic variation formula}.}, we can obtain a first estimate on the product of the parameters as follows,
 
@@
 \end{proof}
-\textcolor{red}{When using Lamperti, the form }
+
+\section{New model}
+In what follows we adapt the proof of the above theorem for the new model 
+\begin{align}\label{eq:model2}
+dX_t&= \big(\dot p_t - \theta_t(X_t-p_t)  \big)dt  +\sqrt{2\alpha \red{\theta_0}X_t(1-X_t)} dW_t\quad t\in[0,T]\\
+X_0&=x_0\in[0,1],\notag
+\end{align}
+
+\begin{Thm}\label{thm:mod2}
+Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
+Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$.
+Assume in addition that for all $t\in[0,T]$,  $p_t\in]0,1[$ and that
+\red{
+\begin{equation}\label{Assumption:3}
+\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
+\end{equation}
+}
+ Then, $\tau_0=\tau_1=+\infty$ a.s.
+\end{Thm}
+
+\begin{proof}
+For $t\in[0,\tau_0[$, we have 
+$$
+\frac{dX_t}{X_t}= \left(\frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)dt  +\sqrt{\frac{2\alpha \red{\theta_0}(1-X_t)}{X_t}} dW_t 
+$$  
+so that
+$$
+X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \red{\theta_0}\alpha)}{X_s}ds+\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big),
+$$
+where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_s(1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \red{\theta_0}\alpha\ge0$, we deduce that
+$$
+X_t\ge x_0\exp\Big(\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big).
+$$
+By way of contradiction let us assume that  $\{\tau_0<\infty\}$, then letting $t\to \tau_0$ we deduce that $\lim_{t\to \infty} \mathbf 1_{\{\tau_0<\infty\}}M_{t\wedge \tau_0}=\mathbf -1_{\{\tau_0<\infty\}}\infty$ a.s.
+This leads to a contradiction since we know that continuous martingales likewise the Brownian motion cannot converge  almost surely to $+\infty$ or $-\infty$.
+It follows that $\tau_0=\infty$ almost surely.
+Next, recalling that  the process $(Y_t)_{t\geq 0}$  given by $Y_t=1-X_t$ is solution to
+$$
+dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \red{\theta_0}Y_t(1-Y_t)} dW_t 
+$$
+we deduce using similar arguments as above 
+$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \red{\theta_0}\ge 0$.
+ \end{proof}
+ \section{Answers to Renzo's questions} 
+{\color{blue}So, Theorem \ref{thm:mod2} answers the second question in slide 11.} The new condition \eqref{Assumption:3} that guarantees  for $(X_t)_{t\ge0}$ to stay in $]0,1[$ depends now on $\alpha$.
+I would keep condition \eqref{Assumption:3} as we have a proof for it.
+Moreover, if condition \eqref{Assumption:3} is satisfied, then  the orange condition in slide 8 is also satisfied
+since we have 
+$$
+\max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\ge \max\left(\frac{\frac{\alpha\theta_0}{2}+\dot p_t}{1-p_t},\frac{\frac{\alpha\theta_0}{2}-\dot p_t}{p_t}\right)
+$$
+which ensures that $Z$ don't hit the boundaries too according to Renzo's intuitive arguments.\\ 
+{\color{blue}Concerning, the first question on slide 11:} we can't apply Itô's formula, unless we are sure that the process don't hit the boundaries, that's why we have to assume  \eqref{Assumption:3} before using Itô's formula.
+In addition, as the diffusion coefficient of $X$  given by  $x\mapsto \sqrt{\frac{2\alpha \red{\theta_0}(1-x)}{x}}$  is strictly positive for all $x$ in the state space of $X$, namely $]0,1[$ under assumption \eqref{Assumption:3},  this is enough to ensure that the transformation between $Z$ and $X$ is bijective so that we deduce the existence and uniqueness of $Z$ from those of $X$.
+Otherwise the Lamperti transform is not valid if the state space of $X$ is $[0,1]$.
 

### 2020-03-10 LaTeX_code/paper/paper_1line.tex

@@
 This effect becomes clear when we inspect for different power production levels.
-We split the available data into a low, meduim and high power range.
+We split the available data into low, medium and high power range.
 See Figure (\ref{fig:data_curtailing}).\\

### 2020-03-12 LaTeX_code/paper/paper_1line.tex
Section 2 almost completed

@@
 
-We consider a general phenomenological model for the normalized wind power generation forecasts is the stochastic process $X = \{X_t, \, t>0\}$  be the   c process is defined by the following stochastic differential equation (SDE)
+In this section, once we analyzed the available dataset, we consider a type of phenomenological model for the normalized wind power generation forecasts which is given, in its most general form, as a stochastic process $X = \{X_t, \, t \in [0,T] \}$  defined by the following stochastic differential equation (SDE):
 
@@
   \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&=  a(X_t; p_t, \dot{p}_t,\bm{\theta}) \,dt + b (X_t; p_t, \bm{\theta} ) \,dW_t  \\
-     X_0  \!\!\!&=  x_0,
+    dX_t \!\!\!&=  a(X_t; p_t, \dot{p}_t,\bm{\theta}) \,dt + b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \,dW_t\,, \quad t \in [0,T]  \\
+     X_0  \!\!\!&=  x_0 \in [0,1],
   \end{array}\right. \label{eq:main}
@@
 \begin{itemize}
-\item $a(\cdot; p_t, \dot{p}_t,\bm{\theta}):[0,1] \to \mathbb{R} \ $  denotes a drift function,
-\item $b (\cdot;p_t, \bm{\theta} ):[0,1] \to \mathbb{R} \ $  a  diffusion function,
-\item $\bm{\theta}$ is a vector of parameters,
-\item $p_t$ is a time-dependent scalar value and $ \dot{p}_t$ is its time derivative at time $t$,
-\item $\{W_t, \, t >0\}$ is a standard Wiener process in $\mathbb{R}$.
+\item $a(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R} $  denotes a drift function,
+\item $b(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R}^+ $  a  diffusion function,
+\item $\bm{\theta}$ is a vector of unknown parameters,
+\item $(p_t)_{t \in [0,T]}$ is a time-dependent deterministic function $[0,1]$-valued and $ (\dot{p}_t)_{t \in [0,T]}$ is its time derivative,
+\item $\{W_t, \, t \in [0,T] \}$ is a standard real-valued Wiener process.
 \end{itemize}
 
-In this work, $p_t$ is to be considered as a deterministic forecast of the wind power generation at time $t$ which is available from an official source.
+In this work, $(p_t)_{t \in [0,T]}$ is to be considered as a deterministic forecast for the normalized wind power generation, which is provided by an official source.
 
-Our goal is to provide a specification of the model (\ref{eq:main}) to follow closely the available wind power forecasts while ensuring its unbiasedness with respect to the forecast.
-It is straightforward to show that $\mathbb{E} \left[X_t\right] = p_t$, where $p_t$ is the available deterministic wind power forecast for the time $t$.
+Our goal is to achieve a specification of the model (\ref{eq:main}) to follow closely the available normalized wind power forecasts while ensuring its unbiasedness with respect to the forecast.
 
-\subsection{Physical Constrains}
+\subsection{Physical Constraints}
 
-Let $p_t$ be a numerical wind power forecast, which is an input to this approach.
-Assume that the wind power generation forecasts are modeled as solutions to the following It\^{o} stochastic differential equation
+Let $(p_t)_{t \in [0,T]}$ be the available prediction function for the normalized wind power, which is an input to this approach.
+To start with the model specification, first we introduce a time-dependent drift function that features the mean-reverting property as well as derivative tracking:
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= \dot{p}_t \ dt - \theta_t (X_t - p_t) \ dt + b (X_t; \bm{\theta} ) \ dW_t\,, \quad t > 0  \\
-   X_0  \!\!\!&=  x_0 \,.
- \end{array}\right.  \label{model:derivative_tracking_X}
+a(X_t; p_t, \dot{p}_t, \bm{\theta}) = \dot{p}_t  - \theta_t (X_t - p_t)\,,  \label{drift:meanrev-derivtrack}
 \end{equation} 
+where $ (\theta_t)_{t \in [0,T]} $ is a positive deterministic function, whose range depends on $\bm{\theta}$, as will be explained shortly.
 
-According to the SDE specification in (\ref{model:derivative_tracking_X}), the process $X_t$ satisfies the two following properties: \begin{itemize}
-\item it is mean reverting to the wind power forecast $p_t$, and 
-\item it tracks the time derivative wind power forecast $\dot{p}_t$.  
+Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$.
+
+ Then, the process defined by (\ref{eq:main}) with drift (\ref{drift:meanrev-derivtrack}) satisfies the two following properties: 
+\begin{itemize}
+\item it reverts to its mean $p_t$, with a time-varying speed $ \theta_t$ that is proportional to the deviation of the process $X$ from its mean,
+\item it tracks the time derivative $\dot{p}_t$.  
 \end{itemize} 
@@
 
-We normalize the forecast and production data to Uruguay installed power capacity at the time of observation.
-Thus our process must be limited to the range $[0,1]$.
-To enforce this constraint, our  drift and diffusion terms  must satisfy certain rules.
+The forecast and production wind power data of Uruguay are normalized with respect to the installed power capacity during the period of observation.
+Thus, the mean-reverting level lies in $[0,1]$, and the process $X$  must take values in the same interval,a requirement that is not automatically fulfilled through the derivative tracking.
+To impose that the state space of $X$ is $[0,1]$, we may choose a convenient diffusion term, and require that the time-varying parameter $ \theta_t$ satisfies an ad-hoc condition.
 
-Let $\bm{\theta} = (\theta_0,\alpha)$.
-We want a process that follow the wind forecast, thus we choose mean reverting drift term which also tracks the derivative of $p_t$, which is an input to our model.
+Let $\bm{\theta} = (\theta_0,\alpha)$, and choose a state-dependent diffusion term that avoids the process exiting from the range $[0,1]$ as follows:
   \begin{equation}
-    a(x; p_t,\bm{\theta})=  \dot{p_t} - \theta_t(x - p_t)
+    b (X_t; \bm{\theta} )= \sqrt{2 \theta_0 \alpha X_t (1 - X_t)}
   \end{equation}
-where $\theta_t>0$ is a time-dependent parameter that controls the speed of reversion. {\color{red} Derivative tracking does not assure that the paths of the process $X$ take values in $[0,1]$.}
-
-We would like  a diffusion term that vanishes at the boundaries to prevent the process from escaping the region $[0,1]$.
-  \begin{equation}
-    b (x; p_t,\bm{\theta} )= \sqrt{2 \theta_t \alpha x (1-x)}
-  \end{equation}
-  where $\alpha >0$ is a constant parameter that controls the path variability.
-This diffusion term belongs to the Pearson diffusion family and, in particular, it is a Jacobi type diffusion.
+  where $\alpha >0$ is a unknown parameter that controls the path variability.
+This diffusion term belongs to the Pearson diffusion family and, in particular, it defines a Jacobi type diffusion.
 It is useful to recall that (\cite[440]{foso}) a Pearson diffusion is a stationary solution to a stochastic differential equation of the form
@@
   \end{equation}
-where $\theta>0$, and $a$, $b$ and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space and, together with $\mu$, the mean of the invariant distribution, determine the state space of the diffusion as well as the shape of the invariant distribution.
-\\ An exhaustive classification of the Pearson diffusions is presented in (\cite[440-443]{foso}) where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 \theta a x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the so-called Jacobi diffusions because the related eigenfunctions are Jacobi polynomials.
+where $\theta>0$, and $a$, $b$ and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space.
+These parameters, together with $\mu$, the mean of the invariant distribution, determine the state space of the diffusion as well as the shape of the invariant distribution.
 
-To further ensure that the process does not escape the region $[0,1]$, the mean reversion parameter has to be selected according to the following rule.
+An exhaustive classification of the (stationary) Pearson diffusions is presented in (\cite[440-443]{foso}) where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 \theta a x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the well-known Jacobi diffusions, so-called because the eigenfunctions of the infinitesimal generator of these processes are the Jacobi polynomials (see, for example, \cite[2860-2861]{leph}).
+
+It is worth mentioning that Jacobi diffusions have been successfully applied in several disciplines, among them econometrics (see  and references therein) and neuroscience (\cite{dotala}).
+
+However, a distinctive feature in our proposed model 
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    dX_t \!\!\!&= (\dot{p}_t  - \theta_t (X_t - p_t) ) dt +\sqrt{2 \theta_0 \alpha X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
+   X_0  \!\!\!&=  x_0\in [0,1] \,,
+ \end{array}\right.  \label{ourmodel}
+\end{equation}
+
+is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X$ to (\ref{ourmodel}) a non-stationary and time-inhomogeneous process.
+To ensure that the process $X$ be the unique strong solution to (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the following condition:
+%has to be selected according to the following rule.
 Observe that the time derivative term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays a.s.
@@
 Thus, we must have that
-\begin{equation}
-\frac{- |\dot{p_t}|}{p_t} \leq \theta_t \leq \frac{|\dot{p}_t|}{1- p_t}
+%\begin{equation}
+%\frac{- |\dot{p_t}|}{p_t} \leq \theta_t \leq \frac{|\dot{p}_t|}{1- p_t}
+%\end{equation}
+%which is satisfied  by choosing a time-dependent  $\theta_t$ as follows,
+%\begin{equation}
+%\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \theta_0 >0\,. \label{theta_t}
+%\end{equation}
+\begin{equation}\label{Assumption:3}
+\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
 \end{equation}
-which is satisfied  by choosing a time-dependent  $\theta_t$ as follows,
-\begin{equation}
-\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \theta_0 >0\,. \label{theta_t}
-\end{equation}
+The proof of this theoretical statement is presented in Section \ref{Appendix}.
 
-{\color{red} The expression for $\theta_t$ is important: $\theta_t$ depens on $t$ through $\dot{p_t}$ and $p_t$.
-Besides it is parsimonious because only one unkonwn parameter appear in \ref{theta_t}.
+%{\color{red} The expression for $\theta_t$ is important: $\theta_t$ depens on $t$ through $\dot{p_t}$ and $p_t$.
+Besides it is parsimonious because only one unknown parameter appear in \ref{theta_t}.
 Recall it is an upped bound for the real inequality.
@@
 
-\subsubsection*{Change of Variables:}
-To avoid differentiation of the forecast $p_t$ and simplify, we apply the change of variables $$V_t = X_t - p_t \,.$$
+%\subsubsection*{Change of Variables:}
+\subsection{A model specification for the forecast error}
+ After applying the simple change of variables $$V_t = X_t - p_t \,,$$ we may introduce the following model for the forecast error of the normalized wind power production:
 
-The  model becomes,
 \begin{equation}
-\begin{cases}
-    \dif V_t &=  - \theta_t V_t \ \dif t + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  \dif W_t \\
-V_0 \!\!\!&=  v_0 \,.\\ 
-%\theta_t &= \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
-\end{cases}
-\label{VtSDE}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    dV_t \!\!\!&=  - \theta_t V_t  \, dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \, dW_t\,, \quad t \in [0,T]  \\
+   V_0  \!\!\!&=  v_0\in [-1,1] \,.
+ \end{array}\right.  \label{VtSDE}
 \end{equation}
+
 %---END SECTION 2---
@@
 
+%---BEGIN APPENDIX---
 \section{Appendix} \label{Appendix}

### 2020-03-22 LaTeX_code/paper/paper_1line.tex
Section 2 almost done

@@
 \item $a(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R} $  denotes a drift function,
-\item $b(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R}^+ $  a  diffusion function,
+\item $b(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R}_+ $  a  diffusion function,
 \item $\bm{\theta}$ is a vector of unknown parameters,
@@
   \begin{equation}
-    b (X_t; \bm{\theta} )= \sqrt{2 \theta_0 \alpha X_t (1 - X_t)}
+    b (X_t; \bm{\theta} )= \sqrt{2 \alpha \theta_0 X_t (1 - X_t)}
   \end{equation}
@@
 
-An exhaustive classification of the (stationary) Pearson diffusions is presented in (\cite[440-443]{foso}) where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 \theta a x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the well-known Jacobi diffusions, so-called because the eigenfunctions of the infinitesimal generator of these processes are the Jacobi polynomials (see, for example, \cite[2860-2861]{leph}).
+An exhaustive classification of the (stationary) Pearson diffusions is presented in (\cite[440-443]{foso}) where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 a \theta x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the well-known Jacobi diffusions, so-called because the eigenfunctions of the infinitesimal generator of these processes are the Jacobi polynomials (see, for example, \cite[2860-2861]{leph}).
 
-It is worth mentioning that Jacobi diffusions have been successfully applied in several disciplines, among them econometrics (see  and references therein) and neuroscience (\cite{dotala}).
+It is worth mentioning that Jacobi diffusions have been successfully applied in several disciplines, among them finance (see \cite{vago} and references therein) and neuroscience (\cite{dotala}).
 
@@
   \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= (\dot{p}_t  - \theta_t (X_t - p_t) ) dt +\sqrt{2 \theta_0 \alpha X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
+    dX_t \!\!\!&= (\dot{p}_t  - \theta_t (X_t - p_t) ) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
    X_0  \!\!\!&=  x_0\in [0,1] \,,
@@
 \theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
+\end{equation} \label{condC}
+The proof of this theoretical statement is presented in Section \ref{Appendix}. \\
+
+Remark: Condition (C) shows that the time-varying parameter $\theta_t$ becomes unbounded when $p_t = 0$ or $p_t = 1$. Therefore, we consider the following truncated prediction function
+\begin{equation}
+  p_t^{\epsilon} = \left\{
+  \begin{array}{@{}cl@{}}
+    \epsilon \!\!\!&\text{if } p_t  < \epsilon  \\
+    p_t  \!\!\!&\text{if }  \epsilon \leq p_t < 1 - \epsilon \\
+    1 - \epsilon  \!\!\!&\text{if }  p_t \geq 1 - \epsilon
+ \end{array}\right.  \label{corrforecast}
 \end{equation}
-The proof of this theoretical statement is presented in Section \ref{Appendix}.
+that satisfies $p_t^{\epsilon} \in [\epsilon, 1 - \epsilon]$ for any $0 < \epsilon < \frac{1}{2}$ and $t \in [0,T]$, providing that $\theta_t$ is bounded for every $t \in [0,T]$. \\
+From now on, we will keep the notation $p_t$ to denote the truncated prediction function (\ref{corrforecast}) with, unless specified otherwise, $\epsilon = 10^{-2}$.
 
@@
 \subsection{A model specification for the forecast error}
- After applying the simple change of variables $$V_t = X_t - p_t \,,$$ we may introduce the following model for the forecast error of the normalized wind power production:
+ After applying to (\ref{ourmodel}) the simple change of variables $$V_t = X_t - p_t \,,$$ we may introduce the following model for the forecast error of the normalized wind power production:
 
@@
   \begin{array}{@{}rl@{}}
-    dV_t \!\!\!&=  - \theta_t V_t  \, dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \, dW_t\,, \quad t \in [0,T]  \\
-   V_0  \!\!\!&=  v_0\in [-1,1] \,.
+    dV_t \!\!\!&=  - \theta_t V_t  \, dt + \sqrt{2 \alpha \theta_0 (V_t +p_t ) (1-V_t-p_t)} \, dW_t\,, \quad t \in [0,T]  \\
+   V_0  \!\!\!&=  v_0\in [-1 + \delta,1 - \delta] \,.
  \end{array}\right.  \label{VtSDE}
@@
 
-We consider the following Lamperti transformation  {\color{red} (Remind that in continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
+We consider the following Lamperti transformation  
+%{\color{red} (Remind that continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
 Besides, it can be unstable to work with low frequency.
@@
 \begin{equation}
-Z_t = h(V_t) = \frac{1}{\sqrt{2 \theta_t \alpha}} \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
+Z_t = h(V_t, t) = \frac{1}{\sqrt{2 \theta_0 \alpha}} \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
 \end{equation}
@@
 \begin{equation}
-Z_t = h(V_t) = \frac{1}{\sqrt{2 \theta_t \alpha}} \arcsin (2(V_t + p_t) -1)\,,
+Z_t = h(V_t, t) = \frac{1}{\sqrt{2 \theta_0 \alpha}} \arcsin (2(V_t + p_t) -1)\,,
 \end{equation}
-that, after applying It\^{o}'s formula on $h(V_t)$, gives the state-independent diffusion SDE
+that, after applying It\^{o}'s formula on $h(V_t, t)$, gives the state-independent diffusion SDE
 \begin{equation}
@@
 
-We can see in Figure (\ref{fig:skew_after_lamperti}) the effect of the Lamperti transformation upon the forecast error data. 
+{\color{red}We can see in Figure (\ref{fig:skew_after_lamperti}) the effect of the Lamperti transformation upon the forecast error data. 
 The Lamperti transformation has greatly reduced the forecast error skewness, ensuring that the process stays in the range $[0,1]$.
-Therefore, in this case, the transition densities of the process Z can be adequately approximated through Gaussian densities.
+Therefore, in this case, the transition densities of the process Z can be adequately approximated through Gaussian densities.}
 %---END SECTION 3---
@@
 
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t >0 \}$ is sampled at $N$ equispaced discrete points with length interval $\Delta_N$, and let $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ denote this random sample.
+Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N$ equispaced discrete points with length interval $\Delta_N$, and let $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ denote this random sample.
 
@@
   \item Model 1: This model does not feature derivative tracking.
-  \begin{align}
-  dX_t &=  - \theta_0 (p_t-X_t) \  dt + \sqrt{2 \theta \alpha X_t (1-X_t)} \  dW_t   \nonumber \\ %\quad t > 0
-  X_0 & = x_0 \,, \label{M0}
- \end{align}
-  with $\theta_t= \theta_0 $.
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    dX_t \!\!\!&=  - \theta_0 (X_t - p_t) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
+   X_0  \!\!\!&=  x_0\in [0,1] \,,
+ \end{array}\right.  \label{Model1}
+\end{equation}
+ with $\theta_0 > 0, \, \alpha > 0$.
 
@@
 
-  \item Model 2: This model features derivative tracking, i.e. it is equivalent to (\ref{model:derivative_tracking_X}).
-  \begin{align}
-  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t   \nonumber \\ %\quad t > 0
-  V_0 & = v_0 \,, \label{M2}
-  \end{align}
-  with $\theta_t$ given by (\ref{theta_t}).
+  \item Model 2: This model features derivative tracking and time-varying mean-reversion parameter:  
+%i.e. it is equivalent to (\ref{model:derivative_tracking_X}).
+%  \begin{align}
+%  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t   \nonumber \\ %\quad t > 0
+%  V_0 & = v_0 \,, \label{M2}
+%  \end{align}
+%  with $\theta_t$ given by (\ref{theta_t}).
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    dX_t \!\!\!&= (\dot{p}_t  - \theta_t (X_t - p_t) ) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
+   X_0  \!\!\!&=  x_0\in [0,1] \,,
+ \end{array}\right.  \label{Model2}
+\end{equation}
+ with $\theta_0 > 0, \, \alpha > 0$ and .
 \end{itemize}

### 2020-03-24 LaTeX_code/paper/paper_1line.tex
Section 3 updated

@@
   \begin{array}{@{}cl@{}}
-    \epsilon \!\!\!&\text{if } p_t  < \epsilon  \\
-    p_t  \!\!\!&\text{if }  \epsilon \leq p_t < 1 - \epsilon \\
-    1 - \epsilon  \!\!\!&\text{if }  p_t \geq 1 - \epsilon
+    \epsilon \!\!\!&\text{if \quad} p_t  < \epsilon  \\
+    p_t  \!\!\!&\text{if \quad}  \epsilon \leq p_t < 1 - \epsilon \\
+    1 - \epsilon  \!\!\!&\text{if \quad}  p_t \geq 1 - \epsilon
  \end{array}\right.  \label{corrforecast}
@@
 that satisfies $p_t^{\epsilon} \in [\epsilon, 1 - \epsilon]$ for any $0 < \epsilon < \frac{1}{2}$ and $t \in [0,T]$, providing that $\theta_t$ is bounded for every $t \in [0,T]$. \\
-From now on, we will keep the notation $p_t$ to denote the truncated prediction function (\ref{corrforecast}) with, unless specified otherwise, $\epsilon = 10^{-2}$.
+From now on, we will keep the notation $p_t$ to denote the truncated prediction function (\ref{corrforecast}), unless specified otherwise.
 
@@
 %---BEGIN SECTION 3---
-\section{State independent diffusion: Lamperti transform} \label{Section_3}
+\section{State independent diffusion term: Lamperti transform} \label{Section_3}
 
@@
 To estimate the unknown model parameters, a recommended technique is to modify the SDE (\ref{VtSDE}) by applying the so-called Lamperti transform (see \cite[40--41]{iacus1}, \cite{moma}, \cite[98--100]{saso}) to the process $V$ to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
-\\
-
-We consider the following Lamperti transformation  
+To this purpose, we consider the following Lamperti transformation
 %{\color{red} (Remind that continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
@@
 )}
-\begin{equation}
-Z_t = h(V_t, t) = \frac{1}{\sqrt{2 \theta_0 \alpha}} \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
-\end{equation}
-where $\xi$ is an arbitrary point of the state space of the process $V$. The choice of $\xi = \frac{1}{2} - p_t$, where $p_t$ is a known input, leads to the process 
-\begin{equation}
-Z_t = h(V_t, t) = \frac{1}{\sqrt{2 \theta_0 \alpha}} \arcsin (2(V_t + p_t) -1)\,,
-\end{equation}
-that, after applying It\^{o}'s formula on $h(V_t, t)$, gives the state-independent diffusion SDE
-\begin{equation}
-dZ_t = \left[  \frac{- \theta_t V_t}{ \sqrt{2 \theta_t \alpha (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \theta_t \alpha} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \right] \,dt + dW_t \,.
+%\begin{equation}
+%Z_t = h(V_t, t) = \frac{1}{\sqrt{2 \theta_0 \alpha}} \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
+%\end{equation}
+%where $\xi$ is an arbitrary point of the state space of the process $V$. The choice of $\xi = \frac{1}{2} - p_t$, where $p_t$ is a known input, 
+\begin{align}
+Z_t = h(V_t, t)  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \,dv \Bigg{\vert}_{v = V_t}  \nonumber \\
+& = \frac{1}{\sqrt{2 \alpha \theta_0 }} \arcsin (2(V_t + p_t) -1)
+\end{align}
+that, after applying It\^{o}'s formula on $h(V_t, t)$, leads to the following SDE with state independent diffusion term
+\begin{align}
+dZ_t = \Bigg[  & \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  \nonumber \\ 
+& + \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \,dt + dW_t \,.
 \label{eq:stindepSDE}
-\end{equation}
-After replacing $V_t = \frac{\sin(\sqrt{2 \theta_t \alpha} Z_t) + 1}{2} - p_t$ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
+\end{align}
+After replacing $V_t = \frac{\sin(\sqrt{2 \alpha \theta_0} Z_t) + 1}{2} - p_t$ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
 \begin{align}
-dZ_t & = \left[ \frac{- \theta_t (\sin(\sqrt{2 \theta_t \alpha} Z_t) + 1 - 2 p_t)}{\sqrt{2 \theta_t \alpha} \cos{(\sqrt{2 \theta_t \alpha} Z_t)}} + \frac{\sqrt{2 \theta_t \alpha} \sin{(\sqrt{2 \theta_t \alpha} Z_t)}}{2 \cos{(\sqrt{2 \theta_t \alpha} Z_t)}} \right] \,dt + dW_t \nonumber \\
-&  = \left[  \frac{\sqrt{2 \theta_t} \left( \sin(\sqrt{2 \theta_t \alpha} Z_t) (\alpha - 1) + (2 p_t -1 ) \right)}{2 \sqrt{\alpha} \cos{(\sqrt{2 \theta_t \alpha} Z_t)}}  \right] \,dt + dW_t \,. 
+dZ_t & = \Bigg[ \frac{2 \dot{p}_t}{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}} + \frac{- \theta_t (\sin(\sqrt{2 \alpha \theta_0} Z_t) + 1 - 2 p_t)}{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}} \nonumber \\
+&  + \frac{\sqrt{2 \alpha \theta_0} \sin{(\sqrt{2 \alpha \theta_0} Z_t)}}{2 \cos{(\sqrt{2 \alpha \theta_0} Z_t)}} \Bigg] \,dt + dW_t \nonumber \\
+&  = \left[  \frac{(\alpha \theta_0 - \theta_t) \sin(\sqrt{2 \alpha \theta_0 } Z_t) - \theta_t (1 - 2 p_t) + 2  \dot{p}_t }{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}}  \right] \,dt + dW_t \,.
 \end{align}
-
-%\begin{align}
-%    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} \ dt + \sqrt{2 \alpha \theta_t} dW_t \\
-%    Z_0&=z_0 \,,
-%\end{align}
-%where the Lamperti trasform is given by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
 

### 2020-03-26 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
Added MATLAB files. Removed Python files. Added all extra PDFs with reports

--- 2020-02-09 LaTeX_code/MATLAB_readMe/MATLAB_readMe.tex
@@
 \setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Code diagram:}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.8\textwidth]{../Results/project/20200320_MATLAB_Files_Graph.pdf}
+\end{figure}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
 \begin{frame}\frametitle{Questions:}
@@
 \begin{equation*}
-\dif V_t=-\theta_tV_t\dif t+\sqrt{2\theta_t\alpha(V_t+p_t)(1-V_t-p_t)}\dif W_t,
+\dif V_t=-\theta_tV_t\dif t+\sqrt{2\theta_0\alpha(V_t+p_t)(1-V_t-p_t)}\dif W_t,
 \end{equation*}
@@
 \begin{equation*}
-\dif V_t=-\alert{\theta_tT}V_t\dif\hat{t}+\sqrt{2\alert{\theta_tT}\alpha(V_t+p_t)(1-V_t-p_t)}\dif\hat{W}_t.
+\dif V_t=-\alert{\theta_tT}V_t\dif\hat{t}+\sqrt{2\alert{\theta_0T}\alpha(V_t+p_t)(1-V_t-p_t)}\dif\hat{W}_t.
 \end{equation*}
-We conclude that, whatever the normalization constant T is, it gets absorbed by the parameter $\theta_t$ (let $\hat{\theta}_t=\theta_t T$).
+We conclude that, whatever the normalization constant T is, it gets absorbed by the parameter $\theta_t$ or $\theta_0$ (let $\hat{\theta}_t=\theta_t T$ and $\hat{\theta}_0=\theta_0 T$).
 \quad\\
@@
 \begin{equation*}
-V_{t_{n+1}}=V_{t_{n}}-\left[\hat{\theta}_{t_n}V_{t_n}\right]\Delta s+\left[\sqrt{2\hat{\theta}_{t_n}\alpha(V_{t_n}+p_{t_n})(1-V_{t_n}-p_{t_n})}\right]\sqrt{\Delta s}\Delta\hat{W}_{t_n},\ V_{t_0}=v_0,
+V_{t_{n+1}}=V_{t_{n}}-\left[\hat{\theta}_{t_n}V_{t_n}\right]\Delta s+\left[\sqrt{2\hat{\theta}_{0}\alpha(V_{t_n}+p_{t_n})(1-V_{t_n}-p_{t_n})}\right]\sqrt{\Delta s}\Delta\hat{W}_{t_n},\ V_{t_0}=v_0,
 \end{equation*}
@@
 \end{center}
-
+Notice we use the function \textbf{betaln(a,b)}. It is important to compute the log directly for the beta function, and no first the beta, and after apply log.
 \end{frame}
@@
 \setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{From $\theta_0$ to $\theta_t$:}
+{\small
+To ensure that the analytical solutions is always in $]0,1[$, we choose the drift parameter to be
+\begin{equation*}
+\theta(t) = \max\left(\theta_0,\frac{\theta_0\alpha+2|\dot{p}^\epsilon(t)|}{2\min(p^\epsilon(t),1-p^\epsilon(t))}\right),\quad\theta_0>0.
+\end{equation*}
+\quad\\
+\quad\\
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\tiny
+\lstinputlisting{../theta_t.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{From $p_t$ to $p_t^\epsilon$:}
+
+To ensure that $\theta(t)$ does not blow up, we truncate the forecast so it is always in $[\epsilon,1-\epsilon]$ for some $\epsilon\in(0,1/2)$.
+
+{\small
+\begin{columns}[c]
+
+\column{.5\textwidth}
+Where $p^\epsilon(t)=\begin{cases}
+\epsilon\quad&\text{if}\quad p(t)<\epsilon\\
+p(t)\quad&\text{if}\quad \epsilon\leq p(t)<1-\epsilon\\
+1-\epsilon\quad&\text{if}\quad p(t)\geq1-\epsilon
+\end{cases}$.
+
+\column{.5\textwidth}
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\tiny
+\lstinputlisting{../pe.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}
+
+\end{columns}}
+
+{\small
+\begin{columns}[c]
+
+\column{.5\textwidth}
+$\dot{p}^\epsilon_t=\frac{\dif p^\epsilon}{\dif t}$. We use finite differences.
+
+\column{.5\textwidth}
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\tiny
+\lstinputlisting{../pe_dot.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}
+
+\end{columns}}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Adapting the data:}
+
+\begin{columns}[c]
+
+\column{.2\textwidth}
+We use this function to truncate the forecast, calculate its derivative, and to define the new errors ($X_t-p_t^\epsilon$) associated with the new truncated forecast.\\
+We call to all this new set of data, the truncated data.
+
+\column{.7\textwidth}
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\tiny
+\lstinputlisting{../load_data_eps.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}
+
+\end{columns}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
 \begin{frame}\frametitle{Create a new batch (1/2):} \label{cre_batch}
 
-To guarantee the data homogeneity, we sample per day and not per transition.
-This means that each batch is composed of data corresponding to some amount of days.
-If we sample a total of $Z\in\N$ days, the batch corresponding to this days is
+\alert{This function is independent of if we are using the real data or the truncated one.} If we take a total of $Z\in\N$ days, the batch corresponding to this days is
 \begin{table}[]
@@
 {\tiny
-\lstinputlisting{../new_batch.m}
+\lstinputlisting{../new_batch_fixed.m}
 }\\
@@
 \end{center}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{From $\theta_0$ to $\theta_t$:}
-
-To ensure that the analytical solutions is always in $[0,1]$, we choose the drift parameter to be
-\begin{equation*}
-\theta(t) = \max\left(\theta_0,\frac{|\dot{p}(t)|}{\min(p(t),1-p(t))}\right),\quad\theta_0>0.
-\end{equation*}
-\quad\\
-\quad\\
-\begin{center}
-\begin{tabular}{|c|}
-\toprule
-{\tiny
-\lstinputlisting{../theta_t.m}
-}\\
-\bottomrule
-\end{tabular}
-\end{center}
-
+We call it \textbf{fixed} because, at some point, we were going to optimize the Likelihood taking random batches and increasing the size at each iteration.
+This idea was discarded since we have computational power enough to use all data at once.
 \end{frame}
@@
 \begin{frame}\frametitle{Complete batch:}
-
-After we created a batch with the elements $(p(t),\dot{p}(t),V(t))$, we want to add the parameter $\theta(t)$ to use in the likelihood.
+{\footnotesize
+\alert{This function is independent of if we are using the real data or the truncated one.} After we created a batch with the elements $(p(t),\dot{p}(t),V(t))$, we want to add the parameter $\theta(t)$ to use in the likelihood.
 Following the same idea than in slide {\color{blue}\ref{cre_batch}}, the complete batch is
@@
 \end{tabular}
-\end{center}
+\end{center}}
 
@@
 
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Initial guess for $\theta_0\cdot\alpha$:}
-Recall we have $M$ paths with $N+1$ measurements each.
+%\setbeamercolor{background canvas}{bg=red!20}
+%\begin{frame}\frametitle{Initial guess for $\theta_0\cdot\alpha$:}
+%Recall we have $M$ paths with $N+1$ measurements each.
+%\begin{equation*}
+%\theta_0 \alpha\approx \frac{1}{2M\Delta t} \sum\limits_{j=1}^M \frac{ \sum\limits_{i=1}^{N} (x_{i+1,j}  - x_{i,j})^2}{\sum\limits_{i=1}^{N} x_{i,j}(1-x_{i,j}) }\alert{\approx 0.094}.
+%\end{equation*}
+%
+%\begin{center}
+%\begin{tabular}{|c|}
+%\toprule
+%{\tiny
+%\lstinputlisting{../initial_guess.m}
+%}\\
+%\bottomrule
+%\end{tabular}
+%\end{center}
+%
+%\end{frame}
+%
+%
+%%\setbeamercolor{background canvas}{bg=white!10}
+%\begin{frame}\frametitle{Initial guess for $\theta_0$ (1/2):} \label{VF}
+%Recall we have $M$ paths with $N+1$ measurements each.
+%\begin{equation*}
+%\theta_0\approx\arg\min_{\theta_0}\left[\sum_{j=1}^M\sum_{i=1}^N\left(v_{i+1,j}-v_{i,j}+\theta_{t_i}v_{i,j}\Delta t\right)^2\right].
+%\end{equation*}
+%
+%\begin{center}
+%\begin{tabular}{|c|}
+%\toprule
+%{\tiny
+%\lstinputlisting{../initial_theta.m}
+%}\\
+%\bottomrule
+%\end{tabular}
+%\end{center}
+%
+%\end{frame}
+%
+%
+%%\setbeamercolor{background canvas}{bg=white!10}
+%\begin{frame}\frametitle{Initial guess for $\theta_0$ (2/2):}
+%
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[width=0.35\textwidth]{../Results/initial_guess/initial_theta_1.eps}\quad\quad\quad
+%\includegraphics[width=0.35\textwidth]{../Results/initial_guess/initial_theta_2.eps}
+%\caption{On the left, we use the value function defined in slide {\color{blue}\ref{VF}}.
+On the right, we substitute in the value function $\theta_t$ by $\theta_0$ and plot that \textit{new value function}.
+We use the value from the left plot.}
+%\end{figure}
+%\alert{$\theta_0\approx 0.67
+%$ and $\theta_0\alpha\approx 0.094\implies\alpha\approx0.15$.} If we use the plot on the right, then $\theta_0\approx1.23$ and $\alpha\approx0.08$.
+%
+%\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!20}
+\begin{frame}\frametitle{Initial guess for $\theta_0\cdot\alpha$: Quadratic variation}
+
+Recall we have $M$ paths with $N+1$ measurements each. Depending on the SDE we are using, we have the two approximations:
+{\footnotesize
 \begin{equation*}
-\theta_0 \alpha\approx \frac{1}{2M\Delta t} \sum\limits_{j=1}^M \frac{ \sum\limits_{i=1}^{N} (x_{i+1,j}  - x_{i,j})^2}{\sum\limits_{i=1}^{N} x_{i,j}(1-x_{i,j}) }\alert{\approx 0.021}.
+X_t:\theta_0^*\alpha^*\approx \frac{1}{2M\Delta t} \sum\limits_{j=1}^M \frac{ \sum\limits_{i=1}^{N} (\Delta X_{i,j})^2}{\sum\limits_{i=1}^{N} (X_{i,j})(1-X_{i,j})},\quad V_t:\theta_0^*\alpha^*\approx \frac{1}{2M\Delta t} \sum\limits_{j=1}^M \frac{ \sum\limits_{i=1}^{N} (\Delta V_{i,j})^2}{\sum\limits_{i=1}^{N} (V_{i,j}+p_{i,j})(1-V_{i,j}-p_{i,j})}
 \end{equation*}
-
+}
 \begin{center}
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Initial guess for $\theta_0$:}
-Recall we have $M$ paths with $N+1$ measurements each.
+\begin{frame}\frametitle{Initial guess for $\theta_0$ (1/2): Mean least squares} \label{VF}
+Recall we have $M$ paths with $N+1$ measurements each. If we assume $\theta_t^\epsilon=\theta_0$ for $t\in[0,T]$, then we have
+\begin{equation}
+\theta_0^*\approx\arg\min_{\theta_0}{\left[\sum_{j=1}^M\sum_{i=1}^N\left(V_{i+1,j}-V_{i,j}(1-\theta_0\Delta t)\right)^2\right]}.
+\label{Eq-1}
+\end{equation}
+
+%\begin{center}
+%\begin{tabular}{|c|}
+%\toprule
+%{\tiny
+%\lstinputlisting{../initial_theta_0.m}
+%}\\
+%\bottomrule
+%\end{tabular}
+%\end{center}
+
+As problem (\ref{Eq-1}) is convex, we can formulate the equivalent problem using derivatives
 \begin{equation*}
-\theta_0\approx\arg\min_{\theta_0}\left[\sum_{j=1}^M\sum_{i=1}^N\left(v_{i+1,j}-v_{i,j}+\theta_{t_i}v_{i,j}\Delta t\right)^2\right].
+\theta_0^*\approx\frac{1}{\Delta t\cdot M}\sum_{j=1}^M\frac{\sum_{i=1}^NV_{i,j}(V_{i,j}-V_{i+1,j})}{\sum_{i=1}^NV_{i,j}^2}.
 \end{equation*}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Initial guess for $\theta_0$ (2/2): Mean least squares}
+
+As we need to assume that $\theta_t^\epsilon=\alert{c}\in\R^+$ in order to use correctly the estimator (\ref{Eq-1}), we define $\epsilon,\gamma\in\R^+$, and estimate $\frac{\theta_0\alpha}{\delta}$ using data which original forecast satisfies $p_i\notin(\epsilon,1-\epsilon)$ and $\theta_0$ using data which original forecast satisfies $p_i\in[\gamma,1-\gamma]$.
+The full explanation can be found in slides \textbf{20200308 - Initial Guess.pdf}.
 
@@
 {\tiny
-\lstinputlisting{../initial_theta.m}
+\lstinputlisting{../mean_regression_eps.m}
 }\\
@@
 \end{center}
+To create this specific data sets, we use the functions \textbf{create\_samples\_eps.m} ($\epsilon$-data) and \textbf{create\_samples\_minus\_eps.m} ($\gamma$-data).
 
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Initial guess for $\theta_0$:}
+\begin{frame}\frametitle{Initial guess for $\delta$:}
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.45\textwidth]{theta_0.eps}
-\end{figure}
+We have that, for almost all days, at time $t=t_0$, $X(t_0)\neq p(t_0)$ and then $V(t_0)\neq0$.
+However, by forecast construction, there should exist a time $t_{-\delta}<t_0$ such that $V(t_{-\delta})=0$.\\
+\quad\\
+We extrapolate linearly $p(t)$ so we can evaluate $p(t_{-\delta})$, and assume that $V(t_{-\delta})=0$.
+Then, for each day $j$, we have an initial transition $(V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta)$.
+We assume again that it is Beta and apply the same moment matching as for the rest of transitions.
+With our initial guess for $\bm{\theta}$, we can construct our initial guess for $\delta$ solving the problem
 
-\alert{$\theta_0\approx 1.1450
-$ and $\theta_0\alpha\approx 0.021\implies\alpha\approx0.018$.}
+\begin{equation*}
+\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
+\label{likelihood_delta}
+\end{equation*}
+
+See slides \textbf{20200319 - Time delta} for very detailed information.\\
+\quad\\
+We use $\delta=\SI{5.5}{\hour}$.
 
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Log-likelihood evaluation: CODE}
+\begin{frame}\frametitle{Log-likelihood evaluation (1/2): CODE}
 
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Log-likelihood: Plot}
+\begin{frame}\frametitle{Log-likelihood evaluation (2/2):}
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{../log_likelihood.eps}\quad\includegraphics[width=0.45\textwidth]{../log_likelihood_2.eps}
+\includegraphics[width=0.32\textwidth]{../Results/likelihood/Log-Likelihood.eps}
+\includegraphics[width=0.32\textwidth]{../Results/likelihood/Log-Likelihood_refined.eps}
+\includegraphics[width=0.32\textwidth]{../Results/likelihood/Log-Likelihood_more_refined.eps}
+\caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions, and we can also see the initial guess.}
 \end{figure}
@@
 
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Summing-up:}
+
+\begin{enumerate}
+
+\item Initial guess: From quadratic variation and using all the data we get $\hat{\theta}_0\times\hat{\alpha}$.
+Choosing some appropiate $\gamma$, from mean least squares we get $\hat{\theta}_0$, then we also get $\hat{\alpha}$.\\
+Also, from mean least squares we can estimate $\epsilon^*$, using that the least squares estimator estimates $\frac{\theta_0\alpha}{\epsilon}$ for some appropriate $\epsilon$.\\
+Finally, using the pair $(\hat{\theta}_0,\hat{\alpha})$, we can obtain $\hat{\eta}$ and $\hat{\delta}$.
+
+\item Optimal parameters: Using the training data and the initial point $(\hat{\theta}_0,\hat{\alpha})$, we can find the optimal pair $(\theta_0^*,\alpha^*)$ using the MLE.
+With this new pair, we can find $\eta^*$ and $\delta^*$.
+
+\end{enumerate}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Values for the parameters:}
+
+\begin{table}[]
+\begin{tabular}{cccccc}
+\toprule
+$\hat{\theta}_0$ & $\hat{\alpha}$ & $\hat{\eta}$ & $\hat{\delta}$ & $\gamma$ & $\epsilon$ \\
+\midrule
+$1.63$ & $0.06$ & *not apply* & $\SI{220}{\min}$ & $0.3$ & $0.018$ \\
+\bottomrule
+\end{tabular}
+\end{table}
+$\eta^{ini}$ is not relevant here because we do not need to remove any data to find $\delta^{ini}$.
+\begin{table}[]
+\begin{tabular}{ccccc}
+\toprule
+$\theta_0^{*}$ & $\alpha^{*}$ & $\eta^{*}$ & $\delta^{*}$ \\
+\midrule
+$3.91$ & $0.02$ & $0.1$ & $\SI{220}{\min}$ \\
+\bottomrule
+\end{tabular}
+\end{table}
+Notice that $\hat{\delta}=\delta^*$.
+However, to obtain $\delta^*$ we had to remove all initial errors larger than $\eta^*$, and in this way, we reduced the variance of the initial error.
+This has sense since $\theta^*_0\alpha^*<\hat{\theta}_0\hat{\alpha}$.
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Paths and bands for optimal values (1/4):}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.4\textwidth]{../Results/paths_testing_days/optimal_value/1.eps}\quad
+\includegraphics[width=0.4\textwidth]{../Results/bands_testing_days/optimal_value/1.eps}
+\end{figure}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Paths and bands for optimal values (2/4):}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.4\textwidth]{../Results/paths_testing_days/optimal_value/2.eps}\quad
+\includegraphics[width=0.4\textwidth]{../Results/bands_testing_days/optimal_value/2.eps}
+\end{figure}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Paths and bands for optimal values (3/4):}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.4\textwidth]{../Results/paths_testing_days/optimal_value/3.eps}\quad
+\includegraphics[width=0.4\textwidth]{../Results/bands_testing_days/optimal_value/3.eps}
+\end{figure}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Paths and bands for optimal values (4/4):}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.4\textwidth]{../Results/paths_testing_days/optimal_value/4.eps}\quad
+\includegraphics[width=0.4\textwidth]{../Results/bands_testing_days/optimal_value/4.eps}
+\end{figure}
+\end{frame}
+
 \end{document}

### 2020-03-26 Reports/20200302 - Lamperi for X and V/20200302 - Lamperi for X and V.tex
Added MATLAB files. Removed Python files. Added all extra PDFs with reports

\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{commath}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{siunitx}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}
\DeclareMathOperator{\sign}{sign}

\title{Lamperti Transform for the processes X and V}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{New model for the SDE: $\theta_t=\theta_0$ in the diffusion}

\begin{enumerate}

\item[$X_t$:] $\dif X_t=\left(\dot p_t-\theta_t(X_t-p_t)\right)\dif t+\sqrt{2\alert{\theta_0}\alpha X_t(1-X_t)}\dif W_t$
\item[$V_t$:] $\dif V_t=-\theta_tV_t\dif t+\sqrt{2\alert{\theta_0}\alpha(V_t+p_t)(1-V_t-p_t)}\dif W_t$

\end{enumerate}
Lamperti transform for $V_t$:
\begin{equation*}
\begin{split}
\psi(V_t,t)=\int\frac{1}{\sqrt{2\alert{\theta_0}\alpha(u+p_t)(1-u-p_t)}}\dif u\Bigg|_{u=V_t}&=-\sqrt{\frac{2}{\alpha\alert{\theta_0}}}\arcsin\left(\sqrt{1-V_t-p_t}\right),\\
&=-\sqrt{\frac{2}{\alpha\alert{\theta_0}}}\arcsin\left(\sqrt{1-X_t}\right).
\end{split}
\end{equation*}

We can see that for every $t=t^*$, the primitive function of $\frac{1}{\sigma(v,t^*)}$ is well defined for all $v\in\left[-p(t^*),1-p(t^*)\right]\subset[-1,1]$ (recall $v=x-p_t$, and $x\in[0,1]$; then, when $x=0$ and $x=1$, we have that $v=-p$ and $x=1-p$, respectively).

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Identities for the Lamperti transform of $V_t$:} \label{Q1}

\begin{itemize}
\item $\psi(V_t,t)=-\sqrt{\frac{2}{\alpha\alert{\theta_0}}}\arcsin(\sqrt{1-V_t-p_t})$.
\item $\psi_v(V_t,t)=\frac{1}{\sigma(V_t,t)}=\frac{1}{\sqrt{2\alpha\alert{\theta_0}(V_t+p_t)(1-V_t-p_t)}}$.
\item $\psi_{vv}(V_t,t)=\frac{\dif}{\dif v}\left[\frac{1}{\sigma(V_t,t)}\right]=-\frac{\sigma_v(V_t,t)}{\sigma^2(V_t,t)}=-\frac{1}{\sigma^2(V_t,t)}\cdot\sqrt{\frac{\alpha\alert{\theta_0}}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}$.
\item $\psi_t(V_t,t)=\frac{\dot{p}_t}{\sqrt{2\alpha\alert{\theta_0}(V_t+p_t)(1-V_t-p_t)}}$.
\end{itemize}
\quad\\
\quad\\
Recall $V_t=X_t-p_t$. Then $\psi_v$, $\psi_{vv}$, and $\psi_t$ are not defined when $X_t=0$ or $X_t=1$. However, this only happens in the boundary of the domain $(0,1)$.\\
\quad\\
\alert{Can we apply It\^o's lemma to $\psi$? Maybe as the singularities are in the boundary, it is possible despite that we are not strictly in the hypothesis of the lemma.}
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: ({\color{green}Verified with Mathematica})}

By It\^o's lemma, if $\psi(v,t)$ is $C^2([-p_t,1-p_t])$ for $v$ and $C^1([0,T])$ for $t$, then:
\begin{equation*}
\dif Z_t=\left({\color{blue}\psi_t}+\psi_v\cdot f+\alert{\frac{1}{2}\psi_{vv}\cdot\sigma^2}\right)\dif t+\psi_v\cdot\sigma\dif W_t.
\end{equation*}
If we substitute the terms related with $\psi(V_t,t)$ from slide (\ref{Q1}), we have
\begin{equation*}
{\footnotesize
\begin{split}
\dif Z_t=&\Bigg[{\color{blue}\frac{\dot{p}_t}{\sqrt{2\alpha\theta_0(V_t+p_t)(1-V_t-p_t)}}}\\
&-\frac{\theta_tV_t}{\sqrt{2\alpha\theta_0(V_t+p_t)(1-V_t-p_t)}}\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_0}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}}\Bigg]\dif t+1\cdot \dif W_t.
\end{split}}
\end{equation*}
Recall $\alert{Z_t=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-V_t-p_t}\right)}$, where $Z_t\in\Big[-\frac{\pi}{\sqrt{2\alpha\theta_t}},{\color{black}0\Big]}$.
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: ({\color{green}Computed with Mathematica})} \label{Q2}

\begin{equation*}
\dif Z_t=\underbrace{\left[\frac{\alpha\theta_0\cos(Z_t\sqrt{2\alpha\theta_0})-\theta_t\cos(Z_t\sqrt{2\alpha\theta_0})+2\theta_tp_t+2\dot{p}_t-\theta_t}{\sqrt{\alpha\theta_0}\sqrt{1-\cos(2Z_t\sqrt{2\alpha\theta_0})}}\right]}_{f(Z_t,t)}\dif t+1\cdot\dif W_t.
\end{equation*}\\
\begin{equation*}
\lim_{z\to0^-}f(z,t)=\infty\times\left[\frac{\sign\left(2\theta_tp_t+2\dot{p}_t+\alpha\theta_0-2\theta_t\right)}{\sign(\alpha)\sign(\theta_0)}\right].
\end{equation*}
\begin{equation*}
\lim_{z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+}f(z,t)=\infty\times\left[\frac{\sign\left(2\theta_tp_t+2\dot{p}_t-\alpha\theta_0\right)}{\sign(\alpha)\sign(\theta_0)}\right].
\end{equation*}
We want to find the correct conditions for $\theta_t$.\\
\quad\\
{\small To simplify the SDE, Mathematica has used: $\sin^2(x)-\sin^4(x)=\sin^2(x)\cos^2(x)=\frac{1}{4}\sin^2(2x)=\frac{1}{8}(1-\cos(4x))$.}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Limit when $z\to0^-$:}\label{C1}

Recall we have a bijective mapping $Z_t({\color{blue}[0},\alert{1]})={\color{blue}\Big[\frac{-\pi}{\sqrt{2\alpha\theta_0}}},\alert{0\Big]}$. This helps the intuition, as when $X_t=1$, we expect the diffusion to be negative, and $z\to0^-$ is equivalent to $x\to1^-$.\\
\quad\\
We want $\lim_{z\to0^-}f(z,t)$ to be $-\infty$ or zero, so we do not escape from $z=0$ to $z>0$ ($x=1$ to $x>1$). Then, we need $\alpha\theta_0-2\theta_t+2\theta_tp_t+2\dot{p}_t\leq0$. Then:
\begin{itemize}

\item If $p_t<1$, we have that ${\color{orange}\theta_t\geq\frac{\alpha\theta_0+2\dot{p}_t}{2(1-p_t)}}$.

\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Limit when $z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+$:}\label{C2}

Recall we have a bijective mapping $Z_t({\color{blue}[0},\alert{1]})={\color{blue}\Big[\frac{-\pi}{\sqrt{2\alpha\theta_0}}},\alert{0\Big]}$. This helps the intuition, as when $X_t=0$, we expect the diffusion to be positive, and $z\to\frac{-\pi}{\sqrt{2\alpha\theta_0}}^+$ is equivalent to $x\to0^+$.\\
\quad\\
We want $\lim_{z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+}f(z,t)$ to be $+\infty$ or zero, so we do not escape from $z=\frac{-\pi}{\sqrt{2\alpha\theta_t}}$ to $z<\frac{-\pi}{\sqrt{2\alpha\theta_t}}$ ($x=0$ to $x<0$). Then, we need $2\theta_tp_t+2\dot{p}_t-\alpha\theta_0\geq0$. Then:
\begin{itemize}

\item If $p_t>0$, we have that ${\color{orange}\theta_t\geq\frac{\alpha\theta_0-2\dot{p}_t}{2p_t}}$.

\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Controlled drift:}

From both {\color{orange}orange} conditions in slides (\ref{C1}) and (\ref{C2}), we create a more restrictive condition:
\begin{equation*}
\max\left({\color{orange}\frac{\alpha\theta_0+2\dot{p}_t}{2(1-p_t)}},{\color{orange}\frac{\alpha\theta_0-2\dot{p}_t}{2p_t}}\right)\leq\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}.
\end{equation*}
Then, we choose
\begin{equation}
\theta_t=\max\left(\theta_0,\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}\right).
\label{NC}
\end{equation}
\quad\\
Recall that in the paper, we start by choosing $\theta_t=\max\left(\theta_0,\frac{|\dot{p}_t|}{\min(1-p_t,p_t)}\right)$. Our new condition (\ref{NC}) is slightly more restrictive.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Limits when $p_t\approx0$ and $p_t\approx1$:}

It $p_t\approx0$, then $\theta_t=\frac{\alpha\theta_0+|2\dot{p}_t|}{2p_t}$, and we have the limit: $$\lim_{z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+}f(z,t)=\infty\times\sign(|\dot{p}_t|+\dot{p}_t).$$
As $p_t\approx0$, it is reasonable to assume $\dot{p}_t\geq0$. Then, the limit is $+\infty$.\\
\quad\\
It $p_t\approx1$, then $\theta_t=\frac{\alpha\theta_0+|2\dot{p}_t|}{2(1-p_t)}$, and we have the limit: $$\lim_{z\to0^-}f(z,t)=\infty\times\sign(\dot{p}_t-|\dot{p}_t|).$$
As $p_t\approx1$, it is reasonable to assume $\dot{p}_t\leq0$. Then, the limit is $-\infty$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Conditions summary:}

\begin{itemize}

\item First model: $\theta_t^{first}=\max\left(\theta_0,\frac{|\dot{p}_t|}{\min(1-p_t,p_t)}\right)$.
\item New condition from Lamperti: $\theta_t^{lamperti}=\max\left(\theta_0,\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}\right)$. Notice $\theta_t^{first}\leq\theta_t^{lamperti}$.
\item Professor Kebaier's condition: $0<\alpha<1/2$, $\alpha<p_t<1-\alpha$, and $\theta_t^{kebaier}=\max\left(\theta_0,\frac{|\dot{p}|}{\min(p-\alpha,1-p-\alpha)}\right)$.

\end{itemize}
Now, given $p_t\approx\alpha$, we have that $\theta_t^{lamperti}=\theta_t^{kebaier}$ if $\theta_0=\frac{|2\dot{p}_t|}{p_t-\alpha}>0$. Then, which is more restrictive depends on $|\dot{p}_t|$ and $p_t$.\\
\quad\\
Now, given $p_t\approx1-\alpha$, we have that $\theta_t^{lamperti}=\theta_t^{kebaier}$ if $\theta_0=\frac{|2\dot{p}_t|}{1-p_t-\alpha}>0$. Then, which is more restrictive depends on $|\dot{p}_t|$ and $p_t$.\\
\quad\\
\alert{We can see that, we can have $\theta_t^{lamperti}>\theta_t^{kebaier}$ or $\theta_t^{lamperti}<\theta_t^{kebaier}$, depending on the values of $p_t$ and $\dot{p}_t$.}
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Particular questions:}

\begin{itemize}

\item In slide ({\color{blue}\ref{Q1}}), we can see that the Lamperti transform $\psi(v,t)$ has undefined partial derivatives when $x=0$, or $x=1$. This is a consequence of the singularities of $\frac{1}{\sigma(v,t)}$ when $x=0$, or $x=1$. \alert{What can we say about the SDE of $Z_t=\psi(V_t,t)$ in the sense of existence and unicity? Can we use It\^o's lemma considering that the singularities are in the boundary of the domain?}
\item In slide ({\color{blue}\ref{Q2}}), the limits for the drift when $Z_t$ touch the boundaries of its domain depend on $\alpha$. Then, the condition for $Z_t$ to stay always in $\Big[\frac{-\pi}{\sqrt{2\alpha\theta_0}},0\Big]$ also depends on $\alpha$. \alert{This is not intuitive because the condition for $X_t$ to be in $[0,1]$, and there is a bijective mapping between $X_t$ and $Z_t$, so they both should require the same condition.}

\end{itemize}

\end{frame}

\end{document}

### 2020-03-26 Reports/20200308 - Initial Guess/20200308 - Initial Guess.tex
Added MATLAB files. Removed Python files. Added all extra PDFs with reports

\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{commath}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{siunitx}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}
\DeclareMathOperator{\sign}{sign}

\title{Initial Guess}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\begin{frame}
\titlepage
{\tiny Note: We compute the following results using \textbf{errorVsForecast.m} and \textbf{plot\_epsilon.m}.}
\end{frame}

%\setbeamercolor{background canvas}{bg=white!10}
%\begin{frame}\frametitle{Discrete approximation}
%
%We consider the transition $\Delta V_i=V_{i+1}-V_i$ with $\Delta t=t_{i+1}-t_i$, and we approximate the SDE by its Euler–Maruyama scheme for $t\in\left\{t_i,t_{i+1}\right\}$:
%\begin{equation*}
%\begin{cases}
%{\color{blue}V(t_{i+1})}&={\color{blue}V(t_i)-\theta_{t_i}V(t_i)\Delta t}+\sqrt{2\theta_0\alpha(V(t_i)+p_i)(1-V(t_i)-p_i)\Delta t}\Delta W\\
%V(t_i)&=V_i.
%\end{cases}
%\end{equation*}
%Then, ${\color{blue}V_{i+1}-V_{i}(1-\theta_{t_i}\Delta	t)}$ is a random variable with Gaussian distribution, zero mean and variance
%\begin{equation*}
%\sigma^2_i=2\theta_0\alpha(V_i+p_i)(1-V_i-p_i)\Delta t.
%\end{equation*}
%The approximation becomes better as $\Delta t$ becomes smaller.
%\end{frame}
%
%
%\setbeamercolor{background canvas}{bg=white!10}
%\begin{frame}\frametitle{Discrete approximation}
%
%Now, we consider a total of $n$ transitions $\{\Delta V_i\}_{i=1}^n$ with the corresponding forecasts $\{p_i\}_{i=1}^n$. Then, we can approximate the variance using means:
%\begin{equation*}
%\frac{1}{n}\sum_{i=1}^n\left(V_{i+1}-V_i(1-\theta_{t_i}\Delta t)\right)^2\approx\frac{1}{n}\sum_{i=1}^n\left[2\theta_0\alpha(V_i+p_i)(1-V_i-p_i)\Delta t\right],
%\end{equation*}
%from where we can deduce
%\begin{equation}
%\frac{\sum_{i=1}^n\left(V_{i+1}-V_i(1-\theta_{t_i}\Delta t)\right)^2}{2\Delta t\sum_{i=1}^n(V_i+p_i)(1-V_i-p_i)}\approx\theta_0\alpha.
%\label{Eq-1}
%\end{equation}
%
%\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Boundedness of $\theta_t$ (we define $\theta_t^\epsilon$)}\label{theta_t}
To guarantee an unique solution for the process $X_t$, we need boundedness in $\theta_t$ for $t\in[0,T]$. For our definition
\begin{equation}
\theta_t=\max\left(\theta_0,\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}\right),
\label{Eq-6}
\end{equation}
we do not have a bound for $\theta_t$ if $p_t\to0^+$ or $p_t\to1^-$.
However, if we ensure that $p_t\in[\epsilon,1-\epsilon]$ for some $0<\epsilon<\frac{1}{2}$ and all $t\in[0,T]$, then $\theta_t<M(\epsilon)<\infty$ for all $t\in[0,T]$.\\
So, we define the corrected forecast
\begin{equation}
p_t^\epsilon=\begin{cases}
\epsilon\quad&\text{if}\quad p_t<\epsilon\\
p_t\quad&\text{if}\quad\epsilon\leq p_t<1-\epsilon\\
1-\epsilon\quad&\text{if}\quad p_t\geq1-\epsilon,
\end{cases}
\label{Eq-5}
\end{equation}
and the corrected (and bounded) drift coefficient
\begin{equation}
\theta_t^\epsilon=\max\left(\theta_0,\frac{\alpha\theta_0+2|\dot{p}_t^\epsilon|}{2\min(1-p_t^\epsilon,p_t^\epsilon)}\right).
\label{Eq-11}
\end{equation}

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Boundedness of $\theta_t$ (we define $\theta_t^\epsilon$)}

Using our new definition $\theta_t^\epsilon$ in the drift of our SDE:
\begin{itemize}

\item We guarantee existence and uniqueness of the solution, and that $X_t\in]0,1[$ for all $t\in[0,1]$.
\item As $X_t\in]0,1[$, the Lamperti transform is well defined for all $t\in[0,T]$ and we can use It\^o's lemma to compute the SDE for the transformed process.

\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Least square minimization (LSM)}\label{S1}
{\small
\begin{columns}[c]

\column{.6\textwidth}
We consider the transition $\Delta V_i=V_{i+1}-V_i$ with $\Delta t=t_{i+1}-t_i$. $(V_{i+1}|V_i)$ is a random variable which conditional mean can be approximated by the solution of the system
\begin{equation*}
\begin{cases}
\dif \E\left[V\right]&=-\theta_t^\epsilon\E\left[V\right]\dif t\\
\E\left[V(t_i)\right]&=V_i,
\end{cases}
\end{equation*}
evaluated in $t_{i+1}$ (i.e., $\E\left[V(t_{i+1})\right]$). Then, the random variable $(V_{i+1}-\E\left[V(t_{i+1})\right])$ has approximately zero mean.

\column{.3\textwidth}
\includegraphics[width=0.7\columnwidth]{1.jpg}

\end{columns}}
\quad\\
\quad\\
If we assume that $\theta_t^\epsilon=\alert{c}\in\R^+$ for all $t\in[t_i,t_{i+1}]$, then $\E\left[V(t_{i+1})\right]=V_ie^{-\alert{c}\Delta t}$. If we have a total of $n$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
\begin{equation}
\alert{c}^*\approx\arg\min_{\alert{c}\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-\E\left[V(t_{i+1})\right]\right)^2\right]=\arg\min_{\alert{c}\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-V_ie^{-\alert{c}\Delta t}\right)^2\right].
\label{Eq-1}
\end{equation}

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Least square minimization (we are assuming $\theta_t^\epsilon=\alert{c}\in\R^+$)}

We take the first order approximation w.r.t. $\alert{c}$
\begin{equation*}
e^{-\alert{c}\Delta t}=1-\alert{c}\Delta t+\mathcal{O}\left((\alert{c}\Delta t)^2\right),
\end{equation*}
and introduce it in equation ({\color{blue}\ref{Eq-1}}). We get
\begin{equation}
\alert{c}^*\approx\arg\min_{\alert{c}\geq0}\underbrace{\left[\sum_{i=1}^n\left(V_{i+1}-V_i(1-\alert{c}\Delta t)\right)^2\right]}_{:=f(\alert{c})}.
\label{Eq-3}
\end{equation}
As $f(\alert{c})$ is convex in $\alert{c}$, solving ({\color{blue}\ref{Eq-3}}) (finding $\alert{c}^*$) is equivalent to solving
\begin{equation}
\frac{\partial f}{\partial\alert{c}}(\alert{c}^{**})=0,
\label{Eq-9}
\end{equation}
and choosing $\alert{c}^*=\max\{0,\alert{c}^{**}\}$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Least square minimization (we are assuming $\theta_t^\epsilon=\alert{c}\in\R^+$)}\label{QMM}

\begin{equation*}
\begin{split}
\frac{\partial f}{\partial\alert{c}}&=\sum_{i=1}^n2(-V_i)(-\Delta t)(V_{i+1}-V_i(1-\theta_0\Delta t))\\
&=\sum_{i=1}^n2V_i\Delta t(V_{i+1}-V_i(1-\alert{c}\Delta t))\\
&=\sum_{i=1}^n2V_{i+1}V_i\Delta t-2V_i^2\Delta t+2V_i^2\Delta t^2\alert{c}.
\end{split}
\end{equation*}
Then, $\alert{c}^{**}$ satisfies
\begin{equation}
\alert{c}^{**}\approx\frac{\sum_{i=1}^nV_i(V_i-V_{i+1})}{\Delta t\cdot\sum_{i=1}^n(V_i)^2}.
\label{Eq-4}
\end{equation}
Notice that $\alert{c}^{**}$ has dimension $\mathbf{time}^{-1}$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Quadratic variation}\label{QV}

We approximate the SDE by its E-M scheme. In particular, we approximate the It\^o quadratic variation with the discrete one:
\begin{itemize}

\item It\^o process quadratic variation: $[V]_t=\int_0^t\sigma_s^2\dif s$.
\item Discrete process quadratic variation: $[V]_t=\sum_{0<s\leq t}(\Delta V_s)^2$.

\end{itemize}
\quad\\
\quad\\
Then, considering $\Delta t$ the time between measurements, we approximate:
\begin{equation}
\theta_0^*\alpha^*\approx\frac{\sum_{i=1}^n(\Delta V_i)^2}{2\Delta t\sum_{i=1}^n(V_i+p_i)(1-V_i-p_i)}.
\label{Eq-2}
\end{equation}

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$}

In slide ({\color{blue}\ref{theta_t}}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$. We want to estimate the set of parameters $(\theta_0,\alpha,\epsilon)$, we call to the estimations $(\theta_0^*,\alpha^*,\epsilon^*)$.\\
\quad\\
Recall from slide ({\color{blue}\ref{S1}}) that, to use the LSM estimation, we assume $\theta_t^\epsilon=\alert{c}\in\R^+$. Recall also our definition for $\theta_t^\epsilon$ (equation ({\color{blue}\ref{Eq-11}})):
\begin{equation*}
\theta_t^\epsilon=\max\left(\theta_0,\frac{\alpha\theta_0+2|\dot{p}_t^\epsilon|}{2\min(1-p_t^\epsilon,p_t^\epsilon)}\right).
\end{equation*}
Fixed $\epsilon$, we call $\mathcal{V}=\{\Delta V_i^\epsilon\}_{i=1}^n$ to the set of $n$ error transitions where for each measurement $X_i$, we have that $V_i=X_i-p_i^\epsilon$. $\mathcal{P}=\{p_i^\epsilon\}_{i=1}^n$ is the corresponding set of forecasts.\\
Now, if we also fix $\theta_0$ and $\alpha$, we can define the set of indexes $\mathbf{I}=\{i\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\theta_0\}$ and $\mathbf{J}=\left\{j\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\frac{\theta_0\alpha}{\epsilon}\right\}$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$}\label{Slide:Defs}

From the definition of $\theta_t^\epsilon$: We have that for $\epsilon<<1$, and $p_t=\epsilon$ or $p_t=1-\epsilon$, the approximation $\theta^\epsilon_t\approx\frac{\theta_0\alpha}{\epsilon}$ holds. Then, for $\epsilon$ small enough, $\mathbf{J}$ can be approximated by $$\mathbf{J}\approx\tilde{\mathbf{J}}=\{j\in\{1,\dots,n\}:p_j^\epsilon\in\{\epsilon,1-\epsilon\}\}.$$
Now, coming back to the definition of $\theta_t^\epsilon$, we have that it is more likely that $\theta_t^\epsilon=\theta_0$ if $p_t^\epsilon\approx\frac{1}{2}$. Then, we can approximate $\mathbf{I}$ by $$\mathbf{I}\approx\tilde{\mathbf{I}}=\left\{i\in\{1,\dots,n\}:p_i\in(\gamma,1-\gamma)\right\},\ \gamma\approx\frac{1}{2},\ \gamma<\frac{1}{2}.$$

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\theta_0^*$}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../../MATLAB_Files/Results/epsilon/theta_0.eps}\quad\quad
\includegraphics[width=0.4\textwidth]{../../MATLAB_Files/Results/epsilon/num_over_eps_t0.eps}
\end{figure}

In slide ({\color{blue}\ref{Slide:Defs}}), we showed that for $\gamma\approx\frac{1}{2}$, the LSM estimation using indetex from $\tilde{\mathbf{I}}$ is an estimator for $\theta_0$. On the left, we can see $\theta_0^*$ as a function of $\gamma$. The choose ${\color{orange}\theta_0^*\approx1.25}$ seems reasonable from the plot.

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\theta_0^*\alpha^*$ and $\alpha^*$}

Recall the quadratic variation estimator ({\color{blue}\ref{Eq-2}}) from slide ({\color{blue}\ref{QV}}). It uses all the transitions $\mathcal{V}$ and estimated the product $\theta_0\alpha$.\\
\quad\\
We get ${\color{orange}\theta_0^*\alpha^*\approx0.10}$, from where we calculate ${\color{orange}\alpha^*\approx0.08}$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\epsilon^*$}

As we have an approximated value for $\theta_0\alpha$, if we can estimate $\frac{\theta_0\alpha}{\epsilon}$, then we can estimate $\epsilon$. In slide ({\color{blue}\ref{Slide:Defs}}), we showed that for $\epsilon<<1$, the LSM estimation using indexes from $\tilde{\mathbf{J}}$ is an estimator for $\frac{\theta_0\alpha}{\epsilon}=:k$.\\
\quad\\
However, which values of $\epsilon$ satisfies $\epsilon<<1$? We choose an initial guess for $\epsilon$ (call it $\epsilon_0$), and iterating we aim to converge to some local minimum. We proceed with the following steps:

\begin{itemize}

\item We sample $\epsilon_0$ from $\mathcal{U}[0.01,0.1]$ and load $\epsilon\gets\epsilon_0$.
\item We create $\tilde{\mathbf{J}}$ and use the LSM estimation to find $k$. If $k<\theta_0^*$, then the assumption $\theta_t^\epsilon=\alert{c}\in\R^+$ is wrong and we reduce the value of $\epsilon$, i.e., $\epsilon\gets\epsilon*0.999$. If $k\geq\theta_0^*$, we load $\epsilon\gets\frac{\theta_0^*\alpha^*}{k}$ (we allow a maximum relative change of 1\%). We repeat this step *100 times*.
\item We repeat steps 1 and 2 *500 times*. After, we plot the results.

\end{itemize}

\end{frame}

%\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\epsilon^*$}

\begin{columns}

\column{.45\textwidth}
We can see that we converge to four different local minimums.

\column{.45\textwidth}
\includegraphics[width=1\textwidth]{../../MATLAB_Files/Results/epsilon/epsilon.eps}
\end{columns}

\end{frame}

%\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\epsilon^*$}

\begin{columns}

\column{.45\textwidth}
This is the value of $k$ over iterations. When $k<\theta^*_0$, we assume that the estimation and repeat the iteration step.

\column{.45\textwidth}
\includegraphics[width=1.1\textwidth]{../../MATLAB_Files/Results/epsilon/theta_t.eps}
\end{columns}

\end{frame}

%\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\epsilon^*$}

\begin{columns}

\column{.45\textwidth}
In this plot, we can see the minimum of the normalized value function ({\color{blue}\ref{Eq-1}}) over $\epsilon$. We normalize it with respect to the number of elements of $\tilde{\mathbf{J}}$.
\begin{itemize}

\item Using fixed $k$: As $k<\theta^*_0$ has not sense, when we get that condition we set $k\gets\theta^*_0$, and evaluate the value function in $k$.
\item Analytical optimal value function.
\item Numerical optimal value function.

\end{itemize}
We can see that all plots almost coincide. We choose ${\color{orange}\epsilon^*\approx0.018}$.

\column{.45\textwidth}
\includegraphics[width=1\textwidth]{../../MATLAB_Files/Results/epsilon/QMM.eps}
\end{columns}

\end{frame}

%\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\epsilon^*$}

\begin{columns}

\column{.45\textwidth}
When we get $k<\theta^*_0$, we set $k\gets\theta_0^*$.

\column{.45\textwidth}
\includegraphics[width=1\textwidth]{../../MATLAB_Files/Results/epsilon/theta_over_eps.eps}
\end{columns}

\end{frame}

%\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\epsilon^*$}

\begin{columns}

\column{.45\textwidth}
Number of elements in $\tilde{\mathbf{J}}$ as a function of $\epsilon$.

\column{.45\textwidth}
\includegraphics[width=1\textwidth]{../../MATLAB_Files/Results/epsilon/num_over_eps.eps}
\end{columns}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Extra: Interesting data processing}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/mean_error.eps}\quad\quad
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/mean_abs_error.eps}
\end{figure}
{\small What we are seeing is the \textbf{mean error} and \textbf{mean absolute error} as a function of the forecast. This is, for each interval with length 0.1 (i.e., [0,0.1), [0.1,0.2), etc.), we average all the errors corresponding to measurement where the forecast was in that intervals, and after we average over the number of elements in each interval. \alert{In some future, we can use this information to construct an even more realistic model.}}

\end{frame}

%\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Extra: Error Vs. Forecast for all training days}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/error_over_forecast.eps}
\end{figure}

\end{frame}

%\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{How do we ensure $\dot{p}^\epsilon_i=0$ in $\tilde{\mathbf{J}}$?}

\begin{columns}

\column{.5\textwidth}

To guarantee that $\dot{p}^\delta_{t_i}=0$, we need that $p_{t_i}=p_{t_{i+1}}$. Then, if we have $n+1$ truncated consecutive forecasts (i.e., $p_{t_i},\dots,p_{t_{i+n}}$), we can use the $n$ transitions $\Delta V_{t_i}$ because $\dot{p}^\delta_{t_{i}}=\dots=\dot{p}^\delta_{t_{i+n-1}}=0$, but $\dot{p}^\delta_{t_{i+n}}\neq0$.

\column{.5\textwidth}
\includegraphics[width=0.9\columnwidth]{2.jpg}

\end{columns}

\end{frame}

\end{document}

### 2020-03-26 MATLAB_Files/batch_with_theta.m

@@ -1,0 +1,9 @@
+function [batch_theta] = batch_with_theta(batch, alpha, theta_0) % 09/02/2020 18:51
+    batch(4,1)   = theta_t(theta_0, alpha, batch(1,1), batch(2,1));
+    batch(4,end) = theta_t(theta_0, alpha, batch(1,end), batch(2,end));
+    for i = 2:2:length(batch(1,:))-1
+        batch(4,i:i+1) = theta_t(theta_0, alpha, batch(1,i), batch(2,i));
+    end
+    batch_theta = batch;
+%     batch_theta = batch(:,1:end-1);
+end

### 2020-03-26 MATLAB_Files/likelihood_optimization.m

@@ -1,0 +1,7 @@
+function [val] = likelihood_optimization(batch, theta0, alpha, dt)
+    % 10/02/2020 11:20
+    disp(['Theta = ',num2str(theta0),', Alpha = ',num2str(alpha)]);
+    batch_complete = batch_with_theta(batch, alpha, theta0);
+    val            = log_LH_evaluation(batch_complete, alpha, dt);
+
+end

### 2020-03-26 MATLAB_Files/moment_2.m

@@ -1,0 +1,18 @@
+function m2 = moment_2(v,th1,th2,p1,p2,alpha,m1,dt,n) % 02/02/2020 18:28
+
+    if th1 == th2
+        theta = @(i) th2;
+        m1    = @(i) v*exp(-th1*dt*(i/n));
+    else
+        theta = @(i) th1 + (th2-th1) * i/n;
+    end
+    p     = @(i) p1  + (p2-p1)   * i/n;
+    m2(1) = v^2;
+    ds    = dt/n;
+    
+    for i = 2:n
+        m2(i) = m2(i-1) + 2*theta(i-1)*ds * (-(1+alpha)*m2(i-1) + ...
+            alpha*m1(i-1)*(1-2*p(i-1)) + alpha*p(i-1)*(1-p(i-1))); 
+    end
+    
+end

### 2020-03-26 MATLAB_Files/new_batch.m

@@ -1,0 +1,19 @@
+function [Table_Training, new_bat] = new_batch(Table_Training, batch_size, N)
+    % 03/02/2020 17:41
+    idx          = randperm(height(Table_Training), batch_size); % Sample indices.
+    idx          = -sort(-idx); % We order the indices from large to small.
+    Forecast     = Table_Training.Forecast;
+    Forecast_Dot = Table_Training.Forecast_Dot;
+    Error        = Table_Training.Error;
+    new_bat      = [];
+        
+    for i = 1:length(idx)
+        Table_Training(idx(i),:) = []; % We remove the row that we sample from.
+        for j = 2:N
+            forecast(2*j-3:2*j-2)     = Forecast(idx(i),j-1:j);
+            forecast_dot(2*j-3:2*j-2) = Forecast_Dot(idx(i),j-1:j);
+            error(2*j-3:2*j-2)        = Error(idx(i),j-1:j);
+        end
+        new_bat = [new_bat, [forecast; forecast_dot; error]];
+    end
+end

### 2020-03-26 MATLAB_Files/pe.m

@@ -1,0 +1,11 @@
+function [pe] = pe(p, eps) % 18/03/2020 09:51
+    for i = 1:length(p)    
+        if p(i) < eps
+                pe(i) = eps;
+            elseif p(i) >= eps && p(i) < 1-eps
+                pe(i) = p(i);
+            elseif p(i) >= 1-eps
+                pe(i) = 1-eps;
+        end
+    end
+end

### 2020-03-26 python_code/Urugauy_data_importer.py

@@ -1,93 +1,0 @@
-#%%
-import os
-import sys
-os.chdir(sys.path[0])
-from data_cleansing import *
-#%%
-
-# %%
-#file paths
-forecast_A='./raw_data/Uruguay/wind/Wind_Data_2018_provider_A.csv'
-forecast_B='./raw_data/Uruguay/wind/Wind_Data_provider_B.csv'
-production_path='./raw_data/Uruguay/wind/anuales_gen_int_2018_10m_aggregated.csv'
-#normalization_path='/Users/alhaddwt/Google Drive/GitLab/wind-power/raw_data/France/normalization_2019.txt'
-
-
-#import files
-d = pd.read_csv(production_path, delimiter= ',', header=2,  dtype=str)
-#n = pd.read_csv(normalization_path, delimiter= '\s+', header=0)
-f_A = pd.read_csv(forecast_A, delimiter= ',',  header=0, dtype={'Date': str})
-f_B = pd.read_csv(forecast_B, delimiter= ',', header=0, dtype={'Date': str})
-
-#empty containers
-data=np.zeros((3,d.shape[0]))
-forecast_A=np.zeros((2,f_A.shape[0]))
-forecast_B=np.zeros((2,f_B.shape[0]))
-production=np.zeros((2,d.shape[0]))
-# %%
-
-# %%
-#convert string date and time to timestamp in seconds, strings to numerical values
-#forecast A
-forecast_A[0,:]=get_unixtime(pd.to_datetime(\
-f_A['Unnamed: 0'] + ' ' + f_A['Unnamed: 1'], dayfirst=True ).values)
-forecast_A[1,:]=pd.to_numeric(f_A['Forecast']).values
-
-#forecast B
-forecast_B[0,:]=get_unixtime(pd.to_datetime(\
-f_B['Unnamed: 0'] + ' ' + f_B['Unnamed: 1'], dayfirst=True ).values)
-forecast_B[1,:]=pd.to_numeric(f_B['Forecast']).values
-
-#production
-production[0,:]=get_unixtime(pd.to_datetime(\
-d['Fecha'], dayfirst=False ).values)
-production[1,:]=pd.to_numeric(d['Eólica']).values
-# %%
-
-# %%
-# split forecasts into path
-forecast_A_split=split_data(forecast_A,72)
-forecast_B_split=split_data(forecast_B,72)
-
-# match data to forecast
-observ_path_A=np.stack(match_data_to_forecast(\
[…]

### 2020-03-26 python_code/config/loadconfig.py

@@ -1,6 +1,0 @@
-import json
-import os
-
-class Test(object):
-    def __init__(self, data):
-	    self.__dict__ = json.load(data)

### 2020-03-26 python_code/depreciated_code/Iso_72_2.py

@@ -1,187 +1,0 @@
-# %%
-from multi_path_base import *
-from scipy import interpolate
-forecast_with_data=np.load('forecast_with_data.npy')
-# %%
-#cleaning data
-interpolation_points=73*2
-forecast_data_inter= np.zeros((3,1193, interpolation_points ))
-x = np.arange(1,72+1,1)
-xnew = np.linspace(0,72,interpolation_points)
-counter=0
-i=0;j=0
-while j< forecast_with_data.shape[0]: #fix redundant indicies
-
-    y1=forecast_with_data[j,:,1]
-    y2=forecast_with_data[j,:,2]
-    inter_1=interpolate.interp1d(x, y1, fill_value='extrapolate')
-    inter_2=interpolate.interp1d(x, y2, fill_value='extrapolate')
-    p=inter_1(xnew)
-    d=inter_2(xnew)
-
-    if  sum(1*np.isnan(p))==0 and \
-        sum(1*np.isnan(d))==0 and \
-        np.max(p)<=1 and \
-        np.min(p)>=0 and \
-        np.max(d)<=1 and \
-        np.min(d)>=0:
-
-        forecast_data_inter[0,i,:]= p
-        forecast_data_inter[1,i,:]= d
-        forecast_data_inter[2,i,0]= forecast_with_data[j,0,0]
-        i+=1
-    j+=1
-n_paths=i
-print('paths left', i)
-# %%
-N=forecast_data_inter.shape[2]
-M=forecast_data_inter.shape[1]
-#M=100
-dt=1
-dN=1/interpolation_points
-
-#forecast_data_inter[0,:,:] #forecast
-
-disct_temp = disct(N,dt,M)
-p=forecast_data_inter[0,:,:]
-V= forecast_data_inter[1,:,:] -forecast_data_inter[0,:,:]
-
-this_model=model_modified_drift(disct_temp,V, forecast= p)
-# %%
-
-x = np.linspace(1, 30, 30)
-y = np.linspace(0.1, 1, 30)
-
-X, Y = np.meshgrid(x, y)
-
-Z=np.zeros((len(y), len(x)))
-for i in range(0,len(x)):
[…]

### 2020-03-26 python_code/depreciated_code/eigenvalues_hessian_FD_trials.py

@@ -1,163 +1,0 @@
-from multi_path_base import *
-from matplotlib.patches import Ellipse
-import matplotlib as mpl
-forecast_with_data=np.load('forecast_with_data.npy')
-
-# %%
-#cleaning data
-interpolation_points=73
-forecast_data_inter= np.zeros((3,1193, interpolation_points ))
-x = np.arange(1,72+1,1)
-xnew = np.linspace(0,72,interpolation_points)
-counter=0
-i=0;j=0
-while j< forecast_with_data.shape[0]: #fix redundant indicies
-
-    y1=forecast_with_data[j,:,1]
-    y2=forecast_with_data[j,:,2]
-    inter_1=interpolate.interp1d(x, y1, fill_value='extrapolate')
-    inter_2=interpolate.interp1d(x, y2, fill_value='extrapolate')
-    p=inter_1(xnew)
-    d=inter_2(xnew)
-
-    if  sum(1*np.isnan(p))==0 and \
-        sum(1*np.isnan(d))==0 and \
-        np.max(p)<=1 and \
-        np.min(p)>=0 and \
-        np.max(d)<=1 and \
-        np.min(d)>=0:
-
-        forecast_data_inter[0,i,:]= p
-        forecast_data_inter[1,i,:]= d
-        forecast_data_inter[2,i,0]= forecast_with_data[j,0,0]
-        i+=1
-    j+=1
-n_paths=i
-print('paths left', i)
-
-N=forecast_data_inter.shape[2]
-
-dt=1
-dN=1/interpolation_points
-
-eig_theta=[]
-eig_alpha=[]
-M= 100
-h=1e-2
-for M in [100,1000]:
-    disct_temp = disct(N,dt,M)
-    p=forecast_data_inter[0,:,:]
-    V= forecast_data_inter[1,:,:] -forecast_data_inter[0,:,:]
-    this_model=model_modified_drift(disct_temp,V, forecast= p)
-    h=1e-3
-    x=8
-    y=1
-
-    Z_xx=(this_model.likelihood(param=np.array((x-h,y)))- 2*this_model.likelihood(param=np.array((x,y))) + this_model.likelihood(param=np.array((x+h,y))))/h**2
[…]

### 2020-03-26 python_code/depreciated_code/fit_SDE_gauss_approx_NDLM.py

@@ -1,67 +1,0 @@
-import os
-os.chdir('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code')
-from Base_plus import *
-forecast_data_in=np.load('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code/data/cleansed/URG_forecast_data_A_2018.npy')
-#forecast_data_inter=data_check_interpolate(forecast_with_data=forecast_with_data)
-now = dtM.datetime.now();
-current_time=now.strftime("%y-%m-%d-%H-%M-%S")
-script_name='fit_SDE'
-current_data_dir='data/'+ script_name +current_time
-os.mkdir(current_data_dir)
-
-forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
-print(current_data_dir)
-
-
-
-#check no nans
-np.sum( np.isnan(forecast_data_inter.flatten()))
-np.max(forecast_data_inter[1:,:,:])<=1
-np.min(forecast_data_inter[1:,:,:])>=0
-
-N=forecast_data_inter.shape[2]
-M=forecast_data_inter.shape[1]-240 #to be changed in generalization
-dt=1
-#forecast_data_inter[0,:,:] #forecast
-
-N
-M
-dt
-
-disct_temp = disct(N,dt,M)
-p=forecast_data_inter[2,:-240,:]
-V= forecast_data_inter[2,:-240,:]-forecast_data_inter[1,:-240,:]
-X=forecast_data_inter[1,:-240,:]
-#Z = np.arcsin(2*X - 1)
-
-#answer 9.06 , 0.473
-this_model=model_modified_drift(disct_temp,V, forecast= p)
-intial_point= np.array((1,0.8))
-optim=this_model.optimize(inference="lamperti_likelihood_SDE_approx" ,method="Nelder-Mead",param_initial=intial_point)
-
-
-optim
-
-
-file_object  = open(current_data_dir+'/results.out', 'w')
-note='Fit for ' + str(M) +' paths' + ' of ' + str(N) +' hours. Initialized at '\
-    + str(intial_point)
-file_object.write( note +'\n'+str(optim.x) +'\n' +optim.message[0])
-file_object.close()
-
-optim
-
-
-# co=np.zeros((forecast_data_inter.shape[1]))
-# for sel in range(0,forecast_data_inter.shape[1]):
[…]

### 2020-03-26 python_code/depreciated_code/fit_SDE_new_Beta.py

@@ -1,71 +1,0 @@
-import os
-os.chdir('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code')
-from Base import *
-forecast_data_in=np.load('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code/data/cleansed/URG_forecast_data_A_2018.npy')
-#forecast_data_inter=data_check_interpolate(forecast_with_data=forecast_with_data)
-now = dtM.datetime.now();
-current_time=now.strftime("%y-%m-%d-%H-%M-%S")
-script_name='fit_SDE'
-current_data_dir='data/'+ script_name +current_time
-os.mkdir(current_data_dir)
-
-forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
-print(current_data_dir)
-
-
-
-#check no nans
-np.sum( np.isnan(forecast_data_inter.flatten()))
-np.max(forecast_data_inter[1:,:,:])<=1
-np.min(forecast_data_inter[1:,:,:])>=0
-
-N=forecast_data_inter.shape[2]
-M=forecast_data_inter.shape[1]-240 #to be changed in generalization
-dt=1
-#forecast_data_inter[0,:,:] #forecast
-
-N
-M
-dt
-
-disct_temp = disct(N,dt,M)
-p=forecast_data_inter[2,:-240,:]
-V= forecast_data_inter[2,:-240,:]-forecast_data_inter[1,:-240,:]
-X=forecast_data_inter[1,:-240,:]
-#Z = np.arcsin(2*X - 1)
-
-#answer 9.06 , 0.473
-this_model=model_modified_drift(disct_temp,V, forecast= p)
-intial_point= np.array((11,0.15))
-optim=this_model.optimize(intial_point)
-
-
-optim
-
-
-file_object  = open(current_data_dir+'/results.out', 'w')
-note='Fit for ' + str(M) +' paths' + ' of ' + str(N) +' hours. Initialized at '\
-    + str(intial_point)
-file_object.write( note +'\n'+str(optim.x) +'\n' +optim.message[0])
-file_object.close()
-
-optim
-
-
-# co=np.zeros((forecast_data_inter.shape[1]))
-# for sel in range(0,forecast_data_inter.shape[1]):
-#     LHS=np.sum(np.diff(forecast_data_inter[1,sel,:])**2)
[…]

### 2020-03-26 python_code/depreciated_code/fit_model_old.py

@@ -1,128 +1,0 @@
-import os
-import sys
-os.chdir(sys.path[0])
-from Base_plus import *
-import config.loadconfig
-import argparse
-#import numdifftools as nd
-
-parser = argparse.ArgumentParser(description='Likelihood Evaluator v1.0')
-parser.add_argument('-filename', help=' Config file name or path')
-parser.add_argument('--version', action='version', version='Likelihood Evaluator v1.0')
-args = parser.parse_args()
-
-print( ' loading configuration ')
-#args.filename
-config_file= open(args.filename)  #config/beta_config.JSON
-
-
-setup=config.loadconfig.Test(config_file)
-
-# os.chdir(setup.dir_path)
-
-# orig_stdout = sys.stdout
-# f = open( setup.logs_file_name, 'w')
-# sys.stdout = f
-
-# def customwarn(message, category, filename, lineno, file=None, line=None):
-#     sys.stdout.write(warnings.formatwarning(message, category, filename, lineno))
-#
-# warnings.showwarning = customwarn
-
-warnings.simplefilter("once")
-
-from Base_plus import *
-forecast_data_in=np.load(setup.data_path)
-#forecast_data_inter=data_check_interpolate(forecast_with_data=forecast_with_data)
-now = dtM.datetime.now();
-current_time=now.strftime("%y-%m-%d-%H-%M-%S")
-script_name='fit_SDE'
-current_data_dir= script_name +current_time
-os.mkdir(current_data_dir)
-
-forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
-print('Data output will be save in ',current_data_dir)
-
-
-# #check no nans
-# np.sum( np.isnan(forecast_data_inter.flatten()))
-# np.max(forecast_data_inter[1:,:,:])<=1
-# np.min(forecast_data_inter[1:,:,:])>=0
-
-N=forecast_data_inter.shape[2]
-M= setup.num_paths  #forecast_data_inter.shape[1]-973 #to be changed in generalization
-dt=1
-
-disct_temp = disct(N,dt,M)
-p=forecast_data_inter[2,:-973,:]
-V= forecast_data_inter[2,:-973,:]-forecast_data_inter[1,:-973,:]
-X=forecast_data_inter[1,:-973,:]
-
-
-if setup.likelihood=='lamperti_likelihood_SDE_approx':
-    V = np.arcsin(2*X - 1)
-    print(' Data has been Lamperti transformed ')
-
[…]

### 2020-03-26 python_code/depreciated_code/likelihood_explorer_new_Beta.py

@@ -1,40 +1,0 @@
-
-
-import os
-os.chdir('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code')
-from Base import *
-#from multi_path_base import model_modified_drift
-forecast_data_in=np.load('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code/data/cleansed/URG_forecast_data_A_2018.npy')
-now = dtM.datetime.now();
-current_time=now.strftime("%y-%m-%d-%H-%M-%S")
-script_name='likelihood_explorer'
-current_plotting_dir='data/'+ script_name+'_' +current_time
-os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
-
-forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
-
-N=forecast_data_inter.shape[2];N
-M=forecast_data_inter.shape[1]-500;M
-dt=1
-dN=1/N;dN
-
-disct_temp = disct(N,dt,M)
-p=forecast_data_inter[2,:-500,:]  #240
-V= forecast_data_inter[2,:-500,:] -forecast_data_inter[1,:-500,:]
-
-X=forecast_data_inter[1,:-500,:]
-
-Z = np.arcsin(2*X - 1)
-
-#now for V
-this_model=model_modified_drift(disct_temp,V, forecast= p) #change it
-
-theta_array=np.linspace(6, 15, 30) #np.linspace(1, 30, 30)
-alpha_array=np.linspace(0.07, 1.5, 30) #np.linspace(0.1, 3, 30)
-
-np.save(current_plotting_dir+'/num_paths', M)
-np.save(current_plotting_dir+'/interpolation_points', N)
-likelihood_evaluater(theta_array=theta_array,\
-    alpha_array=alpha_array,\
-    this_model=this_model,path_dir=current_plotting_dir )
-print(current_plotting_dir)

### 2020-03-26 python_code/depreciated_code/likelihood_explorer_new_importer.py

@@ -1,62 +1,0 @@
-import os
-os.chdir('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code')
-from Base_plus import *
-
-orig_stdout = sys.stdout
-f = open('approx_lamperti_out.txt', 'w')
-sys.stdout = f
-
-def customwarn(message, category, filename, lineno, file=None, line=None):
-    sys.stdout.write(warnings.formatwarning(message, category, filename, lineno))
-
-warnings.showwarning = customwarn
-
-warnings.simplefilter("once")
-
-warnings.warn("test warning")
-
-#from multi_path_base import model_modified_drift
-forecast_data_in=np.load('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code/data/cleansed/URG_forecast_data_A_2018.npy')
-now = dtM.datetime.now();
-current_time=now.strftime("%y-%m-%d-%H-%M-%S")
-script_name='likelihood_explorer'
-current_plotting_dir='data/'+ script_name+'_' +current_time
-os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
-
-forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
-
-N=forecast_data_inter.shape[2];N
-M=forecast_data_inter.shape[1]-1070;M
-dt=1
-dN=1/N;dN
-
-disct_temp = disct(N,dt,M)
-p=forecast_data_inter[2,:-973,:]  #240
-V=forecast_data_inter[2,:-973,:] -forecast_data_inter[1,:-973,:]
-
-#plt.plot(p[105])
-#plt.plot(forecast_data_inter[1,105,:])
-#plt.plot(V[105,:])
-#X=forecast_data_inter[1,:-500,:]
-
-Z = np.arcsin(2*(forecast_data_inter[1,:-973,:]) - 1)
-
-
-#now for V
-this_model=model_modified_drift(disct_temp,Z, forecast= p) #change it
-
-
-
-
-theta_array=np.linspace(0.01, 25, 10)
-alpha_array=np.linspace(0.01, 2, 10)
-
-np.save(current_plotting_dir+'/num_paths', M)
-np.save(current_plotting_dir+'/interpolation_points', N)
-likelihood_evaluater(theta_array=theta_array,\
-    alpha_array=alpha_array,\
[…]

### 2020-03-26 python_code/depreciated_code/non_basin_alot_inter.py

@@ -1,50 +1,0 @@
-from multi_path_base import *
-forecast_with_data=np.load('forecast_with_data.npy')
-
-###############################
-#cleaning data
-interpolation_points=73*3
-forecast_data_inter= np.zeros((3,forecast_with_data.shape[0], interpolation_points ))
-x = np.arange(1,72+1,1)
-xnew = np.linspace(0,72,interpolation_points)
-counter=0
-i=0;j=0
-while j< forecast_with_data.shape[0]: #fix redundant indicies
-
-    y1=forecast_with_data[j,:,1]
-    y2=forecast_with_data[j,:,2]
-    inter_1=interpolate.interp1d(x, y1, fill_value='extrapolate')
-    inter_2=interpolate.interp1d(x, y2, fill_value='extrapolate')
-    p=inter_1(xnew)
-    d=inter_2(xnew)
-
-    if  sum(1*np.isnan(p))==0 and \
-        sum(1*np.isnan(d))==0 and \
-        np.max(p)<=1 and \
-        np.min(p)>=0 and \
-        np.max(d)<=1 and \
-        np.min(d)>=0:
-
-        forecast_data_inter[0,i,:]= p
-        forecast_data_inter[1,i,:]= d
-        forecast_data_inter[2,i,0]= forecast_with_data[j,0,0]
-        i+=1
-    j+=1
-n_paths=i
-print('paths left', i)
-################################
-N=forecast_data_inter.shape[2]
-#M=forecast_data_inter.shape[1]
-M= n_paths
-dt=1
-
-#forecast_data_inter[0,:,:] #forecast
-
-disct_temp = disct(N,dt,M)
-p=forecast_data_inter[0,:M,:]
-V= forecast_data_inter[1,:M,:]-forecast_data_inter[0,:M,:]
-#answer 8.57 , 0.29 
-this_model=model_modified_drift(disct_temp,V, forecast= p)
-##################################
-optim=this_model.optimize(np.array((9.5,0.5)))
-optim

### 2020-03-26 python_code/french_data_importer.py

@@ -1,68 +1,0 @@
-#%%
-import os
-os.chdir('/Users/alhaddwt/Google Drive/GitLab/wind-power/python_code')
-from Base import *
-import pandas as pd
-import datetime as dt
-#%%
-
-#function to convert np.datetime64 to unix time, regardless of the units
-def get_unixtime(dt64):
-    return dt64.astype('datetime64[s]').astype('int')
-
-# import data and create empty containers
-# %%
-forecast_path='/Users/alhaddwt/Google Drive/GitLab/wind-power/raw_data/France/Predictions/forecast_2018.txt'
-production_path='/Users/alhaddwt/Google Drive/GitLab/wind-power/raw_data/France/Aggregated_Production/production_2018.xls'
-normalization_path='/Users/alhaddwt/Google Drive/GitLab/wind-power/raw_data/France/normalization_2019.txt'
-
-d = pd.read_excel(production_path, delimiter= '\s+', header=None,  dtype=str)
-n = pd.read_csv(normalization_path, delimiter= '\s+', header=0)
-f = pd.read_csv(forecast_path, delimiter= '\s+', dtype={'Date': str})
-
-data=np.zeros((3,f.shape[0]))
-forecast=np.zeros((2,f.shape[0]))
-production=np.zeros((2,d.shape[0]))
-
-# %%
-
-#prepare forecast, parse it and clean it
-# %%
-forecast[0,:]=get_unixtime(pd.to_datetime(f['Date']+' ' +f['Heure'] ).values)
-forecast[1,:]=f['PrÈvision'].values
-# %%
-
-#prepare real production data, parse it and clean it
-# %%
-D=d.values
-production_list=[]
-production_time_list=[]
-i=0
-while i < d.shape[0]:
-    if D[i,0].find('DonnÈes de rÈalisation du ')==0:
-        date_str=D[i,0][26:]
-        while D[i+2,0] !='nan' and i < d.shape[0]:
-            time_stamp=pd.to_datetime(date_str + ' ' + D[i+2,0][:5]).timestamp()
-            #reverse_time_stamp=np.datetime64(int(datetime_object),'s')
-            #production[0,i]=time_stamp
-            if D[i+2,11]=='*':
-                pass #production[1,i]=float('nan')
-            else:
-                production_list.append(D[i+2,11])
-                production_time_list.append(int(time_stamp))
-                #production[1,i]=D[i+2,11]
-            i+=1
-            if i+2 >= d.shape[0]: break;
-    i+=1
[…]

### 2020-03-26 python_code/generate_bands_temp_2.py

@@ -1,30 +1,0 @@
-import os
-os.chdir('./python_code')
-from Base_plus import *
-forecast_with_data=np.load('data/forecast_with_data.npy')
-data=data_check_interpolate(forecast_with_data=forecast_with_data)
-now = dtM.datetime.now();
-current_time=now.strftime("%y-%m-%d-%H-%M-%S")
-script_name='gen_CI_'
-current_plotting_dir='plots/'+ script_name +current_time
-os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
-
-print(current_plotting_dir)
-
-current_list=list(range(0, data.shape[1])) #=list(range(0, data.shape[1])) #full_set
-disct_in= disct(N=7, dt=1, M=1000) #M is number of paths wanted in ensamble
-real_in=real(2.02,1.25) # SDE parameters to be generated from
-
-plt.plot(data[1,1,:])
-plt.plot(data[0,1,:])
-
-
-data[2,2,:]
-
-
-
-empirical_Confidence_Interval_plots(forecast_data_inter=data,  real_in=real_in,\
-            disct_in=disct_in, list_forecast_number=current_list,\
-            dir_path=current_plotting_dir)
-
-print(current_plotting_dir)

### 2020-03-26 python_code/likelihood_ISO_plotter.py

@@ -1,209 +1,0 @@
-import os
-os.chdir('./python_code')
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.cm as cm
-from matplotlib.patches import Ellipse
-import matplotlib as mpl
-from numpy import linalg as LA
-import math
-
-def Ellipse (H_opt, mean=[ 8 ,  1]):
-    eig_values_opt, eig_vect_opt=LA.eig(H_opt)
-    a_opt=1/np.sqrt(np.max(np.abs(eig_values_opt)))  #radius on the x-axis
-    b_opt=1/np.sqrt( np.min(np.abs(eig_values_opt))) #radius on the y-axis
-    width = a_opt**2
-    height = b_opt**2
-    angle =math.acos(sum(eig_vect_opt[1]*np.array((0,1))));angle
-    return(width,height,angle, eig_vect_opt )
-
-#19-07-26-15-30-16 Beta
-#model of lamperti linearizing fit_SDE 19-09-04-15-54-23
-#model using approx lamperti 19-09-04-16-11-26
-#model of Beta
-base_path=current_plotting_dir='data/'
-chosen_folder='likelihood_explorer_'+ '19-09-11-21-32-05'
-#beta 19-09-08-13-58-19
-
-data_path=base_path+chosen_folder
-
-#plotting chosen_folder
-
-os.makedirs('plots/'+chosen_folder, exist_ok=True)
-
-Z=np.load(data_path+'/value.npy')
-X=np.load(data_path+'/theta.npy')
-Y=np.load(data_path+'/alpha.npy')
-Z_grad_xx=np.load(data_path+'/grad_xx.npy')
-Z_grad_yy=np.load(data_path+'/grad_yy.npy')
-Z_grad_xy=np.load(data_path+'/grad_xy.npy')
-Z_grad_yx=np.load(data_path+'/grad_yx.npy')
-
-M=np.load(data_path+'/num_paths.npy')
-N=np.load(data_path+'/interpolation_points.npy')
-
-dN=1/N
-
-from matplotlib import ticker, cm
-%matplotlib qt
-fig = plt.figure(1)
-
-# max_Z = np.max(np.abs(Z));
[…]

### 2020-03-26 python_code/path_simulator_copy.py

@@ -1,55 +1,0 @@
-import os
-import sys
-os.chdir(sys.path[0])
-from Base_plus import *
-
-import config.loadconfig
-
-warnings.filterwarnings('error', '.*invalid value encountered.*',)
-
-parser = argparse.ArgumentParser(description='Likelihood Evaluator v1.0')
-parser.add_argument('-filename', help=' Config file name or path')
-parser.add_argument('--version', action='version', version='Likelihood Evaluator v1.0')
-args = parser.parse_args()
-
-print( ' loading configuration ')
-# args.filename
-config_file= open(args.filename)  #config/beta_config.JSON
-
-setup=config.loadconfig.Test(config_file)
-
-
-forecast_data_in=np.load(setup.data_path)
-
-forecast_data_in.shape
-
-data=np.swapaxes(forecast_data_in, 0,1)
-
-data_unique=np.unique(data[:,:,:], axis=1  )
-
-
-now = dtM.datetime.now();
-current_time=now.strftime("%y-%m-%d-%H-%M-%S")
-script_name='sample_paths_'
-current_plotting_dir='plots/'+ script_name +current_time
-# os.mkdir(current_plotting_dir) # make a time stamped folder to contain all plots
-os.makedirs(current_plotting_dir,exist_ok=True)
-
-print(current_plotting_dir)
-
-current_list= list(range(0, setup.num_paths)) #=list(range(0, data.shape[1])) #full_set
-M=1 #number of simulated paths in each plot
-N=427
-disct_in= disct(N=N, dt=1, M=M) #M is number of paths wanted in ensamble
-real_in=real(1.36, 0.020) # SDE parameters to be generated from
-
-
-path_simulator(forecast_data_inter=data_unique,hours=59,\
-    real_in=real_in, disct_in=disct_in,list_forecast_number=current_list,\
-    dir_path=current_plotting_dir)
-    # Notice: We plot from 0 transitions to "hours" transitions. E,g,. is "hours" = 100, we plot from 0 to 100
-    # where this 100 has units transitions.
-
-# path_simulator(forecast_data_inter=data,hours=427,\
-#     real_in=real_in, disct_in=disct_in,list_forecast_number=current_list,\
-#     dir_path=current_plotting_dir)

### 2020-03-26 python_code/skew_test_quantiles_10m.py

@@ -1,439 +1,0 @@
-# %%
-import os
-import sys
-os.chdir(sys.path[0])
-from Base_plus import *
-from scipy.stats import moment,skew,probplot, norm,shapiro, normaltest
-
-forecast_data_in=np.load('./data/cleansed/URG_forecast_data_A_2018.npy')
-#forecast_data_inter=data_check_interpolate(forecast_with_data=forecast_with_data)
-forecast_data_inter=np.swapaxes(forecast_data_in, 0,1)
-
-def take_center(data,fctr):
-    upper_limit=np.mean(data)+ fctr*np.std(data)
-    lower_limit=np.mean(data)- fctr*np.std(data)
-    return(data[(data>lower_limit) & (data<upper_limit) ])
-
-def plot_QQ(list_data,labels, colors=['r','k','y', 'm', 'g']):
-    plt.clf()
-    fig = plt.figure()
-    err=[]
-    i=0
-    for i in range(0,len(list_data)):
-        x,y=probplot(list_data[i].flatten(), dist="norm")[0]
-        plt.plot(x,y, 'o'+ colors[i], label=labels[i] )
-        plt.plot(np.unique(x), np.poly1d(np.polyfit(x, y, 1))(np.unique(x)), colors[i])
-        plt.xlabel('Theoretical quantiles', fontsize=18)
-        plt.ylabel('Ordered Values', fontsize=18)
-        plt.legend()
-        err.append( np.mean( (np.poly1d(np.polyfit(x, y, 1))(np.unique(x)) - y)**2 ) )
-    return(err)
-to_Lamperti=lambda data: np.arcsin(2*data-1)
-from_Lamperti=lambda data: 0.5*(1+np.sin(data) )
-
-# %%
-
-# %%
-X=forecast_data_inter[1,:-240,:] #fix this later !!! empty paths
-P=forecast_data_inter[2,:-240,:]
-V=X-P
-dX=np.diff(X)
-dV=np.diff(V)
-dX_Lamprt = np.diff(to_Lamperti(X))
-dV_Lamprt = np.diff(to_Lamperti(V+P))
-# %%
-
-np.max(X)
-np.min(X)
-np.max(V)
-np.min(V)
-
-
-
[…]

### 2020-03-26 python_code/test.py

@@ -1,82 +1,0 @@
-import matplotlib.pyplot as plt
-# import autograd.numpy as np
-
-from mpl_toolkits.mplot3d import Axes3D
-from matplotlib.colors import LogNorm
-from matplotlib import animation
-from IPython.display import HTML
-
-# from autograd import elementwise_grad, value_and_grad
-from scipy.optimize import minimize
-from collections import defaultdict
-from itertools import zip_longest
-from functools import partial
-
-import os
-os.chdir('/home/alhaddwt/Insync/waleedhad@gmail.com/Google Drive/GitLab/wind-power/python_code')
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.cm as cm
-from matplotlib.patches import Ellipse
-import matplotlib as mpl
-from numpy import linalg as LA
-import math
-
-
-
-# fig, ax = plt.subplots(figsize=(10, 6))
-#
-# ax.contour(x, y, z, levels=np.logspace(0, 5, 35), norm=LogNorm(), cmap=plt.cm.jet)
-# ax.plot(*minima_, 'r*', markersize=18)
-#
-# line, = ax.plot([], [], 'b', label='Newton-CG', lw=2)
-# point, = ax.plot([], [], 'bo')
-#
-# ax.set_xlabel('$x$')
-# ax.set_ylabel('$y$')
-#
-# ax.set_xlim((xmin, xmax))
-# ax.set_ylim((ymin, ymax))
-#
-# ax.legend(loc='upper left')
-
-
-
-#model of Beta
-base_path=current_plotting_dir='data/'
-chosen_folder='likelihood_explorer_'+ '19-09-11-21-32-05'
-
-data_path=base_path+chosen_folder
-
-#plotting chosen_folder
-Z=np.load(data_path+'/value.npy')
-X=np.load(data_path+'/theta.npy')
-Y=np.load(data_path+'/alpha.npy')
-
-
-M=np.load(data_path+'/num_paths.npy')
-N=np.load(data_path+'/interpolation_points.npy')
-
-
-from matplotlib import ticker, cm
-%matplotlib qt
-fig = plt.figure(1)
-
-cmap = cm.coolwarm
-contours=plt.contourf(X, Y, Z ,600, cmap=cmap)
-plt.colorbar()
-plt.plot(23.95875, 0.34)
[…]

### 2020-03-26 python_code/test3.py

@@ -1,7 +1,0 @@
-import numpy as np
-import pandas
-
-forecast_data_in = np.load("./data/cleansed/URG_forecast_data_A_2018.npy")
-
-forecast_data_in.shape
-forecast_data_in[45][1]

### 2020-03-26 python_code/unkown.py

@@ -1,198 +1,0 @@
-# %%
-from multi_path_base import *
-import pandas as pd
-import datetime as dt
-from scipy import interpolate
-%matplotlib tk
-# %%
-f = pd.read_csv('sal_utep3_h72_2016_130317.txt', delimiter= '\s+', index_col=False,header=1)
-d = pd.read_csv('sal_uter1_2016_130317_iniper.txt', delimiter= '\s+', index_col=False,header=1)
-n = pd.read_csv('historico_potnom_uruy.txt', delimiter= '\s+', index_col=False,header=None)
-
-# %%
-#setting time and date of the forecasts
-p=f.values
-length_forecast=72 #[hr]
-number_forecasts=int(len(p[:,0])/length_forecast)
-#seperate the forecasts
-forecasts=p.reshape((number_forecasts,72, 10))
-
-#change format of date and time to a datetime object
-forecast_clean=np.empty((forecasts.shape[0],forecasts.shape[1],2))
-for i in range(0,number_forecasts):
-    for j in range(0,72):
-        date_object= dt.datetime.strptime( forecasts[i,j,1] , "%d/%m/%y").date()
-        time_object= dt.datetime.strptime(format(forecasts[i,j,6], '04d'), "%H%M").time()
-        datetime_object = dt.datetime.combine(date_object, time_object)
-        forecast_clean[i,j,0]=datetime_object.timestamp()
-        forecast_clean[i,j,1]=forecasts[i,j,8]
-
-#forecasts[1,1,1].timestamp()
-#forecasts[1,1,1].isoformat()
-#dt.datetime.fromtimestamp(timestamp)
-# %%
-#setting time and data of the data
-data=d.values
-data_clean=np.zeros((2,data.shape[0]))
-for i in range(0,data.shape[0]):
-    date_object= dt.datetime.strptime( data[i,2] , "%d/%m/%Y").date()
-    time_object= dt.datetime.strptime(data[i,3], "%H:%M").time()
-    datetime_object = dt.datetime.combine(date_object, time_object)
-
-    data_clean[0,i]=datetime_object.timestamp()
-    data_clean[1,i]=data[i,4]
-#plt.plot(data_clean[1,:])
-# %%
-#cleaning normalization data
-
-normalization_data=n.values
[…]

### 2020-03-28 Graphs/ToDo/ToDo.tex
I cleaned a bit the directories

--- 2020-01-20 graph/ToDo/ToDo.tex
@@
 Notice that $\theta=\theta(\theta_0,\dot{p})$.
+\item On 28/01/2020: I will save a copy of files \textbf{fit\_model.py}, \textbf{Base\_model.py}, \textbf{path\_simulation.py}, and \textbf{config/beta\_config.JSON} and remove all the extra lines from the original ones.
+
+\item The data Waleed was using is in \textbf{python\_code/data/cleansed/URG\_forecast\_data\_A\_2018.npy.}
 

### 2020-03-28 LaTeX_Code/Discussion/Discussion_14_06_19.tex
I cleaned a bit the directories

--- 2019-08-28 LaTeX_code/Discussion/Discussion_24_06_19.tex
@@
 
-\author{Waleed Alhaddad }
+%\author{Waleed Alhaddad }
 
@@
 
-%\section{Notes and To-do}
+\section{Notes on current work flow}
 \begin{itemize}
-\item Check the how reasonable are the obtained parameters through the quadratic variation
-\begin{equation}
-\sum_{i,j} (X_{i,j} - X_{i,j})^2 \approx 2 \theta_t \alpha \sum_{i,j}  X_{i,j} (1-X_{i,j})
-\end{equation}
-\item Apply the model to the french data 
+\item Fit and simulate  the model for shorter periods of 6hr, 24hr and compare parameters and behavior.
+\item Fit and simulate model without the term $p_t(1-p_t)$  and compare parameters and behavior. Check if it is necessary.
+\item Find a way to  prove that the optimization problem is indeed convex in the parameters of the SDE if possible.
+\item Reasoning why the sensitivity in the parameter $\alpha$ is much higher than the parameter $\theta$, ellipse suggests that a linear combinations of the two parameters $\alpha, \theta_0$ seem to be equivalent.
+Visually, we can also  see by trying out parameters, that certain combination of $\alpha$ and $\theta_0$ seem to be indeed very similar to other combinations.
+\end{itemize}
+
+\section{Notes on future work}
 \begin{itemize}
-	\item We are waiting for the details of the evolution of the maximum installed capacity to be able to normalize.
-	\item Exploit the pyramid structure of the forecast updates, as the french 	recompute the forecast every hour.
-	\item We are also waiting to know if the forecasting technology changed during those years and when.
-This will enable us to  pick upon the particularities of the different forecasting technologies.
-Also, to check if the newest forecasting technology performs better in practice.
-	\end{itemize}
-\item Understand, apply and extend the "R" package DiffusionRgqd to our case of multiple paths and see how it performs in comparison.
-\item Plot the likelihood as two "profile likelihood" plots as common in the statistics literature.
-This means fix one of the parameters, optimize in the other and plot.
-For instance, it  can be expressed in terms varying $\sigma$ as
-\begin{equation}
-R(\sigma) = \frac{\max_\mu \mathcal{L}(\mu, \sigma)}{\mathcal{L}(\hat{\mu}, \hat{\sigma})}
-\end{equation}
-And similarly, we plot $R(\mu)$.
-
-\item The issue with the power curtailing or human intervention is still open. The ideas so far:
-\begin{itemize}
-\item set a threshold to $\theta_t$ to prevent the process from following such sudden changes.
-However, this involves choosing some value of $\theta_t$ and a threshold.
-Also, the data is not refined enough to identify such changes from natural wind speed changes (as currently its recorded at intervals of one hour)
-\item Introduce a jumping process, adds complexity to the model but might enhance it overall. This will enable us to capture the sudden changes.
-\item Regime switching, similar to the first point, but in this case we can assume that $\theta_t$ follows some Markov Chain instead of hard setting thresholds.
-\end{itemize}
-\item Double check that the Feller condition is satisfied to ensure the positivity  of the process.
-\item Try to see if we can make the system ergodic, especially when we have higher frequency data.
-This is done when $\Delta n \to \infty$ where $\Delta$ is the interval between each sample of $n$ total samples.
-
- Then we can leverage existing theoretical results regarding the asymptotic behavior of our model.
-\item Possibility of adding regularizers on $\theta_t$ that way we can manipulate it and differentiate it easily for further theoretical work.
-
-\item Assign an a distribution on the initial point and optimized it separately. By that I mean, optimize it without involving the likelihood and its optimization.
-
-\item Once we have higher frequency data, we can use Ahmad's MLE estimators to find the parameters of the model in a simpler and faster way.
-Regarding this point, I have his papers from 2012 and 2013 which are in the shared Dropbox folder.
-
-\item Another motivation of the project is that power production companies are not allowed to dump more power into the grid than authorized.
-Otherwise, they have to pay hefty fines as they endanger the grid by using it above its capacity.
-
-\item It may also be possible to obtain the aggregated power production of France for both controllable and non-controllable energy sources.
-This will benefit us in two ways, we can identify  human intervention more easily and it can be used as data and a test case for Renzo's optimal control ongoing project.
-Currently this data set is sparse and has some negative values we couldn't understand.
-(see Dropbox shared folder under "Realized\_ Production")
-
+\item Consider regime switching to detect human energy management decisions.
 \end{itemize}

### 2020-03-28 LaTeX_Code/From_Prof_ Kebaier/20200218/UQ_Wind_power.tex
I cleaned a bit the directories

--- 2020-03-12 LaTeX_code/paper/paper_1line.tex
@@
 \documentclass[11pt]{article}
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath}    % need for subequations
+\usepackage{graphicx}   % need for figures
+\usepackage{verbatim}   % useful for program listings
+\usepackage{color}      % use if color is used in text
+%\usepackage{subfigure}  % use for side-by-side figures
+%\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
 
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage{xcolor}
-\usepackage{authblk}
-\usepackage{amsmath}
+%\usepackage[]{showkeys}
+
+%%%%% Comments %%%%%
+\usepackage{todonotes}
+\usepackage{ulem}
+%%%%% Comments %%%%%
+
 \usepackage{amssymb}
 \usepackage{amsthm}
-\usepackage{todonotes}
-%\usepackage[normalem]{ulem}
-\usepackage{float}
-\usepackage{commath}
 \usepackage{fancybox}
-\usepackage{url}
 
+% don't need the following. simply use defaults
+\setlength{\baselineskip}{16.0pt}    % 16 pt usual spacing between lines
+
+\setlength{\parskip}{3pt plus 2pt}
+\setlength{\parindent}{20pt}
+\setlength{\oddsidemargin}{0.5cm}
+\setlength{\evensidemargin}{0.5cm}
+\setlength{\marginparsep}{0.75cm}
+\setlength{\marginparwidth}{2.5cm}
+\setlength{\marginparpush}{1.0cm}
+\setlength{\textwidth}{150mm}
 \theoremstyle{definition}
@@
 \newtheorem{Ex}{Exercise}[section]
+
+%\theoremstyle{plain}
 \newtheorem{Prop}[Def]{Proposition}
@@
 \newtheorem{Res}[Def]{Result}
-\newcommand{\red}{\textcolor{red}}
 
-\usepackage[backend=biber, style=authoryear, citestyle=authoryear, autocite=inline]{biblatex} % package for bibliography 
-%\DeclareLanguageMapping{english}{english-apa}
+\newcommand{\p}{\mathbb{P}}
+\newcommand{\e}{\mathbb{E}}
+\newcommand{\real}{\mathbb{R}}
+\newcommand{\n}{\mathbb{N}}
+\newcommand{\comp}{\mathbb{C}}
+\newcommand{\z}{\mathbb{Z}}
 
-\addbibresource{sdewind.bib}
+%\usepackage{slashbox}
 
-%\renewbibmacro*{title}{%
-%  \ifboolexpr{
-%    test {\iffieldundef{title}}
-%    and
-%    test {\iffieldundef{subtitle}}
-%  }
-%    {}
-%    {\printtext{%
-%     \printtext[titlecase]{\usefield{\uline}{title}}%
-%     \setunit{\subtitlepunct}%
-%     \printfield[titlecase]{subtitle}}%
-%     \newunit}%
-%  \printfield{titleaddon}}
+%\begin{comment}
+%\pagestyle{empty} % use if page numbers not wanted
+%\end{comment}
 
-\newcommand{\add}{\textcolor{red}{[insert]}}
+% above is the preamble
 
-\setcounter{page}{1}
+\allowdisplaybreaks
 
 \begin{document}	
-
-\title{ Stochastic Wind Power Forecasting }  % \\  \small{Report}}
-
-%\author[1]{Waled Alhaddad}
-\author[1]{Renzo Caballero}
-\author[2]{Ahmed Kebaier}
-\author[3]{Marco Scavino}
-\author[4]{ Ra\'ul  Tempone}
-%\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
-\affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
-\affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
-\affil[3]{Universidad de la Rep\'ublica, Instituto de Estad\'{\i}stica (IESTA), Montevideo, Uruguay}
-\affil[4]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}
-
-%\author{ Waled Alhaddad \textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
-%\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University, Germany
-% \\ \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-
-\begin{abstract}
-
-Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price and operation scheduling of conventional power plant.
-We propose a data driven model based on parametric Stochastic Differential Equations (SDEs) to captures real-world asymmetric dynamics of wind power forecast errors.
-Our SDE framework incorporates time derivative tracking of the forecast, time-dependent mean reversion parameter and an improved diffusion term.
-We are able to simulate future wind power production paths and to get sharp confidence bands.
-The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of information criteria.
-We apply the model to historical Uruguayan wind power production data and forecasts on the year 2019.
-
-\end{abstract}
-
-{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, model selection.}
-
-{\color{red} Add AMS Classification.}
-
-%%%%%%%%% BODY TEXT
-
-%---BEGIN SECTION 1---
-\section{Introduction}  \label{Section_1}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\textwidth]{plots/wind_and_solar/plot_over_years.eps}
-\caption{Installed wind and solar power over the years \cite{sultana2017review}. We recall the importance of accurate forecasts to use green energies optimally.}
-\end{figure}
-
-Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
-\begin{itemize}
-\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
-\item Operation scheduling of controlable power plants.
-\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
-\item Maintenance planning such as that of power plants components and transmission lines.
-
-\end{itemize}
-
-Different methods have been applied to wind power forecasting.
-They can be generally categorized as follows: physical models, statistical methods, artificial intelligence methods and hybrid approaches.
-The output of such methods is usually a deterministic forecast.
-Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles.
-{\color{red} Expand discussion about works on probabilistic forecasting.} However, there is a lacking in simulating and producing data driven stochastic forecasts based on real-world performance of forecasting models.
-It is crucial to capture actual performance of a forecast as it has been known that different forecasting technologies exhibits different behavior for different wind farms and seasons [ref].
-This is due to many factors which forecast are challenged to capture such as the surrounding terrains of the wind farm and the condition of the blades such as icing, wear and tear or dirt.
-It is known that complex terrains in both off shore and on shore locations decrease the accuracy of wind power forecasts significantly [ref].
-It also has been shown that the performance of forecasts varies from month to month.
-Thus the performance of wind power forecasts is location and time dependent.
-
-Many approaches have been taken to evaluate the uncertainty of a given forecast.
-There are two types of errors: level errors and phase errors.
-The use of mean or median errors in this context may be misleading as wind power forecast errors are asymmetric.
-This is a natural consequence of wind power being non-negative and bounded by the maximuim capacity of production.
-This is important as the associated cost to power forecast errors are also asymmetric due to different costs for up and down  power regulations which are determined by the electricity market [ref].
-
-We propose to model wind power forecasts errors using parametric stochastic differential equations (SDEs) whose solution defines a stochastic process.
-This resultant stochastic process describes the time evolution dynamics of wind power forecast errors while capturing properties such as a correlation structure and the inherent asymmetry.
-Additionally, the model we propose is agnostic of the forecasting technology and serves to complement forecasting procedures by providing a data driven stochastic forecast.
-Hence, we are able to evaluate wind power forecasts according to their real-world performance and we are able to compare different forecasting technologies.
-Most notably, we are able to simulate future wind power production given a deterministic wind power forecast.
-Future wind power production using Monte Carlo methods, as well as the analytic form of the proposed SDE, can be used in optimal control problems involving wind power production.
-
-Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations.
-Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion and non-Gaussian approximations.
-We apply the model to Uruguayan wind power forecasts together with historical wind power production data pertaining to the year 2019.
-
-{\color{red} Change this paragraph. Discuss with the global dataset, the dataset after removing days when curtailing has been detected, the data set without curtailing and with Lamperti transform.}
-We have available a year long data set from Uruguay based on 363 observation paths, each of which is 24-hours long with observations recorded every 10 min.
-In total, it is a data set of approximately fifty thousand data points recorded in 2019.
-See Figure (\ref{fig:sample_data}).
-Data are normalized with respect to the maximum power capacity of wind power production in Uruguay, which is $\SI{1474}{\mega\watt}$.
-However, sometimes the real production is artificially modifies due to curtailing.
-This effect becomes clear when we inspect for different power production levels.
-We split the available data into low, medium and high power range.
-See Figure (\ref{fig:data_curtailing}).\\
-We identify and remove the days with curtailing, removing a total of 108 days.
-From the resulting 255 days, we use 127 days to train the system and 128 to test it.
-Also, to avoid correlation between days, we intercalate the days we use for training and testing ({\color{red} Show that 24h is enough to ensure independence}).
-
-In this paper we present the phenomenological underlying model in Section \ref{Section_2} and describe the physical constraints in Section \ref{Section_3} and how these constrains can be met.
-Then, in Section \ref{Section_4}, we will introduce an alternative formulation of the model in Lamperti space.
-In Section \ref{Section_5}, we show our parameter estimation procedure and its results in Section \ref{Section_6}.
-We compare alternative models in Section \ref{Section_7} and different forecast providers in Section \ref{Section_8}.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/5.eps}
-\includegraphics[width=0.45\textwidth]{plots/245.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/661.eps}
-\includegraphics[width=0.45\textwidth]{plots/805.eps}
-\caption{Four samples from the Uruguayan data of 2019.
-Each sample compromises of two 24-hour paths.
-In blue is an hourly wind power production forecast.
-In orange is the actual wind power production recorded in 10 minute intervals.}
-  \label{fig:sample_data}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
-\caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production.
-Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$.
-We have a total of 363 days to use.}
-  \label{fig:data_curtailing}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP.eps}
-\caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
-  \label{fig:data_after_clean}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
-\caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
-\label{fig:error_transitions}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
-\caption{Transitions after the Lamperti transform.
-The transitions now present a normal Gaussian shape.
-This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
-  \label{fig:LP_transitions}
-\end{figure}
-%---END SECTION 1---
-
-%---BEGIN SECTION 2---
-\section{Phenomenological  Model} \label{Section_2}
-
-In this section, once we analyzed the available dataset, we consider a type of phenomenological model for the normalized wind power generation forecasts which is given, in its most general form, as a stochastic process $X = \{X_t, \, t \in [0,T] \}$  defined by the following stochastic differential equation (SDE):
-
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&=  a(X_t; p_t, \dot{p}_t,\bm{\theta}) \,dt + b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \,dW_t\,, \quad t \in [0,T]  \\
-     X_0  \!\!\!&=  x_0 \in [0,1],
-  \end{array}\right. \label{eq:main}
-\end{equation}
-
-where
-
-\begin{itemize}
-\item $a(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R} $  denotes a drift function,
-\item $b(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R}^+ $  a  diffusion function,
-\item $\bm{\theta}$ is a vector of unknown parameters,
-\item $(p_t)_{t \in [0,T]}$ is a time-dependent deterministic function $[0,1]$-valued and $ (\dot{p}_t)_{t \in [0,T]}$ is its time derivative,
-\item $\{W_t, \, t \in [0,T] \}$ is a standard real-valued Wiener process.
-\end{itemize}
-
-In this work, $(p_t)_{t \in [0,T]}$ is to be considered as a deterministic forecast for the normalized wind power generation, which is provided by an official source.
-
-Our goal is to achieve a specification of the model (\ref{eq:main}) to follow closely the available normalized wind power forecasts while ensuring its unbiasedness with respect to the forecast.
-
-\subsection{Physical Constraints}
-
-Let $(p_t)_{t \in [0,T]}$ be the available prediction function for the normalized wind power, which is an input to this approach.
-To start with the model specification, first we introduce a time-dependent drift function that features the mean-reverting property as well as derivative tracking:
-\begin{equation}
-a(X_t; p_t, \dot{p}_t, \bm{\theta}) = \dot{p}_t  - \theta_t (X_t - p_t)\,,  \label{drift:meanrev-derivtrack}
-\end{equation} 
-where $ (\theta_t)_{t \in [0,T]} $ is a positive deterministic function, whose range depends on $\bm{\theta}$, as will be explained shortly.
-
-Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$.
-
- Then, the process defined by (\ref{eq:main}) with drift (\ref{drift:meanrev-derivtrack}) satisfies the two following properties: 
-\begin{itemize}
-\item it reverts to its mean $p_t$, with a time-varying speed $ \theta_t$ that is proportional to the deviation of the process $X$ from its mean,
-\item it tracks the time derivative $\dot{p}_t$.  
-\end{itemize} 
-Observe that a mean reverting model without derivative tracking exhibits consistent lags, as it is shown in Figure (\ref{fig:derivative_tracking}). See Section \ref{Section_7} for comparisons.
-
-\begin{figure}
-  %\includegraphics[width=26mm,scale=1]{}
-  \caption{insert figure showing the difference with and without derivative tracking}
-  \label{fig:derivative_tracking}
-\end{figure}
-
-The forecast and production wind power data of Uruguay are normalized with respect to the installed power capacity during the period of observation.
-Thus, the mean-reverting level lies in $[0,1]$, and the process $X$  must take values in the same interval,a requirement that is not automatically fulfilled through the derivative tracking.
-To impose that the state space of $X$ is $[0,1]$, we may choose a convenient diffusion term, and require that the time-varying parameter $ \theta_t$ satisfies an ad-hoc condition.
-
-Let $\bm{\theta} = (\theta_0,\alpha)$, and choose a state-dependent diffusion term that avoids the process exiting from the range $[0,1]$ as follows:
-  \begin{equation}
-    b (X_t; \bm{\theta} )= \sqrt{2 \theta_0 \alpha X_t (1 - X_t)}
-  \end{equation}
-  where $\alpha >0$ is a unknown parameter that controls the path variability.
-This diffusion term belongs to the Pearson diffusion family and, in particular, it defines a Jacobi type diffusion.
-It is useful to recall that (\cite[440]{foso}) a Pearson diffusion is a stationary solution to a stochastic differential equation of the form
- \begin{equation}
-    dX_t = - \theta (X_t - \mu) dt + \sqrt{2 \theta (a X_t^2 + b X_t + c)} dW_t
-  \end{equation}
-where $\theta>0$, and $a$, $b$ and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space.
-These parameters, together with $\mu$, the mean of the invariant distribution, determine the state space of the diffusion as well as the shape of the invariant distribution.
-
-An exhaustive classification of the (stationary) Pearson diffusions is presented in (\cite[440-443]{foso}) where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 \theta a x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the well-known Jacobi diffusions, so-called because the eigenfunctions of the infinitesimal generator of these processes are the Jacobi polynomials (see, for example, \cite[2860-2861]{leph}).
-
-It is worth mentioning that Jacobi diffusions have been successfully applied in several disciplines, among them econometrics (see  and references therein) and neuroscience (\cite{dotala}).
-
-However, a distinctive feature in our proposed model 
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= (\dot{p}_t  - \theta_t (X_t - p_t) ) dt +\sqrt{2 \theta_0 \alpha X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{ourmodel}
-\end{equation}
-
-is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X$ to (\ref{ourmodel}) a non-stationary and time-inhomogeneous process.
-To ensure that the process $X$ be the unique strong solution to (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the following condition:
-%has to be selected according to the following rule.
-Observe that the time derivative term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays a.s.
-inside the range $[0,1]$.
-In other words, the zero drift line defined by $a(x; p_t,\bm{\theta}) =0$, which is an attractor, must be contained inside the range $[0,1]$.
-Thus, we must have that
-%\begin{equation}
-%\frac{- |\dot{p_t}|}{p_t} \leq \theta_t \leq \frac{|\dot{p}_t|}{1- p_t}
-%\end{equation}
-%which is satisfied  by choosing a time-dependent  $\theta_t$ as follows,
-%\begin{equation}
-%\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \theta_0 >0\,. \label{theta_t}
-%\end{equation}
-\begin{equation}\label{Assumption:3}
-\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
-\end{equation}
-The proof of this theoretical statement is presented in Section \ref{Appendix}.
-
-%{\color{red} The expression for $\theta_t$ is important: $\theta_t$ depens on $t$ through $\dot{p_t}$ and $p_t$.
-Besides it is parsimonious because only one unknown parameter appear in \ref{theta_t}.
-Recall it is an upped bound for the real inequality.
-}
-
-%\subsubsection*{Change of Variables:}
-\subsection{A model specification for the forecast error}
- After applying the simple change of variables $$V_t = X_t - p_t \,,$$ we may introduce the following model for the forecast error of the normalized wind power production:
-
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dV_t \!\!\!&=  - \theta_t V_t  \, dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \, dW_t\,, \quad t \in [0,T]  \\
-   V_0  \!\!\!&=  v_0\in [-1,1] \,.
- \end{array}\right.  \label{VtSDE}
-\end{equation}
-
-%---END SECTION 2---
-
-%---BEGIN SECTION 3---
-\section{State independent diffusion: Lamperti transform} \label{Section_3}
-
-Our model (\ref{VtSDE}) for the forecast error has a diffusion term that depends on the state variable $V_t$.
-To estimate the unknown model parameters, a recommended technique is to modify the SDE (\ref{VtSDE}) by applying the so-called Lamperti transform (see \cite[40--41]{iacus1}, \cite{moma}, \cite[98--100]{saso}) to the process $V$ to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
-\\
-
-We consider the following Lamperti transformation  {\color{red} (Remind that in continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
-Besides, it can be unstable to work with low frequency.
-If the frequency of the data is too low, the Lamperti transform helps to detect this problem (in principle, it is not clear how to determine the right frequency for estimation.
-)}
-\begin{equation}
-Z_t = h(V_t) = \frac{1}{\sqrt{2 \theta_t \alpha}} \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
-\end{equation}
-where $\xi$ is an arbitrary point of the state space of the process $V$. The choice of $\xi = \frac{1}{2} - p_t$, where $p_t$ is a known input, leads to the process 
-\begin{equation}
-Z_t = h(V_t) = \frac{1}{\sqrt{2 \theta_t \alpha}} \arcsin (2(V_t + p_t) -1)\,,
-\end{equation}
-that, after applying It\^{o}'s formula on $h(V_t)$, gives the state-independent diffusion SDE
-\begin{equation}
-dZ_t = \left[  \frac{- \theta_t V_t}{ \sqrt{2 \theta_t \alpha (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \theta_t \alpha} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \right] \,dt + dW_t \,.
-\label{eq:stindepSDE}
-\end{equation}
-After replacing $V_t = \frac{\sin(\sqrt{2 \theta_t \alpha} Z_t) + 1}{2} - p_t$ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
-\begin{align}
-dZ_t & = \left[ \frac{- \theta_t (\sin(\sqrt{2 \theta_t \alpha} Z_t) + 1 - 2 p_t)}{\sqrt{2 \theta_t \alpha} \cos{(\sqrt{2 \theta_t \alpha} Z_t)}} + \frac{\sqrt{2 \theta_t \alpha} \sin{(\sqrt{2 \theta_t \alpha} Z_t)}}{2 \cos{(\sqrt{2 \theta_t \alpha} Z_t)}} \right] \,dt + dW_t \nonumber \\
-&  = \left[  \frac{\sqrt{2 \theta_t} \left( \sin(\sqrt{2 \theta_t \alpha} Z_t) (\alpha - 1) + (2 p_t -1 ) \right)}{2 \sqrt{\alpha} \cos{(\sqrt{2 \theta_t \alpha} Z_t)}}  \right] \,dt + dW_t \,. 
-\end{align}
-
-%\begin{align}
-%    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} \ dt + \sqrt{2 \alpha \theta_t} dW_t \\
-%    Z_0&=z_0 \,,
-%\end{align}
-%where the Lamperti trasform is given by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
-
-We can see in Figure (\ref{fig:skew_after_lamperti}) the effect of the Lamperti transformation upon the forecast error data. 
-The Lamperti transformation has greatly reduced the forecast error skewness, ensuring that the process stays in the range $[0,1]$.
-Therefore, in this case, the transition densities of the process Z can be adequately approximated through Gaussian densities.
-%---END SECTION 3---
-
-%---BEGIN SECTION 4---
-\section{Likelihood in $V$ space} \label{Section_4}
-
-\subsection{Likelihood}
-
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t >0 \}$ is sampled at $N$ equispaced discrete points with length interval $\Delta_N$, and let $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ denote this random sample.
-
-Let $\rho_i(v \vert v_{j, t_{i-1}} ; \bm{\theta})$ denote the conditional probability density of $V_{j, t_i}$ given $V_{j, t_{i-1}} = v_{j, t_{i-1}}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha)$ are the unknown model parameters.
-
-The It\^{o} process $V$ defined by the SDE (\ref{VtSDE}) is Markovian, then the likelihood function of the data can be written as the following product of transition densities:  
-%Consider the set of $M$ paths with $N$ observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$, observed in $\Delta_N$ intervals.
-\begin{equation}
-\mathcal{L}(\bm{\theta},\delta; V^{M,N}) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j, t_i}| V_{j, t_{i-1}}} ; p_{[t_{i-1}, t_{i}]},  \bm{\theta} )  \, \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
-\label{likelihood}
-\end{equation}
-
- {\color{red} In \ref{likelihood} modify the expression for $\rho_0$ contemplating the lag, say $\delta$, between the time when the forecast is done and the first time of forecasting.
-$\rho_0$ can be written as a conditional density between these two times.
-Once $\theta_0$ and $\alpha$ have been estimated, one could estimate $\delta$.}
-
-The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized, for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}, \cite[61-68]{saso}):
-
-\begin{align}
-\frac{ \partial f }{\partial t } & \rho_i(v_{j,i} ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} )= - \frac{\partial}{ \partial v} (- \theta_t v \, \rho_i(v ,t_{j,i} \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) ) \nonumber \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( 2 \theta_t \alpha (v+ p_t) (1 - v- p_t) \, \rho_i(v ,t_{j,i} \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) )\,,  \label{eq:fpk}
-\end{align}
-subject to the initial conditions $\rho_{i-1}(v , t_{j, i-1} , \bm{\theta} ) = \delta(v - V_{j, t_{i-1}}) \,,$ where $ \delta(v - V_{j, t_{i-1}})$ is the Dirac-delta generalized function centered at $ V_{j, t_{i-1}}\,.$
-
-Closed-form solutions to initial-boundary value problem for SDEs can be obtained only in a few cases.
-Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
-Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.
-Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.
-
-\subsection{Approximate Likelihood}
-
-A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints which give rise to asymmetric forecasting errors as seen in figure (\ref{fig:skew_data}).\\
-
-We propose a proxy transition density.
-We match the moments of our SDE model with that of the proxy density.
-Using It\^o formula, we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
-\begin{equation}
-\frac{d \mathbb{E}[ V^k_t]}{dt} = - k \theta_t \mathbb{E}[ V^k_t] + \frac{k(k-1)}{2} \mathbb{E}[ V^{k-2}_t  b(V^k_t;\theta_t, \alpha)]
-\end{equation}
-
-For $t\in [t_{n-1}, t]$, the first two moments are given by
-\begin{align}
-\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t   \nonumber \\
-\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta_t(1+\alpha) + 2\alpha\theta_t m_1(t)(1-2p_t)  \nonumber \\
-&\quad + 2 \alpha\theta_t p_t (1-p_t) \,,
-\end{align}
-with initial conditions $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2 \,.$
-
-And for the state independent diffusion formulation, similarly, we  obtain a system of ODEs to determine the centered moments of the Lamperti transformed process $V_t$.
-Due to the non-linearity in the drift, we can only approximate the centered moments by the following ODEs,
-\begin{align}
-\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\alpha) - \theta (1-2 p_t) \nonumber \\
-\frac{d var(t)}{dt} &=  2 var(t) \theta_t (2p_t - 1 ) \tan(m_1 (t)) \sec(m_1 (t))   \nonumber \\
-& \quad + \theta_t (\alpha - 1) \sec^2(m_1 (t))  + 2 \theta_t \alpha \,.
-\end{align}
-
-A suitable candidate for a proxy transition density is a Beta probability distribution as it is compactly supported and can morph into symmetric and asymmetric shapes.
-{\color{red} Move this sentence to next section.}
-
-\subsubsection*{ Moment Matching}
-To approximate the transition densities of  the process $V_t$ by a Beta distribution, we match its moments with the shape parameters $\xi_1, \xi_2$ of a Beta proxy density on $[-1,1]$.
-The any moment of the process $V_t$ is  given by solving the corresponding ODE system  for the $k^{th}$  moment,
-
-The shape parameters are given by
-\begin{equation}
-\xi_1 = - \frac{(1+\mu_t )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2}\,, \quad \xi_2=  \frac{(\mu_t-1 )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2} \,, \label{param_transformed_beta}
-\end{equation}
-where $\mu_t = m_1 (t)$ and $\sigma_t^2= m_2 (t)- m_1 (t)^2\,.$
-
-\subsection{Optimization} \label{opt_sec}
-{\color{red} Rewrite the discussion to obtain fast initial estimate for the two unknow parameters.}
-
-To initialize the optimization process for the likelihood function of the process $V$, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$: {\color{red} Add explanation regarding the motivation for this objective function.}
-
-\begin{equation}
-\theta_0\approx\arg\min_{\theta} \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2,
-\label{inital_theta}
-\end{equation}
-
- where $v_{i,j}=x_{i,j}-p_{i,j}$,  $x_{i,j}$ is historical wind power production and $p_{i,j}$ is the wind power forecast.
-
- By assuming ergodicity {\color{red} not ergodicity, instead simply for the \textbf{quadratic variation formula}.}, we can obtain a first estimate on the product of the parameters as follows,
-
-\begin{equation}
-\theta_0 \alpha \approx \frac{1}{2M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{ \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
-\end{equation}
-
-Solving for $\alpha$, we have both first estimates and we can also estimate $\delta$ solving the problem
-
-\begin{equation}
-\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
-\label{likelihood_delta}
-\end{equation}
-
-With our estimations of $\bm{\theta}$, we can start the inference processes as follows:
-\begin{enumerate}
-\item[Step 1.]  initialize;
-\item[Step 2.]  optimize the log-likelihood function using  Nelder-Mead optimization algorithm on a mini-batch sampled with replacement;
-\item[Step 3.] check if  accuracy threshold is reached. Else, re-initialize the optimization with the most recent result on a larger mini-batch.
-\end{enumerate}
-%---END SECTION 4---
-
-%---BEGIN SECTION 5---
-\section{Model Comparison} \label{Section_5}
-
-We compare two candidate models to find the best-fit that maximizes the retained information,
-\begin{itemize}
-  \item Model 1: This model does not feature derivative tracking.
-  \begin{align}
-  dX_t &=  - \theta_0 (p_t-X_t) \  dt + \sqrt{2 \theta \alpha X_t (1-X_t)} \  dW_t   \nonumber \\ %\quad t > 0
-  X_0 & = x_0 \,, \label{M0}
- \end{align}
-  with $\theta_t= \theta_0 $.
-
-%  \item Model 1: This model features derivative tracking, i.e.
-it is equivalent to (\ref{model:derivative_tracking_X}) with a diffusion term that is forecast dependent by including the term $p_t(1-p_t)$.
-%  \begin{equation}
-%  \begin{split}
-%  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha p_t(1-p_t)(V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
-%  V_0 & = v_0
-%  \end{split}\label{M2}
-%  \end{equation}
-%  with $\theta_t$ given by (\ref{theta_t}).
-This model has been used by [ insert ref ] and [ insert ref ].
-Initial interest in this model stems from interest in long-term stationary solution, which may exists  if the forecast is constant.
-However, this is almost never occurs and thus including the term $p_t(1-p_t)$ is irrelevant.
-Additionally, the term $p_t(1-p_t)$ leads the model to become deterministic when the forecast is at the boundaries (i.e.$p=1$ or $p=0$)  which is not realistic.
-We have run computations on this model and the results were not satisfactory.
-Therefore, we exclude this model from further discussions.
-%
-
-  \item Model 2: This model features derivative tracking, i.e. it is equivalent to (\ref{model:derivative_tracking_X}).
-  \begin{align}
-  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t   \nonumber \\ %\quad t > 0
-  V_0 & = v_0 \,, \label{M2}
-  \end{align}
-  with $\theta_t$ given by (\ref{theta_t}).
-\end{itemize}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{cccc}
-\toprule
-Model   &  parameters $(\theta_0, \alpha,\delta)$   & AIC & BIC \\ \midrule
-Model 1 &  $(\add,\add) $    &  \add   &  \add   \\
-Model 2 &   $(1.2,0.1,0.6)$   &  \add   &   \add    \\ 
-\bottomrule
-\end{tabular}
-\caption{We compare the different models based on information criterion. \add }
-\label{tab:model_comparison}
-\end{table}
-%---END SECTION 5---
-
-%---BEGIN SECTION 6---
-\section{Forecast Provider Comparison} \label{Section_6}
-We compare forecasts from two different companies for the same period.
-\begin{table}[H]
-\centering
-\begin{tabular}{cccc}
-\toprule
-Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \midrule
-Provider A  &  $(\add,\add)$      &  \add   & \add    \\
-Provider B  & $(\add,\add) $  &  \add   &   \add  \\ 
-\bottomrule
-\end{tabular}
-\caption{\add}
-\label{tab:forcast_comparison}
-\end{table}
-In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.
-
- \begin{table}[H]
- \centering
- \begin{tabular}{cccc}
- \toprule
- Model & parameters $(\theta_0, \alpha)$  \\
- \midrule
- \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ 
- \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \bottomrule
- \end{tabular}
- \caption{ \add confidence interval obtained using bootstrap}
- \label{tab:freq_comparison}
- \end{table}
-%---END SECTION 6---
-
-%---BEGIN SECTION 7---
-\section{Results} \label{Section_7}
-
-\subsection{Initial guesses}
-
-Following the instruction for the initial guesses from section $\ref{opt_sec}$, we get the initial guesses $(\theta_0,\alpha,\delta)\approx(1.2,0.1,0.6)$.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/initial_guess/initial_theta_1.eps}\quad\includegraphics[width=0.42\textwidth]{plots/initial_guess/initial_theta_2.eps}
-\caption{Value function from ($\ref{inital_theta}$) as a function of different $\theta_0$ values. We can observe that the function if flat for a wide range.}
-\end{figure}
-
-\subsection{Negative Log-Lihelihood}
-
-We plot the Negative Log-Likelihood as a function of the parameters.
-The plots can be seen in Figure (\ref{fig:neg-LL}).
-We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood.eps}\quad\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_refined.eps}
-\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_more_refined.eps}
-\caption{Negative Log-Likelihood for different domains.}
-\label{fig:neg-LL}
-\end{figure}
-
-\subsection{Main guesses}
-
-We were able to obtain the following for 
-\begin{table}[H]
-\centering
-\begin{tabular}{|c|c|}
-\hline
-Formulation   &  parameters $(\theta_0, \alpha,\delta)$    \\ \hline
-Without Lamperti transform &   $(1.2,0.1,0.6) \pm (\add , \add) $   \\ \hline
-With Lamperti transform &   $(12,0.29) \pm (\add , \add)  $   \\ \hline
-\end{tabular}
-\caption{We compare the parameters obtained in both the original and Lamperti space. Parameters have been obtained based on \add data points from the Uruguayan pertaining to the year 2019\add .}
-\label{tab:model_comparison_2}
-\end{table}
-
-{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models (if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.)}
-
-{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
-How many data we need to achive enough accuracy for the estimates of the two parameters?
-Generally, such accuracy is application dependent}
-
- We are able to obtain the parameters based on the complete data sets. Using the different models variations, we are able to simulate wind power production given a forecast. We see in figures ()-()
-five possible wind power production paths for each model.\\
-
-In Figures ()-(), we show point-wise empirical confidence bands for the different models.
-
-\begin{figure}[H]
-  \includegraphics[width=56mm,scale=1]{plots/alpha_conv_beta.png}
-  \includegraphics[width=56mm,scale=1]{plots/theta_conv_beta.png}
-  \caption{We show self-convergence of our algorithm applied to model $2$. We conlcude that the rate  matches that of of Monte Carlo. Data is from Uruguay pertaining to year 2019.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/2.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/3.eps}
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/4.eps}
-\caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
-Forecast is from Uruguay pertaining to  year 2019.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/2.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/3.eps}
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/4.eps}
-\caption{{\color{red}Pending add legend and choose better colors.}We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
-Actual production plotted in retrospect.
-Forecast and data is from Uruguay pertaining to  year 2019.}
-\end{figure}
-%---END SECTION 7---
-
-%---BEGIN SECTION 8---
-\section{Conclusions} \label{Section_8}
-
-We have proposed a method to produce stochastic wind power forecasts based on parametric SDEs.
-This method is agnostic of the wind power forecasting technology.
-Using this method, we were able to simulate future wind power production paths and obtain confidence bands.
-We conclude that Model 2 is a best-fit model.
-It features time-derivative tracking of the forecast, time-dependent mean reversion parameter, and a more natural diffusion term.
-Moreover, the model preserves the asymmetry of wind power forecast errors and their correlation structure.
-
-We were also able to compare two different forecast providers with respect to their real-world performance on the aggregated data set and on specific wind farm sites.
-Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.
-%---END SECTION 7---
-
-%---BEGIN APPENDIX---
-\section{Appendix} \label{Appendix}
-
 \section{The model}
@@
 $$\sup_{t\in[0,T]}\bigl( |p_s| + |\dot p_s|\big) <+\infty .$$
-The following proofs are based on standard arguments for stochastic processes that can be found e.g. in \cite{Alf} and \cite{KarShr} that we adapted to the setting of our model \eqref{eq:model}.
+The following proofs are based on standard arguments for stochastic processes that can be found e.g.
+in  Alfonsi \cite{Alf} and Karatzas and Shreve \cite{KarShr} that we adapted to the setting of our model \eqref{eq:model}.
 \begin{Thm}\label{thm:exun}
@@
 \end{equation}
-According to Proposition 2.13, p.291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X$ to \eqref{eq:eds1}.
+According to Proposition 2.13, p.
+291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X$ to \eqref{eq:eds1}.
 Moreover, as the diffusion coefficient is of linear growth, we have  for all $p>0$
@@
 \end{align*}
-See the proof of Proposition 2.13, p. 291 of \cite{KarShr} for the construction of such function.
+See the proof of Proposition 2.13, p. 291 of \cite{KarShr} for the construction of such fucntion.
 Applying Itô's formula we get
 \begin{align*}
-\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)ds \\
-&+ \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s + \alpha \int_0^t \theta_sg_n(|X_s|)|X_s(1-X_s)|ds.
+\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)ds + \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s\\
+&+ \alpha \int_0^t \theta_sg_n(|X_s|)|X_s(1-X_s)|ds.
 \end{align*}
@@
 $$
-\frac{dX_t}{X_t}=\left( \frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)\dif t  +\sqrt{\frac{2\alpha \theta_t(1-X_t)}{X_t}} \dif W_t 
+\frac{dX_t}{X_t}= \frac{\dot p_t +\theta_t p_t}{X_t} - \theta_tdt  +\sqrt{\frac{2\alpha \theta_t(1-X_t)}{X_t}} dW_t 
 $$  
@@
  \end{proof}
+\textcolor{red}{When using Lamperti, the form }
+\begin{thebibliography}{00}
 
-\section{New model}
-In what follows we adapt the proof of the above theorem for the new model 
-\begin{align}\label{eq:model2}
-dX_t&= \big(\dot p_t - \theta_t(X_t-p_t)  \big)dt  +\sqrt{2\alpha \red{\theta_0}X_t(1-X_t)} dW_t\quad t\in[0,T]\\
-X_0&=x_0\in[0,1],\notag
-\end{align}
+\bibitem{Alf} Alfonsi, A. (2015) Affine diffusions and related processes: simulation, theory and applications. {\it  Springer, Cham; Bocconi University Press, Milan, 2015}. 
+\bibitem{KarShr} Karatzas, I. and Shreve, S. E. (1991),  Brownian motion and stochastic calculus {\it Springer-Verlag, New York}.
 
-\begin{Thm}\label{thm:mod2}
-Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
-Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$.
-Assume in addition that for all $t\in[0,T]$,  $p_t\in]0,1[$ and that
-\red{
-\begin{equation}\label{Assumption:3}
-\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
-\end{equation}
-}
- Then, $\tau_0=\tau_1=+\infty$ a.s.
-\end{Thm}
-
-\begin{proof}
-For $t\in[0,\tau_0[$, we have 
-$$
-\frac{dX_t}{X_t}= \left(\frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)dt  +\sqrt{\frac{2\alpha \red{\theta_0}(1-X_t)}{X_t}} dW_t 
-$$  
-so that
-$$
-X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \red{\theta_0}\alpha)}{X_s}ds+\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big),
-$$
-where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_s(1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \red{\theta_0}\alpha\ge0$, we deduce that
-$$
-X_t\ge x_0\exp\Big(\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big).
-$$
-By way of contradiction let us assume that  $\{\tau_0<\infty\}$, then letting $t\to \tau_0$ we deduce that $\lim_{t\to \infty} \mathbf 1_{\{\tau_0<\infty\}}M_{t\wedge \tau_0}=\mathbf -1_{\{\tau_0<\infty\}}\infty$ a.s.
-This leads to a contradiction since we know that continuous martingales likewise the Brownian motion cannot converge  almost surely to $+\infty$ or $-\infty$.
-It follows that $\tau_0=\infty$ almost surely.
-Next, recalling that  the process $(Y_t)_{t\geq 0}$  given by $Y_t=1-X_t$ is solution to
-$$
-dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \red{\theta_0}Y_t(1-Y_t)} dW_t 
-$$
-we deduce using similar arguments as above 
-$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \red{\theta_0}\ge 0$.
- \end{proof}
- \section{Answers to Renzo's questions} 
-{\color{blue}So, Theorem \ref{thm:mod2} answers the second question in slide 11.} The new condition \eqref{Assumption:3} that guarantees  for $(X_t)_{t\ge0}$ to stay in $]0,1[$ depends now on $\alpha$.
-I would keep condition \eqref{Assumption:3} as we have a proof for it.
-Moreover, if condition \eqref{Assumption:3} is satisfied, then  the orange condition in slide 8 is also satisfied
-since we have 
-$$
-\max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\ge \max\left(\frac{\frac{\alpha\theta_0}{2}+\dot p_t}{1-p_t},\frac{\frac{\alpha\theta_0}{2}-\dot p_t}{p_t}\right)
-$$
-which ensures that $Z$ don't hit the boundaries too according to Renzo's intuitive arguments.\\ 
-{\color{blue}Concerning, the first question on slide 11:} we can't apply Itô's formula, unless we are sure that the process don't hit the boundaries, that's why we have to assume  \eqref{Assumption:3} before using Itô's formula.
-In addition, as the diffusion coefficient of $X$  given by  $x\mapsto \sqrt{\frac{2\alpha \red{\theta_0}(1-x)}{x}}$  is strictly positive for all $x$ in the state space of $X$, namely $]0,1[$ under assumption \eqref{Assumption:3},  this is enough to ensure that the transformation between $Z$ and $X$ is bijective so that we deduce the existence and uniqueness of $Z$ from those of $X$.
-Otherwise the Lamperti transform is not valid if the state space of $X$ is $[0,1]$.
-
-%---REFERENCES---
-
-\nocite{*}
-
-%\printbibliography
-\printbibliography[keyword={Wind-SDE},title={References}]
-
+\end{thebibliography}
 \end{document}

### 2020-03-28 LaTeX_Code/From_Prof_ Kebaier/20200307/UQ_Wind_power.tex
I cleaned a bit the directories

--- 2020-03-12 LaTeX_code/paper/paper_1line.tex
@@
 \newtheorem{Res}[Def]{Result}
+
+\newcommand{\p}{\mathbb{P}}
+\newcommand{\e}{\mathbb{E}}
+\newcommand{\real}{\mathbb{R}}
+\newcommand{\n}{\mathbb{N}}
+\newcommand{\comp}{\mathbb{C}}
+\newcommand{\z}{\mathbb{Z}}
 \newcommand{\red}{\textcolor{red}}
 
-\usepackage[backend=biber, style=authoryear, citestyle=authoryear, autocite=inline]{biblatex} % package for bibliography 
-%\DeclareLanguageMapping{english}{english-apa}
+%\usepackage{slashbox}
 
-\addbibresource{sdewind.bib}
+%\begin{comment}
+%\pagestyle{empty} % use if page numbers not wanted
+%\end{comment}
 
-%\renewbibmacro*{title}{%
-%  \ifboolexpr{
-%    test {\iffieldundef{title}}
-%    and
-%    test {\iffieldundef{subtitle}}
-%  }
-%    {}
-%    {\printtext{%
-%     \printtext[titlecase]{\usefield{\uline}{title}}%
-%     \setunit{\subtitlepunct}%
-%     \printfield[titlecase]{subtitle}}%
-%     \newunit}%
-%  \printfield{titleaddon}}
+% above is the preamble
 
-\newcommand{\add}{\textcolor{red}{[insert]}}
-
-\setcounter{page}{1}
+\allowdisplaybreaks
 
 \begin{document}	
-
-\title{ Stochastic Wind Power Forecasting }  % \\  \small{Report}}
-
-%\author[1]{Waled Alhaddad}
-\author[1]{Renzo Caballero}
-\author[2]{Ahmed Kebaier}
-\author[3]{Marco Scavino}
-\author[4]{ Ra\'ul  Tempone}
-%\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
-\affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
-\affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
-\affil[3]{Universidad de la Rep\'ublica, Instituto de Estad\'{\i}stica (IESTA), Montevideo, Uruguay}
-\affil[4]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}
-
-%\author{ Waled Alhaddad \textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
-%\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University, Germany
-% \\ \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-
-\begin{abstract}
-
-Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price and operation scheduling of conventional power plant.
-We propose a data driven model based on parametric Stochastic Differential Equations (SDEs) to captures real-world asymmetric dynamics of wind power forecast errors.
-Our SDE framework incorporates time derivative tracking of the forecast, time-dependent mean reversion parameter and an improved diffusion term.
-We are able to simulate future wind power production paths and to get sharp confidence bands.
-The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of information criteria.
-We apply the model to historical Uruguayan wind power production data and forecasts on the year 2019.
-
-\end{abstract}
-
-{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, model selection.}
-
-{\color{red} Add AMS Classification.}
-
-%%%%%%%%% BODY TEXT
-
-%---BEGIN SECTION 1---
-\section{Introduction}  \label{Section_1}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\textwidth]{plots/wind_and_solar/plot_over_years.eps}
-\caption{Installed wind and solar power over the years \cite{sultana2017review}. We recall the importance of accurate forecasts to use green energies optimally.}
-\end{figure}
-
-Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
-\begin{itemize}
-\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
-\item Operation scheduling of controlable power plants.
-\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
-\item Maintenance planning such as that of power plants components and transmission lines.
-
-\end{itemize}
-
-Different methods have been applied to wind power forecasting.
-They can be generally categorized as follows: physical models, statistical methods, artificial intelligence methods and hybrid approaches.
-The output of such methods is usually a deterministic forecast.
-Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles.
-{\color{red} Expand discussion about works on probabilistic forecasting.} However, there is a lacking in simulating and producing data driven stochastic forecasts based on real-world performance of forecasting models.
-It is crucial to capture actual performance of a forecast as it has been known that different forecasting technologies exhibits different behavior for different wind farms and seasons [ref].
-This is due to many factors which forecast are challenged to capture such as the surrounding terrains of the wind farm and the condition of the blades such as icing, wear and tear or dirt.
-It is known that complex terrains in both off shore and on shore locations decrease the accuracy of wind power forecasts significantly [ref].
-It also has been shown that the performance of forecasts varies from month to month.
-Thus the performance of wind power forecasts is location and time dependent.
-
-Many approaches have been taken to evaluate the uncertainty of a given forecast.
-There are two types of errors: level errors and phase errors.
-The use of mean or median errors in this context may be misleading as wind power forecast errors are asymmetric.
-This is a natural consequence of wind power being non-negative and bounded by the maximuim capacity of production.
-This is important as the associated cost to power forecast errors are also asymmetric due to different costs for up and down  power regulations which are determined by the electricity market [ref].
-
-We propose to model wind power forecasts errors using parametric stochastic differential equations (SDEs) whose solution defines a stochastic process.
-This resultant stochastic process describes the time evolution dynamics of wind power forecast errors while capturing properties such as a correlation structure and the inherent asymmetry.
-Additionally, the model we propose is agnostic of the forecasting technology and serves to complement forecasting procedures by providing a data driven stochastic forecast.
-Hence, we are able to evaluate wind power forecasts according to their real-world performance and we are able to compare different forecasting technologies.
-Most notably, we are able to simulate future wind power production given a deterministic wind power forecast.
-Future wind power production using Monte Carlo methods, as well as the analytic form of the proposed SDE, can be used in optimal control problems involving wind power production.
-
-Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations.
-Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion and non-Gaussian approximations.
-We apply the model to Uruguayan wind power forecasts together with historical wind power production data pertaining to the year 2019.
-
-{\color{red} Change this paragraph. Discuss with the global dataset, the dataset after removing days when curtailing has been detected, the data set without curtailing and with Lamperti transform.}
-We have available a year long data set from Uruguay based on 363 observation paths, each of which is 24-hours long with observations recorded every 10 min.
-In total, it is a data set of approximately fifty thousand data points recorded in 2019.
-See Figure (\ref{fig:sample_data}).
-Data are normalized with respect to the maximum power capacity of wind power production in Uruguay, which is $\SI{1474}{\mega\watt}$.
-However, sometimes the real production is artificially modifies due to curtailing.
-This effect becomes clear when we inspect for different power production levels.
-We split the available data into low, medium and high power range.
-See Figure (\ref{fig:data_curtailing}).\\
-We identify and remove the days with curtailing, removing a total of 108 days.
-From the resulting 255 days, we use 127 days to train the system and 128 to test it.
-Also, to avoid correlation between days, we intercalate the days we use for training and testing ({\color{red} Show that 24h is enough to ensure independence}).
-
-In this paper we present the phenomenological underlying model in Section \ref{Section_2} and describe the physical constraints in Section \ref{Section_3} and how these constrains can be met.
-Then, in Section \ref{Section_4}, we will introduce an alternative formulation of the model in Lamperti space.
-In Section \ref{Section_5}, we show our parameter estimation procedure and its results in Section \ref{Section_6}.
-We compare alternative models in Section \ref{Section_7} and different forecast providers in Section \ref{Section_8}.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/5.eps}
-\includegraphics[width=0.45\textwidth]{plots/245.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/661.eps}
-\includegraphics[width=0.45\textwidth]{plots/805.eps}
-\caption{Four samples from the Uruguayan data of 2019.
-Each sample compromises of two 24-hour paths.
-In blue is an hourly wind power production forecast.
-In orange is the actual wind power production recorded in 10 minute intervals.}
-  \label{fig:sample_data}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
-\caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production.
-Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$.
-We have a total of 363 days to use.}
-  \label{fig:data_curtailing}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP.eps}
-\caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
-  \label{fig:data_after_clean}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
-\caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
-\label{fig:error_transitions}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
-\caption{Transitions after the Lamperti transform.
-The transitions now present a normal Gaussian shape.
-This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
-  \label{fig:LP_transitions}
-\end{figure}
-%---END SECTION 1---
-
-%---BEGIN SECTION 2---
-\section{Phenomenological  Model} \label{Section_2}
-
-In this section, once we analyzed the available dataset, we consider a type of phenomenological model for the normalized wind power generation forecasts which is given, in its most general form, as a stochastic process $X = \{X_t, \, t \in [0,T] \}$  defined by the following stochastic differential equation (SDE):
-
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&=  a(X_t; p_t, \dot{p}_t,\bm{\theta}) \,dt + b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \,dW_t\,, \quad t \in [0,T]  \\
-     X_0  \!\!\!&=  x_0 \in [0,1],
-  \end{array}\right. \label{eq:main}
-\end{equation}
-
-where
-
-\begin{itemize}
-\item $a(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R} $  denotes a drift function,
-\item $b(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R}^+ $  a  diffusion function,
-\item $\bm{\theta}$ is a vector of unknown parameters,
-\item $(p_t)_{t \in [0,T]}$ is a time-dependent deterministic function $[0,1]$-valued and $ (\dot{p}_t)_{t \in [0,T]}$ is its time derivative,
-\item $\{W_t, \, t \in [0,T] \}$ is a standard real-valued Wiener process.
-\end{itemize}
-
-In this work, $(p_t)_{t \in [0,T]}$ is to be considered as a deterministic forecast for the normalized wind power generation, which is provided by an official source.
-
-Our goal is to achieve a specification of the model (\ref{eq:main}) to follow closely the available normalized wind power forecasts while ensuring its unbiasedness with respect to the forecast.
-
-\subsection{Physical Constraints}
-
-Let $(p_t)_{t \in [0,T]}$ be the available prediction function for the normalized wind power, which is an input to this approach.
-To start with the model specification, first we introduce a time-dependent drift function that features the mean-reverting property as well as derivative tracking:
-\begin{equation}
-a(X_t; p_t, \dot{p}_t, \bm{\theta}) = \dot{p}_t  - \theta_t (X_t - p_t)\,,  \label{drift:meanrev-derivtrack}
-\end{equation} 
-where $ (\theta_t)_{t \in [0,T]} $ is a positive deterministic function, whose range depends on $\bm{\theta}$, as will be explained shortly.
-
-Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$.
-
- Then, the process defined by (\ref{eq:main}) with drift (\ref{drift:meanrev-derivtrack}) satisfies the two following properties: 
-\begin{itemize}
-\item it reverts to its mean $p_t$, with a time-varying speed $ \theta_t$ that is proportional to the deviation of the process $X$ from its mean,
-\item it tracks the time derivative $\dot{p}_t$.  
-\end{itemize} 
-Observe that a mean reverting model without derivative tracking exhibits consistent lags, as it is shown in Figure (\ref{fig:derivative_tracking}). See Section \ref{Section_7} for comparisons.
-
-\begin{figure}
-  %\includegraphics[width=26mm,scale=1]{}
-  \caption{insert figure showing the difference with and without derivative tracking}
-  \label{fig:derivative_tracking}
-\end{figure}
-
-The forecast and production wind power data of Uruguay are normalized with respect to the installed power capacity during the period of observation.
-Thus, the mean-reverting level lies in $[0,1]$, and the process $X$  must take values in the same interval,a requirement that is not automatically fulfilled through the derivative tracking.
-To impose that the state space of $X$ is $[0,1]$, we may choose a convenient diffusion term, and require that the time-varying parameter $ \theta_t$ satisfies an ad-hoc condition.
-
-Let $\bm{\theta} = (\theta_0,\alpha)$, and choose a state-dependent diffusion term that avoids the process exiting from the range $[0,1]$ as follows:
-  \begin{equation}
-    b (X_t; \bm{\theta} )= \sqrt{2 \theta_0 \alpha X_t (1 - X_t)}
-  \end{equation}
-  where $\alpha >0$ is a unknown parameter that controls the path variability.
-This diffusion term belongs to the Pearson diffusion family and, in particular, it defines a Jacobi type diffusion.
-It is useful to recall that (\cite[440]{foso}) a Pearson diffusion is a stationary solution to a stochastic differential equation of the form
- \begin{equation}
-    dX_t = - \theta (X_t - \mu) dt + \sqrt{2 \theta (a X_t^2 + b X_t + c)} dW_t
-  \end{equation}
-where $\theta>0$, and $a$, $b$ and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space.
-These parameters, together with $\mu$, the mean of the invariant distribution, determine the state space of the diffusion as well as the shape of the invariant distribution.
-
-An exhaustive classification of the (stationary) Pearson diffusions is presented in (\cite[440-443]{foso}) where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 \theta a x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the well-known Jacobi diffusions, so-called because the eigenfunctions of the infinitesimal generator of these processes are the Jacobi polynomials (see, for example, \cite[2860-2861]{leph}).
-
-It is worth mentioning that Jacobi diffusions have been successfully applied in several disciplines, among them econometrics (see  and references therein) and neuroscience (\cite{dotala}).
-
-However, a distinctive feature in our proposed model 
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= (\dot{p}_t  - \theta_t (X_t - p_t) ) dt +\sqrt{2 \theta_0 \alpha X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{ourmodel}
-\end{equation}
-
-is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X$ to (\ref{ourmodel}) a non-stationary and time-inhomogeneous process.
-To ensure that the process $X$ be the unique strong solution to (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the following condition:
-%has to be selected according to the following rule.
-Observe that the time derivative term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays a.s.
-inside the range $[0,1]$.
-In other words, the zero drift line defined by $a(x; p_t,\bm{\theta}) =0$, which is an attractor, must be contained inside the range $[0,1]$.
-Thus, we must have that
-%\begin{equation}
-%\frac{- |\dot{p_t}|}{p_t} \leq \theta_t \leq \frac{|\dot{p}_t|}{1- p_t}
-%\end{equation}
-%which is satisfied  by choosing a time-dependent  $\theta_t$ as follows,
-%\begin{equation}
-%\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \theta_0 >0\,. \label{theta_t}
-%\end{equation}
-\begin{equation}\label{Assumption:3}
-\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
-\end{equation}
-The proof of this theoretical statement is presented in Section \ref{Appendix}.
-
-%{\color{red} The expression for $\theta_t$ is important: $\theta_t$ depens on $t$ through $\dot{p_t}$ and $p_t$.
-Besides it is parsimonious because only one unknown parameter appear in \ref{theta_t}.
-Recall it is an upped bound for the real inequality.
-}
-
-%\subsubsection*{Change of Variables:}
-\subsection{A model specification for the forecast error}
- After applying the simple change of variables $$V_t = X_t - p_t \,,$$ we may introduce the following model for the forecast error of the normalized wind power production:
-
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dV_t \!\!\!&=  - \theta_t V_t  \, dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \, dW_t\,, \quad t \in [0,T]  \\
-   V_0  \!\!\!&=  v_0\in [-1,1] \,.
- \end{array}\right.  \label{VtSDE}
-\end{equation}
-
-%---END SECTION 2---
-
-%---BEGIN SECTION 3---
-\section{State independent diffusion: Lamperti transform} \label{Section_3}
-
-Our model (\ref{VtSDE}) for the forecast error has a diffusion term that depends on the state variable $V_t$.
-To estimate the unknown model parameters, a recommended technique is to modify the SDE (\ref{VtSDE}) by applying the so-called Lamperti transform (see \cite[40--41]{iacus1}, \cite{moma}, \cite[98--100]{saso}) to the process $V$ to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
-\\
-
-We consider the following Lamperti transformation  {\color{red} (Remind that in continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
-Besides, it can be unstable to work with low frequency.
-If the frequency of the data is too low, the Lamperti transform helps to detect this problem (in principle, it is not clear how to determine the right frequency for estimation.
-)}
-\begin{equation}
-Z_t = h(V_t) = \frac{1}{\sqrt{2 \theta_t \alpha}} \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
-\end{equation}
-where $\xi$ is an arbitrary point of the state space of the process $V$. The choice of $\xi = \frac{1}{2} - p_t$, where $p_t$ is a known input, leads to the process 
-\begin{equation}
-Z_t = h(V_t) = \frac{1}{\sqrt{2 \theta_t \alpha}} \arcsin (2(V_t + p_t) -1)\,,
-\end{equation}
-that, after applying It\^{o}'s formula on $h(V_t)$, gives the state-independent diffusion SDE
-\begin{equation}
-dZ_t = \left[  \frac{- \theta_t V_t}{ \sqrt{2 \theta_t \alpha (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \theta_t \alpha} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \right] \,dt + dW_t \,.
-\label{eq:stindepSDE}
-\end{equation}
-After replacing $V_t = \frac{\sin(\sqrt{2 \theta_t \alpha} Z_t) + 1}{2} - p_t$ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
-\begin{align}
-dZ_t & = \left[ \frac{- \theta_t (\sin(\sqrt{2 \theta_t \alpha} Z_t) + 1 - 2 p_t)}{\sqrt{2 \theta_t \alpha} \cos{(\sqrt{2 \theta_t \alpha} Z_t)}} + \frac{\sqrt{2 \theta_t \alpha} \sin{(\sqrt{2 \theta_t \alpha} Z_t)}}{2 \cos{(\sqrt{2 \theta_t \alpha} Z_t)}} \right] \,dt + dW_t \nonumber \\
-&  = \left[  \frac{\sqrt{2 \theta_t} \left( \sin(\sqrt{2 \theta_t \alpha} Z_t) (\alpha - 1) + (2 p_t -1 ) \right)}{2 \sqrt{\alpha} \cos{(\sqrt{2 \theta_t \alpha} Z_t)}}  \right] \,dt + dW_t \,. 
-\end{align}
-
-%\begin{align}
-%    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \alpha \theta_t \sin (Z_t)   }{\cos (Z_t)} \ dt + \sqrt{2 \alpha \theta_t} dW_t \\
-%    Z_0&=z_0 \,,
-%\end{align}
-%where the Lamperti trasform is given by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
-
-We can see in Figure (\ref{fig:skew_after_lamperti}) the effect of the Lamperti transformation upon the forecast error data. 
-The Lamperti transformation has greatly reduced the forecast error skewness, ensuring that the process stays in the range $[0,1]$.
-Therefore, in this case, the transition densities of the process Z can be adequately approximated through Gaussian densities.
-%---END SECTION 3---
-
-%---BEGIN SECTION 4---
-\section{Likelihood in $V$ space} \label{Section_4}
-
-\subsection{Likelihood}
-
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t >0 \}$ is sampled at $N$ equispaced discrete points with length interval $\Delta_N$, and let $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ denote this random sample.
-
-Let $\rho_i(v \vert v_{j, t_{i-1}} ; \bm{\theta})$ denote the conditional probability density of $V_{j, t_i}$ given $V_{j, t_{i-1}} = v_{j, t_{i-1}}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha)$ are the unknown model parameters.
-
-The It\^{o} process $V$ defined by the SDE (\ref{VtSDE}) is Markovian, then the likelihood function of the data can be written as the following product of transition densities:  
-%Consider the set of $M$ paths with $N$ observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$, observed in $\Delta_N$ intervals.
-\begin{equation}
-\mathcal{L}(\bm{\theta},\delta; V^{M,N}) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j, t_i}| V_{j, t_{i-1}}} ; p_{[t_{i-1}, t_{i}]},  \bm{\theta} )  \, \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
-\label{likelihood}
-\end{equation}
-
- {\color{red} In \ref{likelihood} modify the expression for $\rho_0$ contemplating the lag, say $\delta$, between the time when the forecast is done and the first time of forecasting.
-$\rho_0$ can be written as a conditional density between these two times.
-Once $\theta_0$ and $\alpha$ have been estimated, one could estimate $\delta$.}
-
-The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized, for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}, \cite[61-68]{saso}):
-
-\begin{align}
-\frac{ \partial f }{\partial t } & \rho_i(v_{j,i} ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} )= - \frac{\partial}{ \partial v} (- \theta_t v \, \rho_i(v ,t_{j,i} \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) ) \nonumber \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( 2 \theta_t \alpha (v+ p_t) (1 - v- p_t) \, \rho_i(v ,t_{j,i} \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) )\,,  \label{eq:fpk}
-\end{align}
-subject to the initial conditions $\rho_{i-1}(v , t_{j, i-1} , \bm{\theta} ) = \delta(v - V_{j, t_{i-1}}) \,,$ where $ \delta(v - V_{j, t_{i-1}})$ is the Dirac-delta generalized function centered at $ V_{j, t_{i-1}}\,.$
-
-Closed-form solutions to initial-boundary value problem for SDEs can be obtained only in a few cases.
-Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
-Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.
-Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.
-
-\subsection{Approximate Likelihood}
-
-A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints which give rise to asymmetric forecasting errors as seen in figure (\ref{fig:skew_data}).\\
-
-We propose a proxy transition density.
-We match the moments of our SDE model with that of the proxy density.
-Using It\^o formula, we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
-\begin{equation}
-\frac{d \mathbb{E}[ V^k_t]}{dt} = - k \theta_t \mathbb{E}[ V^k_t] + \frac{k(k-1)}{2} \mathbb{E}[ V^{k-2}_t  b(V^k_t;\theta_t, \alpha)]
-\end{equation}
-
-For $t\in [t_{n-1}, t]$, the first two moments are given by
-\begin{align}
-\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t   \nonumber \\
-\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta_t(1+\alpha) + 2\alpha\theta_t m_1(t)(1-2p_t)  \nonumber \\
-&\quad + 2 \alpha\theta_t p_t (1-p_t) \,,
-\end{align}
-with initial conditions $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2 \,.$
-
-And for the state independent diffusion formulation, similarly, we  obtain a system of ODEs to determine the centered moments of the Lamperti transformed process $V_t$.
-Due to the non-linearity in the drift, we can only approximate the centered moments by the following ODEs,
-\begin{align}
-\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\alpha) - \theta (1-2 p_t) \nonumber \\
-\frac{d var(t)}{dt} &=  2 var(t) \theta_t (2p_t - 1 ) \tan(m_1 (t)) \sec(m_1 (t))   \nonumber \\
-& \quad + \theta_t (\alpha - 1) \sec^2(m_1 (t))  + 2 \theta_t \alpha \,.
-\end{align}
-
-A suitable candidate for a proxy transition density is a Beta probability distribution as it is compactly supported and can morph into symmetric and asymmetric shapes.
-{\color{red} Move this sentence to next section.}
-
-\subsubsection*{ Moment Matching}
-To approximate the transition densities of  the process $V_t$ by a Beta distribution, we match its moments with the shape parameters $\xi_1, \xi_2$ of a Beta proxy density on $[-1,1]$.
-The any moment of the process $V_t$ is  given by solving the corresponding ODE system  for the $k^{th}$  moment,
-
-The shape parameters are given by
-\begin{equation}
-\xi_1 = - \frac{(1+\mu_t )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2}\,, \quad \xi_2=  \frac{(\mu_t-1 )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2} \,, \label{param_transformed_beta}
-\end{equation}
-where $\mu_t = m_1 (t)$ and $\sigma_t^2= m_2 (t)- m_1 (t)^2\,.$
-
-\subsection{Optimization} \label{opt_sec}
-{\color{red} Rewrite the discussion to obtain fast initial estimate for the two unknow parameters.}
-
-To initialize the optimization process for the likelihood function of the process $V$, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$: {\color{red} Add explanation regarding the motivation for this objective function.}
-
-\begin{equation}
-\theta_0\approx\arg\min_{\theta} \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2,
-\label{inital_theta}
-\end{equation}
-
- where $v_{i,j}=x_{i,j}-p_{i,j}$,  $x_{i,j}$ is historical wind power production and $p_{i,j}$ is the wind power forecast.
-
- By assuming ergodicity {\color{red} not ergodicity, instead simply for the \textbf{quadratic variation formula}.}, we can obtain a first estimate on the product of the parameters as follows,
-
-\begin{equation}
-\theta_0 \alpha \approx \frac{1}{2M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{ \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
-\end{equation}
-
-Solving for $\alpha$, we have both first estimates and we can also estimate $\delta$ solving the problem
-
-\begin{equation}
-\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
-\label{likelihood_delta}
-\end{equation}
-
-With our estimations of $\bm{\theta}$, we can start the inference processes as follows:
-\begin{enumerate}
-\item[Step 1.]  initialize;
-\item[Step 2.]  optimize the log-likelihood function using  Nelder-Mead optimization algorithm on a mini-batch sampled with replacement;
-\item[Step 3.] check if  accuracy threshold is reached. Else, re-initialize the optimization with the most recent result on a larger mini-batch.
-\end{enumerate}
-%---END SECTION 4---
-
-%---BEGIN SECTION 5---
-\section{Model Comparison} \label{Section_5}
-
-We compare two candidate models to find the best-fit that maximizes the retained information,
-\begin{itemize}
-  \item Model 1: This model does not feature derivative tracking.
-  \begin{align}
-  dX_t &=  - \theta_0 (p_t-X_t) \  dt + \sqrt{2 \theta \alpha X_t (1-X_t)} \  dW_t   \nonumber \\ %\quad t > 0
-  X_0 & = x_0 \,, \label{M0}
- \end{align}
-  with $\theta_t= \theta_0 $.
-
-%  \item Model 1: This model features derivative tracking, i.e.
-it is equivalent to (\ref{model:derivative_tracking_X}) with a diffusion term that is forecast dependent by including the term $p_t(1-p_t)$.
-%  \begin{equation}
-%  \begin{split}
-%  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha p_t(1-p_t)(V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
-%  V_0 & = v_0
-%  \end{split}\label{M2}
-%  \end{equation}
-%  with $\theta_t$ given by (\ref{theta_t}).
-This model has been used by [ insert ref ] and [ insert ref ].
-Initial interest in this model stems from interest in long-term stationary solution, which may exists  if the forecast is constant.
-However, this is almost never occurs and thus including the term $p_t(1-p_t)$ is irrelevant.
-Additionally, the term $p_t(1-p_t)$ leads the model to become deterministic when the forecast is at the boundaries (i.e.$p=1$ or $p=0$)  which is not realistic.
-We have run computations on this model and the results were not satisfactory.
-Therefore, we exclude this model from further discussions.
-%
-
-  \item Model 2: This model features derivative tracking, i.e. it is equivalent to (\ref{model:derivative_tracking_X}).
-  \begin{align}
-  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t   \nonumber \\ %\quad t > 0
-  V_0 & = v_0 \,, \label{M2}
-  \end{align}
-  with $\theta_t$ given by (\ref{theta_t}).
-\end{itemize}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{cccc}
-\toprule
-Model   &  parameters $(\theta_0, \alpha,\delta)$   & AIC & BIC \\ \midrule
-Model 1 &  $(\add,\add) $    &  \add   &  \add   \\
-Model 2 &   $(1.2,0.1,0.6)$   &  \add   &   \add    \\ 
-\bottomrule
-\end{tabular}
-\caption{We compare the different models based on information criterion. \add }
-\label{tab:model_comparison}
-\end{table}
-%---END SECTION 5---
-
-%---BEGIN SECTION 6---
-\section{Forecast Provider Comparison} \label{Section_6}
-We compare forecasts from two different companies for the same period.
-\begin{table}[H]
-\centering
-\begin{tabular}{cccc}
-\toprule
-Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \midrule
-Provider A  &  $(\add,\add)$      &  \add   & \add    \\
-Provider B  & $(\add,\add) $  &  \add   &   \add  \\ 
-\bottomrule
-\end{tabular}
-\caption{\add}
-\label{tab:forcast_comparison}
-\end{table}
-In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.
-
- \begin{table}[H]
- \centering
- \begin{tabular}{cccc}
- \toprule
- Model & parameters $(\theta_0, \alpha)$  \\
- \midrule
- \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ 
- \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \bottomrule
- \end{tabular}
- \caption{ \add confidence interval obtained using bootstrap}
- \label{tab:freq_comparison}
- \end{table}
-%---END SECTION 6---
-
-%---BEGIN SECTION 7---
-\section{Results} \label{Section_7}
-
-\subsection{Initial guesses}
-
-Following the instruction for the initial guesses from section $\ref{opt_sec}$, we get the initial guesses $(\theta_0,\alpha,\delta)\approx(1.2,0.1,0.6)$.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/initial_guess/initial_theta_1.eps}\quad\includegraphics[width=0.42\textwidth]{plots/initial_guess/initial_theta_2.eps}
-\caption{Value function from ($\ref{inital_theta}$) as a function of different $\theta_0$ values. We can observe that the function if flat for a wide range.}
-\end{figure}
-
-\subsection{Negative Log-Lihelihood}
-
-We plot the Negative Log-Likelihood as a function of the parameters.
-The plots can be seen in Figure (\ref{fig:neg-LL}).
-We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood.eps}\quad\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_refined.eps}
-\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_more_refined.eps}
-\caption{Negative Log-Likelihood for different domains.}
-\label{fig:neg-LL}
-\end{figure}
-
-\subsection{Main guesses}
-
-We were able to obtain the following for 
-\begin{table}[H]
-\centering
-\begin{tabular}{|c|c|}
-\hline
-Formulation   &  parameters $(\theta_0, \alpha,\delta)$    \\ \hline
-Without Lamperti transform &   $(1.2,0.1,0.6) \pm (\add , \add) $   \\ \hline
-With Lamperti transform &   $(12,0.29) \pm (\add , \add)  $   \\ \hline
-\end{tabular}
-\caption{We compare the parameters obtained in both the original and Lamperti space. Parameters have been obtained based on \add data points from the Uruguayan pertaining to the year 2019\add .}
-\label{tab:model_comparison_2}
-\end{table}
-
-{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models (if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.)}
-
-{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
-How many data we need to achive enough accuracy for the estimates of the two parameters?
-Generally, such accuracy is application dependent}
-
- We are able to obtain the parameters based on the complete data sets. Using the different models variations, we are able to simulate wind power production given a forecast. We see in figures ()-()
-five possible wind power production paths for each model.\\
-
-In Figures ()-(), we show point-wise empirical confidence bands for the different models.
-
-\begin{figure}[H]
-  \includegraphics[width=56mm,scale=1]{plots/alpha_conv_beta.png}
-  \includegraphics[width=56mm,scale=1]{plots/theta_conv_beta.png}
-  \caption{We show self-convergence of our algorithm applied to model $2$. We conlcude that the rate  matches that of of Monte Carlo. Data is from Uruguay pertaining to year 2019.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/2.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/3.eps}
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/4.eps}
-\caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
-Forecast is from Uruguay pertaining to  year 2019.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/2.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/3.eps}
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/4.eps}
-\caption{{\color{red}Pending add legend and choose better colors.}We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
-Actual production plotted in retrospect.
-Forecast and data is from Uruguay pertaining to  year 2019.}
-\end{figure}
-%---END SECTION 7---
-
-%---BEGIN SECTION 8---
-\section{Conclusions} \label{Section_8}
-
-We have proposed a method to produce stochastic wind power forecasts based on parametric SDEs.
-This method is agnostic of the wind power forecasting technology.
-Using this method, we were able to simulate future wind power production paths and obtain confidence bands.
-We conclude that Model 2 is a best-fit model.
-It features time-derivative tracking of the forecast, time-dependent mean reversion parameter, and a more natural diffusion term.
-Moreover, the model preserves the asymmetry of wind power forecast errors and their correlation structure.
-
-We were also able to compare two different forecast providers with respect to their real-world performance on the aggregated data set and on specific wind farm sites.
-Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.
-%---END SECTION 7---
-
-%---BEGIN APPENDIX---
-\section{Appendix} \label{Appendix}
-
 \section{The model}
@@
 \end{Thm}
+
 \begin{proof}
@@
  \end{proof}
+
+\textcolor{red}{When using Lamperti, the form }
 
@@
 Otherwise the Lamperti transform is not valid if the state space of $X$ is $[0,1]$.
+\begin{thebibliography}{00}
 
-%---REFERENCES---
+\bibitem{Alf} Alfonsi, A. (2015) Affine diffusions and related processes: simulation, theory and applications. {\it  Springer, Cham; Bocconi University Press, Milan, 2015}. 
+\bibitem{KarShr} Karatzas, I. and Shreve, S. E. (1991),  Brownian motion and stochastic calculus {\it Springer-Verlag, New York}.
 
-\nocite{*}
-
-%\printbibliography
-\printbibliography[keyword={Wind-SDE},title={References}]
-
+\end{thebibliography}
 \end{document}

### 2020-03-28 LaTeX_Code/presentation/Palacio_WindPower.tex
I cleaned a bit the directories

--- 2019-10-01 LaTeX_code/presentation/DELFT_pres.tex
@@
 
-\title{On the Uncertainty of Wind Power Generation}
+\addtobeamertemplate{navigation symbols}{}{%
+    \usebeamerfont{footline}%
+    \usebeamercolor[fg]{footline}%
+    \hspace{1em}%
+    \insertframenumber/\inserttotalframenumber
+}
+
+\setbeamercolor{footline}{fg=blue}
+\setbeamerfont{footline}{series=\bfseries}
+
+\title{Uncertainty Quantification in Wind Power Forecasting}
 
@@
 \setbeamercolor{background canvas}{bg=blue!10}
-\date{}
+\date{October 4th, 2019}
 
 \begin{frame}
+\center
+  \includegraphics[width=30mm,scale=1]{KAUST_Logo.pdf}\quad 
+  \includegraphics[width=40mm,scale=1]{rwth_UQ.png}\quad 
+  \includegraphics[width=30mm,scale=1]{UParis_13.png} \quad
+ \vspace*{0.2in}
 \titlepage
-\center
-  \includegraphics[width=40mm,scale=1]{KAUST_Logo.pdf}\quad 
-  \includegraphics[width=60mm,scale=1]{rwth_UQ.png}\quad 
-  \includegraphics[width=40mm,scale=1]{UParis_13.png} \quad
 \end{frame}
@@
 
-\begin{frame}\frametitle{Status quo }
+\begin{frame}\frametitle{Current State of Affairs}
   Wind power forecasts can be generally categorized as follows:
@@
     \item artificial intelligence methods
-    \item spatial correlation methods
     \item other hybrid approaches
   \end{itemize}
- The output of such methods is usually a \textcolor{red}{deterministic forecast}.
-Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles.
-However, little has been done in terms of producing \textcolor{red}{data driven probabilistic forecasts} based on the real-world performance of forecasting models.
+ The output of such methods is usually a \textcolor{red}{deterministic forecast}. \\
+ \bigskip 
+ Occasionally probabilistic forecasts are produced through uncertainty propagation or through forecast ensembles. \\
+  \bigskip 
+ However, there is a lacking in  \textcolor{red}{data driven stochastic forecasts} based on the real-world performance of forecasting models.
 \end{frame}
@@
 \begin{frame}\frametitle{Data}
-This is a year long data set from Uruguay based on \textbf{1000 72-hour long paths of observations every 10 min \textcolor{red}{ ($\sim$ half a million data points)}} recorded in 2018.
+This is a year long data set from Uruguay based on \textbf{1000 72-hour long paths with observations recorded  every 10 min \textcolor{red}{ ($\sim$ half a million data points)}} recorded in 2018.
 \begin{figure}
@@
 \begin{frame}\frametitle{Model}
-Our goals are to
+
+Our goals are to produce a stochastic forecast of wind power production forecasting errors while:
 \begin{itemize}
-  \item Generate a probabilistic forecast centered around a given deterministic forecast, i.e. unbiased with respect to the deterministic forecast.
-  \item Capture the dynamics and correlation structure.
-  \item Capture the skew nature of forecast errors.
-  \item Be forecasting technology agnostic. Thus, compatible with future forecasting technology.
-  \item Learn from historical power production data.
+  \item Capturing the dynamics of the forecast error process.
+  \item Capturing the skew nature of forecast errors.
+  \item Being forecasting-technology agnostic. Thus, compatible with past and future forecasting-technology.
+  \item Learning from historical power production data.
 \end{itemize}
@@
 We propose to model wind power forecasts errors using \textcolor{red}{parametric stochastic differential equations (SDEs)} whose solution defines a stochastic process.
-This resultant stochastic process describes the time evolution dynamics of wind power forecast errors.
+This resultant stochastic process describes the time evolution dynamics of wind power forecasting errors.
 \begin{equation}
 \begin{split}
-dX_t &= a(X_t; p_t,\bm{\theta}) dt + b (X_t;p_t, \bm{\theta} ) dW_t \quad t > 0 \\
+dX_t &= a(X_t; p_t, \dot{p}_t,\bm{\theta}) dt + b (X_t;p_t, \bm{\theta} ) dW_t \quad t > 0 \\
 X_0 & = x_0
@@
 \begin{itemize}
-\item $a(\cdot; \bm{\theta}):[0,1] \to \R $  a drift function.
-\item $b (\cdot; \bm{\theta} ):[0,1] \to \R$  a  diffusion function.
+\item $a(\cdot; p_t, \dot{p}_t,\bm{\theta}):[0,1] \to \R $  a drift function.
+\item $b (\cdot;p_t, \bm{\theta} ):[0,1] \to \R$  a  diffusion function.
 \item $\bm{\theta}$: a vector of parameters.
-\item $p_t$ time-dependent scalar value.
+\item $p_t$ time-dependent scalar value and $ \dot{p}_t$ is its time derivative at time $t$. (in our case  $p_t$ is a deterministic forecast).
 \item $W_t$: Standard Wiener random process in $\R$.
@@
 
-\begin{frame}\frametitle{Model}
-\textcolor{blue}{Answer:}
-Let $\bm{\theta} = (\textcolor{red}{\theta_0}, \textcolor{red}{\alpha})$
+\begin{frame}\frametitle{How do we choose an appropriate drift and diffusion functions?}
+
+Let $\textcolor{red}{ \bm{\theta} }= (\textcolor{red}{\theta_0}, \textcolor{red}{\alpha})$
 \begin{enumerate}
@@
   \begin{equation}
-    a(x; \bm{\theta})=  \dot{p_t} - \theta_t(x - p_t)
+    a(x; p_t,\textcolor{red}{ \bm{\theta} })=  \dot{p_t} - \theta_t(x - p_t)
   \end{equation}
-where $\theta_t$ is a time-dependent parameter that controls the speed of reversion.
+where $\theta_t>0$ is a time-dependent parameter that controls the speed of reversion.
   \item We want a diffusion term that vanishes at the boundaries to prevent the process from escaping the region $[0,1]$.
   \begin{equation}
-    b (x; \bm{\theta} )= \sqrt{2 \theta_t \textcolor{red}{\textcolor{red}{\alpha}} x (1-x)}
+    b (x; p_t,\textcolor{red}{ \bm{\theta} } )= \sqrt{2 \theta_t \textcolor{red}{\textcolor{red}{\alpha}} x (1-x)}
   \end{equation}
-  where $\textcolor{red}{\alpha}$ is a constant parameter that controls the path variability.
+  where $\textcolor{red}{\alpha} >0$ is a constant parameter that controls the path variability.
 
@@
 \begin{equation}
-\theta_t = \max \left( \textcolor{red}{\theta_0} \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ) \label{theta_t}
+\theta_t = \max \left( \textcolor{red}{\theta_0} \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \textcolor{red}{\theta_0} >0 \label{theta_t}
 \end{equation}
@@
 \begin{equation}
-\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}}, \bm{\theta})  \rho (V_{j,0})
+\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}},\textcolor{red}{ \bm{\theta} })  \rho (V_{j,0})
 \label{likelihood}
@@
 \begin{split}
-\frac{ \partial f }{\partial t } & (y ,t | x , s, \theta_t, \textcolor{red}{\alpha} )= - \frac{\partial}{ \partial y} ( a( y;\dot{p}_t , p_t, \theta_t ) f( y ,t | x , s, \theta_t , \textcolor{red}{\alpha} ) ) \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b(y;\theta_t, \textcolor{red}{\alpha}  )  f( y ,t | x , s, \theta_t , \textcolor{red}{\alpha} )  ) \quad  t < s\\
+\frac{ \partial f }{\partial t } & (y ,t | x , s, \textcolor{red}{\theta_0} , \textcolor{red}{\alpha} )= - \frac{\partial}{ \partial y} ( a( y;  p_t, \dot{p}_t, \textcolor{red}{\theta_0} ) f( y ,t | x , s, \textcolor{red}{\theta_0}  , \textcolor{red}{\alpha} ) ) \\
+& + \frac{1}{2} \frac{\partial^2}{ \partial y^2} ( b^2(y; p_t, \textcolor{red}{\theta_0}, \textcolor{red}{\alpha}  )  f(y ,t | x , s,\textcolor{red}{\theta_0} , \textcolor{red}{\alpha} ) ) \quad  t < s\\
 \end{split}
@@
 \begin{frame}\frametitle{Moment Matching}
-Instead of solving for exact transition densities by the Fokker-Planck, we propose a \textcolor{red}{proxy transition density}.
-We match the moments of our SDE model with that of the proxy density.
-Using Ito, we arrive at the following iterative ODEs.
+We propose a \textcolor{red}{proxy transition density}. We match the moments of our SDE model with that of the proxy density. Using It$\hat{o}$ formula, we arrive at the following iterative ODEs.
 
@@
 \frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t \\
-\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta(1+\textcolor{red}{\alpha}) + 2\textcolor{red}{\alpha}\theta_t m_1(t)(1-2p_t) + 2 \textcolor{red}{\alpha}\theta_t p_t (1-p_t)\\
+\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta_t(1+\textcolor{red}{\alpha}) + 2\textcolor{red}{\alpha}\theta_t m_1(t)(1-2p_t) + 2 \textcolor{red}{\alpha}\theta_t p_t (1-p_t)\\
 \end{split}
 \end{equation}
-with initial conditions, $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2$ where $t_{n-1}$ is the time of the previous obseravtion and $v_{n-1}$ is its value.
+with initial conditions, $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2$.
 
@@
 \begin{enumerate}
-  \item \textcolor{red}{Sample} a random mini-batch of transitions and their associated forecast and parameters.
+  \item \textcolor{red}{Sample} a mini-batch of transitions randomly with their associated forecast and parameters.
   \item \textcolor{red}{Solve} the ODE system for every transition to obtain the moments.
@@
       \includegraphics[width=75mm,scale=1]{simulated/24hr/1178.pdf}
-      \caption{We simulate five possible future wind power production paths using the obtain optimal parameters $(\textcolor{red}{\theta_0}, \textcolor{red}{\alpha} )=(12,0.3)$ }
+      \caption{We simulate five possible future wind power production paths using the obtained optimal parameters $(\textcolor{red}{\theta_0}, \textcolor{red}{\alpha} )=(12,0.3)$ }
     \end{figure}
@@
       \includegraphics[width=75mm,scale=1]{confidence_intervals/24hr/820.pdf}
-       \caption{We obtain confidence intervals for future wind power production using the obtain optimal parameters $(\textcolor{red}{\theta_0}, \textcolor{red}{\alpha} )=(12,0.3)$.
+       \caption{We obtain confidence intervals for future wind power production using the obtained optimal parameters $(\textcolor{red}{\theta_0}, \textcolor{red}{\alpha} )=(12,0.3)$.
 Actual production plotted in retrospect.
@@
 
-\begin{frame}\frametitle{State-Independent model}
-The model we have demonstrated previously is state-dependent, that is the diffusion of the SDE depends on the state.
+\begin{frame}\frametitle{State-Independent Diffusion Formulation}
+The model we have demonstrated previously is \textcolor{red}{state-dependent diffusion} formulation, that is the diffusion of the SDE depends on the state.
 \begin{equation}
@@
 
-Why are we interested in a state-independent model? Because it's more tractable.\\
-We apply a \textbf{Lamperti transform} to obtain the following state-independent system,
+Why are we interested in a state-independent diffusion formulation? Because it's more tractable and numerically stable.\\
+We apply a \textbf{Lamperti transform} to obtain the following \textcolor{red}{state-independent diffusion} SDE,
 
@@
   \begin{split}
-    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \textcolor{red}{\alpha} \theta_t \sin (Z_t)   }{\cos (Z_t)} + \sqrt{2 \textcolor{red}{\alpha} \theta_t} dW_t \\
+    dZ_t&= \frac{- \theta_t (1+ \sin(Z_t) - 2p_t) + \textcolor{red}{\alpha} \theta_t \sin (Z_t)   }{\cos (Z_t)} \ dt + \sqrt{2 \textcolor{red}{\alpha} \theta_t} dW_t \\
     Z_0&=z_0
@@
 
-\begin{frame}\frametitle{Data Skewness after Lamperti transformation}
-As stated before, the state-independent SDE follows a Lamperti transformed process $Z_t$ give by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
+\begin{frame}\frametitle{Data Skewness after Lamperti Transformation}
+As stated before, the state-independent diffusion SDE follows a Lamperti transformed process $Z_t$ given by $Z_t = \arcsin \left( \frac{1}{2} \left( V_t+p_t \right) - 1 \right) $.
 \begin{figure}
@@
 
-\begin{frame}\frametitle{State-Independent model}
+\begin{frame}\frametitle{State-Independent diffusion formulation}
 Similarly, we try to obtain a system of ODEs to determine the centered moments of the Lamperti transformed process $V_t$.
@@
 \frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\textcolor{red}{\alpha}) - \theta (1-2 p_t) \\
-\frac{d v(t)}{dt} &=  2 v(t) \theta_t (2p_t - 1 ) \tan(x) \sec(x) + \theta_t (\textcolor{red}{\alpha} - 1) \sec^2(x)  + 2 \theta_t \textcolor{red}{\alpha}\\
+\frac{d var(t)}{dt} &=  2 var(t) \theta_t (2p_t - 1 ) \tan(m_1 (t)) \sec(m_1 (t)) + \theta_t (\textcolor{red}{\alpha} - 1) \sec^2(m_1 (t))  + 2 \theta_t \textcolor{red}{\alpha}\\
 \end{split}
 \end{equation}
-These are not exact moment ODEs, however they are accurate enough for small time intervals.
+with initial conditions, $m_1(t_{n-1})= v_{n-1}$ and $var(t_{n-1})= v_{n-1}^2 - v_{n-1}$.\\
+\bigskip 
+\textcolor{red}{These are not exact ODEs for the centered moments}, however they are accurate enough for small time intervals. 
 \end{frame}
 
-\begin{frame}\frametitle{Inference Results}
-\begin{figure}
-  \includegraphics[width=70mm,scale=1]{plots/alpha_conv_beta.pdf}
-  \includegraphics[width=70mm,scale=1]{plots/theta_conv_beta.pdf}
-    \caption{We have self-convergence of our algorithm in the Lamperti space at a rate that matches the convergence rate of Monte Carlo.}
-\end{figure}
-\end{frame}
-
-\begin{frame}\frametitle{Model comparison}
+\begin{frame}\frametitle{Result Comparison in the Different Spaces}
 \begin{table}[]
@@
 \hline
-Model   &  parameters $(\textcolor{red}{\theta_0}, \textcolor{red}{\alpha})$    \\ \hline
-state-dependent &   (12,0.3)    \\ \hline
-state-independent &   (14,0.29)     \\ \hline
+Formulation   &  parameters $(\textcolor{red}{\theta_0}, \textcolor{red}{\alpha})$    \\ \hline
+Without Lamperti transform &   $(12,0.3) $   \\ \hline
+With Lamperti transform &   $(12,0.29)  $   \\ \hline
 \end{tabular}
-\caption{We compare the parameters obtain in both the original and Lamperti space. }
+\caption{We compare the parameters obtained in both the original and Lamperti space. }
 \label{tab:model_comparison}
@@
 
-\begin{frame}\frametitle{Concluding remarks}
+\begin{frame}\frametitle{Concluding Remarks}
 We were able to:
@@
   \item develop a forecasting technology agnostic method.
-  \item capture skewness of the error process and its correlation structure.
+  \item capture skewness of the error process and its dynamics.
 \end{itemize}
@@
 \begin{itemize}
-\item Alhaddad, W. ,  Kebaier, A. , \& Tempone, R. (2019). Stochastic Wind Power Forecasting. Coming soon to  arXiv.
+\item Alhaddad, W. ,  Kebaier, A. , \& Tempone, R. (2019). Stochastic Wind Power Forecasting. In preparation.
 \item  M\o ller, J.

### 2020-03-28 LaTeX_Code/reports/demo.tex
I cleaned a bit the directories

\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{lmodern}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

\setbeamertemplate{caption}[numbered]

\title{On the Uncertainty of Wind Power Generation\\ demo}
\subtitle{ Waleed Alhaddad}

\begin{document}
\setbeamercolor{background canvas}{bg=blue!1}

\begin{frame}{Uncertainty in Wind Power production}
Reliable wind power generation forecasting is crucial to:
\begin{itemize}
\item  Meet energy demand through renewable power sources.
\item  Energy trading of future excess power.
\item Design of Investment strategies.
\end{itemize}
We would like to:
\begin{itemize}
\item  Simulate forecast error and quantify its uncertainty.
\item  Calibrate a forecast model for  optimal dispatch of electric power.
\end{itemize}
Our model is based on:
\begin{itemize}
\item Parametric Stochastic Differential Equations.
\item Continuous optimization of approximate Maximum Likelihood.
\end{itemize}
\end{frame}

\begin{frame}{Uncertainty in Wind Power production}
\begin{minipage}{0.4\textwidth}
Prediction error of Wind Power production can be modeled by a parametric SDE,
		\begin{equation*}
		\begin{split}
		dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} dW_t  \\ %\quad t > 0
		V_0 & = v_0
	\end{split}
	\end{equation*}
	where $V_t$ is an error stochastic process, $p_t$ is a given wind power forecast and $(\alpha, \theta)$ are parameters to the model
\end{minipage}%
\begin{minipage}{0.6\textwidth}
		\begin{figure}
			\includegraphics[width=0.7\linewidth]{plots_SGD/0.pdf}\\
			\hskip 125pt
			\includegraphics[width=0.7\linewidth]{plots_SGD/820.pdf}
			\caption{Example of Wind power production simulation and confidence intervals.}
			\end{figure}
\end{minipage}
\end{frame}

\begin{frame}\frametitle{Uncertainty in Wind Power production}
\noindent
\begin{minipage}[t]{0.5\textwidth}
\hskip 10pt
Parameters of the model are inferred using optimization techniques of approximate transition likelihood functions.
\begin{equation*}
\mathcal{L}(\bm{\theta};V) =\prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j,i+1}|V_{j,i}}, \bm{\theta})  \rho (V_{j,0})
\end{equation*}
Where  $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ is a set of M paths with N observations observed in intervals of time $\Delta_N$.
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\begin{figure}
\includegraphics[width=0.8\linewidth]{plots_SGD/ISO_833_inter=427.pdf}
   \caption{Likelihood of sample paths. Point of optimality shown in blue.}
\label{samples}
\end{figure}
\end{minipage}
\end{frame}

\end{document}

### 2020-03-28 LaTeX_Code/reports/old_reports/pres2.tex
I cleaned a bit the directories

\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{color}
\usepackage{tabularx}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

\title{Sequential Monte Carlo And  its Applications}
\subtitle{Renzo Caballero \& Waleed Alhaddad}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}\frametitle{Introduction: Sequential Monte Carlo (SMC)}
We are interested in sampling from a "hard to sample" distribution  $\pi (\cdot): E \rightarrow [0,1] $. Then we find a sequence of distributions $\{\pi_n  \}_{n\in \T}$ where $\T = \{ 1,2, \ldots , N  \}$  such that $\pi_n = K_{n-1,n}\pi_{n-1} $ and $\pi = \pi_N $. The general  procedure is as follows:
\begin{enumerate}
\item Apply Importance Sampling sequentially (SIS)
\item A resampling step to control the variance of the SIS.
\item Compute probability weights corresponding  to the next distribution using a proposal  density.
\item Compute a quantity of interest using the weights of $\pi_N$.
\end{enumerate}
\end{frame}

\begin{frame}\frametitle{SMC Applications }

SMC has many applications and particle filtering is one of the most well known. However, SMC is a general class of algorithms and here we will present other areas where it could be applied. The applications presented here are:
\begin{itemize}
\item SMC for sampling from difficult distributions.
\item SMC in  the  Bayesian  framework
\item SMC for rare event sampling from difficult distributions.
\end{itemize}
A distribution may be  considered difficult if:
\begin{itemize}
\item Its parametric form has many sharp peaks and valleys.
\item It attains mass in a tiny space in a high dimensional setting. 
\end{itemize}

\end{frame}

\begin{frame}\frametitle{SMC for sampling }
We would like to sample from a difficult distribution $\pi (x)$. We use tempering to construct a sequence of functions $\{ \pi (x)^\eta \}_{\eta \in \{ \frac{1}{N}, \frac{2}{N}, \ldots , 1 \}}$ tending to  our target  $\pi (x)$.\\
The method consists of the following steps:
\begin{itemize}
\item STEP 1:  Importance Sampling  (SIS)
\item STEP 2: Resampling.
\item STEP 3: Obtaining  a quantity of interest

\end{itemize}
\end{frame}

\begin{frame}\frametitle{SMC for sampling }
\textbf{ STEP 1: Applying Sequential Importance Sampling  (SIS)}\\
For $j=1$
\begin{enumerate}
\item[§1.1]  We choose a proposal density   $\kappa (x) $.
\item[§1.2] Sample IID $X_1^{(i)} \sim\kappa (x)$  for $i =1,2,\ldots, M$.
\item[§1.3] Compute the weights $w^{(i)}_1= \frac{ \pi (X^{(i)})^{1/N}}{\kappa (X^{(i)}) }$\\
\end{enumerate}
For $ 1 < j \leq N  $
\begin{enumerate}
\item[§1.4]  We choose  $\pi_{j-1}(x)$  as our  proposal density.
\item[§1.5] Compute the weights $w^{(i)}_j= \frac{\pi_{j}(X_1^{(i)})}{\pi_{j-1}(X_1^{(i)})}$
\item[§1.6] Normalize the weights, $\tilde{w}^{(i)}_j = \frac{w^{(i)}_j}{\sum_{i=1}^M w^{(i)}_j}$ 
\end{enumerate}
\end{frame}

\begin{frame}\frametitle{SMC for sampling }
\textbf{STEP 2: Resampling }\\
Next,  we aim to place more samples in our area of interest , and in this case, it is  where the  probability is high. Hence, we resample the samples  associated with large weights.\\
\begin{enumerate}
\item[§2.1] Compute the Effective Sample Size $ESS= \frac{1}{\sum_{i=1}^M (\tilde{w}^{(i)}_j )^2 }$ 
\item [§2.2] Given a threshold $T \in [0,M]$ we check if $ESS < T$: 
\begin{enumerate}
\item[§2.2.1]  Sample IID $\tilde{X}_j  \sim  multinomial(M,\underbar{w}_j)$  where $\underbar{w}_j=(\tilde{w}^{(1)}_j , \tilde{w}^{(2)}_j ,\tilde{w}^{(3)}_j ,\ldots, \tilde{w}^{(M)}_j )^{tr} $ and remove duplicated samples.
\item[§2.2.2]  For all $i \leq M$, set the weights $ \tilde{w}_j^{(i)} = \frac{1}{M} $
\end{enumerate}
\end{enumerate}
\textbf{STEP 3: Obtaining quantity of interest  QoI }\\
Now we have all the pairs $(\tilde{w}_N^{(i)},X_N^{(i)} )$, we can directly approximate a  QoI  in the following way, 
\begin{equation}
\E [ \psi (x)] \approx \sum_{i=1}^M \tilde{w}_N^{(i)}  \psi (X_N^{(i)})
\end{equation}

\end{frame}

\begin{frame}\frametitle{Example: SMC for sampling  }
We apply our technique to a mixture of sharp Gaussians.
\begin{figure}[h!]
	\centering
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{F1.eps}
		\caption{Using $M=1000, N=3$ with  $ \kappa \sim uniform $. We see that the samples accumulate in the areas of high probability as required.   }
		\label{Ex1}
	\end{minipage}%
	\begin{minipage}{.05\textwidth}
	\end{minipage}
	\begin{minipage}{.40\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{F2.eps}
		\caption{Effective sample size for $N\leq 3$ steps. We started with a very low effective sample size and after only one iteration we have exceeded the required normalized (respect of the total number of samples) threshold at $T=0.5$}
		\label{Ex2}
	\end{minipage}
\end{figure}
\end{frame}

\begin{frame}\frametitle{SMC for rare events sampling }
Again we have  a difficult distribution $\pi (x)$ to sample from. However, now we are interested in get samples in areas with extremly low probability, this describe the probability to happen of very rare events. This means that we have to modify our resampling step as follows:
\textbf{STEP 2: Resampling (modified for rare events) }\\
\begin{enumerate}
\item[§2.0]  set $\hat{w}^{(i)}= 1-\tilde{w}^{(i)}$ and normalize.
\item[§2.1] Compute the Effective Sample Size $ESS= \frac{1}{\sum_{i=1}^M (\hat{w}^{(i)}_j )^2 }$ 
\item [§2.2] Given a threshold $T \in [0,M]$ we check if $ESS < T$: 
\begin{enumerate}
\item[§2.2.1]  Sample IID $\tilde{X}_j  \sim  multinomial(M,\underbar{w}_j)$  where $\underbar{w}_j=(\hat{w}^{(1)}_j , \hat{w}^{(2)}_j ,\hat{w}^{(3)}_j ,\ldots, \hat{w}^{(M)}_j )^{tr} $ and remove duplicated samples.
\item[§2.2.2]  For all $i \leq M$, set the weights $ \hat{w}_j^{(i)} = \frac{1}{M} $
\end{enumerate}
\end{enumerate}
We choose  $\hat{w}^{(i)}= 1-\tilde{w}^{(i)}$ to obtain the probability of an event not taking place which corresponds to having $1-p$ in a $multinomial(n,1-p)$. And in this way, we are resampling  samples which are associated with low probabilities.
\end{frame}

\begin{frame}\frametitle{Example: SMC for rare event sampling  }
We apply our technique to a mixture of  Gaussians and track the evolution of the samples
\begin{figure}[h!]
	\centering
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{F120.png}
		\caption{Using $M=1000$ with  $ \kappa \sim uniform $. We see that the samples accumulate in the areas of low probability as required.   }
		\label{Ex1}
	\end{minipage}%
	\begin{minipage}{.05\textwidth}
	\end{minipage}
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{F130.eps}
		\caption{Effective sample size for $N\leq10$. We started with a very low effective sample size and it increases until we have exceeded the required threshold at $T=0.91$}
		\label{Ex2}
	\end{minipage}
\end{figure}

\end{frame}

\begin{frame}\frametitle{Example: SMC for sampling rare events  }
Results using  the same threshold $T=0.91$.
\begin{figure}[h!]
	\centering
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{F3.eps}
		\caption{Using $M=1000$ with  $ \kappa \sim uniform $. We see that the samples accumulate in the areas of low probability as required. However, with few samples in a higher probability area    }
		\label{Ex1}
	\end{minipage}%
	\begin{minipage}{.05\textwidth}
	\end{minipage}
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{F4.eps}
		\caption{Effective sample size for $N\leq 10$. The effective sample size  increases as resampling is performed.  }
		\label{Ex2}
	\end{minipage}
\end{figure}
\end{frame}

\begin{frame}\frametitle{Example: SMC for sampling rare events  }
Results using  a higher threshold $T=1$.
\begin{figure}[h!]
	\centering
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{F8.eps}
		\caption{Using $M=1000$ with  $ \kappa \sim uniform $. We see that the samples accumulate exclusively  in  areas of very low probability as expected     }
		\label{Ex1}
	\end{minipage}%
	\begin{minipage}{.05\textwidth}
	\end{minipage}
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{F11.eps}
		\caption{Effective sample size for $N\leq 10$. The effective sample size  increases as resampling is performed.  }
		\label{Ex2}
	\end{minipage}
\end{figure}
\end{frame}

\begin{frame}\frametitle{SMC in Bayesian Framework}
In the Bayesian setting, our target distribution $\pi(\cdot)$ is the posterior $\pi(\theta|x) = \frac{\gamma(x, \theta)}{\int_\theta \gamma (x,\theta) \ d\theta} $ where $\gamma(x, \theta)= \underbrace{\mathcal{L}(x|\theta)}_{liklihood} prior(\theta)$. Then we construct  sequence of functions through tempering of $\gamma(x, \theta)$ into $N$ densities, where each density is given by:
\begin{equation}
\begin{split}
&\gamma_0 (\theta , x) =  \Big[ \mathcal{L} (x|\theta) \Big]^0  prior(\theta)  = prior (\theta) \\
&\gamma_1 (\theta , x) =  \Big[\mathcal{L} (x|\theta) \Big]^{1/N}\gamma_0 (\theta , x)   \\
&\gamma_2 (\theta , x) =  \Big[ \mathcal{L} (x|\theta) \Big]^{1/N}\gamma_1 (\theta , x) \\
&\gamma_3(\theta , x) =  \Big[ \mathcal{L} (x|\theta) \Big]^{1/N}\gamma_2 (\theta , x) \\
&  \quad \quad  \quad  \quad  \quad  \quad  \quad \vdots \\
&\gamma_N(\theta , x) =  \Big[ \mathcal{L} (x|\theta) \Big] \gamma_{N-1} (\theta , x) \\
\end{split}
\end{equation}

%\begin{equation*}
%\begin{split}
%\gamma_1 (\theta |\{x_k\}^{\ell-1}_{k=1}) & =\underbrace{ \prod_{i=1}^{\ell -1} \mathcal{L} (x_i|\theta)}_{=K_{0, 1}} \ \gamma_{0} (\theta)\\
%\gamma_2 (\theta |\{x_k\}^{2\ell-1}_{k=1}) & =\underbrace{ \prod_{i=\ell}^{2 \ell -1} \mathcal{L} (x_i|\theta)}_{=K_{1,2}} \ \gamma_{1} (\theta | \{x_k\}^{\ell-1}_{k=1})\\
%\quad \quad &  \quad \vdots  \quad \quad  \quad \vdots  \\ 
%\gamma_j (\theta |\{x_k\}^{j\ell-1}_{k=1}) & =\underbrace{ \prod_{i=(j-1)\ell}^{j \ell -1} \mathcal{L} (x_i|\theta)}_{=K_{j-1,\ j}} \ \gamma_{j-1} (\theta | \{x_k\}^{(j-1)\ell-1}_{k=1})\\
%\end{split}
%\end{equation*}
\end{frame}

\begin{frame}\frametitle{STEP 1: Applying Sequential Importance Sampling  (SIS)  }
  We perform importance sampling sequentially as follows:\\
  For $j=1$
\begin{enumerate}
\item[§1.1]  We choose  $\gamma_{0}(\theta , x)$  as our first proposal density.
\item[§1.2] Sample IID $\theta_1^{(i)} \sim \gamma_{0}$  for $i =1,2,\ldots, M$.
\item[§1.3] Compute the weights $w^{(i)}_1= \frac{\gamma_1(\theta_1)}{\gamma_0(\theta_1)}$
\end{enumerate}
For  $1< j \leq N$
\begin{enumerate}
\item[§2.1]  We choose  $\gamma_{j-1}(\theta , x)$  as our  proposal density.
\item[§2.2] Compute the weights $w^{(i)}_j= \frac{\gamma_{j}(\theta_1)}{\gamma_{j-1}(\theta_1)}$
\item[§2.3] Normalize the weights, $\tilde{w}^{(i)}_j = \frac{w^{(i)}_j}{\sum_{i=1}^M w^{(i)}_j}$ 
\end{enumerate}
\end{frame}

\begin{frame}\frametitle{STEP 2: Resampling  }
Next,  we aim to place more samples in our area of interest, and in this case, it is  where the  probability is high. Hence, we resample the samples  based on a $multinomial(n,p)$  with parameter $p$ as chosen below.\\
\begin{enumerate}
\item[§3.1] Compute the Effective Sample Size $ESS= \frac{1}{\sum_{i=1}^M (w^{(i)}_j )^2 }$ 
\item [§3.2] Given a threshold $T \in [0,M]$ we check if $ESS < T$: 
\begin{enumerate}
\item[§3.2.1]  Sample IID $\tilde{\theta}_j  \sim  multinomial(M,\underbar{w}_j)$  where $\underbar{w}_j=(\tilde{w}^{(1)}_j , \tilde{w}^{(2)}_j ,\tilde{w}^{(3)}_j ,\ldots, \tilde{w}^{(M)}_j )^{tr} $ and remove duplicated samples.
\item[§3.2.2]  For all $i \leq M$, set the weights $ \tilde{w}_j^{(i)} = \frac{1}{M} $
\end{enumerate}

\end{enumerate}
%\begin{equation}
%\begin{cases}
%\sigma=\Big(\sum^{n}_{i=1}\sigma^{-2}_i\Big)^{-\frac{1}{2}},\\
%\mu=\sigma^2\sum^{n}_{i=1}\sigma^{-2}_i\mu_i.
%\end{cases}
%\end{equation}
%If all the PDF have variance $\sigma_x$, then:
%\begin{equation}
%\begin{cases}
%\sigma=\Big(\sum^{n}_{i=1}\sigma^{-2}_x\Big)^{-\frac{1}{2}}=\frac{\sigma_x}{\sqrt{n}},\\
%\mu=\sigma^2\sum^{n}_{i=1}\sigma^{-2}_x\mu_i=\frac{1}{n}\sum^n_{i=1}\mu_i.
%\end{cases}
%\end{equation}
\end{frame}

\begin{frame}\frametitle{STEP 3: Obtaining quantity of interest  QoI }
Now we have all the pairs $(\tilde{w}_N^{(i)},\theta_N^{(i)} )$, we can directly approximate a  QoI  in the following way, 
\begin{equation}
\E [ \psi (\theta)] \approx \sum_{i=1}^M \tilde{w}_N^{(i)}  \psi (\theta_N^{(i)})
\end{equation}
\end{frame}

\begin{frame}\frametitle{Example: SMC for Bayesian }
We model the measurement error of a deterministic parameter as $R \sim N(0,\tau)$. Then our joint posterior is given by 
\begin{equation}
\pi (\mu, \tau| x ) \propto \mathcal{L}(x|\mu, \tau) prior(\mu , \tau)
\end{equation}
where  $prior(\mu , \tau)=NormalGamma(\mu, \tau; \lambda, \alpha, \beta)$. We use synthetic data  following a normal distribution $N(\hat{\mu}, \hat{\tau})$. Then through Bayesian  inference we obtain the joint distribution of the parameters of interest $\mu$ and $\tau$ which are assumed to follow a  $NormalGamma$ and our goal is to sample from it. This  choice also enables us to benchmark the method, as these densities are conjugates.

\end{frame}

\begin{frame}
Applying (SIS) without resampling,
\begin{figure}[h!]
	\centering
	\begin{minipage}{.60\textwidth}
		\centering
		\includegraphics[width=1.\linewidth]{F7.eps}
		\caption{Using $M=1000$. We observe that we have a lot of samples in low probability regions of no interest  }
		\label{Ex1}
	\end{minipage}%
\end{figure}
\end{frame}

\begin{frame}\frametitle{Example: SMC for Bayesian }
Applying  sequential Monte Carlo
\begin{figure}[h!]
	\centering
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=1.4\linewidth]{F9.eps}
				\caption{Using $M=1000, N=5$ with  $ \kappa \sim uniform $. The samples (shown in dots) are in  areas of high probability  }
		\label{Ex1}
	\end{minipage}%
	\begin{minipage}{.05\textwidth}
	\end{minipage}
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{F6.eps}
		\caption{Effective sample size for $N\leq5, T=0.91$. The effective sample size  increases as resampling is performed.  }
		\label{Ex2}
	\end{minipage}
\end{figure}
\end{frame}

\begin{frame}\frametitle{Example: SMC for Bayesian }
\begin{figure}[h!]
	\centering
%	\begin{minipage}{.45\textwidth}
%		\centering
%		\includegraphics[width=1.3\linewidth]{F5.eps}
%				\caption{Using $M=1000$ with  $ \kappa \sim uniform $ (different view)   }
%		\label{Ex1}
%	\end{minipage}%
%	\begin{minipage}{.05\textwidth}
%	\end{minipage}
		\includegraphics[width=0.8\linewidth]{F10.eps}
				\caption{Using $M=1000, N=5, T=0.91$. Top view  (samples shown in dots)    }
		\label{Ex2}
\end{figure}
\end{frame}

\begin{frame}\frametitle{Conclusion: }
 We conclude that sequential Monte Carlo is able to correct the increasing variance of the weights produced in sequential importance sampling by resampling. Also, we are able to sample from difficult distribution  while controlling our sensitivity to either high probability events or low probability events. Therefore, we are able to sample common and rare events without increasing the number of samples needed and only by accumulating them in the areas of interest.
\end{frame}

\begin{frame}\frametitle{Other implementations: }
Sequential Monte Carlo works in every sequence of distributions that converge to the target distribution. In particular we can have the next configurations:
\begin{enumerate}
\item In Bayesian framework, we can construct the sequence adding the data by steps.
\item Given a sequence that converge to our target, we can construct Markov kernels for use as transition kernels in the sequence. In this case the algorithm changes and instead of removing the duplicated samples, we apply the markov kernel which split them into different locations.
\item In a more general case, the samples can be transdimensional. This means, each distribution in the sequence can have different dimension (i.e. computing changepoints of a process, the number of changepoints is not fix and then, the vector of times where they are changes dimension).

\end{enumerate}

\end{frame}

\begin{frame}\frametitle{References: }
\begin{itemize}
\item AMCS 308 course notes.
\item  Del Moral P, Doucet A, Jasra A. Sequential Monte Carlo samplers. Journal of the Royal Statistical Society, Series B. 2006;68:411–436.
\end{itemize}
\end{frame}

\begin{frame}
Thanks to $ \{ Raul, \ Erik, \ Marco_{{Scavino}} \}$
\end{frame}
\end{document}

### 2020-03-28 LaTeX_Code/reports/results_stochastic_gradient.tex
I cleaned a bit the directories

\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{lmodern}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

\setbeamertemplate{caption}[numbered]

\title{On the Uncertainty of Wind Power Generation\\ continuous report}
\subtitle{ Waleed Alhaddad}

\begin{document}
\setbeamercolor{background canvas}{bg=blue!1}

\begin{frame}
\titlepage
\end{frame}

% \begin{frame}[label=guide]\frametitle{ Reader's Guide }
% List of changes in this iteration:
% \begin{itemize}
% \item Removed the term $p(1-p)$ from the model.
%     \begin{itemize}
%         \item derived the new ODE for the moments.
%         \end{itemize}
% \item Non-academic poster prepared.
% \end{itemize}
% Next steps:
% \begin{itemize}
% \item The french data set
%     \begin{itemize}
%         \item Organize and clean.
%     \end{itemize}
% \item Check the performance of the optimization.
%
% \end{itemize}
% \small{
% Note :
% \begin{itemize}
% \item Green slides: possible future extensions
% \item Red slides: notes to be removed
% \end{itemize}
% }
% \end{frame}

\begin{frame}\frametitle{ Base Model }
Moments approach with a Beta proxy. The SDE is given by
		\begin{equation}
		\begin{split}
		dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
		V_0 & = v_0
	\end{split}\label{VtSDE}
	\end{equation}
		and the moments by,
		\begin{equation*}
		\frac{d m_1 (t)}{dt} = - m_1(t)\theta_t \implies m_1(t_2)= V_{t_1} e^{-\int_{t_1}^{t_2} \theta_t \ dt }
		\end{equation*}
		\begin{equation*}
		\begin{split}
		\frac{d m_2 (t)}{dt} &=  - m_2(t)\theta(1+\alpha) + \alpha\theta m_1(t)( (1-p_t -p_t^2)) +2 \\
		& \implies m_2(t_2) = v_{t_1}^2 e^{-(1+\alpha)\int_{t_1}^{t_2} \theta_t \ dt} \\
		& \quad \quad + \alpha \int_{t_1}^{t_2} \left(\theta_s m_1(s)( 1-p_s - p_s^2 )+2\right)   e^{-(1+\alpha)\int_{t_1}^{t_2-s} \theta_u \ du}  \ ds
		\end{split}
		\end{equation*}
\end{frame}

\begin{frame}\frametitle{ solving for the moments numerically }
We discretize and integrate numerically step-by-step using  Euler,
\begin{align*}
  m_{1,i+1}&= v_i \ e^{ - \theta_i \Delta t} \\
  m_{2,i+1} &= \frac{v_i^2  + 2 \Delta t v_i  \alpha \theta_i p_i (1-p_i)(1-2p_i)  \alpha \theta_i p_i^2 (1-p_i)^2}{1+ 2 \Delta t (\theta_i + \alpha \theta_i p_i (1-p_i))}
\end{align*}
\end{frame}

\begin{frame}\frametitle{ Proposed Mini-Batch Stochastic Gradient Descent }
We have the following beta log-likelihood,
\begin{equation*}
\ell ( \theta_0 , \alpha | \{V_{i,j}\}) = \sum\limits_{j=1}^M \sum\limits_{i=1}^N \ (s_1 -1 ) \log \left( \frac{V_{j,i+1}+1}{2} \right) +  (s_2 -1 ) \log \left( 1 - \frac{V_{j,i+1}+1}{2} \right) - \log\left( 2 B(s_1, s_2) \right)
\end{equation*}
where $B(\cdot, \cdot)$ is the Beta function and
\begin{equation}
s_1 = - \frac{ (m_1+1)(m_1^2 + m_2 - m_1^2  -1 )}{2(m_2 - m_1^2)}
\end{equation}
\begin{equation}
s_2 = \frac{(m_1-1)(m_1^2 + m_2 - m_1^2  -1 )}{2(m_2 - m_1^2)}
\end{equation}
\end{frame}

\begin{frame}\frametitle{ 10 min data interval results }
We optimize the likelihood using Nelder-Mead Method which is a derivative-free method for non-linear objectives.
\begin{figure} %[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
\includegraphics[width=0.3\linewidth]{plots_SGD/ISO_100_inter=427.pdf}
\includegraphics[width=0.3\linewidth]{plots_SGD/ISO_500_inter=427.pdf}
\includegraphics[width=0.3\linewidth]{plots_SGD/ISO_833_inter=427.pdf}
\end{center}
   \caption{Likelihood evaluation with different number of sample paths. Optimal point $(\theta_0^*, \alpha^*) = (22.33,  0.049)$ shown in blue obtained using Nelder-Mead optimization method.}
\label{samples}
\end{figure}
\end{frame}

\begin{frame}\frametitle{ 10 min data interval results  }
\begin{figure} %[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
\includegraphics[width=0.6\linewidth]{plots_SGD/ISO_173_inter=427.pdf}
\end{center}
   \caption{Likelihood evaluation with 173 paths. Optimal point $(\theta_0^*, \alpha^*) = (22.33,  0.049)$ shown in blue obtained using Nelder-Mead optimization method.}
\label{100samples}
\end{figure}
\end{frame}

\begin{frame}\frametitle{ 10 min data interval results  }
\begin{figure} %[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
\includegraphics[width=0.8\linewidth]{plots_SGD/0.pdf}
\end{center}
   \caption{ Example 24hr simulation paths with the optimal parameters $(\theta_0^*, \alpha^*) = (22.33,  0.049)$}
\label{100samples}
\end{figure}
\end{frame}
\begin{frame}\frametitle{ 10 min data interval results  }
\begin{figure} %[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
\includegraphics[width=0.8\linewidth]{plots_SGD/18.pdf}
\end{center}
   \caption{ Example 24hr simulation paths with the optimal parameters $(\theta_0^*, \alpha^*) = (22.33,  0.049)$}
\label{100samples}
\end{figure}
\end{frame}
\begin{frame}\frametitle{ 10 min data interval results  }
\begin{figure} %[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
\includegraphics[width=0.8\linewidth]{plots_SGD/4.pdf}
\end{center}
   \caption{ Example 12hr simulation paths with the optimal parameters $(\theta_0^*, \alpha^*) = (22.33,  0.049)$}
\label{100samples}
\end{figure}
\end{frame}
\begin{frame}\frametitle{ 10 min data interval results  }
\begin{figure} %[t]
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
\includegraphics[width=0.8\linewidth]{plots_SGD/105.pdf}
\end{center}
   \caption{ Example 12hr simulation paths with the optimal parameters $(\theta_0^*, \alpha^*) = (22.33,  0.049)$}
\label{100samples}
\end{figure}
\end{frame}

\begin{frame}\frametitle{ Proposed Mini-Batch Stochastic Gradient Descent }
Let $B$ be the mini-batch size and $\eta$ the learning rate.\\

We iterate from an initial guess $\Theta_0 = (\theta_0 , \alpha)^T$ in the following way,
\begin{equation}
  \Theta = \Theta  - \eta \nabla \ell  \left( \Theta ; V_{1:B, 1:N} \right)
\end{equation}

until an accuracy threshold is reached. Note that $V_{1:B, 1:N}$ is a mini-batch of size $B$ of complete sample paths. The components of the gradient $\nabla \ell = (\frac{\partial \ell }{\partial \theta_0},\frac{\partial \ell}{\alpha} )^T$ are given by,

\begin{equation*}
\frac{\partial \ell }{\partial \theta_0} = \frac{\partial \ell }{\partial s_1}\frac{\partial s_1 }{\partial m_1}\frac{\partial m_1 }{\partial \theta_t}\frac{\partial \theta_t }{\partial \theta_0} + \frac{\partial \ell }{\partial s_1}\frac{\partial s_1 }{\partial m_2}\frac{\partial m_2 }{\partial \theta_t}\frac{\partial \theta_t }{\partial \theta_0} + \frac{\partial \ell }{\partial s_2}\frac{\partial s_2 }{\partial m_1}\frac{\partial m_1 }{\partial \theta_t}\frac{\partial \theta_t }{\partial \theta_0} + \frac{\partial \ell }{\partial s_2}\frac{\partial s_2 }{\partial m_2}\frac{\partial m_2 }{\partial \theta_t}\frac{\partial \theta_t }{\partial \theta_0}
\end{equation*}

\begin{equation*}
\frac{\partial \ell }{\partial \alpha} =  \frac{\partial \ell }{\partial s_1}\frac{\partial s_1 }{\partial m_2}\frac{\partial m_2 }{\partial \alpha} + \frac{\partial \ell }{\partial s_2}\frac{\partial s_2 }{\partial m_2}\frac{\partial m_2 }{\partial \alpha}
\end{equation*}

\end{frame}

\begin{frame}\frametitle{Proposed Mini-Batch Stochastic Gradient Descent}
We run into an issue here because the term $ \frac{\partial \theta_t }{\partial \theta_0} $ is undefined as $\theta_t$ is non-differentiable and given by,
\begin{equation*}
  \theta_t = \max \left( \theta_0 , \frac{ |\dot{p}| }{ \min (p, 1-p)} \right)
\end{equation*}

We can either regularize or continue to use the Nelder-Mead optimization method which is derivative-free. Is it possible to use mini-batches with Nelder-Mead?

\end{frame}

% \begin{frame}\frametitle{ Proposed Mini-Batch Stochastic Gradient Descent }
%  We differentiate with respect to the parameters:
% \begin{equation}
%   J_{s_1}^M\left( s_1, s_2 ; V_{1:M, 1:N} \right)=\frac{\partial \ell}{ \partial \alpha } = \sum\limits_{j=1}^M \sum\limits_{i=1}^N \  \log \left( \frac{V_{j,i+1}+1}{2} \right) - \psi(s_1) + \psi(s_1 + s_2)
% \end{equation}
% \begin{equation}
%   J_{s_2}^M \left( s_1, s_2 ; V_{1:M, 1:N} \right) =\frac{\partial \ell}{ \partial \beta } = \sum\limits_{j=1}^M \sum\limits_{i=1}^N \  \log \left(1-  \frac{V_{j,i+1}+1}{2} \right) - \psi(s_2) + \psi(s_1 + s_2)
% \end{equation}
% % \begin{equation}
% %   \nabla_{\alpha,\beta} J \left( \Theta ; V_{1:M, 1:N} \right) = \frac{\partial \ell}{ \partial \alpha \partial \beta } = \frac{\partial \ell}{ \partial \beta \partial \alpha  }= M N \ \psi^{(1)} (\alpha + \beta)
% % \end{equation}
% %$\psi^{(1)}(\cdot)$ is the trigamma function.
% where $\psi(\cdot)$ is the digamma function.
% \end{frame}

%\againframe{guide}

\end{document}

### 2020-03-28 parallel_test_loop.py

@@ -1,103 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.cm as cm
-import scipy.stats
-from scipy.optimize import minimize
-from scipy.stats import multivariate_normal, norm
-from mpl_toolkits.mplot3d import Axes3D
-import operator
-from scipy.optimize import minimize
-from scipy.optimize import basinhopping
-import math
-import random
-from scipy import interpolate
-from math import pi
-from numpy import linalg as LA
-import datetime as dtM
-import os
-from multiprocessing import Process
-import time
-
-def f(name, sec):
-    info('function f')
-    time.sleep(sec)
-    print ('hello', name)
-    L=sec
-
-def info(title):
-    print (title)
-    print ('module name:', __name__)
-    if hasattr(os, 'getppid'):  # only available on Unix
-        print('parent process:', os.getppid())
-    print('process id:', os.getpid())
-
-if __name__ == '__main__':
-    p1 = Process(target=f, args=('bob',0))
-    p2 = Process(target=f, args=('tom',5))
-    p3 = Process(target=f, args=('goerge',10))
-    p1.start()
-    p2.start()
-    p3.start()
-    p1.join()
-
-
-def moment_compute(dN, X_prev, X_next, p_prev, theta_current, alpha_current ):
-    m_1=X_prev*np.exp(- dN*theta_current)
-    m_2=  (X_prev**2 + 2*dN*( X_prev*(alpha_current*theta_current*p_prev*(1-p_prev)*(1-2*p_prev )) + \
-                 alpha_current*theta_current*p_prev**2*(1-p_prev)**2) ) /(  1+ dN*2*(theta_current+alpha_current*theta_current*p_prev*(1-p_prev) ))
-    a=m_1;
-    b=m_2- m_1**2;
-
-    if b==0: b=1e-16
-    if b<0:
-        b=1e-16
-
-    beta_param_alpha= - ( (1+a)*(a**2 +b -1)    )/(2*b)
-    beta_param_beta= ( (a-1)*(a**2 + b -1)  )  /(2*b)
-
-    L_n_current=(beta_param_alpha-1 )*np.log(  (X_next+1)/2 ) +\
-     (beta_param_beta-1)*np.log(1-( X_next +1)/2 )-\
-     scipy.special.betaln(beta_param_alpha, beta_param_beta)
-
-    return(L_n_current)
-
-
-
[…]

### 2020-03-28 LaTeX_Code/Reports/continous_report.tex
Minor corrections

\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{lmodern}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

\setbeamertemplate{caption}[numbered]

\title{On the Uncertainty of Wind Power Generation\\ continuous report}
\subtitle{ Waleed Alhaddad}

\begin{document}
\setbeamercolor{background canvas}{bg=blue!1}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}[label=guide]\frametitle{ Reader's Guide }
List of changes in this iteration:
\begin{itemize}
\item Removed the term $p(1-p)$ from the model.
    \begin{itemize}
        \item derived the new ODE for the moments.
        \item simulated and built the confidence intervals.
        \end{itemize}
\item Non-academic poster prepared.
\end{itemize}
Next steps:
\begin{itemize}
\item The french data set
    \begin{itemize}
        \item Organize and clean.
        \item Normalize by the changing installed capacity.
        \item Obtain the optimal parameters.
        \item generate paths and build the confidence bands.
        \item consider seasonality and human intervention.
    \end{itemize}
\item Check the performance of the optimization.
\item simultaneous versus point-wise confidence bands.
\end{itemize}
\small{
Note :
\begin{itemize}
\item Green slides: possible future extensions
\item Red slides: notes to be removed
\end{itemize}
}
\end{frame}

\begin{frame}\frametitle{ Moments of the process }
After removing the term $p_t(1-p_t)$ from the model, the first moment is unaffected and the second moment of the process is now given by,
\begin{equation*}
\frac{d m_2 (t)}{dt} = 2 \right( - m_2(t)\theta(1+\alpha) + \alpha\theta m_1(t)( (1-2p_t) + p_t(1-p_t)) \left)
\end{equation*}
\end{frame}

\begin{frame}\frametitle{ Moments of the process after Lamperti transform }
After removing the term $p_t(1-p_t)$ from the model, the moments of the process are now given by,

\begin{equation*}
m_1 (t_2) = \arcsin \left(  e^{-\int_{t_1}^{t_2} \theta_t (1-2 \alpha) \ dt  } \left( \int_{t_1}^{t_2} \theta_s (2p_s - 1)e^{ \int_{t_1}^{s} \theta_t (1-2 \alpha) \ dt  } \ ds + \sin (z_{t_1})\right)  \right)
\end{equation*}

\begin{equation*}
m_2 (t_2) =  2\alpha \int_{t_1}^{t_2}  \theta_t  \ dt + m_2(t_1)
\end{equation*}

\end{frame}

\againframe{guide}

\end{document}

### 2020-03-28 LaTeX_Code/Paper/paper_1line.tex
proof Xt centered ariund pt

--- 2020-03-24 LaTeX_code/paper/paper_1line.tex
@@
 
-Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$.
+Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $X_0 = p_0$.
+The application of  It\^{o}'s lemma on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s ds}$, leads to
+\begin{equation*}
+d \left( X_t e^{\int_{0}^{t} \theta_s ds} \right) = e^{\int_{0}^{t} \theta_s ds} (\dot{p}_t + \theta_t p_t ) dt  + e^{\int_{0}^{t} \theta_s ds}\, b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \,dW_t\,,
+\end{equation*}
+whose integral form is
+\begin{equation}
+e^{\int_{0}^{t} \theta_s ds}  X_t - X_0 = \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u du} ds + \int_{0}^{t}  b (X_s; p_s, \dot{p}_s, \bm{\theta} )  e^{\int_{0}^{s} \theta_u du}\, d W_s\,.
+\label{eq:tomeanX}
+\end{equation} 
+Taking expectation on (\ref{eq:tomeanX}) we obtain
+\begin{align}
+\mathbb{E} X_t & = e^{ - \int_{0}^{t} \theta_s ds} \left(  \mathbb{E} X_0 +   \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u du} ds   \right) \nonumber \\ 
+& =  e^{ - \int_{0}^{t} \theta_s ds} \left(  \mathbb{E} X_0 +   \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u du} ds +  \big[ p_s \, e^{\int_{0}^{s} \theta_u du} \big]^{t}_0  - \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u du} ds  \right) \nonumber \\
+& =  e^{ - \int_{0}^{t} \theta_s ds} \left(  \mathbb{E} X_0 + p_t \, e^{ \int_{0}^{t} \theta_s ds} - p_0 \right) = p_t \,.
+\end{align}
 
- Then, the process defined by (\ref{eq:main}) with drift (\ref{drift:meanrev-derivtrack}) satisfies the two following properties: 
+ At this stage, the process defined by (\ref{eq:main}) with drift (\ref{drift:meanrev-derivtrack}) satisfies the two following properties: 
 \begin{itemize}
@@
 \end{itemize} 
-Observe that a mean reverting model without derivative tracking exhibits consistent lags, as it is shown in Figure (\ref{fig:derivative_tracking}). See Section \ref{Section_7} for comparisons.
+{\color{red} Observe that a mean reverting model without derivative tracking exhibits consistent lags, as it is shown in Figure (\ref{fig:derivative_tracking}).} See Section \ref{Section_7} for comparisons.
 
@@
   \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= (\dot{p}_t  - \theta_t (X_t - p_t) ) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
+    dX_t \!\!\!&= \big(\dot{p}_t  - \theta_t (X_t - p_t) \big) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
    X_0  \!\!\!&=  x_0\in [0,1] \,,
@@
 Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.
-%---END SECTION 7---
+%---END SECTION 8---
 
@@
 For a time horizon $T>0$ and  a parameter $\alpha > 0$ and $(\theta_t)_{t\in[0,T]}$ a positive deterministic  function,  let us consider the model  given by
-\begin{align}\label{eq:model}
-dX_t&= \big(\dot p_t - \theta_t(X_t-p_t)  \big)dt  +\sqrt{2\alpha \theta_tX_t(1-X_t)} dW_t\quad t\in[0,T]\\
-X_0&=x_0\in[0,1],\notag
-\end{align}
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    dX_t \!\!\!&= \big(\dot p_t - \theta_t (X_t-p_t)  \big)dt  +\sqrt{2 \alpha \theta_t X_t (1-X_t)} dW_t\,, \quad t\in[0,T] \\
+   X_0  \!\!\!&=  x_0\in [0,1] \,,
+ \end{array}\right.  \label{eq:model}
+\end{equation}
 where $(p_t)_{t\in[0,T]}$ denotes the prediction function that satisfies $0\le p_t\le 1$ for all $t\in[0,T]$. This prediction function is assumed to be a smooth function of the time so that 
@@
 In what follows we adapt the proof of the above theorem for the new model 
-\begin{align}\label{eq:model2}
-dX_t&= \big(\dot p_t - \theta_t(X_t-p_t)  \big)dt  +\sqrt{2\alpha \red{\theta_0}X_t(1-X_t)} dW_t\quad t\in[0,T]\\
-X_0&=x_0\in[0,1],\notag
-\end{align}
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    dX_t \!\!\!&= \big(\dot p_t - \theta_t (X_t-p_t)  \big)dt  +\sqrt{2 \alpha \red{\theta_0} X_t (1-X_t)} dW_t\,, \quad t\in[0,T] \\
+   X_0  \!\!\!&=  x_0\in [0,1] \,,
+ \end{array}\right.  \label{eq:model2}
+\end{equation}
 

### 2020-03-30 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
Added most Lamperti MATLAB files. The parameters are 10 and 0.1, now I need to check that all functions are working as they should.

@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Normalization:}
+\begin{frame}\frametitle{Normalization:}\label{Norm}
 
@@
 \begin{frame}\frametitle{SDE first moment (1/2):} \label{m1}
-
+\alert{Check if still correct for the new model!!!}\\
 Given some measurement $v_{t_{n-1}}$, we want to compute the first moment at time $t_n$. The exact first moment $m_1(s)$ for $s\in[t_{n-1},t_n]$ is the solution of the ODE
@@
 
+\alert{Check if still correct for the new model!!!}\\
 Given some measurement $v_{t_{n-1}}$, we want to compute the second moment at time $t_n$. The exact second moment $m_2(s)$ for $s\in[t_{n-1},t_n]$ is the solution of the ODE
@@
 \begin{frame}\frametitle{From $\theta_0$ to $\theta_t$:}
-{\small
+
 To ensure that the analytical solutions is always in $]0,1[$, we choose the drift parameter to be
@@
 \end{tabular}
-\end{center}}
+\end{center}
+{\tiny Recall that we normalized w.r.t.
+time $T$.
+The normalized $\hat{\theta}_t$ is $\hat{\theta}_t=\theta_tT$.
+Notice that in the definition of $\theta_t$, if we use $\hat{\theta}_0=\theta_0T$ and the derivative of $p_t$ w.r.t.
+$\dif \hat{t}$ instead of w.r.t.
+$\dif t$, then we automatically have $\hat{\theta}_t$.
+See slide \ref{Norm}.}
 
@@
 
-\alert{This function is independent of if we are using the real data or the truncated one.} If we take a total of $Z\in\N$ days, the batch corresponding to this days is
+\alert{This function is independent of if we are using the real data or the truncated one.}\\
+If we take a total of $Z\in\N$ days, the batch corresponding to this days is
 \begin{table}[]
@@
 
+\setbeamercolor{background canvas}{bg=green!20}
+\begin{frame}
+
+{\Huge Lamperti Transform}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!20}
+\begin{frame}\frametitle{Two candidates:}
+
+\begin{columns}
+
+\column{.5\textwidth}
+Recall $X_t=V_t+p_t$.\\
+\quad\\
+We have the candidates:
+\begin{itemize}
+
+\item {\color{blue} $Z_t=\frac{1}{\sqrt{2\alpha\theta_0}}\arcsin(2(V_t+p_t)-1)$.}
+\item {\color{red} $Z_t=\sqrt{\frac{2}{\alpha\theta_0}}\arcsin(\sqrt{1-V_t-p_t})$.}
+
+\end{itemize}
+\quad\\
+\quad\\
+They have the same partial derivatives.
+The main difference appears in the resulting SDE for $Z_t$.
+In the {\color{blue} first case}, we have a $\sin(\sqrt{2\alpha\theta_0}Z_t)$ in the drift, while in the \alert{second case}, we have $\cos(\sqrt{2\alpha\theta_0}Z_t)$.\\
+\quad\\
+For now, we will use the {\color{blue}first candidate}.
+
+\column{.5\textwidth}
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.9\textwidth]{../../Mathematica_Files/new_model/Lamp_Comp.pdf}
+\end{figure}
+
+\end{columns}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Lamperti data:}
+
+We are following the {\color{blue}first candidate}. Then, we caa
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Lamperti moments:}
+
+The Lamperti SDE is:
+\begin{align*}
+\dif Z_t= \underbrace{\left[  \frac{(\alpha \theta_0 - \theta_t) {\color{blue}\sin(\sqrt{2 \alpha \theta_0 } Z_t) }- \theta_t (1 - 2 p_t) + 2  \dot{p}_t }{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}}  \right]}_{\coloneqq b(Z_t)} \dif t + \dif W_t .
+\end{align*}
+Here we follow Bayesian Filtering and Smoothing, Chapter 9. We use the linearization-based approximation for the moments.
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{SDE first Lamperti moment (mean) (1/2):}
+Given some measurement $z_{t_{n-1}}$, we want to compute the first moment at time $t_n$. The linearly approximated first moment $\mu_Z(s)$ for $s\in[t_{n-1},t_n]$ is the solution of the ODE
+
+\begin{equation*}
+\begin{cases}
+\dif \mu_L(s)&=b(\mu_L(s))\dif s,\\
+\mu_L(t_{n-1})&=z_{t_{n-1}}.
+\end{cases}
+\end{equation*}
+\quad\\
+We solve numerically the ODE using Forward-Euler:
+\begin{equation*}
+\mu_L(s_{n})=\mu_L(s_{n-1})+b(\mu_L(s_{n-1}))\Delta s.
+\end{equation*}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{SDE first Lamperti moment (mean) (2/2):}
+
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\scriptsize
+\lstinputlisting{../moment_1_L.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{SDE Lamperti variance (1/2):}
+Given some measurement $z_{t_{n-1}}$, we want to compute the variance at time $t_n$. The linearly approximated variance $v_Z(s)$ for $s\in[t_{n-1},t_n]$ is the solution of the ODE
+
+\begin{equation*}
+\begin{cases}
+\dif \sigma^2_L(s)&=\left(2\sigma^2_Lb'(\mu_L(s))+1\right)\dif s,\\
+\sigma^2_L(t_{n-1})&=0.
+\end{cases}
+\end{equation*}
+\quad\\
+We solve numerically the ODE using Forward-Euler:
+\begin{equation*}
+\sigma^2_L(s_{n})=\sigma^2_L(s_{n-1})+\left(1+2\sigma^2_L(s_{n-1})b'(\mu_L(s_{n-1}))\right)\Delta s.
+\end{equation*}
+We have that (computed with Mathematica):
+\begin{equation*}
+b'(z)=\frac{\dif b}{\dif z}(z)=\frac{\alpha\theta_0-\theta_t+(2\dot{p}_t+(2p_t-1)\theta_t)\sin(z\sqrt{2\alpha\theta_0}))}{\cos^2(z\sqrt{2\alpha\theta_0})}.
+\end{equation*}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{SDE Lamperti variance (2/2):}
+
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\tiny
+\lstinputlisting{../moment_2_L.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Density next measurement:}
+
+We want the next measurement $Z_{t_n}|Z_{t_{n-1}}$ to have a Gaussian with mean $\mu_Z$ and variance $\sigma_Z^2$ ($f_Z(z)=\mathcal{N}(\mu_Z,\sigma^2_Z)$).\\
+\quad\\
+Then, we want the SDE and our new PDF $f_Z(z)$ to have the same moments at each $t\in\{\text{some appropriate domain}\}$, i.e., $\mu_Z(t)=\mu_L(t)$ and $\sigma^2_Z(t)=\sigma^2_L(t)$.\\
+\quad\\
+The density and log-density (natural logarithm) are:
+\begin{equation*}
+f_Z(z)=\frac{e^{-\frac{1}{2}\left(\frac{z-\mu_Z}{\sigma_Z}\right)^2}}{\sigma_Z\sqrt{2\pi}}\iff \log(f_Z(z))=-\frac{1}{2}\left(\frac{z-\mu_Z}{\sigma_Z}\right)^2-\log(\sigma_Z\sqrt{2\pi}).
+\end{equation*}
+
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\tiny
+\lstinputlisting{../log_dist_L.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}
+
+\end{frame}
+
 \end{document}

### 2020-03-30 MATLAB_Files/lamperti_transform.m

@@ -1,0 +1,7 @@
+function [val] = lamperti_transform(theta_0,alpha,v,p) 
+
+    % 29/03/2020 17:49
+
+    val = (1/sqrt(2*alpha*theta_0)) * asin(2*(v+p)-1);
+    
+end

### 2020-04-02 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
I am checking that the empirical moments match with the analytic ones.

@@
 \begin{frame}\frametitle{SDE first moment (1/2):} \label{m1}
-\alert{Check if still correct for the new model!!!}\\
 Given some measurement $v_{t_{n-1}}$, we want to compute the first moment at time $t_n$. The exact first moment $m_1(s)$ for $s\in[t_{n-1},t_n]$ is the solution of the ODE
@@
 
-The code is automatically imported from the MATLAB script.
-
 \end{frame}
@@
 
-\alert{Check if still correct for the new model!!!}\\
 Given some measurement $v_{t_{n-1}}$, we want to compute the second moment at time $t_n$. The exact second moment $m_2(s)$ for $s\in[t_{n-1},t_n]$ is the solution of the ODE
@@
 \begin{cases}
-\dif m_2(s)&=\alert{\left[-2(1+\alpha)m_2(s)\theta(s)+2\alpha\theta(s)m_1(s)(1-2p(s))+2\alpha\theta(s)p(s)(1-p(s))\right]\dif s,}\\
-&=2\theta(s)\left[-(1+\alpha)m_2(s)+\alpha m_1(s)(1-2p(s))+\alpha p(s)(1-p(s))\right]\dif s,\\
+\dif m_2(s)&=\left[\alert{-2m_2(s)(\theta(s)+\alpha\theta_0)}+2\alpha\theta_0m_1(s)(1-2p(s))+{\color{blue}2\alpha\theta_0p(s)(1-p(s))}\right]\dif s,\\
 m_2(t_{n-1})&=v^2_{t_{n-1}}.
@@
 \begin{equation*}
-m_2(s_n)=m_2(s_{n-1})+2\theta(s_{n-1})\left[-(1+\alpha)m_2(s_{n-1})+\alpha m_1(s_{n-1})(1-2p(s_{n-1}))+\alpha p(s_{n-1})(1-p(s_{n-1}))\right]\Delta s.
+m_2(s_n)=m_2(s_{n-1})+\left[\alert{-2m_2(s_{n-1})(\theta(s_{n-1})+\alpha\theta_0)}+2\alpha\theta_0m_1(s_{n-1})(1-2p(s_{n-1}))+{\color{blue}2\alpha\theta_0p(s_{n-1})(1-p(s_{n-1}))}\right]\Delta s.
 \end{equation*}}
@@
 \toprule
-{\footnotesize
+{\tiny
 \lstinputlisting{../moment_2.m}
@@
 \begin{equation*}
-\theta(t) = \max\left(\theta_0,\frac{\theta_0\alpha+2|\dot{p}^\epsilon(t)|}{2\min(p^\epsilon(t),1-p^\epsilon(t))}\right),\quad\theta_0>0.
+\theta(t) = \max\left(\theta_0,\frac{\theta_0\alpha+|\dot{p}^\epsilon(t)|}{\min(p^\epsilon(t),1-p^\epsilon(t))}\right),\quad\theta_0>0.
 \end{equation*}
@@
 \centering
-\includegraphics[width=0.32\textwidth]{../Results/likelihood/Log-Likelihood.eps}
-\includegraphics[width=0.32\textwidth]{../Results/likelihood/Log-Likelihood_refined.eps}
-\includegraphics[width=0.32\textwidth]{../Results/likelihood/Log-Likelihood_more_refined.eps}
+\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood.eps}
+\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_refined.eps}
+\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_more_refined.eps}
 \caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions, and we can also see the initial guess.}
@@
 \item {\color{blue} $Z_t=\frac{1}{\sqrt{2\alpha\theta_0}}\arcsin(2(V_t+p_t)-1)$.}
-\item {\color{red} $Z_t=\sqrt{\frac{2}{\alpha\theta_0}}\arcsin(\sqrt{1-V_t-p_t})$.}
+\item {\color{red} $Z_t=-\sqrt{\frac{2}{\alpha\theta_0}}\arcsin(\sqrt{1-V_t-p_t})$.}
 
@@
 \quad\\
-They have the same partial derivatives.
-The main difference appears in the resulting SDE for $Z_t$.
-In the {\color{blue} first case}, we have a $\sin(\sqrt{2\alpha\theta_0}Z_t)$ in the drift, while in the \alert{second case}, we have $\cos(\sqrt{2\alpha\theta_0}Z_t)$.\\
+They have the same partial derivatives. The main difference appears in the resulting SDE for $Z_t$.\\
 \quad\\
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Lamperti data:}
-
-We are following the {\color{blue}first candidate}. Then, we caa
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
 \begin{frame}\frametitle{Lamperti moments:}
@@
 \begin{align*}
-\dif Z_t= \underbrace{\left[  \frac{(\alpha \theta_0 - \theta_t) {\color{blue}\sin(\sqrt{2 \alpha \theta_0 } Z_t) }- \theta_t (1 - 2 p_t) + 2  \dot{p}_t }{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}}  \right]}_{\coloneqq b(Z_t)} \dif t + \dif W_t .
+\dif Z_t= \underbrace{\left[  \frac{(\alpha \theta_0 - \theta_t) {\color{black}\sin(\sqrt{2 \alpha \theta_0 } Z_t) }- \theta_t (1 - 2 p_t) + 2  \dot{p}_t }{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}}  \right]}_{\coloneqq b(Z_t)} \dif t + \dif W_t .
 \end{align*}
-Here we follow Bayesian Filtering and Smoothing, Chapter 9. We use the linearization-based approximation for the moments.
+Here we follow Bayesian Filtering and Smoothing, Chapter 9. We use the linearization-based approximation for the moments.\\
+\quad\\
+As $X_t\in(\alert{0},1)$, we have that $Z_t\in\left(\alert{-\frac{\pi}{2}\frac{1}{\sqrt{2\alpha\theta_0}}},\frac{\pi}{2}\frac{1}{\sqrt{2\alpha\theta_0}}\right)$.
 
@@
 
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Lamperti Log-likelihood evaluation (1/2): CODE}
+
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\tiny
+\lstinputlisting{../log_LH_evaluation_L.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Lamperti Log-likelihood evaluation (2/2):}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.5\textwidth]{../Results/likelihood/lamperti/Log-Likelihood.eps}
+\caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions.}
+\end{figure}
+
+\end{frame}
+
 \end{document}

### 2020-04-02 MATLAB_Files/likelihood_optimization.m

@@ -1,7 +1,7 @@
-function [val] = likelihood_optimization(batch, theta0, alpha, dt)
+function [val] = likelihood_optimization(batch, theta_0, alpha, dt)
     % 10/02/2020 11:20
-    disp(['Theta = ',num2str(theta0),', Alpha = ',num2str(alpha)]);
-    batch_complete = batch_with_theta(batch, alpha, theta0);
-    val            = log_LH_evaluation(batch_complete, alpha, dt);
+    disp(['Theta = ',num2str(theta_0),', Alpha = ',num2str(alpha)]);
+    batch_complete = batch_with_theta(batch, alpha, theta_0);
+    val            = log_LH_evaluation(batch_complete, alpha, theta_0, dt);
 
 end

### 2020-04-02 MATLAB_Files/moment_2.m

@@ -1,18 +1,21 @@
-function m2 = moment_2(v,th1,th2,p1,p2,alpha,m1,dt,n) % 02/02/2020 18:28
+function m2 = moment_2(v,theta_0,th1,th2,p1,p2,alpha,m1,dt,n) % 02/04/2020 15:13
 
-    if th1 == th2
+    p      = @(i) p1 + (p2-p1) * i/n; % We interpolate p(t).
+    pe_dot = (p2-p1) / dt;
+    m2(1)  = v^2;
+    ds     = dt/n;
+    
+    if th1 == th2 % In this case, m_1 has exact solution and theta_t = theta_0.
         theta = @(i) th2;
         m1    = @(i) v*exp(-th1*dt*(i/n));
     else
-        theta = @(i) th1 + (th2-th1) * i/n;
+        theta  = @(i) theta_t(theta_0, alpha, p(i), pe_dot);
     end
-    p     = @(i) p1  + (p2-p1)   * i/n;
-    m2(1) = v^2;
-    ds    = dt/n;
     
     for i = 2:n
-        m2(i) = m2(i-1) + 2*theta(i-1)*ds * (-(1+alpha)*m2(i-1) + ...
-            alpha*m1(i-1)*(1-2*p(i-1)) + alpha*p(i-1)*(1-p(i-1))); 
+        m2(i) = m2(i-1) + (-2*m2(i-1)*(theta(i-1)+alpha*theta_0) + ...
+            2*alpha*theta_0*m1(i-1)*(1-2*p(i-1)) + ...
+            2*alpha*theta_0*p(i-1)*(1-p(i-1))) * ds;
     end
     
 end

### 2020-04-02 MATLAB_Files/moments_verification.m

@@ -1,0 +1,157 @@
+close all;
+clear all;
+clc;
+
+epsilon                = 0.018;
+Table_Testing_Complete = load_data_eps_test(epsilon);
+
+t  = Table_Testing_Complete.Time(1,:);
+dt = t(2);
+
+theta_0 = 3.912;
+alpha   = 0.019308;
+n       = 100;
+p_end   = 1/2;
+p_lims  = 0.03;
+
+p = p_end-p_lims:0.001:p_end+p_lims;
+v = -0.2:0.001:0.2;
+
+for i = 1:length(p)
+    for j = 1:length(v)
+                
+        P_dot        = (p_end-p(i)) / dt;
+        Theta_t      = theta_t(theta_0, alpha, p(i), P_dot);
+        Theta_t_next = theta_t(theta_0, alpha, p_end, 0);
+        
+        Exp_V   = moment_1(v(j),theta_0,alpha,Theta_t,Theta_t_next,p(i),p_end,dt,n);
+        Exp_V_2 = moment_2(v(j),theta_0,Theta_t,Theta_t_next,p(i),p_end,alpha,Exp_V,dt,n);
+                
+        for k = 1:100
+            sim_path_v(k)   = sde_FE_error(v(j),alpha,theta_0,Theta_t,dt,p(i));
+            sim_path_v_2(k) = sde_FE_error_2(v(j)^2,alpha,theta_0,Theta_t,dt,p(i));
+        end
+        
+        Exp_V_emp   = mean(sim_path_v);
+        Exp_V_emp_2 = mean(sim_path_v_2);
+
+        exp_v_ode(i,j)   = Exp_V(end);
+        exp_v_2_ode(i,j) = Exp_V_2(end);
+        exp_v_emp(i,j)   = Exp_V_emp;
+        exp_v_emp_2(i,j) = Exp_V_emp_2;
+        
+    end
+end
+
+error_v   = abs(exp_v_ode-exp_v_emp);
+error_v_2 = abs(exp_v_2_ode-exp_v_emp_2);
+
+figure;
+[V,Y] = meshgrid(p-p_end,v);
+surf(V,Y,exp_v_emp');
+title('$E[V]$ Empirical','interpreter','latex');
+xlabel('Prev. Rel. Forecast'); ylabel('Prev. Error (V)');
+xlim([min(p-p_end) max(p-p_end)]); ylim([min(v) max(v)]);
[…]

### 2020-04-02 MATLAB_Files/moments_verification_Lamperti.m

@@ -1,0 +1,114 @@
+close all;
+clear all;
+clc;
+
+epsilon                = 0.018;
+Table_Testing_Complete = load_data_eps_test(epsilon);
+
+t  = Table_Testing_Complete.Time(1,:);
+dt = t(2);
+
+theta_0 = 3.912;
+alpha   = 0.019308;
+p_end   = 1/2;
+n       = 100;
+
+lims = 0.1;
+
+p = lims:0.01:1-lims;
+x = lims:0.01:1-lims;
+
+for i = 1:length(p)
+    for j = 1:length(x)
+                
+        v            = x(j) - p(i);
+        P_dot        = (p_end-p(i)) / dt;
+        Theta_t      = theta_t(theta_0, alpha, p(i), P_dot);
+        Theta_t_next = theta_t(theta_0, alpha, p_end, 0);
+        
+        Exp_V   = moment_1(v,Theta_t,Theta_t_next,dt,n);
+        Exp_V_2 = moment_2(v,Theta_t,Theta_t_next,p(i),p_end,alpha,Exp_V,dt,n);
+        
+        for k = 1:100
+            sim_path_x(k)   = sde_FE(x(j),alpha,theta_0,Theta_t,dt,p(i),P_dot);
+            sim_path_x_2(k) = sim_path_x(k)^2;
+            
+            sim_path_v(k)   = sde_FE_error(v,alpha,theta_0,Theta_t,dt,p(i));
+            sim_path_v_2(k) = sim_path_v(k)^2;
+        end
+        Exp_X   = mean(sim_path_x);
+        Exp_X_2 = mean(sim_path_x_2);
+        Exp_V_emp   = mean(sim_path_v);
+        Exp_V_emp_2 = mean(sim_path_v_2);
+        
+        error_x_1(i,j) = (Exp_X -  + p_end);
+        error_x_2(i,j) = (Exp_X_2 - Exp_V_2(end) -2*p_end*Exp_X - p_end^2);      
+        error_V_1(i,j) = (Exp_V_emp - Exp_V(end));
+        error_V_2(i,j) = (Exp_V_emp_2 - Exp_V_2(end));       
+        exp_x(i,j)   = Exp_X;
+        exp_x_2(i,j) = Exp_X_2;
+        exp_v(i,j)   = Exp_V(end);
+        exp_v_2(i,j) = Exp_V_2(end);
+        exp_v_emp(i,j)   = Exp_V_emp;
[…]

### 2020-04-02 MATLAB_Files/optimizeLogLikelihood.m

@@ -2,7 +2,7 @@ close all;
 clear all;
 clc;
 
-likelihood    = 'lamperti'; % 'normal' or 'lamperti'.
+likelihood    = 'normal'; % 'normal' or 'lamperti'.
 epsilon       = 0.018;
 [Ta_Tra_Comp] = load_data_eps(epsilon);
 

### 2020-04-02 MATLAB_Files/path_simulator_OPT.m

@@ -7,10 +7,10 @@ Table_Testing_Complete = load_data_eps_test(epsilon);
 
 % PARAMETERS:
 % set(0,'defaultAxesFontSize',18);
-quantil  = 1;
-save     = 1;
+quantil  = 0;
+save     = 0;
 delta    = 22; % The time is delta*10 minutes.
-xlimit   = 1; % If this in 1, the plots start at time 0. Otherwise, at -delta.
+xlimit   = 0; % If this in 1, the plots start at time 0. Otherwise, at -delta.
 
 if quantil
     numPaths = 5000;
@@ -18,8 +18,8 @@ else
     numPaths = 5;
 end
 
-theta = 3.912;
-alpha = 0.019308;
+theta_0 = 3.912;
+alpha   = 0.019308;
 
 d  = Table_Testing_Complete.Date;
 p  = Table_Testing_Complete.Forecast;
@@ -52,7 +52,7 @@ for i = 1 : height(Table_Testing_Complete)
     end
     P_dot   = (-P(1:end-1) + P(2:end)) / dt; % This starts at 1 end ends at (end - 1).
     for j = 1:length(P)-1
-        Theta_t(j) = theta_t(theta, alpha, P(j), P_dot(j));
+        Theta_t(j) = theta_t(theta_0, alpha, P(j), P_dot(j));
     end
     
     % We assume that the forecast is perfect one hour before it starts.
@@ -69,8 +69,7 @@ for i = 1 : height(Table_Testing_Complete)
     
     for k = 1:numPaths
         for j = 1 : length(exten_t)-1
-            sim_path(k,j+1) = sim_path(k,j) + (P_dot(j)-Theta_t(j)*(sim_path(k,j)-P(j)))*dt +...
-                sqrt(dt)*sqrt(2*Theta_t(j)*alpha*sim_path(k,j)*(1-sim_path(k,j)))*randn(1);
+            sim_path(k,j+1) = sde_FE(sim_path(k,j),alpha,theta_0,Theta_t(j),dt,P(j),P_dot(j));
             if sim_path(k,j+1) > 1
                 sim_path(k,j+1) = 1;
             elseif sim_path(k,j+1) < 0

### 2020-04-03 Reports/20200403 - Moments_all/20200403 - Moments_all.tex
The file moments_verification_Lamperti.e seems to be working almost correctly. I noticed that in the SDE for the second moment, it was necessary a sqrt(). However, now we need to choose another Lamp. Transform, because of this square root.

\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{commath}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{siunitx}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}
\DeclareMathOperator{\sign}{sign}

\title{Error SDE ($Z_t$) moments}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Introduction:} \label{S1}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_1.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_2.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_3.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_4.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_5.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_6.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_7.eps}
\end{figure}

\end{frame}

\end{document}

### 2020-04-03 MATLAB_Files/moment_1_L.m

@@ -1,4 +1,4 @@
-function m1 = moment_1_L(z,theta,alpha,p1,p2,dt,n)
+function m1 = moment_1_L(z,theta_0,alpha,p1,p2,dt,n)
     % 29/03/2020 16:28
     p_dot   = (p2-p1) / dt;
     m1(1)   = z;
@@ -6,11 +6,11 @@ function m1 = moment_1_L(z,theta,alpha,p1,p2,dt,n)
     ds      = dt/n;
     
     for i = 2:n
-        Theta_t = theta_t(theta, alpha, p_t(i), p_dot);
+        Theta_t = theta_t(theta_0, alpha, p_t(i), p_dot);
         m1(i)   = m1(i-1) + ds * ...
-            ((alpha*theta-Theta_t) * sin(m1(i-1)*sqrt(2*alpha*theta)) - ...
+            ((alpha*theta_0-Theta_t) * sin(m1(i-1)*sqrt(2*alpha*theta_0)) - ...
             Theta_t*(1-2*p_t(i)) + 2*p_dot) / ...
-            (sqrt(2*alpha*theta) * cos(m1(i-1)*sqrt(2*alpha*theta)));
+            (sqrt(2*alpha*theta_0) * cos(m1(i-1)*sqrt(2*alpha*theta_0)));
     end
     
 end

### 2020-04-03 MATLAB_Files/moments_verification.m

@@ -8,14 +8,14 @@ Table_Testing_Complete = load_data_eps_test(epsilon);
 t  = Table_Testing_Complete.Time(1,:);
 dt = t(2);
 
-theta_0 = 3.912;
-alpha   = 0.019308;
+theta_0 = 1.2656;
+alpha   = 0.07052;
 n       = 100;
 p_end   = 1/2;
 p_lims  = 0.03;
 
 p = p_end-p_lims:0.001:p_end+p_lims;
-v = -0.2:0.001:0.2;
+v = -0.3:0.001:0.3;
 
 for i = 1:length(p)
     for j = 1:length(v)

### 2020-04-03 MATLAB_Files/moments_verification_Lamperti.m

@@ -8,107 +8,219 @@ Table_Testing_Complete = load_data_eps_test(epsilon);
 t  = Table_Testing_Complete.Time(1,:);
 dt = t(2);
 
-theta_0 = 3.912;
-alpha   = 0.019308;
+theta_0 = 1.2656;
+alpha   = 0.07052;
+n       = 500;
 p_end   = 1/2;
-n       = 100;
+p_lims  = 0.03;
 
-lims = 0.1;
-
-p = lims:0.01:1-lims;
-x = lims:0.01:1-lims;
+p = p_end-p_lims:0.001:p_end+p_lims;
+v = -0.3:0.01:0.3;
 
 for i = 1:length(p)
-    for j = 1:length(x)
+    
+    for j = 1:length(v)
+        
+        disp([num2str(i/length(p)),' and ',num2str(j/length(v))]);
                 
-        v            = x(j) - p(i);
+        z = lamperti_transform(theta_0,alpha,v(j),p(i));
+        
         P_dot        = (p_end-p(i)) / dt;
         Theta_t      = theta_t(theta_0, alpha, p(i), P_dot);
-        Theta_t_next = theta_t(theta_0, alpha, p_end, 0);
         
-        Exp_V   = moment_1(v,Theta_t,Theta_t_next,dt,n);
-        Exp_V_2 = moment_2(v,Theta_t,Theta_t_next,p(i),p_end,alpha,Exp_V,dt,n);
-        
-        for k = 1:100
-            sim_path_x(k)   = sde_FE(x(j),alpha,theta_0,Theta_t,dt,p(i),P_dot);
-            sim_path_x_2(k) = sim_path_x(k)^2;
-            
-            sim_path_v(k)   = sde_FE_error(v,alpha,theta_0,Theta_t,dt,p(i));
-            sim_path_v_2(k) = sim_path_v(k)^2;
+        Exp_Z   = moment_1_L(z,theta_0,alpha,p(i),p_end,dt,n);
+        Exp_Z_2 = moment_2_L(Exp_Z,theta_0,alpha,p(i),p_end,dt,n) + Exp_Z(end)^2;
+                
+        parfor k = 1:100
+            sim_path_z(k)   = sde_Lamperti_FE(z,alpha,theta_0,Theta_t,dt,p(i),P_dot);
+            sim_path_z_2(k) = sde_Lamperti_FE_2(z^2,alpha,theta_0,Theta_t,dt,p(i),P_dot);
         end
[…]

### 2020-04-03 MATLAB_Files/path_simulator_Lamperti.m

@@ -34,8 +34,8 @@ else
     error('Wrong whatToDo script!');
 end
 
-Z_inf = lamperti_transform(theta_0,alpha,0,0) ;
-Z_sup = lamperti_transform(theta_0,alpha,1,0) ;
+Z_inf = lamperti_transform(theta_0,alpha,0,0);
+Z_sup = lamperti_transform(theta_0,alpha,1,0);
 Z_100 = (Z_sup-Z_inf)/100;
 
 d  = Table_Testing_Complete.Date;

### 2020-04-03 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
The file moments_verification_Lamperti.e seems to be working almost correctly. I noticed that in the SDE for the second moment, it was necessary a sqrt(). However, now we need to choose another Lamp. Transform, because of this square root.
The moments seem to be working well.

@@
 \item Which data in the histograms? Measurements or transitions?
+
+\item I had to add an artificial correction to ensure that the second moment is always positive. It is in function log\_LH\_evaluation.m.
 
@@
 \quad\\
-For now, we will use the {\color{blue}first candidate}.
+For now, we will use the {\color{red}second candidate}. The problem with the {\color{blue} first candidate} is that the mapping $Z_t\to Z_t^2$ is not injective.
 
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Lamperti moments:}
+\begin{frame}\frametitle{Lamperti SDE: {\color{blue} first candidate} (this slide may be deleted so soon...)}
 
@@
 As $X_t\in(\alert{0},1)$, we have that $Z_t\in\left(\alert{-\frac{\pi}{2}\frac{1}{\sqrt{2\alpha\theta_0}}},\frac{\pi}{2}\frac{1}{\sqrt{2\alpha\theta_0}}\right)$.
+{
+Also, we have that (computed with Mathematica):
+\begin{equation*}
+b'(z)=\frac{\dif b}{\dif z}(z)=\frac{\alpha\theta_0-\theta_t+(2\dot{p}_t+(2p_t-1)\theta_t)\sin(z\sqrt{2\alpha\theta_0}))}{\cos^2(z\sqrt{2\alpha\theta_0})}.
+\end{equation*}}
+
+\end{frame}
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Lamperti SDE: {\color{red} second candidate}}
+
+The Lamperti SDE is:
+\begin{align*}
+\dif Z_t= \underbrace{\left[\frac{\alpha\theta_0\cos(Z_t\sqrt{2\alpha\theta_0})-\theta_t\cos(Z_t\sqrt{2\alpha\theta_0})+2\theta_tp_t+2\dot{p}_t-\theta_t}{\sqrt{\alpha\theta_0}\sqrt{1-\cos(2Z_t\sqrt{2\alpha\theta_0})}}\right]}_{\coloneqq b(Z_t)} \dif t + \dif W_t .
+\end{align*}
+Here we follow Bayesian Filtering and Smoothing, Chapter 9. We use the linearization-based approximation for the moments.\\
+\quad\\
+As $X_t\in(\alert{0},1)$, we have that $Z_t({\color{blue}[0},\alert{1]})={\color{blue}\Big[\frac{-\pi}{\sqrt{2\alpha\theta_0}}},\alert{0\Big]}$.
+{
+Also, we have that (computed with Mathematica):
+\begin{equation*}
+b'(z)=\frac{\dif b}{\dif z}(z)=-\frac{\alpha\theta_0-\theta_t+\cos(\sqrt{2\alpha\theta_0}z)(2\dot{p}_t+\theta_t(2p_t-1))}{\left(\sin(\sqrt{2\alpha\theta_0}z)\right)^2}.
+\end{equation*}}
 
@@
 \sigma^2_L(s_{n})=\sigma^2_L(s_{n-1})+\left(1+2\sigma^2_L(s_{n-1})b'(\mu_L(s_{n-1}))\right)\Delta s.
-\end{equation*}
-We have that (computed with Mathematica):
-\begin{equation*}
-b'(z)=\frac{\dif b}{\dif z}(z)=\frac{\alpha\theta_0-\theta_t+(2\dot{p}_t+(2p_t-1)\theta_t)\sin(z\sqrt{2\alpha\theta_0}))}{\cos^2(z\sqrt{2\alpha\theta_0})}.
 \end{equation*}

### 2020-04-03 Reports/20200403 - Moments_all/20200403 - Moments_all.tex
The moments seem to be working well.

@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Introduction:} \label{S1}
+\begin{frame}\frametitle{Data histograms:}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/forecast_transitions.eps}\quad
+\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_measurement.eps}\quad
+\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_and_forecast.eps}
+\end{figure}
+From here we can see that the error transitions are approximately in the interval $[-0.3,0.3]$, and the forecast transitions in the interval $[-0.03,0.03]$.\\
+Then, we want to ensure that the moments are well approximated in the rectangle $[-0.3,0.3]\times[-0.03,0.03]$ (for $\Delta V\times\Delta p$).
 
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Approximated first moment for $Z_t$:}
+\begin{frame}\frametitle{Approximated moments for $Z_t$:}
 
@@
 
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Approximated moments for $Z_t$:}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/moments/lamperti/7.eps}
+\end{figure}
+
+\end{frame}
+
 \end{document}

### 2020-04-03 MATLAB_Files/lamperti_transform.m

@@ -1,8 +1,11 @@
-function [val] = lamperti_transform(theta_0,alpha,v,p) 
+function [val] = lamperti_transform(theta_0,alpha,v,p,candidate) 
 
     % 29/03/2020 17:49
 
-    val = (1/sqrt(2*alpha*theta_0)) * asin(2*(v+p)-1);
-%     val = -sqrt(2/(alpha*theta_0)) * asin(sqrt(1-v-p));
+    if candidate == 1
+        val = (1/sqrt(2*alpha*theta_0)) * asin(2*(v+p)-1);
+    elseif candidate == 2
+        val = -sqrt(2/(alpha*theta_0)) * asin(sqrt(1-v-p));
+    end
     
 end

### 2020-04-03 MATLAB_Files/sde_Lamperti_FE_2.m

@@ -1,20 +1,18 @@
-function sim_path_f = sde_Lamperti_FE_2(sim_path_i,alpha,theta_0,Theta_t,dt,P,P_dot) % 02/04/2020 20:40
+function sim_path_f = sde_Lamperti_FE_2(sim_path_i,alpha,theta_0,Theta_t,dt,P,P_dot)
 
-%     b = sde_Lamperti_drift(sim_path_i,alpha,theta_0,Theta_t,P,P_dot);
-% 
-%     sim_path_f = sim_path_i + dt * (2*b*sim_path_i + 1) + ...
-%         2 * sim_path_i * sqrt(dt) * randn(1);
+    % 02/04/2020 20:40
     
-    n  = 10;
+    n  = 50;
     dt = dt / n;
     fv = sim_path_i;
     
     for i = 1:n
-        % ADDED SQRT.
-        b = sde_Lamperti_drift(sqrt(sim_path_i),alpha,theta_0,Theta_t,P,P_dot);
 
-        sim_path_i = sim_path_i + dt * (2*b*sqrt(sim_path_i) + 1) + ...
-        2 * sqrt(sim_path_i) * sqrt(dt) * randn(1);
+        z = -sqrt(sim_path_i);
+        b = sde_Lamperti_drift_cand2(z,alpha,theta_0,Theta_t,P,P_dot);
+
+        sim_path_i = sim_path_i + dt * (2*b*z + 1) + ...
+        2 * z * sqrt(dt) * randn(1);
         sim_path_i = max(0,sim_path_i); % ARTIFICIAL.
         
     end

### 2020-04-04 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
Both optimizations seems to be working well. I still need to find a fixed point for Lamperti

@@
 \centering
-\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood.eps}
-\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_refined.eps}
-\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_more_refined.eps}
+\includegraphics[width=0.5\textwidth]{../Results/likelihood/normal/Log-Likelihood.eps}
+%\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_refined.eps}
+%\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_more_refined.eps}
 \caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions, and we can also see the initial guess.}
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Lamperti Log-likelihood evaluation (1/2): CODE}
+\begin{frame}\frametitle{Lamperti Log-likelihood evaluation: CODE}
 
@@
 
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Lamperti Log-likelihood evaluation (2/2):}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.5\textwidth]{../Results/likelihood/lamperti/Log-Likelihood.eps}
-\caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions.}
-\end{figure}
-
-\end{frame}
-
 \end{document}

### 2020-04-04 Reports/20200403 - Moments_all/20200403 - Moments_all.tex
Both optimizations seems to be working well. I still need to find a fixed point for Lamperti

@@
 \end{figure}
-From here we can see that the error transitions are approximately in the interval $[-0.3,0.3]$, and the forecast transitions in the interval $[-0.03,0.03]$.\\
-Then, we want to ensure that the moments are well approximated in the rectangle $[-0.3,0.3]\times[-0.03,0.03]$ (for $\Delta V\times\Delta p$).
+From here we can see that the errors are approximately in the interval $[-0.3,0.3]$, and the forecast transitions in the interval $[-0.03,0.03]$.\\
+Then, we want to ensure that the moments are well approximated in the rectangle $[-0.3,0.3]\times[-0.03,0.03]$ (for $V\times\Delta p$).
 

### 2020-04-04 Reports/20200404 - Lamperti Optimization/20200404 - Lamperti Optimization.tex
Both optimizations seems to be working well. I still need to find a fixed point for Lamperti

--- 2020-04-03 Reports/20200403 - Moments_all/20200403 - Moments_all.tex
@@
 
-\title{Error SDE ($Z_t$) moments}
+\title{Lamperti Optimization}
 \subtitle{Renzo Miguel Caballero Rosas}
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Introduction:} \label{S1}
+\begin{frame}\frametitle{Description:}
 
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Approximated first moment for $Z_t$:}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_1.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_1.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_1.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_1.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_1.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_1.eps}
-\end{figure}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Approximated first moment for $Z_t$:}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_2.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_2.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_2.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_2.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_2.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_2.eps}
-\end{figure}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Approximated first moment for $Z_t$:}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_3.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_3.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_3.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_3.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_3.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_3.eps}
-\end{figure}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Approximated first moment for $Z_t$:}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_4.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_4.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_4.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_4.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_4.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_4.eps}
-\end{figure}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Approximated first moment for $Z_t$:}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_5.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_5.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_5.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_5.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_5.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_5.eps}
-\end{figure}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Approximated first moment for $Z_t$:}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_6.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_6.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_6.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_6.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_6.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_6.eps}
-\end{figure}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Approximated first moment for $Z_t$:}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_7.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_7.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_7.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_7.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_7.eps}\quad
-\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_7.eps}
-\end{figure}
+Let $\{\Delta V_i\}_{i=1}^n$ be the set of all error transitions, and $\psi(\theta_0,\alpha,\Delta V)$ the Lamperti transform.
+Notice that the Lamperti transitions $\{\Delta Z_i\}_{i=1}^n$ depend on $(\theta_0,\alpha)$ because $$\{\Delta Z_i\}_{i=1}^n=\psi(\theta_0,\alpha,\{\Delta V_i\}_{i=1}^n).$$
+Then, if we compute $$\min_{(\theta_0,\alpha)}\mathbf{L}(\theta_0,\alpha,\{\Delta Z_i\}_{i=1}^n),$$
+we are \alert{NOT} computing a MLE in the classical sense.
+However, we can try to find ${\color{blue}(\theta_0^*,\alpha^*)}$ such that $${\color{blue}(\theta_0^*,\alpha^*)}=\arg\min_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{blue}\theta_0^*},{\color{blue}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).$$
+In this point, the likelihood has a maximum for the data set corresponding to that point.
 

### 2020-04-04 MATLAB_Files/log_LH_evaluation_L.m

@@ -6,11 +6,12 @@ function [value] = log_LH_evaluation_L(batch_complete, theta0, alpha, dt) % 03/0
         % Recall that: j is t_n and j-1 is t_{n-1}.
         p1 = batch_complete(1,j-1); p2 = batch_complete(1,j);
         z1 = batch_complete(5,j-1); z2 = batch_complete(5,j);
-        n = 10; % 10 discretizations for the ODEs.
+        n = 50; % 10 discretizations for the ODEs.
         
-        mu        = moment_1_L(z1,theta0,alpha,p1,p2,dt,n);
-        sig       = moment_2_L(mu,theta0,alpha,p1,p2,dt,n);
-        val(i)    = log_dist_L(z2,mu(end),sig(end));
+        mu     = moment_1_L(z1,theta0,alpha,p1,p2,dt,n);
+        sig2   = moment_2_L(mu,theta0,alpha,p1,p2,dt,n);
+        sig    = sqrt(sig2(end));
+        val(i) = log_dist_L(z2,mu(end),sig);
         
     end
     

### 2020-04-05 LaTeX_Code/Paper/paper_1line.tex
remark

@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
-\caption{Transitions after the Lamperti transform.
-The transitions now present a normal Gaussian shape.
-This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
-  \label{fig:LP_transitions}
-\end{figure}
 %---END SECTION 1---
@@
 
-Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $X_0 = p_0$.
+Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $  \mathbb{E} X_0 = p_0$.
 The application of  It\^{o}'s lemma on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s ds}$, leads to
@@
 \end{itemize}
-{\color{red} Observe that a mean reverting model without derivative tracking exhibits consistent lags, as it is shown in Figure (\ref{fig:derivative_tracking}).} See Section \ref{Section_7} for comparisons.
 
-\begin{figure}
+Remark: {\color{red} Observe that a mean-reverting model without derivative tracking shows a delayed path behavior.
+For instance, consider the diffusion model (\ref{eq:main}) with $a(X_t; p_t, \bm{\theta}) = - \theta_0 (X_t - p_t)\,, \theta_0 > 0$.
+In this case, given  $ \mathbb{E} X_0 = p_0$, the diffusion has mean $\mathbb{E} X_t = p_t - e^{- \theta_0 t } \int_0^t \dot{p}_s  e^{\theta_0 s} ds$.
+The next Figure (\ref{fig:derivative_tracking}) illustrates paths of two diffusions with and without derivative tracking.
+}
+
+\begin{figure}[h]
   %\includegraphics[width=26mm,scale=1]{}
-  \caption{insert figure showing the difference with and without derivative tracking}
+  \caption{Insert Figure showing the difference with and without derivative tracking}
   \label{fig:derivative_tracking}
@@
 The forecast and production wind power data of Uruguay are normalized with respect to the installed power capacity during the period of observation.
-Thus, the mean-reverting level lies in $[0,1]$, and the process $X$  must take values in the same interval,a requirement that is not automatically fulfilled through the derivative tracking.
+Thus, the mean-reverting level lies in $[0,1]$, and the process $X$  must take values in the same interval, a requirement that is not automatically fulfilled through the derivative tracking.
 To impose that the state space of $X$ is $[0,1]$, we may choose a convenient diffusion term, and require that the time-varying parameter $ \theta_t$ satisfies an ad-hoc condition.
@@
     dV_t \!\!\!&=  - \theta_t V_t  \, dt + \sqrt{2 \alpha \theta_0 (V_t +p_t ) (1-V_t-p_t)} \, dW_t\,, \quad t \in [0,T]  \\
-   V_0  \!\!\!&=  v_0\in [-1 + \delta,1 - \delta] \,.
+   V_0  \!\!\!&=  v_0\in [-1 + \epsilon,1 - \epsilon] \,.
  \end{array}\right.  \label{VtSDE}
@@
 
-{\color{red}We can see in Figure (\ref{fig:skew_after_lamperti}) the effect of the Lamperti transformation upon the forecast error data. 
+{\color{red}We can see in Figure (\ref{fig:LP_transitions}) the effect of the Lamperti transformation upon the forecast error data.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
+\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
+\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
+\caption{Transitions after the Lamperti transform.
+The transitions now present a normal Gaussian shape.
+This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
+  \label{fig:LP_transitions}
+\end{figure}
+
 The Lamperti transformation has greatly reduced the forecast error skewness, ensuring that the process stays in the range $[0,1]$.
 Therefore, in this case, the transition densities of the process Z can be adequately approximated through Gaussian densities.}
+
 %---END SECTION 3---
@@
 
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N$ equispaced discrete points with length interval $\Delta_N$, and let $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ denote this random sample.
+Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N$ equispaced discrete points with given length interval $\Delta$, and let $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ denote this random sample.
 

### 2020-04-09 LaTeX_Code/Paper/paper_1line.tex
update Lamperti, likelihood

@@
   %\includegraphics[width=26mm,scale=1]{}
-  \caption{Insert Figure showing the difference with and without derivative tracking}
+  \caption{Add Figure showing the difference with and without derivative tracking}
   \label{fig:derivative_tracking}
@@
 Z_t = h(V_t, t)  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \,dv \Bigg{\vert}_{v = V_t}  \nonumber \\
-& = \frac{1}{\sqrt{2 \alpha \theta_0 }} \arcsin (2(V_t + p_t) -1)
+& = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t})
 \end{align}
@@
 \end{align}
-After replacing $V_t = \frac{\sin(\sqrt{2 \alpha \theta_0} Z_t) + 1}{2} - p_t$ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
+After replacing $V_t = 1 - p_t - \sin^2 \left(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \right) $ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
 \begin{align}
-dZ_t & = \Bigg[ \frac{2 \dot{p}_t}{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}} + \frac{- \theta_t (\sin(\sqrt{2 \alpha \theta_0} Z_t) + 1 - 2 p_t)}{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}} \nonumber \\
-&  + \frac{\sqrt{2 \alpha \theta_0} \sin{(\sqrt{2 \alpha \theta_0} Z_t)}}{2 \cos{(\sqrt{2 \alpha \theta_0} Z_t)}} \Bigg] \,dt + dW_t \nonumber \\
-&  = \left[  \frac{(\alpha \theta_0 - \theta_t) \sin(\sqrt{2 \alpha \theta_0 } Z_t) - \theta_t (1 - 2 p_t) + 2  \dot{p}_t }{\sqrt{2 \alpha \theta_0} \cos{(\sqrt{2 \alpha \theta_0} Z_t)}}  \right] \,dt + dW_t \,.
+dZ_t & = \Bigg[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)}  \nonumber \\
+&  - \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \Bigg] \,dt + dW_t \nonumber \\
+&  = \left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \,dt + dW_t \,.
 \end{align}
@@
 
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N$ equispaced discrete points with given length interval $\Delta$, and let $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$ denote this random sample.
+Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$, and let $ V^{M,N + 1}=\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \}$ denote this random sample, with $V_{t_j^{N + 1}} = \{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \}, \, j = 1, \ldots, M$.
 
-Let $\rho_i(v \vert v_{j, t_{i-1}} ; \bm{\theta})$ denote the conditional probability density of $V_{j, t_i}$ given $V_{j, t_{i-1}} = v_{j, t_{i-1}}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha)$ are the unknown model parameters.
+Let $\rho(v \vert v_{j, i-1} ; \bm{\theta})$ be the conditional probability density of $V_{t_j + i \Delta} \equiv V_{j, i}$ given $V_{j, i-1} = v_{j, i-1}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha, \epsilon)$ are the unknown model parameters.
 
@@
 \begin{equation}
-\mathcal{L}(\bm{\theta},\delta; V^{M,N}) = \prod\limits_{j=1}^M \prod\limits_{i=1}^N \rho ( {V_{j, t_i}| V_{j, t_{i-1}}} ; p_{[t_{i-1}, t_{i}]},  \bm{\theta} )  \, \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
+\mathcal{L}(\bm{\theta}; V^{M,N +1}) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho ( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} )  \,  \right\} \,,
 \label{likelihood}
 \end{equation}
+where $t_{j ,i} \equiv  t_j + i \Delta$ for any $j = 1, \ldots, M$ and $i = 0, \ldots, N$.
 
- {\color{red} In \ref{likelihood} modify the expression for $\rho_0$ contemplating the lag, say $\delta$, between the time when the forecast is done and the first time of forecasting.
-$\rho_0$ can be written as a conditional density between these two times.
-Once $\theta_0$ and $\alpha$ have been estimated, one could estimate $\delta$.}
+ {\color{red} Remark: The statistical model (\ref{likelihood}) can be generalized incorporating the transition that occurs during the time interval, say $\delta$, between the time when the forecast is done and the first date of forecasting.
+In this case, the inner product in  (\ref{likelihood}) must include for any of the $M$ paths an additional factor, say $\rho_0 (V_{j, 0}|V_{j, -\delta};\bm{\theta},\delta)$, expressing the conditional density of this early transition.
+The parameter $\delta$ can be calibrated after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.}
 
@@
 \begin{align}
-\frac{ \partial f }{\partial t } & \rho_i(v_{j,i} ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} )= - \frac{\partial}{ \partial v} (- \theta_t v \, \rho_i(v ,t_{j,i} \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) ) \nonumber \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( 2 \theta_t \alpha (v+ p_t) (1 - v- p_t) \, \rho_i(v ,t_{j,i} \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) )\,,  \label{eq:fpk}
+\frac{ \partial f }{\partial t } & \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} )= - \frac{\partial}{ \partial v} (- \theta_t v \, \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) ) \nonumber \\
+& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( 2 \theta_0 \alpha (v+ p_t) (1 - v- p_t) \, \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) )\,,  \label{eq:fpk}
 \end{align}
-subject to the initial conditions $\rho_{i-1}(v , t_{j, i-1} , \bm{\theta} ) = \delta(v - V_{j, t_{i-1}}) \,,$ where $ \delta(v - V_{j, t_{i-1}})$ is the Dirac-delta generalized function centered at $ V_{j, t_{i-1}}\,.$
+subject to the initial conditions $\rho(v , t_{j, i-1} ; \bm{\theta} ) = \delta(v - V_{j, i-1}) \,,$ where $ \delta(v - V_{j, i-1})$ is the Dirac-delta generalized function centered at $ V_{j, i-1}\,.$
 

### 2020-04-10 LaTeX_Code/Paper/paper_1line.tex
remarks

@@
 
-Closed-form solutions to initial-boundary value problem for SDEs can be obtained only in a few cases.
+Closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases.
 Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
@@
 
-A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints which give rise to asymmetric forecasting errors as seen in figure (\ref{fig:skew_data}).\\
+Gaussian approximations to the transition densities of nonlinear time-in\-ho\-mo\-geneous SDEs are available through different algorithms  \autocite[Chapter 9]{saso}.
+However, as Figure (\ref{fig:error_transitions}) may suggest at a first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
 
-We propose a proxy transition density.
-We match the moments of our SDE model with that of the proxy density.
-Using It\^o formula, we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
+Therefore, we propose to use a surrogate transition density for $V$ other than Gaussian. The moments of the SDE model (\ref{VtSDE}) are then matched to the moments of the surrogate density.
+
+Using It\^o's lemma on , we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
 \begin{equation}

### 2020-04-10 LaTeX_Code/Paper/paper_1line.tex
moments beta

@@
 & =  e^{ - \int_{0}^{t} \theta_s ds} \left(  \mathbb{E} X_0 +   \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u du} ds +  \big[ p_s \, e^{\int_{0}^{s} \theta_u du} \big]^{t}_0  - \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u du} ds  \right) \nonumber \\
-& =  e^{ - \int_{0}^{t} \theta_s ds} \left(  \mathbb{E} X_0 + p_t \, e^{ \int_{0}^{t} \theta_s ds} - p_0 \right) = p_t \,.
+& =  e^{ - \int_{0}^{t} \theta_s ds} \left(  \mathbb{E} X_0 + p_t \, e^{ \int_{0}^{t} \theta_s ds} - p_0 \right) = p_t \,. \label{eq:meanX}
 \end{align}
@@
 Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.
-Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.
+ {\color{red} Rewrite: Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.}
 
@@
 
-Using It\^o's lemma on , we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
+From (\ref{eq:meanX}), we have $m_1(t) \equiv \mathbb{E} V_t = e^{- \int_{t_{j,i-1}}^t \theta_s ds} \,\mathbb{E} V_{t_{j,i-1}}$, for any $t\in [t_{j,i-1}, t_{j, i})$, $j = 1, \ldots, M$ and $i = 1, \ldots, N$ .
+
+For $m \geq 2$, using It\^o's lemma on $g(V_t) = V_t^m$, we obtain
+% arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
+\begin{align}
+d(V_t^m) & = \left( - m \theta_t V_t^m + \frac{1}{2} m (m -1) V_t^{m -2} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \right) dt  \nonumber \\
+& + m V_t^{m-1} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) dW_t \,, \nonumber
+\end{align}
+from which we derive
 \begin{equation}
-\frac{d \mathbb{E}[ V^k_t]}{dt} = - k \theta_t \mathbb{E}[ V^k_t] + \frac{k(k-1)}{2} \mathbb{E}[ V^{k-2}_t  b(V^k_t;\theta_t, \alpha)]
+\frac{d \mathbb{E}[ V^m_t]}{dt} = - m \theta_t \mathbb{E}[ V^m_t] + m (m-1) \alpha \theta_0  \mathbb{E}[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} ] \,.
 \end{equation}
 
-For $t\in [t_{n-1}, t]$, the first two moments are given by
-\begin{align}
-\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t   \nonumber \\
-\frac{d m_2 (t)}{dt} &=  -2 m_2(t)\theta_t(1+\alpha) + 2\alpha\theta_t m_1(t)(1-2p_t)  \nonumber \\
-&\quad + 2 \alpha\theta_t p_t (1-p_t) \,,
-\end{align}
-with initial conditions $m_1(t_{n-1})= v_{n-1}$ and $m_2(t_{n-1})= v_{n-1}^2 \,.$
+For any $t\in [t_{j,i-1}, t_{j, i})$, the first two moments of $V$, $m_1(t)$ and $m_2(t) \equiv \mathbb{E}[V_t^2]$, can be computed by solving the following system
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    \frac{d m_1 (t)}{dt} \!\!\!&=  - m_1(t)\theta_t   \\
+   \frac{d m_2 (t)}{dt}  \!\!\!&=  -2 (\theta_t +\alpha \theta_0) m_2(t) + 2 \alpha\theta_0 (1-2p_t)  m_1(t) + 2 \alpha\theta_0 p_t (1-p_t) 
+ \end{array}\right.  \label{Vtmom}
+\end{equation}
+with initial conditions $m_1(t_{j,i-1})= v_{j, i-1}$ and $m_2(t_{j,i-1})= v_{j, i-1}^2 \,.$
+
+\subsubsection*{ Moment Matching}
+A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape real parameters, $\xi_1, \xi_2$.
+
+To approximate the transition densities of  the process $V$ using a Beta distribution, we equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$ .
+
+The shape parameters are given by
+\begin{equation}
+\xi_1 = - \frac{(\mu_t + 1 - \epsilon)(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2}\,, \quad \xi_2=  \frac{(\mu_t-1 + \epsilon )(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2} \,, \label{param_transformed_beta}
+\end{equation}
+where $\mu_t = m_1 (t)$ and $\sigma_t^2= m_2 (t)- m_1 (t)^2\,.$ \\
 
@@
 \end{align}
-
-A suitable candidate for a proxy transition density is a Beta probability distribution as it is compactly supported and can morph into symmetric and asymmetric shapes.
-{\color{red} Move this sentence to next section.}
-
-\subsubsection*{ Moment Matching}
-To approximate the transition densities of  the process $V_t$ by a Beta distribution, we match its moments with the shape parameters $\xi_1, \xi_2$ of a Beta proxy density on $[-1,1]$.
-The any moment of the process $V_t$ is  given by solving the corresponding ODE system  for the $k^{th}$  moment,
-
-The shape parameters are given by
-\begin{equation}
-\xi_1 = - \frac{(1+\mu_t )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2}\,, \quad \xi_2=  \frac{(\mu_t-1 )(\mu_t^2 + \sigma_t^2 -1)}{2 \sigma_t^2} \,, \label{param_transformed_beta}
-\end{equation}
-where $\mu_t = m_1 (t)$ and $\sigma_t^2= m_2 (t)- m_1 (t)^2\,.$
 

### 2020-04-10 Reports/20200404 - Lamperti Optimization/20200404 - Lamperti Optimization.tex
Added some references.

@@
 Notice that the Lamperti transitions $\{\Delta Z_i\}_{i=1}^n$ depend on $(\theta_0,\alpha)$ because $$\{\Delta Z_i\}_{i=1}^n=\psi(\theta_0,\alpha,\{\Delta V_i\}_{i=1}^n).$$
-Then, if we compute $$\min_{(\theta_0,\alpha)}\mathbf{L}(\theta_0,\alpha,\{\Delta Z_i\}_{i=1}^n),$$
+Then, if we compute $$\max_{(\theta_0,\alpha)}\mathbf{L}(\theta_0,\alpha,\{\Delta Z_i\}_{i=1}^n),$$
 we are \alert{NOT} computing a MLE in the classical sense.
-However, we can try to find ${\color{blue}(\theta_0^*,\alpha^*)}$ such that $${\color{blue}(\theta_0^*,\alpha^*)}=\arg\min_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{blue}\theta_0^*},{\color{blue}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).$$
+However, we can try to find a fixed point ${\color{blue}(\theta_0^*,\alpha^*)}$ such that $${\color{blue}(\theta_0^*,\alpha^*)}=\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{blue}\theta_0^*},{\color{blue}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).$$
 In this point, the likelihood has a maximum for the data set corresponding to that point.

### 2020-04-10 MATLAB_Files/path_simulator_Lamperti.m

@@ -11,8 +11,8 @@ whatToDo               = 'lamperti_clasic_optimal';
 % PARAMETERS:
 % set(0,'defaultAxesFontSize',18);
 quantil  = 1;
-save     = 0;
-delta    = 22; % The time is delta*10 minutes.
+save     = 1;
+delta    = 21; % The time is delta*10 minutes.
 xlimit   = 1; % If this in 1, the plots start at time 0. Otherwise, at -delta.
 
 if quantil
@@ -22,20 +22,20 @@ else
 end
 
 if  strcmp(whatToDo,'lamperti_clasic_optimal')
-    theta_0 = 3.912;
-    alpha   = 0.019308;
+    theta_0 = 1.180;
+    alpha   = 0.070;
 elseif  strcmp(whatToDo,'lamperti_clasic_IG')
     theta_0 = 1.6290;
     alpha   = 0.06;
 elseif  strcmp(whatToDo,'lamperti_optimal')
-    theta_0 = 7.5;
-    alpha   = 0.9;
+    theta_0 = 2.200;
+    alpha   = 0.038;
 else
     error('Wrong whatToDo script!');
 end
 
-Z_inf = lamperti_transform(theta_0,alpha,0,0);
-Z_sup = lamperti_transform(theta_0,alpha,1,0);
+Z_inf = lamperti_transform(theta_0,alpha,0,0,2);
+Z_sup = lamperti_transform(theta_0,alpha,1,0,2);
 Z_100 = (Z_sup-Z_inf)/100;
 
 d  = Table_Testing_Complete.Date;
@@ -56,7 +56,7 @@ for i = 1 : height(Table_Testing_Complete)
 
     X   = x(i,:);
     P   = p(i,:);
-    Z   = lamperti_transform(theta_0,alpha,X-P,P);
+    Z   = lamperti_transform(theta_0,alpha,X-P,P,2);
     
     P_exten_linear = interp1([0 6*dt],[P(1) P(6)],minus_t,'linear','extrap');
     P              = [P_exten_linear,P]; % We extend the forecast.
@@ -69,7 +69,7 @@ for i = 1 : height(Table_Testing_Complete)
     for j = 1:length(P)-1
         Theta_t(j) = theta_t(theta_0, alpha, P(j), P_dot(j));
     end
-    Z_P = lamperti_transform(theta_0,alpha,P,0);
+    Z_P = lamperti_transform(theta_0,alpha,P,0,2);
     % Z_P is the Lamperti transform of the forecast.
     
[…]

### 2020-04-13 LaTeX_Code/Paper/paper_1line.tex
section 4.2

@@
 
-Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $  \mathbb{E} X_0 = p_0$.
+Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} X_t = p_t$, given $  \mathbb{E} X_0 = p_0$.
 The application of  It\^{o}'s lemma on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s ds}$, leads to
@@
 Z_t = h(V_t, t)  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \,dv \Bigg{\vert}_{v = V_t}  \nonumber \\
-& = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t})
+& = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
 \end{align}
-that, after applying It\^{o}'s formula on $h(V_t, t)$, leads to the following SDE with state independent diffusion term
+that, after applying It\^{o}'s formula on $h(V_t, t)$, leads to the following SDE with state independent unit diffusion term
 \begin{align}
@@
 &  = \left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \,dt + dW_t \,.
+\label{eq:stindepSDE2}
 \end{align}
@@
 
-The It\^{o} process $V$ defined by the SDE (\ref{VtSDE}) is Markovian, then the likelihood function of the data can be written as the following product of transition densities:  
-%Consider the set of $M$ paths with $N$ observations each, $ V^{M,N}=\{ V_{t_1^{M,N}} , V_{t_2^{M,N}} ,\ldots , V_{t_N^{M,N}} \}$, observed in $\Delta_N$ intervals.
+The It\^{o} process $V$ defined by the SDE (\ref{VtSDE}) is Markovian, then the likelihood function of the sample $ V^{M,N + 1}$ can be written as the following product of transition densities:
+
 \begin{equation}
@@
 
-And for the state independent diffusion formulation, similarly, we  obtain a system of ODEs to determine the centered moments of the Lamperti transformed process $V_t$.
-Due to the non-linearity in the drift, we can only approximate the centered moments by the following ODEs,
-\begin{align}
-\frac{d m_1 (t)}{dt} &= - m_1(t)\theta_t (1-\alpha) - \theta (1-2 p_t) \nonumber \\
-\frac{d var(t)}{dt} &=  2 var(t) \theta_t (2p_t - 1 ) \tan(m_1 (t)) \sec(m_1 (t))   \nonumber \\
-& \quad + \theta_t (\alpha - 1) \sec^2(m_1 (t))  + 2 \theta_t \alpha \,.
-\end{align}
+The transition density of the process $Z$, which has been defined through the Lamperti transformation (\ref{eq:LampZ}) of $V$, can be conveniently approximated by a Gaussian surrogate density.
+
+The drift coefficient $a(Z_t; p_t, \dot{p}_t, \bm{\theta}) $ of the process $Z$ that satisfies (\ref{eq:stindepSDE2}) is nonlinear.
+After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}Z_t$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i})$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}Z_t$ and $\tilde{v}_Z(t) \approx \text{Var} Z_t$ :\\
+\begin{equation}
+  \left\{
+  \begin{array}{@{}rl@{}}
+    \frac{d \tilde{\mu}_Z (t)}{dt} \!\!\!&=  a\big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big)   \\
+    \frac{d \tilde{v}_Z (t)}{dt}  \!\!\!&= 2  a^{\prime} \big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big) \tilde{v}_Z (t) + 1
+ \end{array}\right.  \label{Ztmom}
+\end{equation}
+with initial conditions $\tilde{\mu}_Z(t_{j,i-1})= z_{j, i-1}$ and $\tilde{v}_Z(t_{j,i-1})= 0 \,,$ and where 
+\begin{equation*}
+a^{\prime} \big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big) =    \frac{  (\alpha \theta_0 - \theta_t)  - \cos(\sqrt{2 \alpha \theta_0 } Z_t) [ \theta_t (1 - 2 p_t) - 2  \dot{p}_t ] }{\sin^2{(\sqrt{2 \alpha \theta_0} Z_t)}} \,.
+\end{equation*}
 

### 2020-04-14 LaTeX_Code/Paper/paper_1line.tex
approximate likelihoods

@@
 
-Remark: {\color{red} Observe that a mean-reverting model without derivative tracking shows a delayed path behavior.
+Remark: Observe that a mean-reverting model without derivative tracking shows a delayed path behavior.
 For instance, consider the diffusion model (\ref{eq:main}) with $a(X_t; p_t, \bm{\theta}) = - \theta_0 (X_t - p_t)\,, \theta_0 > 0$.
@@
 The next Figure (\ref{fig:derivative_tracking}) illustrates paths of two diffusions with and without derivative tracking.
-}
 
@@
   %\includegraphics[width=26mm,scale=1]{}
-  \caption{Add Figure showing the difference with and without derivative tracking}
+  \caption{{\color{red} Add Figure showing the difference with and without derivative tracking}}
   \label{fig:derivative_tracking}
@@
 
-{\color{red}We can see in Figure (\ref{fig:LP_transitions}) the effect of the Lamperti transformation upon the forecast error data.
+{\color{red} We can see in Figure (\ref{fig:LP_transitions}) the effect of the Lamperti transformation upon the forecast error data.
 
@@
 
+The approximate log-likelihood $\tilde{\ell}(\cdot ; v^{V, N+1})$ of the observed sample $v^{V, N+1}$ can be expressed as 
+\begin{equation}
+ \tilde{\ell} (\bm{\theta}; v^{M,N +1}) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1, \xi_2)} \Big( \frac{z_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \Big)^{\xi_1 -1}  \Big( \frac{1 - \epsilon - z_{j,i}}{2(1 - \epsilon)} \Big)^{\xi_2 -1} \right\} \,,
+\label{loglikelihoodV}
+\end{equation}
+where the shape parameters $\xi_1$ and $\xi_2$, according to (\ref{param_transformed_beta}), depend on the quantities $\mu(t_{j,i};\bm{\theta} )$ and $\sigma^2(t_{j,i};\bm{\theta} )$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
+\\
+
 The transition density of the process $Z$, which has been defined through the Lamperti transformation (\ref{eq:LampZ}) of $V$, can be conveniently approximated by a Gaussian surrogate density.
@@
 \end{equation*}
+
+The approximate log-likelihood $\tilde{\ell}(\cdot ; z^{V, N+1})$ of the observed sample $z^{V, N+1}$ is given by
+\begin{equation}
+\tilde{\ell} (\bm{\theta}; z^{M,N +1}) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i};\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}; \bm{\theta})} \Bigg) \right\}   \,,   \label{loglikelihoodZ}
+\end{equation}
+where $\tilde{\mu}_Z(t_{j,i};\bm{\theta} )$ and $\tilde{v}_Z(t_{j,i};\bm{\theta} )$ are computed solving numerically the initial-value problem (\ref{Ztmom}).
 

### 2020-04-14 Reports/20200412 - Main Results/20200412 - Main Results.tex
Added the slides with all the results, and separated the paper into 2 (for Marco and Renzo)

\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{commath}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{siunitx}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}
\DeclareMathOperator{\sign}{sign}

\title{Main Results}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\begin{frame}
\titlepage
The rest can be found in: \textbf{Summary of Advances and Questions}.
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=green!20}
\begin{frame}

{\Huge About the data:}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Curtailing and Delay:}
Files: \textbf{curt\_and\_error.eps} and \textbf{curt\_and\_error\_corr.eps} (dataConditioner.m, cell (2)).
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/curt_and_error.eps}\quad\quad
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/curt_and_error_corr.eps}
\end{figure}

Source 1 has the correct timing; source 2 shows the curtailing and has more frequency. From both sources, we can choose and construct an accurate real production for each day.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Curtailing histograms:}
Files: \textbf{all2019.eps} and \textbf{partially2019.eps} (dataConditioner.m, cell (8)).
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/all2019.eps}\quad\quad
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/partially2019.eps}
\end{figure}

Histograms for the daily mean relative error. On the left, the 365 days. On the right, the corrected data (removed the days with curtailing or other errors).

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Error histograms WITH curtailing:}

\begin{columns}

\column{.4\textwidth}
Files: \textbf{LP\_6.eps}, \textbf{MP\_6.eps}, \textbf{HP\_6.eps}, and \textbf{AP\_6.eps} (dataConditioner.m, cell (12)).\\
\quad\\
Forecast error for different values of the real production. $LP=[0,0.3)$, $MP=[0.3,0.6)$, and $HP=[0.6,1]$. We have also a histogram for all values of power.

\column{.6\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/LP_6.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/MP_6.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/HP_6.eps}\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/AP_6.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Error histograms WITHOUT curtailing:}

\begin{columns}

\column{.4\textwidth}
Files: \textbf{LP.eps}, \textbf{MP.eps}, \textbf{HP.eps}, and \textbf{AP.eps} (dataConditioner.m, cell (11)).\\
\quad\\
Forecast error after cleaning the data for different values of the real production. $LP=[0,0.3)$, $MP=[0.3,0.6)$, and $HP=[0.6,1]$. We have also a histogram for all values of power.

\column{.6\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/LP.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/MP.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/HP.eps}\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/AP.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Lamperti histograms WITHOUT curtailing:}

\begin{columns}

\column{.4\textwidth}
Files: \textbf{LP\_LP.eps}, \textbf{MP\_LP.eps}, \textbf{HP\_LP.eps}, and \textbf{AP\_LP.eps} (dataConditioner.m, cell (11)).\\
\quad\\
Lamperti after cleaning the data for different values of the real production. $LP=[0,0.3)$, $MP=[0.3,0.6)$, and $HP=[0.6,1]$. We have also a histogram for all values of power.

\column{.6\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/LP_LP.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/MP_LP.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/HP_LP.eps}\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/AP_LP.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Error transitions histograms WITHOUT curtailing:}

\begin{columns}

\column{.4\textwidth}
Files: \textbf{LP\_t.eps}, \textbf{MP\_t.eps}, \textbf{HP\_t.eps}, and \textbf{AP\_t.eps} (dataConditioner.m, cell (11)).\\
\quad\\
Forecast error transitions after cleaning the data for different values of the real production. $LP=[0,0.3)$, $MP=[0.3,0.6)$, and $HP=[0.6,1]$. We have also a histogram for all values of power.

\column{.6\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/LP_t.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/MP_t.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/HP_t.eps}\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/AP_t.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Lamperti error transitions histograms WITHOUT curtailing:}

\begin{columns}

\column{.4\textwidth}
Files: \textbf{LP\_t\_LP.eps}, \textbf{MP\_t\_LP.eps}, \textbf{HP\_t\_LP.eps}, and \textbf{AP\_t\_LP.eps} (dataConditioner.m, cell (11)).\\
\quad\\
Lamperti error transitions after cleaning the data for different values of the real production. $LP=[0,0.3)$, $MP=[0.3,0.6)$, and $HP=[0.6,1]$. We have also a histogram for all values of power.\\
\quad\\
We transformed using the initial guesses.

\column{.6\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/LP_t_LP.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/MP_t_LP.eps}
\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/HP_t_LP.eps}\includegraphics[width=0.45\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/AP_t_LP.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Gaussian approximation for the transitions:}
Files: \textbf{Gauss\_Approx.eps} (dataConditioner.m, cell (11)).
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/Gauss_Approx.eps}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Gaussian approximation for the transitions:}
Files: \textbf{Gauss\_Approx\_Err.eps}, and \textbf{Gauss\_Approx\_Lam.eps} (dataConditioner.m, cell (11)).
\begin{figure}[ht!]
\centering
\includegraphics[width=0.48\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/Gauss_Approx_Err.eps}
\includegraphics[width=0.48\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/Gauss_Approx_Lam.eps}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Forecast and production:}
Files: \textbf{allDaysPlots/1.eps}, and \textbf{allDaysPlots/2.eps} (dataConditioner.m, cell (11)).
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/allDaysPlots/1.eps}
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/allDaysPlots/2.eps}\end{figure}

We have this forecast and production plots for the 255 days.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Seasonality effect:}

\begin{columns}

\column{.4\textwidth}
Files: \textbf{seasons.eps} (dataConditioner.m, cell (11)).\\
\quad\\
Daily and weakly mean absolute error between the forecast and the real production. We can see no significant seasonality effect.

\column{.6\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/seasons.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Hourly effect:}

\begin{columns}

\column{.4\textwidth}
Files: \textbf{hourlyEffect.eps} (dataConditioner.m, cell (11)).\\
\quad\\
Hourly mean absolute error between the forecast and the real production. We can see a significant reduction in the error during the day.

\column{.6\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/forPaper/hourlyEffect.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{ME and AME for different intervals of forecast:}
Files: \textbf{mean\_error.eps} and \textbf{mean\_abs\_error.eps} (erroVsForecast.m).\\
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/mean_error.eps}\quad\quad
\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/mean_abs_error.eps}
\end{figure}
{\footnotesize What we are seeing is the \textbf{mean error} and \textbf{mean absolute error} as a function of the forecast. This is, for each interval with length 0.1 (i.e., [0,0.1), [0.1,0.2), etc.), we average all the errors corresponding to measurement where the forecast was in that intervals, and after we average over the number of elements in each interval.}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}\frametitle{Error Vs. Forecast for all training days (scatter plot):}
Files: \textbf{error\_over\_forecast.eps} (erroVsForecast.m).

\begin{figure}[ht!]
\centering
\includegraphics[width=0.75\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/error_over_forecast.eps}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Forecast and error histograms:}
Files: \textbf{MATLAB\_Files/Results/histograms/others} (some\_histograms.m).\\

\begin{figure}[ht!]
\centering
\includegraphics[width=0.31\textwidth]{../../MATLAB_Files/Results/histograms/others/forecast_transitions.eps}\quad
\includegraphics[width=0.31\textwidth]{../../MATLAB_Files/Results/histograms/others/error_measurement.eps}\quad
\includegraphics[width=0.31\textwidth]{../../MATLAB_Files/Results/histograms/others/error_and_forecast.eps}
\end{figure}
From here we can see that the errors are approximately in the interval $[-0.3,0.3]$, and the forecast transitions in the interval $[-0.03,0.03]$.\\
Then, we want to ensure that the moments are well approximated in the rectangle $[-0.3,0.3]\times[-0.03,0.03]$ (for $V\times\Delta p$).

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=green!20}
\begin{frame}

{\Huge Simulations and Results:}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Lamperti transform plot:}

\begin{columns}

\column{.5\textwidth}
Files: \textbf{Mathematica\_Files/Range\_Z.pdf} (Range\_Z.nb).\\
\quad\\
Plot of $Z_t$ as a function of $X_t$ from 0 to 1. We choose $\alpha=0.06$, and $\theta_t=1.63$ (initial guess).

\column{.5\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{../../Mathematica_Files/Range_Z.pdf}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\theta_0^*$ using LSM over different sets}

Files: \textbf{MATLAB\_Files/Results/epsilon}: \textbf{theta\_0.eps} and \textbf{num\_over\_eps\_t0.eps} (plot\_epsilon.m, third cell).\\

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/epsilon/theta_0.eps}\quad\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/epsilon/num_over_eps_t0.eps}
\end{figure}

On the right, the number of samples as a function of $\gamma$. This samples satisfies that $p_i\in[\gamma,1-\gamma]$. On the left, the LSM over the samples that satisfies the $\gamma$ condition.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Estimation of $(\theta_0,\alpha,\epsilon)$: $\epsilon$ using LSM over different sets}

Files: \textbf{MATLAB\_Files/Results/epsilon}: \textbf{LSM.eps} and \textbf{num\_over\_eps.eps} (plot\_epsilon.m, second cell).\\

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/epsilon/LSM.eps}\quad\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/epsilon/num_over_eps.eps}
\end{figure}

On the right, the number of samples as a function of $\epsilon$. This samples satisfies that $p_i^\epsilon\in\{\epsilon,1-\epsilon\}$. On the left, the LSM for $\epsilon$,over the samples that satisfies the $\epsilon$ condition.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{$\delta$ over $\eta$:}

Files: \textbf{MATLAB\_Files/Results/delta}: \textbf{eta\_min\_ini.eps} and \textbf{eta\_min\_opt.eps} (initiasl\_time.m, second cell).\\

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/delta/eta_min_ini.eps}\quad\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/delta/eta_min_opt.eps}
\end{figure}
We use the initial transitions that satisfies $|\Delta V|<\eta$. On the left, we use the initial $(\theta_0,\alpha)$ ($\alpha\theta_0=0.098$) and we get $\delta=\SI{220}{\min}$. On the right, we use the optimal ones. As the optimal product $\alpha\theta_0$ ($\alpha\theta_0=0.083$) is smaller than the initial one, we need either a larger $\delta$ to match the variance of the initial error, or to remove some data.
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Probability bands for model with delay:}
Files: \textbf{MATLAB\_Files/Results/bands\_testing\_days/model\_1} (path\_simulator\_OPT\_model\_1.m).

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/model_1/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/model_1/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/model_1/3.eps}
\end{figure}

We used the optimal parameters of the error SDE. We have results for the 128 testing days.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Probability bands for Lamperti:}
Files: \textbf{MATLAB\_Files/Results/bands\_testing\_days/lamperti\_optimal} (path\_simulator\_Lamperti.m).

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/lamperti_optimal/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/lamperti_optimal/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/lamperti_optimal/3.eps}
\end{figure}

We used the Lamperti optimal parameters to simulate the Lamperti SDE. We have results for the 128 testing days.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Paths for Lamperti:}
Files: \textbf{MATLAB\_Files/Results/paths\_testing\_days/lamperti\_optimal} (path\_simulator\_Lamperti.m).

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/lamperti_optimal/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/lamperti_optimal/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/lamperti_optimal/3.eps}
\end{figure}

We used the Lamperti optimal parameters to simulate the Lamperti SDE. We have results for the 128 testing days.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2020-04-17 LaTeX_Code/Paper/paper_1line_Renzo.tex
Added initial guess in Paper. Still not complete.

--- 2020-04-14 LaTeX_Code/Paper/paper_1line.tex
@@
 \usepackage{url}
+\usepackage[margin=0.5in]{geometry}
 
@@
 \newcommand{\red}{\textcolor{red}}
+\newcommand{\E}{\mathbb{E}}
+\newcommand{\R}{\mathbb{R}}
 
@@
 \subsection{Optimization} \label{opt_sec}
-{\color{red} Rewrite the discussion to obtain fast initial estimate for the two unknow parameters.}
 
-To initialize the optimization process for the likelihood function of the process $V$, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$: {\color{red} Add explanation regarding the motivation for this objective function.}
+\subsubsection{Initial guess}
 
+To guarantee the good behave for our optimization algorithm, we aim to start the optimization as close as we can from the optimal parameters.
+We use \textbf{Lease Square Minimization} and \textbf{Quadratic Variation} to find an initial guess from the data.
+
+\begin{itemize}
+
+\item \textbf{Least Square Minimization:} We consider the transition $\Delta V_i=V_{i+1}-V_i$ with $\Delta t=t_{i+1}-t_i$.
+$(V_{i+1}|V_i)$ is a random variable which conditional mean can be approximated by the solution of the system
+\begin{equation*}
+\begin{cases}
+\dif \E\left[V\right]&=-\theta_t^\epsilon\E\left[V\right]\dif t\\
+\E\left[V(t_i)\right]&=V_i,
+\end{cases}
+\end{equation*}
+evaluated in $t_{i+1}$ (i.e., $\E\left[V(t_{i+1})\right]$). Then, the random variable $(V_{i+1}-\E\left[V(t_{i+1})\right])$ has approximately zero mean.\\
+If we assume that $\theta_t^\epsilon={\color{red}c}\in\R^+$ for all $t\in[t_i,t_{i+1}]$, then $\E\left[V(t_{i+1})\right]=V_ie^{-{\color{red}c}\Delta t}$.
+If we have a total of $n$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
 \begin{equation}
-\theta_0\approx\arg\min_{\theta} \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2,
-\label{inital_theta}
+{\color{red}c}^*\approx\arg\min_{{\color{red}c}\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-\E\left[V(t_{i+1})\right]\right)^2\right]=\arg\min_{{\color{red}c}\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-V_ie^{-{\color{red}c}\Delta t}\right)^2\right].
+\label{Eq-1}
+\end{equation}
+\begin{equation*}
+\begin{split}
+\frac{\partial f}{\partial{\color{red}c}}&=\sum_{i=1}^n2(-V_i)(-\Delta t)(V_{i+1}-V_i(1-\theta_0\Delta t))\\
+&=\sum_{i=1}^n2V_i\Delta t(V_{i+1}-V_i(1-{\color{red}c}\Delta t))\\
+&=\sum_{i=1}^n2V_{i+1}V_i\Delta t-2V_i^2\Delta t+2V_i^2\Delta t^2{\color{red}c}.
+\end{split}
+\end{equation*}
+Then, ${\color{red}c}^{**}$ satisfies
+\begin{equation}
+{\color{red}c}^{**}\approx\frac{\sum_{i=1}^nV_i(V_i-V_{i+1})}{\Delta t\cdot\sum_{i=1}^n(V_i)^2}.
+\label{Eq-4}
+\end{equation}
+Notice that ${\color{red}c}^{**}$ has dimension $\mathbf{time}^{-1}$.
+
+\item \textbf{Quadratic Variation:} We approximate the SDE by its E-M scheme. In particular, we approximate the It\^o quadratic variation with the discrete one:
+\begin{itemize}
+
+\item It\^o process quadratic variation: $[V]_t=\int_0^t\sigma_s^2\dif s$.
+\item Discrete process quadratic variation: $[V]_t=\sum_{0<s\leq t}(\Delta V_s)^2$.
+
+\end{itemize}
+\quad\\
+\quad\\
+Then, considering $\Delta t$ the time between measurements, we approximate:
+\begin{equation}
+\theta_0^*\alpha^*\approx\frac{\sum_{i=1}^n(\Delta V_i)^2}{2\Delta t\sum_{i=1}^n(V_i+p_i)(1-V_i-p_i)}.
+\label{Eq-2}
 \end{equation}
 
- where $v_{i,j}=x_{i,j}-p_{i,j}$,  $x_{i,j}$ is historical wind power production and $p_{i,j}$ is the wind power forecast.
+\end{itemize}
 
- By assuming ergodicity {\color{red} not ergodicity, instead simply for the \textbf{quadratic variation formula}.}, we can obtain a first estimate on the product of the parameters as follows,
+In slide ({\color{blue}\ref{theta_t}}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$.
+We want to estimate the set of parameters $(\theta_0,\alpha,\epsilon)$, we call to the estimations $(\theta_0^*,\alpha^*,\epsilon^*)$.\\
+\quad\\
+Recall from slide ({\color{blue}\ref{S1}}) that, to use the LSM estimation, we assume $\theta_t^\epsilon={\color{red}c}\in\R^+$.
+Recall also our definition for $\theta_t^\epsilon$ (equation ({\color{blue}\ref{Eq-11}})):
+\begin{equation*}
+\theta_t^\epsilon=\max\left(\theta_0,\frac{\alpha\theta_0+2|\dot{p}_t^\epsilon|}{2\min(1-p_t^\epsilon,p_t^\epsilon)}\right).
+\end{equation*}
+Fixed $\epsilon$, we call $\mathcal{V}=\{\Delta V_i^\epsilon\}_{i=1}^n$ to the set of $n$ error transitions where for each measurement $X_i$, we have that $V_i=X_i-p_i^\epsilon$.
+$\mathcal{P}=\{p_i^\epsilon\}_{i=1}^n$ is the corresponding set of forecasts.\\
+Now, if we also fix $\theta_0$ and $\alpha$, we can define the set of indexes $\mathbf{I}=\{i\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\theta_0\}$ and $\mathbf{J}=\left\{j\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\frac{\theta_0\alpha}{\epsilon}\right\}$.
 
-\begin{equation}
-\theta_0 \alpha \approx \frac{1}{2M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{ \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
-\end{equation}
+From the definition of $\theta_t^\epsilon$: We have that for $\epsilon<<1$, and $p_t=\epsilon$ or $p_t=1-\epsilon$, the approximation $\theta^\epsilon_t\approx\frac{\theta_0\alpha}{\epsilon}$ holds.
+Then, for $\epsilon$ small enough, $\mathbf{J}$ can be approximated by $$\mathbf{J}\approx\tilde{\mathbf{J}}=\{j\in\{1,\dots,n\}:p_j^\epsilon\in\{\epsilon,1-\epsilon\}\}.$$
+Now, coming back to the definition of $\theta_t^\epsilon$, we have that it is more likely that $\theta_t^\epsilon=\theta_0$ if $p_t^\epsilon\approx\frac{1}{2}$.
+Then, we can approximate $\mathbf{I}$ by $$\mathbf{I}\approx\tilde{\mathbf{I}}=\left\{i\in\{1,\dots,n\}:p_i\in(\gamma,1-\gamma)\right\},\ \gamma\approx\frac{1}{2},\ \gamma<\frac{1}{2}.$$
 
-Solving for $\alpha$, we have both first estimates and we can also estimate $\delta$ solving the problem
+Recall the quadratic variation estimator ({\color{blue}\ref{Eq-2}}) from slide ({\color{blue}\ref{QV}}). It uses all the transitions $\mathcal{V}$ and estimated the product $\theta_0\alpha$.\\
+\quad\\
+We get ${\color{orange}\theta_0^*\alpha^*\approx0.10}$, from where we calculate ${\color{orange}\alpha^*\approx0.08}$.
 
-\begin{equation}
-\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
-\label{likelihood_delta}
-\end{equation}
+As we have an approximated value for $\theta_0\alpha$, if we can estimate $\frac{\theta_0\alpha}{\epsilon}$, then we can estimate $\epsilon$.
+In slide ({\color{blue}\ref{Slide:Defs}}), we showed that for $\epsilon<<1$, the LSM estimation using indexes from $\tilde{\mathbf{J}}$ is an estimator for $\frac{\theta_0\alpha}{\epsilon}=:k$.\\
+\quad\\
+However, which values of $\epsilon$ satisfies $\epsilon<<1$?
+We choose an initial guess for $\epsilon$ (call it $\epsilon_0$), and iterating we aim to converge to some local minimum.
+We proceed with the following steps:
 
-With our estimations of $\bm{\theta}$, we can start the inference processes as follows:
-\begin{enumerate}
-\item[Step 1.]  initialize;
-\item[Step 2.]  optimize the log-likelihood function using  Nelder-Mead optimization algorithm on a mini-batch sampled with replacement;
-\item[Step 3.] check if  accuracy threshold is reached. Else, re-initialize the optimization with the most recent result on a larger mini-batch.
-\end{enumerate}
+\begin{itemize}
+
+\item We sample $\epsilon_0$ from $\mathcal{U}[0.01,0.1]$ and load $\epsilon\gets\epsilon_0$.
+\item We create $\tilde{\mathbf{J}}$ and use the LSM estimation to find $k$.
+If $k<\theta_0^*$, then the assumption $\theta_t^\epsilon={\color{red}c}\in\R^+$ is wrong and we reduce the value of $\epsilon$, i.e., $\epsilon\gets\epsilon*0.999$.
+If $k\geq\theta_0^*$, we load $\epsilon\gets\frac{\theta_0^*\alpha^*}{k}$ (we allow a maximum relative change of 1\%).
+We repeat this step *100 times*.
+\item We repeat steps 1 and 2 *500 times*. After, we plot the results.
+
+\end{itemize}
+
 %---END SECTION 4---

### 2020-04-18 LaTeX_Code/Paper/paper_1line_Renzo.tex
Added most text from slides to paper.

--- 2020-04-14 LaTeX_Code/Paper/paper_1line.tex
@@
 \setcounter{page}{1}
-
+\sloppy
 \begin{document}
@@
 \includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
+\quad\\
 \includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
@@
 
-\subsection{Physical Constraints}
+\subsection{Physical Constraints} \label{Sec: Physical_Constraints}
 
@@
 \subsection{Optimization} \label{opt_sec}
-{\color{red} Rewrite the discussion to obtain fast initial estimate for the two unknow parameters.}
 
-To initialize the optimization process for the likelihood function of the process $V$, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$: {\color{red} Add explanation regarding the motivation for this objective function.}
+\subsubsection{Initial guess}
 
+To guarantee the good behave for our optimization algorithm, we aim to start the optimization as close as we can from the optimal parameters.
+We use \textbf{Lease Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess, and to tune the hyper-parameter $\epsilon\in(0,\frac{1}{2})$.
+
+\begin{itemize}
+
+\item \textbf{Least Square Minimization:} We consider a set of transitions $\{\Delta V_i\}_{i}$ with $\Delta V_i=V_{i+1}-V_i$ and $\Delta t=t_{i+1}-t_i$.
+$(V_{i+1}|V_i)$ is a random variable which conditional mean can be approximated by the solution of the system
+\begin{equation*}
+\begin{cases}
+\dif \E\left[V\right]&=-\theta_t\E\left[V\right]\dif t\\
+\E\left[V(t_i)\right]&=V_i,
+\end{cases}
+\end{equation*}
+evaluated in $t_{i+1}$ (i.e., $\E\left[V(t_{i+1})\right]$).
+Then, the random variable $(V_{i+1}-\E\left[V(t_{i+1})\right])$ has approximately zero mean.
+If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_i,t_{i+1}]$, then $\E\left[V(t_{i+1})\right]=V_ie^{-c\Delta t}$.
+If we have a total of $n$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
 \begin{equation}
-\theta_0\approx\arg\min_{\theta} \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2,
-\label{inital_theta}
+c^*\approx\arg\min_{c\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-\E\left[V(t_{i+1})\right]\right)^2\right]=\arg\min_{c\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-V_ie^{-c\Delta t}\right)^2\right].
+\label{Eq-1}
+\end{equation}
+As Equation (\ref{Eq-1}) is convex in $c$ (composition of convex is convex), it is enough to verify the first order optimality conditions.
+\begin{equation*}
+\begin{split}
+\frac{\partial f}{\partial c}&=\sum_{i=1}^n2(-V_i)(-\Delta t)(V_{i+1}-V_i(1-\theta_0\Delta t))\\
+&=\sum_{i=1}^n2V_i\Delta t(V_{i+1}-V_i(1-c\Delta t))\\
+&=\sum_{i=1}^n2V_{i+1}V_i\Delta t-2V_i^2\Delta t+2V_i^2\Delta t^2c.
+\end{split}
+\end{equation*}
+Then, $c^{**}$ satisfies
+\begin{equation}
+c^{**}\approx\frac{\sum_{i=1}^nV_i(V_i-V_{i+1})}{\Delta t\cdot\sum_{i=1}^n(V_i)^2}\quad\text{and}\quad c^*=\max\{c^{**},0\}.
+\label{Eq-4}
+\end{equation}
+Notice that $c^{**}$ has dimension $\mathbf{time}^{-1}$.
+
+\item \textbf{Quadratic Variation:} We approximate the SDE by its E-M scheme. In particular, we approximate the It\^o quadratic variation with the discrete one:
+\begin{itemize}
+
+\item It\^o process quadratic variation: $[V]_t=\int_0^t\sigma_s^2\dif s$.
+\item Discrete process quadratic variation: $[V]_t=\sum_{0<s\leq t}(\Delta V_s)^2$.
+
+\end{itemize}
+
+Then, considering $\Delta t$ the time between measurements, we approximate:
+\begin{equation}
+\theta_0^*\alpha^*\approx\frac{\sum_{i=1}^n(\Delta V_i)^2}{2\Delta t\sum_{i=1}^n(V_i+p_i)(1-V_i-p_i)}.
+\label{Eq-2}
 \end{equation}
 
- where $v_{i,j}=x_{i,j}-p_{i,j}$,  $x_{i,j}$ is historical wind power production and $p_{i,j}$ is the wind power forecast.
+\end{itemize}
 
- By assuming ergodicity {\color{red} not ergodicity, instead simply for the \textbf{quadratic variation formula}.}, we can obtain a first estimate on the product of the parameters as follows,
+In section (\ref{Sec: Physical_Constraints}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$.
+Even when it would be reasonable to choose an arbitrary small $\epsilon>0$, we aim to approximate it using the LSM estimator.\\
 
+Fixed $\epsilon$, we call $\mathcal{V}=\{\Delta V_i^\epsilon\}_{i=1}^n$ to the set of $n$ error transitions where for each measurement $X_i$, we have that $V_i=X_i-p_i^\epsilon$.
+$\mathcal{P}=\{p_i^\epsilon\}_{i=1}^n$ is the corresponding set of forecasts.\\
+If we also fix $\theta_0$ and $\alpha$, we can define the set of indexes $\mathbf{I}=\{i\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\theta_0\}$ and $\mathbf{J}=\left\{j\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\frac{\theta_0\alpha}{\epsilon}\right\}$.
+From the definition of $\theta_t$, we have that for $\epsilon<<1$, and $p_t=\epsilon$ or $p_t=1-\epsilon$, the approximation $\theta_t\approx\frac{\theta_0\alpha}{\epsilon}$ holds.
+Then, for $\epsilon$ small enough, $\mathbf{J}$ can be approximated by $$\mathbf{J}\approx\tilde{\mathbf{J}}=\{j\in\{1,\dots,n\}:p_j^\epsilon\in\{\epsilon,1-\epsilon\}\}.$$
+Now, coming back to the definition of $\theta_t$, we have that it is more likely that $\theta_t=\theta_0$ if $p_t^\epsilon\approx\frac{1}{2}$.
+Then, we can approximate $\mathbf{I}$ by $$\mathbf{I}\approx\tilde{\mathbf{I}}=\left\{i\in\{1,\dots,n\}:p_i\in(\gamma,1-\gamma)\right\},\ \gamma\approx\frac{1}{2},\ \gamma<\frac{1}{2}.$$
+We do not see signification differences in the LSM estimator for all $\gamma\in(0.1,0.3)$.
+If $\gamma>0.3$, the reduction in the number of samples makes variations in the LSM estimator.
+As we have an approximated value for $\theta_0\alpha$, if we can estimate $\frac{\theta_0\alpha}{\epsilon}$, then we can estimate $\epsilon$.
+We showed that for $\epsilon<<1$, the LSM estimation using indexes from $\tilde{\mathbf{J}}$ is an estimator for $\frac{\theta_0\alpha}{\epsilon}$.
+
+\subsubsection{Negative Log-Likelihood Minimization in $V$ Space} \label{Sec:MinLH}
+
+To find the optimal parameters, we minimize the negative log-likelihood using the derivative-free function \textit{fminsearch} from MATLAB R2019b over the parameters $(\theta_0,\alpha)$.
+At each step of the iteration,  we:
+\begin{itemize}
+
+\item Use the training dataset to find the SDE first and second moments.
+\item Match the proxy distribution moments with the SDE moments.
+\item Evaluate the negative log-likelihood using the training dataset.
+
+\end{itemize}
+
+\subsubsection{Negative Log-Likelihood Minimization in $Z$ Space} \label{Sec:MinLHL}
+
+Let $\{\Delta V_i\}_{i=1}^n$ be the set of all error transitions, and $\psi(\theta_0,\alpha,\Delta V)$ the Lamperti transform.
+Notice that the Lamperti transitions $\{\Delta Z_i\}_{i=1}^n$ depend on $(\theta_0,\alpha)$ because $$\{\Delta Z_i\}_{i=1}^n=\psi(\theta_0,\alpha,\{\Delta V_i\}_{i=1}^n).$$
+Then, if we compute $$\max_{(\theta_0,\alpha)}\mathbf{L}(\theta_0,\alpha,\{\Delta Z_i\}_{i=1}^n),$$
+we are not computing a MLE in the classical sense, as the data is changing with the parameters. However, we can try to find a fixed point ${\color{blue}(\theta_0^*,\alpha^*)}$ such that
 \begin{equation}
-\theta_0 \alpha \approx \frac{1}{2M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{ \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
+{\color{blue}(\theta_0^*,\alpha^*)}=\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{blue}\theta_0^*},{\color{blue}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
+\label{FP}
 \end{equation}
+In this point, the likelihood has a maximum for the data set corresponding to that point.
 
-Solving for $\alpha$, we have both first estimates and we can also estimate $\delta$ solving the problem
+We are interested in finding the solution of (\ref{FP}). We have that, if $(\theta_0^*,\alpha^*)$ is a solution of (\ref{FP}), then
+\begin{equation*}
+(\theta_0^*,\alpha^*)-\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right)=0.
+\end{equation*}
+Given a pair $(\theta_0^{*},\alpha^{*})$, we call $(\theta_0^{**},\alpha^{**})$ to the solution of
+\begin{equation*}
+\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
+\end{equation*}
+For each $(\theta_0^{*},\alpha^{*})$, we define the relative error function
+\begin{equation*}
+\Psi(\theta_0^{*},\alpha^{*})=\frac{|\theta_0^{*}-\theta_0^{**}|}{|\theta_0^{*}|}+\frac{|\alpha^{*}-\alpha^{**}|}{|\alpha^{*}|}
+\end{equation*}
+and claim that $(\theta_0^*,\alpha^*)$ is a fixed point iff $\Psi(\theta_0^*,\alpha^*)=0$.
 
-\begin{equation}
+\subsubsection{Additional Parameter $\delta$}
+
+{\color{red}[I am not sure if we should introduce this parameter here, of in some previous section].} We observe that for each day, the error at time $t=0$ is not zero.
+However, by construction of the forecast, we may assume that for some time in the past $t_\delta<0$, the error $V_{t_\delta}=0$.\\
+\quad\\
+We extrapolate linearly $p(t)$ considering the truncation at $\epsilon$, so we can evaluate $p(t_{-\delta})$, and assume that $V(t_{-\delta})=0$.
+Then, for each day $j$, we have an initial transition $(V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta)$.
+We assume again that it is Beta and apply the same moment matching as for the rest of transitions.
+With our initial guess for $\bm{\theta}$, we can construct our initial guess for $\delta$ solving the problem
+
+\begin{equation*}
 \delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
 \label{likelihood_delta}
-\end{equation}
+\end{equation*}
+To solve this minimization problem, we repeat the steps described in section (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation.
 
-With our estimations of $\bm{\theta}$, we can start the inference processes as follows:
-\begin{enumerate}
-\item[Step 1.]  initialize;
-\item[Step 2.]  optimize the log-likelihood function using  Nelder-Mead optimization algorithm on a mini-batch sampled with replacement;
-\item[Step 3.] check if  accuracy threshold is reached. Else, re-initialize the optimization with the most recent result on a larger mini-batch.
-\end{enumerate}
 %---END SECTION 4---
@@
 \centering
-\begin{tabular}{cccc}
+\begin{tabular}{ccc}
 \toprule
-Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \midrule
-Provider A  &  $(\add,\add)$      &  \add   & \add    \\
-Provider B  & $(\add,\add) $  &  \add   &   \add  \\ 
+Forecast Provider & Parameters $(\theta_0, \alpha,\delta)$ & Product $\theta_0\alpha$ \\ \midrule
+Provider A  &  $(\add,\add)$      &  \add    \\
+Provider B  & $(\add,\add) $  &  \add \\ 
+Provider C  & $(\add,\add) $  &  \add \\ 
 \bottomrule
@@
 
- \begin{table}[H]
- \centering
- \begin{tabular}{cccc}
- \toprule
- Model & parameters $(\theta_0, \alpha)$  \\
- \midrule
- \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ 
- \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \bottomrule
- \end{tabular}
- \caption{ \add confidence interval obtained using bootstrap}
- \label{tab:freq_comparison}
- \end{table}
 %---END SECTION 6---
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/initial_guess/initial_theta_1.eps}\quad\includegraphics[width=0.42\textwidth]{plots/initial_guess/initial_theta_2.eps}
-\caption{Value function from ($\ref{inital_theta}$) as a function of different $\theta_0$ values. We can observe that the function if flat for a wide range.}
-\end{figure}
-
-\subsection{Negative Log-Lihelihood}
+\subsection{Negative Log-Likelihood in $V$ Space}
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood.eps}\quad\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_refined.eps}
-\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_more_refined.eps}
-\caption{Negative Log-Likelihood for different domains.}
+\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.jpg}
+\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
 \label{fig:neg-LL}
 \end{figure}
+On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood. The thick violet band is the region where the function reaches its minimums.\\
+We can see the \textbf{initial guess} point, the result of three different \textbf{optimization tools} from MATLAB, and the minimum point that we found from the \textbf{evaluations} that generate the plot.
+\begin{table}[]
+\centering
+\begin{tabular}{lccc}
+\toprule
+ & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
+ \midrule
+ Initial guess & 1.629 & 0.060 & 0.098 \\
+ fminsearch & 1.135 & 0.073 & 0.083 \\
+ fmincon & 1.366 & 0.061 & 0.083 \\
+ fminunc & 1.628 & 0.051 & 0.083 \\
+ evaluations & 1.180 & 0.070 & 0.083 \\
+ \bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{Negative Log-Likelihood in $Z$ Space}
+
+We plot the Negative Log-Likelihood as a function of the parameters.
+The plots can be seen in Figure (\ref{fig:neg-LL}).
+We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
+\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
+\label{fig:neg-LLL}
+\end{figure}
+In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets of the error function $\Psi$.\\
+The center deep green band is the set $\mathbb{A}$ such that $\Psi(\mathbb{A})\in[0.05,0.1]$. We do not achieve relative error smaller than 0.05.\\
+We observe a particular behavior over the curves $\theta_0\alpha=k\in\R^+$. However, it can be a numeric effect.\\
+We also observe that: $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.083\}\neq\emptyset.$$
+On the right, we observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.038$ from the error SDE.\\
+We choose $(\theta_0,\alpha)=(2.200,0.038)$.\\
+We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".
 
 \subsection{Main guesses}
-
-We were able to obtain the following for 
-\begin{table}[H]
-\centering
-\begin{tabular}{|c|c|}
-\hline
-Formulation   &  parameters $(\theta_0, \alpha,\delta)$    \\ \hline
-Without Lamperti transform &   $(1.2,0.1,0.6) \pm (\add , \add) $   \\ \hline
-With Lamperti transform &   $(12,0.29) \pm (\add , \add)  $   \\ \hline
-\end{tabular}
-\caption{We compare the parameters obtained in both the original and Lamperti space. Parameters have been obtained based on \add data points from the Uruguayan pertaining to the year 2019\add .}
-\label{tab:model_comparison_2}
-\end{table}
 
@@
 \begin{figure}[H]
-  \includegraphics[width=56mm,scale=1]{plots/alpha_conv_beta.png}
-  \includegraphics[width=56mm,scale=1]{plots/theta_conv_beta.png}
-  \caption{We show self-convergence of our algorithm applied to model $2$. We conlcude that the rate  matches that of of Monte Carlo. Data is from Uruguay pertaining to year 2019.}
-\end{figure}
-
-\begin{figure}[H]
 \centering
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/2.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/3.eps}
-\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/4.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
 \caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/2.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/3.eps}
-\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/4.eps}
-\caption{{\color{red}Pending add legend and choose better colors.}We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/1.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/2.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/3.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/4.eps}
+\caption{We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
 Actual production plotted in retrospect.
@@
 \end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
+\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Lamperti_Optimal.eps}
+\end{figure}
+
+We can see two histograms for the error transitions. On the left, using $(\theta_0^E,\alpha^E)$, while on the right, using $(\theta_0^L,\alpha^L)$.
+
 %---END SECTION 7---
@@
 \red{
-\begin{equation}\label{Assumption:3}
+\begin{equation}
 \theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 

### 2020-04-19 LaTeX_Code/Paper/paper_1line.tex
Added from section 4.3 to section 7 in the paper. Added optimization for the other two datasets. Added likelihood with three parameters.

@@
 \centering
-\begin{tabular}{cccc}
+\begin{tabular}{ccc}
 \toprule
-Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \midrule
-Provider A  &  $(\add,\add)$      &  \add   & \add    \\
-Provider B  & $(\add,\add) $  &  \add   &   \add  \\ 
+Forecast Provider & Parameters $(\theta_0, \alpha)$ & Product $\theta_0\alpha$ \\ \midrule
+Provider A  &  $(1.180,0.070)$      &  0.083    \\
+Provider B  & $(0.766,0.117) $  &  0.090 \\ 
+Provider C  & $(1.347,0.073) $  &  0.099 \\ 
 \bottomrule
@@
 \end{table}
-In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.
 
- \begin{table}[H]
- \centering
- \begin{tabular}{cccc}
- \toprule
- Model & parameters $(\theta_0, \alpha)$  \\
- \midrule
- \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ 
- \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \bottomrule
- \end{tabular}
- \caption{ \add confidence interval obtained using bootstrap}
- \label{tab:freq_comparison}
- \end{table}
 %---END SECTION 6---

### 2020-04-19 LaTeX_Code/Paper/paper_1line_Renzo.tex
Added from section 4.3 to section 7 in the paper. Added optimization for the other two datasets. Added likelihood with three parameters.

@@
 \toprule
-Forecast Provider & Parameters $(\theta_0, \alpha,\delta)$ & Product $\theta_0\alpha$ \\ \midrule
-Provider A  &  $(\add,\add)$      &  \add    \\
-Provider B  & $(\add,\add) $  &  \add \\ 
-Provider C  & $(\add,\add) $  &  \add \\ 
+Forecast Provider & Parameters $(\theta_0, \alpha)$ & Product $\theta_0\alpha$ \\ \midrule
+Provider A  &  $(1.180,0.070)$      &  0.083    \\
+Provider B  & $(0.766,0.117) $  &  0.090 \\ 
+Provider C  & $(1.347,0.073) $  &  0.099 \\ 
 \bottomrule
@@
 \end{table}
-In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.
 

### 2020-04-19 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
Added some references.
Added from section 4.3 to section 7 in the paper. Added optimization for the other two datasets. Added likelihood with three parameters.

@@
 \centering
-\includegraphics[width=0.5\textwidth]{../Results/likelihood/normal/Log-Likelihood.eps}
+\includegraphics[width=0.5\textwidth]{../Results/likelihood/normal/Log-Likelihood.jpg}
 %\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_refined.eps}
@@
 
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Log-likelihood evaluation (2/2):}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.45\textwidth]{../Results/likelihood/normal/Log-Likelihood_Zoom.eps}
+\includegraphics[width=0.41\textwidth]{../Results/likelihood/lamperti/Log-Likelihood_Zoom.eps}
+\end{figure}
+
+\end{frame}
+
 \end{document}

### 2020-04-19 MATLAB_Files/plot_epsilon.m

@@ -2,7 +2,9 @@ close all;
 clear all;
 clc;
 
-[Ta_Tra_Comp, Ta_Test_Compl, Ta_Comp] = load_data();
+% dataSet can be AWSTP (B), MTLOG (A) or UTEP5 (C).
+dataSet = 'UTEP5';
+[Ta_Tra_Comp, Ta_Test_Compl, Ta_Comp] = load_data(dataSet);
 
 figure(1); figure(2); 
 

### 2020-04-24 LaTeX_Code/Paper/paper_1line.tex
Added tables with results in Chapters 5 and 6. The corresponding MATLAB files have also commented this results. Next time, I will add all the plots.

@@
 \centering
-\begin{tabular}{cccc}
+\begin{tabular}{cccccc}
 \toprule
-Model   &  parameters $(\theta_0, \alpha,\delta)$   & AIC & BIC \\ \midrule
-Model 1 &  $(\add,\add) $    &  \add   &  \add   \\
-Model 2 &   $(1.2,0.1,0.6)$   &  \add   &   \add    \\ 
+Model & Forecast Provider & Method & Product $\theta_0\alpha$   & AIC & BIC \\ \midrule
+Model 1 & Provider A & Gaussian Proxy & 0.105 & -58226 & -58211 \\
+ &  & Shoji-Ozaki & 0.104 & -58226 & -58211 \\
+ &  & Beta Proxy & 0.104 & -58286 & -58271 \\
+ & Provider B & Gaussian Proxy & 0.105 & -58226   & -58211 \\
+ &  & Shoji-Ozaki & 0.104 & -58226 & -58211 \\
+ &  & Beta Proxy & 0.104 & -58288 & -58273 \\
+ & Provider C & Gaussian Proxy & 0.105 & -58226 & -58211 \\
+ &  & Shoji-Ozaki & 0.104 & -58226 & -58211 \\
+ &  & Beta Proxy & 0.104 & -58286 & -58271 \\
+Model 2 & Provider A & Beta Proxy & 0.097 & -73700   & -73685 \\ 
+ & Provider B & Beta Proxy & 0.098 &  -73502 & -73487 \\ 
+ & Provider C & Beta Proxy & 0.108 & -72518 & -72503 \\ 
 \bottomrule
@@
 Forecast Provider & Parameters $(\theta_0, \alpha)$ & Product $\theta_0\alpha$ \\ \midrule
-Provider A  &  $(1.180,0.070)$      &  0.083    \\
-Provider B  & $(0.766,0.117) $  &  0.090 \\ 
-Provider C  & $(1.347,0.073) $  &  0.099 \\ 
+Provider A  & $(1.930,0.050)$  &  0.097 \\
+Provider B  & $(1.420,0.069) $  &  0.098 \\ 
+Provider C  & $(1.380,0.078) $  &  0.108 \\ 
 \bottomrule
 \end{tabular}
-\caption{\add}
+\caption{Optimal parameters for different providers using Model 2 with Beta proxies.}
 \label{tab:forcast_comparison}

### 2020-04-24 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
Added tables with results in Chapters 5 and 6. The corresponding MATLAB files have also commented this results. Next time, I will add all the plots.

--- 2020-04-04 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Density next measurement (2/2):}
+\begin{frame}\frametitle{Density next measurement (2/2):}\label{Tr2}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \setbeamercolor{background canvas}{bg=white!10}
@@
 \end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \setbeamercolor{background canvas}{bg=white!20}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \setbeamercolor{background canvas}{bg=green!20}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Density next measurement:}
+\begin{frame}\frametitle{Density next measurement:}\label{lamp_LH}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=green!20}
+\begin{frame}
+
+{\Huge Model 1}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Model 1 SDE:}
+
+Given the SDE
+\begin{equation*}
+\dif X_t=\underbrace{-\theta_0\left(X_t-p_t\right)}_{:=\mu_t}\dif t+\underbrace{\sqrt{2\theta_0\alpha X_t(1-X_t)}}_{:=\sigma_t}\dif W_t,
+\end{equation*}
+we want to approximate its moments. Trivially, we have an exact ODE for the first moment for $t\in[t_0,t_1]$:
+\begin{equation*}
+\begin{cases}
+\dif \E\left[X_t\right]=-\theta_0\left(\E\left[X_t\right]-p_t\right)\dif t\\
+\E\left[X_{t_0}\right]=x_{t_0}.
+\end{cases}
+\end{equation*}
+Now, we can define the process $f_t=f(X_t,t)=X^2_t$ and apply It\^o's lemma. We reach that
+\begin{equation*}
+\dif f_t=\left(\frac{\partial f}{\partial t}+\mu_t\frac{\partial f}{\partial x}+\frac{\sigma^2_t}{2}\frac{\partial^2f}{\partial x^2}\right)\dif t+\sigma_t\frac{\partial f}{\partial x}\dif W_t,
+\end{equation*}
+where $\frac{\partial f}{\partial x}=2x$, $\frac{\partial^2 f}{\partial x^2}=2$, and $\frac{\partial f}{\partial t}=0$.
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Model 1 SDE:}
+
+Doing SOME substitutions, we reach
+\begin{equation*}
+\dif f_t=2\theta_0\left(X_t(\alpha+p_t)-X^2_t(1+\alpha)\right)\dif t+\sigma_t\frac{\partial f}{\partial x}\dif W_t.
+\end{equation*}
+Now, if we apply the expected value operator $\E[\cdot]$, we get
+\begin{equation*}
+\dif\E\left[X^2_t\right]=2\theta_0\left(\E\left[X_t\right](\alpha+p_t)-\E\left[X^2_t\right](1+\alpha)\right)\dif t,
+\end{equation*}
+which is the second moment ODE with IV $\E\left[X^2_t\right]=x_{t_0}^2$ for $t\in[t_0,t_1]$.
+Recall that $\V\left[X_t\right]=\E\left[X_t^2\right]-\E\left[X_t\right]^2$.
+As we will assume Gaussian proxies, we will use the Likelihood described in Slide {\color{blue}\ref{lamp_LH}}.
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Model 1 SDE:}
+
+The forward Euler schemes are:
+\begin{enumerate}
+
+\item $m_1(s_{n})=m_1(s_{n-1})-\theta_0(m_1(s_{n-1})-p_{s_{n-1}})\Delta s.$
+
+\item $m_2(s_{n})=m_2(s_{n-1})+2\theta_0\left(m_1(s_{n-1})(\alpha+p_{s_{n-1}})-m_2(s_{n-1})(1+\alpha)\right)\Delta s.$
+\end{enumerate}
+
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\tiny
+\lstinputlisting{../moment_1_M1.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}
+\begin{center}
+\begin{tabular}{|c|}
+\toprule
+{\tiny
+\lstinputlisting{../moment_2_M1.m}
+}\\
+\bottomrule
+\end{tabular}
+\end{center}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Model 1 SDE: Shoji-Ozaki method}
+{\footnotesize
+An extension of the method to Ozaki the more general case where the drift is allowed to depend on the time variable t, and also the diffusion coefficient can be varied is the method Shoji and Ozaki.
+Consider the stochastic differential equation:
+\begin{equation*}
+\dif X_t=f(t,X_t,\bm{\theta})\dif t+q(X_t,\bm{\theta})\dif W_t,\quad t\geq0,X_0=x_0,
+\end{equation*}
+the transition density for the Shoji-Ozaki method is Gaussian, we have that: $X_{t+\Delta t}|X_t=x\sim\mathcal{N}\left(A_{(t,x)}x,B^2_{(t,x)}\right)$, where:
+\begin{equation*}
+A_{(t,x)}=1+\frac{f(t,x)}{xL_t}\left(e^{L_t\Delta t}-1\right)+\frac{M_t}{xL^2_t}\left(e^{L_t\Delta t}-1-L_t\Delta t\right),
+\end{equation*}
+\begin{equation*}
+B_{(t,x)}=g(x)\sqrt{\frac{e^{2L_t\Delta t}-1}{2L_t}},
+\end{equation*}
+with:
+\begin{equation*}
+L_t=\partial_xf(t,x)\quad\text{and}\quad M_t=\frac{g^2(x)}{2}\partial_{xx}f(t,x)+\partial_tf(t,x).
+\end{equation*}}
+{\tiny
+\url{https://cran.r-project.org/web/packages/Sim.DiffProc/vignettes/fitsde.html}}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=white!10}
+\begin{frame}\frametitle{Model 1 SDE: Beta as proxy}
+
+Following the same idea as in Slides (\ref{Tr}) and (\ref{Tr2}), but using $[a,b]=[0,1]$, we get the moments matching:
+\begin{itemize}
+\item $\xi_1=\frac{-\mu\sigma^2+\mu^2-\mu^3}{\sigma^2}$ all evaluated at time $t_n$ (verified in \textbf{Mathematica 11.0}\footnote{File: {\color{blue}Model1\_Beta.nb}.}).
+\item $\xi_2=\frac{(\mu-1)(\sigma^2-\mu+\mu^2)}{\sigma^2}$ all evaluated at time $t_n$ (verified in \textbf{Mathematica 11.0}).
+\end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2020-04-24 Reports/20200308 - Initial Guess/20200308 - Initial Guess.tex
Added tables with results in Chapters 5 and 6. The corresponding MATLAB files have also commented this results. Next time, I will add all the plots.

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\setbeamercolor{background canvas}{bg=white!20}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=green!20}
+\begin{frame}
+
+{\Huge Model 1}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=white!20}
+\begin{frame}\frametitle{Least square minimization (LSM)}
+
+We consider the transition $\Delta X_i=X_{i+1}-X_i$ with $\Delta t=t_{i+1}-t_i$. $(X_{i+1}|X_i)$ is a random variable which conditional mean can be approximated by the solution of the system
+\begin{equation*}
+\begin{cases}
+\dif \E\left[X\right]&=-\theta_0\left(\E\left[X\right]-p_t\right)\dif t\\
+\E\left[X(t_i)\right]&=X_i,
+\end{cases}
+\end{equation*}
+evaluated in $t_{i+1}$ (i.e., $\E\left[X(t_{i+1})\right]$). Then, the random variable $(X_{i+1}-\E\left[X(t_{i+1})\right])$ has approximately zero mean.\\
+\quad\\
+We consider the IVP $\dif x=-\theta_0(x-p_t)\dif t$ with initial conditions $x(t_i)=x_i$. Also, from now we will assume $t_i=0$.
+\begin{theorem}
+The ODE $\dot{y}=a(t)y+b(t)$ has solution $y(t)=ce^{A(t)}+e^{A(t)}\int e^{-A(t)}b(t)\dif t$ where $c\in\R$ and $A(t)=\int a(t)\dif t$.
+\end{theorem}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=white!20}
+\begin{frame}\frametitle{Least square minimization (LSM) and Quadratic Variation}
+
+$x(t)=ce^{-\theta_0 t}+e^{-\theta_0 t}\int e^{\theta_0 t}\theta_0p_t\dif t$ using the theorem.
+Now, recall that $p=p_i+\frac{(p_{i+1}-p_i)}{\Delta t}y=n+m\cdot y$ (we define $n$ and $m$ for simplicity).\\
+\quad\\
+Then: $x(t)=x_ie^{-\theta_0t}+\theta_0e^{-\theta_0t}\left[\frac{m+(e^{\theta_0t}-1)n\theta_0+e^{\theta_0t}m(\theta_0t-1)}{\theta_0^2}\right]$, where $x(t_{i+1})=\E\left[X(t_{i+1})\right]$.
+
+\begin{equation*}
+\theta_0^*\approx\arg\min_{\theta_0\geq0}\left[\sum_{i=1}^n\left(X_{i+1}-\E\left[X(t_{i+1})\right]\right)^2\right].
+\end{equation*}\\
+\quad\\
+\quad\\
+Quadratic Variation: To estimate $\theta_0\alpha$, we use equation (\ref{Eq-2}) but using $\Delta X$ instead of $\Delta V$, $X$ instead of $V$, and $0$ instead of $p$.
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\setbeamercolor{background canvas}{bg=white!20}
+\begin{frame}\frametitle{Why $\theta_0<0$?}
+
+\includegraphics[width=0.7\columnwidth]{20200422_205641.jpg}
+
+\end{frame}
+
 \end{document}

### 2020-04-24 MATLAB_Files/create_samples_minus_eps.m

@@ -8,7 +8,6 @@ function [minus_eps_samples] = create_samples_minus_eps(Forecast, Error, gamma)
     minus_eps_samples  = -1*ones(M*10,N_ini);
     eps_forecast       = -1*ones(M*10,N_ini); % For testing.
     
-   
     counter1     = 0;
     max_count_2  = 0;
     only_one     = 0; 
@@ -44,5 +43,6 @@ function [minus_eps_samples] = create_samples_minus_eps(Forecast, Error, gamma)
     end
     
     minus_eps_samples  = minus_eps_samples(1:counter1, 1:max_count_2-1);
+    eps_forecast       = eps_forecast(1:counter1, 1:max_count_2-1);
 
 end

### 2020-04-24 MATLAB_Files/likelihood_optimization_all.m

@@ -6,7 +6,7 @@ function [val] = likelihood_optimization_all(batch, theta_0, alpha, delta, dt, N
         val = - Inf;
     else
         val = log_LH_evaluation(batch_complete, alpha, theta_0, dt) - ...
-            144*first_log_LH_evaluation(batch_complete, theta_0, alpha, delta, dt, N, 1e6, 1e6);
+            first_log_LH_evaluation(batch_complete, theta_0, alpha, delta, dt, N, 1e6, 1e6);
     end
 
 end

### 2020-04-24 MATLAB_Files/load_data_eps.m

@@ -1,8 +1,12 @@
-function [Table_Training_Complete] = load_data_eps(ep,dataSet)
+function [Table_Training_Complete] = load_data_eps(ep,dataSet,dataKind)
     
     % 19/04/2020 15:45
-
-    [Table_Training_Complete, ~, ~] = load_data(dataSet);
+    
+    if strcmp(dataKind,'classic')
+        [Table_Training_Complete, ~, ~] = load_data(dataSet);
+    elseif strcmp(dataKind,'comparable')
+        [Table_Training_Complete, ~, ~] = load_data_comparable(dataSet);
+    end
 
     Time      = Table_Training_Complete.Time;
     Forecast  = Table_Training_Complete.Forecast;

### 2020-04-24 MATLAB_Files/log_LH_evaluation_MODEL1.m

@@ -1,0 +1,50 @@
+function [value] = log_LH_evaluation_MODEL1(batch_complete, alpha, theta_0, dt, approx)
+
+    % 19/04/2020 22:09
+    
+    % This makes (t_0,alpha) to be (t_0,gamma).
+%     theta_0 = theta_0;
+%     alpha   = alpha / theta_0;
+
+    for i = 1:length(batch_complete(1,:))/2
+
+        j = i*2; % This is the real index (parfor must go one-by-one).
+        % Recall that: j is t_n and j-1 is t_{n-1}.
+        p1 = batch_complete(1,j-1); p2 = batch_complete(1,j);
+        v1 = batch_complete(3,j-1); v2 = batch_complete(3,j);
+        n  = 100;
+        x1 = v1 + p1;
+        x2 = v2 + p2;
+
+        if approx == 1
+        
+            m1 = moment_1_M1(x1,theta_0,p1,p2,dt,n);
+            m2 = moment_2_M1(x1,m1,theta_0,alpha,p1,p2,dt,n);
+            val(i) = log_dist_L(x2,m1(end),sqrt(m2(end)-m1(end)^2));
+        
+        elseif approx == 2
+
+            m1 = moment_1_M1_SO(x1,theta_0,p1,p2,dt);
+            m2 = moment_2_M1_SO(x1,theta_0,alpha,dt);
+            A = m1; B = m2;
+            val(i) = log_dist_L(x2,A*x1,B);
+        
+        elseif approx == 3
+
+            m1 = moment_1_M1(x1,theta_0,p1,p2,dt,n);
+            m2 = moment_2_M1(x1,m1,theta_0,alpha,p1,p2,dt,n);
+            [xi1,xi2] = moments_matching_MODEL1(m1(end),m2(end));
+            val(i) = log_dist_extra(x2,xi1,xi2);
+        
+        else
+            
+            error('Choose a number between 1, 2 or 3.');
+            
+        end
+        
+    end
+    
+    value = sum(val);
+    
+end
+

### 2020-04-24 MATLAB_Files/moments_verification_MODEL1.m

@@ -1,0 +1,160 @@
+close all;
+clear all;
+clc;
+
+% dataSet can be AWSTP (B), MTLOG (A) or UTEP5 (C).
+dataSet                = 'MTLOG';
+% epsilon can be 0.035 (B), 0.018 (A) or 0.028 (C).
+epsilon                = 0.018;
+Table_Testing_Complete = load_data_eps_test(epsilon,dataSet);
+
+t  = Table_Testing_Complete.Time(1,:);
+dt = t(2);
+
+theta_0 = 1.2656;
+alpha   = 0.07052;
+n       = 100;
+p_end   = 1/2;
+p_lims  = 0.03;
+
+p = p_end-p_lims:0.001:p_end+p_lims;
+x = -0.4:0.001:0.2;
+% Here we are being confused. The vector x is the error vector. The idea is
+% that for each p, we compute the measurement as p+x, which would imply
+% that this vector x is the error vector v, but we called it x.
+
+for i = 1:length(p)
+    for j = 1:length(x)
+                        
+%         moment_1_M1(x,theta_0,p1,p2,dt,n)
+        Exp_X   = moment_1_M1(p(i)+x(j),theta_0,p(i),p_end,dt,n);
+%         moment_2_M1(x,m1,theta_0,alpha,p1,p2,dt,n)
+        Exp_X_2 = moment_2_M1(p(i)+x(j),Exp_X,theta_0,alpha,p(i),p_end,dt,n);
+                
+        for k = 1:100
+%             sde_FE_MODEL1(sim_path_i,alpha,theta_0,dt,P)
+            sim_path_x(k)   = sde_FE_MODEL1(p(i)+x(j),alpha,theta_0,dt,p(i));
+%             sde_FE_MODEL1_2(sim_path_i,alpha,theta_0,dt,P) 
+            sim_path_x_2(k) = sde_FE_MODEL1_2((p(i)+x(j))^2,alpha,theta_0,dt,p(i));
+        end
+        
+        Exp_X_emp   = mean(sim_path_x);
+        Exp_X_emp_2 = mean(sim_path_x_2);
+
+        exp_x_ode(i,j)   = Exp_X(end);
+        exp_x_2_ode(i,j) = Exp_X_2(end);
+        exp_x_emp(i,j)   = Exp_X_emp;
+        exp_x_emp_2(i,j) = Exp_X_emp_2;
+        
+    end
+end
+
+error_v   = abs(exp_x_ode-exp_x_emp);
[…]

### 2020-04-24 MATLAB_Files/path_simulator_OPT.m

@@ -2,15 +2,20 @@ close all;
 clear all;
 clc;
 
-epsilon                = 0.018;
-Table_Testing_Complete = load_data_eps_test(epsilon);
+% dataSet can be AWSTP (B), MTLOG (A) or UTEP5 (C).
+dataSet = 'MTLOG';
+% epsilon can be 0.035 (B), 0.018 (A) or 0.028 (C).
+epsilon = 0.018;
+% dataKind can be classic or comparable.
+dataKind = 'comparable';
+Table_Testing_Complete = load_data_eps_test(epsilon,dataSet,dataKind);
 whatToDo               = 'optimal_value'; 
 % whatToDo               = 'Optimal_Lamperti'; 
 
 % PARAMETERS:
 % set(0,'defaultAxesFontSize',18);
-quantil  = 1;
-save     = 1;
+quantil  = 0;
+save     = 0;
 delta    = 21; % The time is delta*10 minutes.
 xlimit   = 1; % If this in 1, the plots start at time 0. Otherwise, at -delta.
 
@@ -21,8 +26,8 @@ else
 end
 
 if  strcmp(whatToDo,'optimal_value')
-    theta_0 = 1.18;
-    alpha   = 0.07;
+    theta_0 = 1.93;
+    alpha   = 0.05;
 elseif  strcmp(whatToDo,'Optimal_Lamperti')
     theta_0 = 2.200;
     alpha   = 0.038;

### 2020-04-24 MATLAB_Files/plotLogLikelihood.m

@@ -10,8 +10,21 @@ clc;
 likelihood    = 'normal'; % 'normal' or 'lamperti'.
 % dataSet can be AWSTP, MTLOG or UTEP5.
 dataSet = 'MTLOG';
+% epsilon can be 0.035 (B), 0.018 (A) or 0.028 (C).
 epsilon       = 0.018;
-[Ta_Tra_Comp] = load_data_eps(epsilon,dataSet);
+% dataKind can be classic or comparable.
+dataKind = 'comparable';
+[Ta_Tra_Comp] = load_data_eps(epsilon,dataSet,dataKind);
+
+% AWSTP) (B)
+% T_0 = 1.42, Alpha = 0.069, prod = 0.0980, f = -36753.
+% AIC = -73502, BIA = -73487.
+% MTLOG) (A)
+% T_0 = 1.93, Alpha = 0.050, prod = 0.0965, f = -36852.
+% AIC = -73700, BIA = -73685.
+% UTEP5) (B)
+% T_0 = 1.38, Alpha = 0.078, prod = 0.1076, f = -36261.
+% AIC = -72518, BIA = -72503.
 
 Table_Training = Ta_Tra_Comp; % We copy it so we can modify it.
 
@@ -29,7 +42,7 @@ dt             = Time(1,2);
 [M, N_ini]     = size(Forecast);
 N              = N_ini - 1; % We have N_ini measurements but N samples.
 
-num_days = 127;
+num_days = height(Ta_Tra_Comp); % Maximum 127 for MTLOG.
 [Table_Training, batch] = new_batch_fixed(Table_Training,num_days,N);
 
 %% Initial parameters:

### 2020-04-24 MATLAB_Files/plot_epsilon.m

@@ -3,7 +3,7 @@ clear all;
 clc;
 
 % dataSet can be AWSTP (B), MTLOG (A) or UTEP5 (C).
-dataSet = 'UTEP5';
+dataSet = 'MTLOG';
 [Ta_Tra_Comp, Ta_Test_Compl, Ta_Comp] = load_data(dataSet);
 
 figure(1); figure(2); 
@@ -145,7 +145,7 @@ title('Number of samples over $\epsilon$','interpreter','latex');
 xlabel('$\epsilon$','interpreter','latex');
 saveas(gcf,[pwd '/Results/epsilon/num_over_eps'],'epsc');
 
-%% Plor theta_0:
+%% Plot theta_0:
 
 epsilon = [0.01:0.001:0.49];
 accum   = [];

### 2020-04-25 LaTeX_Code/Paper/paper_1line_Renzo.tex

@@
  \midrule
- Initial guess & 1.629 & 0.060 & 0.098 \\
- fminsearch & 1.135 & 0.073 & 0.083 \\
- fmincon & 1.366 & 0.061 & 0.083 \\
- fminunc & 1.628 & 0.051 & 0.083 \\
- evaluations & 1.180 & 0.070 & 0.083 \\
+ Initial guess & 1.544 & 0.072 & 0.111 \\
+ fminsearch & 1.278 & 0.076 & 0.097 \\
+ fmincon & 1.577 & 0.062 & 0.097 \\
+ fminunc & 1.544 & 0.063 & 0.097 \\
+ evaluations & 1.930 & 0.050 & 0.097 \\
  \bottomrule
 \end{tabular}
+\caption{Different important points for provider A using model 2 and beta proxies.}
 \end{table}

### 2020-04-25 Reports/20200406 - Summary of Advances/20200406 - Summary of Advances.tex

\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{commath}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{siunitx}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}
\DeclareMathOperator{\sign}{sign}

\title{Summary of Advances and Questions}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=green!20}
\begin{frame}

{\Huge Error SDE (process $V_t=X_t-p_t$):}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Parameters inference using MLE:} \label{MLE}

\begin{columns}

\column{.5\textwidth}
On the right, we can see the level sets for the negative log-likelihood. The thick violet band is the region where the function reaches its minimums.\\
\quad\\
We can see the \textbf{initial guess} point, the result of three different \textbf{optimization tools} from MATLAB, and the minimum point that we found from the \textbf{evaluations} that generate the plot.\\
\quad\\
Notice that all the optimal locations are in the minimum value band.

\column{.5\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.85\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.eps}\\
{\tiny
\begin{table}[]
\begin{tabular}{lccc}
\toprule
 & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
 \midrule
 Initial guess & 1.629 & 0.060 & 0.098 \\
 fminsearch & 1.135 & 0.073 & 0.083 \\
 fmincon & 1.366 & 0.061 & 0.083 \\
 fminunc & 1.628 & 0.051 & 0.083 \\
 evaluations & 1.180 & 0.070 & 0.083 \\
 \bottomrule
\end{tabular}
\end{table}
}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Some key points:}

\begin{enumerate}

\item The moments' ODEs were verified with the empirical moments using Euler–Maruyama method.
\item All the optimization tools are set to their default specifications. However, if we increment the precision of the tools, or if we normalize the likelihood, we do not see significant changes in the position of the minimums.
\item All the minimums are over the line $\theta_0\alpha=0.083$. This line is exactly located in the center of the thick violet band.
\item We do inference using 127 days ('training days'), and simulate over the other 128 days ('testing days'). In total, we have  255 days, since we removed all the days with curtailing. To guarantee independence between the days, we never do inference using two consecutive (in the calendar sense) days.

\end{enumerate}
\alert{If there is any question, please let me know.}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{More evaluations:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood_Line.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood_Evaluations.eps}
\end{figure}

We can see that the line $\theta_0\alpha=0.083$ presents the smallest evaluations.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Simulations over testing days:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/5.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/6.eps}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Simulations over testing days:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/3.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/4.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/5.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/6.eps}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Histogram over testing days:}

\begin{columns}

\column{.4\textwidth}
On the right, we can see the histogram of the transition error for the testing days, and the histogram of the simulated transition error over the testing days.\\
\quad\\
We simulated the error SDE using Euler-Maruyama and using $\Delta t=\SI{10}{\min}$.\\
\quad\\
We may achieve more variance than needed because of the fat tail of the original data. Many error transitions are large, and they complicate the inference.

\column{.6\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=1\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=green!20}
\begin{frame}

{\Huge Lamperti Transform (process $Z_t=\psi(V_t)$):}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{About Lamperti:}

Let $\{\Delta V_i\}_{i=1}^n$ be the set of all error transitions, and $\psi(\theta_0,\alpha,\Delta V)$ the Lamperti transform. Notice that the Lamperti transitions $\{\Delta Z_i\}_{i=1}^n$ depend on $(\theta_0,\alpha)$ because $$\{\Delta Z_i\}_{i=1}^n=\psi(\theta_0,\alpha,\{\Delta V_i\}_{i=1}^n).$$
Then, if we compute $$\max_{(\theta_0,\alpha)}\mathbf{L}(\theta_0,\alpha,\{\Delta Z_i\}_{i=1}^n),$$
we are not computing a MLE in the classical sense, as the data is changing with the parameters. However, we can try to find a fixed point ${\color{blue}(\theta_0^*,\alpha^*)}$ such that
\begin{equation}
{\color{blue}(\theta_0^*,\alpha^*)}=\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{blue}\theta_0^*},{\color{blue}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
\label{FP}
\end{equation}
In this point, the likelihood has a maximum for the data set corresponding to that point. \alert{Does this approach have sense?}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Fixed point function:}

We are interested in finding the solution of (\ref{FP}). We have that, if $(\theta_0^*,\alpha^*)$ is a solution of (\ref{FP}), then
\begin{equation*}
(\theta_0^*,\alpha^*)-\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right)=0.
\end{equation*}
Given a pair $(\theta_0^{*},\alpha^{*})$, we call $(\theta_0^{**},\alpha^{**})$ to the solution of
\begin{equation*}
\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
\end{equation*}
For each $(\theta_0^{*},\alpha^{*})$, we define the relative error function
\begin{equation*}
\Psi(\theta_0^{*},\alpha^{*})=\frac{|\theta_0^{*}-\theta_0^{**}|}{|\theta_0^{*}|}+\frac{|\alpha^{*}-\alpha^{**}|}{|\alpha^{*}|}
\end{equation*}
and claim that $(\theta_0^*,\alpha^*)$ is a fixed point iff $\Psi(\theta_0^*,\alpha^*)=0$.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%+

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Fixed point function:}

\begin{columns}

\column{.5\textwidth}
On the right, we can see the numerical level sets of the error function $\Psi$.\\
\quad\\
The center deep green band is the set $\mathbb{A}$ such that $\Psi(\mathbb{A})\in[0.05,0.1]$. We do not achieve relative error smaller than 0.05.\\
\quad\\
We observe a particular behavior over the curves $\theta_0\alpha=k\in\R^+$. However, it can be a numeric effect.\\
\quad\\
We also observe that: $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.083\}\neq\emptyset.$$

\column{.5\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=1\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%+

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Fixed point function:}

\begin{columns}

\column{.5\textwidth}
On the right, we observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.038$ from the error SDE.\\
\quad\\
We choose $(\theta_0,\alpha)=(2.200,0.038)$.\\
\quad\\
We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE". \alert{Is this interpretation correct?}

\column{.5\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=1\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood_2.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Simulations over testing days:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/lamperti_optimal/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/lamperti_optimal/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/lamperti_optimal/3.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/lamperti_optimal/4.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/lamperti_optimal/5.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/lamperti_optimal/6.eps}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Simulations over testing days:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/lamperti_optimal/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/lamperti_optimal/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/lamperti_optimal/3.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/lamperti_optimal/4.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/lamperti_optimal/5.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/lamperti_optimal/6.eps}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Histogram over testing days:}

\begin{columns}

\column{.4\textwidth}
On the right, we can see the histogram of the Lamperti transitions for the testing days, and the histogram of the simulated Lamperti transitions over the testing days.\\
\quad\\
We simulated the Lamperti SDE using Euler-Maruyama and using $\Delta t=\SI{10}{\min}$.

\column{.6\textwidth}
\begin{figure}[ht!]
\centering
\includegraphics[width=1\textwidth]{../../MATLAB_Files/Results/histograms/lamperti/Optimal_Lamperti.eps}
\end{figure}

\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Some key points:}

\begin{enumerate}

\item The moments' ODEs were verified with the empirical moments using Euler–Maruyama method.
\item From the set $\mathbb{A}$, we choose a point that satisfies $\theta_0\alpha=0.083$ as it looks to be a necessary condition for the error SDE.
\item We do inference using 127 days ('training days'), and simulate over the other 128 days ('testing days'). In total, we have  255 days, since we removed all the days with curtailing. To guarantee independence between the days, we never do inference using two consecutive (in the calendar sense) days.
\item \alert{Should the bands be centered in the transformed forecast?}
\item \alert{Does this fixed-point method have sense?}
\item The day 07/01/2019 was particularly bad, with a terrible forecast.

\end{enumerate}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=green!20}
\begin{frame}

{\Huge Two optimal values:}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Two optimal values:}

We achieve two possible values for the parameters.
\begin{enumerate}

\item Using inference in the error SDE, we get $(\theta_0^E,\alpha^E)=(1.180,0.070)$.
\item Using our fixed-point method for the Lamperti MLE, and imposing the extra condition $\theta_0\alpha=0.038$, we get $(\theta_0^L,\alpha^L)=(2.200,0.038)$.

\end{enumerate}
\quad\\
\quad\\
\alert{How can we compare which is better? Or even correct?} We will show in the next slides comparative histograms, paths and probability bands. All of them for the original error SDE.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Error transitions histograms:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Lamperti_Optimal.eps}
\end{figure}

We can see two histograms for the error transitions. On the left, using $(\theta_0^E,\alpha^E)$, while on the right, using $(\theta_0^L,\alpha^L)$.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Simulations over testing days: First row: $(\theta_0^E,\alpha^E)$, second row: $(\theta_0^L,\alpha^L)$}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/3.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/Optimal_Lamperti/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/Optimal_Lamperti/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/bands_testing_days/Optimal_Lamperti/3.eps}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Simulations over testing days: First row: $(\theta_0^E,\alpha^E)$, second row: $(\theta_0^L,\alpha^L)$}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/Optimal_Lamperti/1.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/Optimal_Lamperti/2.eps}
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/paths_testing_days/Optimal_Lamperti/3.eps}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=green!20}
\begin{frame}

{\Huge Other option for Lamperti:}\\
\quad\\
\quad\\
Here we follow \textbf{Likelihood Inference for Discussion: A Survey}, from \textbf{Yacine A\"it-Sahalia}.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Density for the error:}

Recall our definitions: $\{\Delta V_i\}_{i=1}^n$ the set of error transitions, $\psi(\theta_0,\alpha,v)$ the Lamperti transform, $\{\Delta Z\}_{i=1}^n$ the transitions after the Lamperti transform, and $\bm{\theta}=(\theta_0,\alpha)$.\\
\quad\\
Our main objective is to estimate the transition density $\rho_V(v|v_0;\bm{\theta})$. Recall from the Lamperti transform definition that $\frac{\dif\psi}{\dif v}(v)=\frac{1}{\sigma(v;\bm{\theta})}$. Then, by the Jacobian formula, we have an expression that related $\rho_V(v|v_0;\bm{\theta})$ and $\rho_Z(z|z_0;\bm{\theta})$:
\begin{equation*}
\rho_V(v|v_0;\bm{\theta})=\frac{\rho_Z(z|z_0;\bm{\theta})}{\sigma(z;\bm{\theta})},
\end{equation*}
where $z=\psi(z;\bm{\theta})$, and we assume that $\rho_Z$ is Gaussian with mean $\mu_Z$ and variance $\sigma_Z^2$ for the random variable $Z$.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Density for the error:}

We still have analytic expressions for the moments of the SDE for $V_t$, and we would like to find a relation between this moments, and the mean $\mu_Z$ and variance $\sigma^2_Z$.\\
\quad\\
As $\psi$ and $\sigma$ are not linear, it is not easy to find $E[V]$ and $E[V^2]$ with respect to the density  $\frac{\rho_Z(z|z_0;\bm{\theta})}{\sigma(z;\bm{\theta})}$. If we could find this moments, we would be able to use the MLE directly with the data $\{\Delta V_i\}_{i=1}^n$.\\
\quad\\
One option is to construct empirical moments as a function of $(\theta_0,\alpha,\mu_Z,\sigma_Z)$ with Monte Carlo, and after do the moments matching using this empirical construction.

\end{frame}

\end{document}

### 2020-04-28 LaTeX_Code/Paper/paper_1line.tex
1line formulas

@@
 
-\subsection{Physical Constraints}
+\subsection{Physical Constraints} \label{Physical_Constraints}
 
@@
 \begin{align}
-Z_t = h(V_t, t)  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \,dv \Bigg{\vert}_{v = V_t}  \nonumber \\
-& = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
+Z_t = h(V_t, t)  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \,dv \Bigg{\vert}_{v = V_t}   = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
 \end{align}
@@
 \begin{align}
-dZ_t = \Bigg[  & \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  \nonumber \\ 
-& + \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \,dt + dW_t \,.
+dZ_t = \Bigg[  & \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  + \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \,dt + dW_t \,.
 \label{eq:stindepSDE}
@@
 \begin{align}
-dZ_t & = \Bigg[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)}  \nonumber \\
-&  - \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \Bigg] \,dt + dW_t \nonumber \\
+dZ_t & = \Bigg[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)}   - \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \Bigg] \,dt + dW_t \nonumber \\
 &  = \left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \,dt + dW_t \,.
@@
 
-In section (\ref{Sec: Physical_Constraints}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$.
+In Subsection (\ref{Physical_Constraints}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$.
 Even when it would be reasonable to choose an arbitrary small $\epsilon>0$, we aim to approximate it using the LSM estimator.\\

### 2020-05-06 LaTeX_Code/Paper/paper_1line.tex
some reorganization

@@
 
-{\color{red} Change this paragraph. Discuss with the global dataset, the dataset after removing days when curtailing has been detected, the data set without curtailing and with Lamperti transform.}
+{\color{red} REWRITE In this paper we present the phenomenological model based on SDE approach in Section \ref{Section_3} and describe the physical constraints in and how these constrains can be met.
+Then, in Section \ref{Section_4}, we will introduce an alternative formulation of the model in Lamperti space.
+In Section \ref{Section_6}, we show our parameter estimation procedure and its results in Section \ref{Section_7}.
+We compare alternative models in Section \ref{Section_8} and different forecast providers in Section \ref{Section_9}.}
+
+%---END SECTION 1---
+
+%---BEGIN SECTION 2---
+\section{Wind power production data in Uruguay and forecast providers } \label{Section_2}
+
+{\color{red} Description of the global 2019 dataset, then the dataset after removing the days with curtailment (curtailment detection and removal), analysis of the dataset without curtailment.}
 We have available a year long data set from Uruguay based on 363 observation paths, each of which is 24-hours long with observations recorded every 10 min.
@@
 
-In this paper we present the phenomenological underlying model in Section \ref{Section_2} and describe the physical constraints in Section \ref{Section_3} and how these constrains can be met.
-Then, in Section \ref{Section_4}, we will introduce an alternative formulation of the model in Lamperti space.
-In Section \ref{Section_5}, we show our parameter estimation procedure and its results in Section \ref{Section_6}.
-We compare alternative models in Section \ref{Section_7} and different forecast providers in Section \ref{Section_8}.
-
 \begin{figure}[H]
 \centering
-\includegraphics[width=0.45\textwidth]{plots/5.eps}
-\includegraphics[width=0.45\textwidth]{plots/245.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/661.eps}
-\includegraphics[width=0.45\textwidth]{plots/805.eps}
+\includegraphics[width=0.35\textwidth]{plots/5.eps}
+\includegraphics[width=0.35\textwidth]{plots/245.eps}\\
+\includegraphics[width=0.35\textwidth]{plots/661.eps}
+\includegraphics[width=0.35\textwidth]{plots/805.eps}
 \caption{Four samples from the Uruguayan data of 2019.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
+\includegraphics[width=0.35\textwidth]{plots/LP_6.eps}
+\includegraphics[width=0.35\textwidth]{plots/MP_6.eps}\\
+\includegraphics[width=0.35\textwidth]{plots/HP_6.eps}
+\includegraphics[width=0.35\textwidth]{plots/AP_6.eps}
 \caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP.eps}
+\includegraphics[width=0.35\textwidth]{plots/LP.eps}
+\includegraphics[width=0.35\textwidth]{plots/MP.eps}\\
+\includegraphics[width=0.35\textwidth]{plots/HP.eps}
+\includegraphics[width=0.35\textwidth]{plots/AP.eps}
 \caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
+\includegraphics[width=0.35\textwidth]{plots/LP_t.eps}
+\includegraphics[width=0.35\textwidth]{plots/MP_t.eps}\\
+\includegraphics[width=0.35\textwidth]{plots/HP_t.eps}
+\includegraphics[width=0.35\textwidth]{plots/AP_t.eps}
 \caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
@@
 
-%---END SECTION 1---
-
-%---BEGIN SECTION 2---
-\section{Phenomenological  Model} \label{Section_2}
+%---END SECTION 2---
+
+%---BEGIN SECTION 3---
+\section{Phenomenological  Model} \label{Section_3}
 
@@
 
-%---END SECTION 2---
-
-%---BEGIN SECTION 3---
-\section{State independent diffusion term: Lamperti transform} \label{Section_3}
+%---END SECTION 3---
+
+%---BEGIN SECTION 4---
+\section{State independent diffusion term: Lamperti transform} \label{Section_4}
 
@@
 \begin{align}
-Z_t = h(V_t, t)  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \,dv \Bigg{\vert}_{v = V_t}   = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
+Z_t = h(V_t, t; \bm{\theta} )  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \,dv \Bigg{\vert}_{v = V_t}   = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
 \end{align}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
+\includegraphics[width=0.35\textwidth]{plots/LP_t_LP.eps}
+\includegraphics[width=0.35\textwidth]{plots/MP_t_LP.eps}\\
+\includegraphics[width=0.35\textwidth]{plots/HP_t_LP.eps}
+\includegraphics[width=0.35\textwidth]{plots/AP_t_LP.eps}
 \caption{Transitions after the Lamperti transform.
@@
 
-%---END SECTION 3---
-
-%---BEGIN SECTION 4---
-\section{Likelihood in $V$ space} \label{Section_4}
-
-\subsection{Likelihood}
+%{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models, that is if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.}
+
+%---END SECTION 4---
+
+%---BEGIN SECTION 5---
+\section{ Likelihood functions of the forecast errors data and optimization algorithm} \label{Section_5}
+
+\subsection{Likelihood in the $V-$space}
 
@@
 
-Closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases.
+Closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
 Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
 Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.
- {\color{red} Rewrite: Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.}
-
-\subsection{Approximate Likelihood}
+ {\color{red} Rewrite: Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, consider Preston and Wood, then Egorov, and then Sorensen, remove the
+ survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}, refer to time-homogeneous.}
+
+\subsection{Approximate likelihood  in the $V-$space}
 
 Gaussian approximations to the transition densities of nonlinear time-in\-ho\-mo\-geneous SDEs are available through different algorithms  \autocite[Chapter 9]{saso}.
-However, as Figure (\ref{fig:error_transitions}) may suggest at a first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
+However, as Figure \ref{fig:error_transitions} may suggest at a first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
 
@@
 
+\subsection{Approximate likelihood  in the $Z-$space}
+
 The transition density of the process $Z$, which has been defined through the Lamperti transformation (\ref{eq:LampZ}) of $V$, can be conveniently approximated by a Gaussian surrogate density.
@@
 
-\subsection{Optimization} \label{opt_sec}
+\subsection{Algorithm for the approximate maximum likelihood estimations} \label{opt_sec}
 
@@
 To guarantee the good behave for our optimization algorithm, we aim to start the optimization as close as we can from the optimal parameters.
-We use \textbf{Lease Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess, and to tune the hyper-parameter $\epsilon\in(0,\frac{1}{2})$.
+We use \textbf{Least Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess, and to tune the hyper-parameter $\epsilon\in(0,\frac{1}{2})$.
 
@@
 \end{equation}
-As Equation (\ref{Eq-1}) is convex in $c$ (composition of convex is convex), it is enough to verify the first order optimality conditions.
+As Equation (\ref{Eq-1}) is convex in $c$ (composition of convex is convex), it is enough to verify the first order optimality conditions. From
 \begin{equation*}
 \begin{split}
-\frac{\partial f}{\partial c}&=\sum_{i=1}^n2(-V_i)(-\Delta t)(V_{i+1}-V_i(1-\theta_0\Delta t))\\
-&=\sum_{i=1}^n2V_i\Delta t(V_{i+1}-V_i(1-c\Delta t))\\
+\frac{\partial f}{\partial c}&=\sum_{i=1}^n2(-V_i)(-\Delta t)(V_{i+1}-V_i(1-\theta_0\Delta t))
+=\sum_{i=1}^n2V_i\Delta t(V_{i+1}-V_i(1-c\Delta t))\\
 &=\sum_{i=1}^n2V_{i+1}V_i\Delta t-2V_i^2\Delta t+2V_i^2\Delta t^2c.
@@
 \end{equation*}
-Then, $c^{**}$ satisfies
+it follows that $c^{**}$ satisfies
 \begin{equation}
@@
 
-\subsubsection{Negative Log-Likelihood Minimization in $V$ Space} \label{Sec:MinLH}
+\subsubsection{Negative log-likelihood minimization in the $V-$space} \label{Sec:MinLH}
 
@@
 
-\subsubsection{Negative Log-Likelihood Minimization in $Z$ Space} \label{Sec:MinLHL}
+\subsubsection{Negative log-likelihood minimization in the $Z-$space} \label{Sec:MinLHL}
 
@@
 
-%---END SECTION 4---
-
-%---BEGIN SECTION 5---
-\section{Model Comparison} \label{Section_5}
+%---END SECTION 5---
+
+%---BEGIN SECTION 6---
+\section{Applications to the Uruguay wind and forecast dataset} \label{Section_6}
+
+Following the instruction for the initial guesses from section $\ref{opt_sec}$, we get the initial guesses $(\theta_0,\alpha,\delta)\approx(1.2,0.1,0.6)$.
+
+\subsection{Calibration of the approximate negative log-likelihood in the $V-$space}
+
+We plot the Negative Log-Likelihood as a function of the parameters.
+The plots can be seen in Figure (\ref{fig:neg-LL}).
+We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.jpg}
+\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
+\label{fig:neg-LL}
+\end{figure}
+On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood. The thick violet band is the region where the function reaches its minimums.\\
+We can see the \textbf{initial guess} point, the result of three different \textbf{optimization tools} from MATLAB, and the minimum point that we found from the \textbf{evaluations} that generate the plot.
+\begin{table}[]
+\centering
+\begin{tabular}{lccc}
+\toprule
+ & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
+ \midrule
+ Initial guess & 1.629 & 0.060 & 0.098 \\
+ fminsearch & 1.135 & 0.073 & 0.083 \\
+ fmincon & 1.366 & 0.061 & 0.083 \\
+ fminunc & 1.628 & 0.051 & 0.083 \\
+ evaluations & 1.180 & 0.070 & 0.083 \\
+ \bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{Calibration of the approximate negative log-likelihood in the $Z-$space}
+
+We plot the Negative Log-Likelihood as a function of the parameters.
+The plots can be seen in Figure (\ref{fig:neg-LL}).
+We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
+\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
+\label{fig:neg-LLL}
+\end{figure}
+In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets of the error function $\Psi$.\\
+The center deep green band is the set $\mathbb{A}$ such that $\Psi(\mathbb{A})\in[0.05,0.1]$. We do not achieve relative error smaller than 0.05.\\
+We observe a particular behavior over the curves $\theta_0\alpha=k\in\R^+$. However, it can be a numeric effect.\\
+We also observe that: $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.083\}\neq\emptyset.$$
+On the right, we observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.038$ from the error SDE.\\
+We choose $(\theta_0,\alpha)=(2.200,0.038)$.\\
+We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".
+
+\subsection{Model comparison} \label{Model_Comp}
 
@@
 \end{table}
-%---END SECTION 5---
-
-%---BEGIN SECTION 6---
-\section{Forecast Provider Comparison} \label{Section_6}
+
+\subsection{Forecast providers comparison} \label{Forecast_Comp}
 We compare forecasts from two different companies for the same period.
@@
 
-%---END SECTION 6---
-
-%---BEGIN SECTION 7---
-\section{Results} \label{Section_7}
-
-\subsection{Initial guesses}
-
-Following the instruction for the initial guesses from section $\ref{opt_sec}$, we get the initial guesses $(\theta_0,\alpha,\delta)\approx(1.2,0.1,0.6)$.
-
-\subsection{Negative Log-Likelihood in $V$ Space}
-
-We plot the Negative Log-Likelihood as a function of the parameters.
-The plots can be seen in Figure (\ref{fig:neg-LL}).
-We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
+{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
+How much data do we need to achieve enough accuracy for the estimates of the two parameters?
+Generally, such accuracy is application dependent.}
+
+\subsection{Calibration of Model 2 with additional parameter $\delta$ TO DO}
+
+After calibrating Model 2 on the training set, we can generate simulations of the wind power production for the time horizon of interest.
+The next Figure \ref{fig:simulation_paths} shows five simulated paths of the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.jpg}
-\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
-\label{fig:neg-LL}
-\end{figure}
-On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood. The thick violet band is the region where the function reaches its minimums.\\
-We can see the \textbf{initial guess} point, the result of three different \textbf{optimization tools} from MATLAB, and the minimum point that we found from the \textbf{evaluations} that generate the plot.
-\begin{table}[]
-\centering
-\begin{tabular}{lccc}
-\toprule
- & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
- \midrule
- Initial guess & 1.629 & 0.060 & 0.098 \\
- fminsearch & 1.135 & 0.073 & 0.083 \\
- fmincon & 1.366 & 0.061 & 0.083 \\
- fminunc & 1.628 & 0.051 & 0.083 \\
- evaluations & 1.180 & 0.070 & 0.083 \\
- \bottomrule
-\end{tabular}
-\end{table}
-
-\subsection{Negative Log-Likelihood in $Z$ Space}
-
-We plot the Negative Log-Likelihood as a function of the parameters.
-The plots can be seen in Figure (\ref{fig:neg-LL}).
-We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
+\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
+\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
+\quad\\
+\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
+\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
+\caption{Five simulated wind power production paths using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. }
+\label{fig:simulation_paths}
+\end{figure}
+
+On the basis of the approximate MLEs for Model 2, we can obtain empirical pointwise confidence bands for the wind power production.
+The next Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
-\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
-\label{fig:neg-LLL}
-\end{figure}
-In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets of the error function $\Psi$.\\
-The center deep green band is the set $\mathbb{A}$ such that $\Psi(\mathbb{A})\in[0.05,0.1]$. We do not achieve relative error smaller than 0.05.\\
-We observe a particular behavior over the curves $\theta_0\alpha=k\in\R^+$. However, it can be a numeric effect.\\
-We also observe that: $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.083\}\neq\emptyset.$$
-On the right, we observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.038$ from the error SDE.\\
-We choose $(\theta_0,\alpha)=(2.200,0.038)$.\\
-We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".
-
-\subsection{Main guesses}
-
-{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models (if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.)}
-
-{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
-How many data we need to achive enough accuracy for the estimates of the two parameters?
-Generally, such accuracy is application dependent}
-
- We are able to obtain the parameters based on the complete data sets. Using the different models variations, we are able to simulate wind power production given a forecast. We see in figures ()-()
-five possible wind power production paths for each model.\\
-
-In Figures ()-(), we show point-wise empirical confidence bands for the different models.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
+\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/1.eps}
+\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/2.eps}\\
 \quad\\
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
-\caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
-Forecast is from Uruguay pertaining to  year 2019.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/1.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/2.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/3.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/4.eps}
-\caption{We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
-Actual production plotted in retrospect.
-Forecast and data is from Uruguay pertaining to  year 2019.}
+\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/3.eps}
+\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/4.eps}
+\caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Blue line: real production.}
+\label{fig:confidence_bands}
 \end{figure}
@@
 
-%---END SECTION 7---
-
-%---BEGIN SECTION 8---
-\section{Conclusions} \label{Section_8}
+%---END SECTION 6---
+
+%---BEGIN SECTION 7---
+\section{Conclusions} \label{Section_7}
 
@@
 Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.
-%---END SECTION 8---
+%---END SECTION 7---
 
@@
 
-\section{The model}
+\subsection{The model}
 For a time horizon $T>0$ and  a parameter $\alpha > 0$ and $(\theta_t)_{t\in[0,T]}$ a positive deterministic  function,  let us consider the model  given by
@@
 
-\section{New model}
+\subsection{New model}
 In what follows we adapt the proof of the above theorem for the new model 
@@
 Otherwise the Lamperti transform is not valid if the state space of $X$ is $[0,1]$.
+%---END APPENDIX---
 

### 2020-05-16 LaTeX_Code/Paper/paper_1line.tex
new section 2 - revised section 8

@@
 
-\usepackage[backend=biber, style=authoryear, citestyle=authoryear, autocite=inline]{biblatex} % package for bibliography 
+\usepackage[backend=biber, style=authoryear, citestyle=authoryear, autocite=inline, isbn=true]{biblatex} % package for bibliography 
 %\DeclareLanguageMapping{english}{english-apa}
@@
 
-{\color{red} Description of the global 2019 dataset, then the dataset after removing the days with curtailment (curtailment detection and removal), analysis of the dataset without curtailment.}
-We have available a year long data set from Uruguay based on 363 observation paths, each of which is 24-hours long with observations recorded every 10 min.
-In total, it is a data set of approximately fifty thousand data points recorded in 2019.
-See Figure (\ref{fig:sample_data}).
-Data are normalized with respect to the maximum power capacity of wind power production in Uruguay, which is $\SI{1474}{\mega\watt}$.
-However, sometimes the real production is artificially modifies due to curtailing.
-This effect becomes clear when we inspect for different power production levels.
-We split the available data into low, medium and high power range.
-See Figure (\ref{fig:data_curtailing}).\\
-We identify and remove the days with curtailing, removing a total of 108 days.
-From the resulting 255 days, we use 127 days to train the system and 128 to test it.
-Also, to avoid correlation between days, we intercalate the days we use for training and testing ({\color{red} Show that 24h is enough to ensure independence}).
+In recent years, Uruguay has triggered a remarkable change in its energy matrix.
+In (\cite{irena}, p.23) Uruguay is among those countries showcasing innovation, like Denmark, Ireland, Germany, Portugal, and Spain, with proven feasibility of managing annual variable renewable energy higher than 25\% in power systems.
+
+According to (\cite{ren21}, pp.118-119), in 2018, Uruguay achieved 36\% of its electricity production from variable wind energy and solar PV, raising the share of generation from wind energy more than five-fold in just four years, from 6.2\% in 2014 to 33\% in 2018.
+
+At present, Uruguay is fostering even higher levels of wind penetration by boosting regional power trading with Argentina and Brazil. 
+In this rapidly evolving scenario, it is essential to analyze national data on wind power production joint with wind power short-term forecastings to orientate and assess the strategies and decisions of wind energy actors and businesses.
+
+Our study is based on publicly available data (source: Administrator of Electric Market) on the wind power production in Uruguay for the period March-December 2019, that we adequately normalized with respect to the present $\SI{1474}{\mega\watt}$ maximum installed wind power capacity.
+Each day, wind power production recordings are available every ten minutes.
+In this work, we have also considered data from three different forecast providers, available each day starting at 1 pm.
+
+The next Figure \ref{fig:sample_data} shows the wind power real production during four segments 24-hour long selected from the observation period together with their corresponding hourly short-term forecast, computed by a forecast provider.
+For the sake of visualization clarity, this Section relies only on forecasts from one provider, called "provider A" from now on, ranked as the most accurate forecast provider, as it emerged from our posterior analysis.
 
@@
 \includegraphics[width=0.35\textwidth]{plots/805.eps}
-\caption{Four samples from the Uruguayan data of 2019.
-Each sample compromises of two 24-hour paths.
-In blue is an hourly wind power production forecast.
-In orange is the actual wind power production recorded in 10 minute intervals.}
+\caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blu line).}
   \label{fig:sample_data}
 \end{figure}
+
+A global view of the discrepancy between the real production and the forecasted production, the forecast error, during the nine months observation period, is displayed in the following Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
+Low normalized generated power corresponds to the range $[0,0.3]$, mid-power refers to the range $(0.3,0.6]$, and high-power to the range $(0.6,1]$.
 
@@
 \includegraphics[width=0.35\textwidth]{plots/AP_6.eps}
-\caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production.
-Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$.
-We have a total of 363 days to use.}
+\caption{Wind production forecast error histograms during the period March-December 2019: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
   \label{fig:data_curtailing}
 \end{figure}
+
+We may observe that all the histograms in the Figure \ref{fig:data_curtailing} exhibit skewed patterns, to a different extent, as well as extreme observations.
+The presence of these features can be partly explained.
+The analysis of the dataset highlighted that, during several 24-hour segments, the system operators decided to reduce, or even cease the wind power production {\color{red} add why curtailment and references}.
+
+The curtailment of the wind power production imposed by the system operators has a strong influence on the forecast error.
+To build a model that, driven by the available forecast, allows to include the true power production with a prescribed degree of uncertainty, it is necessary to remove the data segments affected by wind curtailment.
+
+Once we removed all the 24-hour segments associated with wind curtailment, we kept 147 segments.
+In the absence of the curtailment effect, the forecast error histograms are shown in Figure \ref{fig:data_after_clean} below, where it is appreciable the reduction of skewness.
 
@@
 \includegraphics[width=0.35\textwidth]{plots/AP.eps}
-\caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
+\caption{Wind production forecast error histograms during the period March-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
   \label{fig:data_after_clean}
 \end{figure}
+
+In this stage of data preprocessing, we obtain another useful result by applying the first-order difference operator to the forecast errors. 
+The forecast error transition histograms, displayed in the next Figure \ref{fig:error_transitions}, will constitute later a reference for the visual assessment of the global fit of the proposed models.
 
@@
 \includegraphics[width=0.35\textwidth]{plots/AP_t.eps}
-\caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
+\caption{Forecast error transition histograms during the period March-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
 \label{fig:error_transitions}
 \end{figure}
+
+ {\color{red}  We can observe the lack of gaussianity.}
+
+ ({\color{red} MOVE THIS COMMENT.
+We use 73 days to train the system and 74 to test it.
+Also, to avoid correlation between days, we intercalate the days we use for training and testing.
+Show that 24h is enough to ensure independence}).
 
@@
 
-In this section, once we analyzed the available dataset, we consider a type of phenomenological model for the normalized wind power generation forecasts which is given, in its most general form, as a stochastic process $X = \{X_t, \, t \in [0,T] \}$  defined by the following stochastic differential equation (SDE):
+After analyzing the available dataset, we are now in the condition to build a type of phenomenological model for the normalized wind power generation forecasts that, in its most general form, is a stochastic process $X = \{X_t, \, t \in [0, T] \}$  defined by the following stochastic differential equation (SDE):
 
@@
 \begin{equation}\label{Assumption:3}
-\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
-\end{equation} \label{condC}
+\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{B}. 
+\end{equation} \label{condB}
 The proof of this theoretical statement is presented in Section \ref{Appendix}. \\
 
-Remark: Condition (C) shows that the time-varying parameter $\theta_t$ becomes unbounded when $p_t = 0$ or $p_t = 1$. Therefore, we consider the following truncated prediction function
+Remark: Condition (B) shows that the time-varying parameter $\theta_t$ becomes unbounded when $p_t = 0$ or $p_t = 1$. Therefore, we consider the following truncated prediction function
 \begin{equation}
@@
   \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= \big(\dot p_t - \theta_t (X_t-p_t)  \big)dt  +\sqrt{2 \alpha \theta_t X_t (1-X_t)} dW_t\,, \quad t\in[0,T] \\
+    dX_t \!\!\!&= \big(\dot p_t - \theta_t (X_t-p_t)  \big)dt  +\sqrt{2 \alpha \theta_0 X_t (1-X_t)} dW_t\,, \quad t\in[0,T] \\
    X_0  \!\!\!&=  x_0\in [0,1] \,,
@@
 \begin{equation}\label{eq:eds1}
-X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)ds  + \int_0^t\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s, \quad x_0>0.
+X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)ds  + \int_0^t\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} dW_s, \quad x_0>0.
 \end{equation}
@@
 \psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)ds \\
-&+ \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s + \alpha \int_0^t \theta_sg_n(|X_s|)|X_s(1-X_s)|ds.
+&+ \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} dW_s + \alpha \theta_0 \int_0^t  g_n(|X_s|) |X_s(1-X_s)|ds.
 \end{align*}
@@
 $$
-\mathbb E[\psi_n(X_t)]\le \psi_n(x_0) +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \big)ds + \frac{2\alpha}{n}\int_0^t \theta_s\mathbb E |1-X_s|ds.
+\mathbb E[\psi_n(X_t)]\le \psi_n(x_0) +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \big)ds + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E |1-X_s|ds.
 $$
@@
 $$
-\mathbb E[|X_t| -X_t ]\le \int_0^t \theta_s \mathbb E[|X_s| - X_s ]ds.
+\mathbb E[|X_t| -X_t ]\le \int_0^t \theta_s \mathbb E[ X_s - |X_s| ]ds.
 $$
@@
 \end{proof}
-
-\begin{Thm}
-Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
-Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$. Assume in addition that
-\begin{equation}\label{Assumption:2}
-0<\alpha < \frac 12\quad \mbox{ and }\quad \forall  t\in[0,T],\;\; \alpha\theta_t\le \dot p_t +\theta_tp_t \le (1-\alpha)\theta_t \tag{B}. 
-\end{equation}
- Then, $\tau_0=\tau_1=+\infty$ a.s.
-\end{Thm}
-\begin{proof}
-For $t\in[0,\tau_0[$, we have 
-$$
-\frac{dX_t}{X_t}=\left( \frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)\dif t  +\sqrt{\frac{2\alpha \theta_t(1-X_t)}{X_t}} \dif W_t 
-$$  
-so that
-$$
-X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_s(p_s-\alpha)}{X_s}ds-(1-\alpha)\int_0^t\theta_sds + M_t\Big),
-$$
-where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_s(1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_t(p_t-\alpha)\ge0$, we deduce that
-$$
-X_t\ge x_0\exp\Big(-(1-\alpha)\int_0^t\theta_sds + M_t\Big).
-$$
-By way of contradiction let us assume that  $\{\tau_0<\infty\}$, then letting $t\to \tau_0$ we deduce that $\lim_{t\to \infty} \mathbf 1_{\{\tau_0<\infty\}}M_{t\wedge \tau_0}=\mathbf -1_{\{\tau_0<\infty\}}\infty$ a.s.
-This leads to a contradiction since we know that continuous martingales likewise the Brownian motion cannot converge  almost surely to $+\infty$ or $-\infty$.
-It follows that $\tau_0=\infty$ almost surely.
-Next, recalling that  the process $(Y_t)_{t\geq 0}$  given by $Y_t=1-X_t$ is solution to
-$$
-dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \theta_tY_t(1-Y_t)} dW_t 
-$$
-we deduce using similar arguments as above 
-$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \theta_t\ge 0$.
-\end{proof}
-
-\subsection{New model}
-In what follows we adapt the proof of the above theorem for the new model 
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= \big(\dot p_t - \theta_t (X_t-p_t)  \big)dt  +\sqrt{2 \alpha \red{\theta_0} X_t (1-X_t)} dW_t\,, \quad t\in[0,T] \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{eq:model2}
-\end{equation}
 
@@
 \begin{equation}\label{Assumption:3}
-\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
+\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{B}. 
 \end{equation}
@@
 $$
-X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \red{\theta_0}\alpha)}{X_s}ds+\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big),
-$$
-where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_s(1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \red{\theta_0}\alpha\ge0$, we deduce that
+X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \red{\theta_0}\alpha}{X_s}ds+\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big),
+$$
+where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_0 (1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \red{\theta_0}\alpha\ge0$, we deduce that
 $$
@@
  \end{proof}
- \section{Answers to Renzo's questions} 
-{\color{blue}So, Theorem \ref{thm:mod2} answers the second question in slide 11.} The new condition \eqref{Assumption:3} that guarantees  for $(X_t)_{t\ge0}$ to stay in $]0,1[$ depends now on $\alpha$.
-I would keep condition \eqref{Assumption:3} as we have a proof for it.
-Moreover, if condition \eqref{Assumption:3} is satisfied, then  the orange condition in slide 8 is also satisfied
-since we have 
-$$
-\max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\ge \max\left(\frac{\frac{\alpha\theta_0}{2}+\dot p_t}{1-p_t},\frac{\frac{\alpha\theta_0}{2}-\dot p_t}{p_t}\right)
-$$
-which ensures that $Z$ don't hit the boundaries too according to Renzo's intuitive arguments.\\ 
-{\color{blue}Concerning, the first question on slide 11:} we can't apply Itô's formula, unless we are sure that the process don't hit the boundaries, that's why we have to assume  \eqref{Assumption:3} before using Itô's formula.
-In addition, as the diffusion coefficient of $X$  given by  $x\mapsto \sqrt{\frac{2\alpha \red{\theta_0}(1-x)}{x}}$  is strictly positive for all $x$ in the state space of $X$, namely $]0,1[$ under assumption \eqref{Assumption:3},  this is enough to ensure that the transformation between $Z$ and $X$ is bijective so that we deduce the existence and uniqueness of $Z$ from those of $X$.
-Otherwise the Lamperti transform is not valid if the state space of $X$ is $[0,1]$.
+
+Remark: As the diffusion coefficient of $X$  given by  $x \mapsto \sqrt{2 \alpha \theta_0 x(1-x)}$  is strictly positive for all $x \in  ]0,1[$, the condition \eqref{Assumption:3}  ensures that the transformation between $Z$ and $X$ is bijective, so that we deduce the properties of existence and uniqueness of $Z$ from those of $X$.
+The application of  It\^{o}'s formula in Section \ref{Section_4} is subjected to the condition \eqref{Assumption:3} that avoids the process $X$ hits the boundaries of the interval $ ]0,1[$, otherwise the Lamperti transform is not applicable.
+
 %---END APPENDIX---

### 2020-05-17 LaTeX_Code/Paper/paper_1line.tex
more updates, among them proposal last paragraph Section 1

@@
 We apply the model to Uruguayan wind power forecasts together with historical wind power production data pertaining to the year 2019.
+\\
 
-{\color{red} REWRITE In this paper we present the phenomenological model based on SDE approach in Section \ref{Section_3} and describe the physical constraints in and how these constrains can be met.
-Then, in Section \ref{Section_4}, we will introduce an alternative formulation of the model in Lamperti space.
-In Section \ref{Section_6}, we show our parameter estimation procedure and its results in Section \ref{Section_7}.
-We compare alternative models in Section \ref{Section_8} and different forecast providers in Section \ref{Section_9}.}
+In Section \ref{Section_2}, we introduce the main characteristics of a real data set encompassing the normalized wind power production in Uruguay during the period April-December 2019, joint with the most accurate predictions, as highlighted in our posterior analysis, performed by one out of the three sources of forecast providers.
+The significant steps for constructing phenomenological models of the normalized wind power production and the forecast error based on stochastic differential equations are described in Section \ref{Section_3}.
+After reformulating the SDE for the forecast error in Section \ref{Section_4}, by applying the Lamperti transform that leads to a unit diffusion coefficient, we write down in Section \ref{Section_5} the expressions for the likelihood functions of the forecast error in its original space and in the Lamperti space.
+We also derive simple approximations of the likelihood functions.
+Section \ref{Section_5} concludes with the description of the optimization algorithm to compute approximate maximum likelihood estimates, including the case where we expand the model comprising an initial transition from the time the forecast is performed to the time of the first forecast.
+In Section \ref{Section_6}, we apply our proposed parametric estimation procedure to the Uruguay wind and forecast dataset, comparing two alternative models and assessing, for the best candidate model, the performance of three different forecast providers.
+The proofs of the existence, strong uniqueness, and boundedness of the solutions of the SDE used to model normalized wind power production and its forecast error are given in the Appendix.
 
@@
 
-Our study is based on publicly available data (source: Administrator of Electric Market) on the wind power production in Uruguay for the period March-December 2019, that we adequately normalized with respect to the present $\SI{1474}{\mega\watt}$ maximum installed wind power capacity.
+Our study is based on publicly available data (source: Administrator of Electric Market) on the wind power production in Uruguay for the period April-December 2019, that we adequately normalized with respect to the present $\SI{1474}{\mega\watt}$ maximum installed wind power capacity.
 Each day, wind power production recordings are available every ten minutes.
@@
 \includegraphics[width=0.35\textwidth]{plots/AP_6.eps}
-\caption{Wind production forecast error histograms during the period March-December 2019: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
+\caption{Wind production forecast error histograms during the period April-December 2019: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
   \label{fig:data_curtailing}
@@
 The presence of these features can be partly explained.
-The analysis of the dataset highlighted that, during several 24-hour segments, the system operators decided to reduce, or even cease the wind power production {\color{red} add why curtailment and references}.
+The analysis of the dataset highlighted that, during several 24-hour segments, the system operators decided to reduce, or even cease the wind power production {\color{red} add more on curtailment and references}.
 
@@
 \includegraphics[width=0.35\textwidth]{plots/AP.eps}
-\caption{Wind production forecast error histograms during the period March-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
+\caption{Wind production forecast error histograms during the period April-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
   \label{fig:data_after_clean}
@@
 \includegraphics[width=0.35\textwidth]{plots/AP_t.eps}
-\caption{Forecast error transition histograms during the period March-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
+\caption{Forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
 \label{fig:error_transitions}
@@
 
- {\color{red}  We can observe the lack of gaussianity.}
-
- ({\color{red} MOVE THIS COMMENT.
-We use 73 days to train the system and 74 to test it.
-Also, to avoid correlation between days, we intercalate the days we use for training and testing.
-Show that 24h is enough to ensure independence}).
+The lack of gaussianity is a characteristic trait of the histograms depicted in Figure \ref{fig:error_transitions}, which provides an initial orientation for the model building stage.
+Later, we will also propose transforming data as a strategy that naturally leads to an alternative model.
 
@@
 To ensure that the process $X$ be the unique strong solution to (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the following condition:
-%has to be selected according to the following rule.
-Observe that the time derivative term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays a.s.
-inside the range $[0,1]$.
-In other words, the zero drift line defined by $a(x; p_t,\bm{\theta}) =0$, which is an attractor, must be contained inside the range $[0,1]$.
-Thus, we must have that
-%\begin{equation}
-%\frac{- |\dot{p_t}|}{p_t} \leq \theta_t \leq \frac{|\dot{p}_t|}{1- p_t}
-%\end{equation}
-%which is satisfied  by choosing a time-dependent  $\theta_t$ as follows,
-%\begin{equation}
-%\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \theta_0 >0\,. \label{theta_t}
-%\end{equation}
+
 \begin{equation}\label{Assumption:3}
@@
 that satisfies $p_t^{\epsilon} \in [\epsilon, 1 - \epsilon]$ for any $0 < \epsilon < \frac{1}{2}$ and $t \in [0,T]$, providing that $\theta_t$ is bounded for every $t \in [0,T]$. \\
+
+Remark: In this work, the analysis of the three different forecast datasets shows that there exists, for any forecast provider, a small $\epsilon >0$ to define the truncated prediction function fulfilling the above condition.
+\\
+
 From now on, we will keep the notation $p_t$ to denote the truncated prediction function (\ref{corrforecast}), unless specified otherwise.
 
-%{\color{red} The expression for $\theta_t$ is important: $\theta_t$ depens on $t$ through $\dot{p_t}$ and $p_t$.
-Besides it is parsimonious because only one unknown parameter appear in \ref{theta_t}.
-Recall it is an upped bound for the real inequality.
-}
-
-%\subsubsection*{Change of Variables:}
 \subsection{A model specification for the forecast error}
@@
 %---BEGIN SECTION 6---
-\section{Applications to the Uruguay wind and forecast dataset} \label{Section_6}
+\section{Application to the April-December 2019 Uruguay wind and forecast dataset} \label{Section_6}
+
+Our statistical analysis starts with partitioning the 147 segments of normalized wind power production, each 24-hour long.
+We select 73 non-contiguous segments for the models' calibration procedure, assigning them to the training set.
+The other 74 non-contiguous segments compose the test set.
+Such an allocation mechanism guarantees independence among the segments, matching the assumption we did in Section \ref{Section_5} to formulate the statistical models.
+
+{ \color{red} Show that 24h is enough to ensure independence?}
 
@@
 Assume in addition that for all $t\in[0,T]$,  $p_t\in]0,1[$ and that
-\red{
 \begin{equation}\label{Assumption:3}
@@
 \end{equation}
-}
  Then, $\tau_0=\tau_1=+\infty$ a.s.
@@
 $$
-\frac{dX_t}{X_t}= \left(\frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)dt  +\sqrt{\frac{2\alpha \red{\theta_0}(1-X_t)}{X_t}} dW_t 
+\frac{dX_t}{X_t}= \left(\frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)dt  +\sqrt{\frac{2\alpha \theta_0 (1-X_t)}{X_t}} dW_t 
 $$  
@@
 $$
-X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \red{\theta_0}\alpha}{X_s}ds+\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big),
+X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \theta_0 \alpha}{X_s}ds+\alpha\theta_0 t-  \int_0^t\theta_sds + M_t\Big),
 $$
-where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_0 (1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \red{\theta_0}\alpha\ge0$, we deduce that
+where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_0 (1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \theta_0 \alpha\ge0$, we deduce that
 $$
-X_t\ge x_0\exp\Big(\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big).
+X_t\ge x_0\exp\Big(\alpha\theta_0 t-  \int_0^t\theta_sds + M_t\Big).
 $$
@@
 $$
-dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \red{\theta_0}Y_t(1-Y_t)} dW_t 
+dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \theta_0 Y_t(1-Y_t)} dW_t 
 $$
 we deduce using similar arguments as above 
-$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \red{\theta_0}\ge 0$.
+$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \theta_0 \ge 0$.
  \end{proof}

### 2020-05-17 LaTeX_Code/Paper/paper_1line.tex
Corrected most figures in paper

@@
 \centering
-\includegraphics[width=0.35\textwidth]{plots/5.eps}
-\includegraphics[width=0.35\textwidth]{plots/245.eps}\\
-\includegraphics[width=0.35\textwidth]{plots/661.eps}
-\includegraphics[width=0.35\textwidth]{plots/805.eps}
+\includegraphics[width=0.45\textwidth]{plots/four_days/377.eps}
+\includegraphics[width=0.45\textwidth]{plots/four_days/417.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{plots/four_days/437.eps}
+\includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
 \caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blu line).}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{plots/LP_6.eps}
-\includegraphics[width=0.35\textwidth]{plots/MP_6.eps}\\
-\includegraphics[width=0.35\textwidth]{plots/HP_6.eps}
-\includegraphics[width=0.35\textwidth]{plots/AP_6.eps}
+\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
+\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
+\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
 \caption{Wind production forecast error histograms during the period April-December 2019: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{plots/LP.eps}
-\includegraphics[width=0.35\textwidth]{plots/MP.eps}\\
-\includegraphics[width=0.35\textwidth]{plots/HP.eps}
-\includegraphics[width=0.35\textwidth]{plots/AP.eps}
+\includegraphics[width=0.45\textwidth]{plots/LP.eps}
+\includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{plots/HP.eps}
+\includegraphics[width=0.45\textwidth]{plots/AP.eps}
 \caption{Wind production forecast error histograms during the period April-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{plots/LP_t.eps}
-\includegraphics[width=0.35\textwidth]{plots/MP_t.eps}\\
-\includegraphics[width=0.35\textwidth]{plots/HP_t.eps}
-\includegraphics[width=0.35\textwidth]{plots/AP_t.eps}
+\includegraphics[width=0.45\textwidth]{plots/LP_t.eps}
+\includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
+\includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
 \caption{Forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
@@
 \begin{figure}[h]
-  %\includegraphics[width=26mm,scale=1]{}
+\centering
+  \includegraphics[width=0.45\textwidth]{plots/31.eps}\includegraphics[width=0.45\textwidth]{plots/31_2.eps}
   \caption{{\color{red} Add Figure showing the difference with and without derivative tracking}}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{plots/LP_t_LP.eps}
-\includegraphics[width=0.35\textwidth]{plots/MP_t_LP.eps}\\
-\includegraphics[width=0.35\textwidth]{plots/HP_t_LP.eps}
-\includegraphics[width=0.35\textwidth]{plots/AP_t_LP.eps}
+\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
+\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
+\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
 \caption{Transitions after the Lamperti transform.
@@
 \centering
-\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
-\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
 \quad\\
-\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
-\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
 \caption{Five simulated wind power production paths using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. }
@@
 \centering
-\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/1.eps}
-\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/2.eps}\\
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/1.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/2.eps}\\
 \quad\\
-\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/3.eps}
-\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/4.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/3.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/4.eps}
 \caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Blue line: real production.}
@@
 \centering
-\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
-\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Lamperti_Optimal.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic/Lamperti_Optimal.eps}
 \end{figure}

### 2020-05-17 MATLAB_Files/testingFile.m

@@ -356,11 +356,33 @@ plot(xx,dist_to_plot);
 hold on;
 plot(x2,dist_to_plot_val,'x');
 
+%% Testing datetick:
 
+load count.dat;
+n = length(count);
+year = repmat(1995,1,n);
+month = repmat(4,1,n);
+day = repmat(18,1,n);
+hour = [1:n];
+minutes = zeros(1,n);
+sdate = datenum(year,month,day,hour,minutes,minutes);
+bar3(sdate,count);
+datetick('y','HHPM');
 
+%% Testing datetick:
 
+close all;
+clear all;
+clc;
 
-
+y = rand(25,1);
+x = [13:37]/24;
+plot(x,y);
+xticks(x);
+datetick('x','HHPM','keepticks');
+grid minor;
+xlim([min(x) max(x)]);
+xtickangle(90);
 
 
 

### 2020-05-21 LaTeX_Code/Paper/paper_1line.tex
with bib
sections 2-3

@@
 In recent years, Uruguay has triggered a remarkable change in its energy matrix.
-In (\cite{irena}, p.23) Uruguay is among those countries showcasing innovation, like Denmark, Ireland, Germany, Portugal, and Spain, with proven feasibility of managing annual variable renewable energy higher than 25\% in power systems.
+In (\cite{irena}, p.23) Uruguay is among those countries showcasing innovation, like Denmark, Ireland, Germany, Portugal, and Spain, with proven feasibility of managing annual variable renewable energy (VRE) higher than 25\% in power systems.
 
@@
 
-A global view of the discrepancy between the real production and the forecasted production, the forecast error, during the nine months observation period, is displayed in the following Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
+A view of the global discrepancy between the real production and the forecasted production, during the nine months observation period, is summarized through the forecast error histograms, Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
 Low normalized generated power corresponds to the range $[0,0.3]$, mid-power refers to the range $(0.3,0.6]$, and high-power to the range $(0.6,1]$.
@@
 The presence of these features can be partly explained.
-The analysis of the dataset highlighted that, during several 24-hour segments, the system operators decided to reduce, or even cease the wind power production {\color{red} add more on curtailment and references}.
+The analysis of the dataset highlighted that, during several 24-hour segments, the system operators decided to reduce, or even cease the wind power production.
+Indeed, as recalled in (\cite{irena2}, p.3), ``Uruguay experiences high curtailment levels because generation exceeds demand.'' Despite the large country’s interconnection capacity with Argentina and Brazil, there is no active cross-border market, the energy is traded via ad hoc short-term agreements.
+``Even with interconnection capacity exceeding peak demand, the power system experiences high VRE curtailment, mostly at night when wind generation exceeds demand.''
 
@@
 
-Once we removed all the 24-hour segments associated with wind curtailment, we kept 147 segments.
-In the absence of the curtailment effect, the forecast error histograms are shown in Figure \ref{fig:data_after_clean} below, where it is appreciable the reduction of skewness.
+Once we removed all the 24-hour segments showing wind curtailment, we set up a dataset containing 147 daily segments. 
+In the absence of the curtailment intervention, the forecast error histograms are shown below in Figure \ref{fig:data_after_clean}, where it can be appreciated skewness reduction, except for low power forecast errors histogram.
 
@@
 
-The lack of gaussianity is a characteristic trait of the histograms depicted in Figure \ref{fig:error_transitions}, which provides an initial orientation for the model building stage.
-Later, we will also propose transforming data as a strategy that naturally leads to an alternative model.
+The histograms in Figure \ref{fig:error_transitions} feature a non-Gaussianity trait and provide initial input for the model-building stage, which is described in Section next.
+Later, in Section \ref{Section_4}, guided from inferring the unknown model parameters, we will also propose transforming data as a strategy that naturally leads to an alternative model.
 
@@
 In this case, given  $ \mathbb{E} X_0 = p_0$, the diffusion has mean $\mathbb{E} X_t = p_t - e^{- \theta_0 t } \int_0^t \dot{p}_s  e^{\theta_0 s} ds$.
-The next Figure (\ref{fig:derivative_tracking}) illustrates paths of two diffusions with and without derivative tracking.
+The next Figure (\ref{fig:derivative_tracking}) illustrates how different behave the estimated confidence bands for two diffusion models with and without derivative tracking, fitting the same daily segment.
 
@@
   \includegraphics[width=0.45\textwidth]{plots/31.eps}\includegraphics[width=0.45\textwidth]{plots/31_2.eps}
-  \caption{{\color{red} Add Figure showing the difference with and without derivative tracking}}
+  \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (graph on the left) and with derivative tracking (graph on the right).}
   \label{fig:derivative_tracking}

### 2020-05-23 LaTeX_Code/Paper/paper_1line.tex
Added text in the paper, an extra figure, and some references

@@
 \usepackage{fancybox}
+\usepackage{hyperref}
 \usepackage{url}
 \usepackage[margin=0.5in]{geometry}
+\usepackage[backend=biber, style=authoryear, citestyle=authoryear, autocite=inline, isbn=true]{biblatex} % package for bibliography 
+%\DeclareLanguageMapping{english}{english-apa}
 
@@
 
-\usepackage[backend=biber, style=authoryear, citestyle=authoryear, autocite=inline, isbn=true]{biblatex} % package for bibliography 
-%\DeclareLanguageMapping{english}{english-apa}
-
 \addbibresource{sdewind.bib}
@@
 
-\newcommand{\add}{\textcolor{red}{[insert]}}
-
 \setcounter{page}{1}
@@
 %---BEGIN SECTION 1---
+
 \section{Introduction}  \label{Section_1}
@@
 {\color{red} Expand discussion about works on probabilistic forecasting.} However, there is a lacking in simulating and producing data driven stochastic forecasts based on real-world performance of forecasting models.
-It is crucial to capture actual performance of a forecast as it has been known that different forecasting technologies exhibits different behavior for different wind farms and seasons [ref].
+It is crucial to capture the forecast's actual performance as it has been known that different forecasting technologies exhibit different behavior for different wind farms and seasons (\cite{chang}).
 This is due to many factors which forecast are challenged to capture such as the surrounding terrains of the wind farm and the condition of the blades such as icing, wear and tear or dirt.
-It is known that complex terrains in both off shore and on shore locations decrease the accuracy of wind power forecasts significantly [ref].
+It is known that complex terrains in both off shore and on shore locations decrease the accuracy of wind power forecasts significantly (\cite{schicker2017short}).
 It also has been shown that the performance of forecasts varies from month to month.
@@
 The use of mean or median errors in this context may be misleading as wind power forecast errors are asymmetric.
-This is a natural consequence of wind power being non-negative and bounded by the maximuim capacity of production.
-This is important as the associated cost to power forecast errors are also asymmetric due to different costs for up and down  power regulations which are determined by the electricity market [ref].
+This is a natural consequence of wind power being non-negative and bounded by the maximum capacity of production.
+This is important as the associated cost to power forecast errors are also asymmetric due to different costs for up and down power regulations which are determined by the electricity market (\cite{tsitsiklis2015pricing}).
 
@@
 %---BEGIN SECTION 2---
+
 \section{Wind power production data in Uruguay and forecast providers } \label{Section_2}
@@
 \includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
-\caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blu line).}
+\caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blue line).}
   \label{fig:sample_data}
@@
 %---BEGIN SECTION 3---
+
 \section{Phenomenological  Model} \label{Section_3}
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&=  a(X_t; p_t, \dot{p}_t,\bm{\theta}) \,dt + b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \,dW_t\,, \quad t \in [0,T]  \\
-     X_0  \!\!\!&=  x_0 \in [0,1],
-  \end{array}\right. \label{eq:main}
+\begin{cases}
+    \dif X_t &=  a(X_t; p_t, \dot{p}_t,\bm{\theta})\dif t + b (X_t; p_t, \dot{p}_t, \bm{\theta} )\dif W_t, \quad t \in [0,T]  \\
+     X_0  &=  x_0 \in [0,1],
+\end{cases}
+ \label{eq:main}
 \end{equation}
@@
 
-Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} X_t = p_t$, given $  \mathbb{E} X_0 = p_0$.
-The application of  It\^{o}'s lemma on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s ds}$, leads to
+Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $  \mathbb{E}\left[X_0\right] = p_0$.
+The application of  It\^{o}'s lemma on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s \dif s}$, leads to
 \begin{equation*}
-d \left( X_t e^{\int_{0}^{t} \theta_s ds} \right) = e^{\int_{0}^{t} \theta_s ds} (\dot{p}_t + \theta_t p_t ) dt  + e^{\int_{0}^{t} \theta_s ds}\, b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \,dW_t\,,
+\dif \left( X_t e^{\int_{0}^{t} \theta_s \dif s} \right) = e^{\int_{0}^{t} \theta_s \dif s} (\dot{p}_t + \theta_t p_t ) \dif t  + e^{\int_{0}^{t} \theta_s \dif s}b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \dif W_t,
 \end{equation*}
@@
 \begin{equation}
-e^{\int_{0}^{t} \theta_s ds}  X_t - X_0 = \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u du} ds + \int_{0}^{t}  b (X_s; p_s, \dot{p}_s, \bm{\theta} )  e^{\int_{0}^{s} \theta_u du}\, d W_s\,.
+e^{\int_{0}^{t} \theta_s \dif s}  X_t - X_0 = \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u \dif u} \dif s + \int_{0}^{t}  b (X_s; p_s, \dot{p}_s, \bm{\theta} )  e^{\int_{0}^{s} \theta_u \dif u}\dif  W_s.
 \label{eq:tomeanX}
@@
 \begin{align}
-\mathbb{E} X_t & = e^{ - \int_{0}^{t} \theta_s ds} \left(  \mathbb{E} X_0 +   \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u du} ds   \right) \nonumber \\ 
-& =  e^{ - \int_{0}^{t} \theta_s ds} \left(  \mathbb{E} X_0 +   \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u du} ds +  \big[ p_s \, e^{\int_{0}^{s} \theta_u du} \big]^{t}_0  - \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u du} ds  \right) \nonumber \\
-& =  e^{ - \int_{0}^{t} \theta_s ds} \left(  \mathbb{E} X_0 + p_t \, e^{ \int_{0}^{t} \theta_s ds} - p_0 \right) = p_t \,. \label{eq:meanX}
+\mathbb{E} \left[X_t\right] & = e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E} \left[X_0\right] +   \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u \dif u} \dif s   \right) \nonumber \\
+& =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E} \left[X_0\right] +   \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u \dif u} \dif s +  \big[ p_s \, e^{\int_{0}^{s} \theta_u \dif u} \big]^{t}_0  - \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u \dif u} \dif s  \right) \nonumber \\
+& =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E}\left[ X_0\right] + p_t \, e^{ \int_{0}^{t} \theta_s \dif s} - p_0 \right) = p_t. \label{eq:meanX}
 \end{align}
@@
 For instance, consider the diffusion model (\ref{eq:main}) with $a(X_t; p_t, \bm{\theta}) = - \theta_0 (X_t - p_t)\,, \theta_0 > 0$.
-In this case, given  $ \mathbb{E} X_0 = p_0$, the diffusion has mean $\mathbb{E} X_t = p_t - e^{- \theta_0 t } \int_0^t \dot{p}_s  e^{\theta_0 s} ds$.
+In this case, given  $ \mathbb{E} \left[X_0\right] = p_0$, the diffusion has mean $\mathbb{E} \left[X_t\right] = p_t - e^{- \theta_0 t } \int_0^t \dot{p}_s  e^{\theta_0 s} \dif s$.
 The next Figure (\ref{fig:derivative_tracking}) illustrates how different behave the estimated confidence bands for two diffusion models with and without derivative tracking, fitting the same daily segment.
 
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
  \begin{equation}
-    dX_t = - \theta (X_t - \mu) dt + \sqrt{2 \theta (a X_t^2 + b X_t + c)} dW_t
+    \dif X_t = - \theta (X_t - \mu)\dif t + \sqrt{2 \theta \left(a X_t^2 + b X_t + c\right)} \dif W_t
   \end{equation}
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= (\dot{p}_t  - \theta_t (X_t - p_t) ) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{ourmodel}
-\end{equation}
-
-is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X$ to (\ref{ourmodel}) a non-stationary and time-inhomogeneous process.
-To ensure that the process $X$ be the unique strong solution to (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the following condition:
-
-\begin{equation}\label{Assumption:3}
+\begin{cases}
+    \dif X_t&= \left(\dot{p}_t  - \theta_t (X_t - p_t) \right) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]  \\
+   X_0 &=  x_0\in [0,1] \,,
+\end{cases}
+\label{ourmodel}
+\end{equation}
+
+is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X$ of (\ref{ourmodel}) to a non-stationary and time-inhomogeneous process.
+To ensure that the process $X$ is the unique strong solution of (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the condition:
+
+\begin{equation}
 \theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{B}. 
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dV_t \!\!\!&=  - \theta_t V_t  \, dt + \sqrt{2 \alpha \theta_0 (V_t +p_t ) (1-V_t-p_t)} \, dW_t\,, \quad t \in [0,T]  \\
-   V_0  \!\!\!&=  v_0\in [-1 + \epsilon,1 - \epsilon] \,.
- \end{array}\right.  \label{VtSDE}
+\begin{cases}
+\dif V_t&=  - \theta_t V_t\dif t + \sqrt{2 \alpha \theta_0 (V_t +p_t ) (1-V_t-p_t)}\dif W_t, \quad t \in [0,T]  \\
+V_0&=  v_0\in [-1 + p_0,1 - p_0].
+\end{cases}  \label{VtSDE}
 \end{equation}
@@
 %---BEGIN SECTION 4---
+
 \section{State independent diffusion term: Lamperti transform} \label{Section_4}
@@
 \begin{align}
-Z_t = h(V_t, t; \bm{\theta} )  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \,dv \Bigg{\vert}_{v = V_t}   = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
+Z_t = h(V_t, t; \bm{\theta} )  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \dif v \Bigg{\vert}_{v = V_t}   = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
 \end{align}
@@
 \begin{align}
-dZ_t = \Bigg[  & \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  + \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \,dt + dW_t \,.
+\dif Z_t = \Bigg[  & \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  + \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \dif t + \dif W_t \,.
 \label{eq:stindepSDE}
@@
 \begin{align}
-dZ_t & = \Bigg[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)}   - \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \Bigg] \,dt + dW_t \nonumber \\
-&  = \left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \,dt + dW_t \,.
+\dif Z_t & = \left[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)}   - \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \right]\dif t + \dif W_t \nonumber \\
+&  = \left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \dif t + \dif W_t.
 \label{eq:stindepSDE2}
@@
 %---BEGIN SECTION 5---
+
 \section{ Likelihood functions of the forecast errors data and optimization algorithm} \label{Section_5}
@@
 
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$, and let $ V^{M,N + 1}=\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \}$ denote this random sample, with $V_{t_j^{N + 1}} = \{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \}, \, j = 1, \ldots, M$.
-
-Let $\rho(v \vert v_{j, i-1} ; \bm{\theta})$ be the conditional probability density of $V_{t_j + i \Delta} \equiv V_{j, i}$ given $V_{j, i-1} = v_{j, i-1}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha, \epsilon)$ are the unknown model parameters.
+Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$, and let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}, \, j = 1, \ldots, M$.
+
+Let $\rho(v \vert v_{j, i-1} ; \bm{\theta})$ be the conditional probability density of $V_{t_j + i \Delta} \equiv V_{j, i}$ given $V_{j, i-1} = v_{j, i-1}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha)$ are the unknown model parameters.
 
@@
 \begin{equation}
-\mathcal{L}(\bm{\theta}; V^{M,N +1}) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho ( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} )  \,  \right\} \,,
+\mathcal{L}(\bm{\theta}; V^{M,N +1}) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho ( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} )  \,  \right\},
 \label{likelihood}
@@
 
-\subsection{Approximate likelihood  in the $V-$space}
+\subsection{Approximate likelihood  in the $V-$space} \label{moments_ODEs}
 
@@
 
-From (\ref{eq:meanX}), we have $m_1(t) \equiv \mathbb{E} V_t = e^{- \int_{t_{j,i-1}}^t \theta_s ds} \,\mathbb{E} V_{t_{j,i-1}}$, for any $t\in [t_{j,i-1}, t_{j, i})$, $j = 1, \ldots, M$ and $i = 1, \ldots, N$ .
+From (\ref{eq:meanX}), we have $m_1(t) \equiv \mathbb{E} \left[V_t\right] = e^{- \int_{t_{j,i-1}}^t \theta_s \dif s} \,\mathbb{E} \left[V_{t_{j,i-1}}\right]$, for any $t\in [t_{j,i-1}, t_{j, i})$, $j = 1, \ldots, M$ and $i = 1, \ldots, N$ .
 
@@
 \begin{align}
-d(V_t^m) & = \left( - m \theta_t V_t^m + \frac{1}{2} m (m -1) V_t^{m -2} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \right) dt  \nonumber \\
-& + m V_t^{m-1} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) dW_t \,, \nonumber
+\dif (V_t^m) & = \left( - m \theta_t V_t^m + \frac{1}{2} m (m -1) V_t^{m -2} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \right) \dif t  \nonumber \\
+& + m V_t^{m-1} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \dif W_t \,, \nonumber
 \end{align}
@@
 \begin{equation}
-\frac{d \mathbb{E}[ V^m_t]}{dt} = - m \theta_t \mathbb{E}[ V^m_t] + m (m-1) \alpha \theta_0  \mathbb{E}[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} ] \,.
+\frac{\dif  \mathbb{E}[ V^m_t]}{\dif t} = - m \theta_t \mathbb{E}[ V^m_t] + m (m-1) \alpha \theta_0  \mathbb{E}[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} ] \,.
 \end{equation}
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    \frac{d m_1 (t)}{dt} \!\!\!&=  - m_1(t)\theta_t   \\
-   \frac{d m_2 (t)}{dt}  \!\!\!&=  -2 (\theta_t +\alpha \theta_0) m_2(t) + 2 \alpha\theta_0 (1-2p_t)  m_1(t) + 2 \alpha\theta_0 p_t (1-p_t) 
- \end{array}\right.  \label{Vtmom}
+\begin{cases}
+\frac{\dif  m_1 (t)}{\dif t} &=  - m_1(t)\theta_t   \\
+\frac{\dif  m_2 (t)}{\dif t} &=  -2 (\theta_t +\alpha \theta_0) m_2(t) + 2 \alpha\theta_0 (1-2p_t)  m_1(t) + 2 \alpha\theta_0 p_t (1-p_t) 
+\end{cases}
+\label{Vtmom}
 \end{equation}
@@
 
-\subsubsection*{ Moment Matching}
+\subsubsection{Moment Matching}
 A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape real parameters, $\xi_1, \xi_2$.
@@
 \begin{equation}
- \tilde{\ell} (\bm{\theta}; v^{M,N +1}) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1, \xi_2)} \Big( \frac{z_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \Big)^{\xi_1 -1}  \Big( \frac{1 - \epsilon - z_{j,i}}{2(1 - \epsilon)} \Big)^{\xi_2 -1} \right\} \,,
-\label{loglikelihoodV}
+ \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1, \xi_2)} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1 -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2 -1} \right\},
+\label{eq:loglikelihoodV}
 \end{equation}
 where the shape parameters $\xi_1$ and $\xi_2$, according to (\ref{param_transformed_beta}), depend on the quantities $\mu(t_{j,i};\bm{\theta} )$ and $\sigma^2(t_{j,i};\bm{\theta} )$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
-\\
 
@@
 The drift coefficient $a(Z_t; p_t, \dot{p}_t, \bm{\theta}) $ of the process $Z$ that satisfies (\ref{eq:stindepSDE2}) is nonlinear.
-After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}Z_t$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i})$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}Z_t$ and $\tilde{v}_Z(t) \approx \text{Var} Z_t$ :\\
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    \frac{d \tilde{\mu}_Z (t)}{dt} \!\!\!&=  a\big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big)   \\
-    \frac{d \tilde{v}_Z (t)}{dt}  \!\!\!&= 2  a^{\prime} \big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big) \tilde{v}_Z (t) + 1
- \end{array}\right.  \label{Ztmom}
+After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i})$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} Z_t$ :\\
+\begin{equation}
+\begin{cases}
+\frac{\dif  \tilde{\mu}_Z (t)}{\dif t}&=  a\big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big)   \\
+\frac{\dif  \tilde{v}_Z (t)}{\dif t}&= 2  a^{\prime} \big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big) \tilde{v}_Z (t) + 1
+\end{cases}
+\label{Ztmom}
 \end{equation}
@@
 \begin{equation*}
-a^{\prime} \big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big) =    \frac{  (\alpha \theta_0 - \theta_t)  - \cos(\sqrt{2 \alpha \theta_0 } Z_t) [ \theta_t (1 - 2 p_t) - 2  \dot{p}_t ] }{\sin^2{(\sqrt{2 \alpha \theta_0} Z_t)}} \,.
+a^{\prime} \left( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \right) =    \frac{  (\alpha \theta_0 - \theta_t)  - \cos(\sqrt{2 \alpha \theta_0 } Z_t) [ \theta_t (1 - 2 p_t) - 2  \dot{p}_t ] }{\sin^2{(\sqrt{2 \alpha \theta_0} Z_t)}}.
 \end{equation*}
-
-The approximate log-likelihood $\tilde{\ell}(\cdot ; z^{V, N+1})$ of the observed sample $z^{V, N+1}$ is given by
-\begin{equation}
-\tilde{\ell} (\bm{\theta}; z^{M,N +1}) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i};\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}; \bm{\theta})} \Bigg) \right\}   \,,   \label{loglikelihoodZ}
+The approximate Lamperti log-likelihood $\tilde{\ell}_L\left(\cdot ; z^{V, N+1}\right)$ for the observed sample $z^{V, N+1}$ is given by
+\begin{equation}
+\tilde{\ell}_L \left(\bm{\theta}; z^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i};\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}; \bm{\theta})} \Bigg) \right\},
+\label{loglikelihoodZ}
 \end{equation}
@@
 To guarantee the good behave for our optimization algorithm, we aim to start the optimization as close as we can from the optimal parameters.
-We use \textbf{Least Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess, and to tune the hyper-parameter $\epsilon\in(0,\frac{1}{2})$.
+We use \textbf{Least Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess.
 
@@
 
-\item \textbf{Least Square Minimization:} We consider a set of transitions $\{\Delta V_i\}_{i}$ with $\Delta V_i=V_{i+1}-V_i$ and $\Delta t=t_{i+1}-t_i$.
-$(V_{i+1}|V_i)$ is a random variable which conditional mean can be approximated by the solution of the system
+\item \textbf{Least Square Minimization:} We consider the observed data $v^{M,N+1}$ with $\Delta v_{j,i}=v_{j,i+1}-v_{j,i}$ and length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
+$(V_{j,i+1}|v_{j,i})$ is a random variable which conditional mean can be approximated by the solution of the system
 \begin{equation*}
 \begin{cases}
-\dif \E\left[V\right]&=-\theta_t\E\left[V\right]\dif t\\
-\E\left[V(t_i)\right]&=V_i,
+\dif \E\left[V\right]_{j,i}&=-\theta_t\E\left[V\right]_{j,i}\dif t\\
+\E\left[V\right]_{j,i}(t_{j,i})&=v_{j,i},
 \end{cases}
 \end{equation*}
-evaluated in $t_{i+1}$ (i.e., $\E\left[V(t_{i+1})\right]$).
-Then, the random variable $(V_{i+1}-\E\left[V(t_{i+1})\right])$ has approximately zero mean.
-If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_i,t_{i+1}]$, then $\E\left[V(t_{i+1})\right]=V_ie^{-c\Delta t}$.
-If we have a total of $n$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
-\begin{equation}
-c^*\approx\arg\min_{c\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-\E\left[V(t_{i+1})\right]\right)^2\right]=\arg\min_{c\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-V_ie^{-c\Delta t}\right)^2\right].
+evaluated in $t_{j,i+1}$, i.e., $\E\left[V\right]_{j,i}(t_{j,i+1})$.
+Then, the random variable $(V_{j,i+1}-\E\left[V\right]_{j,i}(t_{j,i+1}))$ has zero mean.
+If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i},t_{j,i+1}]$, then $\E\left[V(t_{j,i+1})\right]_{j,i}=v_{j,i}e^{-c\Delta}$.
+If we have a total of $M\times N$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
+\begin{equation}
+\begin{split}
+c^*&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-\E\left[v\right]_{j,i}(t_{j,i+1})\right)^2\right]\\
+&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}e^{-c\Delta}\right)^2\right]\\
+&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right)^2\right].
+\end{split}
 \label{Eq-1}
@@
 \begin{equation*}
-\begin{split}
-\frac{\partial f}{\partial c}&=\sum_{i=1}^n2(-V_i)(-\Delta t)(V_{i+1}-V_i(1-\theta_0\Delta t))
-=\sum_{i=1}^n2V_i\Delta t(V_{i+1}-V_i(1-c\Delta t))\\
-&=\sum_{i=1}^n2V_{i+1}V_i\Delta t-2V_i^2\Delta t+2V_i^2\Delta t^2c.
-\end{split}
+\frac{\partial}{\partial c}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right)^2\right]=\sum_{j=1}^M\sum_{i=0}^{N-1}2v_{j,i}\Delta\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right),
 \end{equation*}
-it follows that $c^{**}$ satisfies
-\begin{equation}
-c^{**}\approx\frac{\sum_{i=1}^nV_i(V_i-V_{i+1})}{\Delta t\cdot\sum_{i=1}^n(V_i)^2}\quad\text{and}\quad c^*=\max\{c^{**},0\}.
+follows that
+\begin{equation}
+c^{*}=\frac{\sum_{j=1}^M\sum_{i=0}^{N-1}v_{j,i}(v_{j,i}-v_{j,i+1})}{\Delta\cdot\sum_{j=1}^M\sum_{i=0}^{N-1}(v_{j,i})^2}.
 \label{Eq-4}
 \end{equation}
-Notice that $c^{**}$ has dimension $\mathbf{time}^{-1}$.
 
@@
 
-Then, considering $\Delta t$ the time between measurements, we approximate:
-\begin{equation}
-\theta_0^*\alpha^*\approx\frac{\sum_{i=1}^n(\Delta V_i)^2}{2\Delta t\sum_{i=1}^n(V_i+p_i)(1-V_i-p_i)}.
+Then, considering $\Delta$ the time between measurements, we approximate:
+\begin{equation}
+\theta_0^*\alpha^*\approx\frac{\sum_{j=1}^M\sum_{i=1}^N(\Delta v_{j,i})^2}{2\Delta\cdot\sum_{j=1}^M\sum_{i=1}^N(v_{j,i}+p_{j,i})(1-v_{j,i}-p_{j,i})}.
 \label{Eq-2}
@@
 
-In Subsection (\ref{Physical_Constraints}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$.
+%In Subsection (\ref{Physical_Constraints}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$.
 Even when it would be reasonable to choose an arbitrary small $\epsilon>0$, we aim to approximate it using the LSM estimator.\\
-
-Fixed $\epsilon$, we call $\mathcal{V}=\{\Delta V_i^\epsilon\}_{i=1}^n$ to the set of $n$ error transitions where for each measurement $X_i$, we have that $V_i=X_i-p_i^\epsilon$.
+%
+%Fixed $\epsilon$, we call $\mathcal{V}=\{\Delta V_i^\epsilon\}_{i=1}^n$ to the set of $n$ error transitions where for each measurement $X_i$, we have that $V_i=X_i-p_i^\epsilon$.
 $\mathcal{P}=\{p_i^\epsilon\}_{i=1}^n$ is the corresponding set of forecasts.\\
-If we also fix $\theta_0$ and $\alpha$, we can define the set of indexes $\mathbf{I}=\{i\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\theta_0\}$ and $\mathbf{J}=\left\{j\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\frac{\theta_0\alpha}{\epsilon}\right\}$.
+%If we also fix $\theta_0$ and $\alpha$, we can define the set of indexes $\mathbf{I}=\{i\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\theta_0\}$ and $\mathbf{J}=\left\{j\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\frac{\theta_0\alpha}{\epsilon}\right\}$.
 From the definition of $\theta_t$, we have that for $\epsilon<<1$, and $p_t=\epsilon$ or $p_t=1-\epsilon$, the approximation $\theta_t\approx\frac{\theta_0\alpha}{\epsilon}$ holds.
 Then, for $\epsilon$ small enough, $\mathbf{J}$ can be approximated by $$\mathbf{J}\approx\tilde{\mathbf{J}}=\{j\in\{1,\dots,n\}:p_j^\epsilon\in\{\epsilon,1-\epsilon\}\}.$$
-Now, coming back to the definition of $\theta_t$, we have that it is more likely that $\theta_t=\theta_0$ if $p_t^\epsilon\approx\frac{1}{2}$.
+%Now, coming back to the definition of $\theta_t$, we have that it is more likely that $\theta_t=\theta_0$ if $p_t^\epsilon\approx\frac{1}{2}$.
 Then, we can approximate $\mathbf{I}$ by $$\mathbf{I}\approx\tilde{\mathbf{I}}=\left\{i\in\{1,\dots,n\}:p_i\in(\gamma,1-\gamma)\right\},\ \gamma\approx\frac{1}{2},\ \gamma<\frac{1}{2}.$$
-We do not see signification differences in the LSM estimator for all $\gamma\in(0.1,0.3)$.
+%We do not see signification differences in the LSM estimator for all $\gamma\in(0.1,0.3)$.
 If $\gamma>0.3$, the reduction in the number of samples makes variations in the LSM estimator.
@@
 
-To find the optimal parameters, we minimize the negative log-likelihood using the derivative-free function \textit{fminsearch} from MATLAB R2019b over the parameters $(\theta_0,\alpha)$.
+To find the optimal parameters, we minimize the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) using the derivative-free function \textit{fminsearch} from MATLAB R2019b over the parameters $(\theta_0,\alpha)$.
 At each step of the iteration, we:
@@
 
-\item Use the training dataset to find the SDE first and second moments.
-\item Match the proxy distribution moments with the SDE moments.
+\item Use the training dataset to find the SDE's first and second moments as explained in subsection \ref{moments_ODEs}.
+\item Match the proxy distribution moments with the SDE's moments.
 \item Evaluate the negative log-likelihood using the training dataset.
@@
 
-Let $\{\Delta V_i\}_{i=1}^n$ be the set of all error transitions, and $\psi(\theta_0,\alpha,\Delta V)$ the Lamperti transform.
-Notice that the Lamperti transitions $\{\Delta Z_i\}_{i=1}^n$ depend on $(\theta_0,\alpha)$ because $$\{\Delta Z_i\}_{i=1}^n=\psi(\theta_0,\alpha,\{\Delta V_i\}_{i=1}^n).$$
-Then, if we compute $$\max_{(\theta_0,\alpha)}\mathbf{L}(\theta_0,\alpha,\{\Delta Z_i\}_{i=1}^n),$$
-we are not computing a MLE in the classical sense, as the data is changing with the parameters. However, we can try to find a fixed point ${\color{blue}(\theta_0^*,\alpha^*)}$ such that
-\begin{equation}
-{\color{blue}(\theta_0^*,\alpha^*)}=\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{blue}\theta_0^*},{\color{blue}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
+Let $\{\Delta v_{j,i}\}_{j=1,i=1}^{M,N}$ be the set of error observation transitions, and $\psi(\Delta v_{j,i};\bm{\theta})$ the Lamperti transform for the transitions.
+The transformed observations transitions $\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}$ depend on the parameter $\bm{\theta}$.\\
+The problem of maximizing the  $$\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}\right),$$
+is not totally defined as the data $\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}$ depend on $\bm{\theta}$. However, we propose to find a fixed point $\bm{\theta}^*$ such that
+\begin{equation}
+\bm{\theta}^*=\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right).
 \label{FP}
 \end{equation}
-In this point, the likelihood has a maximum for the data set corresponding to that point.
-
-We are interested in finding the solution of (\ref{FP}). We have that, if $(\theta_0^*,\alpha^*)$ is a solution of (\ref{FP}), then
+{\color{red}In this point, the likelihood has a maximum for the data set corresponding to that point. (HOW CAN WE WRITE THIS BETTER?)}
+We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
 \begin{equation*}
-(\theta_0^*,\alpha^*)-\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right)=0.
+\bm{\theta}^*-\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right)=0.
 \end{equation*}
-Given a pair $(\theta_0^{*},\alpha^{*})$, we call $(\theta_0^{**},\alpha^{**})$ to the solution of
+Given $\bm{\theta}^*=(\theta_0^*,\alpha^*)$, we call $\bm{\theta}^{**}=(\theta_0^{**},\alpha^{**})$ to the solution of
 \begin{equation*}
-\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
+\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right).
 \end{equation*}
-For each $(\theta_0^{*},\alpha^{*})$, we define the relative error function
-\begin{equation*}
-\Psi(\theta_0^{*},\alpha^{*})=\frac{|\theta_0^{*}-\theta_0^{**}|}{|\theta_0^{*}|}+\frac{|\alpha^{*}-\alpha^{**}|}{|\alpha^{*}|}
-\end{equation*}
-and claim that $(\theta_0^*,\alpha^*)$ is a fixed point iff $\Psi(\theta_0^*,\alpha^*)=0$.
+For each $\bm{\theta}^*$, we define the relative error function
+\begin{equation}
+\Psi(\bm{\theta}^*)=\frac{|\theta_0^{*}-\theta_0^{**}|}{|\theta_0^{*}|}+\frac{|\alpha^{*}-\alpha^{**}|}{|\alpha^{*}|},
+\label{eq:rel_error}
+\end{equation}
+and remark that $\bm{\theta}^*$ is a fixed point if and only if $\Psi(\bm{\theta}^*)=0$.
 
@@
 
-{\color{red}[I am not sure if we should introduce this parameter here, of in some previous section].} We observe that for each day, the error at time $t=0$ is not zero.
-However, by construction of the forecast, we may assume that for some time in the past $t_\delta<0$, the error $V_{t_\delta}=0$.\\
+We observe that for most days, the error at time $t_{j,0}=0$ is not zero. By forecasts construction, we assume that for some time in the past $t_{j,\delta}<t_{j,0}$, the error $V_{j,\delta}=0$.\\
 \quad\\
-We extrapolate linearly $p(t)$ considering the truncation at $\epsilon$, so we can evaluate $p(t_{-\delta})$, and assume that $V(t_{-\delta})=0$.
-Then, for each day $j$, we have an initial transition $(V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta)$.
+We extrapolate linearly $p_t$ considering the truncation at $\epsilon$, so we have a value for $p_{j,\delta}$, and set $v(t_{j,\delta})=0$.
+Then, for each $j$, we have an initial transition $(V_{j, 0}|v_{j,\delta};\bm{\theta},\delta)$.
 We assume again that it is Beta and apply the same moment matching as for the rest of transitions.
@@
 
-\begin{equation*}
-\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
-\label{likelihood_delta}
-\end{equation*}
-To solve this minimization problem, we repeat the steps described in section (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation.
+\begin{equation}
+\delta\approx\arg\max_{\delta}\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,\delta};\bm{\theta},\delta\right),
+\label{eq:likelihood_delta}
+\end{equation}
+where $\mathcal{L}_\delta$ is the $\delta-$likelihood.
+To solve this problem, we repeat the steps described in section (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation for $p_{j,\delta}$.\\
+\quad\\
+We can extend the likelihood (\ref{likelihood}) to include this extra parameter. The complete likelihood, $\mathcal{L}_c$, is given by
+\begin{equation}
+\mathcal{L}_c\left(\bm{\theta},\delta; v^{M,N +1}\right)=\mathcal{L}\left(\bm{\theta}; v^{M,N +1}\right)\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right).
+\label{eq:complete_LH}
+\end{equation}
+As we can construct initial guesses for $\bm{\theta}$ and $\delta$, we have a staring point for the maximization of (\ref{eq:complete_LH}).
 
@@
 %---BEGIN SECTION 6---
+
 \section{Application to the April-December 2019 Uruguay wind and forecast dataset} \label{Section_6}
@@
 { \color{red} Show that 24h is enough to ensure independence?}
-
-Following the instruction for the initial guesses from section $\ref{opt_sec}$, we get the initial guesses $(\theta_0,\alpha,\delta)\approx(1.2,0.1,0.6)$.
+All the following results involving a single provider refer to Provider A.
+Following the instruction for the initial guesses from section $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.
 
@@
 
-We plot the Negative Log-Likelihood as a function of the parameters.
-The plots can be seen in Figure (\ref{fig:neg-LL}).
-We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.jpg}
-\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
+As an auxiliary verification, we plot the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) as a function of the parameters, and we use extra minimization functions from MATLAB R2019b.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.eps}
+\caption{Negative log-likelihood's level sets. All optimal values are located over the curve $\theta_0\alpha=0.097$.}
 \label{fig:neg-LL}
 \end{figure}
-On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood. The thick violet band is the region where the function reaches its minimums.\\
-We can see the \textbf{initial guess} point, the result of three different \textbf{optimization tools} from MATLAB, and the minimum point that we found from the \textbf{evaluations} that generate the plot.
-\begin{table}[]
+On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood.
+The numerical values of each important point can be seen in Table (\ref{tab:optimal_values}).
+We set $(\theta_0^E,\alpha^E)=(1.93,0.050)$, as it is where the negative log-likelihood reaches its minimum value.
+\begin{table}[H]
 \centering
@@
  \midrule
- Initial guess & 1.629 & 0.060 & 0.098 \\
- fminsearch & 1.135 & 0.073 & 0.083 \\
- fmincon & 1.366 & 0.061 & 0.083 \\
- fminunc & 1.628 & 0.051 & 0.083 \\
- evaluations & 1.180 & 0.070 & 0.083 \\
+ Initial guess & 1.54 & 0.070 & 0.111 \\
+ fminsearch & 1.14 & 0.076 & 0.097 \\
+ fmincon & 1.58 & 0.062 & 0.097 \\
+ fminunc & 1.54 & 0.063 & 0.097 \\
+ evaluations & 1.93 & 0.050 & 0.097 \\
  \bottomrule
 \end{tabular}
+\caption{Value points from Figure \ref{fig:neg-LL}.}
+\label{tab:optimal_values}
 \end{table}
+Observe that all the local (possibly global) minimizers are located in curve $\theta_0,\alpha=0.097$.
+We will explain this effect later, but it is a consequence of Markovianity and the indistinguishable observed transitions.
 
@@
 
-We plot the Negative Log-Likelihood as a function of the parameters.
-The plots can be seen in Figure (\ref{fig:neg-LL}).
-We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
-\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
+As we are working in a low dimensional space, we can evaluate the relative error function (\ref{eq:rel_error}) in all the space of interest.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
+\caption{Relative error function's level sets.}
 \label{fig:neg-LLL}
 \end{figure}
-In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets of the error function $\Psi$.\\
-The center deep green band is the set $\mathbb{A}$ such that $\Psi(\mathbb{A})\in[0.05,0.1]$. We do not achieve relative error smaller than 0.05.\\
-We observe a particular behavior over the curves $\theta_0\alpha=k\in\R^+$. However, it can be a numeric effect.\\
-We also observe that: $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.083\}\neq\emptyset.$$
-On the right, we observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.038$ from the error SDE.\\
-We choose $(\theta_0,\alpha)=(2.200,0.038)$.\\
-We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".
+In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets for the relative error function (\ref{eq:rel_error}).
+The center deep green band is the set $\mathbb{A}$ such that $\Psi(\bm{\theta})<0.1$ if $\bm{\theta}\in\mathbb{A}$, it is the set of fixes-points candidates.
+The set of fixed-points candidates which also satisfies the condition of lying over the line $\theta_0\alpha=0.097$ is non-empty, i.e., $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.097\}\neq\emptyset.$$
+We observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.097$ from the error SDE. We choose $(\theta_0^L,\alpha^L)=(2.45,0.040)$.\\
+{\color{red}We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".}\\
+\quad\\
+To verify and compare this two vector of parameters, (i.e., $(\theta_0^E,\alpha^E)$ and $(\theta_0^L,\alpha^L)$), we simulate error paths in the $V-$space.
+We simulate five error paths for each day in the test set and construct histograms with the transitions.
+The histoframs can be seen in Figure (\ref{fig:hists}).
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic_noDelta/Optimal.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic_noDelta/Lamperti_Optimal.eps}
+\caption{Probability histograms for the error transitions.
+Using the Provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE.
+On the left, simulations using $(\theta_0^E,\alpha^E)$.
+On the right, simulations using $(\theta_0^L,\alpha^L)$.}
+\label{fig:hists}
+\end{figure}
 
@@
 
-We compare two candidate models to find the best-fit that maximizes the retained information,
+We compare two candidate models to find the best-fit that maximizes the retained information:
 \begin{itemize}
-  \item Model 1: This model does not feature derivative tracking.
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&=  - \theta_0 (X_t - p_t) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{Model1}
+  \item Model 1: This model does not feature derivative tracking:
+\begin{equation}
+\begin{cases}
+\dif X_t&=-\theta_0 (X_t - p_t) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]  \\
+X_0&=x_0\in (0,1),
+\end{cases}.  \label{Model1}
 \end{equation}
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= \big(\dot{p}_t  - \theta_t (X_t - p_t) \big) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{Model2}
+\begin{cases}
+\dif X_t&= \big(\dot{p}_t  - \theta_t (X_t - p_t) \big) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]\\
+X_0&=x_0\in (0,1) \,,
+\end{cases}.  \label{Model2}
 \end{equation}
@@
 \end{itemize}
+To show the better performance of Model 2, we calculate the Akaike information criterion (AIC) and Bayesian information criterion (BIC) for each provider, each model, and different proxies densities.
+Table (\ref{tab:model_comparison}) summarizes this computations.
+We can observe that the best fitting is achieved with Model 2 and Beta proxies.
 
@@
 \end{tabular}
-\caption{We compare the different models based on information criterion. \add }
+\caption{We compare the different models based on information criterion.}
 \label{tab:model_comparison}
@@
 \subsection{Forecast providers comparison} \label{Forecast_Comp}
-We compare forecasts from two different companies for the same period.
+We compare forecasts from three different companies for the same period.
 \begin{table}[H]
@@
 
-\subsection{Calibration of Model 2 with additional parameter $\delta$ TO DO}
-
-After calibrating Model 2 on the training set, we can generate simulations of the wind power production for the time horizon of interest.
-The next Figure \ref{fig:simulation_paths} shows five simulated paths of the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
+\subsection{Calibration of Model 2 with additional parameter $\delta$}
+
+After calibrating Model 2 on the training set using the complete likelihood (\ref{eq:complete_LH}), we can generate simulations of the wind power production for the time horizon of interest.
+Figure \ref{fig:simulation_paths} shows five simulated paths of the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
 
@@
 \includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
-\caption{Five simulated wind power production paths using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. }
+\caption{Five simulated wind power production paths using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.93,0.050,0.090)$. }
 \label{fig:simulation_paths}
@@
 \includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/4.eps}
-\caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Blue line: real production.}
+\caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.93,0.050,0.090)$. Blue line: real production.}
 \label{fig:confidence_bands}
@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic/Lamperti_Optimal.eps}
-\end{figure}
-
-We can see two histograms for the error transitions. On the left, using $(\theta_0^E,\alpha^E)$, while on the right, using $(\theta_0^L,\alpha^L)$.
+\subsubsection{Value of $\delta$}
+As a final verification, we study the behavior of $\delta$ as function of $\bm{\theta}$.
+Given a vector of parameters, we calculate an initial guess for $\delta$ solving problem (\ref{eq:likelihood_delta}).
+Even when it is a guess, it helps us to understand qualitatively the meaning of this additional parameter.\\
+\quad\\
+We choose as domain the most significant values of $\theta_0$ and $\theta_0\alpha$, regarding the previous numerical results. In Figure (\ref{fig:delta}) we can observe that:
+\begin{itemize}
+\item The initial time $\delta$ decreases as $\theta_0\alpha$ increases.
+This is a consequence of the increment in the diffusion as $\theta_0\alpha$ increases.
+As there is more diffusion, it is needed less time for the initial transition density to cover the initial error observations.
+\item The initial time $\delta$ increases as $\theta_0$ increases.
+As we increment $\theta_0$, also the mean reversion becomes larger and reduces the variance for the initial transition density.
+Then, it is needed more time for the initial transition density to cover the initial error observations.
+\end{itemize}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/delta/contour_delta.png}
+\caption{Initial value for $\delta$ as a function of the elements of the parameter vector $\bm{\theta}$.}
+\label{fig:delta}
+\end{figure}
 
@@
 %---BEGIN SECTION 7---
+
 \section{Conclusions} \label{Section_7}
@@
 
-We were also able to compare two different forecast providers with respect to their real-world performance on the aggregated data set and on specific wind farm sites.
+We were also able to compare three different forecast providers with respect to their real-world performance on the aggregated data set and on specific wind farm sites.
 Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.
+
 %---END SECTION 7---
@@
 %---BEGIN APPENDIX---
+
 \section{Appendix} \label{Appendix}
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= \big(\dot p_t - \theta_t (X_t-p_t)  \big)dt  +\sqrt{2 \alpha \theta_0 X_t (1-X_t)} dW_t\,, \quad t\in[0,T] \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{eq:model}
+\begin{cases}
+\dif X_t &= \big(\dot p_t - \theta_t (X_t-p_t)  \big)\dif t  +\sqrt{2 \alpha \theta_0 X_t (1-X_t)} \dif W_t, \quad t\in(0,T) \\
+X_0&= x_0\in [0,1],
+\end{cases}.  \label{eq:model}
 \end{equation}
@@
 \begin{equation}\label{eq:eds1}
-X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)ds  + \int_0^t\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} dW_s, \quad x_0>0.
+X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)\dif s  + \int_0^t\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s, \quad 0<x_0<1.
 \end{equation}
@@
 \begin{align*}
-\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)ds \\
-&+ \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} dW_s + \alpha \theta_0 \int_0^t  g_n(|X_s|) |X_s(1-X_s)|ds.
+\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)\dif s \\
+&+ \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s + \alpha \theta_0 \int_0^t  g_n(|X_s|) |X_s(1-X_s)|\dif s.
 \end{align*}
@@
 $$
-\mathbb E[\psi_n(X_t)]\le \psi_n(x_0) +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \big)ds + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E |1-X_s|ds.
+\mathbb E[\psi_n(X_t)]\le \psi_n(x_0) +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \big)\dif s + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E |1-X_s|\dif s.
 $$
@@
 $$
-\mathbb E[|X_t|]\le x_0 +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E|X_s| \big)ds.
+\mathbb E[|X_t|]\le x_0 +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E|X_s| \big)\dif s.
 $$
@@
 $$
-\mathbb E X_t=x_0+  \int_0^t\big(\dot p_s +\theta_sp_s - \theta_s \mathbb EX_s  \big)ds
+\mathbb E X_t=x_0+  \int_0^t\big(\dot p_s +\theta_sp_s - \theta_s \mathbb EX_s  \big)\dif s
 $$
@@
 $$
-\mathbb E[|X_t| -X_t ]\le \int_0^t \theta_s \mathbb E[ X_s - |X_s| ]ds.
+\mathbb E[|X_t| -X_t ]\le \int_0^t \theta_s \mathbb E[ X_s - |X_s| ]\dif s.
 $$
@@
 $$
-dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \theta_tY_t(1-Y_t)} dW_t,
+\dif Y_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)\dif t  -\sqrt{2\alpha \theta_tY_t(1-Y_t)} \dif W_t,
 $$
@@
 $$
-\frac{dX_t}{X_t}= \left(\frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)dt  +\sqrt{\frac{2\alpha \theta_0 (1-X_t)}{X_t}} dW_t 
+\frac{\dif X_t}{X_t}= \left(\frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)\dif t  +\sqrt{\frac{2\alpha \theta_0 (1-X_t)}{X_t}} \dif W_t 
 $$  
@@
 $$
-X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \theta_0 \alpha}{X_s}ds+\alpha\theta_0 t-  \int_0^t\theta_sds + M_t\Big),
-$$
-where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_0 (1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \theta_0 \alpha\ge0$, we deduce that
-$$
-X_t\ge x_0\exp\Big(\alpha\theta_0 t-  \int_0^t\theta_sds + M_t\Big).
+X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \theta_0 \alpha}{X_s}\dif s+\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\Big),
+$$
+where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_0 (1-X_s)}{X_s}} \dif W_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \theta_0 \alpha\ge0$, we deduce that
+$$
+X_t\ge x_0\exp\Big(\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\Big).
 $$
@@
 $$
-dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \theta_0 Y_t(1-Y_t)} dW_t 
+\dif Y_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)\dif t  -\sqrt{2\alpha \theta_0 Y_t(1-Y_t)} \dif W_t 
 $$

### 2020-05-23 MATLAB_Files/histogram_classic_SDE.m

@@ -2,24 +2,25 @@ close all;
 clear all;
 clc;
 
-epsilon                = 0.018;
-Table_Testing_Complete = load_data_eps_test(epsilon);
-whatToDo               = 'Optimal'; 
+epsilon                = 0.020;
+dataKind               = 'comparable';
+dataSet                = 'MTLOG';
+Table_Testing_Complete = load_data_eps_test(epsilon,dataSet,dataKind);
+% whatToDo               = 'Optimal'; 
 whatToDo               = 'Lamperti_Optimal'; 
 % whatToDo               = 'Initial_Guess'; 
 
 % PARAMETERS:
 % set(0,'defaultAxesFontSize',18);
 save     = 0;
-delta    = 21; % The time is delta*10 minutes.
-numPaths = 1;
+delta    = 13; % The time is delta*10 minutes.
 
 if  strcmp(whatToDo,'Optimal')
-    theta_0 = 1.180;
-    alpha   = 0.070;
+    theta_0 = 1.930;
+    alpha   = 0.050;
 elseif  strcmp(whatToDo,'Lamperti_Optimal')
-    theta_0 = 2.200;
-    alpha   = 0.038;
+    theta_0 = 2.450;
+    alpha   = 0.097/2.450;
 elseif  strcmp(whatToDo,'Initial_Guess')
     theta_0 = 1.6290;
     alpha   = 0.06;
@@ -39,49 +40,69 @@ dt = dt/1;
 minus_t = linspace(-delta*dt,-dt,delta);
 exten_t = [minus_t,t];
 
-for i = 1 : height(Table_Testing_Complete)
+total_x_s_trans = [];
+total_v_s_trans = [];
 
-    X = x(i,:);
-    P = p(i,:);
-    % All of them show similar results:
-    P_exten_linear = interp1([0 6*dt],[P(1) P(6)],minus_t,'linear','extrap');
-    P_exten_pchip  = interp1([0 6*dt],[P(1) P(6)],minus_t,'pchip','extrap');
-    P_exten_spline = interp1([0 6*dt],[P(1) P(6)],minus_t,'spline','extrap');
-    P_exten_makima = interp1([0 6*dt],[P(1) P(6)],minus_t,'makima','extrap');
-    
-    P       = [P_exten_linear,P]; % We extend the forecast.
-    for j = 1:length(P)
-        P(j) = max(P(j),epsilon);
-        P(j) = min(P(j),1-epsilon);
-    end
[…]

### 2020-05-23 MATLAB_Files/histogram_lamperti_SDE.m

@@ -3,7 +3,9 @@ clear all;
 clc;
 
 epsilon                = 0.018;
-Table_Testing_Complete = load_data_eps_test(epsilon);
+dataKind               = 'comparable';
+dataSet                = 'MTLOG';
+Table_Testing_Complete = load_data_eps_test(epsilon,dataSet,dataKind);
 % whatToDo               = 'Optimal'; 
 whatToDo               = 'Optimal_Lamperti'; 
 
@@ -90,12 +92,13 @@ for i = 1 : height(Table_Testing_Complete)
         new_Transform(n-1) = (Z(n)-Z(n-1)) / sqrt(dt);
     end
     
-    new_Transform_trans(i,:) = Delta_new_Transform;
+    new_Transform_trans(i,:)   = Delta_new_Transform;
     new_Transform_allData(i,:) = new_Transform;
         
 end
 
-figure('Renderer', 'painters', 'Position', [10 10 1500 900]);
+% figure('Renderer', 'painters', 'Position', [10 10 1500 900]);
+figure;
 h1 = histogram(z_trans);
 hold on; grid minor;
 title('Lamperti (Data and Simulated) Transitions');
@@ -106,16 +109,19 @@ h2.FaceAlpha = 0;
 h2.FaceColor = [0 0 0];
 h2.LineWidth = 2;
 h2.EdgeColor = 'r';
+xlim([-0.5 0.5]);
 xlabel('Value of Transition');
 ylabel('Probability');
 % xlim([-0.4 0.4]);
 % xlim([-1 1]);
-set(gca,'FontSize',18);
+set(gca,'FontSize',12);
 legend('Lamperti Transitions Histogram','Simulated Lamperti Transitions Histogram');
 saveas(gcf,[pwd '/Results/histograms/lamperti/',whatToDo],'epsc');
 
-figure('Renderer', 'painters', 'Position', [10 10 1500 900]);
+% figure('Renderer', 'painters', 'Position', [10 10 1500 900]);
+figure;
 h3 = histogram(new_Transform_allData);
 h3.Normalization = 'pdf';
+set(gca,'FontSize',12);
 disp(['Mean of the second transformation: ',num2str(mean(new_Transform_trans(:)))]);
 disp(['Variance of the second transformation: ',num2str(var(new_Transform_trans(:)))]);

### 2020-05-23 MATLAB_Files/optimizeLogLikelihood.m

@@ -54,6 +54,7 @@ if strcmp(likelihood,'normal')
     % fminsearch -> Theta_0 = 1.278, Alpha = 0.0760, prod = 0.0971 (24/04/2020).
     % fmincon    -> Theta_0 = 1.577, Alpha = 0.0615, prod = 0.0970 (24/04/2020).
     % fminunc    -> Theta_0 = 1.544, Alpha = 0.0628, prod = 0.0970 (24/04/2020).
+    % eval       -> Theta_0 = 1.930, Alpha = 0.0500, prod = 0.0965 (20/05/2020).
     
 elseif strcmp(likelihood,'lamperti')
     

### 2020-05-24 LaTeX_Code/Paper/paper_1line.tex
Mote detaills in the paper

@@
 \end{equation}
-{\color{red}In this point, the likelihood has a maximum for the data set corresponding to that point. (HOW CAN WE WRITE THIS BETTER?)}
+{\color{red}In this point, the likelihood has a maximum for the data set corresponding to that point.}
 We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
@@
 All the following results involving a single provider refer to Provider A.
+Also, all calibrations involve the training sets and all simulations, the test sets.
 Following the instruction for the initial guesses from section $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.
@@
 
-As an auxiliary verification, we plot the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) as a function of the parameters, and we use extra minimization functions from MATLAB R2019b.
+As an auxiliary verification, we plot the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) as a function of the parameters, and we use additional minimization functions from MATLAB R2019b.
 
@@
 
-As we are working in a low dimensional space, we can evaluate the relative error function (\ref{eq:rel_error}) in all the space of interest.
+{\color{red} This part still may change.} As we are working in a low dimensional space, we can evaluate the relative error function (\ref{eq:rel_error}) in all the space of interest.
 
@@
 We simulate five error paths for each day in the test set and construct histograms with the transitions.
-The histoframs can be seen in Figure (\ref{fig:hists}).
+The histograms can be seen in Figure (\ref{fig:hists}).
+We do not observe any particular change in the behavior of the solution for there parameters.
 
@@
 After calibrating Model 2 on the training set using the complete likelihood (\ref{eq:complete_LH}), we can generate simulations of the wind power production for the time horizon of interest.
-Figure \ref{fig:simulation_paths} shows five simulated paths of the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
+Figure (\ref{fig:simulation_paths}) shows five simulated paths of the wind power production for each day of interest.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/1.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/2.eps}\\
 \quad\\
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
-\caption{Five simulated wind power production paths using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.93,0.050,0.090)$. }
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/3.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/4.eps}
+\caption{Four arbitrary days with five simulated wind power production paths each. }
 \label{fig:simulation_paths}
 \end{figure}
-
 On the basis of the approximate MLEs for Model 2, we can obtain empirical pointwise confidence bands for the wind power production.
-The next Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
+Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
 

### 2020-05-24 MATLAB_Files/path_simulator_OPT.m

@@ -14,7 +14,7 @@ whatToDo = 'optimal_value';
 
 % PARAMETERS:
 % set(0,'defaultAxesFontSize',18);
-quantil  = 1;
+quantil  = 0;
 save     = 1;
 delta    = 13; % The time is delta*10 minutes.
 xlimit   = 1; % If this in 1, the plots start at time 0. Otherwise, at -delta.
@@ -28,8 +28,10 @@ else
 end
 
 if  strcmp(whatToDo,'optimal_value')
-    theta_0 = 1.93;
-    alpha   = 0.05;
+%     theta_0 = 1.93;
+%     alpha   = 0.05;
+    theta_0 = 2.2210;
+    alpha   = 0.0436;
 elseif  strcmp(whatToDo,'Optimal_Lamperti')
     theta_0 = 2.200;
     alpha   = 0.038;

### 2020-05-24 MATLAB_Files/plotLamperti.m

@@ -37,9 +37,13 @@ val_alpha   = [];
 val_fval    = [];
 val_fval_2  = [];
 
-vec_theta_0 = 0.5:0.005:3;
-vec_alpha   = 0.01:0.001:0.1;
-num_divs    = 20;
+% vec_theta_0 = 0.5:0.005:3;
+% vec_alpha   = 0.01:0.001:0.1;
+% num_divs    = 20;
+% new_alpha   = 0.0965./vec_theta_0;
+
+vec_theta_0 = 0.5:0.05:10;
+vec_alpha   = 0.01:0.01:1;
 new_alpha   = 0.0965./vec_theta_0;
 
 for i = 1:length(vec_theta_0)
@@ -87,15 +91,20 @@ for i = 1:length(vec_theta_0)
     for j = 1:length(vec_alpha)
         rel_change_theta_0(i,j) = abs(vec_theta_0(i)-val_theta_0(i,j)) / abs(vec_theta_0(i));
         rel_change_alpha(i,j)   = abs(vec_alpha(j)-val_alpha(i,j)) / abs(vec_alpha(j));
+        
+        rel_change_prod(i,j) = abs(vec_theta_0(i)*vec_alpha(j)-val_theta_0(i,j)*val_alpha(i,j)) / ...
+            abs(vec_theta_0(i)*vec_alpha(j));
     end
 end
 
 total_change = rel_change_theta_0 + rel_change_alpha;
+total_change = rel_change_prod;
 
 figure('Renderer', 'painters', 'Position', [10 10 900 600])
 [X,Y] = meshgrid(vec_theta_0,vec_alpha);
 hold on;
-contourf(X,Y,total_change',[0:0.05:1]); colorbar;
+% contourf(X,Y,total_change',[0:0.05:1]); colorbar;
+contourf(X,Y,total_change'); colorbar;
 colormap summer;
 plot(vec_theta_0,new_alpha,'LineWidth',2,'Color','r');
 ylim([min(vec_alpha) max(vec_alpha)]);

### 2020-05-28 LaTeX_Code/Paper/paper_1line.tex
update section 4

@@
 Our model (\ref{VtSDE}) for the forecast error has a diffusion term that depends on the state variable $V_t$.
-To estimate the unknown model parameters, a recommended technique is to modify the SDE (\ref{VtSDE}) by applying the so-called Lamperti transform (see \cite[40--41]{iacus1}, \cite{moma}, \cite[98--100]{saso}) to the process $V$ to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
-To this purpose, we consider the following Lamperti transformation
+Under the conditions that permit to use It\^{o}'s formula on a well-chosen transformation of the process $V$, John Lamperti (\cite{lamp}) first showed that the transformed process is again a diffusion that is solution to a SDE with unit coefficient for the diffusion term.
+A vast literature refers nowadays to this result as the so-called Lamperti transform (see, for example, \cite[40--41]{iacus1}, \cite{moma}, \cite[199--203]{pani}, \cite[98--100]{saso}), which is a basic tool to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
+A remarkable effect of removing the state dependency from the random noise term is to increase the numerical stability of the simulated paths of the transformed process.
+For this reason, some estimation methods of the unknown parameters of non-linear SDE models incorporated the use on the Lamperti's change of variable as part of a more complex approximation procedure (for example, the local linearization method in  \cite{shoz}, or the expansion method in \cite{ait}, later extended to multivariate diffusion in \cite{ait2}).
+
+We consider the following Lamperti transformation  
 %{\color{red} (Remind that continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
@@
 
-{\color{red} We can see in Figure (\ref{fig:LP_transitions}) the effect of the Lamperti transformation upon the forecast error data.
+We can see in Figure (\ref{fig:LP_transitions}) how the Lamperti transformation modifies the forecast error transition histogram without curtailment displayed in Figure (\ref{fig:error_transitions}).
 
@@
 \includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
-\caption{Transitions after the Lamperti transform.
-The transitions now present a normal Gaussian shape.
-This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
+\caption{Lamperti transformed forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
   \label{fig:LP_transitions}
@@
 
-The Lamperti transformation has greatly reduced the forecast error skewness, ensuring that the process stays in the range $[0,1]$.
-Therefore, in this case, the transition densities of the process Z can be adequately approximated through Gaussian densities.}
+The shape of the forecast error transition histograms after the Lamperti transformation has much resemblance with a Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process Z.
 

### 2020-05-28 LaTeX_Code/Paper/paper_1line.tex

@@
 \end{equation}
-where $t_{j ,i} \equiv  t_j + i \Delta$ for any $j = 1, \ldots, M$ and $i = 0, \ldots, N$.
-
- {\color{red} Remark: The statistical model (\ref{likelihood}) can be generalized incorporating the transition that occurs during the time interval, say $\delta$, between the time when the forecast is done and the first date of forecasting.
-In this case, the inner product in  (\ref{likelihood}) must include for any of the $M$ paths an additional factor, say $\rho_0 (V_{j, 0}|V_{j, -\delta};\bm{\theta},\delta)$, expressing the conditional density of this early transition.
-The parameter $\delta$ can be calibrated after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.}
+where $t_{j ,i} \equiv  t_j + i \Delta$ for any $j = 1, \ldots, M$ and $i = 0, \ldots, N$. \\
+
+ Remark: In the last subsection of this Section, we will extend the statistical model (\ref{likelihood}) by adding the transition that occurs during the time interval, say of length $\delta$, between the epoch when the forecast is done and the first epoch (1 pm) of each day-ahead forecast.
+To this purpose, the likelihood function (\ref{likelihood}) must include for any of the $M$ paths an additional factor, say $\rho_0 (V_{j, 0}|V_{j, -\delta};\bm{\theta},\delta)$, expressing the conditional density of the early transition.
+The parameter $\delta$ can be calibrated after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.
+\\
 
@@
 
-\subsubsection{Additional Parameter $\delta$}
-
-We observe that for most days, the error at time $t_{j,0}=0$ is not zero. By forecasts construction, we assume that for some time in the past $t_{j,\delta}<t_{j,0}$, the error $V_{j,\delta}=0$.\\
+\subsection{Model specification with the additional parameter $\delta$}
+
+We observe that for most days, the forecast error at time $t_{j,0}=0$ is not zero.
+According to the forecasts procedure, we may assume that there is a time in the past $t_{j,-\delta}<t_{j,0}$, such that the forecast error $V_{j,-\delta}=0$.\\
+
+For any $j=1, \ldots, M$, we extrapolate linearly the truncated prediction function to get the value for $p_{j,-\delta}$, and set $v(t_{j,-\delta})=0$.
+In this way, we consider the initial transition $(V_{j, 0}|v_{j,-\delta};\bm{\theta},\delta)$.
+We assume that this initial transition has a Beta distribution and apply the same moment matching method as for the rest of the transitions described above.
+Given an initial guess for $\bm{\theta}$, we obtain the initial estimation for $\delta$ solving the following problem
+\begin{equation}
+\delta\approx\arg\max_{\delta}\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,-\delta};\bm{\theta},\delta\right),
+\label{eq:likelihood_delta}
+\end{equation}
+where $\mathcal{L}_\delta$ is the $\delta-$likelihood.
+To solve this problem, we repeat the steps described in subsection (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation for $p_{j,-\delta}$.\\
 \quad\\
-We extrapolate linearly $p_t$ considering the truncation at $\epsilon$, so we have a value for $p_{j,\delta}$, and set $v(t_{j,\delta})=0$.
-Then, for each $j$, we have an initial transition $(V_{j, 0}|v_{j,\delta};\bm{\theta},\delta)$.
-We assume again that it is Beta and apply the same moment matching as for the rest of transitions.
-With our initial guess for $\bm{\theta}$, we can construct our initial guess for $\delta$ solving the problem
-
-\begin{equation}
-\delta\approx\arg\max_{\delta}\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,\delta};\bm{\theta},\delta\right),
-\label{eq:likelihood_delta}
-\end{equation}
-where $\mathcal{L}_\delta$ is the $\delta-$likelihood.
-To solve this problem, we repeat the steps described in section (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation for $p_{j,\delta}$.\\
-\quad\\
-We can extend the likelihood (\ref{likelihood}) to include this extra parameter. The complete likelihood, $\mathcal{L}_c$, is given by
+As remarked, we can extend the statistical model (\ref{likelihood}) to include the extra parameter $\delta$. The complete likelihood, $\mathcal{L}_c$, is given by
 \begin{equation}
@@
 \end{equation}
-As we can construct initial guesses for $\bm{\theta}$ and $\delta$, we have a staring point for the maximization of (\ref{eq:complete_LH}).
+As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the maximization of (\ref{eq:complete_LH}).
 

### 2020-05-28 LaTeX_Code/Paper/paper_1line.tex
Latest paper's version

@@
 
-{\color{red} Add AMS Classification.}
+{\color{red} 2020 AMS Subject Classification: 60H10}
 
@@
 
-\item \textbf{Least Square Minimization:} We consider the observed data $v^{M,N+1}$ with $\Delta v_{j,i}=v_{j,i+1}-v_{j,i}$ and length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
+\item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with $\Delta v_{j,i}=v_{j,i+1}-v_{j,i}$ and length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
 $(V_{j,i+1}|v_{j,i})$ is a random variable which conditional mean can be approximated by the solution of the system
@@
 \end{equation*}
-follows that
+it follows that
 \begin{equation}
@@
 
-\item \textbf{Quadratic Variation:} We approximate the SDE by its E-M scheme. In particular, we approximate the It\^o quadratic variation with the discrete one:
-\begin{itemize}
-
-\item It\^o process quadratic variation: $[V]_t=\int_0^t\sigma_s^2\dif s$.
-\item Discrete process quadratic variation: $[V]_t=\sum_{0<s\leq t}(\Delta V_s)^2$.
-
-\end{itemize}
-
-Then, considering $\Delta$ the time between measurements, we approximate:
-\begin{equation}
-\theta_0^*\alpha^*\approx\frac{\sum_{j=1}^M\sum_{i=1}^N(\Delta v_{j,i})^2}{2\Delta\cdot\sum_{j=1}^M\sum_{i=1}^N(v_{j,i}+p_{j,i})(1-v_{j,i}-p_{j,i})}.
+\item \textbf{Quadratic variation:} We use the numerical Euler-Maruyama (E-M) scheme to approximate the solution to the SDE  \eqref{VtSDE}.
+In particular, we approximate the quadratic variation of the  It\^{o}'s  process $V$
+\begin{equation*}
+[V]_t=\int_0^t b(V_s; \bm{\theta}, p_s)^2 \dif s, \text{ where }  \:\: b(V_s; \bm{\theta}, p_s) = 
+\sqrt{2 \alpha \theta_0 (V_s +p_s ) (1-V_s - p_s)}\,,
+\end{equation*}
+with the discrete sum $\sum_{0< t_{j, i-1} \leq t}(V_{t_{j, i}} - V_{t_{j, i-1}})^2$.
+
+As initial guess for the diffusion variability coefficient $\theta_0 \alpha$, we choose
+\begin{equation}
+\theta_0^*\alpha^*\approx\frac{\sum_{j=1}^M\sum_{i=1}^N(v_{j,i} - v_{j,i-1})^2}{2\Delta\cdot\sum_{j=1}^M\sum_{i=1}^N(v_{j,i}+p_{j,i})(1-v_{j,i}-p_{j,i})}\,,
 \label{Eq-2}
 \end{equation}
-
+where $\Delta$ is the length of the time interval between two consecutive measurements.
 \end{itemize}
@@
 \begin{equation}
-\Psi(\bm{\theta}^*)=\frac{|\theta_0^{*}-\theta_0^{**}|}{|\theta_0^{*}|}+\frac{|\alpha^{*}-\alpha^{**}|}{|\alpha^{*}|},
+\Psi(\bm{\theta}^*)=\frac{|\theta_0^*\alpha^*-\theta_0^{**}\alpha^{**}|}{|\theta_0^*\alpha^*|},
 \label{eq:rel_error}
@@
 
-For any $j=1, \ldots, M$, we extrapolate linearly the truncated prediction function to get the value for $p_{j,-\delta}$, and set $v(t_{j,-\delta})=0$.
-In this way, we consider the initial transition $(V_{j, 0}|v_{j,-\delta};\bm{\theta},\delta)$.
-We assume that this initial transition has a Beta distribution and apply the same moment matching method as for the rest of the transitions described above.
-Given an initial guess for $\bm{\theta}$, we obtain the initial estimation for $\delta$ solving the following problem
+For any $j=1, \ldots, M$, we extrapolate backward linearly the truncated prediction function to get its value at time $-\delta$,$p_{j,-\delta}$, and set $v_{t_{j,-\delta}}=0$.
+We assume that the initial transition $(V_{j, 0}|v_{j,-\delta};\bm{\theta},\delta)$
+has a Beta distribution and apply to it the same moment matching method used above.
+Given a starting value for $\bm{\theta}$, we obtain the initial estimation for $\delta$ solving the following problem
 \begin{equation}
@@
 \quad\\
-As remarked, we can extend the statistical model (\ref{likelihood}) to include the extra parameter $\delta$. The complete likelihood, $\mathcal{L}_c$, is given by
+As remarked, we extend the statistical model (\ref{likelihood}) to include the extra parameter $\delta$. The complete likelihood, $\mathcal{L}_c$, is given by
 \begin{equation}
@@
 \end{equation}
-As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the maximization of (\ref{eq:complete_LH}).
+As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the complete likelihood (\ref{eq:complete_LH}).
 
@@
 \end{table}
-Observe that all the local (possibly global) minimizers are located in curve $\theta_0,\alpha=0.097$.
+Observe that all the local (possibly global) minimizers are located in curve $\theta_0\alpha=0.097$.
 We will explain this effect later, but it is a consequence of Markovianity and the indistinguishable observed transitions.
@@
 \end{equation}
- with $\theta_0 > 0, \, \alpha > 0$ and .
+ with $\theta_0 > 0, \, \alpha > 0$ and $\theta_t$ satisfying the condition \eqref{Assumption:3} .
 \end{itemize}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/delta/contour_delta.png}
+\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/delta/contour_delta.eps}
 \caption{Initial value for $\delta$ as a function of the elements of the parameter vector $\bm{\theta}$.}

### 2020-05-30 LaTeX_Code/Paper/paper_1line_Renzo.tex
Corrected paper (added subsections 5.4.1, 5.)

@@
 
-\usepackage[backend=biber, style=authoryear, citestyle=authoryear, autocite=inline]{biblatex} % package for bibliography 
-%\DeclareLanguageMapping{english}{english-apa}
-
 \addbibresource{sdewind.bib}
@@
 
-\newcommand{\add}{\textcolor{red}{[insert]}}
-
 \setcounter{page}{1}
-\sloppy
+
 \begin{document}
@@
 We apply the model to Uruguayan wind power forecasts together with historical wind power production data pertaining to the year 2019.
-
-{\color{red} Change this paragraph. Discuss with the global dataset, the dataset after removing days when curtailing has been detected, the data set without curtailing and with Lamperti transform.}
-We have available a year long data set from Uruguay based on 363 observation paths, each of which is 24-hours long with observations recorded every 10 min.
-In total, it is a data set of approximately fifty thousand data points recorded in 2019.
-See Figure (\ref{fig:sample_data}).
-Data are normalized with respect to the maximum power capacity of wind power production in Uruguay, which is $\SI{1474}{\mega\watt}$.
-However, sometimes the real production is artificially modifies due to curtailing.
-This effect becomes clear when we inspect for different power production levels.
-We split the available data into low, medium and high power range.
-See Figure (\ref{fig:data_curtailing}).\\
-We identify and remove the days with curtailing, removing a total of 108 days.
-From the resulting 255 days, we use 127 days to train the system and 128 to test it.
-Also, to avoid correlation between days, we intercalate the days we use for training and testing ({\color{red} Show that 24h is enough to ensure independence}).
-
-In this paper we present the phenomenological underlying model in Section \ref{Section_2} and describe the physical constraints in Section \ref{Section_3} and how these constrains can be met.
-Then, in Section \ref{Section_4}, we will introduce an alternative formulation of the model in Lamperti space.
-In Section \ref{Section_5}, we show our parameter estimation procedure and its results in Section \ref{Section_6}.
-We compare alternative models in Section \ref{Section_7} and different forecast providers in Section \ref{Section_8}.
+\\
+
+In Section \ref{Section_2}, we introduce the main characteristics of a real data set encompassing the normalized wind power production in Uruguay during the period April-December 2019, joint with the most accurate predictions, as highlighted in our posterior analysis, performed by one out of the three sources of forecast providers.
+The significant steps for constructing phenomenological models of the normalized wind power production and the forecast error based on stochastic differential equations are described in Section \ref{Section_3}.
+After reformulating the SDE for the forecast error in Section \ref{Section_4}, by applying the Lamperti transform that leads to a unit diffusion coefficient, we write down in Section \ref{Section_5} the expressions for the likelihood functions of the forecast error in its original space and in the Lamperti space.
+We also derive simple approximations of the likelihood functions.
+Section \ref{Section_5} concludes with the description of the optimization algorithm to compute approximate maximum likelihood estimates, including the case where we expand the model comprising an initial transition from the time the forecast is performed to the time of the first forecast.
+In Section \ref{Section_6}, we apply our proposed parametric estimation procedure to the Uruguay wind and forecast dataset, comparing two alternative models and assessing, for the best candidate model, the performance of three different forecast providers.
+The proofs of the existence, strong uniqueness, and boundedness of the solutions of the SDE used to model normalized wind power production and its forecast error are given in the Appendix.
+
+%---END SECTION 1---
+
+%---BEGIN SECTION 2---
+
+\section{Wind power production data in Uruguay and forecast providers } \label{Section_2}
+
+In recent years, Uruguay has triggered a remarkable change in its energy matrix.
+In (\cite{irena}, p.23) Uruguay is among those countries showcasing innovation, like Denmark, Ireland, Germany, Portugal, and Spain, with proven feasibility of managing annual variable renewable energy (VRE) higher than 25\% in power systems.
+
+According to (\cite{ren21}, pp.118-119), in 2018, Uruguay achieved 36\% of its electricity production from variable wind energy and solar PV, raising the share of generation from wind energy more than five-fold in just four years, from 6.2\% in 2014 to 33\% in 2018.
+
+At present, Uruguay is fostering even higher levels of wind penetration by boosting regional power trading with Argentina and Brazil. 
+In this rapidly evolving scenario, it is essential to analyze national data on wind power production joint with wind power short-term forecastings to orientate and assess the strategies and decisions of wind energy actors and businesses.
+
+Our study is based on publicly available data (source: Administrator of Electric Market) on the wind power production in Uruguay for the period April-December 2019, that we adequately normalized with respect to the present $\SI{1474}{\mega\watt}$ maximum installed wind power capacity.
+Each day, wind power production recordings are available every ten minutes.
+In this work, we have also considered data from three different forecast providers, available each day starting at 1 pm.
+
+The next Figure \ref{fig:sample_data} shows the wind power real production during four segments 24-hour long selected from the observation period together with their corresponding hourly short-term forecast, computed by a forecast provider.
+For the sake of visualization clarity, this Section relies only on forecasts from one provider, called "provider A" from now on, ranked as the most accurate forecast provider, as it emerged from our posterior analysis.
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/5.eps}
-\includegraphics[width=0.45\textwidth]{plots/245.eps}\\
-\includegraphics[width=0.45\textwidth]{plots/661.eps}
-\includegraphics[width=0.45\textwidth]{plots/805.eps}
-\caption{Four samples from the Uruguayan data of 2019.
-Each sample compromises of two 24-hour paths.
-In blue is an hourly wind power production forecast.
-In orange is the actual wind power production recorded in 10 minute intervals.}
+\includegraphics[width=0.45\textwidth]{plots/four_days/377.eps}
+\includegraphics[width=0.45\textwidth]{plots/four_days/417.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{plots/four_days/437.eps}
+\includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
+\caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blue line).}
   \label{fig:sample_data}
 \end{figure}
+
+A view of the global discrepancy between the real production and the forecasted production, during the nine months observation period, is summarized through the forecast error histograms, Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
+Low normalized generated power corresponds to the range $[0,0.3]$, mid-power refers to the range $(0.3,0.6]$, and high-power to the range $(0.6,1]$.
 
@@
 \includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
-\caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production.
-Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$.
-We have a total of 363 days to use.}
+\caption{Wind production forecast error histograms during the period April-December 2019: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
   \label{fig:data_curtailing}
 \end{figure}
+
+We may observe that all the histograms in the Figure \ref{fig:data_curtailing} exhibit skewed patterns, to a different extent, as well as extreme observations.
+The presence of these features can be partly explained.
+The analysis of the dataset highlighted that, during several 24-hour segments, the system operators decided to reduce, or even cease the wind power production.
+Indeed, as recalled in (\cite{irena2}, p.3), ``Uruguay experiences high curtailment levels because generation exceeds demand.'' Despite the large country’s interconnection capacity with Argentina and Brazil, there is no active cross-border market, the energy is traded via ad hoc short-term agreements.
+``Even with interconnection capacity exceeding peak demand, the power system experiences high VRE curtailment, mostly at night when wind generation exceeds demand.''
+
+The curtailment of the wind power production imposed by the system operators has a strong influence on the forecast error.
+To build a model that, driven by the available forecast, allows to include the true power production with a prescribed degree of uncertainty, it is necessary to remove the data segments affected by wind curtailment.
+
+Once we removed all the 24-hour segments showing wind curtailment, we set up a dataset containing 147 daily segments. 
+In the absence of the curtailment intervention, the forecast error histograms are shown below in Figure \ref{fig:data_after_clean}, where it can be appreciated skewness reduction, except for low power forecast errors histogram.
 
@@
 \includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
+\quad\\
 \includegraphics[width=0.45\textwidth]{plots/HP.eps}
 \includegraphics[width=0.45\textwidth]{plots/AP.eps}
-\caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
+\caption{Wind production forecast error histograms during the period April-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
   \label{fig:data_after_clean}
 \end{figure}
+
+In this stage of data preprocessing, we obtain another useful result by applying the first-order difference operator to the forecast errors. 
+The forecast error transition histograms, displayed in the next Figure \ref{fig:error_transitions}, will constitute later a reference for the visual assessment of the global fit of the proposed models.
 
@@
 \includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
+\quad\\
 \includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
 \includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
-\caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
+\caption{Forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
 \label{fig:error_transitions}
@@
 
-%---END SECTION 1---
-
-%---BEGIN SECTION 2---
-\section{Phenomenological  Model} \label{Section_2}
-
-In this section, once we analyzed the available dataset, we consider a type of phenomenological model for the normalized wind power generation forecasts which is given, in its most general form, as a stochastic process $X = \{X_t, \, t \in [0,T] \}$  defined by the following stochastic differential equation (SDE):
-
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&=  a(X_t; p_t, \dot{p}_t,\bm{\theta}) \,dt + b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \,dW_t\,, \quad t \in [0,T]  \\
-     X_0  \!\!\!&=  x_0 \in [0,1],
-  \end{array}\right. \label{eq:main}
+The histograms in Figure \ref{fig:error_transitions} feature a non-Gaussianity trait and provide initial input for the model-building stage, which is described in Section next.
+Later, in Section \ref{Section_4}, guided from inferring the unknown model parameters, we will also propose transforming data as a strategy that naturally leads to an alternative model.
+
+%---END SECTION 2---
+
+%---BEGIN SECTION 3---
+
+\section{Phenomenological  Model} \label{Section_3}
+
+After analyzing the available dataset, we are now in the condition to build a type of phenomenological model for the normalized wind power generation forecasts that, in its most general form, is a stochastic process $X = \{X_t, \, t \in [0, T] \}$  defined by the following stochastic differential equation (SDE):
+
+\begin{equation}
+\begin{cases}
+    \dif X_t &=  a(X_t; p_t, \dot{p}_t,\bm{\theta})\dif t + b (X_t; p_t, \dot{p}_t, \bm{\theta} )\dif W_t, \quad t \in [0,T]  \\
+     X_0  &=  x_0 \in [0,1],
+\end{cases}
+ \label{eq:main}
 \end{equation}
@@
 
-\subsection{Physical Constraints} \label{Sec: Physical_Constraints}
+\subsection{Physical Constraints} \label{Physical_Constraints}
 
@@
 For instance, consider the diffusion model (\ref{eq:main}) with $a(X_t; p_t, \bm{\theta}) = - \theta_0 (X_t - p_t)\,, \theta_0 > 0$.
-In this case, given  $ \mathbb{E} X_0 = p_0$, the diffusion has mean $\mathbb{E} X_t = p_t - e^{- \theta_0 t } \int_0^t \dot{p}_s  e^{\theta_0 s} ds$.
-The next Figure (\ref{fig:derivative_tracking}) illustrates paths of two diffusions with and without derivative tracking.
-
-\begin{figure}[h]
-  %\includegraphics[width=26mm,scale=1]{}
-  \caption{{\color{red} Add Figure showing the difference with and without derivative tracking}}
+In this case, given  $ \mathbb{E} \left[X_0\right] = p_0$, the diffusion has mean $\mathbb{E} \left[X_t\right] = p_t - e^{- \theta_0 t } \int_0^t \dot{p}_s  e^{\theta_0 s} \dif s$.
+The next Figure (\ref{fig:derivative_tracking}) illustrates how different behave the estimated confidence bands for two diffusion models with and without derivative tracking, fitting the same daily segment.
+
+\begin{figure}[H]
+\centering
+  \includegraphics[width=0.45\textwidth]{plots/31.eps}\includegraphics[width=0.45\textwidth]{plots/31_2.eps}
+  \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (graph on the left) and with derivative tracking (graph on the right).}
   \label{fig:derivative_tracking}
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= (\dot{p}_t  - \theta_t (X_t - p_t) ) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{ourmodel}
-\end{equation}
-
-is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X$ to (\ref{ourmodel}) a non-stationary and time-inhomogeneous process.
-To ensure that the process $X$ be the unique strong solution to (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the following condition:
-%has to be selected according to the following rule.
-Observe that the time derivative term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays a.s.
-inside the range $[0,1]$.
-In other words, the zero drift line defined by $a(x; p_t,\bm{\theta}) =0$, which is an attractor, must be contained inside the range $[0,1]$.
-Thus, we must have that
-%\begin{equation}
-%\frac{- |\dot{p_t}|}{p_t} \leq \theta_t \leq \frac{|\dot{p}_t|}{1- p_t}
-%\end{equation}
-%which is satisfied  by choosing a time-dependent  $\theta_t$ as follows,
-%\begin{equation}
-%\theta_t = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right ),  \quad \theta_0 >0\,. \label{theta_t}
-%\end{equation}
-\begin{equation}\label{Assumption:3}
-\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
-\end{equation} \label{condC}
+\begin{cases}
+    \dif X_t&= \left(\dot{p}_t  - \theta_t (X_t - p_t) \right) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]  \\
+   X_0 &=  x_0\in [0,1] \,,
+\end{cases}
+\label{ourmodel}
+\end{equation}
+
+is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X$ of (\ref{ourmodel}) to a non-stationary and time-inhomogeneous process.
+To ensure that the process $X$ is the unique strong solution of (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the condition:
+
+\begin{equation}
+\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{B}. 
+\end{equation} \label{condB}
 The proof of this theoretical statement is presented in Section \ref{Appendix}. \\
 
-Remark: Condition (C) shows that the time-varying parameter $\theta_t$ becomes unbounded when $p_t = 0$ or $p_t = 1$. Therefore, we consider the following truncated prediction function
+Remark: Condition (B) shows that the time-varying parameter $\theta_t$ becomes unbounded when $p_t = 0$ or $p_t = 1$. Therefore, we consider the following truncated prediction function
 \begin{equation}
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dV_t \!\!\!&=  - \theta_t V_t  \, dt + \sqrt{2 \alpha \theta_0 (V_t +p_t ) (1-V_t-p_t)} \, dW_t\,, \quad t \in [0,T]  \\
-   V_0  \!\!\!&=  v_0\in [-1 + \epsilon,1 - \epsilon] \,.
- \end{array}\right.  \label{VtSDE}
-\end{equation}
-
-%---END SECTION 2---
-
-%---BEGIN SECTION 3---
-\section{State independent diffusion term: Lamperti transform} \label{Section_3}
+\begin{cases}
+\dif V_t&=  - \theta_t V_t\dif t + \sqrt{2 \alpha \theta_0 (V_t +p_t ) (1-V_t-p_t)}\dif W_t, \quad t \in [0,T]  \\
+V_0&=  v_0\in [-1 + p_0,1 - p_0].
+\end{cases}  \label{VtSDE}
+\end{equation}
+
+%---END SECTION 3---
+
+%---BEGIN SECTION 4---
+
+\section{State independent diffusion term: Lamperti transform} \label{Section_4}
 
 Our model (\ref{VtSDE}) for the forecast error has a diffusion term that depends on the state variable $V_t$.
-To estimate the unknown model parameters, a recommended technique is to modify the SDE (\ref{VtSDE}) by applying the so-called Lamperti transform (see \cite[40--41]{iacus1}, \cite{moma}, \cite[98--100]{saso}) to the process $V$ to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
-To this purpose, we consider the following Lamperti transformation
+Under the conditions that permit to use It\^{o}'s formula on a well-chosen transformation of the process $V$, John Lamperti (\cite{lamp}) first showed that the transformed process is again a diffusion that is solution to a SDE with unit coefficient for the diffusion term.
+A vast literature refers nowadays to this result as the so-called Lamperti transform (see, for example, \cite[40--41]{iacus1}, \cite{moma}, \cite[199--203]{pani}, \cite[98--100]{saso}), which is a basic tool to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
+A remarkable effect of removing the state dependency from the random noise term is to increase the numerical stability of the simulated paths of the transformed process.
+For this reason, some estimation methods of the unknown parameters of non-linear SDE models incorporated the use on the Lamperti's change of variable as part of a more complex approximation procedure (for example, the local linearization method in  \cite{shoz}, or the expansion method in \cite{ait}, later extended to multivariate diffusion in \cite{ait2}).
+
+We consider the following Lamperti transformation  
 %{\color{red} (Remind that continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
@@
 \begin{align}
-Z_t = h(V_t, t)  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \,dv \Bigg{\vert}_{v = V_t}  \nonumber \\
-& = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
+Z_t = h(V_t, t; \bm{\theta} )  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \dif v \Bigg{\vert}_{v = V_t}   = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
 \end{align}
@@
 \begin{align}
-dZ_t = \Bigg[  & \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  \nonumber \\ 
-& + \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \,dt + dW_t \,.
+\dif Z_t = \Bigg[  & \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  + \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \dif t + \dif W_t \,.
 \label{eq:stindepSDE}
@@
 \begin{align}
-dZ_t & = \Bigg[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)}  \nonumber \\
-&  - \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \Bigg] \,dt + dW_t \nonumber \\
-&  = \left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \,dt + dW_t \,.
+\dif Z_t & = \left[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)}   - \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \right]\dif t + \dif W_t \nonumber \\
+&  = \left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \dif t + \dif W_t.
 \label{eq:stindepSDE2}
@@
 \includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
+\quad\\
 \includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
 \includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
-\caption{Transitions after the Lamperti transform.
-The transitions now present a normal Gaussian shape.
-This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
+\caption{Lamperti transformed forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
   \label{fig:LP_transitions}
@@
 
-The Lamperti transformation has greatly reduced the forecast error skewness, ensuring that the process stays in the range $[0,1]$.
-Therefore, in this case, the transition densities of the process Z can be adequately approximated through Gaussian densities.}
-
-%---END SECTION 3---
-
-%---BEGIN SECTION 4---
-\section{Likelihood in $V$ space} \label{Section_4}
-
-\subsection{Likelihood}
-
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$, and let $ V^{M,N + 1}=\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \}$ denote this random sample, with $V_{t_j^{N + 1}} = \{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \}, \, j = 1, \ldots, M$.
-
-Let $\rho(v \vert v_{j, i-1} ; \bm{\theta})$ be the conditional probability density of $V_{t_j + i \Delta} \equiv V_{j, i}$ given $V_{j, i-1} = v_{j, i-1}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha, \epsilon)$ are the unknown model parameters.
+The shape of the forecast error transition histograms after the Lamperti transformation has much resemblance with a Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process Z.
+
+%{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models, that is if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.}
+
+%---END SECTION 4---
+
+%---BEGIN SECTION 5---
+
+\section{ Likelihood functions of the forecast errors data and optimization algorithm} \label{Section_5}
+
+\subsection{Likelihood in the $V-$space}
+
+Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$, and let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}, \, j = 1, \ldots, M$.
+
+Let $\rho(v \vert v_{j, i-1} ; \bm{\theta})$ be the conditional probability density of $V_{t_j + i \Delta} \equiv V_{j, i}$ given $V_{j, i-1} = v_{j, i-1}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha)$ are the unknown model parameters.
 
@@
 \begin{equation}
-\mathcal{L}(\bm{\theta}; V^{M,N +1}) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho ( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} )  \,  \right\} \,,
+\mathcal{L}(\bm{\theta}; V^{M,N +1}) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho ( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} )  \,  \right\},
 \label{likelihood}
 \end{equation}
-where $t_{j ,i} \equiv  t_j + i \Delta$ for any $j = 1, \ldots, M$ and $i = 0, \ldots, N$.
-
- {\color{red} Remark: The statistical model (\ref{likelihood}) can be generalized incorporating the transition that occurs during the time interval, say $\delta$, between the time when the forecast is done and the first date of forecasting.
-In this case, the inner product in  (\ref{likelihood}) must include for any of the $M$ paths an additional factor, say $\rho_0 (V_{j, 0}|V_{j, -\delta};\bm{\theta},\delta)$, expressing the conditional density of this early transition.
-The parameter $\delta$ can be calibrated after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.}
+where $t_{j ,i} \equiv  t_j + i \Delta$ for any $j = 1, \ldots, M$ and $i = 0, \ldots, N$. \\
+
+ Remark: In the last subsection of this Section, we will extend the statistical model (\ref{likelihood}) by adding the transition that occurs during the time interval, say of length $\delta$, between the epoch when the forecast is done and the first epoch (1 pm) of each day-ahead forecast.
+To this purpose, the likelihood function (\ref{likelihood}) must include for any of the $M$ paths an additional factor, say $\rho_0 (V_{j, 0}|V_{j, -\delta};\bm{\theta},\delta)$, expressing the conditional density of the early transition.
+The parameter $\delta$ can be calibrated after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.
+\\
 
@@
 
-Closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases.
+Closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
 Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
 Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.
- {\color{red} Rewrite: Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.}
-
-\subsection{Approximate Likelihood}
+ {\color{red} Rewrite: Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, consider Preston and Wood, then Egorov, and then Sorensen, remove the
+ survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}, refer to time-homogeneous.}
+
+\subsection{Approximate likelihood  in the $V-$space} \label{moments_ODEs}
 
 Gaussian approximations to the transition densities of nonlinear time-in\-ho\-mo\-geneous SDEs are available through different algorithms \autocite[Chapter 9]{saso}.
-However, as Figure (\ref{fig:error_transitions}) may suggest at a first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
+However, as Figure \ref{fig:error_transitions} may suggest at a first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
 
@@
 \begin{equation}
- \tilde{\ell} (\bm{\theta}; v^{M,N +1}) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1, \xi_2)} \Big( \frac{z_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \Big)^{\xi_1 -1}  \Big( \frac{1 - \epsilon - z_{j,i}}{2(1 - \epsilon)} \Big)^{\xi_2 -1} \right\} \,,
-\label{loglikelihoodV}
+ \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1, \xi_2)} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1 -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2 -1} \right\},
+\label{eq:loglikelihoodV}
 \end{equation}
 where the shape parameters $\xi_1$ and $\xi_2$, according to (\ref{param_transformed_beta}), depend on the quantities $\mu(t_{j,i};\bm{\theta} )$ and $\sigma^2(t_{j,i};\bm{\theta} )$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
-\\
+
+\subsection{Approximate likelihood  in the $Z-$space}
 
@@
 To guarantee the good behave for our optimization algorithm, we aim to start the optimization as close as we can from the optimal parameters.
-We use \textbf{Lease Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess, and to tune the hyper-parameter $\epsilon\in(0,\frac{1}{2})$.
+We use \textbf{Least Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess.
 
@@
 
-\item \textbf{Least Square Minimization:} We consider a set of transitions $\{\Delta V_i\}_{i}$ with $\Delta V_i=V_{i+1}-V_i$ and $\Delta t=t_{i+1}-t_i$.
-$(V_{i+1}|V_i)$ is a random variable which conditional mean can be approximated by the solution of the system
+\item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
+$(V_{j,i+1}|v_{j,i})$ is a random variable which conditional mean can be approximated for any $t\in [t_{j,i-1}, t_{j, i})$ by the solution of the system
 \begin{equation*}
@@
 \dif \E\left[V\right]&=-\theta_t\E\left[V\right]\dif t\\
-\E\left[V(t_i)\right]&=V_i,
+\E\left[V\right](t_{j,i})&=v_{j,i},
 \end{cases}
 \end{equation*}
-evaluated in $t_{i+1}$ (i.e., $\E\left[V(t_{i+1})\right]$).
-Then, the random variable $(V_{i+1}-\E\left[V(t_{i+1})\right])$ has approximately zero mean.
-If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_i,t_{i+1}]$, then $\E\left[V(t_{i+1})\right]=V_ie^{-c\Delta t}$.
-If we have a total of $n$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
-\begin{equation}
-c^*\approx\arg\min_{c\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-\E\left[V(t_{i+1})\right]\right)^2\right]=\arg\min_{c\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-V_ie^{-c\Delta t}\right)^2\right].
+evaluated in $t_{j,i+1}$, i.e., $\E\left[V\right](t_{j,i+1})$.
+Then, the random variable $(V_{j,i+1}-\E\left[V\right](t_{j,i+1}))$ has zero mean.
+If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i},t_{j,i+1}]$, then $\E\left[V(t_{j,i+1})\right]=v_{j,i}e^{-c\Delta}$.
+If we have a total of $M\times N$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
+\begin{equation}
+\begin{split}
+c^*&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-\E\left[V\right](t_{j,i+1})\right)^2\right]\\
+&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}e^{-c\Delta}\right)^2\right]\\
+&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right)^2\right].
+\end{split}
 \label{Eq-1}
 \end{equation}
-As Equation (\ref{Eq-1}) is convex in $c$ (composition of convex is convex), it is enough to verify the first order optimality conditions.
+As Equation (\ref{Eq-1}) is convex in $c$ (composition of convex is convex), it is enough to verify the first order optimality conditions. From
 \begin{equation*}
-\begin{split}
-\frac{\partial f}{\partial c}&=\sum_{i=1}^n2(-V_i)(-\Delta t)(V_{i+1}-V_i(1-\theta_0\Delta t))\\
-&=\sum_{i=1}^n2V_i\Delta t(V_{i+1}-V_i(1-c\Delta t))\\
-&=\sum_{i=1}^n2V_{i+1}V_i\Delta t-2V_i^2\Delta t+2V_i^2\Delta t^2c.
-\end{split}
+\frac{\partial}{\partial c}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right)^2\right]=\sum_{j=1}^M\sum_{i=0}^{N-1}2v_{j,i}\Delta\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right),
 \end{equation*}
-Then, $c^{**}$ satisfies
-\begin{equation}
-c^{**}\approx\frac{\sum_{i=1}^nV_i(V_i-V_{i+1})}{\Delta t\cdot\sum_{i=1}^n(V_i)^2}\quad\text{and}\quad c^*=\max\{c^{**},0\}.
+it follows that
+\begin{equation}
+c^{*}=\frac{\sum_{j=1}^M\sum_{i=0}^{N-1}v_{j,i}(v_{j,i}-v_{j,i+1})}{\Delta\cdot\sum_{j=1}^M\sum_{i=0}^{N-1}(v_{j,i})^2}.
 \label{Eq-4}
 \end{equation}
-Notice that $c^{**}$ has dimension $\mathbf{time}^{-1}$.
-
-\item \textbf{Quadratic Variation:} We approximate the SDE by its E-M scheme. In particular, we approximate the It\^o quadratic variation with the discrete one:
-\begin{itemize}
-
-\item It\^o process quadratic variation: $[V]_t=\int_0^t\sigma_s^2\dif s$.
-\item Discrete process quadratic variation: $[V]_t=\sum_{0<s\leq t}(\Delta V_s)^2$.
-
+
+\item \textbf{Quadratic variation:} We use the numerical Euler-Maruyama (E-M) scheme to approximate the solution to the SDE  \eqref{VtSDE}.
+In particular, we approximate the quadratic variation of the  It\^{o}'s  process $V$
+\begin{equation*}
+[V]_t=\int_0^t b(V_s; \bm{\theta}, p_s)^2 \dif s, \text{ where }  \:\: b(V_s; \bm{\theta}, p_s) = 
+\sqrt{2 \alpha \theta_0 (V_s +p_s ) (1-V_s - p_s)}\,,
+\end{equation*}
+with the discrete sum $\sum_{0< t_{j, i-1} \leq t}(V_{t_{j, i}} - V_{t_{j, i-1}})^2$.
+
+As initial guess for the diffusion variability coefficient $\theta_0 \alpha$, we choose
+\begin{equation}
+\theta_0^*\alpha^*\approx\frac{\sum_{j=1}^M\sum_{i=1}^N(v_{j,i} - v_{j,i-1})^2}{2\Delta\cdot\sum_{j=1}^M\sum_{i=1}^N(v_{j,i}+p_{j,i})(1-v_{j,i}-p_{j,i})}\,,
+\label{Eq-2}
+\end{equation}
+where $\Delta$ is the length of the time interval between two consecutive measurements.
 \end{itemize}
 
-Then, considering $\Delta t$ the time between measurements, we approximate:
-\begin{equation}
-\theta_0^*\alpha^*\approx\frac{\sum_{i=1}^n(\Delta V_i)^2}{2\Delta t\sum_{i=1}^n(V_i+p_i)(1-V_i-p_i)}.
-\label{Eq-2}
-\end{equation}
-
-\end{itemize}
-
-In section (\ref{Sec: Physical_Constraints}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$.
+%In Subsection (\ref{Physical_Constraints}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$.
 Even when it would be reasonable to choose an arbitrary small $\epsilon>0$, we aim to approximate it using the LSM estimator.\\
-
-Fixed $\epsilon$, we call $\mathcal{V}=\{\Delta V_i^\epsilon\}_{i=1}^n$ to the set of $n$ error transitions where for each measurement $X_i$, we have that $V_i=X_i-p_i^\epsilon$.
+%
+%Fixed $\epsilon$, we call $\mathcal{V}=\{\Delta V_i^\epsilon\}_{i=1}^n$ to the set of $n$ error transitions where for each measurement $X_i$, we have that $V_i=X_i-p_i^\epsilon$.
 $\mathcal{P}=\{p_i^\epsilon\}_{i=1}^n$ is the corresponding set of forecasts.\\
-If we also fix $\theta_0$ and $\alpha$, we can define the set of indexes $\mathbf{I}=\{i\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\theta_0\}$ and $\mathbf{J}=\left\{j\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\frac{\theta_0\alpha}{\epsilon}\right\}$.
+%If we also fix $\theta_0$ and $\alpha$, we can define the set of indexes $\mathbf{I}=\{i\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\theta_0\}$ and $\mathbf{J}=\left\{j\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\frac{\theta_0\alpha}{\epsilon}\right\}$.
 From the definition of $\theta_t$, we have that for $\epsilon<<1$, and $p_t=\epsilon$ or $p_t=1-\epsilon$, the approximation $\theta_t\approx\frac{\theta_0\alpha}{\epsilon}$ holds.
 Then, for $\epsilon$ small enough, $\mathbf{J}$ can be approximated by $$\mathbf{J}\approx\tilde{\mathbf{J}}=\{j\in\{1,\dots,n\}:p_j^\epsilon\in\{\epsilon,1-\epsilon\}\}.$$
-Now, coming back to the definition of $\theta_t$, we have that it is more likely that $\theta_t=\theta_0$ if $p_t^\epsilon\approx\frac{1}{2}$.
+%Now, coming back to the definition of $\theta_t$, we have that it is more likely that $\theta_t=\theta_0$ if $p_t^\epsilon\approx\frac{1}{2}$.
 Then, we can approximate $\mathbf{I}$ by $$\mathbf{I}\approx\tilde{\mathbf{I}}=\left\{i\in\{1,\dots,n\}:p_i\in(\gamma,1-\gamma)\right\},\ \gamma\approx\frac{1}{2},\ \gamma<\frac{1}{2}.$$
-We do not see signification differences in the LSM estimator for all $\gamma\in(0.1,0.3)$.
+%We do not see signification differences in the LSM estimator for all $\gamma\in(0.1,0.3)$.
 If $\gamma>0.3$, the reduction in the number of samples makes variations in the LSM estimator.
@@
 
-\subsubsection{Negative Log-Likelihood Minimization in $V$ Space} \label{Sec:MinLH}
-
-To find the optimal parameters, we minimize the negative log-likelihood using the derivative-free function \textit{fminsearch} from MATLAB R2019b over the parameters $(\theta_0,\alpha)$.
+\subsubsection{Negative log-likelihood minimization in the $V-$space} \label{Sec:MinLH}
+
+To find the optimal parameters, we minimize the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) using the derivative-free function \textit{fminsearch} from MATLAB R2019b over the parameters $(\theta_0,\alpha)$.
 At each step of the iteration, we:
@@
 
-\subsubsection{Negative Log-Likelihood Minimization in $Z$ Space} \label{Sec:MinLHL}
-
-Let $\{\Delta V_i\}_{i=1}^n$ be the set of all error transitions, and $\psi(\theta_0,\alpha,\Delta V)$ the Lamperti transform.
-Notice that the Lamperti transitions $\{\Delta Z_i\}_{i=1}^n$ depend on $(\theta_0,\alpha)$ because $$\{\Delta Z_i\}_{i=1}^n=\psi(\theta_0,\alpha,\{\Delta V_i\}_{i=1}^n).$$
-Then, if we compute $$\max_{(\theta_0,\alpha)}\mathbf{L}(\theta_0,\alpha,\{\Delta Z_i\}_{i=1}^n),$$
-we are not computing a MLE in the classical sense, as the data is changing with the parameters. However, we can try to find a fixed point ${\color{blue}(\theta_0^*,\alpha^*)}$ such that
-\begin{equation}
-{\color{blue}(\theta_0^*,\alpha^*)}=\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{blue}\theta_0^*},{\color{blue}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
+\subsubsection{Negative log-likelihood minimization in the $Z-$space} \label{Sec:MinLHL}
+
+Let $v^{M,N+1}$ be the observed data, and $h( v_{j,i};\bm{\theta})$ the Lamperti transform of the observation $v_{j,i}$.
+The transformed observations $z^{M,N+1}$ depend on the parameter $\bm{\theta}$.\\
+The problem of maximizing the approximated Lamperti log-likelihood (\ref{loglikelihoodZ}), i.e.,  $$\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta}; z^{M,N+1}\right),$$
+is not totally defined as the data $z^{M,N+1}$ depend on $\bm{\theta}$. However, we propose to find a fixed point $\bm{\theta}^*$ such that
+\begin{equation}
+\bm{\theta}^*=\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=1}^{M,N}\right).
 \label{FP}
 \end{equation}
-In this point, the likelihood has a maximum for the data set corresponding to that point.
-
-We are interested in finding the solution of (\ref{FP}). We have that, if $(\theta_0^*,\alpha^*)$ is a solution of (\ref{FP}), then
+{\color{red}In this point, the likelihood has a maximum for the data set corresponding to that point.}
+We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
 \begin{equation*}
-(\theta_0^*,\alpha^*)-\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right)=0.
+\bm{\theta}^*-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=1}^{M,N}\right)=0.
 \end{equation*}
-Given a pair $(\theta_0^{*},\alpha^{*})$, we call $(\theta_0^{**},\alpha^{**})$ to the solution of
+Given $\bm{\theta}^*=(\theta_0^*,\alpha^*)$, we call $\bm{\theta}^{**}=(\theta_0^{**},\alpha^{**})$ to the solution of
 \begin{equation*}
-\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
+\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=1}^{M,N}\right).
 \end{equation*}
-For each $(\theta_0^{*},\alpha^{*})$, we define the relative error function
-\begin{equation*}
-\Psi(\theta_0^{*},\alpha^{*})=\frac{|\theta_0^{*}-\theta_0^{**}|}{|\theta_0^{*}|}+\frac{|\alpha^{*}-\alpha^{**}|}{|\alpha^{*}|}
-\end{equation*}
-and claim that $(\theta_0^*,\alpha^*)$ is a fixed point iff $\Psi(\theta_0^*,\alpha^*)=0$.
-
-\subsubsection{Additional Parameter $\delta$}
-
-{\color{red}[I am not sure if we should introduce this parameter here, of in some previous section].} We observe that for each day, the error at time $t=0$ is not zero.
-However, by construction of the forecast, we may assume that for some time in the past $t_\delta<0$, the error $V_{t_\delta}=0$.\\
+For each $\bm{\theta}^*$, we define the relative error function $\Psi:\R^+\times\R^+\to\R^+$ as
+\begin{equation}
+\Psi(\bm{\theta}^*)=\frac{|\theta_0^*-\theta_0^{**}|}{|\theta_0^*|}+\frac{|\alpha^*-\alpha^{**}|}{|\alpha^*|},
+\label{eq:rel_error}
+\end{equation}
+and remark that $\bm{\theta}^*$ is a fixed point if and only if $\Psi(\bm{\theta}^*)=0$.
+To find minimizers for $\Psi$, we proceed in the same way as described in subsection (\ref{Sec:MinLH}), but using Gaussian surrogate densities.
+
+\subsection{Model specification with the additional parameter $\delta$}
+
+We observe that for most days, the forecast error at time $t_{j,0}=0$ is not zero.
+According to the forecasts procedure, we may assume that there is a time in the past $t_{j,-\delta}<t_{j,0}$, such that the forecast error $V_{j,-\delta}=0$.\\
+
+For any $j=1, \ldots, M$, we extrapolate backward linearly the truncated prediction function to get its value at time $-\delta$,$p_{j,-\delta}$, and set $v_{t_{j,-\delta}}=0$.
+We assume that the initial transition $(V_{j, 0}|v_{j,-\delta};\bm{\theta},\delta)$
+has a Beta distribution and apply to it the same moment matching method used above.
+Given a starting value for $\bm{\theta}$, we obtain the initial estimation for $\delta$ solving the following problem
+\begin{equation}
+\delta\approx\arg\max_{\delta}\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,-\delta};\bm{\theta},\delta\right),
+\label{eq:likelihood_delta}
+\end{equation}
+where $\mathcal{L}_\delta$ is the $\delta-$likelihood.
+To solve this problem, we repeat the steps described in subsection (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation for $p_{j,-\delta}$.\\
 \quad\\
-We extrapolate linearly $p(t)$ considering the truncation at $\epsilon$, so we can evaluate $p(t_{-\delta})$, and assume that $V(t_{-\delta})=0$.
-Then, for each day $j$, we have an initial transition $(V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta)$.
-We assume again that it is Beta and apply the same moment matching as for the rest of transitions.
-With our initial guess for $\bm{\theta}$, we can construct our initial guess for $\delta$ solving the problem
-
-\begin{equation*}
-\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
-\label{likelihood_delta}
-\end{equation*}
-To solve this minimization problem, we repeat the steps described in section (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation.
-
-%---END SECTION 4---
-
-%---BEGIN SECTION 5---
-\section{Model Comparison} \label{Section_5}
-
-We compare two candidate models to find the best-fit that maximizes the retained information,
+As remarked, we extend the statistical model (\ref{likelihood}) to include the extra parameter $\delta$. The complete likelihood, $\mathcal{L}_c$, is given by
+\begin{equation}
+\mathcal{L}_c\left(\bm{\theta},\delta; v^{M,N +1}\right)=\mathcal{L}\left(\bm{\theta}; v^{M,N +1}\right)\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right).
+\label{eq:complete_LH}
+\end{equation}
+As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the complete likelihood (\ref{eq:complete_LH}).
+
+%---END SECTION 5---
+
+%---BEGIN SECTION 6---
+
+\section{Application to the April-December 2019 Uruguay wind and forecast dataset} \label{Section_6}
+
+Our statistical analysis starts with partitioning the 147 segments of normalized wind power production, each 24-hour long.
+We select 73 non-contiguous segments for the models' calibration procedure, assigning them to the training set.
+The other 74 non-contiguous segments compose the test set.
+Such an allocation mechanism guarantees independence among the segments, matching the assumption we did in Section \ref{Section_5} to formulate the statistical models.
+
+{ \color{red} Show that 24h is enough to ensure independence?}
+All the following results involving a single provider refer to Provider A.
+Also, all calibrations involve the training sets and all simulations, the test sets.
+Following the instruction for the initial guesses from section $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.
+
+\subsection{Calibration of the approximate negative log-likelihood in the $V-$space}
+
+As an auxiliary verification, we plot the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) as a function of the parameters, and we use additional minimization functions from MATLAB R2019b.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.eps}
+\caption{Negative log-likelihood's level sets. All optimal values are located over the curve $\theta_0\alpha=0.097$.}
+\label{fig:neg-LL}
+\end{figure}
+On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood.
+The numerical values of each important point can be seen in Table (\ref{tab:optimal_values}).
+We set $\bm{\theta}^V=(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood reaches its minimum value.
+\begin{table}[H]
+\centering
+\begin{tabular}{lccc}
+\toprule
+ & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
+ \midrule
+ Initial guess & 1.54 & 0.070 & 0.111 \\
+ fminsearch & 1.14 & 0.076 & 0.097 \\
+ fmincon & 1.58 & 0.062 & 0.097 \\
+ fminunc & 1.54 & 0.063 & 0.097 \\
+ evaluations & 1.93 & 0.050 & 0.097 \\
+ \bottomrule
+\end{tabular}
+\caption{Value points from Figure \ref{fig:neg-LL}.}
+\label{tab:optimal_values}
+\end{table}
+Observe that all the local (possibly global) minimizers are located in curve $\theta_0\alpha=0.097$.
+We will explain this effect later, but it is a consequence of Markovianity and the indistinguishable observed transitions.
+
+\subsection{Calibration of the approximate negative log-likelihood in the $Z-$space}
+
+%{\color{red} This part still may change.} As we are working in a low dimensional space, we can evaluate the relative error function (\ref{eq:rel_error}) in all the space of interest.
+%
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
+%\caption{Relative error function's level sets.}
+%\label{fig:neg-LLL}
+%\end{figure}
+%In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets for the relative error function (\ref{eq:rel_error}).
+The center deep green band is the set $\mathbb{A}$ such that $\Psi(\bm{\theta})<0.1$ if $\bm{\theta}\in\mathbb{A}$, it is the set of fixes-points candidates.
+The set of fixed-points candidates which also satisfies the condition of lying over the line $\theta_0\alpha=0.097$ is non-empty, i.e., $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.097\}\neq\emptyset.$$
+
+We obtain $(\theta_0^Z,\alpha^Z)=(1.87,0.043)$ as a minimizer for the relative error function (\ref{eq:rel_error}).\\
+\quad\\
+To verify and compare this two vector of parameters, (i.e., $(\theta_0^V,\alpha^V)$ and $(\theta_0^Z,\alpha^Z)$), we simulate error paths in the $V-$space.
+We simulate five error paths for each day in the test set and construct histograms with the transitions.
+The histograms can be seen in Figure (\ref{fig:hists}).
+We observe a slightly better approximation using $(\theta^Z_0,\alpha^Z)$.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic_noDelta/Optimal.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic_noDelta/Lamperti_Optimal.eps}
+\caption{Probability histograms for the error transitions.
+Using the Provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE.
+On the left, simulations using $(\theta_0^V,\alpha^V)$.
+On the right, simulations using $(\theta_0^Z,\alpha^Z)$.}
+\label{fig:hists}
+\end{figure}
+
+\subsection{Model comparison} \label{Model_Comp}
+
+We compare two candidate models to find the best-fit that maximizes the retained information:
 \begin{itemize}
-  \item Model 1: This model does not feature derivative tracking.
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&=  - \theta_0 (X_t - p_t) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{Model1}
+  \item Model 1: This model does not feature derivative tracking:
+\begin{equation}
+\begin{cases}
+\dif X_t&=-\theta_0 (X_t - p_t) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]  \\
+X_0&=x_0\in (0,1),
+\end{cases}.  \label{Model1}
 \end{equation}
@@
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= \big(\dot{p}_t  - \theta_t (X_t - p_t) \big) dt +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} dW_t\,, \quad t \in [0,T]  \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{Model2}
-\end{equation}
- with $\theta_0 > 0, \, \alpha > 0$ and .
+\begin{cases}
+\dif X_t&= \big(\dot{p}_t  - \theta_t (X_t - p_t) \big) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]\\
+X_0&=x_0\in (0,1) \,,
+\end{cases}.  \label{Model2}
+\end{equation}
+ with $\theta_0 > 0, \, \alpha > 0$ and $\theta_t$ satisfying the condition \eqref{Assumption:3} .
 \end{itemize}
+To show the better performance of Model 2, we calculate the Akaike information criterion (AIC) and Bayesian information criterion (BIC) for each provider, each model, and different proxies densities.
+Table (\ref{tab:model_comparison}) summarizes this computations.
+We can observe that the best fitting is achieved with Model 2 and Beta proxies.
 
@@
 \end{tabular}
-\caption{We compare the different models based on information criterion. \add }
+\caption{We compare the different models based on information criterion.}
 \label{tab:model_comparison}
 \end{table}
-%---END SECTION 5---
-
-%---BEGIN SECTION 6---
-\section{Forecast Provider Comparison} \label{Section_6}
-We compare forecasts from two different companies for the same period.
+
+\subsection{Forecast providers comparison} \label{Forecast_Comp}
+We compare forecasts from three different companies for the same period.
 \begin{table}[H]
@@
 
+{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
+How much data do we need to achieve enough accuracy for the estimates of the two parameters?
+Generally, such accuracy is application dependent.}
+
+\subsection{Calibration of Model 2 with additional parameter $\delta$}
+
+After calibrating Model 2 on the training set using the complete likelihood (\ref{eq:complete_LH}), we can generate simulations of the wind power production for the time horizon of interest.
+Figure (\ref{fig:simulation_paths}) shows five simulated paths of the wind power production for each day of interest.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/1.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/2.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/3.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/4.eps}
+\caption{Four arbitrary days with five simulated wind power production paths each. }
+\label{fig:simulation_paths}
+\end{figure}
+On the basis of the approximate MLEs for Model 2, we can obtain empirical pointwise confidence bands for the wind power production.
+Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/1.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/2.eps}\\
+\quad\\
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/3.eps}
+\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/4.eps}
+\caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.93,0.050,0.090)$. Blue line: real production.}
+\label{fig:confidence_bands}
+\end{figure}
+
+\subsubsection{Value of $\delta$}
+As a final verification, we study the behavior of $\delta$ as function of $\bm{\theta}$.
+Given a vector of parameters, we calculate an initial guess for $\delta$ solving problem (\ref{eq:likelihood_delta}).
+Even when it is a guess, it helps us to understand qualitatively the meaning of this additional parameter.\\
+\quad\\
+We choose as domain the most significant values of $\theta_0$ and $\theta_0\alpha$, regarding the previous numerical results. In Figure (\ref{fig:delta}) we can observe that:
+\begin{itemize}
+\item The initial time $\delta$ decreases as $\theta_0\alpha$ increases.
+This is a consequence of the increment in the diffusion as $\theta_0\alpha$ increases.
+As there is more diffusion, it is needed less time for the initial transition density to cover the initial error observations.
+\item The initial time $\delta$ increases as $\theta_0$ increases.
+As we increment $\theta_0$, also the mean reversion becomes larger and reduces the variance for the initial transition density.
+Then, it is needed more time for the initial transition density to cover the initial error observations.
+\end{itemize}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/delta/contour_delta.eps}
+\caption{Initial value for $\delta$ as a function of the elements of the parameter vector $\bm{\theta}$.}
+\label{fig:delta}
+\end{figure}
+
 %---END SECTION 6---
@@
 %---BEGIN SECTION 7---
-\section{Results} \label{Section_7}
-
-\subsection{Initial guesses}
-
-Following the instruction for the initial guesses from section $\ref{opt_sec}$, we get the initial guesses $(\theta_0,\alpha,\delta)\approx(1.2,0.1,0.6)$.
-
-\subsection{Negative Log-Likelihood in $V$ Space}
-
-We plot the Negative Log-Likelihood as a function of the parameters.
-The plots can be seen in Figure (\ref{fig:neg-LL}).
-We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.jpg}
-\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
-\label{fig:neg-LL}
-\end{figure}
-On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood. The thick violet band is the region where the function reaches its minimums.\\
-We can see the \textbf{initial guess} point, the result of three different \textbf{optimization tools} from MATLAB, and the minimum point that we found from the \textbf{evaluations} that generate the plot.
-\begin{table}[]
-\centering
-\begin{tabular}{lccc}
-\toprule
- & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
- \midrule
- Initial guess & 1.544 & 0.072 & 0.111 \\
- fminsearch & 1.278 & 0.076 & 0.097 \\
- fmincon & 1.577 & 0.062 & 0.097 \\
- fminunc & 1.544 & 0.063 & 0.097 \\
- evaluations & 1.930 & 0.050 & 0.097 \\
- \bottomrule
-\end{tabular}
-\caption{Different important points for provider A using model 2 and beta proxies.}
-\end{table}
-
-\subsection{Negative Log-Likelihood in $Z$ Space}
-
-We plot the Negative Log-Likelihood as a function of the parameters.
-The plots can be seen in Figure (\ref{fig:neg-LL}).
-We used all the training data (127 days of data) to construct and optimize the Negative Log-Likelihood.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
-\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
-\label{fig:neg-LLL}
-\end{figure}
-In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets of the error function $\Psi$.\\
-The center deep green band is the set $\mathbb{A}$ such that $\Psi(\mathbb{A})\in[0.05,0.1]$. We do not achieve relative error smaller than 0.05.\\
-We observe a particular behavior over the curves $\theta_0\alpha=k\in\R^+$. However, it can be a numeric effect.\\
-We also observe that: $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.083\}\neq\emptyset.$$
-On the right, we observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.038$ from the error SDE.\\
-We choose $(\theta_0,\alpha)=(2.200,0.038)$.\\
-We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".
-
-\subsection{Main guesses}
-
-{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models (if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.)}
-
-{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
-How many data we need to achive enough accuracy for the estimates of the two parameters?
-Generally, such accuracy is application dependent}
-
- We are able to obtain the parameters based on the complete data sets. Using the different models variations, we are able to simulate wind power production given a forecast. We see in figures ()-()
-five possible wind power production paths for each model.\\
-
-In Figures ()-(), we show point-wise empirical confidence bands for the different models.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
-\caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
-Forecast is from Uruguay pertaining to  year 2019.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/1.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/2.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/3.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/4.eps}
-\caption{We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$.
-Actual production plotted in retrospect.
-Forecast and data is from Uruguay pertaining to  year 2019.}
-\end{figure}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
-\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Lamperti_Optimal.eps}
-\end{figure}
-
-We can see two histograms for the error transitions. On the left, using $(\theta_0^E,\alpha^E)$, while on the right, using $(\theta_0^L,\alpha^L)$.
-
-%---END SECTION 7---
-
-%---BEGIN SECTION 8---
-\section{Conclusions} \label{Section_8}
+
+\section{Conclusions} \label{Section_7}
 
@@
 
-We were also able to compare two different forecast providers with respect to their real-world performance on the aggregated data set and on specific wind farm sites.
+We were also able to compare three different forecast providers with respect to their real-world performance on the aggregated data set and on specific wind farm sites.
 Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.
-%---END SECTION 8---
+
+%---END SECTION 7---
 
 %---BEGIN APPENDIX---
+
 \section{Appendix} \label{Appendix}
 
-\section{The model}
+\subsection{The model}
 For a time horizon $T>0$ and  a parameter $\alpha > 0$ and $(\theta_t)_{t\in[0,T]}$ a positive deterministic  function,  let us consider the model  given by
 \begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= \big(\dot p_t - \theta_t (X_t-p_t)  \big)dt  +\sqrt{2 \alpha \theta_t X_t (1-X_t)} dW_t\,, \quad t\in[0,T] \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{eq:model}
+\begin{cases}
+\dif X_t &= \big(\dot p_t - \theta_t (X_t-p_t)  \big)\dif t  +\sqrt{2 \alpha \theta_0 X_t (1-X_t)} \dif W_t, \quad t\in(0,T) \\
+X_0&= x_0\in [0,1],
+\end{cases}.  \label{eq:model}
 \end{equation}
@@
 \begin{equation}\label{eq:eds1}
-X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)ds  + \int_0^t\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s, \quad x_0>0.
+X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)\dif s  + \int_0^t\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s, \quad 0<x_0<1.
 \end{equation}
@@
 \begin{align*}
-\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)ds \\
-&+ \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_s|X_s(1-X_s)|} dW_s + \alpha \int_0^t \theta_sg_n(|X_s|)|X_s(1-X_s)|ds.
+\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)\dif s \\
+&+ \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s + \alpha \theta_0 \int_0^t  g_n(|X_s|) |X_s(1-X_s)|\dif s.
 \end{align*}
@@
 $$
-\mathbb E[\psi_n(X_t)]\le \psi_n(x_0) +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \big)ds + \frac{2\alpha}{n}\int_0^t \theta_s\mathbb E |1-X_s|ds.
+\mathbb E[\psi_n(X_t)]\le \psi_n(x_0) +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \big)\dif s + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E |1-X_s|\dif s.
 $$
@@
 $$
-\mathbb E[|X_t| -X_t ]\le \int_0^t \theta_s \mathbb E[|X_s| - X_s ]ds.
+\mathbb E[|X_t| -X_t ]\le \int_0^t \theta_s \mathbb E[ X_s - |X_s| ]\dif s.
 $$
@@
 
-\begin{Thm}
+\begin{Thm}\label{thm:mod2}
 Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
-Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$. Assume in addition that
-\begin{equation}\label{Assumption:2}
-0<\alpha < \frac 12\quad \mbox{ and }\quad \forall  t\in[0,T],\;\; \alpha\theta_t\le \dot p_t +\theta_tp_t \le (1-\alpha)\theta_t \tag{B}. 
+Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$.
+Assume in addition that for all $t\in[0,T]$,  $p_t\in]0,1[$ and that
+\begin{equation}\label{Assumption:3}
+\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{B}. 
 \end{equation}
@@
 $$
-\frac{dX_t}{X_t}=\left( \frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)\dif t  +\sqrt{\frac{2\alpha \theta_t(1-X_t)}{X_t}} \dif W_t 
+\frac{\dif X_t}{X_t}= \left(\frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)\dif t  +\sqrt{\frac{2\alpha \theta_0 (1-X_t)}{X_t}} \dif W_t 
 $$  
@@
 $$
-X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_s(p_s-\alpha)}{X_s}ds-(1-\alpha)\int_0^t\theta_sds + M_t\Big),
-$$
-where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_s(1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_t(p_t-\alpha)\ge0$, we deduce that
-$$
-X_t\ge x_0\exp\Big(-(1-\alpha)\int_0^t\theta_sds + M_t\Big).
+X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \theta_0 \alpha}{X_s}\dif s+\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\Big),
+$$
+where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_0 (1-X_s)}{X_s}} \dif W_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \theta_0 \alpha\ge0$, we deduce that
+$$
+X_t\ge x_0\exp\Big(\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\Big).
 $$
@@
 $$
-dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \theta_tY_t(1-Y_t)} dW_t 
+\dif Y_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)\dif t  -\sqrt{2\alpha \theta_0 Y_t(1-Y_t)} \dif W_t 
 $$
 we deduce using similar arguments as above 
-$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \theta_t\ge 0$.
+$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \theta_0 \ge 0$.
  \end{proof}
 
-\section{New model}
-In what follows we adapt the proof of the above theorem for the new model 
-\begin{equation}
-  \left\{
-  \begin{array}{@{}rl@{}}
-    dX_t \!\!\!&= \big(\dot p_t - \theta_t (X_t-p_t)  \big)dt  +\sqrt{2 \alpha \red{\theta_0} X_t (1-X_t)} dW_t\,, \quad t\in[0,T] \\
-   X_0  \!\!\!&=  x_0\in [0,1] \,,
- \end{array}\right.  \label{eq:model2}
-\end{equation}
-
-\begin{Thm}\label{thm:mod2}
-Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
-Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$.
-Assume in addition that for all $t\in[0,T]$,  $p_t\in]0,1[$ and that
-\red{
-\begin{equation}
-\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
-\end{equation}
-}
- Then, $\tau_0=\tau_1=+\infty$ a.s.
-\end{Thm}
-
-\begin{proof}
-For $t\in[0,\tau_0[$, we have 
-$$
-\frac{dX_t}{X_t}= \left(\frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)dt  +\sqrt{\frac{2\alpha \red{\theta_0}(1-X_t)}{X_t}} dW_t 
-$$  
-so that
-$$
-X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \red{\theta_0}\alpha)}{X_s}ds+\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big),
-$$
-where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_s(1-X_s)}{X_s}} dW_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \red{\theta_0}\alpha\ge0$, we deduce that
-$$
-X_t\ge x_0\exp\Big(\alpha\red{\theta_0}t-  \int_0^t\theta_sds + M_t\Big).
-$$
-By way of contradiction let us assume that  $\{\tau_0<\infty\}$, then letting $t\to \tau_0$ we deduce that $\lim_{t\to \infty} \mathbf 1_{\{\tau_0<\infty\}}M_{t\wedge \tau_0}=\mathbf -1_{\{\tau_0<\infty\}}\infty$ a.s.
-This leads to a contradiction since we know that continuous martingales likewise the Brownian motion cannot converge  almost surely to $+\infty$ or $-\infty$.
-It follows that $\tau_0=\infty$ almost surely.
-Next, recalling that  the process $(Y_t)_{t\geq 0}$  given by $Y_t=1-X_t$ is solution to
-$$
-dY_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)dt  -\sqrt{2\alpha \red{\theta_0}Y_t(1-Y_t)} dW_t 
-$$
-we deduce using similar arguments as above 
-$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \red{\theta_0}\ge 0$.
- \end{proof}
- \section{Answers to Renzo's questions} 
-{\color{blue}So, Theorem \ref{thm:mod2} answers the second question in slide 11.} The new condition \eqref{Assumption:3} that guarantees  for $(X_t)_{t\ge0}$ to stay in $]0,1[$ depends now on $\alpha$.
-I would keep condition \eqref{Assumption:3} as we have a proof for it.
-Moreover, if condition \eqref{Assumption:3} is satisfied, then  the orange condition in slide 8 is also satisfied
-since we have 
-$$
-\max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\ge \max\left(\frac{\frac{\alpha\theta_0}{2}+\dot p_t}{1-p_t},\frac{\frac{\alpha\theta_0}{2}-\dot p_t}{p_t}\right)
-$$
-which ensures that $Z$ don't hit the boundaries too according to Renzo's intuitive arguments.\\ 
-{\color{blue}Concerning, the first question on slide 11:} we can't apply Itô's formula, unless we are sure that the process don't hit the boundaries, that's why we have to assume  \eqref{Assumption:3} before using Itô's formula.
-In addition, as the diffusion coefficient of $X$  given by  $x\mapsto \sqrt{\frac{2\alpha \red{\theta_0}(1-x)}{x}}$  is strictly positive for all $x$ in the state space of $X$, namely $]0,1[$ under assumption \eqref{Assumption:3},  this is enough to ensure that the transformation between $Z$ and $X$ is bijective so that we deduce the existence and uniqueness of $Z$ from those of $X$.
-Otherwise the Lamperti transform is not valid if the state space of $X$ is $[0,1]$.
+Remark: As the diffusion coefficient of $X$  given by  $x \mapsto \sqrt{2 \alpha \theta_0 x(1-x)}$  is strictly positive for all $x \in  ]0,1[$, the condition \eqref{Assumption:3}  ensures that the transformation between $Z$ and $X$ is bijective, so that we deduce the properties of existence and uniqueness of $Z$ from those of $X$.
+The application of  It\^{o}'s formula in Section \ref{Section_4} is subjected to the condition \eqref{Assumption:3} that avoids the process $X$ hits the boundaries of the interval $ ]0,1[$, otherwise the Lamperti transform is not applicable.
+
+%---END APPENDIX---
 

### 2020-05-30 MATLAB_Files/autocorrelation_test.m

@@ -1,0 +1,98 @@
+close all;
+clear all;
+clc;
+
+% dataSet can be AWSTP (B), MTLOG (A) or UTEP5 (C).
+dataSet       = 'MTLOG';
+% epsilon can be 0.035 (B), 0.020 (A) or 0.028 (C).
+epsilon       = 0.020;
+% dataKind can be classic or comparable.
+dataKind      = 'comparable';
+train_data             = load_data_eps(epsilon,dataSet,dataKind);
+test_data              = load_data_eps_test(epsilon,dataSet,dataKind);
+[~, ~, table_complete] = load_data(dataSet);
+
+train_error = transpose(train_data.Error);
+test_error  = transpose(test_data.Error);
+all_error   = transpose(table_complete.Error);
+
+train_error_vec = train_error(:);
+test_error_vec  = test_error(:);
+all_error_vec   = all_error(:);
+L               = length(train_error_vec) + length(test_error_vec);
+all_error_vec   = all_error_vec(end-L+1:end);
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+figure;
+
+[acf,lags,bounds] = autocorr(train_error_vec,'NumLags',200);
+stem(lags,acf); xlabel('Lag'); ylabel('\rho(k)');
+hold on;
+% h = line(lags,bounds(1)*ones(length(acf),1));
+% h1 = line(lags,bounds(2)*ones(length(acf),1));
+% set(h,'color',[1 0 0]);
+% set(h1,'color',[1 0 0]);
+
+hold on;
+
+[acf,lags,bounds] = autocorr(test_error_vec,'NumLags',200);
+stem(lags,acf); xlabel('Lag'); ylabel('\rho(k)');
+% h = line(lags,bounds(1)*ones(length(acf),1));
+% h1 = line(lags,bounds(2)*ones(length(acf),1));
+% set(h,'color',[1 0 0]);
+% set(h1,'color',[1 0 0]);
+
+[acf,lags,bounds] = autocorr(all_error_vec,'NumLags',200);
+stem(lags,acf); xlabel('Lag'); ylabel('\rho(k)');
+% h = line(lags,bounds(1)*ones(length(acf),1));
+% h1 = line(lags,bounds(2)*ones(length(acf),1));
+% set(h,'color',[1 0 0]);
[…]

### 2020-05-30 MATLAB_Files/path_simulator_OPT.m

@@ -10,12 +10,12 @@ epsilon  = 0.020;
 dataKind = 'comparable';
 Table_Testing_Complete = load_data_eps_test(epsilon,dataSet,dataKind);
 whatToDo = 'optimal_value'; 
-% whatToDo = 'Optimal_Lamperti'; 
+whatToDo = 'Optimal_Lamperti'; 
 
 % PARAMETERS:
 % set(0,'defaultAxesFontSize',18);
-quantil  = 0;
-save     = 1;
+quantil  = 1;
+save     = 0;
 delta    = 13; % The time is delta*10 minutes.
 xlimit   = 1; % If this in 1, the plots start at time 0. Otherwise, at -delta.
 norm_lim = 0; % If 1, x=[0,1], if 0, x=[1PM 1PM].
@@ -33,8 +33,11 @@ if  strcmp(whatToDo,'optimal_value')
     theta_0 = 2.2210;
     alpha   = 0.0436;
 elseif  strcmp(whatToDo,'Optimal_Lamperti')
-    theta_0 = 2.200;
-    alpha   = 0.038;
+%     theta_0 = 2.200;
+%     alpha   = 0.038;
+% V2:
+    theta_0 = 1.8708;
+    alpha   = 0.0431;    
 else
     error('Wrong whatToDo script!');
 end
@@ -151,6 +154,12 @@ for i = 1 : height(Table_Testing_Complete)
             J = plot(t,X,'b'); J.LineWidth = 2;
             legend({'99% confidence interval', '90% confidence interval', '50% confidence interval',...
                 'Forecast', 'Real production'});
+%             legend({'99% confidence interval', '90% confidence interval', '50% confidence interval',...
+%                 'Forecast', 'Real production'},'location','southeast');
+%             legend({'99% confidence interval', '90% confidence interval', '50% confidence interval',...
+%                 'Forecast', 'Real production'},'location','northwest');
+%             legend({'99% confidence interval', '90% confidence interval', '50% confidence interval',...
+%                 'Forecast', 'Real production'},'location','southwest');
             
             xticks(t_ticks);
             datetick('x','HHPM','keepticks');

### 2020-05-30 LaTeX_Code/Paper/paper_1line.tex
Corrected small things in the paper

@@
 
-{\color{red} 2020 AMS Subject Classification: 60H10}
+{\color{red} 2020 AMS Subject Classification: 60H10, 62M20}
 
@@
 
+The rest of the paper is organized as follows.
 In Section \ref{Section_2}, we introduce the main characteristics of a real data set encompassing the normalized wind power production in Uruguay during the period April-December 2019, joint with the most accurate predictions, as highlighted in our posterior analysis, performed by one out of the three sources of forecast providers.
 The significant steps for constructing phenomenological models of the normalized wind power production and the forecast error based on stochastic differential equations are described in Section \ref{Section_3}.
-After reformulating the SDE for the forecast error in Section \ref{Section_4}, by applying the Lamperti transform that leads to a unit diffusion coefficient, we write down in Section \ref{Section_5} the expressions for the likelihood functions of the forecast error in its original space and in the Lamperti space.
+The application of the Lamperti transform with unknown parameters in Section \ref{Section_4} leads to model the forecast error through a stochastic differential equation with a unit diffusion coefficient.
+In Section \ref{Section_5} we write down the expressions for the likelihood functions of the forecast error in its original space and in the Lamperti space.
 We also derive simple approximations of the likelihood functions.
 Section \ref{Section_5} concludes with the description of the optimization algorithm to compute approximate maximum likelihood estimates, including the case where we expand the model comprising an initial transition from the time the forecast is performed to the time of the first forecast.
-In Section \ref{Section_6}, we apply our proposed parametric estimation procedure to the Uruguay wind and forecast dataset, comparing two alternative models and assessing, for the best candidate model, the performance of three different forecast providers.
+In Section \ref{Section_6}, we apply our proposed numerical estimation procedures to the Uruguay wind and forecast dataset, comparing two alternative models and assessing, for the best candidate model, the performance of three different forecast providers.
+Section \ref{Section_7} concludes the paper.
 The proofs of the existence, strong uniqueness, and boundedness of the solutions of the SDE used to model normalized wind power production and its forecast error are given in the Appendix.
@@
 A remarkable effect of removing the state dependency from the random noise term is to increase the numerical stability of the simulated paths of the transformed process.
-For this reason, some estimation methods of the unknown parameters of non-linear SDE models incorporated the use on the Lamperti's change of variable as part of a more complex approximation procedure (for example, the local linearization method in  \cite{shoz}, or the expansion method in \cite{ait}, later extended to multivariate diffusion in \cite{ait2}).
-
-We consider the following Lamperti transformation  
+For this reason, some estimation methods of the unknown parameters of non-linear SDE models incorporated the Lamperti's change of variable as part of a more complex approximation procedure (for example, in the case of one-dimensional diffusions, the local linearization method in  \cite{shoz}, or the expansion method in \cite{ait}, later extended to time-inhomogeneous SDEs in \cite{eglix}).
+% later extended to multivariate diffusion in \cite{ait2}).
+
+We consider the following Lamperti transform with unknown parameters
 %{\color{red} (Remind that continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
@@
 
-We can see in Figure (\ref{fig:LP_transitions}) how the Lamperti transformation modifies the forecast error transition histogram without curtailment displayed in Figure (\ref{fig:error_transitions}).
+We can see in Figure (\ref{fig:LP_transitions}) how the Lamperti transform modifies the forecast error transition histogram without curtailment displayed in Figure (\ref{fig:error_transitions}).
 
@@
 
-The shape of the forecast error transition histograms after the Lamperti transformation has much resemblance with a Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process Z.
+The shape of the forecast error transition histograms after applying the Lamperti transform has much resemblance with a Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process Z.
 
@@
 
-Closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
+However, closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
 Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
-Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.
- {\color{red} Rewrite: Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, consider Preston and Wood, then Egorov, and then Sorensen, remove the
- survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}, refer to time-homogeneous.}
+Several numerical techniques have been devised to obtain estimates for the unknown parameters of continuous-time SDE models with discrete observations (see, for example, \cite{prewo} for likelihood-based inference techniques, \cite{Sor} for an estimating function approach, to mention a few contributions).
+As explained in the next subsection, we have considered approximate likelihood methods, similar in spirit to \autocite[Section 11.4]{saso}.
 
@@
 The drift coefficient $a(Z_t; p_t, \dot{p}_t, \bm{\theta}) $ of the process $Z$ that satisfies (\ref{eq:stindepSDE2}) is nonlinear.
-After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i})$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} Z_t$ :\\
+After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i})$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} \left[Z_t\right]$ :\\
 \begin{equation}
@@
 \end{equation*}
-The approximate Lamperti log-likelihood $\tilde{\ell}_L\left(\cdot ; z^{V, N+1}\right)$ for the observed sample $z^{V, N+1}$ is given by
+The approximate Lamperti log-likelihood $\tilde{\ell}_L\left(\cdot ; z^{M, N+1}\right)$ for the observed sample $z^{M, N+1}$ is given by
 \begin{equation}
@@
 
-\item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with $\Delta v_{j,i}=v_{j,i+1}-v_{j,i}$ and length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
-$(V_{j,i+1}|v_{j,i})$ is a random variable which conditional mean can be approximated by the solution of the system
+\item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
+$(V_{j,i}|v_{j,i-1})$ is a random variable which conditional mean can be approximated for any $t\in [t_{j,i-1}, t_{j, i})$ by the solution of the system
 \begin{equation*}
 \begin{cases}
-\dif \E\left[V\right]_{j,i}&=-\theta_t\E\left[V\right]_{j,i}\dif t\\
-\E\left[V\right]_{j,i}(t_{j,i})&=v_{j,i},
+\dif \E\left[V\right]&=-\theta_t\E\left[V\right]\dif t\\
+\E\left[V\right](t_{j,i-1})&=v_{j,i-1},
 \end{cases}
 \end{equation*}
-evaluated in $t_{j,i+1}$, i.e., $\E\left[V\right]_{j,i}(t_{j,i+1})$.
-Then, the random variable $(V_{j,i+1}-\E\left[V\right]_{j,i}(t_{j,i+1}))$ has zero mean.
-If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i},t_{j,i+1}]$, then $\E\left[V(t_{j,i+1})\right]_{j,i}=v_{j,i}e^{-c\Delta}$.
+evaluated in $t_{j,i}$, i.e., $\E\left[V\right](t_{j,i})$.
+Then, the random variable $(V_{j,i}-\E\left[V\right](t_{j,i}))$ has zero mean.
+If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i-1},t_{j,i}]$, then $\E\left[V(t_{j,i})\right]=v_{j,i-1}e^{-c\Delta}$.
 If we have a total of $M\times N$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
@@
 \begin{split}
-c^*&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-\E\left[v\right]_{j,i}(t_{j,i+1})\right)^2\right]\\
-&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}e^{-c\Delta}\right)^2\right]\\
-&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right)^2\right].
+c^*&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-\E\left[V\right](t_{j,i})\right)^2\right]\\
+&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}e^{-c\Delta}\right)^2\right]\\
+&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right)^2\right].
 \end{split}
@@
 \begin{equation*}
-\frac{\partial}{\partial c}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right)^2\right]=\sum_{j=1}^M\sum_{i=0}^{N-1}2v_{j,i}\Delta\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right),
+\frac{\partial}{\partial c}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right)^2\right]=\sum_{j=1}^M\sum_{i=1}^{N}2v_{j,i-1}\Delta\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right),
 \end{equation*}
@@
 \begin{equation}
-c^{*}=\frac{\sum_{j=1}^M\sum_{i=0}^{N-1}v_{j,i}(v_{j,i}-v_{j,i+1})}{\Delta\cdot\sum_{j=1}^M\sum_{i=0}^{N-1}(v_{j,i})^2}.
+c^{*}=\frac{\sum_{j=1}^M\sum_{i=1}^{N}v_{j,i-1}(v_{j,i-1}-v_{j,i})}{\Delta\cdot\sum_{j=1}^M\sum_{i=1}^{N}(v_{j,i-1})^2}.
 \label{Eq-4}
@@
 
-Let $\{\Delta v_{j,i}\}_{j=1,i=1}^{M,N}$ be the set of error observation transitions, and $\psi(\Delta v_{j,i};\bm{\theta})$ the Lamperti transform for the transitions.
-The transformed observations transitions $\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}$ depend on the parameter $\bm{\theta}$.\\
-The problem of maximizing the  $$\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}\right),$$
-is not totally defined as the data $\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}$ depend on $\bm{\theta}$. However, we propose to find a fixed point $\bm{\theta}^*$ such that
-\begin{equation}
-\bm{\theta}^*=\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right).
+Let $v^{M,N+1}$ be the observed data, and $h( v_{j,i};\bm{\theta})$ the Lamperti transform of the observation $v_{j,i}$.
+The transformed observations $z^{M,N+1}$ depend on the parameter $\bm{\theta}$.\\
+The problem of maximizing the approximated Lamperti log-likelihood (\ref{loglikelihoodZ}), i.e.,  $$\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta}; z^{M,N+1}\right),$$
+is not totally defined as the data $z^{M,N+1}$ depend on $\bm{\theta}$. However, we propose to find a fixed point $\bm{\theta}^*$ such that
+\begin{equation}
+\bm{\theta}^*=\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
 \label{FP}
@@
 \begin{equation*}
-\bm{\theta}^*-\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right)=0.
+\bm{\theta}^*-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right)=0.
 \end{equation*}
@@
 \begin{equation*}
-\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right).
+\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
 \end{equation*}
-For each $\bm{\theta}^*$, we define the relative error function
-\begin{equation}
-\Psi(\bm{\theta}^*)=\frac{|\theta_0^*\alpha^*-\theta_0^{**}\alpha^{**}|}{|\theta_0^*\alpha^*|},
+For each $\bm{\theta}^*$, we define the relative error function $\Psi:\R^+\times\R^+\to\R^+$ as
+\begin{equation}
+\Psi(\bm{\theta}^*)=\frac{|\theta_0^*-\theta_0^{**}|}{|\theta_0^*|}+\frac{|\alpha^*-\alpha^{**}|}{|\alpha^*|},
 \label{eq:rel_error}
@@
 and remark that $\bm{\theta}^*$ is a fixed point if and only if $\Psi(\bm{\theta}^*)=0$.
+To find minimizers for $\Psi$, we proceed in the same way as described in subsection (\ref{Sec:MinLH}), but using Gaussian surrogate densities.
 
@@
 
-For any $j=1, \ldots, M$, we extrapolate backward linearly the truncated prediction function to get its value at time $-\delta$,$p_{j,-\delta}$, and set $v_{t_{j,-\delta}}=0$.
+For any $j=1, \ldots, M$, we extrapolate backward linearly the truncated prediction function to get its value at time $t_{j,-\delta}$, $p_{j,-\delta}$, and set $v_{t_{j,-\delta}}=0$.
 We assume that the initial transition $(V_{j, 0}|v_{j,-\delta};\bm{\theta},\delta)$
-has a Beta distribution and apply to it the same moment matching method used above.
-Given a starting value for $\bm{\theta}$, we obtain the initial estimation for $\delta$ solving the following problem
-\begin{equation}
-\delta\approx\arg\max_{\delta}\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,-\delta};\bm{\theta},\delta\right),
+has a Beta distribution and apply to it the same moment matching method used above. Given a vector of parameters $\bm{\theta}$, we estimate $\delta$ solving the following problem
+\begin{equation}
+\delta\approx\arg\max_{\delta}\tilde{\mathcal{L}}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,-\delta};\bm{\theta},\delta\right),
 \label{eq:likelihood_delta}
 \end{equation}
-where $\mathcal{L}_\delta$ is the $\delta-$likelihood.
-To solve this problem, we repeat the steps described in subsection (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation for $p_{j,-\delta}$.\\
+where $\tilde{\mathcal{L}}_\delta$ is the approximated $\delta-$likelihood.
+To solve this problem, we repeat the steps described in subsection (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation for $p_{j,-\delta}$ at each $j\in\{1,2,\dots,M\}$.\\
 \quad\\
-As remarked, we extend the statistical model (\ref{likelihood}) to include the extra parameter $\delta$. The complete likelihood, $\mathcal{L}_c$, is given by
-\begin{equation}
-\mathcal{L}_c\left(\bm{\theta},\delta; v^{M,N +1}\right)=\mathcal{L}\left(\bm{\theta}; v^{M,N +1}\right)\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right).
+As remarked, we extend the statistical model (\ref{likelihood}) to include the extra parameter $\delta$.
+The approximated complete likelihood $\tilde{\mathcal{L}}_c$, which estimates the vector $(\theta_0,\alpha,\delta)$, is given by
+\begin{equation}
+\tilde{\mathcal{L}}_c\left(\bm{\theta},\delta; v^{M,N +1}\right)=\tilde{\mathcal{L}}\left(\bm{\theta}; v^{M,N +1}\right)\tilde{\mathcal{L}}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right),
 \label{eq:complete_LH}
 \end{equation}
-As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the complete likelihood (\ref{eq:complete_LH}).
+where $\tilde{\mathcal{L}}\left(\bm{\theta}; v^{M,N +1}\right)$ is the approximation of (\ref{likelihood}).
+As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the approximated complete likelihood (\ref{eq:complete_LH}).
 
@@
 The numerical values of each important point can be seen in Table (\ref{tab:optimal_values}).
-We set $(\theta_0^E,\alpha^E)=(1.93,0.050)$, as it is where the negative log-likelihood reaches its minimum value.
+We set $(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood reaches its minimum value.
 \begin{table}[H]
@@
 
-{\color{red} This part still may change.} As we are working in a low dimensional space, we can evaluate the relative error function (\ref{eq:rel_error}) in all the space of interest.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
-\caption{Relative error function's level sets.}
-\label{fig:neg-LLL}
-\end{figure}
-In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets for the relative error function (\ref{eq:rel_error}).
+%{\color{red} This part still may change.} As we are working in a low dimensional space, we can evaluate the relative error function (\ref{eq:rel_error}) in all the space of interest.
+%
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
+%\caption{Relative error function's level sets.}
+%\label{fig:neg-LLL}
+%\end{figure}
+%In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets for the relative error function (\ref{eq:rel_error}).
 The center deep green band is the set $\mathbb{A}$ such that $\Psi(\bm{\theta})<0.1$ if $\bm{\theta}\in\mathbb{A}$, it is the set of fixes-points candidates.
 The set of fixed-points candidates which also satisfies the condition of lying over the line $\theta_0\alpha=0.097$ is non-empty, i.e., $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.097\}\neq\emptyset.$$
-We observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.097$ from the error SDE. We choose $(\theta_0^L,\alpha^L)=(2.45,0.040)$.\\
-{\color{red}We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".}\\
+
+We obtain $(\theta_0^Z,\alpha^Z)=(1.87,0.043)$ as a minimizer for the relative error function (\ref{eq:rel_error}) using \textit{fminsearch} from MATLAB R2019b.\\
 \quad\\
-To verify and compare this two vector of parameters, (i.e., $(\theta_0^E,\alpha^E)$ and $(\theta_0^L,\alpha^L)$), we simulate error paths in the $V-$space.
+To verify and compare this two vector of parameters, (i.e., $(\theta_0^V,\alpha^V)$ and $(\theta_0^Z,\alpha^Z)$), we simulate error paths in the $V-$space.
 We simulate five error paths for each day in the test set and construct histograms with the transitions.
 The histograms can be seen in Figure (\ref{fig:hists}).
-We do not observe any particular change in the behavior of the solution for there parameters.
+We observe a slightly better approximation using $(\theta^Z_0,\alpha^Z)$.
 
@@
 Using the Provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE.
-On the left, simulations using $(\theta_0^E,\alpha^E)$.
-On the right, simulations using $(\theta_0^L,\alpha^L)$.}
+On the left, simulations using $(\theta_0^V,\alpha^V)$.
+On the right, simulations using $(\theta_0^Z,\alpha^Z)$.}
 \label{fig:hists}
@@
 
-\subsection{Model comparison} \label{Model_Comp}
+\subsection{Model comparison and assessment of the forecast providers} \label{Model_Comp}
 
@@
 \end{itemize}
-To show the better performance of Model 2, we calculate the Akaike information criterion (AIC) and Bayesian information criterion (BIC) for each provider, each model, and different proxies densities.
-Table (\ref{tab:model_comparison}) summarizes this computations.
-We can observe that the best fitting is achieved with Model 2 and Beta proxies.
+To show the better performance of Model 2, we have computed the Akaike information criterion (AIC) and the Bayesian information criterion (BIC) for the two considered models, and any combination of the three different forecast providers with the three approximate likelihood methods.
+Table (\ref{tab:model_comparison}) summarizes these results, also reporting the estimate of the variability diffusion coefficient $\alpha \theta_0$.
+It is worth observing that the best fitting is achieved with Model 2 and adopting Beta distributions as proxies of the transition densities.
 
@@
 \end{tabular}
-\caption{We compare the different models based on information criterion.}
+\caption{Model comparison based on Akaike and Bayesian information criteria.}
 \label{tab:model_comparison}
@@
 
-\subsection{Forecast providers comparison} \label{Forecast_Comp}
-We compare forecasts from three different companies for the same period.
+%\subsection{Forecast providers comparison} \label{Forecast_Comp}
+The optimal estimates of the parameters of Model 2, for the three forecast providers, when using Beta surrogates for the transition density are presented next:
 \begin{table}[H]
@@
 \end{tabular}
-\caption{Optimal parameters for different providers using Model 2 with Beta proxies.}
+\caption{Optimal parameters for the three different forecast providers using Model 2 with Beta proxies.}
 \label{tab:forcast_comparison}
@@
 
-{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
+%{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
 How much data do we need to achieve enough accuracy for the estimates of the two parameters?
@@
 \end{figure}
-On the basis of the approximate MLEs for Model 2, we can obtain empirical pointwise confidence bands for the wind power production.
-Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
+Once derived optimal estimates of the parameters of the complete likelihood for Model 2, we obtain empirical pointwise confidence bands for wind power production.
+Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for wind power production for each day of interest, assuming Model 2 specification, a given forecaster, and 5000 simulations per day.
 
@@
 \begin{equation}\label{prop:fm}
-\mathbb E[ \sup_{t\in[0,T]}|X_t|^p]<\infty.
+\mathbb E\left[ \sup_{t\in[0,T]}|X_t|^p\right]<\infty.
 \end{equation}
@@
 $$
-\mathbb E[\psi_n(X_t)]\le \psi_n(x_0) +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \big)\dif s + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E |1-X_s|\dif s.
+\mathbb E\left[\psi_n(X_t)\right]\le \psi_n(x_0) +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \right)\dif s + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E |1-X_s|\dif s.
 $$
@@
 $$
-\mathbb E[|X_t|]\le x_0 +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E|X_s| \big)\dif s.
+\mathbb E\left[|X_t|\right]\le x_0 +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E|X_s| \right)\dif s.
 $$
@@
 $$
-\mathbb E[|X_t| -X_t ]\le \int_0^t \theta_s \mathbb E[ X_s - |X_s| ]\dif s.
+\mathbb E\left[|X_t| -X_t \right]\le \int_0^t \theta_s \mathbb E\left[ X_s - |X_s| \right]\dif s.
 $$
@@
 $$
-X_t=x_0\exp\Big(\int_0^t \frac{\dot p_s +\theta_sp_s- \theta_0 \alpha}{X_s}\dif s+\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\Big),
+X_t=x_0\exp\left(\int_0^t \frac{\dot p_s +\theta_sp_s- \theta_0 \alpha}{X_s}\dif s+\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\right),
 $$

### 2020-05-31 LaTeX_Code/Paper/paper_1line.tex
section 7

@@
 
-{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, model selection.}
-
-{\color{red} 2020 AMS Subject Classification: 60H10, 62M20}
+Keywords: Wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, numerical optimizaton, model selection.
+
+2020 AMS Subject Classification: 60H10, 62M20.
 
@@
 
-A view of the global discrepancy between the real production and the forecasted production, during the nine months observation period, is summarized through the forecast error histograms, Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
+A view of the global discrepancy between the real production and the forecasted production, during the nine months observation period, is summarized through the forecast error histograms in Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
 Low normalized generated power corresponds to the range $[0,0.3]$, mid-power refers to the range $(0.3,0.6]$, and high-power to the range $(0.6,1]$.
@@
 \includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
-\caption{Wind production forecast error histograms during the period April-December 2019: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
+\caption{Wind production forecast error histograms during the period April-December 2019: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
   \label{fig:data_curtailing}
@@
 \includegraphics[width=0.45\textwidth]{plots/AP.eps}
-\caption{Wind production forecast error histograms during the period April-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
+\caption{Wind production forecast error histograms during the period April-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
   \label{fig:data_after_clean}
@@
 \includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
-\caption{Forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
+\caption{Forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
 \label{fig:error_transitions}
@@
   \includegraphics[width=0.45\textwidth]{plots/31.eps}\includegraphics[width=0.45\textwidth]{plots/31_2.eps}
-  \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (graph on the left) and with derivative tracking (graph on the right).}
+  \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (plot on the left) and with derivative tracking (plot on the right).}
   \label{fig:derivative_tracking}
@@
 
-We can see in Figure (\ref{fig:LP_transitions}) how the Lamperti transform modifies the forecast error transition histogram without curtailment displayed in Figure (\ref{fig:error_transitions}).
+To summarize visually the effect of the Lamperti transform, we can see in the next Figure (\ref{fig:LP_transitions}) how the forecast error transition histograms (without curtailment) modify in comparison with Figure (\ref{fig:error_transitions}).
+
+In this case, the Lamperti transform has been applied using the optimal estimates of the parameters in the SDE model (\ref{VtSDE}), obtained applying our numerical procedure detailed later in subsection (\ref{opt_sec}).
 
@@
 \includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
-\caption{Lamperti transformed forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
+\caption{Lamperti transformed forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
   \label{fig:LP_transitions}
@@
 
-We have proposed a method to produce stochastic wind power forecasts based on parametric SDEs.
-This method is agnostic of the wind power forecasting technology.
-Using this method, we were able to simulate future wind power production paths and obtain confidence bands.
-We conclude that Model 2 is a best-fit model.
-It features time-derivative tracking of the forecast, time-dependent mean reversion parameter, and a more natural diffusion term.
-Moreover, the model preserves the asymmetry of wind power forecast errors and their correlation structure.
-
-We were also able to compare three different forecast providers with respect to their real-world performance on the aggregated data set and on specific wind farm sites.
-Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.
+In this work, we propose a method to assess the short-term forecast of the normalized wind power, which is agnostic of the wind power forecast technology.
+
+To this purpose, we built a phenomenological stochastic differential equation model for the forecast error of the normalized wind power production, with time-varying mean-reversion parameter in the linear drift coefficient, and state-dependent and time non-homogenous diffusion coefficient.
+We also used the Lamperti transform with unknown parameters to provide a version of the proposed model with a unit diffusion coefficient, increasing its stability properties.
+
+We used approximate likelihood-based methods for the calibration of the models, developing original algorithms to derive optimal estimates of the unknown parameters.
+The likelihood approach has allowed extending the SDE models in a very effective way, incorporating an early transition with an additional parameter that accounts for the uncertainty of the forecast at the beginning of each future period.
+As a result, we obtained a robust procedure for synthetic data generation that, using the available forecast input, allows embracing the future wind power production paths through empirical pointwise bands with prescribed confidence.
+
+On the basis of historical data of wind power production and forecast from different sources, our method comes up with an objective tool for forecast assessment and comparison, by performing the model selection stage.
+The application of the procedure of modeling, inference through numerical optimization, and model selection through information criteria, to the wind power production real dataset in Uruguay during April-December 2019, with three different providers, shown the excellent performance of our proposed model, that preserves the asymmetry of wind power forecast errors and their correlation structure.
+
+ We conclude that our SDE model, featuring the time-derivative tracking of the forecast prediction function, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward managing of renewable energies efficiently.
+This methodology paves the way for stochastic optimal control methods enabling principled decision making under uncertainty in the presence of complex energy matrix.
 

### 2020-05-31 LaTeX_Code/Paper/paper_1line.tex
abstract

@@
 
-Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price and operation scheduling of conventional power plant.
-We propose a data driven model based on parametric Stochastic Differential Equations (SDEs) to captures real-world asymmetric dynamics of wind power forecast errors.
-Our SDE framework incorporates time derivative tracking of the forecast, time-dependent mean reversion parameter and an improved diffusion term.
-We are able to simulate future wind power production paths and to get sharp confidence bands.
-The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of information criteria.
-We apply the model to historical Uruguayan wind power production data and forecasts on the year 2019.
+Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price, and operation scheduling of conventional power plants.
+We propose a data-driven model based on parametric Stochastic Differential Equations (SDEs) to capture the real asymmetric dynamics of wind power forecast errors.
+Our SDE framework features time-derivative tracking of the forecast, time-varying mean-reversion parameter, and an improved state-dependent diffusion term.
+The methodology we developed allows the simulation of future wind power production paths and to obtain sharp empirical confidence bands.
+All the procedure is agnostic of the forecasting technology and enables comparing different forecast providers.
+We apply the model to historical Uruguayan wind power production data and forecasts during the period April-December 2019.
 
@@
 
-Keywords: Wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, numerical optimizaton, model selection.
-
-2020 AMS Subject Classification: 60H10, 62M20.
+Keywords: Wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform,
+
+numerical optimizaton, model selection.
+
+2020 AMS Subject Classification: 60H10, 62M20, 65K10.
 
@@
 
-In this work, we propose a method to assess the short-term forecast of the normalized wind power, which is agnostic of the wind power forecast technology.
+In this work, we propose a methodology to assess the short-term forecast of the normalized wind power, which is agnostic of the wind power forecasting technology.
 
@@
 
- We conclude that our SDE model, featuring the time-derivative tracking of the forecast prediction function, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward managing of renewable energies efficiently.
+ We conclude that our SDE model, featuring the time-derivative tracking of the forecast, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward managing of renewable energies efficiently.
 This methodology paves the way for stochastic optimal control methods enabling principled decision making under uncertainty in the presence of complex energy matrix.

### 2020-05-31 LaTeX_Code/Paper/paper_1line.tex
start intro

@@
 \section{Introduction}  \label{Section_1}
+
+Despite the Covid-19 pandemic caused ``the biggest shock to the global energy system in more than seven decades'' and the recent report released on April 30, 2020, by the International Energy Agency (\url{https://www.iea.org/reports/global-energy-review-2020}) stresses that projections of energy demand will fall 6\% in 2020 - seven times the decline after the 2008 global financial crisis - it is emphasized that ``renewables are set to be the only energy source that will grow in 2020, with their share of global electricity generation projected to jump thanks to their priority access to grids and low operating cost'' (\cite{IEA}).
+
+Although the growth of renewables in electricity generation in 2020 is set to be lower than in previous years,  solar PV and wind are on track to help lift renewable electricity generation by 5\% in 2020, aided by higher output from hydropower.
+\\
+
+Wind and solar energy are expanding renewable generation capacity, experiencing record growth in the last years.
 

### 2020-05-31 LaTeX_Code/Paper/paper_1line.tex
Corrected the paper and added slides with unused results. Now, it is ready to be seen by Prof. Ahmed and Prof. Raul.

@@
 
-Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price, and operation scheduling of conventional power plants.
+Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization for electricity price, and operation scheduling of conventional power plants.
 We propose a data-driven model based on parametric Stochastic Differential Equations (SDEs) to capture the real asymmetric dynamics of wind power forecast errors.
@@
 Different methods have been applied to wind power forecasting.
-They can be generally categorized as follows: physical models, statistical methods, artificial intelligence methods and hybrid approaches.
+They can be generally categorized as follows: physical models, statistical methods, artificial intelligence methods, and hybrid approaches.
 The output of such methods is usually a deterministic forecast.
-Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters or through forecast ensembles.
-{\color{red} Expand discussion about works on probabilistic forecasting.} However, there is a lacking in simulating and producing data driven stochastic forecasts based on real-world performance of forecasting models.
+Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters, or forecast ensembles.
+{\color{red} Expand discussion about works on probabilistic forecasting.} However, there is a lack of simulating and producing data-driven stochastic forecasts based on forecasting models.
 It is crucial to capture the forecast's actual performance as it has been known that different forecasting technologies exhibit different behavior for different wind farms and seasons (\cite{chang}).
-This is due to many factors which forecast are challenged to capture such as the surrounding terrains of the wind farm and the condition of the blades such as icing, wear and tear or dirt.
+This is due to many factors that forecast are challenged to capture, such as the surrounding terrains of the wind farm and the condition of the blades such as icing, wear and tear, or dirt.
 It is known that complex terrains in both off shore and on shore locations decrease the accuracy of wind power forecasts significantly (\cite{schicker2017short}).
@@
 This is a natural consequence of wind power being non-negative and bounded by the maximum capacity of production.
-This is important as the associated cost to power forecast errors are also asymmetric due to different costs for up and down power regulations which are determined by the electricity market (\cite{tsitsiklis2015pricing}).
-
-We propose to model wind power forecasts errors using parametric stochastic differential equations (SDEs) whose solution defines a stochastic process.
+This is important as the associated cost to power forecast errors is also asymmetric due to different costs for up and down power regulations, which are determined by the electricity market (\cite{tsitsiklis2015pricing}).
+
+We propose to model wind power forecast errors using parametric stochastic differential equations (SDEs) whose solution defines a stochastic process.
 This resultant stochastic process describes the time evolution dynamics of wind power forecast errors while capturing properties such as a correlation structure and the inherent asymmetry.
-Additionally, the model we propose is agnostic of the forecasting technology and serves to complement forecasting procedures by providing a data driven stochastic forecast.
-Hence, we are able to evaluate wind power forecasts according to their real-world performance and we are able to compare different forecasting technologies.
-Most notably, we are able to simulate future wind power production given a deterministic wind power forecast.
+Additionally, the model we propose is agnostic of the forecasting technology and serves to complement forecasting procedures by providing a data-driven stochastic forecast.
+Hence, we can evaluate wind power forecasts according to their real-world performance, and we can compare different forecasting technologies.
+Most notably, we can simulate future wind power production given a deterministic wind power forecast.
 Future wind power production using Monte Carlo methods, as well as the analytic form of the proposed SDE, can be used in optimal control problems involving wind power production.
@@
 Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations.
-Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion and non-Gaussian approximations.
+Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion, and non-Gaussian approximations.
 We apply the model to Uruguayan wind power forecasts together with historical wind power production data pertaining to the year 2019.
@@
 The application of the Lamperti transform with unknown parameters in Section \ref{Section_4} leads to model the forecast error through a stochastic differential equation with a unit diffusion coefficient.
-In Section \ref{Section_5} we write down the expressions for the likelihood functions of the forecast error in its original space and in the Lamperti space.
+In Section \ref{Section_5}, we write down the expressions for the likelihood functions of the forecast error in its original space and the Lamperti space.
 We also derive simple approximations of the likelihood functions.
 Section \ref{Section_5} concludes with the description of the optimization algorithm to compute approximate maximum likelihood estimates, including the case where we expand the model comprising an initial transition from the time the forecast is performed to the time of the first forecast.
+
 In Section \ref{Section_6}, we apply our proposed numerical estimation procedures to the Uruguay wind and forecast dataset, comparing two alternative models and assessing, for the best candidate model, the performance of three different forecast providers.
 Section \ref{Section_7} concludes the paper.
-The proofs of the existence, strong uniqueness, and boundedness of the solutions of the SDE used to model normalized wind power production and its forecast error are given in the Appendix.
+The proofs of the existence, strong uniqueness, and boundedness of the SDE solutions used to model normalized wind power production and its forecast error are given in the Appendix.
 
@@
 In recent years, Uruguay has triggered a remarkable change in its energy matrix.
-In (\cite{irena}, p.23) Uruguay is among those countries showcasing innovation, like Denmark, Ireland, Germany, Portugal, and Spain, with proven feasibility of managing annual variable renewable energy (VRE) higher than 25\% in power systems.
+In (\cite{irena}, p.23), Uruguay is among those countries showcasing innovation, like Denmark, Ireland, Germany, Portugal, and Spain, with proven feasibility of managing annual variable renewable energy (VRE) higher than 25\% in power systems.
 
@@
 A view of the global discrepancy between the real production and the forecasted production, during the nine months observation period, is summarized through the forecast error histograms in Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
-Low normalized generated power corresponds to the range $[0,0.3]$, mid-power refers to the range $(0.3,0.6]$, and high-power to the range $(0.6,1]$.
+Low normalized generated power corresponds to the range $[0,0.3]$, mid-power refers to the range $]0.3,0.6]$, and high-power to the range $]0.6,1]$.
 
@@
 
-We may observe that all the histograms in the Figure \ref{fig:data_curtailing} exhibit skewed patterns, to a different extent, as well as extreme observations.
+We may observe that all the histograms in Figure \ref{fig:data_curtailing} exhibit skewed patterns, to a different extent, as well as extreme observations.
 The presence of these features can be partly explained.
-The analysis of the dataset highlighted that, during several 24-hour segments, the system operators decided to reduce, or even cease the wind power production.
-Indeed, as recalled in (\cite{irena2}, p.3), ``Uruguay experiences high curtailment levels because generation exceeds demand.'' Despite the large country’s interconnection capacity with Argentina and Brazil, there is no active cross-border market, the energy is traded via ad hoc short-term agreements.
+The data analysis highlighted that, during several 24-hour segments, the system operators decided to reduce or even cease the wind power production.
+Indeed, as recalled in (\cite{irena2}, p.3), ``Uruguay experiences high curtailment levels because generation exceeds demand.'' Despite the large country's interconnection capacity with Argentina and Brazil, there is no active cross-border market; the energy is traded via ad hoc short-term agreements.
 ``Even with interconnection capacity exceeding peak demand, the power system experiences high VRE curtailment, mostly at night when wind generation exceeds demand.''
@@
 The curtailment of the wind power production imposed by the system operators has a strong influence on the forecast error.
-To build a model that, driven by the available forecast, allows to include the true power production with a prescribed degree of uncertainty, it is necessary to remove the data segments affected by wind curtailment.
+To build a model that, driven by the available forecast, allows the inclusion of true power production with a prescribed degree of uncertainty, it is necessary to remove the data segments affected by wind curtailment.
 
@@
 \item $a(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R} $  denotes a drift function,
-\item $b(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R}_+ $  a  diffusion function,
+\item $b(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R}^+ $  a  diffusion function,
 \item $\bm{\theta}$ is a vector of unknown parameters,
@@
 
-Our goal is to achieve a specification of the model (\ref{eq:main}) to follow closely the available normalized wind power forecasts while ensuring its unbiasedness with respect to the forecast.
+Our goal is to achieve a specification of the model (\ref{eq:main}) to follow the available normalized wind power forecasts closely while ensuring its unbiasedness with respect to the forecast.
 
@@
 Let $(p_t)_{t \in [0,T]}$ be the available prediction function for the normalized wind power, which is an input to this approach.
-To start with the model specification, first we introduce a time-dependent drift function that features the mean-reverting property as well as derivative tracking:
-\begin{equation}
-a(X_t; p_t, \dot{p}_t, \bm{\theta}) = \dot{p}_t  - \theta_t (X_t - p_t)\,,  \label{drift:meanrev-derivtrack}
+To start with the model specification, first, we introduce a time-dependent drift function that features the mean-reverting property as well as derivative tracking:\begin{equation}
+a(X_t; p_t, \dot{p}_t, \bm{\theta}) = \dot{p}_t  - \theta_t (X_t - p_t),  \label{drift:meanrev-derivtrack}
 \end{equation} 
@@
 
-Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $  \mathbb{E}\left[X_0\right] = p_0$.
+Now, looking at the normalized wind power generation forecast process $X_t$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $  \mathbb{E}\left[X_0\right] = p_0$.
 The application of  It\^{o}'s lemma on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s \dif s}$, leads to
@@
 \begin{itemize}
-\item it reverts to its mean $p_t$, with a time-varying speed $ \theta_t$ that is proportional to the deviation of the process $X$ from its mean,
+\item it reverts to its mean $p_t$, with a time-varying speed $ \theta_t$ that is proportional to the deviation of the process $X_t$ from its mean,
 \item it tracks the time derivative $\dot{p}_t$.  
@@
 The forecast and production wind power data of Uruguay are normalized with respect to the installed power capacity during the period of observation.
-Thus, the mean-reverting level lies in $[0,1]$, and the process $X$  must take values in the same interval, a requirement that is not automatically fulfilled through the derivative tracking.
-To impose that the state space of $X$ is $[0,1]$, we may choose a convenient diffusion term, and require that the time-varying parameter $ \theta_t$ satisfies an ad-hoc condition.
+Thus, the mean-reverting level lies in $[0,1]$, and the process $X_t$  must take values in the same interval, a requirement that is not automatically fulfilled through the derivative tracking.
+To impose that the state space of $X_t$ is $[0,1]$, we may choose a convenient diffusion term, and require that the time-varying parameter $ \theta_t$ satisfies an ad-hoc condition.
 
@@
   \end{equation}
-  where $\alpha >0$ is a unknown parameter that controls the path variability.
+  where $\alpha >0$ is an unknown parameter that controls the path variability.
 This diffusion term belongs to the Pearson diffusion family and, in particular, it defines a Jacobi type diffusion.
-It is useful to recall that (\cite[440]{foso}) a Pearson diffusion is a stationary solution to a stochastic differential equation of the form
- \begin{equation}
+It is useful to recall that (\cite[440]{foso}) a Pearson diffusion is a stationary solution to a stochastic differential equation of the form \begin{equation}
     \dif X_t = - \theta (X_t - \mu)\dif t + \sqrt{2 \theta \left(a X_t^2 + b X_t + c\right)} \dif W_t
   \end{equation}
-where $\theta>0$, and $a$, $b$ and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space.
+where $\theta>0$, and $a$, $b$, and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space.
 These parameters, together with $\mu$, the mean of the invariant distribution, determine the state space of the diffusion as well as the shape of the invariant distribution.
@@
     \dif X_t&= \left(\dot{p}_t  - \theta_t (X_t - p_t) \right) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]  \\
-   X_0 &=  x_0\in [0,1] \,,
+   X_0 &=  x_0\in [0,1] ,
 \end{cases}
@@
 
-is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X$ of (\ref{ourmodel}) to a non-stationary and time-inhomogeneous process.
-To ensure that the process $X$ is the unique strong solution of (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the condition:
+is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X_t$ of (\ref{ourmodel}) to a non-stationary and time-inhomogeneous process.
+To ensure that the process $X_t$ is the unique strong solution of (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the condition:
 
@@
 \end{align}
-that, after applying It\^{o}'s formula on $h(V_t, t)$, leads to the following SDE with state independent unit diffusion term
+that, after applying It\^{o}'s formula on $h(V_t, t; \bm{\theta} )$, leads to the following SDE with state independent unit diffusion term
 \begin{align}
@@
 \end{align}
-After replacing $V_t = 1 - p_t - \sin^2 \left(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \right) $ in (\ref{eq:stindepSDE}), we obtain that the  process $Z$ satisfies the SDE
+After replacing $V_t = 1 - p_t - \sin^2 \left(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \right) $ in (\ref{eq:stindepSDE}), we obtain that the  process $Z_t$ satisfies the SDE
 \begin{align}
@@
 
-To summarize visually the effect of the Lamperti transform, we can see in the next Figure (\ref{fig:LP_transitions}) how the forecast error transition histograms (without curtailment) modify in comparison with Figure (\ref{fig:error_transitions}).
-
-In this case, the Lamperti transform has been applied using the optimal estimates of the parameters in the SDE model (\ref{VtSDE}), obtained applying our numerical procedure detailed later in subsection (\ref{opt_sec}).
+To summarize the effect of the Lamperti transform visually, we can see in the next Figure (\ref{fig:LP_transitions}) how the forecast error transition histograms (without curtailment) modify in comparison with Figure (\ref{fig:error_transitions}).
+
+In this case, the Lamperti transform has been applied using the optimal estimates of the parameters in the SDE model (\ref{VtSDE}), obtained applying our numerical procedure detailed later in Subsection \ref{opt_sec}.
 
@@
 
-The shape of the forecast error transition histograms after applying the Lamperti transform has much resemblance with a Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process Z.
+The shape of the forecast error transition histograms after applying the Lamperti transform has much resemblance with a Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process $Z_t$.
 
@@
 
-Remark: In the last subsection of this Section, we will extend the statistical model (\ref{likelihood}) by adding the transition that occurs during the time interval, say of length $\delta$, between the epoch when the forecast is done and the first epoch (1 pm) of each day-ahead forecast.
+Remark: In the last Subsection of this Section, we will extend the statistical model (\ref{likelihood}) by adding the transition that occurs during the time interval, say of length $\delta$, between the epoch when the forecast is done and the first epoch (1 pm) of each day-ahead forecast.
 To this purpose, the likelihood function (\ref{likelihood}) must include for any of the $M$ paths an additional factor, say $\rho_0 (V_{j, 0}|V_{j, -\delta};\bm{\theta},\delta)$, expressing the conditional density of the early transition.
-The parameter $\delta$ can be calibrated after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.
-\\
-
-The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized, for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}, \cite[61-68]{saso}):
+The parameter $\delta$ can be calibrated together or after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.\\
+
+The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}, \cite[61-68]{saso}):
 
@@
 
-However, closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
-Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
+However, closed-form solutions to initial-boundary value problem for time-inhomogeneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
+Besides, in our case, solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
 Several numerical techniques have been devised to obtain estimates for the unknown parameters of continuous-time SDE models with discrete observations (see, for example, \cite{prewo} for likelihood-based inference techniques, \cite{Sor} for an estimating function approach, to mention a few contributions).
-As explained in the next subsection, we have considered approximate likelihood methods, similar in spirit to \autocite[Section 11.4]{saso}.
+As explained in the next Subsection, we have considered approximate likelihood methods, similar in spirit to \autocite[Section 11.4]{saso}.
 
@@
 
-Gaussian approximations to the transition densities of nonlinear time-in\-ho\-mo\-geneous SDEs are available through different algorithms \autocite[Chapter 9]{saso}.
-However, as Figure \ref{fig:error_transitions} may suggest at a first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
-
-Therefore, we propose to use a surrogate transition density for $V$ other than Gaussian. The moments of the SDE model (\ref{VtSDE}) are then matched to the moments of the surrogate density.
-
-From (\ref{eq:meanX}), we have $m_1(t) \equiv \mathbb{E} \left[V_t\right] = e^{- \int_{t_{j,i-1}}^t \theta_s \dif s} \,\mathbb{E} \left[V_{t_{j,i-1}}\right]$, for any $t\in [t_{j,i-1}, t_{j, i})$, $j = 1, \ldots, M$ and $i = 1, \ldots, N$ .
+Gaussian approximations to the transition densities of nonlinear time-inhomogeneous SDEs are available through different algorithms \autocite[Chapter 9]{saso}.
+However, as Figure \ref{fig:error_transitions} may suggest at first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
+
+Therefore, we propose to use a surrogate transition density for $V$ other than Gaussian. The moments of the SDE model (\ref{VtSDE}) are then matched to the surrogate density moments.
+
+From (\ref{eq:meanX}), we have $m_1(t) \equiv \mathbb{E} \left[V_t\right] = e^{- \int_{t_{j,i-1}}^t \theta_s \dif s} \,\mathbb{E} \left[V_{t_{j,i-1}}\right]$, for any $t\in [t_{j,i-1}, t_{j, i}[$, $j = 1, \ldots, M$ and $i = 1, \ldots, N$ .
 
@@
 \begin{equation}
-\frac{\dif  \mathbb{E}[ V^m_t]}{\dif t} = - m \theta_t \mathbb{E}[ V^m_t] + m (m-1) \alpha \theta_0  \mathbb{E}[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} ] \,.
-\end{equation}
-
-For any $t\in [t_{j,i-1}, t_{j, i})$, the first two moments of $V$, $m_1(t)$ and $m_2(t) \equiv \mathbb{E}[V_t^2]$, can be computed by solving the following system
+\frac{\dif  \mathbb{E}\left[ V^m_t\right]}{\dif t} = - m \theta_t \mathbb{E}\left[ V^m_t\right] + m (m-1) \alpha \theta_0  \mathbb{E}\left[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} \right] \,.
+\end{equation}
+
+For any $t\in [t_{j,i-1}, t_{j, i}[$, the first two moments of $V$, $m_1(t)$ and $m_2(t) \equiv \mathbb{E}\left[V_t^2\right]$, can be computed by solving the following system
 \begin{equation}
@@
 \subsubsection{Moment Matching}
+
 A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape real parameters, $\xi_1, \xi_2$.
 
-To approximate the transition densities of  the process $V$ using a Beta distribution, we equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$ .
+To approximate the transition densities of the process $V$ using a Beta distribution, we equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$.
 
@@
 \begin{equation}
-\xi_1 = - \frac{(\mu_t + 1 - \epsilon)(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2}\,, \quad \xi_2=  \frac{(\mu_t-1 + \epsilon )(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2} \,, \label{param_transformed_beta}
+\xi_1 = - \frac{(\mu_t + 1 - \epsilon)(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2}, \quad \xi_2=  \frac{(\mu_t-1 + \epsilon )(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2} , \label{param_transformed_beta}
 \end{equation}
@@
 The drift coefficient $a(Z_t; p_t, \dot{p}_t, \bm{\theta}) $ of the process $Z$ that satisfies (\ref{eq:stindepSDE2}) is nonlinear.
-After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i})$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} \left[Z_t\right]$ :\\
+After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i}[$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} \left[Z_t\right]$ :\\
 \begin{equation}
@@
 \end{equation*}
-The approximate Lamperti log-likelihood $\tilde{\ell}_L\left(\cdot ; z^{M, N+1}\right)$ for the observed sample $z^{M, N+1}$ is given by
-\begin{equation}
-\tilde{\ell}_L \left(\bm{\theta}; z^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i};\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}; \bm{\theta})} \Bigg) \right\},
+The approximate Lamperti log-likelihood $\tilde{\ell}_Z\left(\cdot ; z^{M, N+1}\right)$ for the observed sample $z^{M, N+1}$ is given by
+\begin{equation}
+\tilde{\ell}_Z \left(\bm{\theta}; z^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i};\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}; \bm{\theta})} \Bigg) \right\},
 \label{loglikelihoodZ}
@@
 \item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
-$(V_{j,i}|v_{j,i-1})$ is a random variable which conditional mean can be approximated for any $t\in [t_{j,i-1}, t_{j, i})$ by the solution of the system
+$(V_{j,i}|v_{j,i-1})$ is a random variable which conditional mean can be approximated for any $t\in [t_{j,i-1}, t_{j, i}[$ by the solution of the system
 \begin{equation*}
@@
 Then, the random variable $(V_{j,i}-\E\left[V\right](t_{j,i}))$ has zero mean.
-If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i-1},t_{j,i}]$, then $\E\left[V(t_{j,i})\right]=v_{j,i-1}e^{-c\Delta}$.
+If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i-1},t_{j,i}[$, then $\E\left[V(t_{j,i})\right]=v_{j,i-1}e^{-c\Delta}$.
 If we have a total of $M\times N$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
@@
 \end{equation*}
-with the discrete sum $\sum_{0< t_{j, i-1} \leq t}(V_{t_{j, i}} - V_{t_{j, i-1}})^2$.
+with the discrete sum $\sum_{0< t_{j, i-1} \leq t}\left(V_{t_{j, i}} - V_{t_{j, i-1}}\right)^2$.
 
@@
 
-\item Use the training dataset to find the SDE's first and second moments as explained in subsection \ref{moments_ODEs}.
+\item Use the training dataset to find the SDE's first and second moments as explained in Subsection \ref{moments_ODEs}.
 \item Match the proxy distribution moments with the SDE's moments.
@@
 
-Let $v^{M,N+1}$ be the observed data, and $h( v_{j,i};\bm{\theta})$ the Lamperti transform of the observation $v_{j,i}$.
+Let $v^{M,N+1}$ be the observed data, and $h( v_{j,i},t_{j,i};\bm{\theta})$ the Lamperti transform of the observation $v_{j,i}$.
 The transformed observations $z^{M,N+1}$ depend on the parameter $\bm{\theta}$.\\
@@
 \begin{equation}
-\bm{\theta}^*=\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
+\bm{\theta}^*=\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
 \label{FP}
 \end{equation}
-{\color{red}In this point, the likelihood has a maximum for the data set corresponding to that point.}
-We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
+At a fixed point, the likelihood has a maximum for the data set corresponding to that point. We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
 \begin{equation*}
-\bm{\theta}^*-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right)=0.
+\bm{\theta}^*-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right)=0.
 \end{equation*}
@@
 \begin{equation*}
-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
+\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
 \end{equation*}
@@
 and remark that $\bm{\theta}^*$ is a fixed point if and only if $\Psi(\bm{\theta}^*)=0$.
-To find minimizers for $\Psi$, we proceed in the same way as described in subsection (\ref{Sec:MinLH}), but using Gaussian surrogate densities.
+To find minimizers for $\Psi$, we proceed in the same way as described in Subsection \ref{Sec:MinLH}, but using Gaussian surrogate densities.
 
@@
 where $\tilde{\mathcal{L}}_\delta$ is the approximated $\delta-$likelihood.
-To solve this problem, we repeat the steps described in subsection (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation for $p_{j,-\delta}$ at each $j\in\{1,2,\dots,M\}$.\\
+To solve this problem, we repeat the steps described in Subsection \ref{Sec:MinLH}, with the additional initial step of creating the linear extrapolation for $p_{j,-\delta}$ at each $j\in\{1,2,\dots,M\}$.\\
 \quad\\
@@
 \end{equation}
-where $\tilde{\mathcal{L}}\left(\bm{\theta}; v^{M,N +1}\right)$ is the approximation of (\ref{likelihood}).
+where $\tilde{\mathcal{L}}\left(\bm{\theta}; v^{M,N +1}\right)$ is the non-log version of (\ref{likelihood}).
 As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the approximated complete likelihood (\ref{eq:complete_LH}).
@@
 
-{ \color{red} Show that 24h is enough to ensure independence?}
-All the following results involving a single provider refer to Provider A.
+All the following results involving a single provider refer to provider A.
 Also, all calibrations involve the training sets and all simulations, the test sets.
-Following the instruction for the initial guesses from section $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.
+Following the instruction for the initial guesses from Subsection $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.
 
@@
 On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood.
-The numerical values of each important point can be seen in Table (\ref{tab:optimal_values}).
+The numerical values of each relevant point can be seen in Table (\ref{tab:optimal_values}).
 We set $(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood reaches its minimum value.
@@
 \end{table}
-Observe that all the local (possibly global) minimizers are located in curve $\theta_0\alpha=0.097$.
-We will explain this effect later, but it is a consequence of Markovianity and the indistinguishable observed transitions.
+Observe that all the local (possibly global) minimizers are located in curve $\theta_0\alpha=0.097$. {\color{red}This is a consequence of Markovianity and the indistinguishable observed transitions.}
 
@@
 \caption{Probability histograms for the error transitions.
-Using the Provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE.
+Using provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE.
 On the left, simulations using $(\theta_0^V,\alpha^V)$.
@@
 \dif X_t&=-\theta_0 (X_t - p_t) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]  \\
-X_0&=x_0\in (0,1),
+X_0&=x_0\in [0,1],
 \end{cases}.  \label{Model1}
@@
 \dif X_t&= \big(\dot{p}_t  - \theta_t (X_t - p_t) \big) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]\\
-X_0&=x_0\in (0,1) \,,
+X_0&=x_0\in [0,1],
 \end{cases}.  \label{Model2}
 \end{equation}
- with $\theta_0 > 0, \, \alpha > 0$ and $\theta_t$ satisfying the condition \eqref{Assumption:3} .
+ with $\theta_0 > 0$, $\alpha > 0$ and $\theta_t$ satisfying condition \eqref{Assumption:3} .
 \end{itemize}
@@
 After calibrating Model 2 on the training set using the complete likelihood (\ref{eq:complete_LH}), we can generate simulations of the wind power production for the time horizon of interest.
-Figure (\ref{fig:simulation_paths}) shows five simulated paths of the wind power production for each day of interest.
+Figure (\ref{fig:simulation_paths}) shows five simulated paths of wind power production for each day of interest.
 
@@
 \includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/4.eps}
-\caption{Four arbitrary days with five simulated wind power production paths each. }
+\caption{Four arbitrary days with five simulated wind power production paths each.}
 \label{fig:simulation_paths}
@@
 Once derived optimal estimates of the parameters of the complete likelihood for Model 2, we obtain empirical pointwise confidence bands for wind power production.
-Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for wind power production for each day of interest, assuming Model 2 specification, a given forecaster, and 5000 simulations per day.
+Figure (\ref{fig:confidence_bands}) shows the empirical pointwise confidence bands for wind power production for each day of interest, assuming Model 2 specification, a given forecaster, and 5000 simulations per day.
 
@@
 \includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/4.eps}
-\caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.93,0.050,0.090)$. Blue line: real production.}
+\caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(2.22,0.044,0.054)$. Blue line: real production.}
 \label{fig:confidence_bands}
@@
 \subsubsection{Value of $\delta$}
-As a final verification, we study the behavior of $\delta$ as function of $\bm{\theta}$.
+As a final verification, we study the behavior of $\delta$ as a function of $\bm{\theta}$.
 Given a vector of parameters, we calculate an initial guess for $\delta$ solving problem (\ref{eq:likelihood_delta}).
-Even when it is a guess, it helps us to understand qualitatively the meaning of this additional parameter.\\
+Even when it is a guess, it helps us to understand the meaning of this additional parameter qualitatively.\\
 \quad\\
@@
 This is a consequence of the increment in the diffusion as $\theta_0\alpha$ increases.
-As there is more diffusion, it is needed less time for the initial transition density to cover the initial error observations.
+As there is more diffusion, less time is needed for the initial transition density to cover the initial error observations.
 \item The initial time $\delta$ increases as $\theta_0$ increases.
 As we increment $\theta_0$, also the mean reversion becomes larger and reduces the variance for the initial transition density.
-Then, it is needed more time for the initial transition density to cover the initial error observations.
-\end{itemize}
+Then, it is needed more time for the initial transition density to cover the initial error observations.\end{itemize}
 
@@
 
-To this purpose, we built a phenomenological stochastic differential equation model for the forecast error of the normalized wind power production, with time-varying mean-reversion parameter in the linear drift coefficient, and state-dependent and time non-homogenous diffusion coefficient.
+To this purpose, we built a phenomenological stochastic differential equation model for the normalized wind power production forecast error, with time-varying mean-reversion parameter in the linear drift coefficient, and state-dependent and time non-homogenous diffusion coefficient.
 We also used the Lamperti transform with unknown parameters to provide a version of the proposed model with a unit diffusion coefficient, increasing its stability properties.
 
-We used approximate likelihood-based methods for the calibration of the models, developing original algorithms to derive optimal estimates of the unknown parameters.
-The likelihood approach has allowed extending the SDE models in a very effective way, incorporating an early transition with an additional parameter that accounts for the uncertainty of the forecast at the beginning of each future period.
+We used approximate likelihood-based methods for the models' calibration, developing original algorithms to derive optimal estimates of the unknown parameters.
+The likelihood approach has allowed extending the SDE models in a very effective way, incorporating an early transition with an additional parameter that accounts for the forecast's uncertainty at the beginning of each future period.
 As a result, we obtained a robust procedure for synthetic data generation that, using the available forecast input, allows embracing the future wind power production paths through empirical pointwise bands with prescribed confidence.
@@
 \subsection{The model}
-For a time horizon $T>0$ and  a parameter $\alpha > 0$ and $(\theta_t)_{t\in[0,T]}$ a positive deterministic  function,  let us consider the model  given by
+For a time horizon $T>0$, a parameter $\alpha > 0$, and $(\theta_t)_{t\in[0,T]}$ a positive deterministic  function,  let us consider the model  given by
 \begin{equation}
 \begin{cases}
-\dif X_t &= \big(\dot p_t - \theta_t (X_t-p_t)  \big)\dif t  +\sqrt{2 \alpha \theta_0 X_t (1-X_t)} \dif W_t, \quad t\in(0,T) \\
+\dif X_t &= \big(\dot p_t - \theta_t (X_t-p_t)  \big)\dif t  +\sqrt{2 \alpha \theta_0 X_t (1-X_t)} \dif W_t, \quad t\in[0,T] \\
 X_0&= x_0\in [0,1],
-\end{cases}.  \label{eq:model}
+\end{cases}  \label{eq:model}
 \end{equation}
@@
 \begin{equation}\label{eq:eds1}
-X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)\dif s  + \int_0^t\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s, \quad 0<x_0<1.
-\end{equation}
-According to Proposition 2.13, p.291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X$ to \eqref{eq:eds1}.
+X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)\dif s  + \int_0^t\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s, \quad 0\leq x_0\leq1.
+\end{equation}
+According to Proposition 2.13, p.291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X_t$ to \eqref{eq:eds1}.
 Moreover, as the diffusion coefficient is of linear growth, we have  for all $p>0$
@@
 Then, it remains to show that for all $t\in[0,T]$, $X_t\in[0,1]$ a.s.
-For this aim, we need to use the so-called Yamada function $\psi_n$ that is a $\mathcal C^2$ function that satisfies a bench of useful properties:
+For this aim, we need to use the so-called Yamada function $\psi_n$ that is a $\mathcal C^2$ function that satisfies a bunch of useful properties:
 \begin{align*}
 &|\psi_n(x)|\underset{n\rightarrow+\infty}{\rightarrow}|x|, \;\; x{\psi'}_n(x)\underset{n\rightarrow+\infty}{\rightarrow}|x|, \;\; |\psi_n(x)|\wedge |x{\psi'}_n(x)| \le |x|\\
-&{\psi'}_n(x)\le 1, \;\; \mbox{ and } {\psi''}_n(x)=g_n(|x|)\ge 0\;\; \mbox{ with } \;\; g_n(x)x\le \frac 2n\;\;  \mbox{ for all } x\in \mathbb R .
+&{\psi'}_n(x)\le 1, \;\; \mbox{and}\;\; {\psi''}_n(x)=g_n(|x|)\ge 0\;\; \mbox{with} \;\; g_n(x)x\le \frac 2n\;\;  \mbox{for all}\;\; x\in \mathbb R .
 \end{align*}
@@
 \end{align*}
-Now, thanks to  \eqref{Assumption:1}, \eqref{prop:fm} and to the above properties of $\psi_n$ and $g_n$, we get
-$$
-\mathbb E\left[\psi_n(X_t)\right]\le \psi_n(x_0) +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \right)\dif s + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E |1-X_s|\dif s.
-$$
-Therefore, letting $n$ tends to infinity we use Lebesgue's theorem to get
-$$
-\mathbb E\left[|X_t|\right]\le x_0 +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E|X_s| \right)\dif s.
+Now, thanks to  \eqref{Assumption:1}, \eqref{prop:fm}, and to the above properties of $\psi_n$ and $g_n$, we get
+$$
+\mathbb E\left[\psi_n(X_t)\right]\le \psi_n(x_0) +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \right)\dif s + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E \left[|1-X_s|\right]\dif s.
+$$
+Therefore, letting $n$ tends to infinity, we use Lebesgue's theorem to get
+$$
+\mathbb E\left[|X_t|\right]\le x_0 +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E\left[|X_s|\right] \right)\dif s.
 $$
@@
 $$
-\mathbb E X_t=x_0+  \int_0^t\big(\dot p_s +\theta_sp_s - \theta_s \mathbb EX_s  \big)\dif s
+\mathbb E \left[X_t\right]=x_0+  \int_0^t\big(\dot p_s +\theta_sp_s - \theta_s \mathbb E\left[X_s\right]  \big)\dif s,
 $$
@@
 $$
-Then, Gronwall's lemma gives us $\mathbb E[|X_t|]=\mathbb E X_t$ and thus for any $t\in[0,T]$ $X_t\ge0$ a.s.
+Then, Gronwall's lemma gives us $\mathbb E\left[|X_t|\right]=\mathbb E \left[X_t\right]$ and thus for any $t\in[0,T]$ $X_t\ge0$ a.s.
 The same arguments work to prove that  for any $t\in[0,T]$ $Y_t:=1-X_t\ge0$  a.s.
@@
 $$
-\dif Y_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)\dif t  -\sqrt{2\alpha \theta_tY_t(1-Y_t)} \dif W_t,
+\dif Y_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)\dif t  -\sqrt{2\alpha \theta_0Y_t(1-Y_t)} \dif W_t,
 $$
@@
 $$
-X_t\ge x_0\exp\Big(\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\Big).
+X_t\ge x_0\exp\left(\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\right).
 $$
@@
 $$
-\dif Y_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)\dif t  -\sqrt{2\alpha \theta_0 Y_t(1-Y_t)} \dif W_t 
+\dif Y_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)\dif t  -\sqrt{2\alpha \theta_0 Y_t(1-Y_t)} \dif W_t,
 $$
@@
 
-Remark: As the diffusion coefficient of $X$  given by  $x \mapsto \sqrt{2 \alpha \theta_0 x(1-x)}$  is strictly positive for all $x \in  ]0,1[$, the condition \eqref{Assumption:3}  ensures that the transformation between $Z$ and $X$ is bijective, so that we deduce the properties of existence and uniqueness of $Z$ from those of $X$.
-The application of  It\^{o}'s formula in Section \ref{Section_4} is subjected to the condition \eqref{Assumption:3} that avoids the process $X$ hits the boundaries of the interval $ ]0,1[$, otherwise the Lamperti transform is not applicable.
+Remark: As the diffusion coefficient of $X_t$  given by  $x \mapsto \sqrt{2 \alpha \theta_0 x(1-x)}$  is strictly positive for all $x \in  ]0,1[$, the condition \eqref{Assumption:3}  ensures that the transformation between $Z_t$ and $X_t$ is bijective, so that we deduce the properties of existence and uniqueness of $Z_t$ from those of $X_t$.
+The application of  It\^{o}'s formula in Section \ref{Section_4} is subjected to the condition \eqref{Assumption:3} that avoids the process $X_t$ hits the boundaries of the interval $ ]0,1[$, otherwise the Lamperti transform is not applicable.
 

### 2020-06-03 MATLAB_Files/cross_correlation_test_Lamperti.m
Added cross-correlation Lamperti

@@ -12,10 +12,11 @@ train_data             = load_data_eps(epsilon,dataSet,dataKind);
 test_data              = load_data_eps_test(epsilon,dataSet,dataKind);
 [~, ~, table_complete] = load_data(dataSet);
 lag                    = 150;
+font_size              = 14;
 
-train_error = transpose(train_data.Error);
-test_error  = transpose(test_data.Error);
-all_error   = transpose(table_complete.Error);
+train_error = transpose(train_data.Error_Lamp);
+test_error  = transpose(test_data.Error_Lamp);
+all_error   = transpose(table_complete.Error_Lamp);
 
 [N1,M1]   = size(train_error);
 [N2,M2]   = size(test_error);
@@ -46,7 +47,8 @@ figure('Renderer', 'painters', 'Position', [10 10 900 600]);
 imagesc(X1,Y,train_xcorr); colorbar;
 title('Sample xcorr Function (observatios - training)');
 xlabel('Day'); ylabel('Lag');
-saveas(gcf,[pwd '/Results/cross_correlation/obs_training'],'epsc');
+set(gca,'FontSize',font_size);
+saveas(gcf,[pwd '/Results/cross_correlation/obs_training_L'],'epsc');
 
 figure('Renderer', 'painters', 'Position', [10 10 900 600]);
 contour(x2,y2,test_xcorr); colorbar;
@@ -54,7 +56,8 @@ figure('Renderer', 'painters', 'Position', [10 10 900 600]);
 imagesc(X2,Y,test_xcorr); colorbar;
 title('Sample xcorr Function (observatios - testing)');
 xlabel('Day'); ylabel('Lag');
-saveas(gcf,[pwd '/Results/cross_correlation/obs_testing'],'epsc');
+set(gca,'FontSize',font_size);
+saveas(gcf,[pwd '/Results/cross_correlation/obs_testing_L'],'epsc');
 
 figure('Renderer', 'painters', 'Position', [10 10 900 600]);
 contour(x3,y3,all_xcorr); colorbar;
@@ -62,13 +65,14 @@ figure('Renderer', 'painters', 'Position', [10 10 900 600]);
 imagesc(X3,Y,all_xcorr); colorbar;
 title('Sample xcorr Function (observatios - all data)');
 xlabel('Day'); ylabel('Lag');
[…]

### 2020-06-04 Python_code/Slides/Wind_project.tex
Added thesis

\documentclass{beamer}

\mode<presentation>
{
  \usetheme{default}     
  \usecolortheme{default} 
  \usefonttheme{default} 
}

\usepackage[french]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{pgffor}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{ragged2e}

\apptocmd{\frame}{}{\justifying}{}

\setbeamertemplate{caption}[numbered]
\setbeamertemplate{frametitle}{\color{blue}\textbf{\small\insertframetitle}}
%\setbeamerfont{frametitle}{size=\small}
\setbeamertemplate{footline}{% 
  \hfill% 
  \usebeamercolor[fg]{page number in head/foot}% 
  \usebeamerfont{page number in head/foot}% 
  \insertframenumber%
  %\,/\,\inserttotalframenumber
  \kern1em\vskip2pt% 
}
\graphicspath{{C:/Users/HP/Desktop/plots/}}}

}

\title[Title]{Wind project inference}
\author{Khaoula Ben Chaabane}
\institute{Ecole Polytechnique de Tunisie}
\date{02/06/2020}

\begin{document}

\begin{frame}
  \titlepage
  \thispagestyle{empty}
\end{frame}

\section{Introduction}
\begin{frame}{Introduction}
\justifying
In these slides, I will explain the inference process with which we estimate the parameters of our model.
\end{frame}

\section{Model}
\begin{frame}{Model}
\justifying
The wind power production is modeled as follows, where $X_{t}$ is the normalized real production:$$\\ 
\left\{\begin{array}{l}
d X_{t}=\left(\dot{p}_{t}-\theta_{t}\left(X_{t}-p_{t}\right)\right) d t+\sqrt{2 \alpha \theta_{0} X_{t}\left(1-X_{t}\right)} d W_{t}, \quad t \in[0, T] \\
X_{0}=x_{0} \in[0,1]
\end{array}\right.$$$$\\
We may introduce the following model for the forcecast error of the normalized wind power production where $X_{t}$ is the real production, $p_{t}$ the forecast and $V_{t}=X_{t}-p_{t}$  is the error:
$$
\begin{equation}
\left\{\begin{array}{l}
d V_{t}=-\theta_{t} V_{t} d t+\sqrt{2 \alpha \theta_{0}\left(V_{t}+p_{t}\right)\left(1-V_{t}-p_{t}\right)} d W_{t}, \quad t \in[0, T] \\
V_{0}=v_{0} \in[-1+\varepsilon, 1-\varepsilon]
\end{array}\right.
\end{equation}
\end{frame}

\begin{frame}{Model}
To guarantee a unique solution for the process $X_{t},$ $\theta_{t}$ needs to be bounded for $t \in[0, T]$. We have that:
$$$$
\theta_{t}=\max \left(\theta_{0}, \frac{\alpha \theta_{0}+\left|\dot{p}_{t}\right|}{ \min \left(1-p_{t}, p_{t}\right)}\right)
$$$$
This is not true for $\theta_{t}$ if $p_{t} \rightarrow 0^{+}$ or $p_{t} \rightarrow 1^{-} .$ Therefore we need to ensure that $p_{t} \in[\varepsilon, 1-\varepsilon]$ for some $0<\varepsilon<\frac{1}{2}$, $\forall$ $t \in[0, T]$.
\end{frame}

\begin{frame}{Model}
We define then the corrected forecast:
$$
p_{t}^{\varepsilon}=\left\{\begin{array}{ll}
\varepsilon & \text { if } \quad p_{t}<\varepsilon \\
p_{t} & \text { if } \quad \varepsilon \leq p_{t}<1-\varepsilon \\
1-\varepsilon & \text { if } \quad p_{t} \geq 1-\varepsilon
\end{array}\right.
$$\\
and the corrected (and bounded) drift coefficient is therefore:
$$
\theta_{t}^{\varepsilon}=\max \left(\theta_{0}, \frac{\alpha \theta_{0}+\left|\dot{p}_{t}^{\varepsilon}\right|}{ \min \left(1-p_{t}^{\varepsilon}, p_{t}^{\varepsilon}\right)}\right)
$$
\end{frame}

\section{Likelihood}

\begin{frame}{Likelihood}
\justifying
We sample each of our M continuous-time Itô process $V=(V_{t})_{t \in[0, T]}$  at $N+1$ equidistant discrete points with a given length interval $\Delta$.
\\ $V^{M, N+1}=\left\{V_{t_{1}}^{N+1}, V_{t_{2}}^{N+1}, \ldots, V_{t_{M+1}}^{N+1}\right\}$ denotes this random sample, with $V_{t_{j}}^{N+1}=\left\{V_{t_{j}+i \Delta}, i=0, \ldots, N\right\}, \forall j\in\left\{1, \ldots, M\right\}.$
\vskip 0.5cm
\\Let $\rho\left(v | v_{j, i-1} ; \boldsymbol{\theta}\right)$ be the conditional probability density of $V_{t_{j}+i \Delta} \equiv V_{j, i}$,  given $V_{j, i-1}$  where $\boldsymbol{\theta}=\left(\theta_{0}, \alpha\right)$ are the unknown model parameters.
\vskip 0.5cm
The Itô process $V$ defined by the SDE (1) is Markovian, then the likelihood function of the sample $V^{M, N+1}$ can be written as follows:
\[
\mathcal{L}\left(\boldsymbol{\theta} ; V^{M, N+1}\right)=\prod_{j=1}^{M}\left\{\prod_{i=1}^{N} \rho\left(V_{j, i} | V_{j, i-1} ; p_{\left[t_{j, i-1}, t_{j, i}\right]}, \boldsymbol{\theta}\right)\right\}
\]
where $t_{j, i} \equiv t_{j}+i \Delta$ for any $j\in\left\{1, \ldots, M\right\}$ and $i\in\left\{0, \ldots, N\right\}$
\end{frame}

\begin{frame}{Likelihood approximation}
\justifying
In order to compute the exact likelihood function, we need a closed-form expression of the transition probability of V which can be found using the Fokker-Planck equation:
\vskip 0.5cm
 \begin{array}{l}
\frac{\partial f}{\partial t} \rho\left(v, t | v_{j, i-1}, t_{j, i-1} ; \theta\right)=-\frac{\partial}{\partial v}\left(-\theta_{t} v \rho\left(v, t | v_{j, i-1}, t_{j, i-1} ; \theta\right)\right) \\
\quad+\frac{1}{2} \frac{\partial^{2}}{\partial v^{2}}\left(2 \theta_{0} \alpha\left(v+p_{t}\right)\left(1-v-p_{t}\right) \rho\left(v, t | v_{j, i-1}, t_{j, i-1} ; \theta\right)\right)
\end{array}\vskip 0.5cm
However, solving this equation is not always possible and is computationally costly. For this reason, we approximated the likelihood using a proxy distribution for V. \\In our case we used a Beta distribution $\Beta(\xi_{1},\xi_{2})$ as for the family of diffusion term in our SDE (1) (Pearson diffusion), it has been proved to be the best approximation. In order to find the parameters $(\xi_{1},\xi_{2})$ of this proxy distribution we will match its first and second moments with the ones of the exact distribution deduced from the SDE (1).
\end{frame}

\begin{frame}{Moment matching: First moment}
\justifying
For a time s $\in \left[t_{n},t_{n+1}\right]$ the exact first moment $m_{1}(s)$ deduced from the SDE (1) is the solution of the following ODE:\\
\left\{\begin{array}{l}
\mathrm{d} m_{1}(s)=\left[-m_{1}(s) \theta(s)\right] \mathrm{d} s \\
m_{1}\left(t_{n-1}\right)=v_{t_{n-1}}
\end{array}\right.
\vskip 0.5cm
We want to compute $m_{1}(t_{n})$:
\begin{itemize}
\item If $\theta(t_{n})=\theta(t_{n+1})=\theta$ then the exact solution is : $m_{1}(t_{n})=m_{1}(t_{n-1})\exp(-\theta(t_{n}-t_{n-1}))$
\item else, we compute a linear approximation of $\theta(s)$ and approximate the ODE using Forward-Euler:
\vskip 0.5cm
$m_{1}\left(s_{n}\right)=m_{1}\left(s_{n-1}\right)\left(1-\theta\left(s_{n-1}\right) \Delta s\right)$
\end{itemize}
\end{frame}

\begin{frame}{Moment matching: Second moment}
\justifying
Using Ito's formula, we find, for a time s $\in \left[t_{n},t_{n+1}\right]$, the exact second moment $m_{2}(s)$ deduced from the SDE (1) is the solution of the following ODE:
\vskip 0.5cm
$\left\{\begin{array}{ll}
\mathrm{d}m_{2}(s)=\left[-2 m_{2}(s)\left(\theta(s)+\alpha\theta_{0}\right)+2 \alpha\theta_{0} m_{1}(s)(1-2 p(s))\\+2\alpha \theta_{0}p(s)(1-p(s))\right]\mathrm{d}s\\
m_{2}\left(t_{n-1}\right)=v_{t_{n-1}}^{2}
\end{array}$.
\vskip 0.5cm
We compute a linear interpolation for the functions $\theta(s)$ and $p(s)$. After, we solve the ODE using Forward-Euler:\\
$m_{2}\left(s_{n}\right)=m_{2}\left(s_{n-1}\right)+\left[-2 m_{2}\left(s_{n-1}\right)\left(\theta\left(s_{n-1}\right)+\alpha \theta_{0}\right)\\+2 \alpha \theta_{0} m_{1}\left(s_{n-1}\right)\left(1-2 p\left(s_{n-1}\right)\right)+2 \alpha \theta_{0} p\left(s_{n-1}\right)\left(1-p\left(s_{n-1}\right)\right)\right] \Delta s
$\vskip 0.5cm
We use the same discretization points for both $m_{1}(s)$ and $m_{2}(s)$.
\end{frame}

\begin{frame}{Moment matching}
\justifying
V is approximated by a new proxy random variable: $V=a+(b-a) X$ with support in $[a,b]=[-1,1],$ where $X \sim \beta\left(\xi_{1}, \xi_{2}\right)$ and $\operatorname{PDF} f_{V}(v)$.
We find the two first moments:
\vskip 0.5cm
\begin{itemize}
\item $\mathbb{E}[V]=a+(b-a) \mathbb{E}[X]=a+(b-a) \frac{\xi_{1}}{\xi_{1}+\xi_{2}}=\mu_{V}$
\item $\mathbb{V}[V]=(b-a)^{2} \mathbb{V}[X]=\frac{(b-a)^{2} \xi_{1} \xi_{2}}{\left(\xi_{1}+\xi_{2}\right)^{2}\left(\xi_{1}+\xi_{2}+1\right)}=\sigma_{V}^{2}$
\end{itemize}
\vskip 0.5cm
We want the first two moments of the true random variable and its approximation to be equal $\forall t$. \\Therefore, $\mu(t)=m_{1}(t)$ and $\sigma^{2}(t)=m_{2}(t)-m_{1}^{2}(t)$. 
\vskip 0.5cm
For each measurement $V_{t_{n-1}},$ we can find the analytical moments at time $t_{n}$ solving the ODEs from the previous slides. We can then find the parameters $\xi_{1}$ and $\xi_{2}$ of the proxy.
\end{frame}

\begin{frame}{Evaluation of $(\xi_{1},\xi_{2})$}
\begin{itemize}
\item $\xi_{1}=-\frac{(1+\mu)\left(\mu^{2}+\sigma^{2}-1\right)}{2 \sigma^{2}}$.
\item $\xi_{2}=\frac{(\mu-1)\left(\mu^{2}+\sigma^{2}-1\right)}{2 \sigma^{2}}$.
\end{itemize}
\vskip 0.5cm
 all evaluated at time $t_{n}$
\end{frame}

\begin{frame}{Log-density of the proxy random variable V}
\justifying
We want to compute the PDF $f_{V}(v)$ of the random variable:\\ $V=a+(b-a)X$. 
\vskip 0.5cm
 For $[a, b]=[-1,1],$ we have that: \\
$f_{V}(v)=f_{X}\left(g^{-1}(v)\right)\left|\frac{\mathrm{d}}{\mathrm{d} v} g^{-1}(v)\right| \quad$ where $\quad f_{X}(x)=\operatorname{Beta}\left(\xi_{1}, \xi_{2}\right) \quad$ and $\quad g(x)=a+(b-a) x$.
\vskip 0.5cm
Then, 
\\$f_{V}(v)=\frac{1}{|(b-a)|} \frac{1}{B\left(\xi_{1}, \xi_{2}\right)}\left(\frac{v-a}{b-a}\right)^{\xi_{1}-1}\left(1-\frac{v-a}{b-a}\right)^{\xi_{2}-1}$, because \\$g^{-1}(v)=\frac{v-a}{b-a}$.\vskip 0.5cm
Therefore:\\
$\log \left(f_{V}(v)\right)=\log \left(\frac{1}{B\left(\xi_{1}, \xi_{2}\right)}\right)+\left(\xi_{1}-1\right) \log \left(\frac{v-a}{b-a}\right)+\left(\xi_{2}-1\right) \log \left(\frac{b-v}{b-a}\right)$
\end{frame}
\begin{frame}{Log-likelihood}
\justifying
We introduce the number of paths (days) $M,$ and the number of measurements per path $N+1(N$ transitions). We have a total of $M \times N$ samples. 	The log-likelihood is:
\[
\mathfrak{L}\left(\{V\}_{M, N}\right)=\sum_{i=1}^{M} \sum_{j=2}^{N+1} \log \left[\rho_{i, j}\left(V_{i, j} | V_{i, j-1}\right)\right]
\]
where $\rho_{i, j}\left(V_{i, j} | V_{i, j-1}\right)=\rho_{i, j}\left(V_{i, j} | V_{i, j-1} ; \xi_{1, j}, \xi_{2, j}\right)$.
\end{frame}

\section{Initial Estimation of the parameters}

\begin{frame}{Initial Estimation of the parameters}
\justifying
In order to evaluate the initial parameters of our model we apply the least square method on the forecast error $V_{t}$.\\ We consider the transition $\Delta V_{i}=V_{i+1}-V_{i}$ with $\Delta t=t_{i+1}-t_{i}.\\
\left(V_{i+1} | V_{i}\right)$ is a random variable which conditional mean can be approximated by the solution of the following system:
\vskip 0.5cm
\left\{\begin{array}{l}
\mathrm{d} \mathbb{E}[V]=-\theta_{t}^{\varepsilon} \mathbb{E}[V] \mathrm{d} t \\
\mathbb{E}\left[V\left(t_{i}\right)\right]=V_{i}
\end{array}\right.

evaluated in $t_{i+1}$ (i.e., $\mathbb{E}\left[V\left(t_{i+1}\right)\right]$ ).
\end{frame}
\section{LSM}
\begin{frame}{Least Square Minimization: LSM}
\justifying
 Then, the random variable $\left(V_{i+1}-\mathbb{E}\left[V\left(t_{i+1}\right)\right]\right)$ has a mean equal to 0 approximately.\\
If we assume that $\theta_{t}^{\varepsilon}=c \in \mathbb{R}^{+}$ for all $t \in\left[t_{i}, t_{i+1}\right],$ then $\mathbb{E}\left[V\left(t_{i+1}\right)\right]=V_{i} e^{-c \Delta t} .$ \\If we have a total of $n$ transitions, we can write the regression problem for the conditional mean with $L^{2}$ loss function as:\\$$
\begin{equation}
%\begin{aligned}
c^{*} \approx \arg \min _{c \geq 0}\left[\sum_{i=1}^{n}\left(V_{i+1}-\mathbb{E}\left[V\left(t_{i+1}\right)\right]\right)^{2}\right]\\&$$=\arg \min _{c \geq 0}\left[\sum_{i=1}^{n}\left(V_{i+1}-V_{i} e^{-c \Delta t}\right)^{2}\right]
%\end{aligned}
\end{equation}
\end{frame}

\begin{frame}{Least Square Minimization: LSM}
\justifying
We take the first order approximation of $e^{-c \Delta t}$  w.r.t. $c$: 
$$
e^{-c \Delta t}=1-c \Delta t+\mathscr{O}\left((c \Delta t)^{2}\right)
$$
and introduce it in equation $(1) .$ We get
$$
c^{*} \approx \arg \min _{c \geq 0} \underbrace{\left[\sum_{i=1}^{n}\left(V_{i+1}-V_{i}(1-c \Delta t)\right)^{2}\right]}_{=f(c)}
$$
As $f(c)$ is convex in $c,$ solving (5) (finding $c^{*}$ ) is equivalent to solving
$$
\frac{\partial f}{\partial c}\left(c^{* }\right)=0
$$
\end{frame}

\begin{frame}{Least Square Minimization: LSM}
\justifying
$$
\begin{aligned}
\frac{\partial f}{\partial c} &=\sum_{i=1}^{n} 2\left(-V_{i}\right)(-\Delta t)\left(V_{i+1}-V_{i}\left(1-\theta_{0} \Delta t\right)\right) \\
&=\sum_{i=1}^{n} 2 V_{i} \Delta t\left(V_{i+1}-V_{i}(1-c \Delta t)\right) \\
&=\sum_{i=1}^{n} 2 V_{i+1} V_{i} \Delta t-2 V_{i}^{2} \Delta t+2 V_{i}^{2} \Delta t^{2} c
\end{aligned}
$$
Then, $c^{* }$ satisfies the following: 
$$
c^{ *} \approx \frac{\sum_{i=1}^{n} V_{i}\left(V_{i}-V_{i+1}\right)}{\Delta t \cdot \sum_{i=1}^{n}\left(V_{i}\right)^{2}}
$$
\end{frame}

\section{Quadratic variation}
\begin{frame}{Quadratic variation}
\justifying
We approximate the SDE by its E-M scheme. In particular, we approximate the Itô quadratic variation with the discrete one:
\begin{itemize}
\item ltô process quadratic variation: $[V]_{t}=\int_{0}^{t} \sigma_{s}^{2} \mathrm{d} s$
\item Discrete process quadratic variation: $[V]_{t}=\Sigma_{0<s \leq t}\left(\Delta V_{s}\right)^{2}$
\end{itemize}$$$$\\
Then, considering $\Delta t$ the time between the measurements, we approximate:
$$
\theta_{0}^{*} \alpha^{*} \approx \frac{\sum_{i=1}^{n}\left(\Delta V_{i}\right)^{2}}{2 \Delta t \sum_{i=1}^{n}\left(V_{i}+p_{i}\right)\left(1-V_{i}-p_{i}\right)}
$$
\end{frame}

\section{\text { Estimation of} $\left(\theta_{0}, \alpha, \varepsilon\right)$}
\begin{frame}{\text { Estimation of} $\left(\theta_{0}, \alpha, \varepsilon\right)$}
\justifying
In this section, we will use the approximation made previously to estimate the parameters $\left(\theta_{0}, \alpha, \varepsilon\right)$ of the SDE. Let us define $\left(\theta_{0}^{*}, \alpha^{*}, \varepsilon^{*}\right)$ as their estimators.$$\\
\text{If we fix} $\varepsilon,$ we define the forecast error $\forall i \in {1...n}$ $V_{i}=X_{i}-p_{i}^{\varepsilon}$. \\ 
If we also fix $\theta_{0}$ and $\alpha,$ we can define the set of indexes: $$ \\
$\mathbf{I}=\left\{i \in\{1, \ldots, n\}: \text { the LSM estimation will estimate } \theta_{0}\right\}$ \\ $\mathbf{J}=\left\{j \in\{1, \ldots, n\}: \text { the } L S M \text { estimation will estimate } \frac{\theta_{0} \alpha}{\varepsilon}\right\}$ \\
We will proceed then to approximate these sets in order to estimate our parameters. 
\end{frame}

\begin{frame}{\text { Estimation of} $\left(\theta_{0}, \alpha, \varepsilon\right)$}
\justifying
To use the LSM estimation, we assumed that $\theta_{t}^{\varepsilon}=c \in \mathbb{R}^{+}, $ and we defined $\theta_{t}^{\varepsilon}$:
$$
\theta_{t}^{\varepsilon}=\max \left(\theta_{0}, \frac{\alpha \theta_{0}+\left|\dot{p}_{t}^{\varepsilon}\right|}{\min \left(1-p_{t}^{\varepsilon}, p_{t}^{\varepsilon}\right)}\right)
$$
From the definition of $\theta_{t}^{\varepsilon}:$ We have that for $\varepsilon<<1,$ and $p_{t}=\varepsilon$ or $p_{t}=1-\varepsilon,$ the approximation $\theta_{t}^{\varepsilon} \approx \frac{\theta_{0} \alpha}{\varepsilon}$ holds. Then, for $\varepsilon$ small enough, $\mathrm{J}$ can be approximated by the following:
$$
\mathbf{J} \approx \mathbf{J}=\left\{j \in\{1, \ldots, n\}: p_{j}^{\varepsilon} \in\{\varepsilon, 1-\varepsilon\}\right\}
$$
We have that it is more likely that $\theta_{t}^{\varepsilon}=\theta_{0}$ if $p_{t}^{\varepsilon} \approx \frac{1}{2} .$ Then, we can approximate I by
$$
\mathbf{I} \approx \tilde{\mathbf{I}}=\left\{i \in\{1, \ldots, n\}: p_{i} \in(\gamma, 1-\gamma)\right\}, \gamma \approx \frac{1}{2}, \gamma<\frac{1}{2}
$$
\end{frame}

 \begin{frame}{Estimation of $\alpha^{*}$}
\justifying
\\ With the previous approximation made of the quadratic variation we can estimate $\color{red} \theta_{0}*\alpha*=0.094$ therefore, with our given estimation of $\theta_{0}*$ we find that: $\color{red} \alpha*=0.08$
\end{frame}

 \begin{frame}{Estimation of $\varepsilon^{*}$}
\justifying
Now that we have an approximated value of $\theta_{0} \alpha,$ if we can estimate $\frac{\theta_{0} \alpha}{\varepsilon},$ then we can estimate $\varepsilon$.
We showed previously that for $\varepsilon<<1$, the LSM estimation using indexes from $\mathbf{J}$ is an estimator for $\frac{\theta_{0} \alpha}{\varepsilon}=: k$

The goal is to find values for $\varepsilon$ that satisfy $\varepsilon<<1$. For that we start by randomly choosing a small initial value for $\varepsilon$ (that we will call $\varepsilon_{0}$ ), and iterating we aim to converge to some local minimum. We proceed with the following steps:
\begin{itemize}
\justifying
\item We sample $\varepsilon_{0}$ from $\mathscr{U}[0.01,0.1]$ and load $\varepsilon \leftarrow \varepsilon_{0}$
\item We create $\tilde{J}$ and use the LSM estimation to find $k$. 
\begin{itemize}
\item If $k<\theta_{0}^{*},$ then the assumption $\theta_{t}^{\varepsilon}=c \in \mathbb{R}^{+}$ is wrong and we reduce the value of $\varepsilon,$ i.e., $\varepsilon \leftarrow \varepsilon * 0.999 .$ 
\item If $k \geq \theta_{0}^{*},$ we load $\varepsilon \leftarrow \frac{\theta_{0}^{*} \alpha^{*}}{k}(\text { we allow a maximum relative change of } 1 \%) .$
\end{itemize}
 We repeat this step 100 times.
\item We repeat steps 1 and 2, 50 times.
\end{itemize}
 \end{frame}

 \begin{frame}{Initial parameters estimation}
\justifying
 To conclude, the estimations of the SDE parameters that we found are: $\left(\theta_{0}^{*}, \alpha^{*}, \varepsilon^{*}\right)=(1.25,0.08,0.018).$
 \vskip 0.5cm
 The code computing this process can be found in the file\\  \textbf{Wind\_}\textbf{project\_}\textbf{intial\_}\textbf{guess.ipynb}.
 \end{frame}

 \begin{frame}{Log-likelihood optimization}
\justifying
 I minimized the negative log-likelihood using the function \textbold{fmin} from the library \textbold{scipy.optimize} in Python to estimate the parameters $(\theta_{0},\alpha)$. I found the following results for the different datasets provided:\\
 \begin{table}
\centering
\begin{tabular}{|l|l|l|l|} 
\hline
\textbf{Data providers} & $\theta_{0}$ & $\alpha$ & $\theta_{0}\alpha$  \\ 
\hline
First dataset                & 1.161                            & 0.0718                    & 0.083                                                  \\ 
\hline
UTEP5                   & 1.357                            & 0.0809                    & 0.108                                                  \\ 
\hline
MTLOG                   & 1.175                            & 0.0856                    & 0.100                                                  \\ 
\hline
AWSTEP                  & 1.196                            & 0.0846                    & 0.101                                                  \\
\hline
\end{tabular}
\end{table}
 \vskip 0.5cm
 The code of this optimization can be found in the file\\ \textbf{Wind\_project\_optimization.ipynb}
 \end{frame}

 \section{$\delta$}
 \begin{frame}{Time parameter $\delta$}
 In order to have $E(X)=p$ at all times, our SDE (1) needs to have a starting point where $V=0$ $(X=p)$.\\ \vspace{0.5cm}
 However, we noticed that with our data, the error $V$ at $t=0$ is not 0. Therefore, to still unsure we have this property, we suppose that there existed a time $t_{\delta}<0$ in the past where the condition $X=p$ was verified. (This can be justified as we assume that the forecast providers had at some point perfect information on the data).  \\ \vspace{0.5cm}.
 \end{frame}

 \begin{frame}{Time parameter $\delta$}
 To do this, we will linearly interpolate the forecast to a time $t_{\delta}$ $(t_{0}-t_{\delta}=\delta)$, and for the transition $V^{i}_{t_{0}}|V^{i}_{t_{\delta}}$ $\forall i\in \{1,\dots, M\}$  we will solve the following problem: 
\[
\delta \approx \arg \min _{\delta} \mathcal{L}_{\delta}\left(\boldsymbol{\theta}, \delta ; V^{M, 1}\right)=\arg \min _{\delta} \prod_{j=1}^{M} \rho_{0}\left(V^{i}_{t_{0}} |V^{i}_{t_{\delta}} ; \boldsymbol{\theta}, \delta\right) \]\\
We will approximate again the density with a $\Beta$ distribution and redo the same steps as before of moment matching to find its parameters.\\ \vspace{0.5cm}

We finally find that $\delta=0.0837=120$ minutes.

 \end{frame}

 \begin{frame}{Path simulation}
 I plotted the path for the real production, the forecast and some simulations of the production using the model.
\begin{figure}[ht] 
\centering
    \centering
    \includegraphics[width=1\linewidth]{paths0.eps} 
    \label{fig:dynamics}
 \end{figure}
 \end{frame}
 \begin{figure}[ht] 
\centering
    \centering
    \includegraphics[width=1\linewidth]{paths45.eps} 
    \label{fig:dynamics}
 \end{figure}
 \end{frame}
 \begin{figure}[ht] 
\centering
    \centering
    \includegraphics[width=1\linewidth]{paths80.eps} 
    \label{fig:dynamics}
 \end{figure}
 \end{frame}
 \begin{figure}[ht] 
\centering
    \centering
    \includegraphics[width=1\linewidth]{paths105.eps} 
    \label{fig:dynamics}
 \end{figure}
 \end{frame}

 \begin{frame}{Confidence intervals}
 I plotted the 99\%, 90\% and 50\% confidence intervals using 100 simulations per day.
\begin{figure}[ht] 
\centering
    \centering
    \includegraphics[width=1\linewidth]{bands0.eps} 
    \label{fig:dynamics}
 \end{figure}
 \end{frame}
 \begin{figure}[ht] 
\centering
    \centering
    \includegraphics[width=1\linewidth]{bands45.eps} 
    \label{fig:dynamics}
 \end{figure}
 \end{frame}
 \begin{figure}[ht] 
\centering
    \centering
    \includegraphics[width=1\linewidth]{bands80.eps} 
    \label{fig:dynamics}
 \end{figure}
 \end{frame}
 \begin{figure}[ht] 
\centering
    \centering
    \includegraphics[width=1\linewidth]{bands105.eps} 
    \label{fig:dynamics}
 \end{figure}
 \end{frame}

\end{document}

### 2020-06-07 LaTeX_Code/Paper/paper_1line.tex
Added prof. kebayer feedback PDF
Added updates

@@
 \affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
-\affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
+\affil[2]{{\color{red}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}}
 \affil[3]{Universidad de la Rep\'ublica, Instituto de Estad\'{\i}stica (IESTA), Montevideo, Uruguay}
@@
 Now, looking at the normalized wind power generation forecast process $X_t$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $  \mathbb{E}\left[X_0\right] = p_0$.
-The application of  It\^{o}'s lemma on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s \dif s}$, leads to
-\begin{equation*}
-\dif \left( X_t e^{\int_{0}^{t} \theta_s \dif s} \right) = e^{\int_{0}^{t} \theta_s \dif s} (\dot{p}_t + \theta_t p_t ) \dif t  + e^{\int_{0}^{t} \theta_s \dif s}b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \dif W_t,
-\end{equation*}
-whose integral form is
+The application of  It\^{o}'s lemma % on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s \dif s}$, leads to
+leads to
+%\begin{equation*}
+%\dif \left( X_t e^{\int_{0}^{t} \theta_s \dif s} \right) = e^{\int_{0}^{t} \theta_s \dif s} (\dot{p}_t + \theta_t p_t ) \dif t  + e^{\int_{0}^{t} \theta_s \dif s}b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \dif W_t,
+%\end{equation*}
+%whose integral form is
 \begin{equation}
@@
 Taking expectation on (\ref{eq:tomeanX}) we obtain
-\begin{align}
-\mathbb{E} \left[X_t\right] & = e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E} \left[X_0\right] +   \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u \dif u} \dif s   \right) \nonumber \\
-& =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E} \left[X_0\right] +   \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u \dif u} \dif s +  \big[ p_s \, e^{\int_{0}^{s} \theta_u \dif u} \big]^{t}_0  - \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u \dif u} \dif s  \right) \nonumber \\
-& =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E}\left[ X_0\right] + p_t \, e^{ \int_{0}^{t} \theta_s \dif s} - p_0 \right) = p_t. \label{eq:meanX}
-\end{align}
+%\begin{align}
+%\mathbb{E} \left[X_t\right] & = e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E} \left[X_0\right] +   \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u \dif u} \dif s   \right) \nonumber \\
+%& =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E} \left[X_0\right] +   \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u \dif u} \dif s +  \big[ p_s \, e^{\int_{0}^{s} \theta_u \dif u} \big]^{t}_0  - \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u \dif u} \dif s  \right) \nonumber \\
+%& =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E}\left[ X_0\right] + p_t \, e^{ \int_{0}^{t} \theta_s \dif s} - p_0 \right) = p_t. \label{eq:meanX}
+%\end{align}
+\begin{equation}
+\mathbb{E} \left[X_t\right] =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E}\left[ X_0\right] + p_t \, e^{ \int_{0}^{t} \theta_s \dif s} - p_0 \right) = p_t.
+\label{eq:meanX}
+\end{equation}
 
@@
     \dif X_t = - \theta (X_t - \mu)\dif t + \sqrt{2 \theta \left(a X_t^2 + b X_t + c\right)} \dif W_t
+    \label{eq:poly_diff}
   \end{equation}
@@
 
+Remark: Moreover, this obtained Gaussian distribution supports the validity of the choice of our model diffusion coefficient given by (\ref{eq:poly_diff}).
+
 %{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models, that is if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.}
@@
 
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$, and let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}, \, j = 1, \ldots, M$.
+Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at time $t_j$ with $j = 1, \dots, M$, is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
+Let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}$.
 
@@
 \begin{equation}
-\mathcal{L}(\bm{\theta}; V^{M,N +1}) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho ( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} )  \,  \right\},
+\mathcal{L}\left(\bm{\theta}; V^{M,N +1}\right) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho ( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} )    \right\},
 \label{likelihood}
@@
 \frac{ \partial f }{\partial t } & \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} )= - \frac{\partial}{ \partial v} (- \theta_t v \, \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) ) \nonumber \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( 2 \theta_0 \alpha (v+ p_t) (1 - v- p_t) \, \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) )\,,  \label{eq:fpk}
+& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( 2 \theta_0 \alpha (v+ p_t) (1 - v- p_t) \, \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) ),  \label{eq:fpk}
 \end{align}
@@
 
-For $m \geq 2$, using It\^o's lemma on $g(V_t) = V_t^m$, we obtain
+For $m \geq 2$, using It\^o's lemma % on $g(V_t) = V_t^m$, we obtain
 % arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
-\begin{align}
-\dif (V_t^m) & = \left( - m \theta_t V_t^m + \frac{1}{2} m (m -1) V_t^{m -2} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \right) \dif t  \nonumber \\
-& + m V_t^{m-1} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \dif W_t \,, \nonumber
-\end{align}
-from which we derive
-\begin{equation}
-\frac{\dif  \mathbb{E}\left[ V^m_t\right]}{\dif t} = - m \theta_t \mathbb{E}\left[ V^m_t\right] + m (m-1) \alpha \theta_0  \mathbb{E}\left[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} \right] \,.
+%\begin{align}
+%\dif (V_t^m) & = \left( - m \theta_t V_t^m + \frac{1}{2} m (m -1) V_t^{m -2} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \right) \dif t  \nonumber \\
+%& + m V_t^{m-1} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \dif W_t \,, \nonumber
+%\end{align}
+%from which we derive
+we derive
+\begin{equation}
+\frac{\dif  \mathbb{E}\left[ V^m_t\right]}{\dif t} = - m \theta_t \mathbb{E}\left[ V^m_t\right] + m (m-1) \alpha \theta_0  \mathbb{E}\left[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} \right] .
 \end{equation}
@@
 A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape real parameters, $\xi_1, \xi_2$.
-
-To approximate the transition densities of the process $V$ using a Beta distribution, we equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$.
+Recall that the choice of the beta proxy distribution is a natural choice as it is the invariant distribution of the Jacobi type processes.
+
+For any $t\in [t_{j,i-1}, t_{j, i}[$, we approximate the transition densities of the process $V$ using a Beta distribution.
+We equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$.
 
@@
 \begin{equation}
-\xi_1 = - \frac{(\mu_t + 1 - \epsilon)(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2}, \quad \xi_2=  \frac{(\mu_t-1 + \epsilon )(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2} , \label{param_transformed_beta}
+\xi_1(t) = - \frac{(\mu_t + 1 - \epsilon)(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2}, \quad \xi_2(t)=  \frac{(\mu_t-1 + \epsilon )(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2} , \label{param_transformed_beta}
 \end{equation}
@@
 
-The approximate log-likelihood $\tilde{\ell}(\cdot ; v^{V, N+1})$ of the observed sample $v^{V, N+1}$ can be expressed as 
-\begin{equation}
- \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1, \xi_2)} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1 -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2 -1} \right\},
+The approximate log-likelihood $\tilde{\ell}(\cdot ; v^{M, N+1})$ of the observed sample $v^{M, N+1}$ can be expressed as 
+\begin{equation}
+ \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1(t_{j,i}), \xi_2(t_{j,i}))} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1(t_{j,i}) -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2(t_{j,i}) -1} \right\},
 \label{eq:loglikelihoodV}
 \end{equation}
-where the shape parameters $\xi_1$ and $\xi_2$, according to (\ref{param_transformed_beta}), depend on the quantities $\mu(t_{j,i};\bm{\theta} )$ and $\sigma^2(t_{j,i};\bm{\theta} )$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
+where the shape parameters $\xi_1(t_{j,i})$ and $\xi_2(t_{j,i})$, according to (\ref{param_transformed_beta}), depend on the quantities $\mu(t_{j,i};\bm{\theta} )$ and $\sigma^2(t_{j,i};\bm{\theta} )$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
+$B(\xi_1,\xi_1)$ denotes the Beta distribution with parameters $\xi_1$ and $\xi_2$.
 
@@
 The drift coefficient $a(Z_t; p_t, \dot{p}_t, \bm{\theta}) $ of the process $Z$ that satisfies (\ref{eq:stindepSDE2}) is nonlinear.
-After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i}[$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} \left[Z_t\right]$ :\\
+After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i}[$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} \left[Z_t\right]$:
 \begin{equation}
@@
 To guarantee the good behave for our optimization algorithm, we aim to start the optimization as close as we can from the optimal parameters.
-We use \textbf{Least Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess.
+We use \textbf{Least Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess $(\theta_0^*,\alpha^*)$.
 
@@
 \item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
-$(V_{j,i}|v_{j,i-1})$ is a random variable which conditional mean can be approximated for any $t\in [t_{j,i-1}, t_{j, i}[$ by the solution of the system
+For any $t\in [t_{j,i-1}, t_{j, i}[$, we can approximate the first moment of $V$ by the solution of the system
 \begin{equation*}
 \begin{cases}
-\dif \E\left[V\right]&=-\theta_t\E\left[V\right]\dif t\\
+\dif \E\left[V\right](t)&=-\theta_t\E\left[V\right](t)\dif t\\
 \E\left[V\right](t_{j,i-1})&=v_{j,i-1},
@@
 Then, the random variable $(V_{j,i}-\E\left[V\right](t_{j,i}))$ has zero mean.
-If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i-1},t_{j,i}[$, then $\E\left[V(t_{j,i})\right]=v_{j,i-1}e^{-c\Delta}$.
+If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i-1},t_{j,i}[$, then $\E\left[V\right](t_{j,i})=v_{j,i-1}e^{-c\Delta}$.
 If we have a total of $M\times N$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
@@
 \end{equation}
-As Equation (\ref{Eq-1}) is convex in $c$ (composition of convex is convex), it is enough to verify the first order optimality conditions. From
+As Equation (\ref{Eq-1}) is convex in $c$, it is enough to verify the first order optimality conditions. From
 \begin{equation*}
@@
 \end{equation}
-
-\item \textbf{Quadratic variation:} We use the numerical Euler-Maruyama (E-M) scheme to approximate the solution to the SDE  \eqref{VtSDE}.
-In particular, we approximate the quadratic variation of the  It\^{o}'s  process $V$
+We are going to use Equation (\ref{Eq-4}) to approximate $\theta_0$ setting $\theta_0^*=c^*$.
+
+\item \textbf{Quadratic variation:} We approximate the quadratic variation of the  It\^{o}'s  process $V$
 \begin{equation*}
@@
 
-\subsection{Calibration of the approximate negative log-likelihood in the $V-$space}
+\subsection{Calibration of the approximate negative log-likelihood in $V$-space and $Z$-space}
 
@@
 \end{table}
-Observe that all the local (possibly global) minimizers are located in curve $\theta_0\alpha=0.097$. {\color{red}This is a consequence of Markovianity and the indistinguishable observed transitions.}
-
-\subsection{Calibration of the approximate negative log-likelihood in the $Z-$space}
+Observe that all the local (possibly global) minimizers are located in curve $\theta_0\alpha=0.097$.
+
+%\subsection{Calibration of the approximate negative log-likelihood in the $Z-$space}
 

### 2020-06-08 LaTeX_Code/Paper/paper_1line.tex
two comments

@@
 \affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
-\affil[2]{{\color{red}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}}
+\affil[2]{Universit\'e Sorbonne Paris Nord, LAGA, CNRS, UMR 7539, F-93430, Villetaneuse, France}
 \affil[3]{Universidad de la Rep\'ublica, Instituto de Estad\'{\i}stica (IESTA), Montevideo, Uruguay}
@@
 
-\subsection{Approximate likelihood  in the $Z-$space}
+\subsection{Approximate likelihood  in the $Z-$space} \label{moments_ODEs_Z}
 
@@
 
-We compare two candidate models to find the best-fit that maximizes the retained information:
+We compare two candidate models to find the best-fit that maximizes the retained information, {\color{red} the Model 1, introduced in (\cite{elkate}, p.383), and our proposed model  (\ref{ourmodel}), from hereafter called Model 2.}
 \begin{itemize}
@@
 \end{itemize}
-To show the better performance of Model 2, we have computed the Akaike information criterion (AIC) and the Bayesian information criterion (BIC) for the two considered models, and any combination of the three different forecast providers with the three approximate likelihood methods.
+To show the better performance of Model 2, we have computed the Akaike information criterion (AIC) and the Bayesian information criterion (BIC) for the two considered models, and any combination of the three different forecast providers with  {\color{red} three approximate likelihood methods, the one based on the Beta surrogate density in the$V$-space (Subsection \ref{moments_ODEs}), the one based on the Gaussian surrogate density in the $Z$-space (Subsection \ref{moments_ODEs_Z}), and the Shoji-Ozaki local linearization method (\cite{shoz}).}
 Table (\ref{tab:model_comparison}) summarizes these results, also reporting the estimate of the variability diffusion coefficient $\alpha \theta_0$. 

### 2020-06-08 LaTeX_Code/Paper/paper_1line.tex
probabilistic forecasting intro

@@
 Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters, or forecast ensembles.
-{\color{red} Expand discussion about works on probabilistic forecasting.} However, there is a lack of simulating and producing data-driven stochastic forecasts based on forecasting models.
+%{\color{red} Expand discussion about works on probabilistic forecasting.} 
+However, there is a lack of simulating and producing data-driven stochastic forecasts based on forecasting models.
 It is crucial to capture the forecast's actual performance as it has been known that different forecasting technologies exhibit different behavior for different wind farms and seasons (\cite{chang}).
@@
 
-Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations.
+%Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations.
+ {\color{red} Some interesting works have been devoted to probabilistic forecasting related to renewable energies based on stochastic differential equations, among them (\cite{mozuma}) on wind power forecast, (\cite{immm}) and (\cite{bggk}) on forecasts of solar irradiance.}
 Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion, and non-Gaussian approximations.

### 2020-06-09 LaTeX_Code/Paper/paper_1line.tex
Modifications in paper. Still there are more to do (hopefully I will finish today)

@@
 \affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
-\affil[2]{Universit\'e Sorbonne Paris Nord, LAGA, CNRS, UMR 7539, F-93430, Villetaneuse, France}
+\affil[2]{\red{Universit\'e Sorbonne Paris Nord, LAGA, CNRS, UMR 7539, F-93430, Villetaneuse, France}}
 \affil[3]{Universidad de la Rep\'ublica, Instituto de Estad\'{\i}stica (IESTA), Montevideo, Uruguay}
@@
 The application of  It\^{o}'s lemma % on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s \dif s}$, leads to
-leads to
+leads to \red{(here we reduced the step-by-step...)}
 %\begin{equation*}
@@
 
-Remark: Moreover, this obtained Gaussian distribution supports the validity of the choice of our model diffusion coefficient given by (\ref{eq:poly_diff}).
-
+\red{Remark: Moreover, this obtained Gaussian distribution supports the validity of the choice of our model diffusion coefficient given by (\ref{eq:poly_diff}). 
+}
 %{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models, that is if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.}
@@
 
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at time $t_j$ with $j = 1, \dots, M$, is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
-Let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}$.
+\red{Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at a different time $t_j$ with $j = 1, \dots, M$, is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
+Let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}$.}
 
@@
 A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape real parameters, $\xi_1, \xi_2$.
-Recall that the choice of the beta proxy distribution is a natural choice as it is the invariant distribution of the Jacobi type processes.
+\red{Recall that the choice of the beta proxy distribution is a natural choice as it is the invariant distribution of the Jacobi type processes.}
 
@@
 We equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$.
+\red{(See new notation for $\xi_1$ and $\xi_2$...)}
 
@@
 \item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
-For any $t\in [t_{j,i-1}, t_{j, i}[$, we can approximate the first moment of $V$ by the solution of the system
+\red{For any $t\in [t_{j,i-1}, t_{j, i}[$, the random variable $(V_{j,i}|v_{j,i-1})$ has a conditional mean that can be approximate by the solution of the system}
 \begin{equation*}
@@
 \end{equation}
-We are going to use Equation (\ref{Eq-4}) to approximate $\theta_0$ setting $\theta_0^*=c^*$.
-
-\item \textbf{Quadratic variation:} We approximate the quadratic variation of the  It\^{o}'s  process $V$
+\red{We approximate $\theta_0$ by Equation (\ref{Eq-4}) setting $\theta_0^*=c^*$.}
+
+\item \textbf{Quadratic variation:} \red{(Does this sentence have sense now?)} We approximate the quadratic variation of the  It\^{o}'s  process $V$
 \begin{equation*}
-[V]_t=\int_0^t b(V_s; \bm{\theta}, p_s)^2 \dif s, \text{ where }  \:\: b(V_s; \bm{\theta}, p_s) = 
-\sqrt{2 \alpha \theta_0 (V_s +p_s ) (1-V_s - p_s)}\,,
+\langle V\rangle _t=\int_0^t b(V_s; \bm{\theta}, p_s)^2 \dif s, \text{ where }  \:\: b(V_s; \bm{\theta}, p_s) = 
+\sqrt{2 \alpha \theta_0 (V_s +p_s ) (1-V_s - p_s)},
 \end{equation*}
@@
 \begin{equation}
-\theta_0^*\alpha^*\approx\frac{\sum_{j=1}^M\sum_{i=1}^N(v_{j,i} - v_{j,i-1})^2}{2\Delta\cdot\sum_{j=1}^M\sum_{i=1}^N(v_{j,i}+p_{j,i})(1-v_{j,i}-p_{j,i})}\,,
+\theta_0^*\alpha^*=\frac{\sum_{j=1}^M\sum_{i=1}^N(v_{j,i} - v_{j,i-1})^2}{2\Delta\cdot\sum_{j=1}^M\sum_{i=1}^N(v_{j,i}+p_{j,i})(1-v_{j,i}-p_{j,i})},
 \label{Eq-2}
@@
 The problem of maximizing the approximated Lamperti log-likelihood (\ref{loglikelihoodZ}), i.e.,  $$\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta}; z^{M,N+1}\right),$$
-is not totally defined as the data $z^{M,N+1}$ depend on $\bm{\theta}$. However, we propose to find a fixed point $\bm{\theta}^*$ such that
-\begin{equation}
-\bm{\theta}^*=\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
+is not totally defined as the data $z^{M,N+1}$ depend on $\bm{\theta}$. However, we propose to find a fixed point $\bm{\theta}^\star $ such that
+\begin{equation}
+\bm{\theta}^\star=\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^\star )\}_{j=1,i=0}^{M,N}\right).
 \label{FP}
 \end{equation}
-At a fixed point, the likelihood has a maximum for the data set corresponding to that point. We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
+At a fixed point, the likelihood has a maximum for the data set corresponding to that point. We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^\star $ solves (\ref{FP}), then
 \begin{equation*}
-\bm{\theta}^*-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right)=0.
+\bm{\theta}^\star -\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^\star )\}_{j=1,i=0}^{M,N}\right)=0.
 \end{equation*}
-Given $\bm{\theta}^*=(\theta_0^*,\alpha^*)$, we call $\bm{\theta}^{**}=(\theta_0^{**},\alpha^{**})$ to the solution of
+Given $\bm{\theta}^\star =(\theta_0^\star ,\alpha^\star )$, we call $\bm{\theta}^{\star \star }=(\theta_0^{\star \star },\alpha^{\star \star })$ to the solution of
 \begin{equation*}
-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
+\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^\star )\}_{j=1,i=0}^{M,N}\right).
 \end{equation*}
-For each $\bm{\theta}^*$, we define the relative error function $\Psi:\R^+\times\R^+\to\R^+$ as
-\begin{equation}
-\Psi(\bm{\theta}^*)=\frac{|\theta_0^*-\theta_0^{**}|}{|\theta_0^*|}+\frac{|\alpha^*-\alpha^{**}|}{|\alpha^*|},
+For each $\bm{\theta}^\star $, we define the relative error function $\Psi:\R^+\times\R^+\to\R^+$ as
+\begin{equation}
+\Psi(\bm{\theta}^\star )=\frac{|\theta_0^\star -\theta_0^{\star \star }|}{|\theta_0^\star |}+\frac{|\alpha^\star -\alpha^{\star \star }|}{|\alpha^\star |},
 \label{eq:rel_error}
 \end{equation}
-and remark that $\bm{\theta}^*$ is a fixed point if and only if $\Psi(\bm{\theta}^*)=0$.
+and remark that $\bm{\theta}^\star $ is a fixed point if and only if $\Psi(\bm{\theta}^\star )=0$.
 To find minimizers for $\Psi$, we proceed in the same way as described in Subsection \ref{Sec:MinLH}, but using Gaussian surrogate densities.
@@
 Such an allocation mechanism guarantees independence among the segments, matching the assumption we did in Section \ref{Section_5} to formulate the statistical models.
+\red{Additional cross-correlation tests were performed to ensure this assumption.}
 
@@
 Also, all calibrations involve the training sets and all simulations, the test sets.
-Following the instruction for the initial guesses from Subsection $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.
+Following the instruction for the initial guesses from Subsection $\ref{opt_sec}$, we obtain the initial guess $(\theta_0^*,\alpha^*,\delta^*)\approx(1.54,0.072,073)$.
 
@@
 As an auxiliary verification, we plot the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) as a function of the parameters, and we use additional minimization functions from MATLAB R2019b.
+\red{Moreover, we realized an additional inference utilizing the test sets to guarantee the robustness of our numerical methods.}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.eps}
-\caption{Negative log-likelihood's level sets. All optimal values are located over the curve $\theta_0\alpha=0.097$.}
+\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.eps}\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood_testing.eps}
+\caption{\red{Negative log-likelihood's level sets for the training sets (plot on the left), and for the test sets (plot on the right).
+All optimal values are located over the curve $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.}}
 \label{fig:neg-LL}
 \end{figure}
-On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood.
-The numerical values of each relevant point can be seen in Table (\ref{tab:optimal_values}).
-We set $(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood reaches its minimum value.
+\red{On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood for both training and test sets.} The numerical values of each relevant point can be seen in Table (\ref{tab:optimal_values}).
+We set $(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood for the training sets reaches its minimum value.
 \begin{table}[H]
 \centering
-\begin{tabular}{lccc}
+\begin{tabular}{lcccccc}
 \toprule
- & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
+ & \multicolumn{3}{c}{Training sets} & \multicolumn{3}{c}{Test sets} \\
  \midrule
- Initial guess & 1.54 & 0.070 & 0.111 \\
- fminsearch & 1.14 & 0.076 & 0.097 \\
- fmincon & 1.58 & 0.062 & 0.097 \\
- fminunc & 1.54 & 0.063 & 0.097 \\
- evaluations & 1.93 & 0.050 & 0.097 \\
+ & $\theta_0$ & $\alpha$ & $\theta_0\alpha$ & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
+ \midrule
+ Initial guess & 1.54 & 0.070 & 0.111 & 1.96 & 0.053 & 0.104 \\
+ fminsearch & 1.14 & 0.076 & 0.097 & 1.64 & 0.054 & 0.089 \\
+ fmincon & 1.58 & 0.062 & 0.097 & 1.63 & 0.055 & 0.089 \\
+ fminunc & 1.54 & 0.063 & 0.097 & 1.96 & 0.045 & 0.089 \\
+ evaluations & 1.93 & 0.050 & 0.097 & 1.59 & 0.056 & 0.089 \\
  \bottomrule
@@
 \end{table}
-Observe that all the local (possibly global) minimizers are located in curve $\theta_0\alpha=0.097$.
+Observe that all the local (possibly global) minimizers are located over the curves $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.
 

### 2020-06-09 LaTeX_Code/Paper/paper_1line_Renzo.tex
Modifications in paper. Still there are more to do (hopefully I will finish today)

@@
 
-Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization of electricity price and operation scheduling of conventional power plant.
-We propose a data driven model based on parametric Stochastic Differential Equations (SDEs) to captures real-world asymmetric dynamics of wind power forecast errors.
-Our SDE framework incorporates time derivative tracking of the forecast, time-dependent mean reversion parameter and an improved diffusion term.
-We are able to simulate future wind power production paths and to get sharp confidence bands.
-The method is forecast technology agnostic and enables the comparison between different forecasting technologies on the basis of information criteria.
-We apply the model to historical Uruguayan wind power production data and forecasts on the year 2019.
+Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization for electricity price, and operation scheduling of conventional power plants.
+We propose a data-driven model based on parametric Stochastic Differential Equations (SDEs) to capture the real asymmetric dynamics of wind power forecast errors.
+Our SDE framework features time-derivative tracking of the forecast, time-varying mean-reversion parameter, and an improved state-dependent diffusion term.
+The methodology we developed allows the simulation of future wind power production paths and to obtain sharp empirical confidence bands.
+All the procedure is agnostic of the forecasting technology and enables comparing different forecast providers.
+We apply the model to historical Uruguayan wind power production data and forecasts during the period April-December 2019.
 
@@
 
-{\color{red}Keywords: Indirect inference, wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, model selection.}
-
-{\color{red} 2020 AMS Subject Classification: 60H10}
+Keywords: Wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform,
+
+numerical optimizaton, model selection.
+
+2020 AMS Subject Classification: 60H10, 62M20, 65K10.
 
@@
 
+The rest of the paper is organized as follows.
 In Section \ref{Section_2}, we introduce the main characteristics of a real data set encompassing the normalized wind power production in Uruguay during the period April-December 2019, joint with the most accurate predictions, as highlighted in our posterior analysis, performed by one out of the three sources of forecast providers.
 The significant steps for constructing phenomenological models of the normalized wind power production and the forecast error based on stochastic differential equations are described in Section \ref{Section_3}.
-After reformulating the SDE for the forecast error in Section \ref{Section_4}, by applying the Lamperti transform that leads to a unit diffusion coefficient, we write down in Section \ref{Section_5} the expressions for the likelihood functions of the forecast error in its original space and in the Lamperti space.
+The application of the Lamperti transform with unknown parameters in Section \ref{Section_4} leads to model the forecast error through a stochastic differential equation with a unit diffusion coefficient.
+In Section \ref{Section_5}, we write down the expressions for the likelihood functions of the forecast error in its original space and the Lamperti space.
 We also derive simple approximations of the likelihood functions.
 Section \ref{Section_5} concludes with the description of the optimization algorithm to compute approximate maximum likelihood estimates, including the case where we expand the model comprising an initial transition from the time the forecast is performed to the time of the first forecast.
-In Section \ref{Section_6}, we apply our proposed parametric estimation procedure to the Uruguay wind and forecast dataset, comparing two alternative models and assessing, for the best candidate model, the performance of three different forecast providers.
-The proofs of the existence, strong uniqueness, and boundedness of the solutions of the SDE used to model normalized wind power production and its forecast error are given in the Appendix.
+
+In Section \ref{Section_6}, we apply our proposed numerical estimation procedures to the Uruguay wind and forecast dataset, comparing two alternative models and assessing, for the best candidate model, the performance of three different forecast providers.
+Section \ref{Section_7} concludes the paper.
+The proofs of the existence, strong uniqueness, and boundedness of the SDE solutions used to model normalized wind power production and its forecast error are given in the Appendix.
 
@@
 
-A view of the global discrepancy between the real production and the forecasted production, during the nine months observation period, is summarized through the forecast error histograms, Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
-Low normalized generated power corresponds to the range $[0,0.3]$, mid-power refers to the range $(0.3,0.6]$, and high-power to the range $(0.6,1]$.
+A view of the global discrepancy between the real production and the forecasted production, during the nine months observation period, is summarized through the forecast error histograms in Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
+Low normalized generated power corresponds to the range $[0,0.3]$, mid-power refers to the range $]0.3,0.6]$, and high-power to the range $]0.6,1]$.
 
@@
 
-Now, looking at the normalized wind power generation forecast process $X$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $  \mathbb{E}\left[X_0\right] = p_0$.
-The application of  It\^{o}'s lemma on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s \dif s}$, leads to
-\begin{equation*}
-\dif \left( X_t e^{\int_{0}^{t} \theta_s \dif s} \right) = e^{\int_{0}^{t} \theta_s \dif s} (\dot{p}_t + \theta_t p_t ) \dif t  + e^{\int_{0}^{t} \theta_s \dif s}b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \dif W_t,
-\end{equation*}
-whose integral form is
+Now, looking at the normalized wind power generation forecast process $X_t$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $  \mathbb{E}\left[X_0\right] = p_0$.
+The application of  It\^{o}'s lemma % on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s \dif s}$, leads to
+leads to
+%\begin{equation*}
+%\dif \left( X_t e^{\int_{0}^{t} \theta_s \dif s} \right) = e^{\int_{0}^{t} \theta_s \dif s} (\dot{p}_t + \theta_t p_t ) \dif t  + e^{\int_{0}^{t} \theta_s \dif s}b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \dif W_t,
+%\end{equation*}
+%whose integral form is
 \begin{equation}
@@
   \end{equation}
-  where $\alpha >0$ is a unknown parameter that controls the path variability.
+  where $\alpha >0$ is an unknown parameter that controls the path variability.
 This diffusion term belongs to the Pearson diffusion family and, in particular, it defines a Jacobi type diffusion.
-It is useful to recall that (\cite[440]{foso}) a Pearson diffusion is a stationary solution to a stochastic differential equation of the form
- \begin{equation}
+It is useful to recall that (\cite[440]{foso}) a Pearson diffusion is a stationary solution to a stochastic differential equation of the form \begin{equation}
     \dif X_t = - \theta (X_t - \mu)\dif t + \sqrt{2 \theta \left(a X_t^2 + b X_t + c\right)} \dif W_t
-  \end{equation}
-where $\theta>0$, and $a$, $b$ and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space.
+    \label{eq:poly_diff}
+  \end{equation}
+where $\theta>0$, and $a$, $b$, and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space.
 These parameters, together with $\mu$, the mean of the invariant distribution, determine the state space of the diffusion as well as the shape of the invariant distribution.
@@
 
-We can see in Figure (\ref{fig:LP_transitions}) how the Lamperti transformation modifies the forecast error transition histogram without curtailment displayed in Figure (\ref{fig:error_transitions}).
+To summarize the effect of the Lamperti transform visually, we can see in the next Figure (\ref{fig:LP_transitions}) how the forecast error transition histograms (without curtailment) modify in comparison with Figure (\ref{fig:error_transitions}).
+
+In this case, the Lamperti transform has been applied using the optimal estimates of the parameters in the SDE model (\ref{VtSDE}), obtained applying our numerical procedure detailed later in Subsection \ref{opt_sec}.
 
@@
 
-The shape of the forecast error transition histograms after the Lamperti transformation has much resemblance with a Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process Z.
+The shape of the forecast error transition histograms after applying the Lamperti transform has much resemblance with a Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process $Z_t$.
+
+{\color{red}Remark: Moreover, this obtained Gaussian distribution supports the validity of the choice of our model diffusion coefficient given by (\ref{eq:poly_diff}).}
 
@@
 
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$ is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$, and let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}, \, j = 1, \ldots, M$.
+{\color{red}Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at time $t_j$ with $j = 1, \dots, M$, is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
+Let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}$.}
 
@@
 \begin{equation}
-\mathcal{L}(\bm{\theta}; V^{M,N +1}) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho ( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} )  \,  \right\},
+\mathcal{L}\left(\bm{\theta}; V^{M,N +1}\right) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho \left( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} \right)    \right\},
 \label{likelihood}
@@
 
- Remark: In the last subsection of this Section, we will extend the statistical model (\ref{likelihood}) by adding the transition that occurs during the time interval, say of length $\delta$, between the epoch when the forecast is done and the first epoch (1 pm) of each day-ahead forecast.
+Remark: In the last Subsection of this Section, we will extend the statistical model (\ref{likelihood}) by adding the transition that occurs during the time interval, say of length $\delta$, between the epoch when the forecast is done and the first epoch (1 pm) of each day-ahead forecast.
 To this purpose, the likelihood function (\ref{likelihood}) must include for any of the $M$ paths an additional factor, say $\rho_0 (V_{j, 0}|V_{j, -\delta};\bm{\theta},\delta)$, expressing the conditional density of the early transition.
-The parameter $\delta$ can be calibrated after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.
-\\
-
-The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized, for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}, \cite[61-68]{saso}):
+The parameter $\delta$ can be calibrated together or after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.\\
+
+The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}, \cite[61-68]{saso}):
 
@@
 
-Closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
-Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
-Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.
- {\color{red} Rewrite: Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, consider Preston and Wood, then Egorov, and then Sorensen, remove the
- survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}, refer to time-homogeneous.}
+However, closed-form solutions to initial-boundary value problem for time-inhomogeneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
+Besides, in our case, solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
+Several numerical techniques have been devised to obtain estimates for the unknown parameters of continuous-time SDE models with discrete observations (see, for example, \cite{prewo} for likelihood-based inference techniques, \cite{Sor} for an estimating function approach, to mention a few contributions).
+As explained in the next Subsection, we have considered approximate likelihood methods, similar in spirit to \autocite[Section 11.4]{saso}.
 
@@
 
-Gaussian approximations to the transition densities of nonlinear time-in\-ho\-mo\-geneous SDEs are available through different algorithms \autocite[Chapter 9]{saso}.
-However, as Figure \ref{fig:error_transitions} may suggest at a first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
-
-Therefore, we propose to use a surrogate transition density for $V$ other than Gaussian. The moments of the SDE model (\ref{VtSDE}) are then matched to the moments of the surrogate density.
-
-From (\ref{eq:meanX}), we have $m_1(t) \equiv \mathbb{E} \left[V_t\right] = e^{- \int_{t_{j,i-1}}^t \theta_s \dif s} \,\mathbb{E} \left[V_{t_{j,i-1}}\right]$, for any $t\in [t_{j,i-1}, t_{j, i})$, $j = 1, \ldots, M$ and $i = 1, \ldots, N$ .
-
-For $m \geq 2$, using It\^o's lemma on $g(V_t) = V_t^m$, we obtain
+Gaussian approximations to the transition densities of nonlinear time-inhomogeneous SDEs are available through different algorithms \autocite[Chapter 9]{saso}.
+However, as Figure \ref{fig:error_transitions} may suggest at first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
+
+Therefore, we propose to use a surrogate transition density for $V$ other than Gaussian. The moments of the SDE model (\ref{VtSDE}) are then matched to the surrogate density moments.
+
+From (\ref{eq:meanX}), we have $m_1(t) \equiv \mathbb{E} \left[V_t\right] = e^{- \int_{t_{j,i-1}}^t \theta_s \dif s} \,\mathbb{E} \left[V_{t_{j,i-1}}\right]$, for any $t\in [t_{j,i-1}, t_{j, i}[$, $j = 1, \ldots, M$ and $i = 1, \ldots, N$ .
+
+For $m \geq 2$, using It\^o's lemma % on $g(V_t) = V_t^m$, we obtain
 % arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
-\begin{align}
-\dif (V_t^m) & = \left( - m \theta_t V_t^m + \frac{1}{2} m (m -1) V_t^{m -2} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \right) \dif t  \nonumber \\
-& + m V_t^{m-1} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \dif W_t \,, \nonumber
-\end{align}
-from which we derive
-\begin{equation}
-\frac{\dif  \mathbb{E}[ V^m_t]}{\dif t} = - m \theta_t \mathbb{E}[ V^m_t] + m (m-1) \alpha \theta_0  \mathbb{E}[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} ] \,.
-\end{equation}
-
-For any $t\in [t_{j,i-1}, t_{j, i})$, the first two moments of $V$, $m_1(t)$ and $m_2(t) \equiv \mathbb{E}[V_t^2]$, can be computed by solving the following system
+%\begin{align}
+%\dif (V_t^m) & = \left( - m \theta_t V_t^m + \frac{1}{2} m (m -1) V_t^{m -2} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \right) \dif t  \nonumber \\
+%& + m V_t^{m-1} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \dif W_t \,, \nonumber
+%\end{align}
+%from which we derive
+we derive
+\begin{equation}
+\frac{\dif  \mathbb{E}\left[ V^m_t\right]}{\dif t} = - m \theta_t \mathbb{E}\left[ V^m_t\right] + m (m-1) \alpha \theta_0  \mathbb{E}\left[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} \right] .
+\end{equation}
+
+For any $t\in [t_{j,i-1}, t_{j, i}[$, the first two moments of $V$, $m_1(t)$ and $m_2(t) \equiv \mathbb{E}\left[V_t^2\right]$, can be computed by solving the following system
 \begin{equation}
@@
 \subsubsection{Moment Matching}
-A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape real parameters, $\xi_1, \xi_2$.
-
-To approximate the transition densities of  the process $V$ using a Beta distribution, we equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$ .
+
+A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape real parameters, $\xi_1, \xi_2$.{\color{red} Recall that the choice of the beta proxy distribution is a natural choice as it is the invariant distribution of the Jacobi type processes.}
+
+For any $t\in [t_{j,i-1}, t_{j, i}[$, we approximate the transition densities of the process $V$ using a Beta distribution.
+We equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$.
+{\color{red}See new notation for $\xi_1$ and $\xi_2$.}
 
@@
 \begin{equation}
-\xi_1 = - \frac{(\mu_t + 1 - \epsilon)(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2}\,, \quad \xi_2=  \frac{(\mu_t-1 + \epsilon )(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2} \,, \label{param_transformed_beta}
+\xi_1(t) = - \frac{(\mu_t + 1 - \epsilon)(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2}, \quad \xi_2(t)=  \frac{(\mu_t-1 + \epsilon )(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2} , \label{param_transformed_beta}
 \end{equation}
@@
 
-The approximate log-likelihood $\tilde{\ell}(\cdot ; v^{V, N+1})$ of the observed sample $v^{V, N+1}$ can be expressed as 
-\begin{equation}
- \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1, \xi_2)} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1 -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2 -1} \right\},
+The approximate log-likelihood $\tilde{\ell}(\cdot ; v^{M, N+1})$ of the observed sample $v^{M, N+1}$ can be expressed as 
+\begin{equation}
+ \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1(t_{j,i}), \xi_2(t_{j,i}))} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1(t_{j,i}) -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2(t_{j,i}) -1} \right\},
 \label{eq:loglikelihoodV}
 \end{equation}
-where the shape parameters $\xi_1$ and $\xi_2$, according to (\ref{param_transformed_beta}), depend on the quantities $\mu(t_{j,i};\bm{\theta} )$ and $\sigma^2(t_{j,i};\bm{\theta} )$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
+where the shape parameters $\xi_1(t_{j,i})$ and $\xi_2(t_{j,i})$, according to (\ref{param_transformed_beta}), depend on the quantities $\mu(t_{j,i};\bm{\theta} )$ and $\sigma^2(t_{j,i};\bm{\theta} )$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
+{\color{red}$B(\xi_1,\xi_1)$ denotes the Beta distribution with parameters $\xi_1$ and $\xi_2$.}
 
@@
 The drift coefficient $a(Z_t; p_t, \dot{p}_t, \bm{\theta}) $ of the process $Z$ that satisfies (\ref{eq:stindepSDE2}) is nonlinear.
-After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i})$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} Z_t$ :\\
+After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i}[$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} \left[Z_t\right]$:
 \begin{equation}
@@
 \end{equation*}
-The approximate Lamperti log-likelihood $\tilde{\ell}_L\left(\cdot ; z^{V, N+1}\right)$ for the observed sample $z^{V, N+1}$ is given by
-\begin{equation}
-\tilde{\ell}_L \left(\bm{\theta}; z^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i};\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}; \bm{\theta})} \Bigg) \right\},
+The approximate Lamperti log-likelihood $\tilde{\ell}_Z\left(\cdot ; z^{M, N+1}\right)$ for the observed sample $z^{M, N+1}$ is given by
+\begin{equation}
+\tilde{\ell}_Z \left(\bm{\theta}; z^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i};\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}; \bm{\theta})} \Bigg) \right\},
 \label{loglikelihoodZ}
@@
 \item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
-$(V_{j,i+1}|v_{j,i})$ is a random variable which conditional mean can be approximated for any $t\in [t_{j,i-1}, t_{j, i})$ by the solution of the system
+For any $t\in [t_{j,i-1}, t_{j, i}[$, we can approximate the first moment of $V$ by the solution of the system
 \begin{equation*}
 \begin{cases}
-\dif \E\left[V\right]&=-\theta_t\E\left[V\right]\dif t\\
-\E\left[V\right](t_{j,i})&=v_{j,i},
+\dif \E\left[V\right](t)&=-\theta_t\E\left[V\right](t)\dif t\\
+\E\left[V\right](t_{j,i-1})&=v_{j,i-1},
 \end{cases}
 \end{equation*}
-evaluated in $t_{j,i+1}$, i.e., $\E\left[V\right](t_{j,i+1})$.
-Then, the random variable $(V_{j,i+1}-\E\left[V\right](t_{j,i+1}))$ has zero mean.
-If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i},t_{j,i+1}]$, then $\E\left[V(t_{j,i+1})\right]=v_{j,i}e^{-c\Delta}$.
+evaluated in $t_{j,i}$, i.e., $\E\left[V\right](t_{j,i})$.
+Then, the random variable $(V_{j,i}-\E\left[V\right](t_{j,i}))$ has zero mean.
+If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i-1},t_{j,i}[$, then $\E\left[V\right](t_{j,i})=v_{j,i-1}e^{-c\Delta}$.
 If we have a total of $M\times N$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
@@
 \begin{split}
-c^*&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-\E\left[V\right](t_{j,i+1})\right)^2\right]\\
-&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}e^{-c\Delta}\right)^2\right]\\
-&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right)^2\right].
+c^*&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-\E\left[V\right](t_{j,i})\right)^2\right]\\
+&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}e^{-c\Delta}\right)^2\right]\\
+&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right)^2\right].
 \end{split}
@@
 \end{equation}
-As Equation (\ref{Eq-1}) is convex in $c$ (composition of convex is convex), it is enough to verify the first order optimality conditions. From
+As Equation (\ref{Eq-1}) is convex in $c$, it is enough to verify the first order optimality conditions. From
 \begin{equation*}
-\frac{\partial}{\partial c}\left[\sum_{j=1}^M\sum_{i=0}^{N-1}\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right)^2\right]=\sum_{j=1}^M\sum_{i=0}^{N-1}2v_{j,i}\Delta\left(v_{j,i+1}-v_{j,i}(1-c\Delta)\right),
+\frac{\partial}{\partial c}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right)^2\right]=\sum_{j=1}^M\sum_{i=1}^{N}2v_{j,i-1}\Delta\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right),
 \end{equation*}
@@
 \begin{equation}
-c^{*}=\frac{\sum_{j=1}^M\sum_{i=0}^{N-1}v_{j,i}(v_{j,i}-v_{j,i+1})}{\Delta\cdot\sum_{j=1}^M\sum_{i=0}^{N-1}(v_{j,i})^2}.
+c^{*}=\frac{\sum_{j=1}^M\sum_{i=1}^{N}v_{j,i-1}(v_{j,i-1}-v_{j,i})}{\Delta\cdot\sum_{j=1}^M\sum_{i=1}^{N}(v_{j,i-1})^2}.
 \label{Eq-4}
 \end{equation}
-
-\item \textbf{Quadratic variation:} We use the numerical Euler-Maruyama (E-M) scheme to approximate the solution to the SDE  \eqref{VtSDE}.
-In particular, we approximate the quadratic variation of the  It\^{o}'s  process $V$
+We are going to use Equation (\ref{Eq-4}) to approximate $\theta_0$ setting $\theta_0^*=c^*$.
+
+\item \textbf{Quadratic variation:} {\color{red}(removed E-M scheme stuff...)} We approximate the quadratic variation of the  It\^{o}'s  process $V$
 \begin{equation*}
@@
 \begin{equation}
-\bm{\theta}^*=\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=1}^{M,N}\right).
+\bm{\theta}^*=\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
 \label{FP}
 \end{equation}
-{\color{red}In this point, the likelihood has a maximum for the data set corresponding to that point.}
-We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
+At a fixed point, the likelihood has a maximum for the data set corresponding to that point. We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
 \begin{equation*}
-\bm{\theta}^*-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=1}^{M,N}\right)=0.
+\bm{\theta}^*-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right)=0.
 \end{equation*}
@@
 \begin{equation*}
-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i};\bm{\theta}^*)\}_{j=1,i=1}^{M,N}\right).
+\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^*)\}_{j=1,i=0}^{M,N}\right).
 \end{equation*}
@@
 
-For any $j=1, \ldots, M$, we extrapolate backward linearly the truncated prediction function to get its value at time $-\delta$,$p_{j,-\delta}$, and set $v_{t_{j,-\delta}}=0$.
+For any $j=1, \ldots, M$, we extrapolate backward linearly the truncated prediction function to get its value at time $t_{j,-\delta}$, $p_{j,-\delta}$, and set $v_{t_{j,-\delta}}=0$.
 We assume that the initial transition $(V_{j, 0}|v_{j,-\delta};\bm{\theta},\delta)$
-has a Beta distribution and apply to it the same moment matching method used above.
-Given a starting value for $\bm{\theta}$, we obtain the initial estimation for $\delta$ solving the following problem
-\begin{equation}
-\delta\approx\arg\max_{\delta}\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,-\delta};\bm{\theta},\delta\right),
+has a Beta distribution and apply to it the same moment matching method used above. Given a vector of parameters $\bm{\theta}$, we estimate $\delta$ solving the following problem
+\begin{equation}
+\delta\approx\arg\max_{\delta}\tilde{\mathcal{L}}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,-\delta};\bm{\theta},\delta\right),
 \label{eq:likelihood_delta}
 \end{equation}
-where $\mathcal{L}_\delta$ is the $\delta-$likelihood.
-To solve this problem, we repeat the steps described in subsection (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation for $p_{j,-\delta}$.\\
+where $\tilde{\mathcal{L}}_\delta$ is the approximated $\delta-$likelihood.
+To solve this problem, we repeat the steps described in Subsection \ref{Sec:MinLH}, with the additional initial step of creating the linear extrapolation for $p_{j,-\delta}$ at each $j\in\{1,2,\dots,M\}$.\\
 \quad\\
-As remarked, we extend the statistical model (\ref{likelihood}) to include the extra parameter $\delta$. The complete likelihood, $\mathcal{L}_c$, is given by
-\begin{equation}
-\mathcal{L}_c\left(\bm{\theta},\delta; v^{M,N +1}\right)=\mathcal{L}\left(\bm{\theta}; v^{M,N +1}\right)\mathcal{L}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right).
+As remarked, we extend the statistical model (\ref{likelihood}) to include the extra parameter $\delta$.
+The approximated complete likelihood $\tilde{\mathcal{L}}_c$, which estimates the vector $(\theta_0,\alpha,\delta)$, is given by
+\begin{equation}
+\tilde{\mathcal{L}}_c\left(\bm{\theta},\delta; v^{M,N +1}\right)=\tilde{\mathcal{L}}\left(\bm{\theta}; v^{M,N +1}\right)\tilde{\mathcal{L}}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right),
 \label{eq:complete_LH}
 \end{equation}
-As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the complete likelihood (\ref{eq:complete_LH}).
+where $\tilde{\mathcal{L}}\left(\bm{\theta}; v^{M,N +1}\right)$ is the non-log version of (\ref{likelihood}).
+As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the approximated complete likelihood (\ref{eq:complete_LH}).
 
@@
 
-{ \color{red} Show that 24h is enough to ensure independence?}
-All the following results involving a single provider refer to Provider A.
+All the following results involving a single provider refer to provider A.
 Also, all calibrations involve the training sets and all simulations, the test sets.
-Following the instruction for the initial guesses from section $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.
-
-\subsection{Calibration of the approximate negative log-likelihood in the $V-$space}
+Following the instruction for the initial guesses from Subsection $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.
+
+\subsection{Calibration of the approximate negative log-likelihood in $V$-space and $Z$-space}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.eps}
+\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.eps}\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood_testing.eps}
 \caption{Negative log-likelihood's level sets. All optimal values are located over the curve $\theta_0\alpha=0.097$.}
@@
 On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood.
-The numerical values of each important point can be seen in Table (\ref{tab:optimal_values}).
-We set $\bm{\theta}^V=(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood reaches its minimum value.
+The numerical values of each relevant point can be seen in Table (\ref{tab:optimal_values}).
+We set $(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood reaches its minimum value.
 \begin{table}[H]
@@
 Observe that all the local (possibly global) minimizers are located in curve $\theta_0\alpha=0.097$.
-We will explain this effect later, but it is a consequence of Markovianity and the indistinguishable observed transitions.
-
-\subsection{Calibration of the approximate negative log-likelihood in the $Z-$space}
+
+%\subsection{Calibration of the approximate negative log-likelihood in the $Z-$space}
 
@@
 
-We obtain $(\theta_0^Z,\alpha^Z)=(1.87,0.043)$ as a minimizer for the relative error function (\ref{eq:rel_error}).\\
+We obtain $(\theta_0^Z,\alpha^Z)=(1.87,0.043)$ as a minimizer for the relative error function (\ref{eq:rel_error}) using \textit{fminsearch} from MATLAB R2019b.\\
 \quad\\
@@
 \dif X_t&= \big(\dot{p}_t  - \theta_t (X_t - p_t) \big) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]\\
-X_0&=x_0\in (0,1) \,,
+X_0&=x_0\in [0,1],
 \end{cases}.  \label{Model2}
 \end{equation}
- with $\theta_0 > 0, \, \alpha > 0$ and $\theta_t$ satisfying the condition \eqref{Assumption:3} .
+ with $\theta_0 > 0$, $\alpha > 0$ and $\theta_t$ satisfying condition \eqref{Assumption:3} .
 \end{itemize}
-To show the better performance of Model 2, we calculate the Akaike information criterion (AIC) and Bayesian information criterion (BIC) for each provider, each model, and different proxies densities.
-Table (\ref{tab:model_comparison}) summarizes this computations.
-We can observe that the best fitting is achieved with Model 2 and Beta proxies.
+To show the better performance of Model 2, we have computed the Akaike information criterion (AIC) and the Bayesian information criterion (BIC) for the two considered models, and any combination of the three different forecast providers with the three approximate likelihood methods.
+Table (\ref{tab:model_comparison}) summarizes these results, also reporting the estimate of the variability diffusion coefficient $\alpha \theta_0$.
+It is worth observing that the best fitting is achieved with Model 2 and adopting Beta distributions as proxies of the transition densities.
 
@@
 \includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/4.eps}
-\caption{Four arbitrary days with five simulated wind power production paths each. }
+\caption{Four arbitrary days with five simulated wind power production paths each.}
 \label{fig:simulation_paths}
 \end{figure}
-On the basis of the approximate MLEs for Model 2, we can obtain empirical pointwise confidence bands for the wind power production.
-Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
+Once derived optimal estimates of the parameters of the complete likelihood for Model 2, we obtain empirical pointwise confidence bands for wind power production.
+Figure (\ref{fig:confidence_bands}) shows the empirical pointwise confidence bands for wind power production for each day of interest, assuming Model 2 specification, a given forecaster, and 5000 simulations per day.
 
@@
 
-We have proposed a method to produce stochastic wind power forecasts based on parametric SDEs.
-This method is agnostic of the wind power forecasting technology.
-Using this method, we were able to simulate future wind power production paths and obtain confidence bands.
-We conclude that Model 2 is a best-fit model.
-It features time-derivative tracking of the forecast, time-dependent mean reversion parameter, and a more natural diffusion term.
-Moreover, the model preserves the asymmetry of wind power forecast errors and their correlation structure.
-
-We were also able to compare three different forecast providers with respect to their real-world performance on the aggregated data set and on specific wind farm sites.
-Finally, the model paves the way for stochastic optimal control methods enabling optimal decision making under uncertainty.
+In this work, we propose a methodology to assess the short-term forecast of the normalized wind power, which is agnostic of the wind power forecasting technology.
+
+To this purpose, we built a phenomenological stochastic differential equation model for the normalized wind power production forecast error, with time-varying mean-reversion parameter in the linear drift coefficient, and state-dependent and time non-homogenous diffusion coefficient.
+We also used the Lamperti transform with unknown parameters to provide a version of the proposed model with a unit diffusion coefficient, increasing its stability properties.
+
+We used approximate likelihood-based methods for the models' calibration, developing original algorithms to derive optimal estimates of the unknown parameters.
+The likelihood approach has allowed extending the SDE models in a very effective way, incorporating an early transition with an additional parameter that accounts for the forecast's uncertainty at the beginning of each future period.
+As a result, we obtained a robust procedure for synthetic data generation that, using the available forecast input, allows embracing the future wind power production paths through empirical pointwise bands with prescribed confidence.
+
+On the basis of historical data of wind power production and forecast from different sources, our method comes up with an objective tool for forecast assessment and comparison, by performing the model selection stage.
+The application of the procedure of modeling, inference through numerical optimization, and model selection through information criteria, to the wind power production real dataset in Uruguay during April-December 2019, with three different providers, shown the excellent performance of our proposed model, that preserves the asymmetry of wind power forecast errors and their correlation structure.
+
+ We conclude that our SDE model, featuring the time-derivative tracking of the forecast, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward managing of renewable energies efficiently.
+This methodology paves the way for stochastic optimal control methods enabling principled decision making under uncertainty in the presence of complex energy matrix.
 
@@
 \begin{equation}\label{eq:eds1}
-X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)\dif s  + \int_0^t\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s, \quad 0<x_0<1.
-\end{equation}
-According to Proposition 2.13, p.291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X$ to \eqref{eq:eds1}.
+X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)\dif s  + \int_0^t\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s, \quad 0\leq x_0\leq1.
+\end{equation}
+According to Proposition 2.13, p.291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X_t$ to \eqref{eq:eds1}.
 Moreover, as the diffusion coefficient is of linear growth, we have  for all $p>0$
 \begin{equation}\label{prop:fm}
-\mathbb E[ \sup_{t\in[0,T]}|X_t|^p]<\infty.
+\mathbb E\left[ \sup_{t\in[0,T]}|X_t|^p\right]<\infty.
 \end{equation}
 Then, it remains to show that for all $t\in[0,T]$, $X_t\in[0,1]$ a.s.
-For this aim, we need to use the so-called Yamada function $\psi_n$ that is a $\mathcal C^2$ function that satisfies a bench of useful properties:
+For this aim, we need to use the so-called Yamada function $\psi_n$ that is a $\mathcal C^2$ function that satisfies a bunch of useful properties:
 \begin{align*}
 &|\psi_n(x)|\underset{n\rightarrow+\infty}{\rightarrow}|x|, \;\; x{\psi'}_n(x)\underset{n\rightarrow+\infty}{\rightarrow}|x|, \;\; |\psi_n(x)|\wedge |x{\psi'}_n(x)| \le |x|\\
-&{\psi'}_n(x)\le 1, \;\; \mbox{ and } {\psi''}_n(x)=g_n(|x|)\ge 0\;\; \mbox{ with } \;\; g_n(x)x\le \frac 2n\;\;  \mbox{ for all } x\in \mathbb R .
+&{\psi'}_n(x)\le 1, \;\; \mbox{and}\;\; {\psi''}_n(x)=g_n(|x|)\ge 0\;\; \mbox{with} \;\; g_n(x)x\le \frac 2n\;\;  \mbox{for all}\;\; x\in \mathbb R .
 \end{align*}
@@
 \end{align*}
-Now, thanks to  \eqref{Assumption:1}, \eqref{prop:fm} and to the above properties of $\psi_n$ and $g_n$, we get
-$$
-\mathbb E[\psi_n(X_t)]\le \psi_n(x_0) +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \big)\dif s + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E |1-X_s|\dif s.
-$$
-Therefore, letting $n$ tends to infinity we use Lebesgue's theorem to get
-$$
-\mathbb E[|X_t|]\le x_0 +\int_0^t \big(\dot p_s + \theta_sp_s -  \theta_s \mathbb E|X_s| \big)\dif s.
+Now, thanks to  \eqref{Assumption:1}, \eqref{prop:fm}, and to the above properties of $\psi_n$ and $g_n$, we get
+$$
+\mathbb E\left[\psi_n(X_t)\right]\le \psi_n(x_0) +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \right)\dif s + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E \left[|1-X_s|\right]\dif s.
+$$
+Therefore, letting $n$ tends to infinity, we use Lebesgue's theorem to get
+$$
+\mathbb E\left[|X_t|\right]\le x_0 +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E\left[|X_s|\right] \right)\dif s.
 $$
@@
 $$
-\mathbb E[|X_t| -X_t ]\le \int_0^t \theta_s \mathbb E[ X_s - |X_s| ]\dif s.
-$$
-Then, Gronwall's lemma gives us $\mathbb E[|X_t|]=\mathbb E X_t$ and thus for any $t\in[0,T]$ $X_t\ge0$ a.s.
+\mathbb E\left[|X_t| -X_t \right]\le \int_0^t \theta_s \mathbb E\left[ X_s - |X_s| \right]\dif s.
+$$
+Then, Gronwall's lemma gives us $\mathbb E\left[|X_t|\right]=\mathbb E \left[X_t\right]$ and thus for any $t\in[0,T]$ $X_t\ge0$ a.s.
 The same arguments work to prove that  for any $t\in[0,T]$ $Y_t:=1-X_t\ge0$  a.s.

### 2020-06-09 MATLAB_Files/fixed_point_function.m

@@ -2,7 +2,7 @@ function [fval] = fixed_point_function(batch, x0, dt)
 
     [x1,~] = likelihood_nested_optimization_L(batch, x0, dt);
 
-    fval = abs(x1(1)-x0(1))/x0(1) + abs(x1(2)-x0(2))/x0(2);
-%     fval = abs(x1(1)*x1(2)-x0(1)*x0(2)) / (x0(1)*x0(2));
+%     fval = abs(x1(1)-x0(1))/x0(1) + abs(x1(2)-x0(2))/x0(2);
+    fval = abs(x1(1)*x1(2)-x0(1)*x0(2)) / (x0(1)*x0(2));
 
 end

### 2020-06-09 MATLAB_Files/optimizeLogLikelihood.m

@@ -9,7 +9,8 @@ dataSet       = 'MTLOG';
 epsilon       = 0.020;
 % dataKind can be classic or comparable.
 dataKind      = 'comparable';
-[Ta_Tra_Comp] = load_data_eps(epsilon,dataSet,dataKind);
+dataNumber    = 'testing';
+[Ta_Tra_Comp] = load_data_eps(epsilon,dataSet,dataKind,dataNumber);
 
 Date              = Ta_Tra_Comp.Date;
 Time              = Ta_Tra_Comp.Time;
@@ -55,6 +56,13 @@ if strcmp(likelihood,'normal')
     % fmincon    -> Theta_0 = 1.577, Alpha = 0.0615, prod = 0.0970 (24/04/2020).
     % fminunc    -> Theta_0 = 1.544, Alpha = 0.0628, prod = 0.0970 (24/04/2020).
     % eval       -> Theta_0 = 1.930, Alpha = 0.0500, prod = 0.0965 (20/05/2020).
+    
+    % For the testing data:
+    % Initial    -> Theta_0 = 1.963, Alpha = 0.0527, prod = 0.1036 (09/06/2020).
+    % fminsearch -> Theta_0 = 1.642, Alpha = 0.0542, prod = 0.0890 (08/06/2020).
+    % fmincon    -> Theta_0 = 1.632, Alpha = 0.0545, prod = 0.0890 (08/06/2020).
+    % fminunc    -> Theta_0 = 1.963, Alpha = 0.0454, prod = 0.0891 (08/06/2020).
+    % eval       -> Theta_0 = 1.590, Alpha = 0.0560, prod = 0.0890 (08/06/2020).
     
 elseif strcmp(likelihood,'lamperti')
     

### 2020-06-09 LaTeX_Code/Paper/paper_1line.tex
All corrections were done in paper

@@
 \begin{equation}
-\mathcal{L}\left(\bm{\theta}; V^{M,N +1}\right) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho ( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} )    \right\},
+\mathcal{L}\left(\bm{\theta}; V^{M,N +1}\right) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho \left( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} \right)    \right\},
 \label{likelihood}
@@
 \begin{equation}
- \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1(t_{j,i}), \xi_2(t_{j,i}))} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1(t_{j,i}) -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2(t_{j,i}) -1} \right\},
+ \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1(t_{j,i}^-), \xi_2(t_{j,i}^-))} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1(t_{j,i}^-) -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2(t_{j,i}^-) -1} \right\},
 \label{eq:loglikelihoodV}
 \end{equation}
-where the shape parameters $\xi_1(t_{j,i})$ and $\xi_2(t_{j,i})$, according to (\ref{param_transformed_beta}), depend on the quantities $\mu(t_{j,i};\bm{\theta} )$ and $\sigma^2(t_{j,i};\bm{\theta} )$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
-$B(\xi_1,\xi_1)$ denotes the Beta distribution with parameters $\xi_1$ and $\xi_2$.
+where the shape parameters $\xi_1(t_{j,i}^-)$ and $\xi_2(t_{j,i}^-)$, according to (\ref{param_transformed_beta}), depend on the limit quantities $\mu(t_{j,i}^-;\bm{\theta} )$ and $\sigma^2(t_{j,i}^-;\bm{\theta} )$ as $t\uparrow t_{j,i}$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
+$B(\xi_1,\xi_2)$ denotes the Beta distribution with parameters $\xi_1$ and $\xi_2$.
 
@@
 \begin{equation}
-\tilde{\ell}_Z \left(\bm{\theta}; z^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i};\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}; \bm{\theta})} \Bigg) \right\},
+\tilde{\ell}_Z \left(\bm{\theta}; z^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}^-; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i}^-;\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}^-; \bm{\theta})} \Bigg) \right\},
 \label{loglikelihoodZ}
 \end{equation}
-where $\tilde{\mu}_Z(t_{j,i};\bm{\theta} )$ and $\tilde{v}_Z(t_{j,i};\bm{\theta} )$ are computed solving numerically the initial-value problem (\ref{Ztmom}).
+where the limits $\tilde{\mu}_Z(t_{j,i}^-;\bm{\theta} )$ and $\tilde{v}_Z(t_{j,i}^-;\bm{\theta} )$ are computed solving numerically the initial-value problem (\ref{Ztmom}).
 
 \subsection{Algorithm for the approximate maximum likelihood estimations} \label{opt_sec}
+
+\red{In this Subsection, we aim to infer the model's parameters using optimization techniques.
+We start by finding an initial guess close enough to the optimal value, and from that point, start the optimization.}
 
@@
 \end{equation*}
-evaluated in $t_{j,i}$, i.e., $\E\left[V\right](t_{j,i})$.
-Then, the random variable $(V_{j,i}-\E\left[V\right](t_{j,i}))$ has zero mean.
-If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i-1},t_{j,i}[$, then $\E\left[V\right](t_{j,i})=v_{j,i-1}e^{-c\Delta}$.
+in the limit $t\uparrow t_{j,i}$, i.e., $\E\left[V\right](t_{j,i}^-)$.
+Then, the random variable $(V_{j,i}-\E\left[V\right](t_{j,i}^-))$ has zero mean.
+If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i-1},t_{j,i}[$, then $\E\left[V\right](t_{j,i}^-)=v_{j,i-1}e^{-c\Delta}$.
 If we have a total of $M\times N$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
@@
 \begin{split}
-c^*&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-\E\left[V\right](t_{j,i})\right)^2\right]\\
+\hat{c}&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-\E\left[V\right](t_{j,i}^-)\right)^2\right]\\
 &=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}e^{-c\Delta}\right)^2\right]\\
@@
 \begin{equation}
-c^{*}=\frac{\sum_{j=1}^M\sum_{i=1}^{N}v_{j,i-1}(v_{j,i-1}-v_{j,i})}{\Delta\cdot\sum_{j=1}^M\sum_{i=1}^{N}(v_{j,i-1})^2}.
+\hat{c}\approx\frac{\sum_{j=1}^M\sum_{i=1}^{N}v_{j,i-1}(v_{j,i-1}-v_{j,i})}{\Delta\cdot\sum_{j=1}^M\sum_{i=1}^{N}(v_{j,i-1})^2}.
 \label{Eq-4}
 \end{equation}
-\red{We approximate $\theta_0$ by Equation (\ref{Eq-4}) setting $\theta_0^*=c^*$.}
+\red{We approximate $\theta_0$ by Equation (\ref{Eq-4}) setting $\theta_0^*=\hat{c}$.}
 
@@
 Let $v^{M,N+1}$ be the observed data, and $h( v_{j,i},t_{j,i};\bm{\theta})$ the Lamperti transform of the observation $v_{j,i}$.
-The transformed observations $z^{M,N+1}$ depend on the parameter $\bm{\theta}$.\\
+As we can see in Section \ref{Section_4}, the transformed observations $z^{M,N+1}$ depend on the vector $\bm{\theta}$.\\
 The problem of maximizing the approximated Lamperti log-likelihood (\ref{loglikelihoodZ}), i.e.,  $$\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta}; z^{M,N+1}\right),$$
@@
 \begin{equation}
-\delta\approx\arg\max_{\delta}\tilde{\mathcal{L}}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,-\delta};\bm{\theta},\delta\right),
+\arg\max_{\delta}\tilde{\mathcal{L}}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,-\delta};\bm{\theta},\delta\right),
 \label{eq:likelihood_delta}
@@
 where $\tilde{\mathcal{L}}\left(\bm{\theta}; v^{M,N +1}\right)$ is the non-log version of (\ref{likelihood}).
-As we may provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the approximated complete likelihood (\ref{eq:complete_LH}).
+As we can provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the approximated complete likelihood (\ref{eq:complete_LH}).
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.eps}\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood_testing.eps}
+\includegraphics[width=0.5\textwidth]{plots/LL/Log-Likelihood.eps}\includegraphics[width=0.5\textwidth]{plots/LL/Log-Likelihood_testing.eps}
 \caption{\red{Negative log-likelihood's level sets for the training sets (plot on the left), and for the test sets (plot on the right).
@@
 \red{On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood for both training and test sets.} The numerical values of each relevant point can be seen in Table (\ref{tab:optimal_values}).
-We set $(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood for the training sets reaches its minimum value.
+We set the optimal parameters in the $V$-space $(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood for the training sets reaches its minimum value.
 \begin{table}[H]
@@
  \midrule
- Initial guess & 1.54 & 0.070 & 0.111 & 1.96 & 0.053 & 0.104 \\
+ Initial guess & 1.54 & 0.072 & 0.111 & 1.96 & 0.053 & 0.104 \\
  fminsearch & 1.14 & 0.076 & 0.097 & 1.64 & 0.054 & 0.089 \\
@@
 \end{table}
-Observe that all the local (possibly global) minimizers are located over the curves $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.
+\red{Observe that all the local (possibly global) minimizers are located over the curves $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.
+This effect shows that the optimization is more sensitive to the diffusion than to the drift.}\\
 
@@
 
-We obtain $(\theta_0^Z,\alpha^Z)=(1.87,0.043)$ as a minimizer for the relative error function (\ref{eq:rel_error}) using \textit{fminsearch} from MATLAB R2019b.\\
-\quad\\
+In the $Z$-space, we obtain the optimal parameters $(\theta_0^Z,\alpha^Z)=(1.87,0.043)$ as a minimizer for the relative error function (\ref{eq:rel_error}) using \textit{fminsearch} from MATLAB R2019b and the training sets.\\
+
 To verify and compare this two vector of parameters, (i.e., $(\theta_0^V,\alpha^V)$ and $(\theta_0^Z,\alpha^Z)$), we simulate error paths in the $V-$space.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic_noDelta/Optimal.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic_noDelta/Lamperti_Optimal.eps}
+\includegraphics[width=0.45\textwidth]{plots/classic_noDelta/Optimal.eps}
+\includegraphics[width=0.45\textwidth]{plots/classic_noDelta/Lamperti_Optimal.eps}
 \caption{Probability histograms for the error transitions.
@@
 Forecast Provider & Parameters $(\theta_0, \alpha)$ & Product $\theta_0\alpha$ \\ \midrule
-Provider A  & $(1.930,0.050)$  &  0.097 \\
-Provider B  & $(1.420,0.069) $  &  0.098 \\ 
-Provider C  & $(1.380,0.078) $  &  0.108 \\ 
+Provider A  & $(1.93,0.050)$  &  0.097 \\
+Provider B  & $(1.42,0.069) $  &  0.098 \\ 
+Provider C  & $(1.38,0.078) $  &  0.108 \\ 
 \bottomrule
@@
 \centering
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/1.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/2.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/paths/1.eps}
+\includegraphics[width=0.45\textwidth]{plots/paths/2.eps}\\
 \quad\\
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/3.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/4.eps}
+\includegraphics[width=0.45\textwidth]{plots/paths/3.eps}
+\includegraphics[width=0.45\textwidth]{plots/paths/4.eps}
 \caption{Four arbitrary days with five simulated wind power production paths each.}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/1.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/2.eps}\\
+\includegraphics[width=0.45\textwidth]{plots/bands/1.eps}
+\includegraphics[width=0.45\textwidth]{plots/bands/2.eps}\\
 \quad\\
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/3.eps}
-\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/4.eps}
+\includegraphics[width=0.45\textwidth]{plots/bands/3.eps}
+\includegraphics[width=0.45\textwidth]{plots/bands/4.eps}
 \caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(2.22,0.044,0.054)$. Blue line: real production.}
@@
 \subsubsection{Value of $\delta$}
-As a final verification, we study the behavior of $\delta$ as a function of $\bm{\theta}$.
+As a final verification, we study the behavior of $\delta$ as a function of the vector $\bm{\theta}$.
 Given a vector of parameters, we calculate an initial guess for $\delta$ solving problem (\ref{eq:likelihood_delta}).
@@
 \centering
-\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/delta/contour_delta.eps}
+\includegraphics[width=0.7\textwidth]{plots/delta/contour_delta.eps}
 \caption{Initial value for $\delta$ as a function of the elements of the parameter vector $\bm{\theta}$.}

### 2020-06-09 LaTeX_Code/Paper/paper_1line.tex
Removed comments from paper

@@
 The application of  It\^{o}'s lemma % on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s \dif s}$, leads to
-leads to \red{(here we reduced the step-by-step...)}
+leads to
 %\begin{equation*}
@@
 We equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$.
-\red{(See new notation for $\xi_1$ and $\xi_2$...)}
 
@@
 
-\item \textbf{Quadratic variation:} \red{(Does this sentence have sense now?)} We approximate the quadratic variation of the  It\^{o}'s  process $V$
+\item \textbf{Quadratic variation:} We approximate the quadratic variation of the  It\^{o}'s  process $V$
 \begin{equation*}

### 2020-06-09 LaTeX_Code/Paper/paper_1line_Renzo.tex
Removed comments from paper

@@
 We equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$.
-{\color{red}See new notation for $\xi_1$ and $\xi_2$.}
 
@@
 
-\item \textbf{Quadratic variation:} {\color{red}(removed E-M scheme stuff...)} We approximate the quadratic variation of the  It\^{o}'s  process $V$
+\item \textbf{Quadratic variation:}  We approximate the quadratic variation of the  It\^{o}'s  process $V$
 \begin{equation*}

### 2020-06-23 LaTeX_Code/Paper/paper_1line.tex
Corrected some typos in the paper
Added corrections (english) to paper

@@
 \newtheorem{Res}[Def]{Result}
-\newcommand{\red}{\textcolor{red}}
+\newcommand{\red}{\textcolor{black}}
 \newcommand{\E}{\mathbb{E}}
@@
 The methodology we developed allows the simulation of future wind power production paths and to obtain sharp empirical confidence bands.
-All the procedure is agnostic of the forecasting technology and enables comparing different forecast providers.
-We apply the model to historical Uruguayan wind power production data and forecasts during the period April-December 2019.
+All the procedures are agnostic of the forecasting technology, and they enable comparisons between different forecast providers.
+We apply the model to historical Uruguayan wind power production data and forecasts between April and December 2019.
 
@@
 
-Keywords: Wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform,
-
-numerical optimizaton, model selection.
+Keywords: wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, numerical optimization, model selection
 
@@
 
-Despite the Covid-19 pandemic caused ``the biggest shock to the global energy system in more than seven decades'' and the recent report released on April 30, 2020, by the International Energy Agency (\url{https://www.iea.org/reports/global-energy-review-2020}) stresses that projections of energy demand will fall 6\% in 2020 - seven times the decline after the 2008 global financial crisis - it is emphasized that ``renewables are set to be the only energy source that will grow in 2020, with their share of global electricity generation projected to jump thanks to their priority access to grids and low operating cost'' (\cite{IEA}).
-
-Although the growth of renewables in electricity generation in 2020 is set to be lower than in previous years,  solar PV and wind are on track to help lift renewable electricity generation by 5\% in 2020, aided by higher output from hydropower.
+Despite the Covid-19 pandemic causing ``the biggest shock to the global energy system in more than seven decades'' the recent report released on April 30, 2020, by the International Energy Agency (\url{https://www.iea.org/reports/global-energy-review-2020}) stresses that projections of energy demand will fall 6\% in 2020 -- seven times the decline after the 2008 global financial crisis -- It is emphasized that ``renewables are set to be the only energy source that will grow in 2020, with their share of global electricity generation projected to jump thanks to their priority access to grids and low operating cost'' (\cite{IEA}).
+
+Although the growth of renewables in electricity generation in 2020 is set to be lower than in previous years,  solar photo-voltaic (PV) and wind are on track to help lift renewable electricity generation by 5\% in 2020, aided by higher output from hydropower.
 \\
@@
 \item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
-\item Operation scheduling of controlable power plants.
+\item Operation scheduling of controllable power plants.
 \item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
@@
 %Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations.
- {\color{red} Some interesting works have been devoted to probabilistic forecasting related to renewable energies based on stochastic differential equations, among them (\cite{mozuma}) on wind power forecast, (\cite{immm}) and (\cite{bggk}) on forecasts of solar irradiance.}
+ {\color{black} Some interesting works have been devoted to probabilistic forecasting related to renewable energies based on stochastic differential equations, among them (\cite{mozuma}) on wind power forecast, (\cite{immm}) and (\cite{bggk}) on forecasts of solar irradiance.}
 Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion, and non-Gaussian approximations.
@@
 The rest of the paper is organized as follows.
-In Section \ref{Section_2}, we introduce the main characteristics of a real data set encompassing the normalized wind power production in Uruguay during the period April-December 2019, joint with the most accurate predictions, as highlighted in our posterior analysis, performed by one out of the three sources of forecast providers.
+In Section \ref{Section_2}, we introduce the main characteristics of a real data set encompassing the normalized wind power production in Uruguay between April and December 2019, with the most accurate predictions, as highlighted in our posterior analysis, performed by one out of the three sources of forecast providers.
 The significant steps for constructing phenomenological models of the normalized wind power production and the forecast error based on stochastic differential equations are described in Section \ref{Section_3}.
@@
 In recent years, Uruguay has triggered a remarkable change in its energy matrix.
-In (\cite{irena}, p.23), Uruguay is among those countries showcasing innovation, like Denmark, Ireland, Germany, Portugal, and Spain, with proven feasibility of managing annual variable renewable energy (VRE) higher than 25\% in power systems.
-
-According to (\cite{ren21}, pp.118-119), in 2018, Uruguay achieved 36\% of its electricity production from variable wind energy and solar PV, raising the share of generation from wind energy more than five-fold in just four years, from 6.2\% in 2014 to 33\% in 2018.
+In (\cite{irena}, p.23), Uruguay was among those countries showcasing innovation, like Denmark, Ireland, Germany, Portugal, and Spain, with proven feasibility of managing annual variable renewable energy (VRE) higher than 25\% in power systems.
+
+According to (\cite{ren21}, pp.118--119), in 2018, Uruguay achieved 36\% of its electricity production from variable wind energy and solar PV, raising the share of generation from wind energy more than five-fold in just four years, from 6.2\% in 2014 to 33\% in 2018.
 
 At present, Uruguay is fostering even higher levels of wind penetration by boosting regional power trading with Argentina and Brazil. 
-In this rapidly evolving scenario, it is essential to analyze national data on wind power production joint with wind power short-term forecastings to orientate and assess the strategies and decisions of wind energy actors and businesses.
-
-Our study is based on publicly available data (source: Administrator of Electric Market) on the wind power production in Uruguay for the period April-December 2019, that we adequately normalized with respect to the present $\SI{1474}{\mega\watt}$ maximum installed wind power capacity.
+In this rapidly evolving scenario, it is essential to analyze national data on wind power production with wind power short-term forecastings to orientate and assess the strategies and decisions of wind energy actors and businesses.
+
+Our study is based on publicly available data (source: Administrator of Electric Market) on the wind power production in Uruguay between April and December 2019, that we adequately normalized with respect to the present $\SI{1474}{\mega\watt}$ maximum installed wind power capacity.
 Each day, wind power production recordings are available every ten minutes.
-In this work, we have also considered data from three different forecast providers, available each day starting at 1 pm.
-
-The next Figure \ref{fig:sample_data} shows the wind power real production during four segments 24-hour long selected from the observation period together with their corresponding hourly short-term forecast, computed by a forecast provider.
-For the sake of visualization clarity, this Section relies only on forecasts from one provider, called "provider A" from now on, ranked as the most accurate forecast provider, as it emerged from our posterior analysis.
+In this work, we also considered data from three different forecast providers, available each day starting at 1 pm.
+
+The next Figure \ref{fig:sample_data} shows the wind power real production during four segments 24 hours selected from the observation period together with their corresponding hourly short-term forecast, computed by a forecast provider.
+For the sake of visualization clarity, this section relies only on forecasts from one provider, called ``provider A'' from now on, ranked as the most accurate forecast provider, as it emerged from our posterior analysis.
 
@@
 Once we removed all the 24-hour segments showing wind curtailment, we set up a dataset containing 147 daily segments. 
-In the absence of the curtailment intervention, the forecast error histograms are shown below in Figure \ref{fig:data_after_clean}, where it can be appreciated skewness reduction, except for low power forecast errors histogram.
+In the absence of the curtailment intervention, the forecast error histograms shown below in Figure \ref{fig:data_after_clean}, can appreciate skewness reduction, except for low power forecast error histogram.
 
@@
 In this stage of data preprocessing, we obtain another useful result by applying the first-order difference operator to the forecast errors. 
-The forecast error transition histograms, displayed in the next Figure \ref{fig:error_transitions}, will constitute later a reference for the visual assessment of the global fit of the proposed models.
+The forecast error transition histograms, displayed in the next Figure \ref{fig:error_transitions}, will later constitute a reference for the visual assessment of the global fit of the proposed models.
 
@@
 
-The histograms in Figure \ref{fig:error_transitions} feature a non-Gaussianity trait and provide initial input for the model-building stage, which is described in Section next.
+The histograms in Figure \ref{fig:error_transitions} feature a non-Gaussianity trait and provide initial input for the model-building stage, which is described in the next section.
 Later, in Section \ref{Section_4}, guided from inferring the unknown model parameters, we will also propose transforming data as a strategy that naturally leads to an alternative model.
@@
 
-In this work, $(p_t)_{t \in [0,T]}$ is to be considered as a deterministic forecast for the normalized wind power generation, which is provided by an official source.
+In this work, $(p_t)_{t \in [0,T]}$ is to be considered a deterministic forecast for the normalized wind power generation, which is provided by an official source.
 
@@
 Our model (\ref{VtSDE}) for the forecast error has a diffusion term that depends on the state variable $V_t$.
-Under the conditions that permit to use It\^{o}'s formula on a well-chosen transformation of the process $V$, John Lamperti (\cite{lamp}) first showed that the transformed process is again a diffusion that is solution to a SDE with unit coefficient for the diffusion term.
-A vast literature refers nowadays to this result as the so-called Lamperti transform (see, for example, \cite[40--41]{iacus1}, \cite{moma}, \cite[199--203]{pani}, \cite[98--100]{saso}), which is a basic tool to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
+Under the conditions that permit the use of It\^{o}'s formula on a well-chosen transformation of the process $V$, John Lamperti (\cite{lamp}) first showed that the transformed process is again a diffusion process that is solution to a SDE with unit coefficient for the diffusion term.
+The vast literature nowadays refers to this result as the so-called Lamperti transform (see, for example, \cite[40--41]{iacus1}; \cite{moma}; \cite[199--203]{pani}; \cite[98--100]{saso}), which is a basic tool to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
 A remarkable effect of removing the state dependency from the random noise term is to increase the numerical stability of the simulated paths of the transformed process.
@@
 \includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
-\caption{Lamperti transformed forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
+\caption{Lamperti transformed forecast error transition histograms between April and December 2019 without wind power production curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
   \label{fig:LP_transitions}
@@
 
-The shape of the forecast error transition histograms after applying the Lamperti transform has much resemblance with a Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process $Z_t$.
+The shape of the forecast error transition histograms after applying the Lamperti transform has similarities with the Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process $Z_t$.
 
@@
 
-\red{Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at a different time $t_j$ with $j = 1, \dots, M$, is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
+\red{Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at a different time $t_j$ with $j = 1, \dots, M$, sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
 Let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}$.}
@@
 
-Remark: In the last Subsection of this Section, we will extend the statistical model (\ref{likelihood}) by adding the transition that occurs during the time interval, say of length $\delta$, between the epoch when the forecast is done and the first epoch (1 pm) of each day-ahead forecast.
+Remark: In the last subsection of this section, we will extend the statistical model (\ref{likelihood}) by adding the transition that occurs during the time interval, say of length $\delta$, between the epoch when the forecast is done and the first epoch (1 pm) of each day-ahead forecast.
 To this purpose, the likelihood function (\ref{likelihood}) must include for any of the $M$ paths an additional factor, say $\rho_0 (V_{j, 0}|V_{j, -\delta};\bm{\theta},\delta)$, expressing the conditional density of the early transition.
@@
 
-The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}, \cite[61-68]{saso}):
+The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}; \cite[61-68]{saso}):
 
@@
 
-However, closed-form solutions to initial-boundary value problem for time-inhomogeneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
-Besides, in our case, solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
-Several numerical techniques have been devised to obtain estimates for the unknown parameters of continuous-time SDE models with discrete observations (see, for example, \cite{prewo} for likelihood-based inference techniques, \cite{Sor} for an estimating function approach, to mention a few contributions).
-As explained in the next Subsection, we have considered approximate likelihood methods, similar in spirit to \autocite[Section 11.4]{saso}.
+However, closed-form solutions to initial-boundary value problems for time-inhomogeneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
+In our case, solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
+Several numerical techniques have been devised to obtain estimates for the unknown parameters of continuous-time SDE models with discrete observations (see, for example, \cite{prewo} for likelihood-based inference techniques, \cite{Sor} for an estimating function approach).
+As explained in the next subsection, we have considered approximate likelihood methods, similar in spirit to \autocite[Section 11.4]{saso}.
 
@@
 
-A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape real parameters, $\xi_1, \xi_2$.
+A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive real-valued shape parameters, $\xi_1, \xi_2$.
 \red{Recall that the choice of the beta proxy distribution is a natural choice as it is the invariant distribution of the Jacobi type processes.}
@@
 
-\red{In this Subsection, we aim to infer the model's parameters using optimization techniques.
+\red{In this subsection, we aim to infer the model's parameters using optimization techniques.
 We start by finding an initial guess close enough to the optimal value, and from that point, start the optimization.}
@@
 \item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
-\red{For any $t\in [t_{j,i-1}, t_{j, i}[$, the random variable $(V_{j,i}|v_{j,i-1})$ has a conditional mean that can be approximate by the solution of the system}
+\red{For any $t\in [t_{j,i-1}, t_{j, i}[$, the random variable $(V_{j,i}|v_{j,i-1})$ has a conditional mean that can be approximated by the solution of the system}
 \begin{equation*}
@@
 
-Our statistical analysis starts with partitioning the 147 segments of normalized wind power production, each 24-hour long.
+Our statistical analysis starts with partitioning the 147 segments of normalized wind power production, each 24-hours long.
 We select 73 non-contiguous segments for the models' calibration procedure, assigning them to the training set.
@@
 All the following results involving a single provider refer to provider A.
-Also, all calibrations involve the training sets and all simulations, the test sets.
+Furthermore, all calibrations involve the training sets and all simulations, the test sets.
 Following the instruction for the initial guesses from Subsection $\ref{opt_sec}$, we obtain the initial guess $(\theta_0^*,\alpha^*,\delta^*)\approx(1.54,0.072,073)$.
@@
  fminunc & 1.54 & 0.063 & 0.097 & 1.96 & 0.045 & 0.089 \\
- evaluations & 1.93 & 0.050 & 0.097 & 1.59 & 0.056 & 0.089 \\
+ Evaluations & 1.93 & 0.050 & 0.097 & 1.59 & 0.056 & 0.089 \\
  \bottomrule
@@
 \end{table}
-\red{Observe that all the local (possibly global) minimizers are located over the curves $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.
+\red{We observe that all the local (possibly global) minimizers are located over the curves $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.
 This effect shows that the optimization is more sensitive to the diffusion than to the drift.}\\
@@
 
-In the $Z$-space, we obtain the optimal parameters $(\theta_0^Z,\alpha^Z)=(1.87,0.043)$ as a minimizer for the relative error function (\ref{eq:rel_error}) using \textit{fminsearch} from MATLAB R2019b and the training sets.\\
-
-To verify and compare this two vector of parameters, (i.e., $(\theta_0^V,\alpha^V)$ and $(\theta_0^Z,\alpha^Z)$), we simulate error paths in the $V-$space.
+In the $Z$-space, we obtain the optimal parameters $(\theta_0^Z,\alpha^Z)=(1.87,0.043)$ as minimizers for the relative error function (\ref{eq:rel_error}) using \textit{fminsearch} from MATLAB R2019b and the training sets.\\
+
+To verify and compare these two vector of parameters, (i.e., $(\theta_0^V,\alpha^V)$ and $(\theta_0^Z,\alpha^Z)$), we simulate error paths in the $V-$space.
 We simulate five error paths for each day in the test set and construct histograms with the transitions.
@@
 \includegraphics[width=0.45\textwidth]{plots/classic_noDelta/Lamperti_Optimal.eps}
-\caption{Probability histograms for the error transitions.
+\caption{Probability histograms for error transitions.
 Using provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE.
-On the left, simulations using $(\theta_0^V,\alpha^V)$.
-On the right, simulations using $(\theta_0^Z,\alpha^Z)$.}
+On the left, simulations use $(\theta_0^V,\alpha^V)$.
+On the right, simulations use $(\theta_0^Z,\alpha^Z)$.}
 \label{fig:hists}
@@
 
-We compare two candidate models to find the best-fit that maximizes the retained information, {\color{red} the Model 1, introduced in (\cite{elkate}, p.383), and our proposed model  (\ref{ourmodel}), from hereafter called Model 2.}
+We compare two candidate models to find the best-fit that maximizes the retained information, {\color{black} the Model 1, introduced in (\cite{elkate}, p.383), and our proposed model  (\ref{ourmodel}), from hereafter called Model 2.}
 \begin{itemize}
@@
 \end{itemize}
-To show the better performance of Model 2, we have computed the Akaike information criterion (AIC) and the Bayesian information criterion (BIC) for the two considered models, and any combination of the three different forecast providers with  {\color{red} three approximate likelihood methods, the one based on the Beta surrogate density in the$V$-space (Subsection \ref{moments_ODEs}), the one based on the Gaussian surrogate density in the $Z$-space (Subsection \ref{moments_ODEs_Z}), and the Shoji-Ozaki local linearization method (\cite{shoz}).}
+To show the better performance of Model 2, we have computed the Akaike information criterion (AIC) and the Bayesian information criterion (BIC) for the two considered models, and any combination of the three different forecast providers with  {\color{black} three approximate likelihood methods, the one based on the Beta surrogate density in the$V$-space (Subsection \ref{moments_ODEs}), the one based on the Gaussian surrogate density in the $Z$-space (Subsection \ref{moments_ODEs_Z}), and the Shoji-Ozaki local linearization method (\cite{shoz}).}
 Table (\ref{tab:model_comparison}) summarizes these results, also reporting the estimate of the variability diffusion coefficient $\alpha \theta_0$. 
@@
 Given a vector of parameters, we calculate an initial guess for $\delta$ solving problem (\ref{eq:likelihood_delta}).
-Even when it is a guess, it helps us to understand the meaning of this additional parameter qualitatively.\\
+Even when it is a guess, it helps us understand the meaning of this additional parameter qualitatively.\\
 \quad\\
@@
 \item The initial time $\delta$ increases as $\theta_0$ increases.
-As we increment $\theta_0$, also the mean reversion becomes larger and reduces the variance for the initial transition density.
-Then, it is needed more time for the initial transition density to cover the initial error observations.\end{itemize}
+As we increment $\theta_0$, the mean reversion becomes larger and reduces the variance for the initial transition density.
+Then, more time is needed for the initial transition density to cover the initial error observations.\end{itemize}
 
@@
 
-We used approximate likelihood-based methods for the models' calibration, developing original algorithms to derive optimal estimates of the unknown parameters.
+We used approximate likelihood-based methods for the models' calibration, and developed original algorithms to derive optimal estimates of the unknown parameters.
 The likelihood approach has allowed extending the SDE models in a very effective way, incorporating an early transition with an additional parameter that accounts for the forecast's uncertainty at the beginning of each future period.
-As a result, we obtained a robust procedure for synthetic data generation that, using the available forecast input, allows embracing the future wind power production paths through empirical pointwise bands with prescribed confidence.
-
-On the basis of historical data of wind power production and forecast from different sources, our method comes up with an objective tool for forecast assessment and comparison, by performing the model selection stage.
-The application of the procedure of modeling, inference through numerical optimization, and model selection through information criteria, to the wind power production real dataset in Uruguay during April-December 2019, with three different providers, shown the excellent performance of our proposed model, that preserves the asymmetry of wind power forecast errors and their correlation structure.
-
- We conclude that our SDE model, featuring the time-derivative tracking of the forecast, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward managing of renewable energies efficiently.
-This methodology paves the way for stochastic optimal control methods enabling principled decision making under uncertainty in the presence of complex energy matrix.
+As a result, we obtained a robust procedure for synthetic data generation that, using the available forecast input, embraces future wind power production paths through empirical pointwise bands with prescribed confidence.
+
+On the basis of historical data of wind power production and forecast from different sources, our method came up with an objective tool for forecast assessment and comparison, by performing the model selection stage.
+The application of the modeling procedure, inference through numerical optimization, and model selection through information criteria, to the wind power production dataset in Uruguay between April and December 2019, with three different providers, shows the excellent performance of our proposed model, which preserves the asymmetry of wind power forecast errors and their correlation structure.
+
+ We conclude that our SDE model, featuring the time-derivative tracking of the forecast, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward the management of renewable energies efficiently.
+This methodology paves the way for stochastic optimal control methods enabling principled decision making under uncertainty in the presence of complex energy matrices.
 

### 2020-06-23 LaTeX_Code/Paper/paper_1line.tex
Corrected english in the paper.

@@
 The data analysis highlighted that, during several 24-hour segments, the system operators decided to reduce or even cease the wind power production.
-Indeed, as recalled in (\cite{irena2}, p.3), ``Uruguay experiences high curtailment levels because generation exceeds demand.'' Despite the large country's interconnection capacity with Argentina and Brazil, there is no active cross-border market; the energy is traded via ad hoc short-term agreements.
-``Even with interconnection capacity exceeding peak demand, the power system experiences high VRE curtailment, mostly at night when wind generation exceeds demand.''
+Indeed, as recalled in (\cite{irena2}, p.8), ``Uruguay experiences high curtailment levels because generation exceeds demand.'' Despite the large country's interconnection capacity with Argentina and Brazil, there is no active cross-border market; the energy is traded via ad hoc short-term agreements.
+(\cite{irena2}, p.3) ``Even with interconnection capacity exceeding peak demand, the power system experiences high VRE curtailment, mostly at night when wind generation exceeds demand.''
 
@@
 
-In this work, $(p_t)_{t \in [0,T]}$ is to be considered a deterministic forecast for the normalized wind power generation, which is provided by an official source.
+In this work, $(p_t)_{t \in [0,T]}$ is to be considered a deterministic forecast for the normalized wind power generation, which is provided by Administrator of Electric Market.
 
@@
 
-\section{ Likelihood functions of the forecast errors data and optimization algorithm} \label{Section_5}
+\section{ Likelihood functions of the forecast error data and optimization algorithm} \label{Section_5}
 
@@
 
-\red{Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at a different time $t_j$ with $j = 1, \dots, M$, sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
+\red{Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at a different time $t_j$ with $j = 1, \dots, M$, is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
 Let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}$.}
@@
 
-The It\^{o} process $V$ defined by the SDE (\ref{VtSDE}) is Markovian, then the likelihood function of the sample $ V^{M,N + 1}$ can be written as the following product of transition densities:
+The It\^{o} process $V$ defined by the SDE (\ref{VtSDE}) is Markovian, and the likelihood function of the sample $ V^{M,N + 1}$ can be written as the following product of transition densities:
 
@@
 
-However, closed-form solutions to initial-boundary value problems for time-inhomogeneous diffusions can be obtained only in a few cases (see, for example, \autocite[Section 3.1]{eglix}).
+However, closed-form solutions to initial-boundary value problems for time-inhomogeneous diffusions can be obtained only in a few cases (see, for example, \cite[Section 3.1]{eglix}).
 In our case, solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
@@
 
-A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive real-valued shape parameters, $\xi_1, \xi_2$.
+A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape parameters, $\xi_1, \xi_2$.
 \red{Recall that the choice of the beta proxy distribution is a natural choice as it is the invariant distribution of the Jacobi type processes.}
@@
 To guarantee the good behave for our optimization algorithm, we aim to start the optimization as close as we can from the optimal parameters.
-We use \textbf{Least Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess $(\theta_0^*,\alpha^*)$.
+We use {least square minimization} and {quadratic variation} over the data to find an initial guess $(\theta_0^*,\alpha^*)$.
 
@@
 
-\item \textbf{Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
+\item {Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
 \red{For any $t\in [t_{j,i-1}, t_{j, i}[$, the random variable $(V_{j,i}|v_{j,i-1})$ has a conditional mean that can be approximated by the solution of the system}
@@
 
-\item \textbf{Quadratic variation:} We approximate the quadratic variation of the  It\^{o}'s  process $V$
+\item {Quadratic variation:} We approximate the quadratic variation of the  It\^{o}'s  process $V$
 \begin{equation*}
@@
 As a final verification, we study the behavior of $\delta$ as a function of the vector $\bm{\theta}$.
-Given a vector of parameters, we calculate an initial guess for $\delta$ solving problem (\ref{eq:likelihood_delta}).
+Given a parameter vector, we calculate an initial guess for $\delta$ solving problem (\ref{eq:likelihood_delta}).
 Even when it is a guess, it helps us understand the meaning of this additional parameter qualitatively.\\
@@
 We used approximate likelihood-based methods for the models' calibration, and developed original algorithms to derive optimal estimates of the unknown parameters.
-The likelihood approach has allowed extending the SDE models in a very effective way, incorporating an early transition with an additional parameter that accounts for the forecast's uncertainty at the beginning of each future period.
+The likelihood approach allowed for the extending of the SDE models in a very effective way, incorporating an early transition with an additional parameter that accounts for the forecast's uncertainty at the beginning of each future period.
 As a result, we obtained a robust procedure for synthetic data generation that, using the available forecast input, embraces future wind power production paths through empirical pointwise bands with prescribed confidence.
 
-On the basis of historical data of wind power production and forecast from different sources, our method came up with an objective tool for forecast assessment and comparison, by performing the model selection stage.
+On the basis of historical data of wind power production and forecast from different sources, our method came up with an objective tool for forecast assessment and comparison by performing the model selection stage.
 The application of the modeling procedure, inference through numerical optimization, and model selection through information criteria, to the wind power production dataset in Uruguay between April and December 2019, with three different providers, shows the excellent performance of our proposed model, which preserves the asymmetry of wind power forecast errors and their correlation structure.
 
- We conclude that our SDE model, featuring the time-derivative tracking of the forecast, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward the management of renewable energies efficiently.
+We conclude that our SDE model, featuring a time-derivative tracking of the forecast, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward the management of renewable energies efficiently.
 This methodology paves the way for stochastic optimal control methods enabling principled decision making under uncertainty in the presence of complex energy matrices.

### 2020-06-27 LaTeX_Code/Paper/paper_1line.tex
Added ORCID (missing Prof. Kebaier) and corrected Fig. 9
Added Prof. Kebaier and Prof. Scavino comments. Tomorrow I will submit the paper to arXiv after cheking the numerical values a last time

@@
 \usepackage{fancybox}
+\usepackage{tikz}
 \usepackage{hyperref}
@@
 %\DeclareLanguageMapping{english}{english-apa}
+\definecolor{lime}{HTML}{A6CE39}
+
+\DeclareRobustCommand{\orcidicon}{
+	\begin{tikzpicture}
+	\draw[lime, fill=lime] (0,0) 
+	circle [radius=0.16] 
+	node[white] {{\fontfamily{qag}\selectfont \tiny ID}};
+	\draw[white, fill=white] (-0.0625,0.095) 
+	circle [radius=0.007];
+	\end{tikzpicture}
+	\hspace{-2mm}
+}
+\foreach \x in {A, ..., Z}{\expandafter\xdef\csname orcid\x\endcsname{\noexpand\href{https://orcid.org/\csname orcidauthor\x\endcsname}
+			{\noexpand\orcidicon}}
+}
+
+\newcommand{\orcidauthorA}{0000-0003-3220-0923} % For author RC
+\newcommand{\orcidauthorB}{0000-0003-1967-4446} % For author RT
+\newcommand{\orcidauthorC}{0000-0003-3468-8811} % For author AK
+\newcommand{\orcidauthorD}{0000-0001-5114-853X} % For author MS
 
@@
 
-\title{ Stochastic Wind Power Forecasting }  % \\  \small{Report}}
+\title{ A Derivative Tracking Model for Wind Power Forecast Error }  % \\  \small{Report}}
 
 %\author[1]{Waled Alhaddad}
-\author[1]{Renzo Caballero}
-\author[2]{Ahmed Kebaier}
-\author[3]{Marco Scavino}
-\author[4]{ Ra\'ul Tempone}
+\author[1]{Renzo Caballero\orcidA{}}
+\author[2]{Ahmed Kebaier\orcidC{}}
+\author[3]{Marco Scavino\orcidD{}}
+\author[4]{ Ra\'ul Tempone\orcidB{}}
 %\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
@@
 
-Keywords: wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, numerical optimization, model selection
+Keywords: wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, numerical optimization, model selection, time-inhomogeneous Jacobi diffusion
 
@@
 Furthermore, all calibrations involve the training sets and all simulations, the test sets.
-Following the instruction for the initial guesses from Subsection $\ref{opt_sec}$, we obtain the initial guess $(\theta_0^*,\alpha^*,\delta^*)\approx(1.54,0.072,073)$.
+Following the instruction for the initial guesses from Subsection $\ref{opt_sec}$ and assuming that
+\begin{equation*}
+\theta_t=\max\left(\theta_0,\frac{\alpha\theta_0+|\dot{p}_t|}{\min(p_t,1-p_t)}\right),
+\end{equation*}
+we obtain the initial guess $(\theta_0^*,\alpha^*,\delta^*)\approx(1.54,0.072,073)$.
 

### 2020-07-06 LaTeX_Code/Annals of Applied Statistics Guidelines/Annals of Applied Statistics Guidelines.tex
We ordered the files. We need to addapt the paper to the jurnals template

--- 2019-04-23 LaTeX_code/abstract_Berlin_NT.tex
@@
 \usepackage{siunitx}
+\usepackage{commath}
 
@@
 
-\title{Uncertainty Quantification in Wind Power Forecasting  \\ Conference Abstract}
+%\setcounter{secnumdepth}{0} % This line removes the numbers in the titles.
 
-\author{Waleed Alhaddad \quad  Ra\'ul Fidel Tempone \\ CEMSE, KAUST}
-
-\date{}
 \begin{document}
+\title{Annals of Applied Statistics Guidelines}
+\author{Renzo Miguel Caballero Rosas\\
+\url{Renzo.CaballeroRosas@kaust.edu.sa}\\
+\url{CaballeroRenzo@hotmail.com}\\
+\url{CaballeroRen@gmail.com}} 
 \maketitle
 
-%\pagebreak
-%\tableofcontents
-%\pagebreak
-\section{Abstract 600 char}
-Reliable wind power generation forecasting is crucial to meet energy demand, to trade and invest.
-We propose a model to simulate and quantify uncertainties in such forecasts.
-This model is based on Stochastic Differential Equations whose time-dependent parameters are inferred using continuous optimization of an approximate Likelihood function.
-The result is a skew stochastic process that simulates uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects.
-We apply the model to historical Uruguayan data and forecasts.
+\tableofcontents
 
-\section{Motivation}
+\section{Manuscript Submission}
 
-The adoption of renewable energy is accelerating due to technological advancements.
-However, the power generated by renewables is difficult to predict and thus such predictions require advanced uncertainty quantification techniques to ensure the bare minimum of meeting electricity power demands.
-This is also of importance for energy trading and insurance, that it is to deliver power in an optimal cost-effective way to adhere to a variety of financial contracts.
-Uncertainty quantification is key in the design of financial contracts and taking investment decisions in the energy sector.
-Additionally, it assists in the placement and design of renewable power plants.
+The abstract and introduction need to say \textbf{What scientific/policy question(s)} the paper addresses, \textbf{Why the topic is of interest}, and \textbf{How the data analyses will address these questions}, in as non-technical a manner as possible.\\
+\quad\\
+References should be in the name/year format (e.g., Smith, Jones, and Roberts (1992)), using “et al.” for more than three authors; subsequent references can be abbreviated (e.g., Smith et al.
+(1992)).\\
+\quad\\
+We encourage use of the IMS LaTex template when preparing your manuscript. The default setting is for numbered citations and references. To get the name-year format, change the line
+\begin{itemize}
 
-\section{Introduction}
+\item RequirePackage[numbers]\{natbib\} to
+\item RequirePackage\{natbib\},
 
-    We propose a model to simulate and quantify uncertainties in wind power generation forecasts.
-This model is based on Stochastic Differential Equations (SDEs) whose time-dependent parameters are inferred using optimization techniques of an associated approximate Likelihood function.
-Through continuous optimization, we find the optimal parameters of an unbounded convex problem with convex constraints.
-
-    We are able to simulate and quantify uncertainties in a variety of wind power generation forecasts while taking into account the skewness of the errors.
-This method is non-intrusive and is independent of forecasting technology or future developments.
-Through optimization, we update and tune the parameters of our SDE as we receive new sets of observations and their associated forecasts.
-Additionally, we are able to compare in a quantitative manner the different forecast technologies and how they behave in different real-world scenarios.
-This model is to be extended to the uncertainty quantification of other power generation sources such as the uncertainties in the power generation of solar power plants.
-This introduces new challenges in terms of optimization and modeling.
-Finally, we apply our model to synthetic and real wind power generation data for benchmarking.
-We apply the model to Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the period of March 1 to May 31, 2016.
-
-\section{Model}
-Wind power generation forecasts have certain properties that need to be satisfied.
-One such particularity is that the forecasts are limited to the maximum power capabilities of the wind farm.
-Thus a proposed model for the uncertainties of the forecast must be controlled and restricted to a certain range.
-Due to this requirement, we propose an SDE whose solution is a controlled stochastic process that is contained inside a given range.
-Another challenge is when the forecast approaches the boundaries of this power production range.
-In this case, the errors of the forecast are compressed into a skew or asymmetric distribution.
-This renders the Gaussian approximations in such situations as unrealistic.
-Therefore, we propose a new approximate model based on a skew stochastic process.
-
-Another particularity of forecast uncertainties is that the validity of the forecast lessens as time evolves.
-Usually, such forecasts are prepared on a periodic basis and their uncertainty grows in time.
-This is taken into account through the mean reversion and variability of the stochastic process associated with the SDE.
-This behavior is learned through the time-dependent parameters of the SDE.
-
-\section{Conclusion}
-We were able to simulate and quantify the uncertainties for a diverse range of forecasts based on the Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the period of March 1 to May 31, 2016.
-We compare our results to similar works in the literature.
-And we highlight the importance of asymmetry and the avoidance of phase shift artifacts which we were able to overcome.
+\end{itemize}
+i.e., delete [numbers].\\
+\quad\\
+Authors may use British or American spelling, as they prefer.
 

### 2020-07-11 LaTeX_Code/Paper/aoas-template.tex
Added latest paper version

--- 2020-06-23 LaTeX_Code/Paper/paper_1line.tex
@@
-\documentclass[11pt]{article}
-
+% Template for the submission to:
+%   The Annals of Applied Statistics    [AOAS]
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% In this template, the places where you   %%
+%% need to fill in your information are     %%
+%% indicated by '???'.                      %%
+%%                                          %%
+%% Please do not use \input{...} to include %%
+%% other tex files. Submit your LaTeX       %%
+%% manuscript as one .tex document.         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[aoas,preprint]{imsart}
+
+%% Packages
+\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
+\RequirePackage[authoryear]{natbib}
 \usepackage{graphicx}
@@
 \usepackage{xcolor}
-\usepackage{authblk}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{todonotes}
-%\usepackage[normalem]{ulem}
 \usepackage{float}
@@
 \usepackage{fancybox}
+\usepackage{tikz}
 \usepackage{hyperref}
 \usepackage{url}
-\usepackage[margin=0.5in]{geometry}
-\usepackage[backend=biber, style=authoryear, citestyle=authoryear, autocite=inline, isbn=true]{biblatex} % package for bibliography 
-%\DeclareLanguageMapping{english}{english-apa}
-
-\theoremstyle{definition}
-\newtheorem{Def}{Definition}[section]
-\newtheorem{Eg}{Example}[section]
-\newtheorem{Rm}{Remark}[section]
-\newtheorem{Ex}{Exercise}[section]
-\newtheorem{Prop}[Def]{Proposition}
-\newtheorem{Lem}[Def]{Lemma}
-\newtheorem{Thm}[Def]{Theorem}
-\newtheorem{Cor}[Def]{Corollary}
-\newtheorem{Rem}[Def]{Remark}
-\newtheorem{Ass}[Def]{Assumption}
-\newtheorem{Met}[Def]{Method}
-\newtheorem{Res}[Def]{Result}
-\newcommand{\red}{\textcolor{black}}
+%\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
+%\RequirePackage{graphicx}% uncomment this for including figures
+
+\startlocaldefs
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Uncomment next line to change            %%
+%% the type of equation numbering           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\numberwithin{equation}{section}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% For Axiom, Claim, Corollary, Hypothezis, %%
+%% Lemma, Theorem, Proposition              %%
+%% use \theoremstyle{plain}                 %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{???}{???}
+%\newtheorem*{???}{???}
+%\newtheorem{???}{???}[???]
+%\newtheorem{???}[???]{???}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% For Assumption, Definition, Example,     %%
+%% Notation, Property, Remark, Fact         %%
+%% use \theoremstyle{remark}                %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\theoremstyle{remark}
+%\newtheorem{???}{???}
+%\newtheorem*{???}{???}
+%\newtheorem{???}{???}[???]
+%\newtheorem{???}[???]{???}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Please put your definitions here:        %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newcommand{\E}{\mathbb{E}}
@@
 
-\addbibresource{sdewind.bib}
-
-%\renewbibmacro*{title}{%
-%  \ifboolexpr{
-%    test {\iffieldundef{title}}
-%    and
-%    test {\iffieldundef{subtitle}}
-%  }
-%    {}
-%    {\printtext{%
-%     \printtext[titlecase]{\usefield{\uline}{title}}%
-%     \setunit{\subtitlepunct}%
-%     \printfield[titlecase]{subtitle}}%
-%     \newunit}%
-%  \printfield{titleaddon}}
-
-\setcounter{page}{1}
+\endlocaldefs
 
@@
 
-\title{ Stochastic Wind Power Forecasting }  % \\  \small{Report}}
-
-%\author[1]{Waled Alhaddad}
-\author[1]{Renzo Caballero}
-\author[2]{Ahmed Kebaier}
-\author[3]{Marco Scavino}
-\author[4]{ Ra\'ul Tempone}
-%\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
-\affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
-\affil[2]{\red{Universit\'e Sorbonne Paris Nord, LAGA, CNRS, UMR 7539, F-93430, Villetaneuse, France}}
-\affil[3]{Universidad de la Rep\'ublica, Instituto de Estad\'{\i}stica (IESTA), Montevideo, Uruguay}
-\affil[4]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}
-
-%\author{ Waled Alhaddad \textsuperscript{\textasteriskcentered} \qquad Ahmed Kebaier\textsuperscript{\ddag} \qquad Ra\'ul  Tempone\textsuperscript{\textasteriskcentered}\textsuperscript{\textdagger} \\
-%\textsuperscript{\textasteriskcentered}CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia \\ \textsuperscript{\textdagger}Alexander von Humboldt Professor, RWTH Aachen University, Germany
-% \\ \textsuperscript{\ddag}Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
+\begin{frontmatter}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the title of your article here     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{A Derivative Tracking Model for Wind Power Forecast Error}
+%\title{A sample article title with some additional note\thanksref{T1}}
+\runtitle{A Derivative Tracking Model for Wind Power Forecast Error}
+%\thankstext{T1}{A sample of additional note to the title.}
+
+\begin{aug}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%Only one address is permitted per author. %%
+%%Only division, organization and e-mail is %%
+%%included in the address.                  %%
+%%Additional information can be included in %%
+%%the Acknowledgments section if necessary. %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author[A]{\fnms{Renzo} \snm{Caballero}\ead[label=e1]{Renzo.CaballeroRosas@kaust.edu.sa}},
+\author[B]{\fnms{Ahmed} \snm{Kebaier}\ead[label=e2,mark]{kebaier@math.univ-paris13.fr}},
+\author[C]{\fnms{Marco} \snm{Scavino}\ead[label=e3,mark]{mscavino@iesta.edu.uy}}
+\and
+\author[D]{\fnms{Ra\'ul} \snm{Tempone}\ead[label=e4,mark]{tempone@uq.rwth-aachen.de}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Addresses                                %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\address[A]{CEMSE Division, King Abdullah University of Science and Technology, Saudi Arabia, \printead{e1}}
+\address[B]{Universit\'e Sorbonne Paris Nord, LAGA, CNRS, UMR 7539, F-93430, Villetaneuse, France, \printead{e2}}
+\address[C]{Instituto de Estad\'{\i}stica (IESTA), Universidad de la Rep\'ublica, Montevideo, Uruguay, \printead{e3}}
+\address[D]{Chair of Mathematics for Uncertainty Quantification, RWTH Aachen University, Germany, \printead{e4}}
+\end{aug}
 
 \begin{abstract}
-
 Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization for electricity price, and operation scheduling of conventional power plants.
@@
 We apply the model to historical Uruguayan wind power production data and forecasts between April and December 2019.
-
 \end{abstract}
 
-Keywords: wind power, probabilistic forecasting, stochastic differential equations, Lamperti transform, numerical optimization, model selection
-
-2020 AMS Subject Classification: 60H10, 62M20, 65K10.
-
-%%%%%%%%% BODY TEXT
+\begin{keyword}
+\kwd{Wind Power}
+\kwd{Probabilistic Forecasting}
+\kwd{Stochastic Differential Equations}
+\kwd{Lamperti Transform}
+\kwd{Numerical Optimization}
+\kwd{Model Selection}
+\kwd{Time-Inhomogeneous Jacobi Diffusion}
+\end{keyword}
+
+\end{frontmatter}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Please use \tableofcontents for articles %%
+%% with 50 pages and more                   %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\tableofcontents
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Main text entry area:
 
@@
 \includegraphics[width=0.45\textwidth]{plots/four_days/417.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{plots/four_days/437.eps}
-\includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
+%\quad\\
+%\includegraphics[width=0.45\textwidth]{plots/four_days/437.eps}
+%\includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
 \caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blue line).}
@@
 This diffusion term belongs to the Pearson diffusion family and, in particular, it defines a Jacobi type diffusion.
-It is useful to recall that (\cite[440]{foso}) a Pearson diffusion is a stationary solution to a stochastic differential equation of the form \begin{equation}
+It is useful to recall that \cite[440]{foso} a Pearson diffusion is a stationary solution to a stochastic differential equation of the form \begin{equation}
     \dif X_t = - \theta (X_t - \mu)\dif t + \sqrt{2 \theta \left(a X_t^2 + b X_t + c\right)} \dif W_t
@@
 
-An exhaustive classification of the (stationary) Pearson diffusions is presented in (\cite[440-443]{foso}) where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 a \theta x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the well-known Jacobi diffusions, so-called because the eigenfunctions of the infinitesimal generator of these processes are the Jacobi polynomials (see, for example, \cite[2860-2861]{leph}).
+An exhaustive classification of the (stationary) Pearson diffusions is presented in \cite[440-443]{foso} where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 a \theta x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the well-known Jacobi diffusions, so-called because the eigenfunctions of the infinitesimal generator of these processes are the Jacobi polynomials (see, for example, \cite[2860-2861]{leph}).
 
@@
 \begin{align}
-Z_t = h(V_t, t; \bm{\theta} )  & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \dif v \Bigg{\vert}_{v = V_t}   = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
+\begin{split}
+Z_t = h(V_t, t; \bm{\theta} ) & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \dif v \Bigg{\vert}_{v = V_t}  \\
+& = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
+\end{split}
 \end{align}
 that, after applying It\^{o}'s formula on $h(V_t, t; \bm{\theta} )$, leads to the following SDE with state independent unit diffusion term
+\begin{multline}
+\begin{split}
+\dif Z_t=& \Bigg[   \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  \\
+&+ \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \dif t + \dif W_t .
+\label{eq:stindepSDE}
+\end{split}
+\end{multline}
+After replacing $V_t = 1 - p_t - \sin^2 \left(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \right) $ in (\ref{eq:stindepSDE}), we obtain that the  process $Z_t$ satisfies the SDE
+{\small
 \begin{align}
-\dif Z_t = \Bigg[  & \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  + \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \dif t + \dif W_t \,.
-\label{eq:stindepSDE}
-\end{align}
-After replacing $V_t = 1 - p_t - \sin^2 \left(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \right) $ in (\ref{eq:stindepSDE}), we obtain that the  process $Z_t$ satisfies the SDE
-\begin{align}
-\dif Z_t & = \left[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)}   - \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \right]\dif t + \dif W_t \nonumber \\
-&  = \left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \dif t + \dif W_t.
+\begin{split}
+\dif Z_t  =& \left[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \right.
+\\
+& \left.- \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \right]\dif t + \dif W_t \\
+ = &\left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \dif t + \dif W_t.
 \label{eq:stindepSDE2}
-\end{align}
+\end{split}
+\end{align}}
 
@@
 
-\red{Remark: Moreover, this obtained Gaussian distribution supports the validity of the choice of our model diffusion coefficient given by (\ref{eq:poly_diff}). 
-}
+Remark: Moreover, this obtained Gaussian distribution supports the validity of the choice of our model diffusion coefficient given by (\ref{eq:poly_diff}).
+
 %{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models, that is if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.}
@@
 
-\red{Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at a different time $t_j$ with $j = 1, \dots, M$, is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
-Let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}$.}
+Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at a different time $t_j$ with $j = 1, \dots, M$, is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
+Let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}$.
 
@@
 Several numerical techniques have been devised to obtain estimates for the unknown parameters of continuous-time SDE models with discrete observations (see, for example, \cite{prewo} for likelihood-based inference techniques, \cite{Sor} for an estimating function approach).
-As explained in the next subsection, we have considered approximate likelihood methods, similar in spirit to \autocite[Section 11.4]{saso}.
+As explained in the next subsection, we have considered approximate likelihood methods, similar in spirit to \cite[Section 11.4]{saso}.
 
@@
 
-Gaussian approximations to the transition densities of nonlinear time-inhomogeneous SDEs are available through different algorithms \autocite[Chapter 9]{saso}.
+Gaussian approximations to the transition densities of nonlinear time-inhomogeneous SDEs are available through different algorithms \cite[Chapter 9]{saso}.
 However, as Figure \ref{fig:error_transitions} may suggest at first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
@@
 A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape parameters, $\xi_1, \xi_2$.
-\red{Recall that the choice of the beta proxy distribution is a natural choice as it is the invariant distribution of the Jacobi type processes.}
+{Recall that the choice of the beta proxy distribution is a natural choice as it is the invariant distribution of the Jacobi type processes.}
 
@@
 The approximate log-likelihood $\tilde{\ell}(\cdot ; v^{M, N+1})$ of the observed sample $v^{M, N+1}$ can be expressed as
-\begin{equation}
- \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1(t_{j,i}^-), \xi_2(t_{j,i}^-))} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1(t_{j,i}^-) -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2(t_{j,i}^-) -1} \right\},
+{\small
+\begin{multline}
+ \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) \\
+ = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1(t_{j,i}^-), \xi_2(t_{j,i}^-))} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1(t_{j,i}^-) -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2(t_{j,i}^-) -1} \right\},
 \label{eq:loglikelihoodV}
-\end{equation}
+\end{multline}
+}
 where the shape parameters $\xi_1(t_{j,i}^-)$ and $\xi_2(t_{j,i}^-)$, according to (\ref{param_transformed_beta}), depend on the limit quantities $\mu(t_{j,i}^-;\bm{\theta} )$ and $\sigma^2(t_{j,i}^-;\bm{\theta} )$ as $t\uparrow t_{j,i}$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
@@
 
-\red{In this subsection, we aim to infer the model's parameters using optimization techniques.
+{In this subsection, we aim to infer the model's parameters using optimization techniques.
 We start by finding an initial guess close enough to the optimal value, and from that point, start the optimization.}
@@
 \item {Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
-\red{For any $t\in [t_{j,i-1}, t_{j, i}[$, the random variable $(V_{j,i}|v_{j,i-1})$ has a conditional mean that can be approximated by the solution of the system}
+{For any $t\in [t_{j,i-1}, t_{j, i}[$, the random variable $(V_{j,i}|v_{j,i-1})$ has a conditional mean that can be approximated by the solution of the system}
 \begin{equation*}
@@
 \hat{c}&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-\E\left[V\right](t_{j,i}^-)\right)^2\right]\\
-&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}e^{-c\Delta}\right)^2\right]\\
+%&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}e^{-c\Delta}\right)^2\right]\\
 &\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right)^2\right].
@@
 \end{equation}
-As Equation (\ref{Eq-1}) is convex in $c$, it is enough to verify the first order optimality conditions. From
-\begin{equation*}
-\frac{\partial}{\partial c}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right)^2\right]=\sum_{j=1}^M\sum_{i=1}^{N}2v_{j,i-1}\Delta\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right),
-\end{equation*}
-it follows that
+As Equation (\ref{Eq-1}) is convex in $c$, it is enough to verify the first order optimality conditions. % From
+%\begin{equation*}
+%\frac{\partial}{\partial c}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right)^2\right]=\sum_{j=1}^M\sum_{i=1}^{N}2v_{j,i-1}\Delta\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right),
+%\end{equation*}
+It follows that
 \begin{equation}
@@
 \end{equation}
-\red{We approximate $\theta_0$ by Equation (\ref{Eq-4}) setting $\theta_0^*=\hat{c}$.}
+{We approximate $\theta_0$ by Equation (\ref{Eq-4}) setting $\theta_0^*=\hat{c}$.}
 
@@
 Such an allocation mechanism guarantees independence among the segments, matching the assumption we did in Section \ref{Section_5} to formulate the statistical models.
-\red{Additional cross-correlation tests were performed to ensure this assumption.}
+{Additional cross-correlation tests were performed to ensure this assumption.}
 
@@
 As an auxiliary verification, we plot the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) as a function of the parameters, and we use additional minimization functions from MATLAB R2019b.
-\red{Moreover, we realized an additional inference utilizing the test sets to guarantee the robustness of our numerical methods.}
+{Moreover, we realized an additional inference utilizing the test sets to guarantee the robustness of our numerical methods.}
 
@@
 \includegraphics[width=0.5\textwidth]{plots/LL/Log-Likelihood.eps}\includegraphics[width=0.5\textwidth]{plots/LL/Log-Likelihood_testing.eps}
-\caption{\red{Negative log-likelihood's level sets for the training sets (plot on the left), and for the test sets (plot on the right).
+\caption{{Negative log-likelihood's level sets for the training sets (plot on the left), and for the test sets (plot on the right).
 All optimal values are located over the curve $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.}}
@@
 \end{figure}
-\red{On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood for both training and test sets.} The numerical values of each relevant point can be seen in Table (\ref{tab:optimal_values}).
+{On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood for both training and test sets.} The numerical values of each relevant point can be seen in Table (\ref{tab:optimal_values}).
 We set the optimal parameters in the $V$-space $(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood for the training sets reaches its minimum value.
@@
 \end{table}
-\red{We observe that all the local (possibly global) minimizers are located over the curves $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.
+{We observe that all the local (possibly global) minimizers are located over the curves $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.
 This effect shows that the optimization is more sensitive to the diffusion than to the drift.}\\
@@
 \includegraphics[width=0.45\textwidth]{plots/paths/2.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{plots/paths/3.eps}
-\includegraphics[width=0.45\textwidth]{plots/paths/4.eps}
-\caption{Four arbitrary days with five simulated wind power production paths each.}
+%\quad\\
+%\includegraphics[width=0.45\textwidth]{plots/paths/3.eps}
+%\includegraphics[width=0.45\textwidth]{plots/paths/4.eps}
+\caption{Two arbitrary days with five simulated wind power production paths each.}
 \label{fig:simulation_paths}
@@
 \includegraphics[width=0.45\textwidth]{plots/bands/2.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{plots/bands/3.eps}
-\includegraphics[width=0.45\textwidth]{plots/bands/4.eps}
+%\quad\\
+%\includegraphics[width=0.45\textwidth]{plots/bands/3.eps}
+%\includegraphics[width=0.45\textwidth]{plots/bands/4.eps}
 \caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(2.22,0.044,0.054)$. Blue line: real production.}
@@
 The following proofs are based on standard arguments for stochastic processes that can be found e.g. in \cite{Alf} and \cite{KarShr} that we adapted to the setting of our model \eqref{eq:model}.
-\begin{Thm}\label{thm:exun}
+\begin{theorem}\label{thm:exun}
 Assume that    
@@
 Then, there is a unique strong solution to \eqref{eq:model} s.t.  for all $t\in[0,T]$, $X_t\in[0,1]$ a.s.
-\end{Thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{Thm}\label{thm:mod2}
+\begin{theorem}\label{thm:mod2}
 Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
@@
  Then, $\tau_0=\tau_1=+\infty$ a.s.
-\end{Thm}
+\end{theorem}
 
@@
 
-%---REFERENCES---
-
-\nocite{*}
-
-%\printbibliography
-\printbibliography[keyword={Wind-SDE},title={References}]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Single Appendix:                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{appendix}
+%\section*{???}%% if no title is needed, leave empty \section*{}.
+%\end{appendix}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Multiple Appendixes:                     %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{appendix}
+%\section{???}
+%
+%\section{???}
+%
+%\end{appendix}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Support information (funding), if any,   %%
+%% should be provided in the                %%
+%% Acknowledgements section.                %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Acknowledgements}
+% The authors would like to thank ...
+% 
+% The first author was supported by ...
+% 
+% The second author was supported in part by ...
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Supplementary Material, if any, should   %%
+%% be provided in {supplement} environment  %%
+%% with title inside \textbf{} and short    %%
+%% description below.                       %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{supplement}
+%\textbf{???}.
+%???.
+%\end{supplement}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                  The Bibliography                       %%
+%%                                                         %%
+%%  imsart-nameyear.bst  will be used to                   %%
+%%  create a .BBL file for submission.                     %%
+%%                                                         %%
+%%  Note that the displayed Bibliography will not          %%
+%%  necessarily be rendered by Latex exactly as specified  %%
+%%  in the online Instructions for Authors.                %%
+%%                                                         %%
+%%  MR numbers will be added by VTeX.                      %%
+%%                                                         %%
+%%  Use \cite{...} to cite references in text.             %%
+%%                                                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% if your bibliography is in bibtex format, uncomment commands:
+\bibliographystyle{imsart-nameyear} % Style BST file
+\bibliography{aoas-template.bib}    % Bibliography file (usually '*.bib')
+
+%% or include bibliography directly:
+% \begin{thebibliography}{}
+% \bibitem[\protect\citeauthoryear{???}{???}]{b1}
+% \end{thebibliography}
 

### 2020-07-13 LaTeX_Code/Paper/Supplementary Material/supp_mat_1.tex
Added all supplementary material plots (maybe I still need the xcross one)

--- 2020-07-11 LaTeX_Code/Paper/aoas-template.tex
@@
 \RequirePackage[authoryear]{natbib}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{siunitx}
-\usepackage{booktabs}
-\usepackage{xcolor}
-\usepackage{float}
-\usepackage{commath}
-\usepackage{fancybox}
-\usepackage{tikz}
-\usepackage{hyperref}
-\usepackage{url}
 %\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
@@
 %\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
 %\newtheorem{???}{???}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\E}{\mathbb{E}}
-\newcommand{\R}{\mathbb{R}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{A Derivative Tracking Model for Wind Power Forecast Error}
+\title{Supplementary Material (1/3): Data Statistics}
 %\title{A sample article title with some additional note\thanksref{T1}}
-\runtitle{A Derivative Tracking Model for Wind Power Forecast Error}
+\runtitle{Supplementary Material}
 %\thankstext{T1}{A sample of additional note to the title.}
@@
 \begin{abstract}
-Reliable wind power generation forecasting is crucial for applications such as the allocation of energy reserves, optimization for electricity price, and operation scheduling of conventional power plants.
-We propose a data-driven model based on parametric Stochastic Differential Equations (SDEs) to capture the real asymmetric dynamics of wind power forecast errors.
-Our SDE framework features time-derivative tracking of the forecast, time-varying mean-reversion parameter, and an improved state-dependent diffusion term.
-The methodology we developed allows the simulation of future wind power production paths and to obtain sharp empirical confidence bands.
-All the procedures are agnostic of the forecasting technology, and they enable comparisons between different forecast providers.
-We apply the model to historical Uruguayan wind power production data and forecasts between April and December 2019.
+ABSTRACT FOR THIS DATA.
 \end{abstract}
@@
 
-%---BEGIN SECTION 1---
-
-\section{Introduction}  \label{Section_1}
-
-Despite the Covid-19 pandemic causing ``the biggest shock to the global energy system in more than seven decades'' the recent report released on April 30, 2020, by the International Energy Agency (\url{https://www.iea.org/reports/global-energy-review-2020}) stresses that projections of energy demand will fall 6\% in 2020 -- seven times the decline after the 2008 global financial crisis -- It is emphasized that ``renewables are set to be the only energy source that will grow in 2020, with their share of global electricity generation projected to jump thanks to their priority access to grids and low operating cost'' (\cite{IEA}).
-
-Although the growth of renewables in electricity generation in 2020 is set to be lower than in previous years,  solar photo-voltaic (PV) and wind are on track to help lift renewable electricity generation by 5\% in 2020, aided by higher output from hydropower.
-\\
-
-Wind and solar energy are expanding renewable generation capacity, experiencing record growth in the last years.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\textwidth]{plots/wind_and_solar/plot_over_years.eps}
-\caption{Installed wind and solar power over the years \cite{sultana2017review}. We recall the importance of accurate forecasts to use green energies optimally.}
-\end{figure}
-
-Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
-\begin{itemize}
-\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
-\item Operation scheduling of controllable power plants.
-\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
-\item Maintenance planning such as that of power plants components and transmission lines.
-
-\end{itemize}
-
-Different methods have been applied to wind power forecasting.
-They can be generally categorized as follows: physical models, statistical methods, artificial intelligence methods, and hybrid approaches.
-The output of such methods is usually a deterministic forecast.
-Occasionally probabilistic forecasts are produced through uncertainty propagation in the data, parameters, or forecast ensembles.
-%{\color{red} Expand discussion about works on probabilistic forecasting.} 
-However, there is a lack of simulating and producing data-driven stochastic forecasts based on forecasting models.
-It is crucial to capture the forecast's actual performance as it has been known that different forecasting technologies exhibit different behavior for different wind farms and seasons (\cite{chang}).
-This is due to many factors that forecast are challenged to capture, such as the surrounding terrains of the wind farm and the condition of the blades such as icing, wear and tear, or dirt.
-It is known that complex terrains in both off shore and on shore locations decrease the accuracy of wind power forecasts significantly (\cite{schicker2017short}).
-It also has been shown that the performance of forecasts varies from month to month.
-Thus the performance of wind power forecasts is location and time dependent.
-
-Many approaches have been taken to evaluate the uncertainty of a given forecast.
-There are two types of errors: level errors and phase errors.
-The use of mean or median errors in this context may be misleading as wind power forecast errors are asymmetric.
-This is a natural consequence of wind power being non-negative and bounded by the maximum capacity of production.
-This is important as the associated cost to power forecast errors is also asymmetric due to different costs for up and down power regulations, which are determined by the electricity market (\cite{tsitsiklis2015pricing}).
-
-We propose to model wind power forecast errors using parametric stochastic differential equations (SDEs) whose solution defines a stochastic process.
-This resultant stochastic process describes the time evolution dynamics of wind power forecast errors while capturing properties such as a correlation structure and the inherent asymmetry.
-Additionally, the model we propose is agnostic of the forecasting technology and serves to complement forecasting procedures by providing a data-driven stochastic forecast.
-Hence, we can evaluate wind power forecasts according to their real-world performance, and we can compare different forecasting technologies.
-Most notably, we can simulate future wind power production given a deterministic wind power forecast.
-Future wind power production using Monte Carlo methods, as well as the analytic form of the proposed SDE, can be used in optimal control problems involving wind power production.
-
-%Previous attempt by (\cite{mozuma}) considered stochastic wind power forecast models based on stochastic differential equations.
- {\color{black} Some interesting works have been devoted to probabilistic forecasting related to renewable energies based on stochastic differential equations, among them (\cite{mozuma}) on wind power forecast, (\cite{immm}) and (\cite{bggk}) on forecasts of solar irradiance.}
-Here, we propose an improved model featuring time derivative tracking of the forecast, time-dependent mean reversion, modified diffusion, and non-Gaussian approximations.
-We apply the model to Uruguayan wind power forecasts together with historical wind power production data pertaining to the year 2019.
-\\
-
-The rest of the paper is organized as follows.
-In Section \ref{Section_2}, we introduce the main characteristics of a real data set encompassing the normalized wind power production in Uruguay between April and December 2019, with the most accurate predictions, as highlighted in our posterior analysis, performed by one out of the three sources of forecast providers.
-The significant steps for constructing phenomenological models of the normalized wind power production and the forecast error based on stochastic differential equations are described in Section \ref{Section_3}.
-The application of the Lamperti transform with unknown parameters in Section \ref{Section_4} leads to model the forecast error through a stochastic differential equation with a unit diffusion coefficient.
-In Section \ref{Section_5}, we write down the expressions for the likelihood functions of the forecast error in its original space and the Lamperti space.
-We also derive simple approximations of the likelihood functions.
-Section \ref{Section_5} concludes with the description of the optimization algorithm to compute approximate maximum likelihood estimates, including the case where we expand the model comprising an initial transition from the time the forecast is performed to the time of the first forecast.
-
-In Section \ref{Section_6}, we apply our proposed numerical estimation procedures to the Uruguay wind and forecast dataset, comparing two alternative models and assessing, for the best candidate model, the performance of three different forecast providers.
-Section \ref{Section_7} concludes the paper.
-The proofs of the existence, strong uniqueness, and boundedness of the SDE solutions used to model normalized wind power production and its forecast error are given in the Appendix.
-
-%---END SECTION 1---
-
-%---BEGIN SECTION 2---
-
-\section{Wind power production data in Uruguay and forecast providers } \label{Section_2}
-
-In recent years, Uruguay has triggered a remarkable change in its energy matrix.
-In (\cite{irena}, p.23), Uruguay was among those countries showcasing innovation, like Denmark, Ireland, Germany, Portugal, and Spain, with proven feasibility of managing annual variable renewable energy (VRE) higher than 25\% in power systems.
-
-According to (\cite{ren21}, pp.118--119), in 2018, Uruguay achieved 36\% of its electricity production from variable wind energy and solar PV, raising the share of generation from wind energy more than five-fold in just four years, from 6.2\% in 2014 to 33\% in 2018.
-
-At present, Uruguay is fostering even higher levels of wind penetration by boosting regional power trading with Argentina and Brazil. 
-In this rapidly evolving scenario, it is essential to analyze national data on wind power production with wind power short-term forecastings to orientate and assess the strategies and decisions of wind energy actors and businesses.
-
-Our study is based on publicly available data (source: Administrator of Electric Market) on the wind power production in Uruguay between April and December 2019, that we adequately normalized with respect to the present $\SI{1474}{\mega\watt}$ maximum installed wind power capacity.
-Each day, wind power production recordings are available every ten minutes.
-In this work, we also considered data from three different forecast providers, available each day starting at 1 pm.
-
-The next Figure \ref{fig:sample_data} shows the wind power real production during four segments 24 hours selected from the observation period together with their corresponding hourly short-term forecast, computed by a forecast provider.
-For the sake of visualization clarity, this section relies only on forecasts from one provider, called ``provider A'' from now on, ranked as the most accurate forecast provider, as it emerged from our posterior analysis.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/four_days/377.eps}
-\includegraphics[width=0.45\textwidth]{plots/four_days/417.eps}\\
-%\quad\\
-%\includegraphics[width=0.45\textwidth]{plots/four_days/437.eps}
-%\includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
-\caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blue line).}
-  \label{fig:sample_data}
-\end{figure}
-
-A view of the global discrepancy between the real production and the forecasted production, during the nine months observation period, is summarized through the forecast error histograms in Figure \ref{fig:data_curtailing}, where we also partitioned the forecast errors according to three contiguous categories of normalized generated power.
-Low normalized generated power corresponds to the range $[0,0.3]$, mid-power refers to the range $]0.3,0.6]$, and high-power to the range $]0.6,1]$.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
-\caption{Wind production forecast error histograms during the period April-December 2019: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
-  \label{fig:data_curtailing}
-\end{figure}
-
-We may observe that all the histograms in Figure \ref{fig:data_curtailing} exhibit skewed patterns, to a different extent, as well as extreme observations.
-The presence of these features can be partly explained.
-The data analysis highlighted that, during several 24-hour segments, the system operators decided to reduce or even cease the wind power production.
-Indeed, as recalled in (\cite{irena2}, p.8), ``Uruguay experiences high curtailment levels because generation exceeds demand.'' Despite the large country's interconnection capacity with Argentina and Brazil, there is no active cross-border market; the energy is traded via ad hoc short-term agreements.
-(\cite{irena2}, p.3) ``Even with interconnection capacity exceeding peak demand, the power system experiences high VRE curtailment, mostly at night when wind generation exceeds demand.''
-
-The curtailment of the wind power production imposed by the system operators has a strong influence on the forecast error.
-To build a model that, driven by the available forecast, allows the inclusion of true power production with a prescribed degree of uncertainty, it is necessary to remove the data segments affected by wind curtailment.
-
-Once we removed all the 24-hour segments showing wind curtailment, we set up a dataset containing 147 daily segments. 
-In the absence of the curtailment intervention, the forecast error histograms shown below in Figure \ref{fig:data_after_clean}, can appreciate skewness reduction, except for low power forecast error histogram.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{plots/HP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP.eps}
-\caption{Wind production forecast error histograms during the period April-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
-  \label{fig:data_after_clean}
-\end{figure}
-
-In this stage of data preprocessing, we obtain another useful result by applying the first-order difference operator to the forecast errors. 
-The forecast error transition histograms, displayed in the next Figure \ref{fig:error_transitions}, will later constitute a reference for the visual assessment of the global fit of the proposed models.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
-\caption{Forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
-\label{fig:error_transitions}
-\end{figure}
-
-The histograms in Figure \ref{fig:error_transitions} feature a non-Gaussianity trait and provide initial input for the model-building stage, which is described in the next section.
-Later, in Section \ref{Section_4}, guided from inferring the unknown model parameters, we will also propose transforming data as a strategy that naturally leads to an alternative model.
-
-%---END SECTION 2---
-
-%---BEGIN SECTION 3---
-
-\section{Phenomenological  Model} \label{Section_3}
-
-After analyzing the available dataset, we are now in the condition to build a type of phenomenological model for the normalized wind power generation forecasts that, in its most general form, is a stochastic process $X = \{X_t, \, t \in [0, T] \}$  defined by the following stochastic differential equation (SDE):
-
-\begin{equation}
-\begin{cases}
-    \dif X_t &=  a(X_t; p_t, \dot{p}_t,\bm{\theta})\dif t + b (X_t; p_t, \dot{p}_t, \bm{\theta} )\dif W_t, \quad t \in [0,T]  \\
-     X_0  &=  x_0 \in [0,1],
-\end{cases}
- \label{eq:main}
-\end{equation}
-
-where
-
-\begin{itemize}
-\item $a(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R} $  denotes a drift function,
-\item $b(\cdot; p_t, \dot{p}_t, \bm{\theta}): [0,1] \to \mathbb{R}^+ $  a  diffusion function,
-\item $\bm{\theta}$ is a vector of unknown parameters,
-\item $(p_t)_{t \in [0,T]}$ is a time-dependent deterministic function $[0,1]$-valued and $ (\dot{p}_t)_{t \in [0,T]}$ is its time derivative,
-\item $\{W_t, \, t \in [0,T] \}$ is a standard real-valued Wiener process.
-\end{itemize}
-
-In this work, $(p_t)_{t \in [0,T]}$ is to be considered a deterministic forecast for the normalized wind power generation, which is provided by Administrator of Electric Market.
-
-Our goal is to achieve a specification of the model (\ref{eq:main}) to follow the available normalized wind power forecasts closely while ensuring its unbiasedness with respect to the forecast.
-
-\subsection{Physical Constraints} \label{Physical_Constraints}
-
-Let $(p_t)_{t \in [0,T]}$ be the available prediction function for the normalized wind power, which is an input to this approach.
-To start with the model specification, first, we introduce a time-dependent drift function that features the mean-reverting property as well as derivative tracking:\begin{equation}
-a(X_t; p_t, \dot{p}_t, \bm{\theta}) = \dot{p}_t  - \theta_t (X_t - p_t),  \label{drift:meanrev-derivtrack}
-\end{equation} 
-where $ (\theta_t)_{t \in [0,T]} $ is a positive deterministic function, whose range depends on $\bm{\theta}$, as will be explained shortly.
-
-Now, looking at the normalized wind power generation forecast process $X_t$, modeled as solution to the It\^{o} stochastic differential equation (\ref{eq:main}) with the drift specified in (\ref{drift:meanrev-derivtrack}), it is straightforward to check that $\mathbb{E} \left[X_t\right] = p_t$, given $  \mathbb{E}\left[X_0\right] = p_0$.
-The application of  It\^{o}'s lemma % on $g(X_t, t) = X_t e^{\int_{0}^{t} \theta_s \dif s}$, leads to
-leads to
-%\begin{equation*}
-%\dif \left( X_t e^{\int_{0}^{t} \theta_s \dif s} \right) = e^{\int_{0}^{t} \theta_s \dif s} (\dot{p}_t + \theta_t p_t ) \dif t  + e^{\int_{0}^{t} \theta_s \dif s}b (X_t; p_t, \dot{p}_t, \bm{\theta} ) \dif W_t,
-%\end{equation*}
-%whose integral form is
-\begin{equation}
-e^{\int_{0}^{t} \theta_s \dif s}  X_t - X_0 = \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u \dif u} \dif s + \int_{0}^{t}  b (X_s; p_s, \dot{p}_s, \bm{\theta} )  e^{\int_{0}^{s} \theta_u \dif u}\dif  W_s.
-\label{eq:tomeanX}
-\end{equation} 
-Taking expectation on (\ref{eq:tomeanX}) we obtain
-%\begin{align}
-%\mathbb{E} \left[X_t\right] & = e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E} \left[X_0\right] +   \int_{0}^{t}  (\dot{p}_s + \theta_s p_s ) e^{\int_{0}^{s} \theta_u \dif u} \dif s   \right) \nonumber \\
-%& =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E} \left[X_0\right] +   \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u \dif u} \dif s +  \big[ p_s \, e^{\int_{0}^{s} \theta_u \dif u} \big]^{t}_0  - \int_{0}^{t}  \dot{p}_s e^{\int_{0}^{s} \theta_u \dif u} \dif s  \right) \nonumber \\
-%& =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E}\left[ X_0\right] + p_t \, e^{ \int_{0}^{t} \theta_s \dif s} - p_0 \right) = p_t. \label{eq:meanX}
-%\end{align}
-\begin{equation}
-\mathbb{E} \left[X_t\right] =  e^{ - \int_{0}^{t} \theta_s \dif s} \left(  \mathbb{E}\left[ X_0\right] + p_t \, e^{ \int_{0}^{t} \theta_s \dif s} - p_0 \right) = p_t.
-\label{eq:meanX}
-\end{equation}
-
- At this stage, the process defined by (\ref{eq:main}) with drift (\ref{drift:meanrev-derivtrack}) satisfies the two following properties: 
-\begin{itemize}
-\item it reverts to its mean $p_t$, with a time-varying speed $ \theta_t$ that is proportional to the deviation of the process $X_t$ from its mean,
-\item it tracks the time derivative $\dot{p}_t$.  
-\end{itemize}
-
-Remark: Observe that a mean-reverting model without derivative tracking shows a delayed path behavior.
-For instance, consider the diffusion model (\ref{eq:main}) with $a(X_t; p_t, \bm{\theta}) = - \theta_0 (X_t - p_t)\,, \theta_0 > 0$.
-In this case, given  $ \mathbb{E} \left[X_0\right] = p_0$, the diffusion has mean $\mathbb{E} \left[X_t\right] = p_t - e^{- \theta_0 t } \int_0^t \dot{p}_s  e^{\theta_0 s} \dif s$.
-The next Figure (\ref{fig:derivative_tracking}) illustrates how different behave the estimated confidence bands for two diffusion models with and without derivative tracking, fitting the same daily segment.
-
-\begin{figure}[H]
-\centering
-  \includegraphics[width=0.45\textwidth]{plots/31.eps}\includegraphics[width=0.45\textwidth]{plots/31_2.eps}
-  \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (plot on the left) and with derivative tracking (plot on the right).}
-  \label{fig:derivative_tracking}
-\end{figure}
-
-The forecast and production wind power data of Uruguay are normalized with respect to the installed power capacity during the period of observation.
-Thus, the mean-reverting level lies in $[0,1]$, and the process $X_t$  must take values in the same interval, a requirement that is not automatically fulfilled through the derivative tracking.
-To impose that the state space of $X_t$ is $[0,1]$, we may choose a convenient diffusion term, and require that the time-varying parameter $ \theta_t$ satisfies an ad-hoc condition.
-
-Let $\bm{\theta} = (\theta_0,\alpha)$, and choose a state-dependent diffusion term that avoids the process exiting from the range $[0,1]$ as follows:
-  \begin{equation}
-    b (X_t; \bm{\theta} )= \sqrt{2 \alpha \theta_0 X_t (1 - X_t)}
-  \end{equation}
-  where $\alpha >0$ is an unknown parameter that controls the path variability.
-This diffusion term belongs to the Pearson diffusion family and, in particular, it defines a Jacobi type diffusion.
-It is useful to recall that \cite[440]{foso} a Pearson diffusion is a stationary solution to a stochastic differential equation of the form \begin{equation}
-    \dif X_t = - \theta (X_t - \mu)\dif t + \sqrt{2 \theta \left(a X_t^2 + b X_t + c\right)} \dif W_t
-    \label{eq:poly_diff}
-  \end{equation}
-where $\theta>0$, and $a$, $b$, and $c$ are parameters such that the square root is well defined when $X_t$ is in the state space.
-These parameters, together with $\mu$, the mean of the invariant distribution, determine the state space of the diffusion as well as the shape of the invariant distribution.
-
-An exhaustive classification of the (stationary) Pearson diffusions is presented in \cite[440-443]{foso} where, in particular, it is discussed the case $a < 0$ and $b(x; \bm{\theta}) = \sqrt{2 a \theta x (x-1)}$, where the invariant distribution is a Beta distribution with parameters $\left( \frac{\mu}{-a}, \frac{1 - \mu}{-a} \right),$ that leads to the well-known Jacobi diffusions, so-called because the eigenfunctions of the infinitesimal generator of these processes are the Jacobi polynomials (see, for example, \cite[2860-2861]{leph}).
-
-It is worth mentioning that Jacobi diffusions have been successfully applied in several disciplines, among them finance (see \cite{vago} and references therein) and neuroscience (\cite{dotala}).
-
-However, a distinctive feature in our proposed model 
-\begin{equation}
-\begin{cases}
-    \dif X_t&= \left(\dot{p}_t  - \theta_t (X_t - p_t) \right) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]  \\
-   X_0 &=  x_0\in [0,1] ,
-\end{cases}
-\label{ourmodel}
-\end{equation}
-
-is that the drift term contains the time-varying parameter $\theta_t$, rendering the solution $X_t$ of (\ref{ourmodel}) to a non-stationary and time-inhomogeneous process.
-To ensure that the process $X_t$ is the unique strong solution of (\ref{ourmodel}) for all $t \in [0,T]$ with state space $[0,1]$ a.s., the mean-reversion time-varying parameter must satisfy the condition:
-
-\begin{equation}
-\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{B}. 
-\end{equation} \label{condB}
-The proof of this theoretical statement is presented in Section \ref{Appendix}. \\
-
-Remark: Condition (B) shows that the time-varying parameter $\theta_t$ becomes unbounded when $p_t = 0$ or $p_t = 1$. Therefore, we consider the following truncated prediction function
-\begin{equation}
-  p_t^{\epsilon} = \left\{
-  \begin{array}{@{}cl@{}}
-    \epsilon \!\!\!&\text{if \quad} p_t  < \epsilon  \\
-    p_t  \!\!\!&\text{if \quad}  \epsilon \leq p_t < 1 - \epsilon \\
-    1 - \epsilon  \!\!\!&\text{if \quad}  p_t \geq 1 - \epsilon
- \end{array}\right.  \label{corrforecast}
-\end{equation}
-that satisfies $p_t^{\epsilon} \in [\epsilon, 1 - \epsilon]$ for any $0 < \epsilon < \frac{1}{2}$ and $t \in [0,T]$, providing that $\theta_t$ is bounded for every $t \in [0,T]$. \\
-
-Remark: In this work, the analysis of the three different forecast datasets shows that there exists, for any forecast provider, a small $\epsilon >0$ to define the truncated prediction function fulfilling the above condition.
-\\
-
-From now on, we will keep the notation $p_t$ to denote the truncated prediction function (\ref{corrforecast}), unless specified otherwise.
-
-\subsection{A model specification for the forecast error}
- After applying to (\ref{ourmodel}) the simple change of variables $$V_t = X_t - p_t \,,$$ we may introduce the following model for the forecast error of the normalized wind power production:
-
-\begin{equation}
-\begin{cases}
-\dif V_t&=  - \theta_t V_t\dif t + \sqrt{2 \alpha \theta_0 (V_t +p_t ) (1-V_t-p_t)}\dif W_t, \quad t \in [0,T]  \\
-V_0&=  v_0\in [-1 + p_0,1 - p_0].
-\end{cases}  \label{VtSDE}
-\end{equation}
-
-%---END SECTION 3---
-
-%---BEGIN SECTION 4---
-
-\section{State independent diffusion term: Lamperti transform} \label{Section_4}
-
-Our model (\ref{VtSDE}) for the forecast error has a diffusion term that depends on the state variable $V_t$.
-Under the conditions that permit the use of It\^{o}'s formula on a well-chosen transformation of the process $V$, John Lamperti (\cite{lamp}) first showed that the transformed process is again a diffusion process that is solution to a SDE with unit coefficient for the diffusion term.
-The vast literature nowadays refers to this result as the so-called Lamperti transform (see, for example, \cite[40--41]{iacus1}; \cite{moma}; \cite[199--203]{pani}; \cite[98--100]{saso}), which is a basic tool to obtain a SDE for the transformed process whose diffusion term does not depend anymore on the state variable.
-A remarkable effect of removing the state dependency from the random noise term is to increase the numerical stability of the simulated paths of the transformed process.
-For this reason, some estimation methods of the unknown parameters of non-linear SDE models incorporated the Lamperti's change of variable as part of a more complex approximation procedure (for example, in the case of one-dimensional diffusions, the local linearization method in  \cite{shoz}, or the expansion method in \cite{ait}, later extended to time-inhomogeneous SDEs in \cite{eglix}).
-% later extended to multivariate diffusion in \cite{ait2}).
-
-We consider the following Lamperti transform with unknown parameters
-%{\color{red} (Remind that continuous-time models with different diffusion term are singular and the likelihood cannot be written down.
-Besides, it can be unstable to work with low frequency.
-If the frequency of the data is too low, the Lamperti transform helps to detect this problem (in principle, it is not clear how to determine the right frequency for estimation.
-)}
-%\begin{equation}
-%Z_t = h(V_t, t) = \frac{1}{\sqrt{2 \theta_0 \alpha}} \int_{\xi}^{x} \frac{1}{\sqrt{(u + p_t)(1 - u - p_t)}} \,du \Bigg{\vert}_{x = V_t} \,,
-%\end{equation}
-%where $\xi$ is an arbitrary point of the state space of the process $V$. The choice of $\xi = \frac{1}{2} - p_t$, where $p_t$ is a known input, 
-\begin{align}
-\begin{split}
-Z_t = h(V_t, t; \bm{\theta} ) & = \frac{1}{\sqrt{2 \alpha \theta_0 }} \int \frac{1}{\sqrt{(v + p_t)(1 - v - p_t)}} \dif v \Bigg{\vert}_{v = V_t}  \\
-& = - \sqrt{ \frac{2}{ \alpha \theta_0 }} \arcsin (\sqrt{ 1 - V_t - p_t}) \label{eq:LampZ}
-\end{split}
-\end{align}
-that, after applying It\^{o}'s formula on $h(V_t, t; \bm{\theta} )$, leads to the following SDE with state independent unit diffusion term
-\begin{multline}
-\begin{split}
-\dif Z_t=& \Bigg[   \frac{\dot{p}_t}{ \sqrt{2 \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}}  \\
-&+ \frac{- \theta_t V_t}{ \sqrt{2  \alpha \theta_0 (V_t + p_t)(1 - V_t - p_t)}} - \frac{1}{4} \frac{\sqrt{2 \alpha \theta_0} \left( 1 - 2 (V_t + p_t)\right)}{\sqrt{(V_t + p_t)(1 - V_t - p_t)}}  \Bigg] \dif t + \dif W_t .
-\label{eq:stindepSDE}
-\end{split}
-\end{multline}
-After replacing $V_t = 1 - p_t - \sin^2 \left(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \right) $ in (\ref{eq:stindepSDE}), we obtain that the  process $Z_t$ satisfies the SDE
-{\small
-\begin{align}
-\begin{split}
-\dif Z_t  =& \left[ \frac{ \dot{p}_t  - \theta_t  \left(1 - p_t - \sin^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\sqrt{2 \alpha \theta_0} \cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \right.
-\\
-& \left.- \frac{1}{4}  \frac{\sqrt{2 \alpha \theta_0} \left(1 - 2 \cos^2 \Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big) \right) }{\cos\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)  \sin\Big(- \sqrt{ \frac{ \alpha \theta_0}{2} } Z_t \Big)} \right]\dif t + \dif W_t \\
- = &\left[  \frac{  2  \dot{p}_t - \theta_t (1 - 2 p_t)  + (\alpha \theta_0 - \theta_t) \cos(- \sqrt{2 \alpha \theta_0 } Z_t) }{\sqrt{2 \alpha \theta_0} \sin{(- \sqrt{2 \alpha \theta_0} Z_t)}}  \right] \dif t + \dif W_t.
-\label{eq:stindepSDE2}
-\end{split}
-\end{align}}
-
-To summarize the effect of the Lamperti transform visually, we can see in the next Figure (\ref{fig:LP_transitions}) how the forecast error transition histograms (without curtailment) modify in comparison with Figure (\ref{fig:error_transitions}).
-
-In this case, the Lamperti transform has been applied using the optimal estimates of the parameters in the SDE model (\ref{VtSDE}), obtained applying our numerical procedure detailed later in Subsection \ref{opt_sec}.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
-\quad\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
-\caption{Lamperti transformed forecast error transition histograms between April and December 2019 without wind power production curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
-  \label{fig:LP_transitions}
-\end{figure}
-
-The shape of the forecast error transition histograms after applying the Lamperti transform has similarities with the Gaussian distribution, motivating toward the use of Gaussian-like approximations of the unknown density transition functions of the process $Z_t$.
-
-Remark: Moreover, this obtained Gaussian distribution supports the validity of the choice of our model diffusion coefficient given by (\ref{eq:poly_diff}).
-
-%{\color{red} Remind that Lamperti transform has the purpose tho check the consistency of the models, that is if the estimation of $\bm{\theta}$ with $V$ and $Z$ differs it is alarming.}
-
-%---END SECTION 4---
-
-%---BEGIN SECTION 5---
-
-\section{ Likelihood functions of the forecast error data and optimization algorithm} \label{Section_5}
-
-\subsection{Likelihood in the $V-$space}
-
-Suppose that any of $M$ non-overlapping paths of the continuous-time It\^{o} process $V = \{ V_t, t  \in [0,T] \}$, each one starting at a different time $t_j$ with $j = 1, \dots, M$, is sampled at $N + 1$ equispaced discrete points with given length interval $\Delta$.
-Let $ V^{M,N + 1}=\left\{ V_{t_1^{N + 1}} , V_{t_2^{N + 1}} ,\ldots , V_{t_M^{N + 1}} \right\}$ denote this random sample, with $V_{t_j^{N + 1}} =\left\{ V_{t_j + i \Delta}\,, i = 0, \ldots, N \right\}$.
-
-Let $\rho(v \vert v_{j, i-1} ; \bm{\theta})$ be the conditional probability density of $V_{t_j + i \Delta} \equiv V_{j, i}$ given $V_{j, i-1} = v_{j, i-1}$ evaluated at $v$, where $\bm{\theta} = (\theta_0, \alpha)$ are the unknown model parameters.
-
-The It\^{o} process $V$ defined by the SDE (\ref{VtSDE}) is Markovian, and the likelihood function of the sample $ V^{M,N + 1}$ can be written as the following product of transition densities:
-
-\begin{equation}
-\mathcal{L}\left(\bm{\theta}; V^{M,N +1}\right) = \prod\limits_{j=1}^M \left\{ \prod\limits_{i=1}^N \rho \left( {V_{j, i}| V_{j, i-1}} ; p_{[t_{j,  i-1}, t_{j , i} ]},  \bm{\theta} \right)    \right\},
-\label{likelihood}
-\end{equation}
-where $t_{j ,i} \equiv  t_j + i \Delta$ for any $j = 1, \ldots, M$ and $i = 0, \ldots, N$. \\
-
-Remark: In the last subsection of this section, we will extend the statistical model (\ref{likelihood}) by adding the transition that occurs during the time interval, say of length $\delta$, between the epoch when the forecast is done and the first epoch (1 pm) of each day-ahead forecast.
-To this purpose, the likelihood function (\ref{likelihood}) must include for any of the $M$ paths an additional factor, say $\rho_0 (V_{j, 0}|V_{j, -\delta};\bm{\theta},\delta)$, expressing the conditional density of the early transition.
-The parameter $\delta$ can be calibrated together or after the estimation of $\bm{\theta}$, suggesting an optimal time for the scheduling of the forecasts.\\
-
-The exact computation of the likelihood (\ref{likelihood}) relies on the availability of a closed-form expression for the transition densities of $V$ that, on the basis of the Markovian property of $V$, are characterized for $ t_{j, i-1} < t < t_{j,i}$,  as solutions of the Fokker-Planck-Kolmogorov equation (\cite[36]{iacus1}; \cite[61-68]{saso}):
-
-\begin{align}
-\frac{ \partial f }{\partial t } & \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} )= - \frac{\partial}{ \partial v} (- \theta_t v \, \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) ) \nonumber \\
-& + \frac{1}{2} \frac{\partial^2}{ \partial v^2} ( 2 \theta_0 \alpha (v+ p_t) (1 - v- p_t) \, \rho(v ,t \vert v_{j,i-1} ,  t_{j,i-1} ; \bm{\theta} ) ),  \label{eq:fpk}
-\end{align}
-subject to the initial conditions $\rho(v , t_{j, i-1} ; \bm{\theta} ) = \delta(v - V_{j, i-1}) \,,$ where $ \delta(v - V_{j, i-1})$ is the Dirac-delta generalized function centered at $ V_{j, i-1}\,.$
-
-However, closed-form solutions to initial-boundary value problems for time-inhomogeneous diffusions can be obtained only in a few cases (see, for example, \cite[Section 3.1]{eglix}).
-In our case, solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive.
-Several numerical techniques have been devised to obtain estimates for the unknown parameters of continuous-time SDE models with discrete observations (see, for example, \cite{prewo} for likelihood-based inference techniques, \cite{Sor} for an estimating function approach).
-As explained in the next subsection, we have considered approximate likelihood methods, similar in spirit to \cite[Section 11.4]{saso}.
-
-\subsection{Approximate likelihood  in the $V-$space} \label{moments_ODEs}
-
-Gaussian approximations to the transition densities of nonlinear time-inhomogeneous SDEs are available through different algorithms \cite[Chapter 9]{saso}.
-However, as Figure \ref{fig:error_transitions} may suggest at first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.
-
-Therefore, we propose to use a surrogate transition density for $V$ other than Gaussian. The moments of the SDE model (\ref{VtSDE}) are then matched to the surrogate density moments.
-
-From (\ref{eq:meanX}), we have $m_1(t) \equiv \mathbb{E} \left[V_t\right] = e^{- \int_{t_{j,i-1}}^t \theta_s \dif s} \,\mathbb{E} \left[V_{t_{j,i-1}}\right]$, for any $t\in [t_{j,i-1}, t_{j, i}[$, $j = 1, \ldots, M$ and $i = 1, \ldots, N$ .
-
-For $m \geq 2$, using It\^o's lemma % on $g(V_t) = V_t^m$, we obtain
-% arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
-%\begin{align}
-%\dif (V_t^m) & = \left( - m \theta_t V_t^m + \frac{1}{2} m (m -1) V_t^{m -2} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \right) \dif t  \nonumber \\
-%& + m V_t^{m-1} 2 \alpha \theta_0 (V_t + p_t) (1 - V_t - p_t) \dif W_t \,, \nonumber
-%\end{align}
-%from which we derive
-we derive
-\begin{equation}
-\frac{\dif  \mathbb{E}\left[ V^m_t\right]}{\dif t} = - m \theta_t \mathbb{E}\left[ V^m_t\right] + m (m-1) \alpha \theta_0  \mathbb{E}\left[ - V_t^m + (1 - 2 p_t) V_t^{m-1} + p_t (1 -p_t) V_t^{m-2} \right] .
-\end{equation}
-
-For any $t\in [t_{j,i-1}, t_{j, i}[$, the first two moments of $V$, $m_1(t)$ and $m_2(t) \equiv \mathbb{E}\left[V_t^2\right]$, can be computed by solving the following system
-\begin{equation}
-\begin{cases}
-\frac{\dif  m_1 (t)}{\dif t} &=  - m_1(t)\theta_t   \\
-\frac{\dif  m_2 (t)}{\dif t} &=  -2 (\theta_t +\alpha \theta_0) m_2(t) + 2 \alpha\theta_0 (1-2p_t)  m_1(t) + 2 \alpha\theta_0 p_t (1-p_t) 
-\end{cases}
-\label{Vtmom}
-\end{equation}
-with initial conditions $m_1(t_{j,i-1})= v_{j, i-1}$ and $m_2(t_{j,i-1})= v_{j, i-1}^2 \,.$
-
-\subsubsection{Moment Matching}
-
-A suitable candidate for a surrogate transition density of $V$ is a Beta distribution on a compact interval parameterized by two positive shape parameters, $\xi_1, \xi_2$.
-{Recall that the choice of the beta proxy distribution is a natural choice as it is the invariant distribution of the Jacobi type processes.}
-
-For any $t\in [t_{j,i-1}, t_{j, i}[$, we approximate the transition densities of the process $V$ using a Beta distribution.
-We equal the first two central moments of $V$ with the corresponding moments of the Beta surrogate distribution on $[-1 + \epsilon,1 - \epsilon]$ with shape parameters $\xi_1, \xi_2$.
-
-The shape parameters are given by
-\begin{equation}
-\xi_1(t) = - \frac{(\mu_t + 1 - \epsilon)(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2}, \quad \xi_2(t)=  \frac{(\mu_t-1 + \epsilon )(\mu_t^2 + \sigma_t^2 - (1- \epsilon)^2)}{2 (1 - \epsilon) \sigma_t^2} , \label{param_transformed_beta}
-\end{equation}
-where $\mu_t = m_1 (t)$ and $\sigma_t^2= m_2 (t)- m_1 (t)^2\,.$ \\
-
-The approximate log-likelihood $\tilde{\ell}(\cdot ; v^{M, N+1})$ of the observed sample $v^{M, N+1}$ can be expressed as
-{\small
-\begin{multline}
- \tilde{\ell} \left(\bm{\theta}; v^{M,N +1}\right) \\
- = \sum_{j=1}^M \sum_{i=1}^N \log  \left\{ \frac{1}{2(1 - \epsilon)} \frac{1}{B(\xi_1(t_{j,i}^-), \xi_2(t_{j,i}^-))} \left( \frac{v_{j,i} + 1 - \epsilon}{2(1 - \epsilon)} \right)^{\xi_1(t_{j,i}^-) -1}  \left( \frac{1 - \epsilon - v_{j,i}}{2(1 - \epsilon)} \right)^{\xi_2(t_{j,i}^-) -1} \right\},
-\label{eq:loglikelihoodV}
-\end{multline}
-}
-where the shape parameters $\xi_1(t_{j,i}^-)$ and $\xi_2(t_{j,i}^-)$, according to (\ref{param_transformed_beta}), depend on the limit quantities $\mu(t_{j,i}^-;\bm{\theta} )$ and $\sigma^2(t_{j,i}^-;\bm{\theta} )$ as $t\uparrow t_{j,i}$ that are computed solving numerically the initial-value problem (\ref{Vtmom}).
-$B(\xi_1,\xi_2)$ denotes the Beta distribution with parameters $\xi_1$ and $\xi_2$.
-
-\subsection{Approximate likelihood  in the $Z-$space} \label{moments_ODEs_Z}
-
-The transition density of the process $Z$, which has been defined through the Lamperti transformation (\ref{eq:LampZ}) of $V$, can be conveniently approximated by a Gaussian surrogate density.
-
-The drift coefficient $a(Z_t; p_t, \dot{p}_t, \bm{\theta}) $ of the process $Z$ that satisfies (\ref{eq:stindepSDE2}) is nonlinear.
-After linearizing the drift around the mean of $Z$, $\mu_Z(t) \equiv \mathbb{E}\left[Z_t\right]$,  we obtain the following system of ODEs to compute, for any $t\in [t_{j,i-1}, t_{j, i}[$, the approximations of the first two central moments of $Z$, say  $\tilde{\mu}_Z(t) \approx \mathbb{E}\left[Z_t\right]$ and $\tilde{v}_Z(t) \approx \text{Var} \left[Z_t\right]$:
-\begin{equation}
-\begin{cases}
-\frac{\dif  \tilde{\mu}_Z (t)}{\dif t}&=  a\big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big)   \\
-\frac{\dif  \tilde{v}_Z (t)}{\dif t}&= 2  a^{\prime} \big( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \big) \tilde{v}_Z (t) + 1
-\end{cases}
-\label{Ztmom}
-\end{equation}
-with initial conditions $\tilde{\mu}_Z(t_{j,i-1})= z_{j, i-1}$ and $\tilde{v}_Z(t_{j,i-1})= 0 \,,$ and where 
-\begin{equation*}
-a^{\prime} \left( \tilde{\mu}_Z (t) ; p_t, \dot{p}_t, \bm{\theta} \right) =    \frac{  (\alpha \theta_0 - \theta_t)  - \cos(\sqrt{2 \alpha \theta_0 } Z_t) [ \theta_t (1 - 2 p_t) - 2  \dot{p}_t ] }{\sin^2{(\sqrt{2 \alpha \theta_0} Z_t)}}.
-\end{equation*}
-The approximate Lamperti log-likelihood $\tilde{\ell}_Z\left(\cdot ; z^{M, N+1}\right)$ for the observed sample $z^{M, N+1}$ is given by
-\begin{equation}
-\tilde{\ell}_Z \left(\bm{\theta}; z^{M,N +1}\right) = \sum_{j=1}^M \sum_{i=1}^N \log \left\{ \frac{1}{\sqrt{2 \pi \tilde{v}_Z(t_{j,i}^-; \bm{\theta})}} \exp \Bigg( -\frac{(z_{j,i} - \tilde{\mu}_Z(t_{j,i}^-;\bm{\theta} ))^2}{2 \tilde{v}_Z(t_{j,i}^-; \bm{\theta})} \Bigg) \right\},
-\label{loglikelihoodZ}
-\end{equation}
-where the limits $\tilde{\mu}_Z(t_{j,i}^-;\bm{\theta} )$ and $\tilde{v}_Z(t_{j,i}^-;\bm{\theta} )$ are computed solving numerically the initial-value problem (\ref{Ztmom}).
-
-\subsection{Algorithm for the approximate maximum likelihood estimations} \label{opt_sec}
-
-{In this subsection, we aim to infer the model's parameters using optimization techniques.
-We start by finding an initial guess close enough to the optimal value, and from that point, start the optimization.}
-
-\subsubsection{Initial guess}
-
-To guarantee the good behave for our optimization algorithm, we aim to start the optimization as close as we can from the optimal parameters.
-We use {least square minimization} and {quadratic variation} over the data to find an initial guess $(\theta_0^*,\alpha^*)$.
-
-\begin{itemize}
-
-\item {Least square minimization:} We consider the observed data $v^{M,N+1}$ with length between observations $\Delta$, where $i\in\{0,\dots,N\}$ and $j\in\{1,\dots,M\}$.
-{For any $t\in [t_{j,i-1}, t_{j, i}[$, the random variable $(V_{j,i}|v_{j,i-1})$ has a conditional mean that can be approximated by the solution of the system}
-\begin{equation*}
-\begin{cases}
-\dif \E\left[V\right](t)&=-\theta_t\E\left[V\right](t)\dif t\\
-\E\left[V\right](t_{j,i-1})&=v_{j,i-1},
-\end{cases}
-\end{equation*}
-in the limit $t\uparrow t_{j,i}$, i.e., $\E\left[V\right](t_{j,i}^-)$.
-Then, the random variable $(V_{j,i}-\E\left[V\right](t_{j,i}^-))$ has zero mean.
-If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_{j,i-1},t_{j,i}[$, then $\E\left[V\right](t_{j,i}^-)=v_{j,i-1}e^{-c\Delta}$.
-If we have a total of $M\times N$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
-\begin{equation}
-\begin{split}
-\hat{c}&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-\E\left[V\right](t_{j,i}^-)\right)^2\right]\\
-%&=\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}e^{-c\Delta}\right)^2\right]\\
-&\approx\arg\min_{c\ \geq\ 0}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right)^2\right].
-\end{split}
-\label{Eq-1}
-\end{equation}
-As Equation (\ref{Eq-1}) is convex in $c$, it is enough to verify the first order optimality conditions. % From
-%\begin{equation*}
-%\frac{\partial}{\partial c}\left[\sum_{j=1}^M\sum_{i=1}^{N}\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right)^2\right]=\sum_{j=1}^M\sum_{i=1}^{N}2v_{j,i-1}\Delta\left(v_{j,i}-v_{j,i-1}(1-c\Delta)\right),
-%\end{equation*}
-It follows that
-\begin{equation}
-\hat{c}\approx\frac{\sum_{j=1}^M\sum_{i=1}^{N}v_{j,i-1}(v_{j,i-1}-v_{j,i})}{\Delta\cdot\sum_{j=1}^M\sum_{i=1}^{N}(v_{j,i-1})^2}.
-\label{Eq-4}
-\end{equation}
-{We approximate $\theta_0$ by Equation (\ref{Eq-4}) setting $\theta_0^*=\hat{c}$.}
-
-\item {Quadratic variation:} We approximate the quadratic variation of the  It\^{o}'s  process $V$
-\begin{equation*}
-\langle V\rangle _t=\int_0^t b(V_s; \bm{\theta}, p_s)^2 \dif s, \text{ where }  \:\: b(V_s; \bm{\theta}, p_s) = 
-\sqrt{2 \alpha \theta_0 (V_s +p_s ) (1-V_s - p_s)},
-\end{equation*}
-with the discrete sum $\sum_{0< t_{j, i-1} \leq t}\left(V_{t_{j, i}} - V_{t_{j, i-1}}\right)^2$.
-
-As initial guess for the diffusion variability coefficient $\theta_0 \alpha$, we choose
-\begin{equation}
-\theta_0^*\alpha^*=\frac{\sum_{j=1}^M\sum_{i=1}^N(v_{j,i} - v_{j,i-1})^2}{2\Delta\cdot\sum_{j=1}^M\sum_{i=1}^N(v_{j,i}+p_{j,i})(1-v_{j,i}-p_{j,i})},
-\label{Eq-2}
-\end{equation}
-where $\Delta$ is the length of the time interval between two consecutive measurements.
-\end{itemize}
-
-%In Subsection (\ref{Physical_Constraints}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$.
-Even when it would be reasonable to choose an arbitrary small $\epsilon>0$, we aim to approximate it using the LSM estimator.\\
-%
-%Fixed $\epsilon$, we call $\mathcal{V}=\{\Delta V_i^\epsilon\}_{i=1}^n$ to the set of $n$ error transitions where for each measurement $X_i$, we have that $V_i=X_i-p_i^\epsilon$.
-$\mathcal{P}=\{p_i^\epsilon\}_{i=1}^n$ is the corresponding set of forecasts.\\
-%If we also fix $\theta_0$ and $\alpha$, we can define the set of indexes $\mathbf{I}=\{i\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\theta_0\}$ and $\mathbf{J}=\left\{j\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\frac{\theta_0\alpha}{\epsilon}\right\}$.
-From the definition of $\theta_t$, we have that for $\epsilon<<1$, and $p_t=\epsilon$ or $p_t=1-\epsilon$, the approximation $\theta_t\approx\frac{\theta_0\alpha}{\epsilon}$ holds.
-Then, for $\epsilon$ small enough, $\mathbf{J}$ can be approximated by $$\mathbf{J}\approx\tilde{\mathbf{J}}=\{j\in\{1,\dots,n\}:p_j^\epsilon\in\{\epsilon,1-\epsilon\}\}.$$
-%Now, coming back to the definition of $\theta_t$, we have that it is more likely that $\theta_t=\theta_0$ if $p_t^\epsilon\approx\frac{1}{2}$.
-Then, we can approximate $\mathbf{I}$ by $$\mathbf{I}\approx\tilde{\mathbf{I}}=\left\{i\in\{1,\dots,n\}:p_i\in(\gamma,1-\gamma)\right\},\ \gamma\approx\frac{1}{2},\ \gamma<\frac{1}{2}.$$
-%We do not see signification differences in the LSM estimator for all $\gamma\in(0.1,0.3)$.
-If $\gamma>0.3$, the reduction in the number of samples makes variations in the LSM estimator.
-As we have an approximated value for $\theta_0\alpha$, if we can estimate $\frac{\theta_0\alpha}{\epsilon}$, then we can estimate $\epsilon$.
-We showed that for $\epsilon<<1$, the LSM estimation using indexes from $\tilde{\mathbf{J}}$ is an estimator for $\frac{\theta_0\alpha}{\epsilon}$.
-
-\subsubsection{Negative log-likelihood minimization in the $V-$space} \label{Sec:MinLH}
-
-To find the optimal parameters, we minimize the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) using the derivative-free function \textit{fminsearch} from MATLAB R2019b over the parameters $(\theta_0,\alpha)$.
-At each step of the iteration, we:
-\begin{itemize}
-
-\item Use the training dataset to find the SDE's first and second moments as explained in Subsection \ref{moments_ODEs}.
-\item Match the proxy distribution moments with the SDE's moments.
-\item Evaluate the negative log-likelihood using the training dataset.
-
-\end{itemize}
-
-\subsubsection{Negative log-likelihood minimization in the $Z-$space} \label{Sec:MinLHL}
-
-Let $v^{M,N+1}$ be the observed data, and $h( v_{j,i},t_{j,i};\bm{\theta})$ the Lamperti transform of the observation $v_{j,i}$.
-As we can see in Section \ref{Section_4}, the transformed observations $z^{M,N+1}$ depend on the vector $\bm{\theta}$.\\
-The problem of maximizing the approximated Lamperti log-likelihood (\ref{loglikelihoodZ}), i.e.,  $$\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta}; z^{M,N+1}\right),$$
-is not totally defined as the data $z^{M,N+1}$ depend on $\bm{\theta}$. However, we propose to find a fixed point $\bm{\theta}^\star $ such that
-\begin{equation}
-\bm{\theta}^\star=\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^\star )\}_{j=1,i=0}^{M,N}\right).
-\label{FP}
-\end{equation}
-At a fixed point, the likelihood has a maximum for the data set corresponding to that point. We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^\star $ solves (\ref{FP}), then
-\begin{equation*}
-\bm{\theta}^\star -\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^\star )\}_{j=1,i=0}^{M,N}\right)=0.
-\end{equation*}
-Given $\bm{\theta}^\star =(\theta_0^\star ,\alpha^\star )$, we call $\bm{\theta}^{\star \star }=(\theta_0^{\star \star },\alpha^{\star \star })$ to the solution of
-\begin{equation*}
-\arg\max_{\bm{\theta}}\tilde{\ell}_Z\left(\bm{\theta};\{h( v_{j,i},t_{j,i};\bm{\theta}^\star )\}_{j=1,i=0}^{M,N}\right).
-\end{equation*}
-For each $\bm{\theta}^\star $, we define the relative error function $\Psi:\R^+\times\R^+\to\R^+$ as
-\begin{equation}
-\Psi(\bm{\theta}^\star )=\frac{|\theta_0^\star -\theta_0^{\star \star }|}{|\theta_0^\star |}+\frac{|\alpha^\star -\alpha^{\star \star }|}{|\alpha^\star |},
-\label{eq:rel_error}
-\end{equation}
-and remark that $\bm{\theta}^\star $ is a fixed point if and only if $\Psi(\bm{\theta}^\star )=0$.
-To find minimizers for $\Psi$, we proceed in the same way as described in Subsection \ref{Sec:MinLH}, but using Gaussian surrogate densities.
-
-\subsection{Model specification with the additional parameter $\delta$}
-
-We observe that for most days, the forecast error at time $t_{j,0}=0$ is not zero.
-According to the forecasts procedure, we may assume that there is a time in the past $t_{j,-\delta}<t_{j,0}$, such that the forecast error $V_{j,-\delta}=0$.\\
-
-For any $j=1, \ldots, M$, we extrapolate backward linearly the truncated prediction function to get its value at time $t_{j,-\delta}$, $p_{j,-\delta}$, and set $v_{t_{j,-\delta}}=0$.
-We assume that the initial transition $(V_{j, 0}|v_{j,-\delta};\bm{\theta},\delta)$
-has a Beta distribution and apply to it the same moment matching method used above. Given a vector of parameters $\bm{\theta}$, we estimate $\delta$ solving the following problem
-\begin{equation}
-\arg\max_{\delta}\tilde{\mathcal{L}}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right) = \arg\max_{\delta}\prod\limits_{j=1}^M \rho_0 \left(v_{j, 0}|v_{j,-\delta};\bm{\theta},\delta\right),
-\label{eq:likelihood_delta}
-\end{equation}
-where $\tilde{\mathcal{L}}_\delta$ is the approximated $\delta-$likelihood.
-To solve this problem, we repeat the steps described in Subsection \ref{Sec:MinLH}, with the additional initial step of creating the linear extrapolation for $p_{j,-\delta}$ at each $j\in\{1,2,\dots,M\}$.\\
-\quad\\
-As remarked, we extend the statistical model (\ref{likelihood}) to include the extra parameter $\delta$.
-The approximated complete likelihood $\tilde{\mathcal{L}}_c$, which estimates the vector $(\theta_0,\alpha,\delta)$, is given by
-\begin{equation}
-\tilde{\mathcal{L}}_c\left(\bm{\theta},\delta; v^{M,N +1}\right)=\tilde{\mathcal{L}}\left(\bm{\theta}; v^{M,N +1}\right)\tilde{\mathcal{L}}_{\delta}\left(\bm{\theta},\delta; v^{M,1}\right),
-\label{eq:complete_LH}
-\end{equation}
-where $\tilde{\mathcal{L}}\left(\bm{\theta}; v^{M,N +1}\right)$ is the non-log version of (\ref{likelihood}).
-As we can provide initial guesses for $\bm{\theta}$ and $\delta$, we have a starting point for the numerical optimization of the approximated complete likelihood (\ref{eq:complete_LH}).
-
-%---END SECTION 5---
-
-%---BEGIN SECTION 6---
-
-\section{Application to the April-December 2019 Uruguay wind and forecast dataset} \label{Section_6}
-
-Our statistical analysis starts with partitioning the 147 segments of normalized wind power production, each 24-hours long.
-We select 73 non-contiguous segments for the models' calibration procedure, assigning them to the training set.
-The other 74 non-contiguous segments compose the test set.
-Such an allocation mechanism guarantees independence among the segments, matching the assumption we did in Section \ref{Section_5} to formulate the statistical models.
-{Additional cross-correlation tests were performed to ensure this assumption.}
-
-All the following results involving a single provider refer to provider A.
-Furthermore, all calibrations involve the training sets and all simulations, the test sets.
-Following the instruction for the initial guesses from Subsection $\ref{opt_sec}$ and assuming that
-\begin{equation*}
-\theta_t=\max\left(\theta_0,\frac{\alpha\theta_0+|\dot{p}_t|}{\min(p_t,1-p_t)}\right),
-\end{equation*}
-we obtain the initial guess $(\theta_0^*,\alpha^*,\delta^*)\approx(1.54,0.072,073)$.
-
-\subsection{Calibration of the approximate negative log-likelihood in $V$-space and $Z$-space}
-
-As an auxiliary verification, we plot the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) as a function of the parameters, and we use additional minimization functions from MATLAB R2019b.
-{Moreover, we realized an additional inference utilizing the test sets to guarantee the robustness of our numerical methods.}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{plots/LL/Log-Likelihood.eps}\includegraphics[width=0.5\textwidth]{plots/LL/Log-Likelihood_testing.eps}
-\caption{{Negative log-likelihood's level sets for the training sets (plot on the left), and for the test sets (plot on the right).
-All optimal values are located over the curve $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.}}
-\label{fig:neg-LL}
-\end{figure}
-{On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood for both training and test sets.} The numerical values of each relevant point can be seen in Table (\ref{tab:optimal_values}).
-We set the optimal parameters in the $V$-space $(\theta_0^V,\alpha^V)=(1.93,0.050)$, as it is where the negative log-likelihood for the training sets reaches its minimum value.
-\begin{table}[H]
-\centering
-\begin{tabular}{lcccccc}
-\toprule
- & \multicolumn{3}{c}{Training sets} & \multicolumn{3}{c}{Test sets} \\
- \midrule
- & $\theta_0$ & $\alpha$ & $\theta_0\alpha$ & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
- \midrule
- Initial guess & 1.54 & 0.072 & 0.111 & 1.96 & 0.053 & 0.104 \\
- fminsearch & 1.14 & 0.076 & 0.097 & 1.64 & 0.054 & 0.089 \\
- fmincon & 1.58 & 0.062 & 0.097 & 1.63 & 0.055 & 0.089 \\
- fminunc & 1.54 & 0.063 & 0.097 & 1.96 & 0.045 & 0.089 \\
- Evaluations & 1.93 & 0.050 & 0.097 & 1.59 & 0.056 & 0.089 \\
- \bottomrule
-\end{tabular}
-\caption{Value points from Figure \ref{fig:neg-LL}.}
-\label{tab:optimal_values}
-\end{table}
-{We observe that all the local (possibly global) minimizers are located over the curves $\theta_0\alpha=0.097$ and $\theta_0\alpha=0.089$ for the training and test sets, respectively.
-This effect shows that the optimization is more sensitive to the diffusion than to the drift.}\\
-
-%\subsection{Calibration of the approximate negative log-likelihood in the $Z-$space}
-
-%{\color{red} This part still may change.} As we are working in a low dimensional space, we can evaluate the relative error function (\ref{eq:rel_error}) in all the space of interest.
-%
-%\begin{figure}[H]
-%\centering
-%\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
-%\caption{Relative error function's level sets.}
-%\label{fig:neg-LLL}
-%\end{figure}
-%In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets for the relative error function (\ref{eq:rel_error}).
-The center deep green band is the set $\mathbb{A}$ such that $\Psi(\bm{\theta})<0.1$ if $\bm{\theta}\in\mathbb{A}$, it is the set of fixes-points candidates.
-The set of fixed-points candidates which also satisfies the condition of lying over the line $\theta_0\alpha=0.097$ is non-empty, i.e., $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.097\}\neq\emptyset.$$
-
-In the $Z$-space, we obtain the optimal parameters $(\theta_0^Z,\alpha^Z)=(1.87,0.043)$ as minimizers for the relative error function (\ref{eq:rel_error}) using \textit{fminsearch} from MATLAB R2019b and the training sets.\\
-
-To verify and compare these two vector of parameters, (i.e., $(\theta_0^V,\alpha^V)$ and $(\theta_0^Z,\alpha^Z)$), we simulate error paths in the $V-$space.
-We simulate five error paths for each day in the test set and construct histograms with the transitions.
-The histograms can be seen in Figure (\ref{fig:hists}).
-We observe a slightly better approximation using $(\theta^Z_0,\alpha^Z)$.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/classic_noDelta/Optimal.eps}
-\includegraphics[width=0.45\textwidth]{plots/classic_noDelta/Lamperti_Optimal.eps}
-\caption{Probability histograms for error transitions.
-Using provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE.
-On the left, simulations use $(\theta_0^V,\alpha^V)$.
-On the right, simulations use $(\theta_0^Z,\alpha^Z)$.}
-\label{fig:hists}
-\end{figure}
-
-\subsection{Model comparison and assessment of the forecast providers} \label{Model_Comp}
-
-We compare two candidate models to find the best-fit that maximizes the retained information, {\color{black} the Model 1, introduced in (\cite{elkate}, p.383), and our proposed model  (\ref{ourmodel}), from hereafter called Model 2.}
-\begin{itemize}
-  \item Model 1: This model does not feature derivative tracking:
-\begin{equation}
-\begin{cases}
-\dif X_t&=-\theta_0 (X_t - p_t) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]  \\
-X_0&=x_0\in [0,1],
-\end{cases}.  \label{Model1}
-\end{equation}
- with $\theta_0 > 0, \, \alpha > 0$.
-
-%  \item Model 1: This model features derivative tracking, i.e.
-it is equivalent to (\ref{model:derivative_tracking_X}) with a diffusion term that is forecast dependent by including the term $p_t(1-p_t)$.
-%  \begin{equation}
-%  \begin{split}
-%  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha p_t(1-p_t)(V_t +p_t ) (1-V_t-p_t)} \  dW_t  \\ %\quad t > 0
-%  V_0 & = v_0
-%  \end{split}\label{M2}
-%  \end{equation}
-%  with $\theta_t$ given by (\ref{theta_t}).
-This model has been used by [ insert ref ] and [ insert ref ].
-Initial interest in this model stems from interest in long-term stationary solution, which may exists  if the forecast is constant.
-However, this is almost never occurs and thus including the term $p_t(1-p_t)$ is irrelevant.
-Additionally, the term $p_t(1-p_t)$ leads the model to become deterministic when the forecast is at the boundaries (i.e.$p=1$ or $p=0$)  which is not realistic.
-We have run computations on this model and the results were not satisfactory.
-Therefore, we exclude this model from further discussions.
-%
-
-  \item Model 2: This model features derivative tracking and time-varying mean-reversion parameter:  
-%i.e. it is equivalent to (\ref{model:derivative_tracking_X}).
-%  \begin{align}
-%  dV_t &=  - \theta_t V_t \  dt + \sqrt{2 \theta_t \alpha (V_t +p_t ) (1-V_t-p_t)} \  dW_t   \nonumber \\ %\quad t > 0
-%  V_0 & = v_0 \,, \label{M2}
-%  \end{align}
-%  with $\theta_t$ given by (\ref{theta_t}).
-\begin{equation}
-\begin{cases}
-\dif X_t&= \big(\dot{p}_t  - \theta_t (X_t - p_t) \big) \dif t +\sqrt{2 \alpha \theta_0 X_t (1 - X_t)} \dif W_t, \quad t \in [0,T]\\
-X_0&=x_0\in [0,1],
-\end{cases}.  \label{Model2}
-\end{equation}
- with $\theta_0 > 0$, $\alpha > 0$ and $\theta_t$ satisfying condition \eqref{Assumption:3} .
-\end{itemize}
-To show the better performance of Model 2, we have computed the Akaike information criterion (AIC) and the Bayesian information criterion (BIC) for the two considered models, and any combination of the three different forecast providers with  {\color{black} three approximate likelihood methods, the one based on the Beta surrogate density in the$V$-space (Subsection \ref{moments_ODEs}), the one based on the Gaussian surrogate density in the $Z$-space (Subsection \ref{moments_ODEs_Z}), and the Shoji-Ozaki local linearization method (\cite{shoz}).}
-Table (\ref{tab:model_comparison}) summarizes these results, also reporting the estimate of the variability diffusion coefficient $\alpha \theta_0$. 
-It is worth observing that the best fitting is achieved with Model 2 and adopting Beta distributions as proxies of the transition densities.
-
-\begin{table}[H]
-\centering
-\begin{tabular}{cccccc}
-\toprule
-Model & Forecast Provider & Method & Product $\theta_0\alpha$   & AIC & BIC \\ \midrule
-Model 1 & Provider A & Gaussian Proxy & 0.105 & -58226 & -58211 \\
- &  & Shoji-Ozaki & 0.104 & -58226 & -58211 \\
- &  & Beta Proxy & 0.104 & -58286 & -58271 \\
- & Provider B & Gaussian Proxy & 0.105 & -58226   & -58211 \\
- &  & Shoji-Ozaki & 0.104 & -58226 & -58211 \\
- &  & Beta Proxy & 0.104 & -58288 & -58273 \\
- & Provider C & Gaussian Proxy & 0.105 & -58226 & -58211 \\
- &  & Shoji-Ozaki & 0.104 & -58226 & -58211 \\
- &  & Beta Proxy & 0.104 & -58286 & -58271 \\
-Model 2 & Provider A & Beta Proxy & 0.097 & -73700   & -73685 \\ 
- & Provider B & Beta Proxy & 0.098 &  -73502 & -73487 \\ 
- & Provider C & Beta Proxy & 0.108 & -72518 & -72503 \\ 
-\bottomrule
-\end{tabular}
-\caption{Model comparison based on Akaike and Bayesian information criteria.}
-\label{tab:model_comparison}
-\end{table}
-
-%\subsection{Forecast providers comparison} \label{Forecast_Comp}
-The optimal estimates of the parameters of Model 2, for the three forecast providers, when using Beta surrogates for the transition density are presented next:
-\begin{table}[H]
-\centering
-\begin{tabular}{ccc}
-\toprule
-Forecast Provider & Parameters $(\theta_0, \alpha)$ & Product $\theta_0\alpha$ \\ \midrule
-Provider A  & $(1.93,0.050)$  &  0.097 \\
-Provider B  & $(1.42,0.069) $  &  0.098 \\ 
-Provider C  & $(1.38,0.078) $  &  0.108 \\ 
-\bottomrule
-\end{tabular}
-\caption{Optimal parameters for the three different forecast providers using Model 2 with Beta proxies.}
-\label{tab:forcast_comparison}
-\end{table}
-
-%{\color{red} Discuss to which extent it is needed more accuracy in the estimation of $\bm{\theta}$.
-How much data do we need to achieve enough accuracy for the estimates of the two parameters?
-Generally, such accuracy is application dependent.}
-
-\subsection{Calibration of Model 2 with additional parameter $\delta$}
-
-After calibrating Model 2 on the training set using the complete likelihood (\ref{eq:complete_LH}), we can generate simulations of the wind power production for the time horizon of interest.
-Figure (\ref{fig:simulation_paths}) shows five simulated paths of wind power production for each day of interest.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/paths/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/paths/2.eps}\\
-%\quad\\
-%\includegraphics[width=0.45\textwidth]{plots/paths/3.eps}
-%\includegraphics[width=0.45\textwidth]{plots/paths/4.eps}
-\caption{Two arbitrary days with five simulated wind power production paths each.}
-\label{fig:simulation_paths}
-\end{figure}
-Once derived optimal estimates of the parameters of the complete likelihood for Model 2, we obtain empirical pointwise confidence bands for wind power production.
-Figure (\ref{fig:confidence_bands}) shows the empirical pointwise confidence bands for wind power production for each day of interest, assuming Model 2 specification, a given forecaster, and 5000 simulations per day.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.45\textwidth]{plots/bands/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/bands/2.eps}\\
-%\quad\\
-%\includegraphics[width=0.45\textwidth]{plots/bands/3.eps}
-%\includegraphics[width=0.45\textwidth]{plots/bands/4.eps}
-\caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(2.22,0.044,0.054)$. Blue line: real production.}
-\label{fig:confidence_bands}
-\end{figure}
-
-\subsubsection{Value of $\delta$}
-As a final verification, we study the behavior of $\delta$ as a function of the vector $\bm{\theta}$.
-Given a parameter vector, we calculate an initial guess for $\delta$ solving problem (\ref{eq:likelihood_delta}).
-Even when it is a guess, it helps us understand the meaning of this additional parameter qualitatively.\\
-\quad\\
-We choose as domain the most significant values of $\theta_0$ and $\theta_0\alpha$, regarding the previous numerical results. In Figure (\ref{fig:delta}) we can observe that:
-\begin{itemize}
-\item The initial time $\delta$ decreases as $\theta_0\alpha$ increases.
-This is a consequence of the increment in the diffusion as $\theta_0\alpha$ increases.
-As there is more diffusion, less time is needed for the initial transition density to cover the initial error observations.
-\item The initial time $\delta$ increases as $\theta_0$ increases.
-As we increment $\theta_0$, the mean reversion becomes larger and reduces the variance for the initial transition density.
-Then, more time is needed for the initial transition density to cover the initial error observations.\end{itemize}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.7\textwidth]{plots/delta/contour_delta.eps}
-\caption{Initial value for $\delta$ as a function of the elements of the parameter vector $\bm{\theta}$.}
-\label{fig:delta}
-\end{figure}
-
-%---END SECTION 6---
-
-%---BEGIN SECTION 7---
-
-\section{Conclusions} \label{Section_7}
-
-In this work, we propose a methodology to assess the short-term forecast of the normalized wind power, which is agnostic of the wind power forecasting technology.
-
-To this purpose, we built a phenomenological stochastic differential equation model for the normalized wind power production forecast error, with time-varying mean-reversion parameter in the linear drift coefficient, and state-dependent and time non-homogenous diffusion coefficient.
-We also used the Lamperti transform with unknown parameters to provide a version of the proposed model with a unit diffusion coefficient, increasing its stability properties.
-
-We used approximate likelihood-based methods for the models' calibration, and developed original algorithms to derive optimal estimates of the unknown parameters.
-The likelihood approach allowed for the extending of the SDE models in a very effective way, incorporating an early transition with an additional parameter that accounts for the forecast's uncertainty at the beginning of each future period.
-As a result, we obtained a robust procedure for synthetic data generation that, using the available forecast input, embraces future wind power production paths through empirical pointwise bands with prescribed confidence.
-
-On the basis of historical data of wind power production and forecast from different sources, our method came up with an objective tool for forecast assessment and comparison by performing the model selection stage.
-The application of the modeling procedure, inference through numerical optimization, and model selection through information criteria, to the wind power production dataset in Uruguay between April and December 2019, with three different providers, shows the excellent performance of our proposed model, which preserves the asymmetry of wind power forecast errors and their correlation structure.
-
-We conclude that our SDE model, featuring a time-derivative tracking of the forecast, a time-dependent mean-reversion parameter, and a state-dependent diffusion term that suitably adjusts to the problem under study, contributes toward the management of renewable energies efficiently.
-This methodology paves the way for stochastic optimal control methods enabling principled decision making under uncertainty in the presence of complex energy matrices.
-
-%---END SECTION 7---
-
-%---BEGIN APPENDIX---
-
-\section{Appendix} \label{Appendix}
-
-\subsection{The model}
-For a time horizon $T>0$, a parameter $\alpha > 0$, and $(\theta_t)_{t\in[0,T]}$ a positive deterministic  function,  let us consider the model  given by
-\begin{equation}
-\begin{cases}
-\dif X_t &= \big(\dot p_t - \theta_t (X_t-p_t)  \big)\dif t  +\sqrt{2 \alpha \theta_0 X_t (1-X_t)} \dif W_t, \quad t\in[0,T] \\
-X_0&= x_0\in [0,1],
-\end{cases}  \label{eq:model}
-\end{equation}
-where $(p_t)_{t\in[0,T]}$ denotes the prediction function that satisfies $0\le p_t\le 1$ for all $t\in[0,T]$. This prediction function is assumed to be a smooth function of the time so that 
-$$\sup_{t\in[0,T]}\bigl( |p_s| + |\dot p_s|\big) <+\infty .$$
-The following proofs are based on standard arguments for stochastic processes that can be found e.g. in \cite{Alf} and \cite{KarShr} that we adapted to the setting of our model \eqref{eq:model}.
-\begin{theorem}\label{thm:exun}
-Assume that    
-\begin{equation}\label{Assumption:1}
-\forall  t\in[0,T],\;\; 0\le \dot p_t +\theta_tp_t\le \theta_t, \;\;\mbox{ and }\;\;
-\sup_{t\in[0,T]}|\theta_t|<+\infty\tag{A}. 
-\end{equation}
-Then, there is a unique strong solution to \eqref{eq:model} s.t.  for all $t\in[0,T]$, $X_t\in[0,1]$ a.s.
-\end{theorem}
-\begin{proof}
-Let us first consider the following SDE for $t\in[0,T]$
-\begin{equation}\label{eq:eds1}
-X_t=x_0+  \int_0^t\big(\dot p_s - \theta_s(X_s-p_s)  \big)\dif s  + \int_0^t\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s, \quad 0\leq x_0\leq1.
-\end{equation}
-According to Proposition 2.13, p.291 of \cite{KarShr}, under assumption  \eqref{Assumption:1} there is a unique strong solution $X_t$ to \eqref{eq:eds1}.
-Moreover, as the diffusion coefficient is of linear growth, we have  for all $p>0$
-\begin{equation}\label{prop:fm}
-\mathbb E\left[ \sup_{t\in[0,T]}|X_t|^p\right]<\infty.
-\end{equation}
-Then, it remains to show that for all $t\in[0,T]$, $X_t\in[0,1]$ a.s.
-For this aim, we need to use the so-called Yamada function $\psi_n$ that is a $\mathcal C^2$ function that satisfies a bunch of useful properties:
-\begin{align*}
-&|\psi_n(x)|\underset{n\rightarrow+\infty}{\rightarrow}|x|, \;\; x{\psi'}_n(x)\underset{n\rightarrow+\infty}{\rightarrow}|x|, \;\; |\psi_n(x)|\wedge |x{\psi'}_n(x)| \le |x|\\
-&{\psi'}_n(x)\le 1, \;\; \mbox{and}\;\; {\psi''}_n(x)=g_n(|x|)\ge 0\;\; \mbox{with} \;\; g_n(x)x\le \frac 2n\;\;  \mbox{for all}\;\; x\in \mathbb R .
-\end{align*}
-See the proof of Proposition 2.13, p. 291 of \cite{KarShr} for the construction of such function.
-Applying Itô's formula we get
-\begin{align*}
-\psi_n(X_t)&=\psi_n(x_0) +\int_0^t {\psi'}_n(X_s)(\dot p_s + \theta_s p_s - \theta_sX_s  \big)\dif s \\
-&+ \int_0^t{\psi'}_n(X_s)\sqrt{2\alpha \theta_0 |X_s(1-X_s)|} \dif W_s + \alpha \theta_0 \int_0^t  g_n(|X_s|) |X_s(1-X_s)|\dif s.
-\end{align*}
-Now, thanks to  \eqref{Assumption:1}, \eqref{prop:fm}, and to the above properties of $\psi_n$ and $g_n$, we get
-$$
-\mathbb E\left[\psi_n(X_t)\right]\le \psi_n(x_0) +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E[{\psi'}_n(X_s)X_s] \right)\dif s + \frac{2\alpha  \theta_0}{n}\int_0^t \mathbb E \left[|1-X_s|\right]\dif s.
-$$
-Therefore, letting $n$ tends to infinity, we use Lebesgue's theorem to get
-$$
-\mathbb E\left[|X_t|\right]\le x_0 +\int_0^t \left(\dot p_s + \theta_sp_s -  \theta_s \mathbb E\left[|X_s|\right] \right)\dif s.
-$$
-Besides, taking the expectation of \eqref{eq:eds1}, we get
-$$
-\mathbb E \left[X_t\right]=x_0+  \int_0^t\big(\dot p_s +\theta_sp_s - \theta_s \mathbb E\left[X_s\right]  \big)\dif s,
-$$
-and thus we have 
-$$
-\mathbb E\left[|X_t| -X_t \right]\le \int_0^t \theta_s \mathbb E\left[ X_s - |X_s| \right]\dif s.
-$$
-Then, Gronwall's lemma gives us $\mathbb E\left[|X_t|\right]=\mathbb E \left[X_t\right]$ and thus for any $t\in[0,T]$ $X_t\ge0$ a.s.
-The same arguments work to prove that  for any $t\in[0,T]$ $Y_t:=1-X_t\ge0$  a.s.
-since the process $(Y_t)_{t\in[0,T]}$ is solution to
-$$
-\dif Y_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)\dif t  -\sqrt{2\alpha \theta_0Y_t(1-Y_t)} \dif W_t,
-$$
-Then similarly, we need to assume that $\dot p_t +\theta_tp_t\ge 0$. This completes the proof.
-\end{proof}
-
-\begin{theorem}\label{thm:mod2}
-Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
-Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$.
-Assume in addition that for all $t\in[0,T]$,  $p_t\in]0,1[$ and that
-\begin{equation}\label{Assumption:3}
-\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{B}. 
-\end{equation}
- Then, $\tau_0=\tau_1=+\infty$ a.s.
-\end{theorem}
-
-\begin{proof}
-For $t\in[0,\tau_0[$, we have 
-$$
-\frac{\dif X_t}{X_t}= \left(\frac{\dot p_t +\theta_t p_t}{X_t} - \theta_t\right)\dif t  +\sqrt{\frac{2\alpha \theta_0 (1-X_t)}{X_t}} \dif W_t 
-$$  
-so that
-$$
-X_t=x_0\exp\left(\int_0^t \frac{\dot p_s +\theta_sp_s- \theta_0 \alpha}{X_s}\dif s+\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\right),
-$$
-where $M_t=\int_0^t\sqrt{\frac{2\alpha \theta_0 (1-X_s)}{X_s}} \dif W_s$ is a continuous martingale. Then as for all $t\in[0,T]$, we have $\dot p_t +\theta_tp_t- \theta_0 \alpha\ge0$, we deduce that
-$$
-X_t\ge x_0\exp\left(\alpha\theta_0 t-  \int_0^t\theta_s\dif s + M_t\right).
-$$
-By way of contradiction let us assume that  $\{\tau_0<\infty\}$, then letting $t\to \tau_0$ we deduce that $\lim_{t\to \infty} \mathbf 1_{\{\tau_0<\infty\}}M_{t\wedge \tau_0}=\mathbf -1_{\{\tau_0<\infty\}}\infty$ a.s.
-This leads to a contradiction since we know that continuous martingales likewise the Brownian motion cannot converge almost surely to $+\infty$ or $-\infty$.
-It follows that $\tau_0=\infty$ almost surely.
-Next, recalling that  the process $(Y_t)_{t\geq 0}$  given by $Y_t=1-X_t$ is solution to
-$$
-\dif Y_t= \big( \theta_t(1-p_t) -\dot p_t - \theta_tY_t  \big)\dif t  -\sqrt{2\alpha \theta_0 Y_t(1-Y_t)} \dif W_t,
-$$
-we deduce using similar arguments as above 
-$\tau_1=\infty$ a.s. provided that $\theta_t(1-p_t) -\dot p_t -\alpha \theta_0 \ge 0$.
- \end{proof}
-
-Remark: As the diffusion coefficient of $X_t$  given by  $x \mapsto \sqrt{2 \alpha \theta_0 x(1-x)}$  is strictly positive for all $x \in  ]0,1[$, the condition \eqref{Assumption:3}  ensures that the transformation between $Z_t$ and $X_t$ is bijective, so that we deduce the properties of existence and uniqueness of $Z_t$ from those of $X_t$.
-The application of  It\^{o}'s formula in Section \ref{Section_4} is subjected to the condition \eqref{Assumption:3} that avoids the process $X_t$ hits the boundaries of the interval $ ]0,1[$, otherwise the Lamperti transform is not applicable.
-
-%---END APPENDIX---
+\tableofcontents
 
@@
 %% if your bibliography is in bibtex format, uncomment commands:
-\bibliographystyle{imsart-nameyear} % Style BST file
-\bibliography{aoas-template.bib}    % Bibliography file (usually '*.bib')
+%\bibliographystyle{imsart-nameyear} % Style BST file
+%\bibliography{bibliography}       % Bibliography file (usually '*.bib')
 

### 2020-07-13 LaTeX_Code/Paper/aoas-template.tex
Added all supplementary material plots (maybe I still need the xcross one)

@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/four_days/377.eps}
-\includegraphics[width=0.45\textwidth]{plots/four_days/417.eps}\\
+\includegraphics[width=0.485\textwidth]{plots/four_days/377.eps}\quad
+\includegraphics[width=0.485\textwidth]{plots/four_days/417.eps}\\
 %\quad\\
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
+\includegraphics[width=0.485\textwidth]{plots/LP_6.eps}
+\includegraphics[width=0.485\textwidth]{plots/MP_6.eps}\\
 \quad\\
-\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
+\includegraphics[width=0.485\textwidth]{plots/HP_6.eps}
+\includegraphics[width=0.485\textwidth]{plots/AP_6.eps}
 \caption{Wind production forecast error histograms during the period April-December 2019: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
+\includegraphics[width=0.485\textwidth]{plots/LP.eps}
+\includegraphics[width=0.485\textwidth]{plots/MP.eps}\\
 \quad\\
-\includegraphics[width=0.45\textwidth]{plots/HP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP.eps}
+\includegraphics[width=0.485\textwidth]{plots/HP.eps}
+\includegraphics[width=0.485\textwidth]{plots/AP.eps}
 \caption{Wind production forecast error histograms during the period April-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
+\includegraphics[width=0.485\textwidth]{plots/LP_t.eps}
+\includegraphics[width=0.485\textwidth]{plots/MP_t.eps}\\
 \quad\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
+\includegraphics[width=0.485\textwidth]{plots/HP_t.eps}
+\includegraphics[width=0.485\textwidth]{plots/AP_t.eps}
 \caption{Forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
@@
 \centering
-  \includegraphics[width=0.45\textwidth]{plots/31.eps}\includegraphics[width=0.45\textwidth]{plots/31_2.eps}
+  \includegraphics[width=0.485\textwidth]{plots/31.eps}\quad\includegraphics[width=0.485\textwidth]{plots/31_2.eps}
   \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (plot on the left) and with derivative tracking (plot on the right).}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
+\includegraphics[width=0.485\textwidth]{plots/LP_t_LP.eps}
+\includegraphics[width=0.485\textwidth]{plots/MP_t_LP.eps}\\
 \quad\\
-\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
-\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
+\includegraphics[width=0.485\textwidth]{plots/HP_t_LP.eps}
+\includegraphics[width=0.485\textwidth]{plots/AP_t_LP.eps}
 \caption{Lamperti transformed forecast error transition histograms between April and December 2019 without wind power production curtailment: low-power (upper-left plot), mid-power (upper-right plot), high-power (lower-left plot), and the global range of power (lower-right plot).}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{plots/LL/Log-Likelihood.eps}\includegraphics[width=0.5\textwidth]{plots/LL/Log-Likelihood_testing.eps}
+\includegraphics[width=0.485\textwidth]{plots/LL/Log-Likelihood.eps}\quad\includegraphics[width=0.485\textwidth]{plots/LL/Log-Likelihood_testing.eps}
 \caption{{Negative log-likelihood's level sets for the training sets (plot on the left), and for the test sets (plot on the right).
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/classic_noDelta/Optimal.eps}
-\includegraphics[width=0.45\textwidth]{plots/classic_noDelta/Lamperti_Optimal.eps}
-\caption{Probability histograms for error transitions.
+\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Optimal.eps}
+\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Lamperti_Optimal.eps}
+\caption{Density histograms for error transitions.
 Using provider A, we overlap the real transitions from the test set with the simulated ones from the $V-$space SDE.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/paths/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/paths/2.eps}\\
+\includegraphics[width=0.485\textwidth]{plots/paths/1.eps}\quad
+\includegraphics[width=0.485\textwidth]{plots/paths/2.eps}\\
 %\quad\\
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/bands/1.eps}
-\includegraphics[width=0.45\textwidth]{plots/bands/2.eps}\\
+\includegraphics[width=0.485\textwidth]{plots/bands/1.eps}\quad
+\includegraphics[width=0.485\textwidth]{plots/bands/2.eps}\\
 %\quad\\
@@
 \centering
-\includegraphics[width=0.7\textwidth]{plots/delta/contour_delta.eps}
+\includegraphics[width=0.6\textwidth]{plots/delta/contour_delta.eps}
 \caption{Initial value for $\delta$ as a function of the elements of the parameter vector $\bm{\theta}$.}

### 2020-07-13 MATLAB_Files/doc/batch_L.m

@@ -1,0 +1,7 @@
+function [val] = batch_L(batch, theta0, alpha)
+
+    % 29/03/2020 19:42
+    
+    
+
+end

### 2020-07-13 MATLAB_Files/doc/batch_with_theta_L.m

@@ -1,0 +1,15 @@
+function [batch_theta] = batch_with_theta_L(batch, alpha, theta_0) % 29/03/2020 19:43
+
+    batch(4,1)   = theta_t(theta_0, alpha, batch(1,1), batch(2,1));
+    batch(4,end) = theta_t(theta_0, alpha, batch(1,end), batch(2,end));
+    batch(5,1)   = lamperti_transform(theta_0,alpha,batch(3,1),batch(1,1),2);
+    batch(5,end) = lamperti_transform(theta_0,alpha,batch(3,end),batch(1,end),2);
+    
+    for i = 2:2:length(batch(1,:))-1
+        batch(4,i:i+1) = theta_t(theta_0, alpha, batch(1,i), batch(2,i));
+        batch(5,i:i+1) = lamperti_transform(theta_0, alpha, batch(3,i), batch(1,i),2);
+    end
+    
+    batch_theta = batch;
+    
+end

### 2020-07-13 MATLAB_Files/doc/cross_correlation_test_Lamperti.m

@@ -1,0 +1,123 @@
+close all;
+clear all;
+clc;
+
+% dataSet can be AWSTP (B), MTLOG (A) or UTEP5 (C).
+dataSet       = 'MTLOG';
+% epsilon can be 0.035 (B), 0.020 (A) or 0.028 (C).
+epsilon       = 0.020;
+% dataKind can be classic or comparable.
+dataKind      = 'comparable';
+train_data             = load_data_eps(epsilon,dataSet,dataKind);
+test_data              = load_data_eps_test(epsilon,dataSet,dataKind);
+[~, ~, table_complete] = load_data(dataSet);
+lag                    = 150;
+font_size              = 14;
+
+train_error = transpose(train_data.Error_Lamp);
+test_error  = transpose(test_data.Error_Lamp);
+all_error   = transpose(table_complete.Error_Lamp);
+
+[N1,M1]   = size(train_error);
+[N2,M2]   = size(test_error);
+all_error = all_error(:,end-(M1+M2)+1:end);
+[N3,M3]   = size(all_error);
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+for i = 1:M1-1
+    train_xcorr(:,i) = xcorr(train_error(:,i),train_error(:,i+1),lag,'normalized');
+end
+for i = 1:M2-1
+    test_xcorr(:,i) = xcorr(test_error(:,i),test_error(:,i+1),lag,'normalized');
+end
+for i = 1:M3-1
+    all_xcorr(:,i) = xcorr(all_error(:,i),all_error(:,i+1),lag,'normalized');
+end
+
+X1 = 1:M1-1; X2 = 1:M2-1; X3 = 1:M3-1;
+Y  = -lag:1:lag;
+[x1,y1] = meshgrid(X1,Y);
+[x2,y2] = meshgrid(X2,Y);
+[x3,y3] = meshgrid(X3,Y);
+
+figure('Renderer', 'painters', 'Position', [10 10 900 600]);
+contour(x1,y1,train_xcorr); colorbar;
+figure('Renderer', 'painters', 'Position', [10 10 900 600]);
+imagesc(X1,Y,train_xcorr); colorbar;
+title('Sample xcorr Function (observatios - training)');
+xlabel('Day'); ylabel('Lag');
+set(gca,'FontSize',font_size);
[…]

### 2020-07-13 MATLAB_Files/doc/dist.m

@@ -1,0 +1,6 @@
+function [val] = dist(v,xi1,xi2) % 03/02/2020 11:20
+    a   = -1;
+    b   =  1;
+    val = (1/abs(b-a)) * (1/beta(xi1,xi2)) * ((v-a)/(b-a))^(xi1-1)...
+        * (1-(v-a)/(b-a))^(xi2-1);
+end

### 2020-07-13 MATLAB_Files/doc/histogram_classic_SDE.m

@@ -1,0 +1,238 @@
+close all;
+clear all;
+clc;
+
+epsilon                = 0.020;
+dataKind               = 'comparable';
+dataSet                = 'MTLOG';
+Table_Testing_Complete = load_data_eps_test(epsilon,dataSet,dataKind);
+whatToDo               = 'Optimal'; 
+% whatToDo               = 'Lamperti_Optimal'; 
+% whatToDo               = 'Initial_Guess'; 
+
+% PARAMETERS:
+% set(0,'defaultAxesFontSize',18);
+save     = 0;
+delta    = 13; % The time is delta*10 minutes.
+
+if  strcmp(whatToDo,'Optimal')
+    theta_0 = 1.930;
+    alpha   = 0.050;
+elseif  strcmp(whatToDo,'Lamperti_Optimal')
+    theta_0 = 2.450;
+    alpha   = 0.097/2.450;
+    % V1: 
+    theta_0 = 2.8150; alpha = 0.1276;
+    % V2: 
+    theta_0 = 1.8708; alpha = 0.0431;
+elseif  strcmp(whatToDo,'Initial_Guess')
+    theta_0 = 1.6290;
+    alpha   = 0.06;
+else
+    error('Wrong whatToDo script!');
+end
+
+d  = Table_Testing_Complete.Date;
+p  = Table_Testing_Complete.Forecast;
+t  = Table_Testing_Complete.Time(1,:);
+x  = Table_Testing_Complete.Real_ADME;
+v  = Table_Testing_Complete.Error;
+dt = t(2); % This is the default dt. I will choose a smaller one.
+% If the dt is not small enough, we always scape from [0 1].
+dt = dt/1;
+
+minus_t = linspace(-delta*dt,-dt,delta);
+exten_t = [minus_t,t];
+
+total_x_s_trans = [];
+total_v_s_trans = [];
+
+for l = 1:1
+    for i = 1 : height(Table_Testing_Complete)
+
+        X = x(i,:);
+        P = p(i,:);
+        % All of them show similar results:
+        P_exten_linear = interp1([0 6*dt],[P(1) P(6)],minus_t,'linear','extrap');
+        P_exten_pchip  = interp1([0 6*dt],[P(1) P(6)],minus_t,'pchip','extrap');
+        P_exten_spline = interp1([0 6*dt],[P(1) P(6)],minus_t,'spline','extrap');
+        P_exten_makima = interp1([0 6*dt],[P(1) P(6)],minus_t,'makima','extrap');
+
[…]

### 2020-07-13 MATLAB_Files/doc/likelihood_nested_optimization_L.m

@@ -1,0 +1,12 @@
+function [x0,fval] = likelihood_nested_optimization_L(batch, x0, dt)
+
+    disp('================================================');
+    disp(['Initial values: Theta_0 = ',num2str(x0(1)),' and alpha = ',num2str(x0(2))]);
+    disp('================================================');
+
+    batch   = batch_with_theta_L(batch, x0(2), x0(1));
+    fun     = @(x) -likelihood_optimization_L(batch, x(1), x(2), dt);
+
+    [x0,fval] = fminsearch(fun, x0);
+
+end

### 2020-07-13 MATLAB_Files/doc/likelihood_optimization_L.m

@@ -1,0 +1,10 @@
+function [val] = likelihood_optimization_L(batch, theta0, alpha, dt)
+
+    % 29/03/2020 11:20
+    
+    disp(['Theta_0 = ',num2str(theta0),', Alpha = ',num2str(alpha),', Product = ',num2str(theta0*alpha)]);
+    
+%     batch = batch_with_theta_L(batch, alpha, theta0);
+    val   = log_LH_evaluation_L(batch, theta0, alpha, dt);
+
+end

### 2020-07-13 MATLAB_Files/doc/log_dist_extra.m

@@ -1,0 +1,6 @@
+function [val] = log_dist_extra(v,xi1,xi2) % 03/02/2020 11:20
+    a   = 0;
+    b   = 1;
+    val = -betaln(xi1,xi2) + (xi1-1)*log((v-a)/(b-a)) + ...
+        (xi2-1)*log((b-v)/(b-a));
+end

### 2020-07-13 MATLAB_Files/doc/mean_regression_M1_fe.m

@@ -1,0 +1,11 @@
+function [val] = mean_regression_M1_fe(x1,theta_0,dt,p1,p2)
+    
+    n   = 50;
+    p   = @(i) p1 + (p2-p1) * i/n;
+    val = x1;
+    
+    for i = 2:n
+        val = val - theta_0*(val - p(i))*dt;
+    end
+
+end

### 2020-07-13 MATLAB_Files/doc/moment_1.m

@@ -1,0 +1,18 @@
+function m1 = moment_1(v,theta_0,alpha,th1,th2,p1,p2,dt,n) 
+    % 02/04/2020 15:16
+
+    if th1 == th2 % We have the exact solution.
+        m1 = v*exp(-th1*dt);
+    else % Otherwise, we compute F-E.
+        p      = @(i) p1 + (p2-p1) * i/n; % We interpolate p(t).
+        pe_dot = (p2-p1) / dt;
+        theta  = @(i) theta_t(theta_0, alpha, p(i), pe_dot);
+        m1(1) = v;
+        
+        ds    = dt/n;
+        for i = 2:n
+            m1(i) = m1(i-1) * (1 - theta(i-1)*ds);
+        end
+    end
+    
+end

### 2020-07-13 MATLAB_Files/doc/moment_1_M1.m

@@ -1,0 +1,8 @@
+function m1 = moment_1_M1(x,theta_0,p1,p2,dt,n) % 19/04/2020 21:56
+    p     = @(i) p1 + (p2-p1) * i/n; % We interpolate p(t).
+    m1(1) = x;
+    ds    = dt/n;
+    for i = 2:n
+        m1(i) = m1(i-1) - theta_0*(m1(i-1)-p(i-1))*ds;
+    end
+end

### 2020-07-13 MATLAB_Files/doc/moment_2.m

@@ -1,0 +1,21 @@
+function m2 = moment_2(v,theta_0,th1,th2,p1,p2,alpha,m1,dt,n) % 02/04/2020 15:13
+
+    p      = @(i) p1 + (p2-p1) * i/n; % We interpolate p(t).
+    pe_dot = (p2-p1) / dt;
+    m2(1)  = v^2;
+    ds     = dt/n;
+    
+    if th1 == th2 % In this case, m_1 has exact solution and theta_t = theta_0.
+        theta = @(i) th2;
+        m1    = @(i) v*exp(-th1*dt*(i/n));
+    else
+        theta  = @(i) theta_t(theta_0, alpha, p(i), pe_dot);
+    end
+    
+    for i = 2:n
+        m2(i) = m2(i-1) + (-2*m2(i-1)*(theta(i-1)+alpha*theta_0) + ...
+            2*alpha*theta_0*m1(i-1)*(1-2*p(i-1)) + ...
+            2*alpha*theta_0*p(i-1)*(1-p(i-1))) * ds;
+    end
+    
+end

### 2020-07-13 MATLAB_Files/doc/moment_2_L.m

@@ -1,0 +1,18 @@
+function m2 = moment_2_L(m1,theta_0,alpha,p1,p2,dt,n)
+    % 29/03/2020 16:50
+
+    % This function returns the approximated variance.
+
+    p_dot = (p2-p1) / dt;
+    m2(1) = 0;
+    p_t   = @(i) p1 + (p2-p1) * i/n;
+    ds    = dt/n;
+    
+    for i = 2:n
+        Theta_t = theta_t(theta_0, alpha, p_t(i), p_dot);
+        b_prime = sde_Lamperti_drift_prime_cand2(m1(i-1),alpha,theta_0,Theta_t,p_t(i-1),p_dot);
+        m2(i)   = m2(i-1) + ds * ...
+            (1+2*m2(i-1)*b_prime);
+    end
+    
+end

### 2020-07-13 MATLAB_Files/doc/moments_verification_Lamperti.m

@@ -1,0 +1,233 @@
+close all;
+clear all;
+clc;
+
+epsilon                = 0.018;
+Table_Testing_Complete = load_data_eps_test(epsilon);
+
+t  = Table_Testing_Complete.Time(1,:);
+dt = t(2);
+
+theta_0 = 1.2656;
+alpha   = 0.07052;
+n       = 500;
+p_end   = 1/2;
+p_lims  = 0.03;
+
+p = p_end-p_lims:0.001:p_end+p_lims;
+v = -0.3:0.01:0.3;
+
+for i = 1:length(p)
+    
+    for j = 1:length(v)
+        
+        disp([num2str(i/length(p)),' and ',num2str(j/length(v))]);
+                
+        z = lamperti_transform(theta_0,alpha,v(j),p(i),2);
+        
+        P_dot        = (p_end-p(i)) / dt;
+        Theta_t      = theta_t(theta_0, alpha, p(i), P_dot);
+        
+        Exp_Z   = moment_1_L(z,theta_0,alpha,p(i),p_end,dt,n);
+        Exp_Z_2 = moment_2_L(Exp_Z,theta_0,alpha,p(i),p_end,dt,n) + Exp_Z(end)^2;
+                
+        for k = 1:100
+            sim_path_z(k)   = sde_Lamperti_FE(z,alpha,theta_0,Theta_t,dt,p(i),P_dot,2);
+            sim_path_z_2(k) = sde_Lamperti_FE_2(z^2,alpha,theta_0,Theta_t,dt,p(i),P_dot);
+        end
+        
+        Exp_Z_emp   = mean(sim_path_z);
+        Exp_Z_emp_2 = mean(sim_path_z_2);
+
+        exp_z_ode(i,j)   = Exp_Z(end);
+        exp_z_2_ode(i,j) = Exp_Z_2(end);
+        exp_z_emp(i,j)   = Exp_Z_emp;
+        exp_z_emp_2(i,j) = Exp_Z_emp_2;
+        
+    end
+end
+
+error_z   = abs(exp_z_ode-exp_z_emp);
+error_z_2 = abs(exp_z_2_ode-exp_z_emp_2);
+
+figure;
+[V,Y] = meshgrid(p-p_end,v);
+surf(V,Y,exp_z_emp');
+title('$E[Z]$ Empirical','interpreter','latex');
+xlabel('Prev. Rel. Forecast'); ylabel('Prev. Error (V)');
[…]

### 2020-07-13 MATLAB_Files/doc/new_batch_fixed_removed_samples.m

@@ -1,0 +1,18 @@
+function [Table_Training, new_bat] = new_batch_fixed_removed_samples(Table_Training, eta, batch_size, N)
+
+    Forecast     = Table_Training.Forecast;
+    Forecast_Dot = Table_Training.Forecast_Dot;
+    Error        = Table_Training.Error;
+    new_bat      = [];
+        
+    for i = 1:batch_size
+        for j = 2:N
+            forecast(2*j-3:2*j-2)     = Forecast(i,j-1:j);
+            forecast_dot(2*j-3:2*j-2) = Forecast_Dot(i,j-1:j);
+            error(2*j-3:2*j-2)        = Error(i,j-1:j);
+        end
+        if error(1) < eta && error(1) > -eta
+            new_bat = [new_bat, [forecast; forecast_dot; error]];
+        end
+    end
+end

### 2020-07-13 MATLAB_Files/doc/path_simulator_IG.m

@@ -1,0 +1,132 @@
+close all;
+clear all;
+clc;
+
+% dataSet can be AWSTP (B), MTLOG (A) or UTEP5 (C).
+dataSet  = 'MTLOG';
+% epsilon can be 0.035 (B), 0.018 (A) or 0.028 (C).
+epsilon  = 0.018;
+dataKind = 'comparable';
+Table_Testing_Complete = load_data_eps_test(epsilon,dataSet,dataKind);
+
+% PARAMETERS:
+% set(0,'defaultAxesFontSize',18);
+quantil  = 0;
+save     = 0;
+delta    = 22; % The time is delta*10 minutes.
+xlimit   = 1; % If this in 1, the plots start at time 0. Otherwise, at -delta.
+
+if quantil
+    numPaths = 5000;
+else
+    numPaths = 5;
+end
+
+theta_0 = 1.6290;
+alpha   = 0.06;
+
+d  = Table_Testing_Complete.Date;
+p  = Table_Testing_Complete.Forecast;
+t  = Table_Testing_Complete.Time(1,:);
+x  = Table_Testing_Complete.Real_ADME;
+v  = Table_Testing_Complete.Error;
+dt = t(2); % This is the default dt. I will choose a smaller one.
+% If the dt is not small enough, we always scape from [0 1].
+dt = dt/1;
+
+figure(10);
+
+minus_t = linspace(-delta*dt,-dt,delta);
+exten_t = [minus_t,t];
+
+for i = 1 : height(Table_Testing_Complete)
+
+    X = x(i,:);
+    P = p(i,:);
+    % All of them show similar results:
+    P_exten_linear = interp1([0 6*dt],[P(1) P(6)],minus_t,'linear','extrap');
+    P_exten_pchip  = interp1([0 6*dt],[P(1) P(6)],minus_t,'pchip','extrap');
+    P_exten_spline = interp1([0 6*dt],[P(1) P(6)],minus_t,'spline','extrap');
+    P_exten_makima = interp1([0 6*dt],[P(1) P(6)],minus_t,'makima','extrap');
+    
+    P        = [P_exten_linear,P]; % We extend the forecast.
+    for j = 1:length(P)
+        P(j) = max(P(j),epsilon);
+        P(j) = min(P(j),1-epsilon);
+    end
+    P_dot    = (-P(1:end-1) + P(2:end)) / dt; % This starts at 1 end ends at (end - 1).
[…]

### 2020-07-13 MATLAB_Files/doc/plotLamperti.m

@@ -1,0 +1,185 @@
+close all;
+clear all;
+clc;
+
+likelihood    = 'lamperti';
+% dataSet can be AWSTP, MTLOG or UTEP5.
+dataSet = 'MTLOG';
+% epsilon can be 0.035 (B), 0.018 (A) or 0.028 (C).
+epsilon       = 0.018;
+% dataKind can be classic or comparable.
+dataKind = 'comparable';
+[Ta_Tra_Comp] = load_data_eps(epsilon,dataSet,dataKind);
+
+Table_Training = Ta_Tra_Comp; % We copy it so we can modify it.
+
+Date              = Ta_Tra_Comp.Date;
+Time              = Ta_Tra_Comp.Time;
+Forecast          = Ta_Tra_Comp.Forecast;
+Forecast_Dot      = Ta_Tra_Comp.Forecast_Dot;
+Real_ADME         = Ta_Tra_Comp.Real_ADME;
+Error             = Ta_Tra_Comp.Error;
+Error_Transitions = Ta_Tra_Comp.Error_Transitions;
+Lamparti_Data     = Ta_Tra_Comp.Error_Lamp;
+Lamparti_Tran     = Ta_Tra_Comp.Error_Lamp_Transitions;
+
+dt         = Time(1,2);
+[M, N_ini] = size(Forecast);
+N          = N_ini - 1; % We have N_ini measurements but N samples.
+
+num_days                = height(Ta_Tra_Comp); % Maximum 127 for MTLOG.
+[Table_Training, batch] = new_batch_fixed(Table_Training,num_days,N);
+
+%% Log-Likelihood plot:
+
+val_theta_0 = [];
+val_alpha   = [];
+val_fval    = [];
+val_fval_2  = [];
+
+vec_theta_0 = 0.5:0.005:3;
+vec_alpha   = 0.01:0.001:0.1;
+num_divs    = 20;
+new_alpha   = 0.0965./vec_theta_0;
+
+% Version 2:
+vec_theta_0 = 0.5:0.05:10;
+vec_alpha   = 0.01:0.01:1;
+new_alpha   = 0.0965./vec_theta_0;
+
+for i = 1:length(vec_theta_0)
+
+    aux_theta_0 = ones(1,length(vec_alpha));
+    aux_alpha   = ones(1,length(vec_alpha));
+    aux_fval    = ones(1,length(vec_alpha));
+    aux_fval_2  = ones(1,length(vec_alpha));
[…]

### 2020-07-13 MATLAB_Files/doc/plotLamperti_V2.m

@@ -1,0 +1,147 @@
+close all;
+clear all;
+clc;
+
+% Lamperti has no sense here. I wanted to plot it as a function of the
+% parameters. Still, as the Lamperti transform also depends on the 
+% parameters, the data set changed in each evaluation of the Likelihood,
+% which has no sense. See plotLamperti.m.
+
+likelihood    = 'lamperti'; % 'normal' or 'lamperti'.
+% dataSet can be AWSTP, MTLOG or UTEP5.
+dataSet = 'MTLOG';
+% epsilon can be 0.035 (B), 0.018 (A) or 0.028 (C).
+epsilon       = 0.018;
+% dataKind can be classic or comparable.
+dataKind   = 'comparable';
+dataNumber = 'training';
+[Ta_Tra_Comp] = load_data_eps(epsilon,dataSet,dataKind,dataNumber);
+
+% AWSTP) (B)
+% T_0 = 1.42, Alpha = 0.069, prod = 0.0980, f = -36753.
+% AIC = -73502, BIA = -73487.
+% MTLOG) (A)
+% T_0 = 1.93, Alpha = 0.050, prod = 0.0965, f = -36852.
+% AIC = -73700, BIA = -73685.
+% UTEP5) (B)
+% T_0 = 1.38, Alpha = 0.078, prod = 0.1076, f = -36261.
+% AIC = -72518, BIA = -72503.
+
+Table_Training = Ta_Tra_Comp; % We copy it so we can modify it.
+
+Date              = Ta_Tra_Comp.Date;
+Time              = Ta_Tra_Comp.Time;
+Forecast          = Ta_Tra_Comp.Forecast;
+Forecast_Dot      = Ta_Tra_Comp.Forecast_Dot;
+Real_ADME         = Ta_Tra_Comp.Real_ADME;
+Error             = Ta_Tra_Comp.Error;
+Error_Transitions = Ta_Tra_Comp.Error_Transitions;
+Lamparti_Data     = Ta_Tra_Comp.Error_Lamp;
+Lamparti_Tran     = Ta_Tra_Comp.Error_Lamp_Transitions;
+
+dt             = Time(1,2);
+[M, N_ini]     = size(Forecast);
+N              = N_ini - 1; % We have N_ini measurements but N samples.
+
+num_days = height(Ta_Tra_Comp); % Maximum 127 for MTLOG.
+[Table_Training, batch] = new_batch_fixed(Table_Training,num_days,N);
+
+%% Initial parameters:
+
[…]

### 2020-07-13 MATLAB_Files/doc/sde_Lamperti_FE_2.m

@@ -1,0 +1,22 @@
+function sim_path_f = sde_Lamperti_FE_2(sim_path_i,alpha,theta_0,Theta_t,dt,P,P_dot)
+
+    % 02/04/2020 20:40
+    
+    n  = 50;
+    dt = dt / n;
+    fv = sim_path_i;
+    
+    for i = 1:n
+
+        z = -sqrt(sim_path_i);
+        b = sde_Lamperti_drift_cand2(z,alpha,theta_0,Theta_t,P,P_dot);
+
+        sim_path_i = sim_path_i + dt * (2*b*z + 1) + ...
+        2 * z * sqrt(dt) * randn(1);
+        sim_path_i = max(0,sim_path_i); % ARTIFICIAL.
+        
+    end
+    
+    sim_path_f = sim_path_i;
+    
+end

### 2020-07-13 MATLAB_Files/doc/sde_Lamperti_drift_prime_cand2.m

@@ -1,0 +1,6 @@
+function drift_prime = sde_Lamperti_drift_prime_cand2(z,alpha,theta_0,theta_t,p,p_dot)
+
+    drift_prime = (alpha*theta_0 - theta_t + cos(sqrt(2*alpha*theta_0)*z) * ...
+        (2*p_dot + theta_t*(2*p - 1))) / (sin(sqrt(2*theta_0*alpha)*z))^2;
+    
+end

### 2020-07-13 MATLAB_Files/doc/theta_t.m

@@ -1,0 +1,5 @@
+function [theta_t] = theta_t(theta_0, alpha, pe, pe_dot) % 13/03/2020 19:09
+
+    theta_t = max(theta_0, (theta_0*alpha + abs(pe_dot))/(min(pe,1-pe)));
+
+end

### 2020-07-13 LaTeX_Code/Paper/Supplementary Material/supp_mat_1.tex
Updated supplementary material

@@
 \RequirePackage[authoryear]{natbib}
+\usepackage{graphicx}
+\usepackage{bm}
+\usepackage{siunitx}
+\usepackage{booktabs}
+\usepackage{xcolor}
+\usepackage{float}
+\usepackage{commath}
+\usepackage{fancybox}
+\usepackage{tikz}
+\usepackage{hyperref}
+\usepackage{url}
 %\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
@@
 
+\section{Seasonality effect}
+
+To guaranty an homogeneous year, we study the Mean Absolute Error (MAE) for each provider and for each day.
+In Figures (\ref{MAE_pA}), (\ref{MAE_pB}), and (\ref{MAE_pC}), we can see the daily and weekly MAE for the providers A, B, and C, respectively.\\
+To compute the vector that we are piloting, we realize the operation
+\begin{equation*}
+\hat{V}(j) =\frac{1}{145} \sum_{i=1}^{145}|V(i,j)|\quad\text{where}\quad j\in\{1,\dots,147\}.
+\end{equation*}
+Recall that $V(i,j)$ is the normalized error between the ADME real production and the UTE forecast at time $i$ and for the day $j$.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_A/MAE.eps}
+\caption{Daily and weekly for the provider A.}
+\label{MAE_pA}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_B/MAE.eps}
+\caption{Daily and weekly for the provider B.}
+\label{MAE_pB}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_C/MAE.eps}
+\caption{Daily and weekly for the provider C.}
+\label{MAE_pC}
+\end{figure}
+
+\section{Hourly effect}
+
+We want to see the error throughout the day.
+We compute the MAE for each provider for each measurement during the day.
+In Figures (\ref{HMAE_pA}), (\ref{HMAE_pB}), and (\ref{HMAE_pC}), we can see the hourly MAE for the providers A, B, and C, respectively.\\
+
+To compute the vector that we are piloting, we realize the operation
+\begin{equation*}
+\hat{V}(i) =\frac{1}{147} \sum_{j=1}^{147}|V(i,j)|\quad\text{where}\quad i\in\{1,\dots,145\}.
+\end{equation*}
+Recall that $V(i,j)$ is the normalized error between the ADME real production and the UTE forecast at time $i$ and for the day $j$.\\
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_A/H_MAE.eps}
+\caption{MAE along the day for the provider A.}
+\label{HMAE_pA}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_B/H_MAE.eps}
+\caption{MAE along the day for the provider B.}
+\label{HMAE_pB}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.485\textwidth]{plots/mean_errors/prov_C/H_MAE.eps}
+\caption{MAE along the day for the provider C.}
+\label{HMAE_pC}
+\end{figure}
+
+\section{Forecast Error Vs Forecast:}
+
+We plot the forecast error as a function of the forecast value for each provider. In Figures (\ref{sA}), (\ref{sB}), and (\ref{sC}), we can see this plots for the providers A, B, and C, respectively.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/scatter/prov_A/scatter.eps}
+\caption{MAE along the day for the provider A.}
+\label{sA}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/scatter/prov_B/scatter.eps}
+\caption{MAE along the day for the provider B.}
+\label{sB}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/scatter/prov_C/scatter.eps}
+\caption{MAE along the day for the provider C.}
+\label{sC}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-07-13 LaTeX_Code/Paper/aoas-template.tex
Updated supplementary material

@@
 \centering
-\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Optimal.eps}
-\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Lamperti_Optimal.eps}
+\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Optimal.pdf}\quad
+\includegraphics[width=0.485\textwidth]{plots/classic_noDelta/Lamperti_Optimal.pdf}
 \caption{Density histograms for error transitions.
@@
 \centering
-\includegraphics[width=0.6\textwidth]{plots/delta/contour_delta.eps}
+\includegraphics[width=0.6\textwidth]{plots/delta/contour_delta.png}
 \caption{Initial value for $\delta$ as a function of the elements of the parameter vector $\bm{\theta}$.}

### 2020-07-19 LaTeX_Code/Paper/aoas-template.tex
Added Marco comments
Added most marcos comments

@@
 \centering
-\includegraphics[width=0.485\textwidth]{plots/four_days/377.eps}\quad
-\includegraphics[width=0.485\textwidth]{plots/four_days/417.eps}\\
+\includegraphics[width=0.485\textwidth]{plots/four_days/1.eps}\quad
+\includegraphics[width=0.485\textwidth]{plots/four_days/3.eps}\\
 %\quad\\
@@
 %\includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
-\caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blue line).}
+\caption{Two 24-hour segments with the normalized wind power real production in Uruguay (blue line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (black line).}
   \label{fig:sample_data}
@@
 \centering
-  \includegraphics[width=0.485\textwidth]{plots/31.eps}\quad\includegraphics[width=0.485\textwidth]{plots/31_2.eps}
+  \includegraphics[width=0.485\textwidth]{plots/31_2.eps}\quad\includegraphics[width=0.485\textwidth]{plots/31.eps}
   \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (plot on the left) and with derivative tracking (plot on the right).}
@@
 
-%---BEGIN APPENDIX---
-
-\section{Appendix} \label{Appendix}
-
-\subsection{The model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Single Appendix:                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{appendix}
+\section*{}%% if no title is needed, leave empty \section*{}.
+
 For a time horizon $T>0$, a parameter $\alpha > 0$, and $(\theta_t)_{t\in[0,T]}$ a positive deterministic  function,  let us consider the model  given by
@@
 
-%---END APPENDIX---
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Single Appendix:                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{appendix}
-%\section*{???}%% if no title is needed, leave empty \section*{}.
-%\end{appendix}
+\end{appendix}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Acknowledgements}
+\section*{Acknowledgements}
+This work was partially supported by the KAUST Office of Sponsored Research (OSR) under Award number URF/1/2584 -- 01 -- 01 in the KAUST Competitive Research Grants Program Round 8 and the Alexander von Humboldt Foundation.
+
 % The authors would like to thank ...
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{supplement}
-%\textbf{???}.
-%???.
-%\end{supplement}
+\begin{supplement}
+
+\sname{Supplement}
+\stitle{DATA AND SIMULATIONS}
+\slink[doi]{COMPLETED BY THE TYPESETTER}
+\sdatatype{.pdf}
+\sdescription{Supplementary Material contains the entire dataset with normalized wind-power production, the simulation-based results, and the complete set of empirical pointwise confidence bands for wind power production -- all corresponding to the forecast provider A.}
+\end{supplement}
 

### 2020-07-23 LaTeX_Code/Paper/aoas-template.tex
Minor changes
Paper submitted!

@@
 \centering
-\includegraphics[width=0.9\textwidth]{plots/wind_and_solar/plot_over_years.eps}
-\caption{Installed wind and solar power over the years \cite{sultana2017review}. We recall the importance of accurate forecasts to use green energies optimally.}
+\includegraphics[width=0.9\textwidth]{plots/wind_and_solar/plot_over_years_IRENA.eps}
+\caption{Worldwide installed wind and solar power 2010--2019 \citep{irena20}. We recall the importance of accurate forecasts to use green energies optimally.}
 \end{figure}
 
-Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
+%Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
+Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite{gieb}, \cite{chang}, \cite{zhbo}):
 \begin{itemize}
@@
 \centering
-  \includegraphics[width=0.485\textwidth]{plots/31_2.eps}\quad\includegraphics[width=0.485\textwidth]{plots/31.eps}
+  \includegraphics[width=0.485\textwidth]{plots/1.eps}\quad\includegraphics[width=0.485\textwidth]{plots/bands/1.eps}
   \caption{Pointwise confidence bands fitted, for the same daily segment, through diffusion models without derivative tracking (plot on the left) and with derivative tracking (plot on the right).}
@@
 
-It is worth mentioning that Jacobi diffusions have been successfully applied in several disciplines, among them finance (see \cite{vago} and references therein) and neuroscience (\cite{dotala}).
+It is worth mentioning that Jacobi diffusions have been successfully applied in several disciplines, among them finance (see (\cite{vago}) and references therein) and neuroscience (\cite{dotala}).
 
@@
 \end{equation} \label{condB}
-The proof of this theoretical statement is presented in Section \ref{Appendix}. \\
+The proof of this theoretical statement is presented in the Appendix. \\
 
@@
 \begin{equation}
-  p_t^{\epsilon} = \left\{
-  \begin{array}{@{}cl@{}}
-    \epsilon \!\!\!&\text{if \quad} p_t  < \epsilon  \\
-    p_t  \!\!\!&\text{if \quad}  \epsilon \leq p_t < 1 - \epsilon \\
-    1 - \epsilon  \!\!\!&\text{if \quad}  p_t \geq 1 - \epsilon
- \end{array}\right.  \label{corrforecast}
+p_t^{\epsilon}=\begin{cases}
+\epsilon&\quad\text{if}\quad p_t<\epsilon\\
+p_t&\quad\text{if}\quad\epsilon\leq p_t<1-\epsilon\\
+1-\epsilon&\quad\text{if}\quad p_t\geq1-\epsilon
+\end{cases}
+\label{corrforecast}
 \end{equation}
@@
 \end{equation*}
-with the discrete sum $\sum_{0< t_{j, i-1} \leq t}\left(V_{t_{j, i}} - V_{t_{j, i-1}}\right)^2$.
+with the discrete sum $\sum_{0< t_{j, i-1} \leq t}\left(V_{t_{j, i}} - V_{t_{j, i-1}}\right)^2$.\smallskip
 
@@
 \end{tabular}
-\caption{Value points from Figure \ref{fig:neg-LL}.}
+\caption{Coordinates of the initial guess point and of the optimal points represented in Figure \ref{fig:neg-LL}.}
 \label{tab:optimal_values}
@@
 \section*{Acknowledgements}
-This work was partially supported by the KAUST Office of Sponsored Research (OSR) under Award number URF/1/2584 -- 01 -- 01 in the KAUST Competitive Research Grants Program Round 8 and the Alexander von Humboldt Foundation.
+This research was partially supported by the KAUST Office of Sponsored Research (OSR) under Award number URF/1/2584 -- 01 -- 01 in the KAUST Competitive Research Grants Program Round 8, the Alexander von Humboldt Foundation, the chair Risques Financiers, Fondation du Risque, and the Laboratory of Excellence MME-DII Grant no.
+ANR11-LBX--0023--01 (\url{http://labex-mme-dii.u-cergy.fr/}).
+We thank UTE (\url{https://portal.ute.com.uy/}) for providing the data used in this research.
 

### 2020-07-23 MATLAB_Files/doc/load_data_eps_test.m

@@ -2,10 +2,10 @@ function [Table_Testing_Complete] = load_data_eps_test(ep,dataSet,dataKind,set_t
     
     % 18/03/2020 10:41
 
-    if strcmp(set_type,'classic')
-        if strcmp(dataKind,'testing')
+    if strcmp(dataKind,'classic')
+        if strcmp(set_type,'testing')
             [~, Table_Testing_Complete, ~] = load_data(dataSet);
-        elseif strcmp(dataKind,'training')
+        elseif strcmp(set_type,'training')
             [Table_Testing_Complete, ~, ~] = load_data(dataSet);
         end
     elseif strcmp(dataKind,'comparable')

### 2020-07-23 MATLAB_Files/doc/path_simulator_OPT_forSuppMat.m

@@ -3,11 +3,14 @@
 % KAUST: King Abdullah University of Science and Technology
 % email: Renzo.CaballeroRosas@kaust.edu.sa CaballeroRenzo@hotmail.com
 % Website: https://orcid.org/0000-0003-3220-0923.
-% July 2020; Last revision: 13/07/2020.
+% July 2020; Last revision: 19/07/2020.
 
 close all;
 clear all;
 clc;
+
+% We fix the seed:
+rng(1);
 
 % dataSet can be AWSTP (B), MTLOG (A) or UTEP5 (C).
 dataSet  = 'MTLOG';
@@ -16,174 +19,176 @@ epsilon  = 0.020;
 % dataKind can be classic or comparable.
 dataKind = 'comparable';
 set_type = 'testing'; % 'testing' or 'training'.
-Table_Testing_Complete = load_data_eps_test(epsilon,dataSet,dataKind,set_type);
-whatToDo = 'optimal_value';
-% whatToDo = 'Optimal_Lamperti';
 
-% PARAMETERS:
-% set(0,'defaultAxesFontSize',18);
-quantil  = 0;
-save     = 0;
-delta    = 13; % The time is delta*10 minutes.
-xlimit   = 1; % If this in 1, the plots start at time 0. Otherwise, at -delta.
-norm_lim = 0; % If 1, x=[0,1], if 0, x=[1PM 1PM].
-% Also, when norm_lim = 0, we check the real accuracy for the bands.
-new_time = [13-(1/6)*delta:1/6:37]/24;
-counting   = zeros(4,1);
-counting_2 = zeros(4,1);
+types    = {'testing','training'};
+options  = {0,1};
+angle    = 45;
 
-if quantil
-    numPaths = 5000;
-else
-    numPaths = 5;
-end
-
-if  strcmp(whatToDo,'optimal_value')
+for y = 1:2
     
-    if  strcmp(set_type,'testing') % We do inference with training.
-        theta_0 = 1.93;
-        alpha   = 0.05;
-    elseif strcmp(set_type,'training') % We do inference with testing.
-        theta_0 = 1.59;
-        alpha   = 0.056;
-    end
-    
-elseif  strcmp(whatToDo,'Optimal_Lamperti')
-    
-%     theta_0 = 2.200;
-%     alpha   = 0.038;
-% V2:
-    theta_0 = 1.8708;
-    alpha   = 0.0431;    
-    
-else
[…]

### 2020-08-05 LaTeX_Code/Reports/old_reports/RW_convergence_results.tex
Updated main files

\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\usepackage{wrapfig}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{bm}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

\setbeamertemplate{caption}[numbered]

\title{Uncertainty of Power Generation Forecasts}
\subtitle{ Waleed Alhaddad}

\begin{document}
\setbeamercolor{background canvas}{bg=blue!3}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}[label=guide]\frametitle{ Reader's Guide }

List of changes in this iteration:
\begin{itemize}
\item Extrapolate one hour backwards to circumvent the big error of the initial point.
\item Implemented the new parameterized drift term  to prevent the process from leaving the permissible range.
\end{itemize}

Next steps:
\begin{itemize}
\item Find some metric to measure how good is the model
\item Compute the confidence intervals in another way.
\end{itemize}

Note :
\begin{itemize}
\item Green slides: possible future extensions
\item Red slides: notes to be removed
\end{itemize}

\end{frame}

\begin{frame}\frametitle{ Base Model }
Let $V_t$ be the deviation of the wind power generation forecasts from actual wind power generation. That is, $V_t$ models the errors or uncertainty of a given set of wind power generation forecasts.

We propose a forecast-error model based on the following parameterized stochastic differential equation (SDE), 
\begin{equation}
\begin{split}
dV_t &= a(V_t; \bm{\theta}) dt + b (V_t; \bm{\theta} ) dW_t \quad t > 0 \\
V_0 & = v_0
\end{split}\label{main}
\end{equation}

\begin{itemize}
%\item $\Delta_N$: any function of the number of samples, $N$. For example, $\Delta_N = \frac{1}{N}$.
\item $a(V_t; \bm{\theta})$: Drift function 
\item $b (V_t; \bm{\theta} )$: Diffusion function 
\item $\bm{\theta}$: a vector of parameters
\item $dW_t$: Standard Wiener random process.
\end{itemize}
\end{frame}

\begin{frame}\frametitle{ Physical  Restriction }
It is necessary to keep  the power generation forecast plus its errors  inside the range $[0,1]$ where we have normalized against the power generating capacity of the power plant.  To ensure that, we choose our model to have zero diffusion near the boundaries. Hence, we  formulate the following diffusion  term, 
\begin{equation*}
b(V_t; \bm{\theta}) =  \sqrt{2 \theta \alpha p_t(1-p_t) X_t (1-X_t)}    = \sqrt{2 \theta \alpha p_t(1-p_t) (V_t +p_t ) (1-V_t-p_t)}  
\end{equation*}
It remains to control the drift term. As a first requirement, we need the drift term to be mean reverting to the power generation forecast. Thus, we formulate the following drift, 
\begin{equation}
a(V_t; \bm{\theta}) =  - \theta (X_t - p_t)= - \theta V_t 
\end{equation}
However, this does not track the rate of change of the forecast $\dot{p}$ which may results in $X_t$ exiting the interval $[0,1]$ when the forecast is a small $\delta$ distance away from the boundaries. 
\end{frame}

\begin{frame}\frametitle{ Physical  Restriction - Drift Near the Boundaries}
To see the issue, we switch to the point of view of the forecast prediction process $X_t$.  In this point of view, we have shown in our results that it is necessary to include derivative tracking in order to follow the power production forecast accurately.The derivative tracking model is given by,
\begin{equation}
\begin{split}
dX_t &= \hat{a}(X_t; \bm{\theta}) dt + \hat{b} (X_t; \bm{\theta} ) dW_t \quad t > 0 \\
X_0 & = x_0
\end{split}\label{main_X}
\end{equation}
where 
\begin{equation}
\begin{split}
\hat{a}(X_t; \bm{\theta}) &= \dot{p}_t + a(X_t; \bm{\theta}) =  \dot{p}_t - \theta \left(X_t - p_t\right)   \\
\hat{b}(X_t; \bm{\theta}) &=  b(X_t; \bm{\theta}) =  \sqrt{2 \theta \alpha p_t(1-p_t) X_t (1-X_t)}    \\
\end{split}
\end{equation}
It is clear in this point of view to see that  term $\dot{p}_t $ is not controlled to maintain that $X_t$ stays inside the  range $[0,1]$.
\end{frame}

\begin{frame}\frametitle{ Physical  Restriction - Drift Near the Boundaries}
We have that the first moment of the process $X_t$ is given by the following ODE, 
\begin{equation}
\dot{m}_1 (t) = \frac{d \E[ X_t] }{d t} = \dot{p}_t- \theta \E [ X_t ]  + \theta p_t =   \dot{p}_t- \theta m(t) + \theta p_t
\end{equation}
Re-arranging, 
\begin{equation}
\frac{\dot{m}_1 (t)}{\theta}  + m(t)=   \frac{\dot{p}_t}{\theta}  + p_t 
\end{equation}
Note that by setting $\hat{a}(X_t; \bm{\theta}) =0$, we find that  $ \frac{\dot{p}_t}{\theta}  + p_t $ is also a line of zero drift or a line of mean stationarity 
Thus, must have that, 
\begin{equation}
 0 \leq  \frac{\dot{p}_t}{\theta}  + p_t  \leq 1
\end{equation}
to keep the process $X_t$ inside the interval $[0,1]$.
The condition  can be rewritten as, 
\begin{equation}
\frac{- |\dot{p_t}|}{p_t} \leq \theta \leq \frac{|\dot{p}_t|}{1- p_t}
\end{equation}
\end{frame}

\begin{frame}\frametitle{ Physical  Restriction - Drift Near the Boundaries}
To enforce the condition, 
\begin{equation}
 0 \leq  \frac{\dot{p}_t}{\theta}  + p_t  \leq 1
 \label{cond_drift}
\end{equation}
We  define an adjusted drift $\theta = \theta_0 f( p_t, \dot{p}_t) $  which satisfies the condition when
\begin{equation}
\theta = \theta_0 f( p_t, \dot{p}_t) \leq \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)} 
\end{equation}

Thus we choose $\theta$ such that,
\begin{equation}
\theta = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
\end{equation}

\end{frame}

\begin{frame}\frametitle{ Base Model }
We combine  the previous results to obtain the following SDE model, 
\begin{equation}
\begin{split}
dV_t &= a(V_t; \bm{\theta}) dt + b (V_t; \bm{\theta} ) dW_t \quad t > 0 \\
V_0 & = v_0
\end{split}\label{main}
\end{equation}

\begin{itemize}
%\item $\Delta_N$: any function of the number of samples, $N$. For example, $\Delta_N = \frac{1}{N}$.
\item $a(V_t; \bm{\theta})$: Drift function 
\item $b (V_t; \bm{\theta} )$: Diffusion function 
\item $\bm{\theta}$: a vector of parameters
\item $dW_t$: Standard Wiener random process.
\end{itemize}
\end{frame}

\begin{frame}
In order to respect the physical restrictions discussed above, we prescribe the following specifications
\begin{equation}
\begin{split}
a(V_t; \bm{\theta}) &= - \theta V_t \\
b(V_t; \bm{\theta}) &=\sqrt{2 \theta \alpha p_t(1-p_t) (V_t +p_t ) (1-V_t-p_t)}  \\
\end{split}
\end{equation}

with
\begin{equation}
\theta = \max \left( \theta_0 \ , \ \frac{|\dot{p}_t|}{\min (p_t, 1-p_t)}  \right )
\end{equation}

Where 
\begin{itemize}
\item $p_t$: Numerical wind power generation forecast.
\item $\theta >0$: Mean reversion parameter.
\item $\alpha>0$: Variability parameter.
\end{itemize}
\end{frame}

\begin{frame}\frametitle{ Implementation }

\begin{itemize}
\item We linearly interpolate the forecast and data. Note that higher-order of interpolation cause the forecast and data to escape the interval $[0,1]$.
\item Extrapolate one hour backwards and take that as the new initial point.
\item We find the first integer $\kappa$ such that the line of mean stationarity $ \frac{\dot{p}_t}{\theta}  + p_t$ is inside the range $[0,1]$. 
\item Simulate each forecast using the modified $\theta = \theta_0 f(p_t)$ with its path specific constant $\kappa$.
\item Obtain the empirical  confidence intervals of each forecast.
\end{itemize}

\end{frame}

\begin{frame}\frametitle{ Results }

See attached two PDF files, the file 6hr.pdf covers the first six hours while 72hr.pdf covers 72 hours.

\end{frame}

\againframe{guide}

\end{document}

### 2020-08-05 LaTeX_Code/Reports/old_reports/abstract_Berlin.tex
Updated main files

--- 2019-04-23 LaTeX_code/abstract_Berlin_NT.tex
@@
-\documentclass[12pt]{article}
-\usepackage[table]{xcolor}
-\usepackage[margin=1in]{geometry} 
-\usepackage{amsmath,amsthm,amssymb}
-\usepackage[english]{babel}
-\usepackage{tcolorbox}
-\usepackage{enumitem}
-\usepackage{hyperref}
-\usepackage{listings}
-\usepackage{blkarray}
+\documentclass[a4paper, 12pt]{article}
+\usepackage[utf8]{inputenc}
+\usepackage[activeacute, english]{babel}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+\usepackage{amsmath}
+\usepackage{bbm}
+\usepackage{mathtools}
+\usepackage{bm}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{amsmath}
+\usepackage{mathrsfs}
+\usepackage{tikz}
 \usepackage{float}
-\usepackage{bm}
-\usepackage{subfigure}
-\usepackage{booktabs}
-\usepackage{siunitx}
+\usepackage{algpseudocode}
+\usepackage{caption}
+\usepackage{subcaption}
 
-\setcounter{secnumdepth}{5}
-\setcounter{tocdepth}{5}
+\newcommand\dist{\stackrel{\mathclap{\footnotesize\mbox{d.}}}{=}}
+\usepackage[spanish,onelanguage,ruled,lined, linesnumbered]{algorithm2e}
+\usepackage[spanish,onelanguage]{algorithm2e}
+\newtheorem{theorem}{Teorema}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposición}
+%\newenvironment{proof}[1][Demostración]{\begin{trivlist}
+%		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+\newenvironment{definition}[1][Definición]{\begin{trivlist}
+		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+\newenvironment{example}[1][Ejemplo]{\begin{trivlist}
+		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+\newenvironment{remark}[1][Nota]{\begin{trivlist}
+		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+\newcommand{\negr}[1]{\textit{\textbf{#1}}}
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{proposition}
-\newtheorem{exmp}{Example}[section]\newtheorem{definition}{Definition}[section]
-\newtheorem{remark}{Remark}
-\newtheorem{ex}{Exercise}
-\theoremstyle{definition}
-\theoremstyle{remark}
-\bibliographystyle{elsarticle-num}
-
-\DeclareMathOperator{\sinc}{sinc}
-\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\E}{\mathbb{E}}
-\newcommand{\matindex}[1]{\mbox{\scriptsize#1}}
-\newcommand{\V}{\mathbb{V}}
-\newcommand{\Q}{\mathbb{Q}}
-\newcommand{\K}{\mathbb{K}}
-\newcommand{\C}{\mathbb{C}}
-\newcommand{\prob}{\mathbb{P}}
-
-\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}
-
-\title{Uncertainty Quantification in Wind Power Forecasting  \\ Conference Abstract}
+\title{On the Uncertainty of Wind Power Forecasts \\ Abstract}
 
@@
 
-%\pagebreak
-%\tableofcontents
-%\pagebreak
-\section{Abstract 600 char}
-Reliable wind power generation forecasting is crucial to meet energy demand, to trade and invest.
-We propose a model to simulate and quantify uncertainties in such forecasts.
-This model is based on Stochastic Differential Equations whose time-dependent parameters are inferred using continuous optimization of an approximate Likelihood function.
-The result is a skew stochastic process that simulates uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects.
-We apply the model to historical Uruguayan data and forecasts.
-
 \section{Motivation}
@@
 This is also of importance for energy trading and insurance, that it is to deliver power in an optimal cost-effective way to adhere to a variety of financial contracts.
-Uncertainty quantification is key in the design of financial contracts and taking investment decisions in the energy sector.
+Uncertainty quantification is key in the design  financial contracts and taking investment decisions in the energy sector.
 Additionally, it assists in the placement and design of renewable power plants.
@@
 
+%\subsection{Model}
+%\begin{thebibliography}{99}
+%	\bibitem{apo} Apostol, T. (1974). \emph{Mathematical Analysis} (2nd ed.),  Addison-Wesley. pp.218-230
+%	\bibitem{E} Cabaña, E. (2012). \emph{Introducción a los
+%		procesos estocásticos}, Notas
+%	para el Curso de la Licenciatura en Estadística, Universidad de la República. pp.98-115
+%\end{thebibliography}
+
 \end{document}

### 2020-08-05 LaTeX_Code/Reports/old_reports/abstract_Berlin_NT.tex
Updated main files

--- 2019-04-23 LaTeX_code/abstract_Berlin_NT.tex
@@
 
-\title{Uncertainty Quantification in Wind Power Forecasting  \\ Conference Abstract}
+\title{Uncertainty Quantification in Wind Power Forecasting  \\ }
 
-\author{Waleed Alhaddad \quad  Ra\'ul Fidel Tempone \\ CEMSE, KAUST}
+\author{Waleed Alhaddad }
 
@@
 %\pagebreak
-\section{Abstract 600 char}
+\section{Abstract}
 Reliable wind power generation forecasting is crucial to meet energy demand, to trade and invest.
@@
 The result is a skew stochastic process that simulates uncertainty of wind power forecasts accounting for maximum power production limit and other temporal effects.
-We apply the model to historical Uruguayan data and forecasts.
+We will apply the model to historical  data and forecasts.
 
@@
 Finally, we apply our model to synthetic and real wind power generation data for benchmarking.
-We apply the model to Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the period of March 1 to May 31, 2016.
+We apply the model to real  wind power production data and their corresponding numerical forecasts.
 
@@
 \section{Conclusion}
-We were able to simulate and quantify the uncertainties for a diverse range of forecasts based on the Uruguayan wind power production as determined by historical data and corresponding numerical forecasts for the period of March 1 to May 31, 2016.
-We compare our results to similar works in the literature.
-And we highlight the importance of asymmetry and the avoidance of phase shift artifacts which we were able to overcome.
+We  propose a model to quantify the uncertainties in wind power generation forecasts.
+It is important to note that this approach is agnostic of forecasting technology.
+We have also taken into account the physical limits of the model by respecting the full installation power of the wind farm.
+Additionally, we have taken into account skew-symmetric errors.
+The skewness of the forecast errors is necessary to correctly model the errors when operating near full installation power production or in cases of extremely low wind power production.
 

### 2020-08-05 LaTeX_Code/Reports/old_reports/continous_report.tex
Updated main files

--- 2019-04-23 LaTeX_code/RW_convergence_results.tex
@@
 \begin{itemize}
-\item Implemented Beta transitions
-\item Implemented time dependent forecast
-\item Numerically solve for the first two moments
-\item Time dependent path variability parameter
-\item Convergence results of all the above
+\item Matched data with every forecast
+\item Normalized according to installed power of each period
+\item Interpolated the forecast using cubic splines.
+
 \end{itemize}
@@
 \begin{itemize}
-\item Use real data and forecast.
-\item Try exponential decay in the mean reversion.
+\item upgrade the numerical integrator and use the interpolated forecast
+\item Check performace using the interpolated forecasts and data
 \end{itemize}
@@
 
-\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent  parameters }
+\begin{frame}\frametitle{ Case 5.2.1: Time dependent Forecast  }
 We approximate all transitions by a Beta transition density, we obtain the log-likelihood, 
@@
 
-\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent parameters }
+\begin{frame}\frametitle{ Case 5.2.1: Time dependent Forecast  }
 We generate samples using the previous Euler scheme to numerically compute the moments before each realization.We obtain the following sample paths
@@
 
-\begin{frame}\frametitle{ Case 5.2: Time dependent Forecast - time dependent parameter }
+\begin{frame}\frametitle{ Case 5.2.1: Time dependent Forecast  }
 We perform a convergence test for speed of reversion parameter $\theta = 0.5$ and time dependent path variablitiy $\alpha (t) =  \alpha p_t (1-p_t)$ where $\alpha=0.3$.
@@
 
+\begin{frame}\frametitle{ Real data and Forecast  }
+\begin{itemize}
+\item We have compiled 1265 forecasts from two full years (2016-2017) along with the measured real power generation.
+\item The real power generation data has been matched to the forecast using timestamps (Unix time). 
+We have 72 hourly observations for each forecast.
+\item Data is normalized according to the installed power at that specific period of the forecast.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}\frametitle{  Real data and Forecast }
+\begin{figure}
+    \includegraphics[scale=0.3]{Figures/forecast_data.eps}
+  \caption{ Random selection of forecasts and their associated real power generation data }
+  %\label{fig:boat1}
+\end{figure}
+\end{frame}
+
+\begin{frame}\frametitle{ Forecast cubic splines interpolation }
+
+For better numerical integration of the ODEs in order to find the moments of the stochastic process $V_t$, we need to interpolate between the discrete values of the forecast (as the given forecast is not fine-grained).
+\\
+
+In this case, we choose to use cubic splines.
+
+\end{frame}
+
+\begin{frame}\frametitle{ Forecast cubic splines interpolation }
+
+\begin{figure}
+    \includegraphics[scale=0.3]{Figures/forecast_splines.eps}
+  \caption{  Random selection of forecasts discrete values and the associated cubic splines interpolation }
+  %\label{fig:boat1}
+\end{figure}
+
+\end{frame}
+
 %\begin{frame}\frametitle{ Case 4.1.1: Following a constant function - constant parameters }

### 2020-08-05 Reports/20200220 - Lamperi for X and V/20200220 - Lamperi for X and V.tex
Updated main files

\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{commath}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{siunitx}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}
\DeclareMathOperator{\sign}{sign}

\title{Lamperti Transform for the processes X and V}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $X_t$:}

$\dif X_t=\left(\dot p_t-\theta_t(X_t-p_t)\right)\dif t+\sqrt{2\theta_t\alpha X_t(1-X_t)}\dif W_t\implies$
\begin{equation*}
\psi(X_t,t)=\int\frac{1}{\sqrt{2\theta_t\alpha u(1-u)}}\dif u\Bigg|_{u=X_t}=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-X_t}\right).
\end{equation*}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $V_t$:}

$\dif V_t=\underbrace{-\theta_tV_t}_{f(V_t,t)}\dif t+\underbrace{\sqrt{2\theta_t\alpha(V_t+p_t)(1-V_t-p_t)}}_{\sigma(V_t,t)}\dif W_t\implies$
\begin{equation*}
\psi(V_t,t)=\int\frac{1}{\sqrt{2\theta_t\alpha(u+p_t)(1-u-p_t)}}\dif u\Bigg|_{u=V_t}=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-V_t-p_t}\right).
\end{equation*}
We can see that for every $t=t^*$, the primitive function of $\frac{1}{\sigma(v,t^*)}$ is well defined for all $v\in\left[-p(t^*),1-p(t^*)\right]\subset[-1,1]$ (recall $V_t=X_t-p_t$, and $x\in[0,1]$).

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $V_t$:}

We define $\Psi(V_t,t)=\int_{\epsilon}^u\frac{1}{\sigma(u,t)}\dif u\Big|_{u=V_t}$ where $\epsilon$ is in the space of $V_t$ (which depends on $p_t$).\\
\quad\\
We have that $V_t=X_t-p_t\iff V_t+p_t=X_t\implies0\leq V_t+p_t\leq1\iff-p_t\leq V_t\leq1-p_t$. Then, for each $t=t^*$, the space of the process is $[-p_{t^*},1-p_{t^*}]$. Now, notice that for all $p_{t^*}\in[0,1]$, we have that $q\in[-p_{t^*},1-p_{t^*}]$ if and only if $q=0$.\\
\quad\\
We conclude that if we want a fix value for $\epsilon$, necessarily we need to choose $\epsilon=0$.\\
\quad\\
We have that $\psi_v(V_t,t)=\Psi_v(V_t,t)$. However, $\psi_t(V_t,t)=\Psi_t(V_t,t)$ is in general no true, and $\Psi_t(V_t,t)$ has a more complicate expression.\\
\quad\\
If we choose $\epsilon=0$, we have that $\Psi_t(V_t,t)=\psi_t(V_t,t)+\frac{\dif}{\dif t}\int\frac{\dif u}{\sigma(u,t)}\Big|_{u=\epsilon=0}$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $V_t$:}

\begin{itemize}
\item $\Psi(V_t,t)=\psi(V_t,t)-\psi(\epsilon,t)\Big|_{\epsilon=0}=\sqrt{\frac{2}{\alpha\theta_t}}\left[\arcsin(\sqrt{1-\epsilon-p_t})-\arcsin(\sqrt{1-V_t-p_t})\right]\Big|_{\epsilon=0}=\sqrt{\frac{2}{\alpha\theta_t}}\left[\arcsin(\sqrt{1-p_t})-\arcsin(\sqrt{1-V_t-p_t})\right]$.
\item $\Psi_v(V_t,t)=\psi_v(V_t,t)=\frac{1}{\sigma(V_t,t)}$.
\item $\Psi_{vv}(V_t,t)=\psi_{vv}(V_t,t)=\frac{\dif}{\dif v}\left[\frac{1}{\sigma(V_t,t)}\right]=-\frac{\sigma_v(V_t,t)}{\sigma^2(V_t,t)}=-\frac{1}{\sigma^2(V_t,t)}\cdot\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}$.
\item $\psi_t(V_t,t)=\frac{\dot{p}_t}{\sqrt{2\alpha\theta_t}(V_t+p_t)(1-V_t-p_t)}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\sqrt{2}(\alpha\theta_t)^{3/2}}$.
\item $\Psi_t(V_t,t)=\psi_t(V_t,t)-\psi_t(\epsilon,t)\Big|_{\epsilon=0}=\frac{\dot{p}_t}{\sqrt{2\alpha\theta_t(V_t+p_t)(1-V_t-p_t)}}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\sqrt{2}(\alpha\theta_t)^{3/2}}-\frac{\dot{p}_t}{\sqrt{2\alpha\theta_t(\alert{0}+p_t)(1\alert{-0}-p_t)}}-\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1\alert{-0}-p_t})}{\sqrt{2}(\alpha\theta_t)^{3/2}}=\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\alpha\theta_t}-\frac{\dot{p}_t}{\sqrt{(\alert{0}+p_t)(1\alert{-0}-p_t)}}-\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1\alert{-0}-p_t})}{\alpha\theta_t}\right)$.
\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{SDE for $Z_t=\Psi(V_t,t)$: ({\color{green}Verified with Mathematica})}

By It\^o's lemma:
\begin{equation*}
\dif Z_t=\left({\color{blue}\Psi_t}+\Psi_v\cdot f+\alert{\frac{1}{2}\Psi_{vv}\cdot\sigma^2}\right)\dif t+\Psi_v\cdot\sigma\dif W_t.
\end{equation*}
If we substitute the terms related with $\Psi(V_t,t)$:
\begin{equation*}
{\footnotesize
\begin{split}
\dif Z_t=&\Bigg[{\color{blue}\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\alpha\theta_t}-\frac{\dot{p}_t}{\sqrt{(p_t)(1-p_t)}}-\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-p_t})}{\alpha\theta_t}\right)}\\
&-\frac{\theta_tV_t}{\sqrt{2\alpha\theta_t(V_t+p_t)(1-V_t-p_t)}}\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}}\Bigg]\dif t+1\cdot \dif W_t.
\end{split}}
\end{equation*}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: ({\color{green}Verified with Mathematica})}

By It\^o's lemma, if $\psi(v,t)$ is $C^2([-p_t,1-p_t])$ for $v$ and $C^1([0,T])$ for $t$, then:
\begin{equation*}
\dif Z_t=\left({\color{blue}\psi_t}+\psi_v\cdot f+\alert{\frac{1}{2}\psi_{vv}\cdot\sigma^2}\right)\dif t+\psi_v\cdot\sigma\dif W_t.
\end{equation*}
If we substitute the terms related with $\psi(V_t,t)$:
\begin{equation*}
{\footnotesize
\begin{split}
\dif Z_t=&\Bigg[{\color{blue}\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\alpha\theta_t}\right)}\\
&-\frac{\theta_tV_t}{\sqrt{2\alpha\theta_t(V_t+p_t)(1-V_t-p_t)}}\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}}\Bigg]\dif t+1\cdot \dif W_t.
\end{split}}
\end{equation*}
{\footnotesize
Recall $\alert{Z_t=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-V_t-p_t}\right)}$. Then, we have the next identities: \textbf{1)} $\sqrt{1-V_t-p_t}=\sin\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)$, \textbf{2)} $1-V_t-p_t=\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)$, and \textbf{3)} $V_t+p_t=1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)$.}
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$:}

\begin{equation*}
{\scriptsize
\begin{split}
\dif Z_t=&\left[{\color{blue}\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{\left(1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)\left(\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}}+\frac{\dot{\theta}_t\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)}{\theta_t}\right)}\right.\\
&-\frac{\theta_t\left(1-p_t-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}{\sqrt{2\alpha\theta_t\left(1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)\left(\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}}\\
&\left.\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2\left(1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}{\sqrt{\left(1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)\left(\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}}}\right]\dif t+1\cdot \dif W_t.
\end{split}}
\end{equation*}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Range for $Z_t=\psi(V_t,t)$:}

We have that $Z_t=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-V_t-p_t}\right)=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-X_t}\right)$, where $X_t\in[0,1]$ almost sure. Then, we have that $Z_t\in\left[-\sqrt{\frac{2}{\alpha\theta_t}}\frac{\pi}{2},0\right]=\left[-\frac{\pi}{\sqrt{2\alpha\theta_t}},0\right]$, because $\arcsin\left([0,1]\right)=\left[0,\frac{\pi}{2}\right]$.\\
\quad\\
\graphicspath{{../../Mathematica_Files/}}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{Range_Z.pdf}
\caption{Plot of $Z_t$ as a function of $X_t$ from 0 to 1. We choose $\alpha=1/2$, and $\theta_t=1$. Notice that $Z_t(0)=-\frac{\pi}{\sqrt{2}}$, and $Z_t(1)=0$.}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$ with the c.o.v. $Y_t=Z_t\sqrt{\frac{\alpha\theta_t}{2}}$:}
We have that $Z_t\in\left[-\frac{\pi}{\sqrt{2\alpha\theta_t}},0\right]\iff Y_t\in\left[-\frac{\pi}{2},0\right]$.
\begin{equation*}
{\footnotesize
\begin{split}
\dif Z_t=&\left[{\color{blue}\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{\left(1-\sin^2\left(Y_t\right)\right)\left(\sin^2\left(Y_t\right)\right)}}-\frac{\dot{\theta}_tY_t}{\theta_t}\right)}\right.\\
&-\frac{\theta_t\left(1-p_t-\sin^2\left(Y_t\right)\right)}{\sqrt{2\alpha\theta_t\left(1-\sin^2\left(Y_t\right)\right)\left(\sin^2\left(Y_t\right)\right)}}\\
&\left.\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2\left(1-\sin^2\left(Y_t\right)\right)}{\sqrt{\left(1-\sin^2\left(Y_t\right)\right)\left(\sin^2\left(Y_t\right)\right)}}}\right]\dif t+1\cdot \dif W_t.
\end{split}}
\end{equation*}

\end{frame}

\setbeamercolor{background canvas}{bg=red!30}
\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: Singularity in $Z_t=-\frac{\pi}{\sqrt{2\alpha\theta_t}}$, and $Z_t=0$}

We call $f_Z(Z_t,t)$ to the drift of $Z_t$. We define $Y_t=Z_t\sqrt{\frac{\alpha\theta_t}{2}}$, notice that $Y_t(Z_t=0)=0$, and $Y_t\left(Z_t=-\frac{\pi}{\sqrt{2\alpha\theta_t}}\right)=-\frac{\pi}{2}$. Now, we define $\hat{f}_Z$ a simplified version of $f_Z$ which has the same limits in the spatial boundaries.\\
We have that:
\begin{equation*}
\hat{f}_Z(y,t)={\color{blue}\left[\frac{\dot{p}_t}{\sqrt{2\alpha\theta_t}}\right]\frac{1}{(1-\sin^2(y))\sin^2(y)}}.
\end{equation*}
We have the next limits for some fixed $t$:
$$\lim_{y\to0^-}\hat{f}_Z(y,t)=\lim_{y\to-\frac{\pi}{2}^+}\hat{f}_Z(y,t)=\infty\times\sign(\dot{p}_t).$$

\alert{This result is a bit scaring because the sing depends on $\dot{p}_t$ when the process $Y_t$ touch the boundaries, not for the forecast $p_t$. LIMITS MAY BE WRONG! CHECK WELL!}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{What about the forecast $p(t)$?}

\begin{columns}[c]

\column{.6\textwidth}
We do not have control about the input $p(t)$. However, as it is discrete, we can choose how to make it continuous.\\
\quad\\
If we have a measurement every $\Delta t$-intervals, and we realize linear interpolation, then $|\dot{p}|\leq\frac{1}{\Delta t}$ as $p(t)\in[0,1]$. In our concrete case we have that $\frac{1}{\Delta t}=144$.\\
Theoretically, $\dot{p}(t)$ is not defined at the measurement times, and it is constant in the time between consecutive measurements.\\
\quad\\
In the case of $\ddot{p}(t)$, theoretically it is zero a.e., and it has Dirac's deltas at the measurement times.

\column{.3\textwidth}
\includegraphics[width=0.9\columnwidth]{20200224_180726.jpg}

\end{columns}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{What about $\dot{\theta}_t$?}

\begin{equation*}
\dot{\theta}_t=\begin{cases}
\frac{\sign(\dot{p}_t)\ddot{p}_tp_t-|\dot{p}_t|\dot{p}_t}{p_t^2}\quad&\text{if}\quad|\dot{p}_t|>\theta_0p_t\ \text{\textbf{and}}\ p_t<\frac{1}{2}\\
\frac{\sign(\dot{p}_t)\ddot{p}_t(1-p_t)+|\dot{p}_t|\dot{p}_t}{(1-p_t)^2}\quad&\text{if}\quad|\dot{p}_t|>\theta_0(1-p_t)\ \text{\textbf{and}}\ p_t\geq\frac{1}{2}\\
0\quad&\text{otherwise}.
\end{cases}
\end{equation*}
\quad\\
\quad\\

\begin{columns}[c]

\column{.6\textwidth}
We need to take care of the extremes $p_t\approx0$ and $1-p_t\approx0$.\\
We will assume that always all the term involving $\ddot{p}_t$ is very small.

\column{.3\textwidth}
\includegraphics[width=0.9\columnwidth]{20200225_150346.jpg}

\end{columns}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{What about $\dot{\theta}_t$?}

We assume that $p_t$ is near the extremes, and then we do \textbf{not} have $\theta_t=\theta_0$. Also, we assume $\ddot{p}_t\approx0$ (because I do not know how to model it).

\begin{itemize}

\item $p_t<\frac{1}{2}$ and $|\dot{p}_t|>\theta_0p_t$: $\frac{\dot{\theta}_t}{\theta_t}\approx-\frac{|\dot{p}_t|\dot{p}_t}{p_t^2}\frac{p_t}{|\dot{p}_t|}=-\frac{\dot{p}_t}{p_t}$. Then, we have $\lim_{p_t\to0^+}\left[\frac{\dot{\theta}_t}{\theta_t}\right]\approx\lim_{p_t\to0^+}\left[-\frac{\dot{p}_t}{p_t}\right]=-\infty\times\sign(\dot{p}_t)$. In this situation, the drift for $Z_t$ tends to $-\infty\times\sign(\dot{p}_t)$.
\item $p_t\geq\frac{1}{2}$ and $|\dot{p}_t|>\theta_0(1-p_t)$: $\frac{\dot{\theta}_t}{\theta_t}\approx\frac{|\dot{p}_t|\dot{p}_t}{(1-p_t)^2}\frac{(1-p_t)}{|\dot{p}_t|}=\frac{\dot{p}_t}{(1-p_t)}$. Then, we have $\lim_{p_t\to1^-}\left[\frac{\dot{\theta}_t}{\theta_t}\right]\approx\lim_{p_t\to1^-}\left[\frac{\dot{p}_t}{(1-p_t)}\right]=\infty\times\sign(\dot{p}_t)$. In this situation, the drift for $Z_t$ tends to $\infty\times\sign(\dot{p}_t)$.

\end{itemize}
\quad\\
\alert{Maybe we can use a model where $\theta_t=\theta_0$ only in the diffusion. The SDE would remain between 0 and 1, and the Lamperti transform would be simpler.}

\end{frame}

%\setbeamercolor{background canvas}{bg=white!10}
%\begin{frame}\frametitle{Plotting the drift for $Z_t$: ($\theta_t$ and $\dot{\theta}_t$ with artificial definitions)}
%
%\graphicspath{{../../Mathematica_Files/}}
%
%\begin{table}[]
%\begin{tabular}{lll}
% \includegraphics[width=0.3\columnwidth]{drift_z_1.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_2.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_3.pdf} \\
% {\tiny$p_t=0,\alpha=0.1,\dot{p}_t=1,\theta_t=1,\dot{\theta}_t=0$} & {\tiny$p_t=0,\alpha=0.1,\dot{p}_t=1,\theta_t=1,\dot{\theta}_t=1000$} & {\tiny$p_t=1,\alpha=0.1,\dot{p}_t=-1,\theta_t=1,\dot{\theta}_t=0$} \\
% \includegraphics[width=0.3\columnwidth]{drift_z_4.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_5.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_6.pdf} \\
% {\tiny$p_t=1,\alpha=0.1,\dot{p}_t=-1,\theta_t=1,\dot{\theta}_t=1000$} & {\tiny$p_t=1/2,\alpha=0.1,\dot{p}_t=1,\theta_t=1,\dot{\theta}_t=0$} & {\tiny$p_t=1/2,\alpha=0.1,\dot{p}_t=-1,\theta_t=1,\dot{\theta}_t=0$}
%\end{tabular}
%\end{table}
%
%\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{$X_t$, $V_t$, $Z_t$, and $Y_t$:}

It is essential to understand what happens with the domain of each process to have a correct intuition about the SDEs.

\begin{enumerate}
\item $X_t\in\alert{[0},{\color{blue}1]}$.
\item $V_t\in\alert{[-p_t},{\color{blue}1-p_t]}$.
\item $Z_t\in\alert{\Big[-\frac{\pi}{\sqrt{2\alpha\theta_t}}},{\color{blue}0\Big]}$.
\item $Y_t\in{\color{red}\Big[-\frac{\pi}{2}},{\color{blue}0\Big]}$.
\end{enumerate}
Notice that none of the changes of variables inverters the domain (red corresponds to red, and blue to blue).

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Plotting the drift for $Z_t$: ($\theta_t$ and $\dot{\theta}_t$ with real definitions, and $\ddot{p}_t=0$)}

\graphicspath{{../../Mathematica_Files/}}

\begin{table}[]
\begin{tabular}{lll}
 \includegraphics[width=0.3\columnwidth]{drift_z_7.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_8.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_9.pdf} \\
 {\tiny$p_t=0.01,\alpha=0.1,\dot{p}_t=0.1$ (common case).} & {\tiny$p_t=0.01,\alpha=0.1,\dot{p}_t=-0.1$ (\alert{uncommon case}).} & {\tiny$p_t=0.99,\alpha=0.1,\dot{p}_t=0.1$ (\alert{uncommon case}).} \\
 \includegraphics[width=0.3\columnwidth]{drift_z_10.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_11.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_12.pdf} \\
 {\tiny$p_t=0.99,\alpha=0.1,\dot{p}_t=-0.1$ (common case).} & {\tiny$p_t=1/2,\alpha=0.1,\dot{p}_t=0.2$ (common case).} & {\tiny$p_t=1/2,\alpha=0.1,\dot{p}_t=-0.2$ (common case).}
\end{tabular}
\end{table}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Plotting the drift for $Z_t$: ($\theta_t$ and $\dot{\theta}_t$ with real definitions, and $\ddot{p}_t=0$)}

\graphicspath{{../../Mathematica_Files/}}

\begin{table}[]
\begin{tabular}{lll}
 \includegraphics[width=0.3\columnwidth]{drift_z_13.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_14.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_15.pdf} \\
 {\tiny$p_t=0.1,\alpha=0.1,\dot{p}_t=0.15$ (common case).} & {\tiny$p_t=0.1,\alpha=0.1,\dot{p}_t=-0.15$ (\alert{uncommon case}).} & {\tiny$p_t=0.9,\alpha=0.1,\dot{p}_t=0.15$ (\alert{uncommon case}).} \\
 \includegraphics[width=0.3\columnwidth]{drift_z_16.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_17.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_18.pdf} \\
 {\tiny$p_t=0.9,\alpha=0.1,\dot{p}_t=-0.15$ (common case).} & {\tiny$p_t=0.1,\alpha=0.1,\dot{p}_t=0.05$ (common case).} & {\tiny$p_t=0.9,\alpha=0.1,\dot{p}_t=-0.05$ (common case).}
\end{tabular}
\end{table}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Professor Kebaier's condition: (In this slide, we remove the time subindex)}

We assume that \textbf{1)} $0<\alpha<\frac{1}{2}$, and \textbf{2)} $\alpha\theta\leq\dot{p}+\theta p\leq(1-\alpha)\theta$.\\
\quad\\
From \textbf{2)}: $\frac{\alpha\theta-\dot{p}}{p}\leq\theta\leq\frac{\theta-\alpha\theta-\dot{p}}{p}$ (recall $p\in[0,1]$, but in this step we assume $p\neq0$). We well check the two inequalities ${\color{red}\frac{\alpha\theta-\dot{p}}{p}\leq\theta}$ and ${\color{blue}\theta\leq\frac{\theta-\alpha\theta-\dot{p}}{p}}$.\\
\quad\\
${\color{blue}\theta(1-p-\alpha)\geq\dot{p}}$ is implied by the more restrictive inequality ${\color{orange}\theta(1-p-\alpha)\geq|\dot{p}|}$. If we assume that $1-p-\alpha>0$ (or equivalently $p<1-\alpha$), we have the more restrictive inequality ${\color{orange}\theta\geq\frac{|\dot{p}|}{(1-p-\alpha)}}$ which implies the {\color{blue}blue one}.\\
\quad\\
\alert{$\theta(\alpha-p)\leq\dot{p}$} is equivalent to ${\color{violet}\theta\geq\frac{\dot{p}}{\alpha-p}}$ assuming that $\alpha-p<0$ (or $p>\alpha$). Now, {\color{violet}violet} is implied by the more restrictive inequality ${\color{brown}\theta\geq\left|\frac{\dot{p}}{\alpha-p}\right|=\frac{|\dot{p}|}{p-\alpha}}$.\\
\quad\\
Combining the two assumptions, we have that \textbf{2)} is true if $\alpha<p<1-\alpha$, and $\theta=\max\left(\theta_0,\frac{|\dot{p}|}{\min(p-\alpha,1-p-\alpha)}\right)$. For very small $\alpha$, we recuperate our classical condition.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Professor Kebaier's Lamperti SDE:}

If we fix $\theta_t=\theta_0$ in the diffusion in both SDEs (our original one and Kebaier's one), then assuming the new condition $\alpha<p<1-\alpha$, we have that both SDEs share the same Lamperti transform (up to the definition of $\theta_t$ in the drift).

\end{frame}

\setbeamercolor{background canvas}{bg=green!20}
\begin{frame}

{\Huge New Model}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{New model for the SDE: $\theta_t=\theta_0$ in the diffusion}

\begin{enumerate}

\item[$X_t$:] $\dif X_t=\left(\dot p_t-\theta_t(X_t-p_t)\right)\dif t+\sqrt{2\alert{\theta_0}\alpha X_t(1-X_t)}\dif W_t$
\item[$V_t$:] $\dif V_t=-\theta_tV_t\dif t+\sqrt{2\alert{\theta_0}\alpha(V_t+p_t)(1-V_t-p_t)}\dif W_t$

\end{enumerate}
Lamperti transform for $V_t$:
\begin{equation*}
\begin{split}
\psi(V_t,t)=\int\frac{1}{\sqrt{2\alert{\theta_0}\alpha(u+p_t)(1-u-p_t)}}\dif u\Bigg|_{u=V_t}&=-\sqrt{\frac{2}{\alpha\alert{\theta_0}}}\arcsin\left(\sqrt{1-V_t-p_t}\right),\\
&=-\sqrt{\frac{2}{\alpha\alert{\theta_0}}}\arcsin\left(\sqrt{1-X_t}\right).
\end{split}
\end{equation*}

We can see that for every $t=t^*$, the primitive function of $\frac{1}{\sigma(v,t^*)}$ is well defined for all $v\in\left[-p(t^*),1-p(t^*)\right]\subset[-1,1]$ (recall $v=x-p_t$, and $x\in[0,1]$).

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Identities for the Lamperti transform of $V_t$:}

\begin{itemize}
\item $\psi(V_t,t)=-\sqrt{\frac{2}{\alpha\alert{\theta_0}}}\arcsin(\sqrt{1-V_t-p_t})$.
\item $\psi_v(V_t,t)=\frac{1}{\sigma(V_t,t)}$.
\item $\psi_{vv}(V_t,t)=\frac{\dif}{\dif v}\left[\frac{1}{\sigma(V_t,t)}\right]=-\frac{\sigma_v(V_t,t)}{\sigma^2(V_t,t)}=-\frac{1}{\sigma^2(V_t,t)}\cdot\sqrt{\frac{\alpha\alert{\theta_0}}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}$.
\item $\psi_t(V_t,t)=\frac{\dot{p}_t}{\sqrt{2\alpha\alert{\theta_0}(V_t+p_t)(1-V_t-p_t)}}$.
\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: ({\color{green}Verified with Mathematica})}

By It\^o's lemma, if $\psi(v,t)$ is $C^2([-p_t,1-p_t])$ for $v$ and $C^1([0,T])$ for $t$, then:
\begin{equation*}
\dif Z_t=\left({\color{blue}\psi_t}+\psi_v\cdot f+\alert{\frac{1}{2}\psi_{vv}\cdot\sigma^2}\right)\dif t+\psi_v\cdot\sigma\dif W_t.
\end{equation*}
If we substitute the terms related with $\psi(V_t,t)$:
\begin{equation*}
{\footnotesize
\begin{split}
\dif Z_t=&\Bigg[{\color{blue}\frac{\dot{p}_t}{\sqrt{2\alpha\theta_0(V_t+p_t)(1-V_t-p_t)}}}\\
&-\frac{\theta_tV_t}{\sqrt{2\alpha\theta_0(V_t+p_t)(1-V_t-p_t)}}\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_0}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}}\Bigg]\dif t+1\cdot \dif W_t.
\end{split}}
\end{equation*}
Recall $\alert{Z_t=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-V_t-p_t}\right)}$, where $Z_t\in\Big[-\frac{\pi}{\sqrt{2\alpha\theta_t}},{\color{black}0\Big]}$.
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: ({\color{green}Computed with Mathematica})}

\begin{equation*}
\dif Z_t=\underbrace{\left[\frac{\alpha\theta_0\cos(Z_t\sqrt{2\alpha\theta_0})-\theta_t\cos(Z_t\sqrt{2\alpha\theta_0})+2\theta_tp_t+2\dot{p}_t-\theta_t}{\sqrt{\alpha\theta_0}\sqrt{1-\cos(2Z_t\sqrt{2\alpha\theta_0})}}\right]}_{f(Z_t,t)}\dif t+1\cdot\dif W_t.
\end{equation*}\\
\begin{equation*}
\lim_{z\to0^-}f(z,t)=\infty\times\left[\frac{\sign\left(2\theta_tp_t+2\dot{p}_t+\alpha\theta_0-2\theta_t\right)}{\sign(\alpha)\sign(\theta_0)}\right].
\end{equation*}
\begin{equation*}
\lim_{z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+}f(z,t)=\infty\times\left[\frac{\sign\left(2\theta_tp_t+2\dot{p}_t-\alpha\theta_0\right)}{\sign(\alpha)\sign(\theta_0)}\right].
\end{equation*}
We want to find the correct conditions for $\theta_t$.\\
\quad\\
{\small To simplify the SDE, Mathematica has used: $\sin^2(x)-\sin^4(x)=\sin^2(x)\cos^2(x)=\frac{1}{4}\sin^2(2x)=\frac{1}{8}(1-\cos(4x))$.}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Limit when $z\to0^-$:}\label{C1}

Recall we have a bijective mapping $Z_t({\color{blue}[0},\alert{1]})={\color{blue}\Big[\frac{-\pi}{\sqrt{2\alpha\theta_0}}},\alert{0\Big]}$.\\
\quad\\
We want $\alpha\theta_0-2\theta_t+2\theta_tp_t+2\dot{p}_t\leq0$ so we do not scape from $x=1$ to $x>1$. Then:
\begin{itemize}

\item If $p_t<1$, we have that ${\color{orange}\theta_t\geq\frac{\alpha\theta_0+2\dot{p}_t}{2(1-p_t)}}$.
\item If $p_t=1$, $\lim_{z\to0^-}f(z,t)=\alpha\theta_0+2\dot{p}_t$.\\
\alert{Then, if $\alpha\theta_0>|2\dot{p}_t|$, we scape from $x=1$ to $x>1$.}

\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Limit when $z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+$:}\label{C2}

Recall we have a bijective mapping $Z_t({\color{blue}[0},\alert{1]})={\color{blue}\Big[\frac{-\pi}{\sqrt{2\alpha\theta_0}}},\alert{0\Big]}$.\\
\quad\\
We want $2\theta_tp_t+2\dot{p}_t-\alpha\theta_0\geq0$ so we do not scape from $x=0$ to $x<0$. Then:
\begin{itemize}

\item If $p_t>0$, we have that ${\color{orange}\theta_t\geq\frac{\alpha\theta_0-2\dot{p}_t}{2p_t}}$.
\item If $p_t=0$, $\lim_{z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+}f(z,t)=2\dot{p}_t-\alpha\theta_0$.\\
\alert{Then, if $\alpha\theta_0>|2\dot{p}_t|$, we scape from $x=0$ to $x<0$.}

\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Controlled drift:}

From both {\color{orange}orange} conditions in slides (\ref{C1}) and (\ref{C2}), we create a more restrictive condition:
\begin{equation*}
\max\left({\color{orange}\frac{\alpha\theta_0+2\dot{p}_t}{2(1-p_t)}},{\color{orange}\frac{\alpha\theta_0-2\dot{p}_t}{2p_t}}\right)\leq\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}.
\end{equation*}
Then, we choose
\begin{equation}
\theta_t=\max\left(\theta_0,\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}\right).
\label{NC}
\end{equation}
\alert{Notice that we still need $\alpha\theta_0>|2\dot{p}_t|$ when $\{x=0,p=0\}$ or $\{x=1,p=1\}$.} As we no control over this condition, it is enough to ensure that we never reach these pairs $\{x,p_t\}$.\\
\quad\\
Recall that in the paper, we start by choosing $\theta_t=\max\left(\theta_0,\frac{|\dot{p}_t|}{\min(1-p_t,p_t)}\right)$. Our new condition (\ref{NC}) is mroe restrictive.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Conditions summary:}

\begin{itemize}

\item Initial condition: $\theta_t^{initial}=\max\left(\theta_0,\frac{|\dot{p}_t|}{\min(1-p_t,p_t)}\right)$
\item New condition from Lamperti: $\theta_t^{lamperti}=\max\left(\theta_0,\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}\right)$. Also, we need that $\alpha\theta_0>|2\dot{p}_t|$ when $\{x=0,p=0\}$ or $\{x=1,p=1\}$. Notice $\theta_t^{initial}\leq\theta_t^{lamperti}$.
\item Professor Kebaier's condition: $0<\alpha<1/2$, $\alpha<p_t<1-\alpha$, and $\theta_t^{kebaier}=\max\left(\theta_0,\frac{|\dot{p}|}{\min(p-\alpha,1-p-\alpha)}\right)$.

\end{itemize}
Now, given $p_t<1/2$, we have that $\theta_t^{lamperti}=\theta_t^{kebaier}$ if $\theta_0=\frac{|2\dot{p}_t|}{p_t-\alpha}$ (assuming that in both cases the maximum is not $\theta_0$). Then, how much each one is restrictive depends on $|\dot{p}_t|$ and $p_t$.\\
Conditions $0<\alpha<1/2$ and $\alpha<p_t<1-\alpha$ implies that we never have $\{x=0,p=0\}$ or $\{x=1,p=1\}$

\end{frame}

\end{document}

### 2020-08-05 Reports/20200319 - Time delta/20200319 - Time delta.tex
Updated main files

\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{commath}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{siunitx}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}
\DeclareMathOperator{\sign}{sign}

\title{Time delta ($\delta$)}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\begin{frame}
\titlepage
{\tiny Note: We compute the following results using \textbf{initial\_time.m}.}
\end{frame}

%\setbeamercolor{background canvas}{bg=white!10}
%\begin{frame}\frametitle{Extra: Interesting data processing}
%
%\begin{figure}[ht!]
%\centering
%\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/mean_error.eps}\quad\quad
%\includegraphics[width=0.4\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/mean_abs_error.eps}
%\end{figure}
%{\small What we are seeing is the \textbf{mean error} and \textbf{mean absolute error} as a function of the forecast. This is, for each interval with length 0.1 (i.e., [0,0.1), [0.1,0.2), etc.), we average all the errors corresponding to measurement where the forecast was in that intervals, and after we average over the number of elements in each interval. \alert{In some future, we can use this information to construct an even more realistic model.}}
%
%\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{\alert{\textbf{Copied from the paper (19/03/20):}}}

We can estimate $\delta$ solving the problem

\begin{equation*}
\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta).
\end{equation*}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{\alert{\textbf{Copied from MATLAB's slides (19/03/20):}}}

We have that, for almost all days, at time $t=t_0$, $X(t_0)\neq p(t_0)$ and then $V(t_0)\neq0$. However, by forecast construction, there should exist a time $t_{-\delta}<t_0$ such that $V(t_{-\delta})=0$.\\
\quad\\
We extrapolate linearly $p(t)$ so we can evaluate $p(t_{-\delta})$, and assume that $V(t_{-\delta})=0$. Then, for each day $j$, we have an initial transition $(V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta)$. We assume again that it is Beta and apply the same moment matching as for the rest of transitions. With our initial guess for $\bm{\theta}$, we can construct our initial guess for $\delta$ solving the problem

\begin{equation*}
\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
\label{likelihood_delta}
\end{equation*}

\alert{We got $\delta\approx\SI{80}{\min}$.}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Step by step: (WLOG we can use $t_0=0$ and $t_{-\delta}=-\delta$)}

We are imposing that $V_{j,t_{-\delta}}=0$ for all $j\in\{1,\dots,M\}$, there $t_{-\delta}=t_0-\delta$. Then, for each path $j$, we have that the first moment $m_1(t)=0$ for all $t\in[t_{-\delta},t_0]$.\\
\quad\\
The second moment is given by
\begin{equation}
\begin{cases}
\frac{\dif m_2}{\dif t}&=-\underbrace{2\theta_t(1+\alpha)}_{k_1(t)}m_2+\underbrace{2\theta_t\alpha}_{k_2(t)} \underbrace{p_t(1-p_t)}_{f(t)}\\
m_2(t_{-\delta})&=0.
\end{cases}
\label{S1}
\end{equation}
Then, as $m_1(t_0)=0$, the R.V. $V_{j,t_0}|(V_{j,t_{del
}}=0)$ can be extracted from
\begin{equation*}
2\times\text{Beta}\left(\frac{1-m_2(t_0)}{2m_2(t_0)},\frac{1-m_2(t_0)}{2m_2(t_0)}\right)-1,
\end{equation*}
which has mean and variance
\begin{equation*}
\mu=0,\quad\sigma^2=m_2(t_0).
\end{equation*}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Step by step:}

If we assume that $\theta_t=\theta_0$ in $[t_{-\delta},t_0]$, the system (\ref{S1}) has solution
\begin{equation*}
m_2({t})=e^{-k_1{t}}\int_{t_{-\delta}}^{{t}}k_2e^{k_1s}f(s)\dif s.
\end{equation*}
As $p_t(1-p_t)\leq1/4$ in $[t_{-\delta},t_0]$, we have the bound
\begin{equation*}
m_2({t})\leq\frac{\frac{k_2}{4}\int_{t_{-\delta}}^{{t}}e^{k_1s}\dif s}{e^{k_1{t}}}=\frac{k_2}{4k_1}\left(1-\frac{e^{k_1t_{-\delta}}}{e^{k_1{t}}}\right)\leq\frac{1}{4}\left(1-e^{k_1(t_{-\delta}-t)}\right).
\end{equation*}
Then, $\lim_{t_{-\delta}\to-\infty}m_2(t_0)\leq 1/4\implies\sigma^2\leq1/4$.\\
\quad\\
{\footnotesize
Then, if we need more variance to model the initial transition, we can not use this model. Noticed that we assumed $\theta_t=\theta_0$ in $[t_{-\delta},t_0]$, this is not true in general as $p_{t_{-\delta}}$ can be very near the boundaries $\epsilon$ and $1-\epsilon$. However, even with the assumption, to have limit variance is a problem as for some set of data the assumption can hold. Still, if the initial error is so large, we would not be able to model it correctly with limited variance.}
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Step by step: We remove points with $|V_{j,t_0}|>\eta=0.1$}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/allLH_0.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/allLH_1.eps}
\end{figure}
{\small
Here we can see all the likelihoods for each initial transition when $\delta=\text{*one day*}$, overlapped with histograms of the initial error. On the left, we use all the initial errors, and clearly, the distribution that fits that histogram needs more variance. On the right, we removed the points with more error, and we can see that we need $\delta<\text{*one day*}$.}
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Step by step: Explanation Problem-Solution}

Basically, what happens is that the variance in the initial point grows with $\delta$ (the more in the past we *start*, the more variance we have at time $t=0$ or $t_0$).\\
\quad\\
The problem is that, as $\delta\uparrow$, we have that $m_2(t_0)\uparrow$. At the same time, as $m_1(t)=0$ (because we fix $V_{j,t_{-\delta}}=0$ for all $j\in\{1,\dots,M\}$), we can prove that $m_2(t_0)\leq1/4$ for all possible $\delta>0$.\\
\quad\\
Now, we have that $\xi_1=\xi_2$ in the Beta distribution, and then $\sigma^2=m_2(t_0)$ for the distribution of $V_{j,t_{-\delta}}$. Then, the variance is bounded by 1/4. This means that, if the set of errors at the initial time has a larger variance, we will not be able to reach the correct Beta distribution using the moments matching.\\
\quad\\
How we solve this problem? Two options: Change model to one with more possible variance, or remove the data with substantial error. {\color{orange}We remove all data s.t. $|V_{j,t_0}|>\eta$ for some $\eta>0$.} To create this new dataset we use \textbf{new\_batch\_fixed\_removed\_samples.m}.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Step by step:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/LL_0.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/LL_1.eps}
\end{figure}
On the left, negative log-likelihood using all the data. On the right, using only the {\color{orange}*corrected data* with $\eta=0.1$}. In the next slide we will see a *zoom* of the right plot.
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Step by step:}

\begin{columns}[c]

\column{.5\textwidth}
We can observe that the minimum, for $\eta=0.1$, is in {\color{orange}$\delta\approx0.083\approx\SI{120}{\min}=\SI{2}{\hour}$}.\\
\quad\\
If we choose (let say...) $\eta=0.08$, we obtain that $\delta\approx\SI{90}{\min}$.

\column{.5\textwidth}
\includegraphics[width=1\textwidth]{../../MATLAB_Files/Results/delta/min.eps}

\end{columns}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Step by step: Averaged $m_2(t_0)$ over all the the used samples}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/M2_0.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/M2_1.eps}
\end{figure}
On the left, all initial points. On the right, only the {\color{orange}*corrected data* with $\eta=0.1$}.
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Step by step: Averaged $\sigma^2(t_0)$ over all the used samples}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/Sig_0.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/Sig_1.eps}
\end{figure}
On the left, all initial points. On the right, only the {\color{orange}*corrected data* with $\eta=0.1$}.
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Some remarks:}

\begin{itemize}

\item We showed plots with $\eta=0.1$. Smaller values also work, but we want to modify the data as few as possible. \alert{Can we plot $\delta$ w.r.t. $\eta$? See next slide.}
\item $1/4$ is a very large upper bound, as we assumed $p_t(1-p(t))=1/4$ for all time. This is the reason why the plots show values of variance smaller by orders of magnitude.
\item By construction of our model, if $m_1(t_0)=0$, then $\xi_1=\xi_2$. And then, $\sigma^2=m_2(t_0)$.
\item We bounded the variance using that $m_1(t)=0$. With no this assumption, maybe we can reach any value of variance.

\end{itemize}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{$\delta$ over $\eta$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/eta.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/delta/eta_min.eps}
\end{figure}
{\color{orange}We choose $\eta=0.15$ which leads to $\delta=\SI{330}{\min}=\SI{5.5}{\hour}$.} \alert{However, this plot is highly dependent on $\alpha$ and $\theta_0$. Then, our selection of $\delta$ may change before and after finding the optimal parameters.}
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{$\delta$ over $\eta$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../../MATLAB_Files/Results/delta/eta_min_ini.eps}\quad\quad
\includegraphics[width=0.4\textwidth]{../../MATLAB_Files/Results/delta/eta_min_opt.eps}
\end{figure}
On the left, we use the initial $(\theta_0,\alpha)$ ($\alpha\theta_0=0.1$) and we get $\delta=\SI{220}{\min}$.\\
On the right, we use the optimal ones. As the optimal product $\alpha\theta_0$ ($\alpha\theta_0=0.08$) is smaller than the initial one, we need a larger $\delta$ to match the variance of the initial error, or to remove some data. If we remove up to $\eta=0.1$, we get $\delta=\SI{220}{\min}$.
\end{frame}

\end{document}

### 2020-08-05 Reports/20200330 - Histograms/20200330 - Histograms.tex
Updated main files

--- 2020-08-05 Reports/20200220 - Lamperi for X and V/20200220 - Lamperi for X and V.tex
@@
 
-\title{Lamperti Transform for the processes X and V}
+\title{Data Histograms}
 \subtitle{Renzo Miguel Caballero Rosas}
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{SDE for $X_t$:}
+\begin{frame}\frametitle{Briefly description}
 
-$\dif X_t=\left(\dot p_t-\theta_t(X_t-p_t)\right)\dif t+\sqrt{2\theta_t\alpha X_t(1-X_t)}\dif W_t\implies$
-\begin{equation*}
-\psi(X_t,t)=\int\frac{1}{\sqrt{2\theta_t\alpha u(1-u)}}\dif u\Bigg|_{u=X_t}=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-X_t}\right).
-\end{equation*}
+In the following slides, we will show histograms for the error ($V_{t_i}=X_{t_i}-p_{i_i}$), and the Lamperti transform ($Z_{t_i}=\psi(V_{t_i})$).
+For each one, we will show the transitions and the real measurements.\\
+\quad\\
+Also, for each histogram, we will find its empirical mean and variance, and approximate it with a Gaussian distribution.
 
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{SDE for $V_t$:}
+\begin{frame}\frametitle{Error transitions and Lamperti transitions}
 
-$\dif V_t=\underbrace{-\theta_tV_t}_{f(V_t,t)}\dif t+\underbrace{\sqrt{2\theta_t\alpha(V_t+p_t)(1-V_t-p_t)}}_{\sigma(V_t,t)}\dif W_t\implies$
-\begin{equation*}
-\psi(V_t,t)=\int\frac{1}{\sqrt{2\theta_t\alpha(u+p_t)(1-u-p_t)}}\dif u\Bigg|_{u=V_t}=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-V_t-p_t}\right).
-\end{equation*}
-We can see that for every $t=t^*$, the primitive function of $\frac{1}{\sigma(v,t^*)}$ is well defined for all $v\in\left[-p(t^*),1-p(t^*)\right]\subset[-1,1]$ (recall $V_t=X_t-p_t$, and $x\in[0,1]$).
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{SDE for $V_t$:}
-
-We define $\Psi(V_t,t)=\int_{\epsilon}^u\frac{1}{\sigma(u,t)}\dif u\Big|_{u=V_t}$ where $\epsilon$ is in the space of $V_t$ (which depends on $p_t$).\\
-\quad\\
-We have that $V_t=X_t-p_t\iff V_t+p_t=X_t\implies0\leq V_t+p_t\leq1\iff-p_t\leq V_t\leq1-p_t$.
-Then, for each $t=t^*$, the space of the process is $[-p_{t^*},1-p_{t^*}]$.
-Now, notice that for all $p_{t^*}\in[0,1]$, we have that $q\in[-p_{t^*},1-p_{t^*}]$ if and only if $q=0$.\\
-\quad\\
-We conclude that if we want a fix value for $\epsilon$, necessarily we need to choose $\epsilon=0$.\\
-\quad\\
-We have that $\psi_v(V_t,t)=\Psi_v(V_t,t)$. However, $\psi_t(V_t,t)=\Psi_t(V_t,t)$ is in general no true, and $\Psi_t(V_t,t)$ has a more complicate expression.\\
-\quad\\
-If we choose $\epsilon=0$, we have that $\Psi_t(V_t,t)=\psi_t(V_t,t)+\frac{\dif}{\dif t}\int\frac{\dif u}{\sigma(u,t)}\Big|_{u=\epsilon=0}$.
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{SDE for $V_t$:}
-
-\begin{itemize}
-\item $\Psi(V_t,t)=\psi(V_t,t)-\psi(\epsilon,t)\Big|_{\epsilon=0}=\sqrt{\frac{2}{\alpha\theta_t}}\left[\arcsin(\sqrt{1-\epsilon-p_t})-\arcsin(\sqrt{1-V_t-p_t})\right]\Big|_{\epsilon=0}=\sqrt{\frac{2}{\alpha\theta_t}}\left[\arcsin(\sqrt{1-p_t})-\arcsin(\sqrt{1-V_t-p_t})\right]$.
-\item $\Psi_v(V_t,t)=\psi_v(V_t,t)=\frac{1}{\sigma(V_t,t)}$.
-\item $\Psi_{vv}(V_t,t)=\psi_{vv}(V_t,t)=\frac{\dif}{\dif v}\left[\frac{1}{\sigma(V_t,t)}\right]=-\frac{\sigma_v(V_t,t)}{\sigma^2(V_t,t)}=-\frac{1}{\sigma^2(V_t,t)}\cdot\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}$.
-\item $\psi_t(V_t,t)=\frac{\dot{p}_t}{\sqrt{2\alpha\theta_t}(V_t+p_t)(1-V_t-p_t)}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\sqrt{2}(\alpha\theta_t)^{3/2}}$.
-\item $\Psi_t(V_t,t)=\psi_t(V_t,t)-\psi_t(\epsilon,t)\Big|_{\epsilon=0}=\frac{\dot{p}_t}{\sqrt{2\alpha\theta_t(V_t+p_t)(1-V_t-p_t)}}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\sqrt{2}(\alpha\theta_t)^{3/2}}-\frac{\dot{p}_t}{\sqrt{2\alpha\theta_t(\alert{0}+p_t)(1\alert{-0}-p_t)}}-\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1\alert{-0}-p_t})}{\sqrt{2}(\alpha\theta_t)^{3/2}}=\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\alpha\theta_t}-\frac{\dot{p}_t}{\sqrt{(\alert{0}+p_t)(1\alert{-0}-p_t)}}-\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1\alert{-0}-p_t})}{\alpha\theta_t}\right)$.
-\end{itemize}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!20}
-\begin{frame}\frametitle{SDE for $Z_t=\Psi(V_t,t)$: ({\color{green}Verified with Mathematica})}
-
-By It\^o's lemma:
-\begin{equation*}
-\dif Z_t=\left({\color{blue}\Psi_t}+\Psi_v\cdot f+\alert{\frac{1}{2}\Psi_{vv}\cdot\sigma^2}\right)\dif t+\Psi_v\cdot\sigma\dif W_t.
-\end{equation*}
-If we substitute the terms related with $\Psi(V_t,t)$:
-\begin{equation*}
-{\footnotesize
-\begin{split}
-\dif Z_t=&\Bigg[{\color{blue}\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\alpha\theta_t}-\frac{\dot{p}_t}{\sqrt{(p_t)(1-p_t)}}-\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-p_t})}{\alpha\theta_t}\right)}\\
-&-\frac{\theta_tV_t}{\sqrt{2\alpha\theta_t(V_t+p_t)(1-V_t-p_t)}}\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}}\Bigg]\dif t+1\cdot \dif W_t.
-\end{split}}
-\end{equation*}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: ({\color{green}Verified with Mathematica})}
-
-By It\^o's lemma, if $\psi(v,t)$ is $C^2([-p_t,1-p_t])$ for $v$ and $C^1([0,T])$ for $t$, then:
-\begin{equation*}
-\dif Z_t=\left({\color{blue}\psi_t}+\psi_v\cdot f+\alert{\frac{1}{2}\psi_{vv}\cdot\sigma^2}\right)\dif t+\psi_v\cdot\sigma\dif W_t.
-\end{equation*}
-If we substitute the terms related with $\psi(V_t,t)$:
-\begin{equation*}
-{\footnotesize
-\begin{split}
-\dif Z_t=&\Bigg[{\color{blue}\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}+\frac{\alpha\dot{\theta}_t\arcsin(\sqrt{1-V_t-p_t})}{\alpha\theta_t}\right)}\\
-&-\frac{\theta_tV_t}{\sqrt{2\alpha\theta_t(V_t+p_t)(1-V_t-p_t)}}\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}}\Bigg]\dif t+1\cdot \dif W_t.
-\end{split}}
-\end{equation*}
-{\footnotesize
-Recall $\alert{Z_t=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-V_t-p_t}\right)}$.
-Then, we have the next identities: \textbf{1)} $\sqrt{1-V_t-p_t}=\sin\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)$, \textbf{2)} $1-V_t-p_t=\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)$, and \textbf{3)} $V_t+p_t=1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)$.}
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$:}
-
-\begin{equation*}
-{\scriptsize
-\begin{split}
-\dif Z_t=&\left[{\color{blue}\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{\left(1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)\left(\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}}+\frac{\dot{\theta}_t\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)}{\theta_t}\right)}\right.\\
-&-\frac{\theta_t\left(1-p_t-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}{\sqrt{2\alpha\theta_t\left(1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)\left(\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}}\\
-&\left.\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2\left(1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}{\sqrt{\left(1-\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)\left(\sin^2\left(-Z_t\sqrt{\frac{\alpha\theta_t}{2}}\right)\right)}}}\right]\dif t+1\cdot \dif W_t.
-\end{split}}
-\end{equation*}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Range for $Z_t=\psi(V_t,t)$:}
-
-We have that $Z_t=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-V_t-p_t}\right)=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-X_t}\right)$, where $X_t\in[0,1]$ almost sure.
-Then, we have that $Z_t\in\left[-\sqrt{\frac{2}{\alpha\theta_t}}\frac{\pi}{2},0\right]=\left[-\frac{\pi}{\sqrt{2\alpha\theta_t}},0\right]$, because $\arcsin\left([0,1]\right)=\left[0,\frac{\pi}{2}\right]$.\\
-\quad\\
-\graphicspath{{../../Mathematica_Files/}}
 \begin{figure}[ht!]
 \centering
-\includegraphics[width=0.3\textwidth]{Range_Z.pdf}
-\caption{Plot of $Z_t$ as a function of $X_t$ from 0 to 1. We choose $\alpha=1/2$, and $\theta_t=1$. Notice that $Z_t(0)=-\frac{\pi}{\sqrt{2}}$, and $Z_t(1)=0$.}
+\includegraphics[width=0.75\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/Gauss_Approx.eps}
 \end{figure}
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$ with the c.o.v. $Y_t=Z_t\sqrt{\frac{\alpha\theta_t}{2}}$:}
-We have that $Z_t\in\left[-\frac{\pi}{\sqrt{2\alpha\theta_t}},0\right]\iff Y_t\in\left[-\frac{\pi}{2},0\right]$.
-\begin{equation*}
-{\footnotesize
-\begin{split}
-\dif Z_t=&\left[{\color{blue}\frac{1}{\sqrt{2\alpha\theta_t}}\left(\frac{\dot{p}_t}{\sqrt{\left(1-\sin^2\left(Y_t\right)\right)\left(\sin^2\left(Y_t\right)\right)}}-\frac{\dot{\theta}_tY_t}{\theta_t}\right)}\right.\\
-&-\frac{\theta_t\left(1-p_t-\sin^2\left(Y_t\right)\right)}{\sqrt{2\alpha\theta_t\left(1-\sin^2\left(Y_t\right)\right)\left(\sin^2\left(Y_t\right)\right)}}\\
-&\left.\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_t}{2}}\frac{1-2\left(1-\sin^2\left(Y_t\right)\right)}{\sqrt{\left(1-\sin^2\left(Y_t\right)\right)\left(\sin^2\left(Y_t\right)\right)}}}\right]\dif t+1\cdot \dif W_t.
-\end{split}}
-\end{equation*}
+\begin{frame}\frametitle{Error transitions and Lamperti transitions}
 
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=red!30}
-\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: Singularity in $Z_t=-\frac{\pi}{\sqrt{2\alpha\theta_t}}$, and $Z_t=0$}
-
-We call $f_Z(Z_t,t)$ to the drift of $Z_t$.
-We define $Y_t=Z_t\sqrt{\frac{\alpha\theta_t}{2}}$, notice that $Y_t(Z_t=0)=0$, and $Y_t\left(Z_t=-\frac{\pi}{\sqrt{2\alpha\theta_t}}\right)=-\frac{\pi}{2}$.
-Now, we define $\hat{f}_Z$ a simplified version of $f_Z$ which has the same limits in the spatial boundaries.\\
-We have that:
-\begin{equation*}
-\hat{f}_Z(y,t)={\color{blue}\left[\frac{\dot{p}_t}{\sqrt{2\alpha\theta_t}}\right]\frac{1}{(1-\sin^2(y))\sin^2(y)}}.
-\end{equation*}
-We have the next limits for some fixed $t$:
-$$\lim_{y\to0^-}\hat{f}_Z(y,t)=\lim_{y\to-\frac{\pi}{2}^+}\hat{f}_Z(y,t)=\infty\times\sign(\dot{p}_t).$$
-
-\alert{This result is a bit scaring because the sing depends on $\dot{p}_t$ when the process $Y_t$ touch the boundaries, not for the forecast $p_t$. LIMITS MAY BE WRONG! CHECK WELL!}
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.48\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/Gauss_Approx_Err.eps}\quad
+\includegraphics[width=0.48\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/Gauss_Approx_Lam.eps}
+\end{figure}
 
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{What about the forecast $p(t)$?}
+\begin{frame}\frametitle{Error measurements and Lamperti measurements}
 
-\begin{columns}[c]
-
-\column{.6\textwidth}
-We do not have control about the input $p(t)$. However, as it is discrete, we can choose how to make it continuous.\\
-\quad\\
-If we have a measurement every $\Delta t$-intervals, and we realize linear interpolation, then $|\dot{p}|\leq\frac{1}{\Delta t}$ as $p(t)\in[0,1]$.
-In our concrete case we have that $\frac{1}{\Delta t}=144$.\\
-Theoretically, $\dot{p}(t)$ is not defined at the measurement times, and it is constant in the time between consecutive measurements.\\
-\quad\\
-In the case of $\ddot{p}(t)$, theoretically it is zero a.e., and it has Dirac's deltas at the measurement times.
-
-\column{.3\textwidth}
-\includegraphics[width=0.9\columnwidth]{20200224_180726.jpg}
-
-\end{columns}
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.75\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/Gauss_Approx_Measurements.eps}
+\end{figure}
 
@@
 \setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{What about $\dot{\theta}_t$?}
+\begin{frame}\frametitle{Error measurements and Lamperti measurements}
 
-\begin{equation*}
-\dot{\theta}_t=\begin{cases}
-\frac{\sign(\dot{p}_t)\ddot{p}_tp_t-|\dot{p}_t|\dot{p}_t}{p_t^2}\quad&\text{if}\quad|\dot{p}_t|>\theta_0p_t\ \text{\textbf{and}}\ p_t<\frac{1}{2}\\
-\frac{\sign(\dot{p}_t)\ddot{p}_t(1-p_t)+|\dot{p}_t|\dot{p}_t}{(1-p_t)^2}\quad&\text{if}\quad|\dot{p}_t|>\theta_0(1-p_t)\ \text{\textbf{and}}\ p_t\geq\frac{1}{2}\\
-0\quad&\text{otherwise}.
-\end{cases}
-\end{equation*}
-\quad\\
-\quad\\
-
-\begin{columns}[c]
-
-\column{.6\textwidth}
-We need to take care of the extremes $p_t\approx0$ and $1-p_t\approx0$.\\
-We will assume that always all the term involving $\ddot{p}_t$ is very small.
-
-\column{.3\textwidth}
-\includegraphics[width=0.9\columnwidth]{20200225_150346.jpg}
-
-\end{columns}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{What about $\dot{\theta}_t$?}
-
-We assume that $p_t$ is near the extremes, and then we do \textbf{not} have $\theta_t=\theta_0$. Also, we assume $\ddot{p}_t\approx0$ (because I do not know how to model it).
-
-\begin{itemize}
-
-\item $p_t<\frac{1}{2}$ and $|\dot{p}_t|>\theta_0p_t$: $\frac{\dot{\theta}_t}{\theta_t}\approx-\frac{|\dot{p}_t|\dot{p}_t}{p_t^2}\frac{p_t}{|\dot{p}_t|}=-\frac{\dot{p}_t}{p_t}$.
-Then, we have $\lim_{p_t\to0^+}\left[\frac{\dot{\theta}_t}{\theta_t}\right]\approx\lim_{p_t\to0^+}\left[-\frac{\dot{p}_t}{p_t}\right]=-\infty\times\sign(\dot{p}_t)$.
-In this situation, the drift for $Z_t$ tends to $-\infty\times\sign(\dot{p}_t)$.
-\item $p_t\geq\frac{1}{2}$ and $|\dot{p}_t|>\theta_0(1-p_t)$: $\frac{\dot{\theta}_t}{\theta_t}\approx\frac{|\dot{p}_t|\dot{p}_t}{(1-p_t)^2}\frac{(1-p_t)}{|\dot{p}_t|}=\frac{\dot{p}_t}{(1-p_t)}$.
-Then, we have $\lim_{p_t\to1^-}\left[\frac{\dot{\theta}_t}{\theta_t}\right]\approx\lim_{p_t\to1^-}\left[\frac{\dot{p}_t}{(1-p_t)}\right]=\infty\times\sign(\dot{p}_t)$.
-In this situation, the drift for $Z_t$ tends to $\infty\times\sign(\dot{p}_t)$.
-
-\end{itemize}
-\quad\\
-\alert{Maybe we can use a model where $\theta_t=\theta_0$ only in the diffusion. The SDE would remain between 0 and 1, and the Lamperti transform would be simpler.}
-
-\end{frame}
-
-%\setbeamercolor{background canvas}{bg=white!10}
-%\begin{frame}\frametitle{Plotting the drift for $Z_t$: ($\theta_t$ and $\dot{\theta}_t$ with artificial definitions)}
-%
-%\graphicspath{{../../Mathematica_Files/}}
-%
-%\begin{table}[]
-%\begin{tabular}{lll}
-% \includegraphics[width=0.3\columnwidth]{drift_z_1.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_2.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_3.pdf} \\
-% {\tiny$p_t=0,\alpha=0.1,\dot{p}_t=1,\theta_t=1,\dot{\theta}_t=0$} & {\tiny$p_t=0,\alpha=0.1,\dot{p}_t=1,\theta_t=1,\dot{\theta}_t=1000$} & {\tiny$p_t=1,\alpha=0.1,\dot{p}_t=-1,\theta_t=1,\dot{\theta}_t=0$} \\
-% \includegraphics[width=0.3\columnwidth]{drift_z_4.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_5.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_6.pdf} \\
-% {\tiny$p_t=1,\alpha=0.1,\dot{p}_t=-1,\theta_t=1,\dot{\theta}_t=1000$} & {\tiny$p_t=1/2,\alpha=0.1,\dot{p}_t=1,\theta_t=1,\dot{\theta}_t=0$} & {\tiny$p_t=1/2,\alpha=0.1,\dot{p}_t=-1,\theta_t=1,\dot{\theta}_t=0$}
-%\end{tabular}
-%\end{table}
-%
-%\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{$X_t$, $V_t$, $Z_t$, and $Y_t$:}
-
-It is essential to understand what happens with the domain of each process to have a correct intuition about the SDEs.
-
-\begin{enumerate}
-\item $X_t\in\alert{[0},{\color{blue}1]}$.
-\item $V_t\in\alert{[-p_t},{\color{blue}1-p_t]}$.
-\item $Z_t\in\alert{\Big[-\frac{\pi}{\sqrt{2\alpha\theta_t}}},{\color{blue}0\Big]}$.
-\item $Y_t\in{\color{red}\Big[-\frac{\pi}{2}},{\color{blue}0\Big]}$.
-\end{enumerate}
-Notice that none of the changes of variables inverters the domain (red corresponds to red, and blue to blue).
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Plotting the drift for $Z_t$: ($\theta_t$ and $\dot{\theta}_t$ with real definitions, and $\ddot{p}_t=0$)}
-
-\graphicspath{{../../Mathematica_Files/}}
-
-\begin{table}[]
-\begin{tabular}{lll}
- \includegraphics[width=0.3\columnwidth]{drift_z_7.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_8.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_9.pdf} \\
- {\tiny$p_t=0.01,\alpha=0.1,\dot{p}_t=0.1$ (common case).} & {\tiny$p_t=0.01,\alpha=0.1,\dot{p}_t=-0.1$ (\alert{uncommon case}).} & {\tiny$p_t=0.99,\alpha=0.1,\dot{p}_t=0.1$ (\alert{uncommon case}).} \\
- \includegraphics[width=0.3\columnwidth]{drift_z_10.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_11.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_12.pdf} \\
- {\tiny$p_t=0.99,\alpha=0.1,\dot{p}_t=-0.1$ (common case).} & {\tiny$p_t=1/2,\alpha=0.1,\dot{p}_t=0.2$ (common case).} & {\tiny$p_t=1/2,\alpha=0.1,\dot{p}_t=-0.2$ (common case).}
-\end{tabular}
-\end{table}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Plotting the drift for $Z_t$: ($\theta_t$ and $\dot{\theta}_t$ with real definitions, and $\ddot{p}_t=0$)}
-
-\graphicspath{{../../Mathematica_Files/}}
-
-\begin{table}[]
-\begin{tabular}{lll}
- \includegraphics[width=0.3\columnwidth]{drift_z_13.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_14.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_15.pdf} \\
- {\tiny$p_t=0.1,\alpha=0.1,\dot{p}_t=0.15$ (common case).} & {\tiny$p_t=0.1,\alpha=0.1,\dot{p}_t=-0.15$ (\alert{uncommon case}).} & {\tiny$p_t=0.9,\alpha=0.1,\dot{p}_t=0.15$ (\alert{uncommon case}).} \\
- \includegraphics[width=0.3\columnwidth]{drift_z_16.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_17.pdf} & \includegraphics[width=0.3\columnwidth]{drift_z_18.pdf} \\
- {\tiny$p_t=0.9,\alpha=0.1,\dot{p}_t=-0.15$ (common case).} & {\tiny$p_t=0.1,\alpha=0.1,\dot{p}_t=0.05$ (common case).} & {\tiny$p_t=0.9,\alpha=0.1,\dot{p}_t=-0.05$ (common case).}
-\end{tabular}
-\end{table}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Professor Kebaier's condition: (In this slide, we remove the time subindex)}
-
-We assume that \textbf{1)} $0<\alpha<\frac{1}{2}$, and \textbf{2)} $\alpha\theta\leq\dot{p}+\theta p\leq(1-\alpha)\theta$.\\
-\quad\\
-From \textbf{2)}: $\frac{\alpha\theta-\dot{p}}{p}\leq\theta\leq\frac{\theta-\alpha\theta-\dot{p}}{p}$ (recall $p\in[0,1]$, but in this step we assume $p\neq0$).
-We well check the two inequalities ${\color{red}\frac{\alpha\theta-\dot{p}}{p}\leq\theta}$ and ${\color{blue}\theta\leq\frac{\theta-\alpha\theta-\dot{p}}{p}}$.\\
-\quad\\
-${\color{blue}\theta(1-p-\alpha)\geq\dot{p}}$ is implied by the more restrictive inequality ${\color{orange}\theta(1-p-\alpha)\geq|\dot{p}|}$.
-If we assume that $1-p-\alpha>0$ (or equivalently $p<1-\alpha$), we have the more restrictive inequality ${\color{orange}\theta\geq\frac{|\dot{p}|}{(1-p-\alpha)}}$ which implies the {\color{blue}blue one}.\\
-\quad\\
-\alert{$\theta(\alpha-p)\leq\dot{p}$} is equivalent to ${\color{violet}\theta\geq\frac{\dot{p}}{\alpha-p}}$ assuming that $\alpha-p<0$ (or $p>\alpha$).
-Now, {\color{violet}violet} is implied by the more restrictive inequality ${\color{brown}\theta\geq\left|\frac{\dot{p}}{\alpha-p}\right|=\frac{|\dot{p}|}{p-\alpha}}$.\\
-\quad\\
-Combining the two assumptions, we have that \textbf{2)} is true if $\alpha<p<1-\alpha$, and $\theta=\max\left(\theta_0,\frac{|\dot{p}|}{\min(p-\alpha,1-p-\alpha)}\right)$.
-For very small $\alpha$, we recuperate our classical condition.
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Professor Kebaier's Lamperti SDE:}
-
-If we fix $\theta_t=\theta_0$ in the diffusion in both SDEs (our original one and Kebaier's one), then assuming the new condition $\alpha<p<1-\alpha$, we have that both SDEs share the same Lamperti transform (up to the definition of $\theta_t$ in the drift).
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=green!20}
-\begin{frame}
-
-{\Huge New Model}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{New model for the SDE: $\theta_t=\theta_0$ in the diffusion}
-
-\begin{enumerate}
-
-\item[$X_t$:] $\dif X_t=\left(\dot p_t-\theta_t(X_t-p_t)\right)\dif t+\sqrt{2\alert{\theta_0}\alpha X_t(1-X_t)}\dif W_t$
-\item[$V_t$:] $\dif V_t=-\theta_tV_t\dif t+\sqrt{2\alert{\theta_0}\alpha(V_t+p_t)(1-V_t-p_t)}\dif W_t$
-
-\end{enumerate}
-Lamperti transform for $V_t$:
-\begin{equation*}
-\begin{split}
-\psi(V_t,t)=\int\frac{1}{\sqrt{2\alert{\theta_0}\alpha(u+p_t)(1-u-p_t)}}\dif u\Bigg|_{u=V_t}&=-\sqrt{\frac{2}{\alpha\alert{\theta_0}}}\arcsin\left(\sqrt{1-V_t-p_t}\right),\\
-&=-\sqrt{\frac{2}{\alpha\alert{\theta_0}}}\arcsin\left(\sqrt{1-X_t}\right).
-\end{split}
-\end{equation*}
-
-We can see that for every $t=t^*$, the primitive function of $\frac{1}{\sigma(v,t^*)}$ is well defined for all $v\in\left[-p(t^*),1-p(t^*)\right]\subset[-1,1]$ (recall $v=x-p_t$, and $x\in[0,1]$).
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Identities for the Lamperti transform of $V_t$:}
-
-\begin{itemize}
-\item $\psi(V_t,t)=-\sqrt{\frac{2}{\alpha\alert{\theta_0}}}\arcsin(\sqrt{1-V_t-p_t})$.
-\item $\psi_v(V_t,t)=\frac{1}{\sigma(V_t,t)}$.
-\item $\psi_{vv}(V_t,t)=\frac{\dif}{\dif v}\left[\frac{1}{\sigma(V_t,t)}\right]=-\frac{\sigma_v(V_t,t)}{\sigma^2(V_t,t)}=-\frac{1}{\sigma^2(V_t,t)}\cdot\sqrt{\frac{\alpha\alert{\theta_0}}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}$.
-\item $\psi_t(V_t,t)=\frac{\dot{p}_t}{\sqrt{2\alpha\alert{\theta_0}(V_t+p_t)(1-V_t-p_t)}}$.
-\end{itemize}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: ({\color{green}Verified with Mathematica})}
-
-By It\^o's lemma, if $\psi(v,t)$ is $C^2([-p_t,1-p_t])$ for $v$ and $C^1([0,T])$ for $t$, then:
-\begin{equation*}
-\dif Z_t=\left({\color{blue}\psi_t}+\psi_v\cdot f+\alert{\frac{1}{2}\psi_{vv}\cdot\sigma^2}\right)\dif t+\psi_v\cdot\sigma\dif W_t.
-\end{equation*}
-If we substitute the terms related with $\psi(V_t,t)$:
-\begin{equation*}
-{\footnotesize
-\begin{split}
-\dif Z_t=&\Bigg[{\color{blue}\frac{\dot{p}_t}{\sqrt{2\alpha\theta_0(V_t+p_t)(1-V_t-p_t)}}}\\
-&-\frac{\theta_tV_t}{\sqrt{2\alpha\theta_0(V_t+p_t)(1-V_t-p_t)}}\alert{-\frac{1}{2}\sqrt{\frac{\alpha\theta_0}{2}}\frac{1-2V_t-2p_t}{\sqrt{(V_t+p_t)(1-V_t-p_t)}}}\Bigg]\dif t+1\cdot \dif W_t.
-\end{split}}
-\end{equation*}
-Recall $\alert{Z_t=-\sqrt{\frac{2}{\alpha\theta_t}}\arcsin\left(\sqrt{1-V_t-p_t}\right)}$, where $Z_t\in\Big[-\frac{\pi}{\sqrt{2\alpha\theta_t}},{\color{black}0\Big]}$.
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{SDE for $Z_t=\psi(V_t,t)$: ({\color{green}Computed with Mathematica})}
-
-\begin{equation*}
-\dif Z_t=\underbrace{\left[\frac{\alpha\theta_0\cos(Z_t\sqrt{2\alpha\theta_0})-\theta_t\cos(Z_t\sqrt{2\alpha\theta_0})+2\theta_tp_t+2\dot{p}_t-\theta_t}{\sqrt{\alpha\theta_0}\sqrt{1-\cos(2Z_t\sqrt{2\alpha\theta_0})}}\right]}_{f(Z_t,t)}\dif t+1\cdot\dif W_t.
-\end{equation*}\\
-\begin{equation*}
-\lim_{z\to0^-}f(z,t)=\infty\times\left[\frac{\sign\left(2\theta_tp_t+2\dot{p}_t+\alpha\theta_0-2\theta_t\right)}{\sign(\alpha)\sign(\theta_0)}\right].
-\end{equation*}
-\begin{equation*}
-\lim_{z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+}f(z,t)=\infty\times\left[\frac{\sign\left(2\theta_tp_t+2\dot{p}_t-\alpha\theta_0\right)}{\sign(\alpha)\sign(\theta_0)}\right].
-\end{equation*}
-We want to find the correct conditions for $\theta_t$.\\
-\quad\\
-{\small To simplify the SDE, Mathematica has used: $\sin^2(x)-\sin^4(x)=\sin^2(x)\cos^2(x)=\frac{1}{4}\sin^2(2x)=\frac{1}{8}(1-\cos(4x))$.}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Limit when $z\to0^-$:}\label{C1}
-
-Recall we have a bijective mapping $Z_t({\color{blue}[0},\alert{1]})={\color{blue}\Big[\frac{-\pi}{\sqrt{2\alpha\theta_0}}},\alert{0\Big]}$.\\
-\quad\\
-We want $\alpha\theta_0-2\theta_t+2\theta_tp_t+2\dot{p}_t\leq0$ so we do not scape from $x=1$ to $x>1$. Then:
-\begin{itemize}
-
-\item If $p_t<1$, we have that ${\color{orange}\theta_t\geq\frac{\alpha\theta_0+2\dot{p}_t}{2(1-p_t)}}$.
-\item If $p_t=1$, $\lim_{z\to0^-}f(z,t)=\alpha\theta_0+2\dot{p}_t$.\\
-\alert{Then, if $\alpha\theta_0>|2\dot{p}_t|$, we scape from $x=1$ to $x>1$.}
-
-\end{itemize}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Limit when $z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+$:}\label{C2}
-
-Recall we have a bijective mapping $Z_t({\color{blue}[0},\alert{1]})={\color{blue}\Big[\frac{-\pi}{\sqrt{2\alpha\theta_0}}},\alert{0\Big]}$.\\
-\quad\\
-We want $2\theta_tp_t+2\dot{p}_t-\alpha\theta_0\geq0$ so we do not scape from $x=0$ to $x<0$. Then:
-\begin{itemize}
-
-\item If $p_t>0$, we have that ${\color{orange}\theta_t\geq\frac{\alpha\theta_0-2\dot{p}_t}{2p_t}}$.
-\item If $p_t=0$, $\lim_{z\to\left[\frac{-\pi}{\sqrt{2\alpha\theta_0}}\right]^+}f(z,t)=2\dot{p}_t-\alpha\theta_0$.\\
-\alert{Then, if $\alpha\theta_0>|2\dot{p}_t|$, we scape from $x=0$ to $x<0$.}
-
-\end{itemize}
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Controlled drift:}
-
-From both {\color{orange}orange} conditions in slides (\ref{C1}) and (\ref{C2}), we create a more restrictive condition:
-\begin{equation*}
-\max\left({\color{orange}\frac{\alpha\theta_0+2\dot{p}_t}{2(1-p_t)}},{\color{orange}\frac{\alpha\theta_0-2\dot{p}_t}{2p_t}}\right)\leq\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}.
-\end{equation*}
-Then, we choose
-\begin{equation}
-\theta_t=\max\left(\theta_0,\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}\right).
-\label{NC}
-\end{equation}
-\alert{Notice that we still need $\alpha\theta_0>|2\dot{p}_t|$ when $\{x=0,p=0\}$ or $\{x=1,p=1\}$.} As we no control over this condition, it is enough to ensure that we never reach these pairs $\{x,p_t\}$.\\
-\quad\\
-Recall that in the paper, we start by choosing $\theta_t=\max\left(\theta_0,\frac{|\dot{p}_t|}{\min(1-p_t,p_t)}\right)$. Our new condition (\ref{NC}) is mroe restrictive.
-
-\end{frame}
-
-\setbeamercolor{background canvas}{bg=white!10}
-\begin{frame}\frametitle{Conditions summary:}
-
-\begin{itemize}
-
-\item Initial condition: $\theta_t^{initial}=\max\left(\theta_0,\frac{|\dot{p}_t|}{\min(1-p_t,p_t)}\right)$
-\item New condition from Lamperti: $\theta_t^{lamperti}=\max\left(\theta_0,\frac{\alpha\theta_0+|2\dot{p}_t|}{2\min(1-p_t,p_t)}\right)$.
-Also, we need that $\alpha\theta_0>|2\dot{p}_t|$ when $\{x=0,p=0\}$ or $\{x=1,p=1\}$.
-Notice $\theta_t^{initial}\leq\theta_t^{lamperti}$.
-\item Professor Kebaier's condition: $0<\alpha<1/2$, $\alpha<p_t<1-\alpha$, and $\theta_t^{kebaier}=\max\left(\theta_0,\frac{|\dot{p}|}{\min(p-\alpha,1-p-\alpha)}\right)$.
-
-\end{itemize}
-Now, given $p_t<1/2$, we have that $\theta_t^{lamperti}=\theta_t^{kebaier}$ if $\theta_0=\frac{|2\dot{p}_t|}{p_t-\alpha}$ (assuming that in both cases the maximum is not $\theta_0$).
-Then, how much each one is restrictive depends on $|\dot{p}_t|$ and $p_t$.\\
-Conditions $0<\alpha<1/2$ and $\alpha<p_t<1-\alpha$ implies that we never have $\{x=0,p=0\}$ or $\{x=1,p=1\}$
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.48\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/Gauss_Approx_Measurements_Error.eps}\quad
+\includegraphics[width=0.48\textwidth]{../../../Python/Represas_Data_2/Wind_Data/someResults/final/Gauss_Approx_Measurements_Lamperti.eps}
+\end{figure}
 

### 2020-08-05 Reports/20200402 - Moments/20200402 - Moments.tex
Updated main files

\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{commath}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{siunitx}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}
\DeclareMathOperator{\sign}{sign}

\title{Error SDE ($V_t$) moments}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Introduction:} \label{S1}

In the next four slides, we will show approximations for the first and the second moment of the Error process SDE (the error $V_t$). We do the next for each moment:\\
\quad\\
We solve the moments ODE for only one $\Delta t$, corresponding to the minimum time between two real measurements (10 minutes or $1/(24*60)$ with no dimensions). We have three main times, $t_0$, $t_1=t_0+\Delta t$, and $t_2=t_0+2\Delta t$. We sweep over $p_{t_0}$, but we fix $p_{t_1}=p_{t_2}=1/2$. $p_{t_0}\in[p_{t_1}-0.03,p_{t_1}+0.03]$, because the maximum $\Delta p$ measured during the year follows $|\Delta p|<0.03$. In the case of the initial error $V_{t_0}$, we have that $V_{t_0}\in[-0.2,0.2]$, for the same reason.\\
\quad\\
To find the empirical moments, we simulate thousands of times the corresponding SDEs for only one time transition $\Delta t$, and average the solution at time $t_1$.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $V_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/moments/classic/1.eps}\quad
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/moments/classic/2.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated first moment for $V_t$:} \label{EM1}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/moments/classic/3.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated second moment for $V_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/moments/classic/4.eps}\quad
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/moments/classic/5.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated second moment for $V_t$:} \label{EM2}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/moments/classic/6.eps}
\end{figure}

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Error in the moments (1/2):}

In the next plot, we sweep over the value of $p_{t_1}$ from 0.2 to 0.8 (we still fix $p_{t_1}=p_{t_2}$).\\
\quad\\
For each value of $p_{t_1}$, we repeat the procedure of slide (\ref{S1}). After we have the error matrices (see slides \ref{EM1} and \ref{EM2}), we just compute the average for each matrix. The result can be seen in the next slide.

\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Error in the moments (2/2):}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/moments/classic/7.eps}
\end{figure}

\end{frame}

\end{document}
